### 2017-02-21 paper/manuscript.tex
added a manuscript

\documentclass[11pt]{article}

%==============Packages & Commands==============
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{tikz}
%%%<
\usepackage{verbatim}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture}
%\setlength\PreviewBorder{5pt}%

\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
% \geometry{a4paper}                   		% ... or a4paper or a5paper or ...
%\geometry{landscape}                		% Activat\usetikzlibrary{arrows}e for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex
\usepackage{amssymb}

\usepackage[ruled,vlined]{algorithm2e}
\usetikzlibrary{arrows}
\usepackage{alltt}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage[longnamesfirst]{natbib} % For references
\bibpunct{(}{)}{;}{a}{}{,} % Reference punctuation
\usepackage{changepage}
\usepackage{setspace}
\usepackage{booktabs} % For tables
\usepackage{rotating} % For sideways tables/figures
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{color}
\usepackage{dcolumn}
\usepackage{comment}
%\usepackage{fullwidth}
\newcolumntype{d}[1]{D{.}{\cdot}{#1}}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{3}{D{.}{.}{3}}
\newcolumntype{4}{D{.}{.}{4}}
\newcolumntype{5}{D{.}{.}{5}}
\usepackage{float}
\usepackage[hyphens]{url}
%\usepackage[margin = 1.25in]{geometry}
%\usepackage[nolists,figuresfirst]{endfloat} % Figures and tables at the end
\usepackage{subfig}
\captionsetup[subfloat]{position = top, font = normalsize} % For sub-figure captions
\usepackage{fancyhdr}
%\makeatletter
%\def\url@leostyle{%
%  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%\makeatother
%% Now actually use the newly defined style.
\urlstyle{same}
\usepackage{times}
% \usepackage{mathptmx}
%\usepackage[colorlinks = true,
%						bookmarksopen = true,
%						pagebackref = true,
%						linkcolor = black,
%						citecolor = black,
% 					urlcolor = black]{hyperref}
%\usepackage[all]{hypcap}
%\urlstyle{same}
\newcommand{\fnote}[1]{\footnote{\normalsize{#1}}} % 12 pt, double spaced footnotes
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
\def\citeaposs#1{\citeauthor{#1}' (\citeyear{#1})}
\newcommand{\bm}[1]{\boldsymbol{#1}} %makes bold math symbols easier
\newcommand{\R}{\textsf{R}\space} %R in textsf font
\newcommand{\netinf}{\texttt{NetInf}\space} %R in textsf font
\newcommand{\iid}{i.i.d} %shorthand for iid
\newcommand{\cites}{{\bf \textcolor{red}{CITES}}} %shorthand for iid
%\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{*0}{*0}
%\titlespacing{\subsection}{0pt}{*0}{*0}
%\titlespacing{\subsubsection}{0pt}{*0}{*0}
%\setlength{\parskip}{0pt}
%\setlength{\parsep}{0pt}
%\setlength{\bibsep}{2pt}
%\renewcommand{\headrulewidth}{0pt}

%\renewcommand{\figureplace}{ % This places [Insert Table X here] and [Insert Figure Y here] in the text
%\begin{center}
%[Insert \figurename~\thepostfig\ here]
%\end{center}}
%\renewcommand{\tableplace}{%
%\begin{center}
%[Insert \tablename~\theposttbl\ here]
%\end{center}}

\newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\Y}{\bm{\mathcal{Y}}}
\newcommand{\bZ}{\bm{Z}}

\usepackage[colorlinks = TRUE, urlcolor = black, linkcolor = black, citecolor = black, pdfstartview = FitV]{hyperref}

%============Article Title, Authors==================
\title{\vspace{-2cm} Content of Municipal Government Websites }

\author{ Markus Neumann \and Bruce Desmarais \and Hanna Wallach} \date{\today}

%===================Startup=======================
\begin{document}
\maketitle

%=============Abstract & Keywords==================

\begin{abstract}

\noindent We study the content of municipal government websites....

\end{abstract}
\thispagestyle{empty}
% \doublespacing
% Description of the possible challenges
\section{Introduction}

\newpage

\bibliographystyle{apsr}
\bibliography{ref}

\end{document}

### 2017-02-21 paper/src/.BatchJobs.R

@@ -1,0 +1,1 @@
+cluster.functions = makeClusterFunctionsTorque("template.tmpl")

### 2017-02-21 paper/src/analysis.R

@@ -1,0 +1,80 @@
+pkgs <- c("dplyr", "reshape2", "ggplot2", "stringr", "coda", "scales")
+invisible(lapply(pkgs, library, character.only = TRUE))
+
+results <- read.csv("results.csv", stringsAsFactors = FALSE) %>%
+  select(-one_of("X", "prob", "repl", "id")) %>%
+  rename(model = algo) %>%
+  mutate(model = ifelse(!is.na(scale) & scale, "lsm_scaled", model)) %>%
+  mutate(model = ifelse(!is.na(beta.var), paste0(model, " (beta.var = ", beta.var, ")"), model)) %>%
+  filter(eta != .1 & !(model == "truth" & latent_space == 0)) %>%
+  mutate(bias = estimate - beta, error = ifelse(beta == 0, 1 - coverage, coverage),
+         type = ifelse(beta == 0, 1, 2)) %>%
+  group_by(model, family, eta, beta, type, latent_space, nodes) %>%
+  summarise(n = length(estimate[!is.na(estimate)]),
+            estimate = mean(estimate, na.rm = TRUE),
+            loss = mean(loss, na.rm = TRUE),
+            coverage = mean(coverage, na.rm = TRUE),
+            bias = mean(bias, na.rm = TRUE),
+            error = mean(error, na.rm = TRUE))
+results$family[results$family == "binomial"] <- "bernoulli"
+
+ggplot(results, aes(eta, n, color = model, linetype = model)) +
+  scale_x_log10(breaks = c(1, 100, 1000000), labels = c("uniform correlation", "low correlation", "independence")) +
+  scale_y_log10() +
+  geom_point() + geom_line() +
+  facet_grid(family + beta ~ nodes + latent_space, scales = "free", labeller = label_context) +
+  labs(x = expression(eta), y = "Iterations Completed") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "bottom")
+ggsave("iterations.png", width = 12, height = 8)
+
+ggplot(filter(results, beta == 1), aes(eta, loss, color = model, linetype = model)) +
+  scale_x_log10(breaks = c(1, 100, 1000000), labels = c("uniform correlation", "low correlation", "independence")) +
+  geom_point() + geom_line() +
+  facet_grid(family ~ nodes + latent_space, scales = "free", labeller = label_context) +
+  labs(x = expression(eta), y = "Mean Squared Error", title = "Generalization Error") +
+  theme_bw() +
[…]

### 2017-02-21 paper/src/simulation.R

@@ -1,0 +1,232 @@
+library("BatchExperiments")
+library("latentnet")
+library("foreach")
+library("clusterGeneration")
+library("iterators")
+
+create_network <- function(y, name = "eweight") {
+  library("network")
+  net <- network(y, directed = FALSE)
+  el <- as.matrix(net, "edgelist")
+  w <- y[el]
+  set.edge.attribute(net, name, w)
+  net
+}
+
+rmvnorm_d <- function(sigma, d) {
+  library("mvtnorm")
+  
+  var_d <- var(d)
+  mu_d <- mean(d)
+  n_var <- ncol(sigma)
+  d_inv <- solve(as.matrix(var_d))
+  sigma_x <- sigma[1:(n_var - 1), 1:(n_var - 1)] - sigma[1:(n_var - 1), n_var] %*%
+    d_inv %*% sigma[n_var, 1:(n_var - 1)]
+  mu_x <- sapply(d, function(z) sigma[1:(n_var - 1), n_var] %*% d_inv %*% z - mu_d)
+  if (!is.matrix(mu_x))
+    as.matrix(sapply(mu_x, rnorm, n = 1, sd = sqrt(sigma_x)))
+  else
+    t(apply(mu_x, 2, function(mu) rmvnorm(1, mu, sigma_x)))
+}
+
+ms_error <- function(x, y, each_column = FALSE) {
+  if (each_column)
+    sapply((x - y)^2, mean)
+  else
+    mean((x - y)^2)
+}
+
+unstack_vector <- function(x, n) {
+  idx <- t(combn(1:n, 2))
+  mat <- diag(n)
+  mat[idx] <- x
+  mat[idx[, c(2, 1)]] <- x
+  stopifnot(isSymmetric(mat))
+  mat
+}
+
+diagnostic <- function(fit) {
+  stopifnot(any(class(fit) %in% "glm"))
+  SVD <- svd(scale(solve(vcov(fit)), center = FALSE))
+  max_d <- max(SVD$d)
+  CI <- sapply(SVD$d, function(x) max_d / x)
+  phi <- t((SVD$v %*% diag(1 / SVD$d))^2)
+  pi <- prop.table(phi, 2)
+  out <- data.frame(CI, pi)
+  colnames(out) <- c("ci", names(coef(fit)))
+  round(out, 3)
+}
+
+create_data <- function(static, family, eta, nodes, beta, latent_space) {
+  library("clusterGeneration")
+
[…]

### 2017-02-23 paper/manuscript.tex
removed uncomments of packages I did earlier

@@
 
+\section{Data}
+The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
+This list is updated once per month - we rely on the version released on January 16, 2017.
+The data from the GSA contains the following variables: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV').
+Two, the type of government entity to which the domain is registered, such as city, county, federal agency, etc.
+Three, for federal agencies, the name is specfied.
+Finally, the city in which the domain is registered, is noted.
+
+Here, we focus only on cities.
+As a first step, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver) to test whether all of the city websites actually work.
+Of the 2425 domains listed by the GSA as cities, 292 are not accessible.
+Furthermore, the .gov domain, as registered at the GSA, is frequently not the website a city actually uses.
+In many cases, these sites redirect to another address, sometimes not a .gov domain (in this case, we simply use this domain).
+We record these URLs, as they are required to retrieve the images websites stored in the Wayback Machine (WbM).
+
+In order to provide an overview of our coverage (as not all cities, towns and villages use .gov addresses), we merge this list with U.S.
+Census data\footnote{http://www2.census.gov/programs-surveys/popest/datasets/2010-2015/cities/totals/sub-est2015\_all.csv}.
+Here, several limitations in the GSA data need to be accounted for: One, even though the GSA nominally separates websites of cities and counties, some of the domains categorized as cities actually belong to counties.
+The same is true for townships and boroughs.
+Ergo, we eliminate all websites belonging to these three types of entities by hand.
+Furthermore, the city name, as given by the GSA, refers to the city in which the domain is registered, which is not necessarily equivalent to the city the website serves.
+In many cases, a website of a larger city may be registered to one of its subdivisions (for example, the website of New York is registered to Brooklyn), or vice versa (for example, the website of Homecroftin, a small town within Indianapolis, is registered to the city as a whole).
+Consequently we fix mismatches between websites and cities manually.
+Finally, a number of cities are simply misspelled, which we also correct by hand.
+
+After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
+
+These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
+
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
+\end{figure}
+
+We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
+To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
+We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
+
+<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
+Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
+
+% latex table generated in R 3.3.2 by xtable 1.8-2 package
+% Wed Feb 22 14:08:54 2017
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{rr}
+		\hline
+		& V1 \\
+		\hline
+		.asp &   1 \\
+		.aspx &  43 \\
+		.css &  32 \\
+		.doc &  35 \\
+		.docx &   5 \\
+		.eot &   1 \\
+		.gif &  99 \\
+		.GIF &   1 \\
+		.htm &   2 \\
+		.html & 819 \\
+		.ico &   1 \\
+		.jpg & 131 \\
+		.JPG &  26 \\
+		.js &  51 \\
+		.Net &  12 \\
+		.pdf & 1371 \\
+		.PDF &  50 \\
+		.png & 210 \\
+		.PNG &   1 \\
+		.ppt &   1 \\
+		.swf &   1 \\
+		.ttf &   3 \\
+		.txt &   1 \\
+		.woff &   2 \\
+		.xls &   2 \\
+		.xlsx &   6 \\
+		.xml &   3 \\
+		\hline
+	\end{tabular}
+\end{table}
+
 \newpage

### 2017-02-23 paper/manuscript.tex
improved file type and size tables

@@
 % latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Wed Feb 22 14:08:54 2017
+% Wed Feb 22 21:39:50 2017
 \begin{table}[ht]
 	\centering
-	\begin{tabular}{rr}
+	\begin{tabular}{lr}
 		\hline
-		& V1 \\
+		File type & Occurrences \\ 
 		\hline
+		.pdf & 1371 \\ 
+		.html & 819 \\ 
+		.png & 210 \\ 
+		.jpg & 131 \\ 
+		.gif &  99 \\ 
+		.js &  51 \\ 
+		.PDF &  50 \\ 
+		.aspx &  43 \\ 
+		.doc &  35 \\ 
+		.css &  32 \\ 
+		.JPG &  26 \\ 
+		.Net &  12 \\ 
+		.xlsx &   6 \\ 
+		.docx &   5 \\ 
+		.ttf &   3 \\ 
+		.xml &   3 \\ 
+		.htm &   2 \\ 
+		.woff &   2 \\ 
+		.xls &   2 \\ 
 		.asp &   1 \\ 
-		.aspx &  43 \\
-		.css &  32 \\
-		.doc &  35 \\
-		.docx &   5 \\
 		.eot &   1 \\ 
-		.gif &  99 \\
 		.GIF &   1 \\ 
-		.htm &   2 \\
-		.html & 819 \\
 		.ico &   1 \\ 
-		.jpg & 131 \\
-		.JPG &  26 \\
-		.js &  51 \\
-		.Net &  12 \\
-		.pdf & 1371 \\
-		.PDF &  50 \\
-		.png & 210 \\
 		.PNG &   1 \\ 
@@
 		.swf &   1 \\ 
-		.ttf &   3 \\
 		.txt &   1 \\ 
-		.woff &   2 \\
-		.xls &   2 \\
-		.xlsx &   6 \\
-		.xml &   3 \\
 		\hline
 	\end{tabular}
+	\caption{File types in scraped websites} 
+\end{table}
+
+% latex table generated in R 3.3.2 by xtable 1.8-2 package
+% Wed Feb 22 21:35:10 2017
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{lrr}
+		\hline
+		Website & Files & Size (MB) \\ 
+		\hline
+		brownsvilletn.gov & 188 & 14328 \\ 
+		www.centralpointoregon.gov & 150 & 137440 \\ 
+		www.dedham-ma.gov & 603 & 212572 \\ 
+		www.duncanok.gov &  84 & 47064 \\ 
+		www.dutchessny.gov & 110 & 291376 \\ 
+		www.ennistx.gov & 200 & 26244 \\ 
+		www.greenvillenc.gov & 333 & 25732 \\ 
+		www.romi.gov & 491 & 112584 \\ 
+		www.trumbull-ct.gov & 787 & 191540 \\ 
+		www.westonct.gov & 861 & 213140 \\ 
+		\hline
+	\end{tabular}
+	\caption{Test websites} 
 \end{table}

### 2017-02-23 govWebsitesFiletypes.R

@@ -1,28 +1,47 @@
+#This script extracts the filetypes, folder sizes, etc.
+#from the 10 test cases scraped from the Wayback Machine
+
 setwd("/home/markus/Dropbox/4_RA/govWebsites/websites/")
 
-a <- list.files(recursive = T, all.files=T)
-list.dirs(recursive = T)
-#aa <- system(sprintf('ls %s', getwd()), intern=TRUE)
-dir(pattern = ".html$", recursive = T)
+a <- list.files(recursive = T) #create a list of all files in all subdirectories
 
+#file types
 library(stringr)
+#extract file type
 b <- str_extract(a,"(\\.[^.]+)$")
-c <- table(b[which(str_length(b)<6)])
-
+#create table for file types with at most 5 characters
+c <- data.frame(table(b[which(str_length(b)<6)]))
+names(c) <- c("File type","Occurrences")
+c <- c[-c(1:8),]
+c <- c[order(c$Occurrences, decreasing = T),]
 library(xtable)
-xtable(c[10:36])
+#omit some of the less useful types and turn table into latex object
+print(xtable(c, caption="File types in scraped websites"), include.rownames = F)
 
-##folder size
-d <- list.files() #list.dirs(recursive = F)
+
+#folder size
+#get folder names
+d <- list.files()
+e <- vector()
+#print directory size with Linux command 'du -s'
 for(i in 1:10){
-  system(paste("du",d[i],"-s"))
+  e[i] <- system(paste("du",d[i],"-s"), intern=T)
 }
+#split character vector into dataframe
+require(reshape2)
+f <- colsplit(e,"\\t",c("Size (MB)","Website"))
 
-system("du -s")
 
 ##number of files
-abc <- vector()
+g <- vector()
+#number of files per website/folder
 for(i in 1:10){
-abc[i] <- length(list.files(list.files()[i],recursive = T, all.files=T))
+g[i] <- length(list.files(list.files()[i],recursive = T, all.files=T))
 }
-abc
+#add to data frame created above
+f$Files <- g
+#re-order and turn table into latex object
+print(xtable(f[,c(2,3,1)], caption="Test websites"), include.rownames = F)
+
+
+rm(a,b,c,d,e,f,g,i)

### 2017-03-01 paper/manuscript.tex
added top term frequencies

@@
 
+% latex table generated in R 3.3.2 by xtable 1.8-2 package
+% Wed Mar  1 11:55:24 2017
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{rr}
+		\hline
+		& tf \\ 
+		\hline
+		tax & 176324 \\ 
+		date & 98949 \\ 
+		due & 97192 \\ 
+		amt & 96382 \\ 
+		town & 86726 \\ 
+		value & 81119 \\ 
+		total & 70825 \\ 
+		parcel & 63589 \\ 
+		county & 56201 \\ 
+		market & 51758 \\ 
+		east & 51357 \\ 
+		full & 51199 \\ 
+		nrth & 50566 \\ 
+		book & 50306 \\ 
+		deed & 50231 \\ 
+		bill & 49719 \\ 
+		acres & 48935 \\ 
+		acct & 44871 \\ 
+		csd & 43792 \\ 
+		owners & 43510 \\ 
+		res & 41803 \\ 
+		family & 36883 \\ 
+		fire & 35156 \\ 
+		school & 33685 \\ 
+		name & 30382 \\ 
+		red & 30362 \\ 
+		taxable & 30248 \\ 
+		hook & 29902 \\ 
+		homestead & 29287 \\ 
+		outside & 28593 \\ 
+		\hline
+	\end{tabular}
+	\caption{Top term frequencies for 10 test websites} 
+\end{table}
+
 \newpage

### 2017-03-09 paper/manuscript.tex
added some questions about CA, and started some background work

@@
 \section{Introduction}
+
+\section{Background}
+
+\cite{grimmelikhuijsen2010transparency} run an experiment in which citizens are exposed to randomly selected levels of information about local government council minutes.
+They find a negative relationship between the information level and perceptions of competence in the local government.
+This raises an interesting question regarding whether citizens or more likely to participate when they perceive competence or when they perceive incompetence.
+
+\cite{wang2005evaluating} present a widely cited `model' for evaluating the accessibility of information on government websites.
+This is an important paper with which we should be familiar at a very detailed level as we use archived web content to assess the volume/accessibility of information provided by local governments.
+
+\cite{osman2014cobra} is less relevant, but they develop a multi-item measure to predict the level of citizen satisfaction with e-government services.
+
+\cite{grimmelikhuijsen2012developing} conduct an enormously relevant study.
+Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study.
+They focus on Dutch municipal websites, and their approach is fairly limited in scope and highly manual (which we can compliment).
+For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''
 
@@
 
+\subsection{California City Websites}
+
+It would be fine to focus on California as a case. First, we need to answer some preliminary questions about the data.
+
+\begin{enumerate}
+
+\item For what percentage and number of CA cities can we find data from the WBM?
+\item For how many election cycles can we find political leadership data for these matched cities?
+\item CA is a deep blue state, in what number and percentage of cities is the local leadership majority Republican? 
+\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
+
+\end{enumerate}
+
 \newpage

### 2017-03-22 paper/manuscript.tex
updated pdf

@@
 
+\subsection{Topic modeling}
+We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas.
+Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order.
+Documents uploaded to city websites are expected to be a reflection of these preferences.
+The author-topic model \citep{Rosen-Zvi2004} captures this concept quite well, because it assumes that different authors prefer different topics, each of which is associated with a group of words.
+We classify all documents that have been present before the change in party control as from one party\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
+If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
+The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
+Ideally, the result would then show significant\footnote{Though I am not sure how to calculate that.} differences in the probabilities of authors being assigned to partisan topics.
+
+Alternatively, the more commonplace LDA is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
+As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
+Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
+In a way, this captures the data-generating process more closely.
+
+Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
+One assumes that multiple authors write one document.
+This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
+This is not as good of a fit for city governments however.
+Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
+For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.
+
+Furthermore, if we only investigate cities in which control of government changes from one party to another, we may overestimate its effect.
+Not only does a transition in party control occur, but the person in charge also changes.
+Parties are fairly homogeneous, so that two mayors from the same party may have very different policy preferences and managerial styles.
+To remedy this problem, we [could] utilize matching, pairing our cases with similar cities in which the incumbent does not run for re-election, but party control stays the same nevertheless.
+
+Another problem with these generative models is that they ignore the fact that despite possible changes to websites due to a leadership transition, large parts of the content carry over.
+This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
+But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
+
+One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
+This way, we could identify directly which issues are considered to be the most divisive.
+
+Traditional author models that rely on lexical or syntactic differences may also be of use.
+Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles.
+However, it seems likely that personal rather than partisan authorship is playing an even larger role here.
+
+Another option, that I have not looked closely at yet, are (continuous) dynamic topic models by David Blei, which would allow us to model the progression of topics over time, i.e.
+when party control changes.
+
 \newpage
 
-\bibliographystyle{apsr}
+%\bibliographystyle{apsr} % apsr stopped working for me
+\bibliographystyle{plainnat}
 \bibliography{ref}

### 2017-03-23 paper/manuscript.tex
big push, adding several rscripts

@@
 
-\subsection{California City Websites}
+\subsection{Indiana City Websites}
 
-It would be fine to focus on California as a case. First, we need to answer some preliminary questions about the data.
+It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
 
@@
 
-\item For what percentage and number of CA cities can we find data from the WBM?
+\item For what percentage and number of IN cities can we find data from the WBM?
 \item For how many election cycles can we find political leadership data for these matched cities?
-\item CA is a deep blue state, in what number and percentage of cities is the local leadership majority Republican? 
+\item In what number and percentage of cities is the local leadership majority Republican? 
 \item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
@@
 \end{enumerate}
+
+\begin{enumerate}
+
+	\item 30 cities, with a combined population of 1,180,435.
+However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
+	\item 2015, 2011, 2007, 2003.
+	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
+	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
+
+\end{enumerate}
+
+% latex table generated in R 3.3.3 by xtable 1.8-2 package
+% Wed Mar 22 11:32:43 2017
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{lrrlrrl}
+		\hline
+		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
+		\hline
+		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
+		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
+		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
+		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
+		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
+		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
+		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
+		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
+		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
+		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
+		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
+		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
+		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
+		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
+		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
+		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
+		\hline
+	\end{tabular}
+	\caption{} 
+\end{table}
 
@@
 
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/wtpIndy.pdf}
+\end{figure}
+
 \newpage

### 2017-03-23 govWebsitesCensusMerge.R

@@ -234,6 +234,9 @@ data6 <- data6[,-c(23:30)]
 data9 <- merge(data8,data6, by.x="Group.1",by.y="StateCity",all.x = F,all.y = T)
 data9 <- data9[!duplicated(data9$Group.1),]
 
+#last minute correction
+data9$redirect[data9$City=="Indianapolis"] <- "http://www.indy.gov"
+
 #save results
 save(data9, file="data/govWebsitesVerifiedCensus.Rdata")
 

### 2017-03-23 govWebsitesIndiana2015.R

@@ -1,0 +1,173 @@
+setwd("D:/Dropbox/4_RA/govWebsites") #Windows
+setwd("~/Dropbox/4_RA/govWebsites") #Linux
+
+#2015
+mIN15 <- read.csv("data/mayorIN2015.csv", header = F)
+
+mIN15$V1 <- as.character(mIN15$V1)
+mIN15$V2 <- as.character(mIN15$V2)
+mIN15$V3 <- as.character(mIN15$V3)
+
+#clean up data - put city name, candidate name and votes in the correct column
+for(i in 1:nrow(mIN15)){
+  if(is.na(mIN15$V3[i])==T){
+    mIN15$V3[i] <- mIN15$V2[i]
+    mIN15$V2[i] <- mIN15$V1[i]
+    mIN15$V1[i] <- mIN15$V1[i-1]
+    }
+}
+
+mIN15$V3 <- as.numeric(mIN15$V3)
+
+#extract party
+library(stringr)
+mIN15$V4 <- str_extract(mIN15$V2,"\\((.+?)\\)$")
+mIN15$V5 <- str_extract(mIN15$V4," \\((.+?)\\)$")
+mIN15$V5 <- str_trim(mIN15$V5)
+mIN15$V4[is.na(mIN15$V5)==F] <- mIN15$V5[is.na(mIN15$V5)==F]
+#mIN15$V4 <- gsub("log\\(", "", mIN15$V4)
+mIN15$V4 <- gsub("(", "", mIN15$V4, fixed="TRUE")
+mIN15$V4 <- gsub(")", "", mIN15$V4, fixed="TRUE")
+
+mIN15$V5 <- 2015
+
+#2011
+mIN11 <- read.csv("data/mayorIN2011compatibility.csv", header = T)
+mIN11$District <- as.character(mIN11$District)
+
+for(i in 1:nrow(mIN11)){
+  if(mIN11$District[i]==""){
+    mIN11$District[i] <- mIN11$District[i-1]
+  }
+}
+
+#extract party
+library(stringr)
+mIN11$Party <- str_extract(mIN11$Candidate,"\\((.+?)\\)$")
+mIN11$Party2 <- str_extract(mIN11$Party,"\\s\\((.+?)\\)$")
+mIN11$Party2 <- str_trim(mIN11$Party2)
+mIN11$Party[is.na(mIN11$Party2)==F] <- mIN11$Party2[is.na(mIN11$Party2)==F]
[…]

### 2017-03-23 internetarchive_webarchive.R

@@ -1,5 +1,3 @@
-
-#
 setwd("/home/markus/Dropbox/4_RA/govWebsites")
 load("data/govWebsitesVerified.Rdata")
 

### 2017-03-23 websites/find_convert_pdfs.sh

@@ -1,5 +1,7 @@
+#make a new folder for just the pdfs
 mkdir pdfsfolder
+#copy pdfs in subdirectories to said pdf folder
 find . -name "*.pdf" -type f -exec cp {} ./pdfsfolder \;
 cd pdfsfolder
-#assuming that xpdf is installed:
+#assuming that xpdf is installed, convert pdfs to text
 for file in *.pdf; do pdftotext "$file" "$file.txt"; done

### 2017-03-23 websites/termFrequencies.R

@@ -1,10 +1,11 @@
 #This script extracts the top term frequencies from the pdfs in the 10 test websites
 #Script is pretty much entirely based on:
 #https://rstudio-pubs-static.s3.amazonaws.com/31867_8236987cf0a8444e962ccd2aec46d9c3.html
+require(tm)
 
 setwd("/home/markus/Dropbox/4_RA/govWebsites/websites/pdfsfolder/")
+setwd("D:/Dropbox/4_RA/govWebsites/websites/pdfsfolder/")
 
-require(tm)
 docs <- Corpus(DirSource(pattern = ".*.txt"))
 
 #Preprocessing
@@ -25,4 +26,8 @@ dtm <- DocumentTermMatrix(docs)
 #tdm <- TermDocumentMatrix(docs)   
 
 #top 30 term frequencies
-sort(apply(dtm,2,sum),decreasing = T)[1:30]
+ttf <- sort(apply(dtm,2,sum),decreasing = T)[1:30]
+ttf <- data.frame(ttf)
+
+require(xtable)
+xtable(ttf, caption = "Top term frequencies for 10 test websites", digits = 0)

### 2017-03-24 paper/manuscript.tex
commented on content change
minor update

@@
 
-Alternatively, the more commonplace LDA is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
+Alternatively, the more commonplace LDA \cite{Blei2003} is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
 As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
@@
 
+There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
+
 Traditional author models that rely on lexical or syntactic differences may also be of use.
@@
 
+% latex table generated in R 3.3.2 by xtable 1.8-2 package
+% Fri Mar 24 12:21:19 2017
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+File type & oct15 & jan16 & feb16 & mar16 \\ 
+  \hline
+.pdf & 358 & 183 & 111 & 394 \\ 
+  .aspx &  99 & 112 & 116 &  76 \\ 
+  .jpg &  22 &  24 &  17 &  12 \\ 
+  .gif &   3 &   5 &   1 &   5 \\ 
+  .JPG &   3 &   2 &   1 &   5 \\ 
+  .png &   3 &   7 &   2 &   1 \\ 
+  .asmx &   2 &   1 &   1 &   5 \\ 
+  .PDF &   1 &   1 &   1 &   2 \\ 
+   \hline
+\end{tabular}
+\caption{File types of Indy.gov at different points in time} 
+\end{table}
+
 \newpage

### 2017-03-27 paper/manuscript.tex
update manuscript

@@
 % latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Fri Mar 24 12:21:19 2017
+% Fri Mar 24 12:52:43 2017
 \begin{table}[ht]
@@
   \hline
-.pdf & 358 & 183 & 111 & 394 \\ 
+.pdf & 179 & 183 & 111 & 197 \\ 
   .aspx &  99 & 112 & 116 &  76 \\ 

### 2017-03-29 paper/manuscript.tex
some changes to RD, structural topic models

@@
 
-\noindent We study the content of municipal government websites....
+\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
+We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent.
+To test this theory, we apply an author-topic model [alternatively: structural topic model] to website data acquired from different points in time through the Wayback Machine.
 
@@
 Documents uploaded to city websites are expected to be a reflection of these preferences.
-The author-topic model \citep{Rosen-Zvi2004} captures this concept quite well, because it assumes that different authors prefer different topics, each of which is associated with a group of words.
-We classify all documents that have been present before the change in party control as from one party\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
-If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
-The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
-Ideally, the result would then show significant\footnote{Though I am not sure how to calculate that.} differences in the probabilities of authors being assigned to partisan topics.
 
-Alternatively, the more commonplace LDA \cite{Blei2003} is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
-As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
-Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
-In a way, this captures the data-generating process more closely.
+The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model.
+However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics.
+There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.
 
-Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
-One assumes that multiple authors write one document.
-This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
-This is not as good of a fit for city governments however.
-Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
-For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.
+The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents.
+Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates.
+In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards).
+Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website.
+Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.
+Further demographic as well as economic data might also be useful to differentiate cities from one another.
+If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.
+
+The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences.
+Unfortunately, we have two types of 'authors' - cities, and parties.
+Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author.
+This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents.
+(Note: In the papers on author-topic models, the intention is often to analyze scientific articles.
+These articles are often co-authored.
+Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)
+
+The critical element in this analysis is to accurately attribute authorship of documents to either party.
+Despite possible changes to websites due to a leadership transition, large parts of the content carry over.
+This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
+But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
+{\em  This is a very important point for municipal websites.
+We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added.
+}
+
+Labeling newly added documents after a change of power is quite simple.
+As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption.
+However, we could, and probably should test how long documents tend to stay on a city website.
+Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient.
+If we want to be really fancy about it, we could create a duration model, with document topics as features.
+This would allow us to measure whether some documents tend to remain longer based on their topic (i.e.
+fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.
+
+If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words.
+After that, we run the actual model.
+This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface.
+It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins.
+'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website.
+Hence, these websites should be filled with purely administrative content.
+
+The use of asymmetric priors \citep{Wallach2009} in our topic model - i.e.
+the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.
+
+Another intervening factor is that for cities in Indiana, mayoral terms begin in January.
+Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year.
+Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity.
+We can test for this by comparing election years to non-election years.
+Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.
 
@@
 
-Another problem with these generative models is that they ignore the fact that despite possible changes to websites due to a leadership transition, large parts of the content carry over.
-This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
-But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
-
-One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
+%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
 This way, we could identify directly which issues are considered to be the most divisive.
 
-There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
+%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
 
-Traditional author models that rely on lexical or syntactic differences may also be of use.
+%Traditional author models that rely on lexical or syntactic differences may also be of use.
 Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles.
@@
 
-Another option, that I have not looked closely at yet, are (continuous) dynamic topic models by David Blei, which would allow us to model the progression of topics over time, i.e.
-when party control changes.
+%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
+As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
+Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
+In a way, this captures the data-generating process more closely.
+
+%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
+One assumes that multiple authors write one document.
+This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
+This is not as good of a fit for city governments however.
+Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
+For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+
+
+%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
+If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
+The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
+Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.
+
+% latex table generated in R 3.3.3 by xtable 1.8-2 package
+% Sun Mar 26 22:39:59 2017
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{rllllllllllllllll}
+		\hline
+		Date & Attica & Connersville & Frankfort & Huntingburg & Indianapolis & Lake Station & Linton & Madison & Mitchell & Monticello & North Vernon & Richmond & Rockport & South Bend & Union City & Winchester \\
+		\hline
+		20150701.00 & 20141219004329 & 20090608160638 & 20150801164305 & 20150326174031 & 20080705032706 & 20150801185836 & 20130907112731 & 20150623192440 & 20150801214647 & 20150701005605 & 20150801221031 & 20150702075332 & 20150617220801 & 20150627165751 & 20150925160622 & 20150925022240 \\
+		20150801.00 & 20160129070621 & 20090608160638 & 20150801164305 & 20151030133234 & 20080705032706 & 20150801185836 & 20130907112731 & 20150801210044 & 20150801214647 & 20150804061315 & 20150801221031 & 20150802055917 & 20150801070026 & 20150726161609 & 20150925160622 & 20150925022240 \\
+		20150901.00 & 20160129070621 & 20090608160638 & 20150918063903 & 20151030133234 & 20080705032706 & 20150906164302 & 20130907112731 & 20150901105012 & 20150811063416 & 20150905074509 & 20150829185257 & 20150904033112 & 20150909192825 & 20150905085030 & 20150925160622 & 20150925022240 \\
+		20151001.00 & 20160129070621 & 20090608160638 & 20150925070028 & 20151030133234 & 20080705032706 & 20150908103757 & 20130907112731 & 20150905063305 & 20150811063416 & 20150908082732 & 20150829185257 & 20150921033423 & 20151011085644 & 20151002075030 & 20150925160622 & 20150925022240 \\
+		20151101.00 & 20160129070621 & 20090608160638 & 20151113140944 & 20151030133234 & 20080705032706 & 20151029043137 & 20130907112731 & 20151110090517 & 20160111041751 & 20151110131337 & 20151103095602 & 20151031212522 & 20151021163057 & 20151101043016 & 20150925160622 & 20151026092123 \\
+		20151201.00 & 20160129070621 & 20090608160638 & 20151121002259 & 20151030133234 & 20080705032706 & 20151201114611 & 20130907112731 & 20151216063136 & 20160111041751 & 20151115102706 & 20151206224620 & 20151201073504 & 20151212093554 & 20151209044311 & 20160111224058 & 20151127174603 \\
+		20160101.00 & 20160129070621 & 20090608160638 & 20160110065704 & 20160113165318 & 20080705032706 & 20160101144553 & 20130907112731 & 20151228192543 & 20160111041751 & 20151228224908 & 20160111074656 & 20160102015111 & 20160110195124 & 20151229083812 & 20160111224058 & 20151127174603 \\
+		20160201.00 & 20160129070621 & 20090608160638 & 20160127035634 & 20160122005059 & 20080705032706 & 20160201195326 & 20130907112731 & 20160201073437 & 20160202113637 & 20160206015204 & 20160111074656 & 20160213102047 & 20160112154213 & 20160206190816 & 20160111224058 & 20160303215247 \\
+		20160301.00 & 20160330220432 & 20090608160638 & 20160304094239 & 20160221045049 & 20080705032706 & 20160303165533 & 20130907112731 & 20160303181704 & 20160301141845 & 20160304035215 & 20160309122910 & 20160302140643 & 20160112154213 & 20160303175057 & 20160111224058 & 20160303215247 \\
+		20160401.00 & 20160330220432 & 20090608160638 & 20160321173048 & 20160317192932 & 20080705032706 & 20160404133508 & 20130907112731 & 20160402214824 & 20160405050341 & 20160403012946 & 20160318230947 & 20160403090645 & 20160603041333 & 20160325014215 & 20160111224058 & 20160416084956 \\
+		20160501.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160504014532 & 20160507154306 & 20160511155648 & 20160420092957 & 20160502154350 & 20160603041333 & 20160427024310 & 20160111224058 & 20160422124026 \\
+		20160601.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160521233726 & 20160507154306 & 20160522012629 & 20160420092957 & 20160522061744 & 20160603041333 & 20160522075620 & 20160111224058 & 20160517165930 \\
+		\hline
+	\end{tabular}
+	\caption{Dates of WaybackMachine snapshots 2015-16} 
+\end{table}
 

### 2017-03-29 paper/manuscript.tex
added less confusing table with snapshot dates

@@
 
-The use of asymmetric priors \citep{Wallach2009} in our topic model - i.e.
+The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e.
 the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.
@@
 % latex table generated in R 3.3.3 by xtable 1.8-2 package
-% Sun Mar 26 22:39:59 2017
+% Wed Mar 29 11:30:05 2017
 \begin{table}[ht]
 	\centering
-	\begin{tabular}{rllllllllllllllll}
+	\begin{tabular}{lllr}
 		\hline
-		Date & Attica & Connersville & Frankfort & Huntingburg & Indianapolis & Lake Station & Linton & Madison & Mitchell & Monticello & North Vernon & Richmond & Rockport & South Bend & Union City & Winchester \\
+		City & snapshotPrior & electionDay & daysToElection \\ 
 		\hline
-		20150701.00 & 20141219004329 & 20090608160638 & 20150801164305 & 20150326174031 & 20080705032706 & 20150801185836 & 20130907112731 & 20150623192440 & 20150801214647 & 20150701005605 & 20150801221031 & 20150702075332 & 20150617220801 & 20150627165751 & 20150925160622 & 20150925022240 \\
-		20150801.00 & 20160129070621 & 20090608160638 & 20150801164305 & 20151030133234 & 20080705032706 & 20150801185836 & 20130907112731 & 20150801210044 & 20150801214647 & 20150804061315 & 20150801221031 & 20150802055917 & 20150801070026 & 20150726161609 & 20150925160622 & 20150925022240 \\
-		20150901.00 & 20160129070621 & 20090608160638 & 20150918063903 & 20151030133234 & 20080705032706 & 20150906164302 & 20130907112731 & 20150901105012 & 20150811063416 & 20150905074509 & 20150829185257 & 20150904033112 & 20150909192825 & 20150905085030 & 20150925160622 & 20150925022240 \\
-		20151001.00 & 20160129070621 & 20090608160638 & 20150925070028 & 20151030133234 & 20080705032706 & 20150908103757 & 20130907112731 & 20150905063305 & 20150811063416 & 20150908082732 & 20150829185257 & 20150921033423 & 20151011085644 & 20151002075030 & 20150925160622 & 20150925022240 \\
-		20151101.00 & 20160129070621 & 20090608160638 & 20151113140944 & 20151030133234 & 20080705032706 & 20151029043137 & 20130907112731 & 20151110090517 & 20160111041751 & 20151110131337 & 20151103095602 & 20151031212522 & 20151021163057 & 20151101043016 & 20150925160622 & 20151026092123 \\
-		20151201.00 & 20160129070621 & 20090608160638 & 20151121002259 & 20151030133234 & 20080705032706 & 20151201114611 & 20130907112731 & 20151216063136 & 20160111041751 & 20151115102706 & 20151206224620 & 20151201073504 & 20151212093554 & 20151209044311 & 20160111224058 & 20151127174603 \\
-		20160101.00 & 20160129070621 & 20090608160638 & 20160110065704 & 20160113165318 & 20080705032706 & 20160101144553 & 20130907112731 & 20151228192543 & 20160111041751 & 20151228224908 & 20160111074656 & 20160102015111 & 20160110195124 & 20151229083812 & 20160111224058 & 20151127174603 \\
-		20160201.00 & 20160129070621 & 20090608160638 & 20160127035634 & 20160122005059 & 20080705032706 & 20160201195326 & 20130907112731 & 20160201073437 & 20160202113637 & 20160206015204 & 20160111074656 & 20160213102047 & 20160112154213 & 20160206190816 & 20160111224058 & 20160303215247 \\
-		20160301.00 & 20160330220432 & 20090608160638 & 20160304094239 & 20160221045049 & 20080705032706 & 20160303165533 & 20130907112731 & 20160303181704 & 20160301141845 & 20160304035215 & 20160309122910 & 20160302140643 & 20160112154213 & 20160303175057 & 20160111224058 & 20160303215247 \\
-		20160401.00 & 20160330220432 & 20090608160638 & 20160321173048 & 20160317192932 & 20080705032706 & 20160404133508 & 20130907112731 & 20160402214824 & 20160405050341 & 20160403012946 & 20160318230947 & 20160403090645 & 20160603041333 & 20160325014215 & 20160111224058 & 20160416084956 \\
-		20160501.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160504014532 & 20160507154306 & 20160511155648 & 20160420092957 & 20160502154350 & 20160603041333 & 20160427024310 & 20160111224058 & 20160422124026 \\
-		20160601.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160521233726 & 20160507154306 & 20160522012629 & 20160420092957 & 20160522061744 & 20160603041333 & 20160522075620 & 20160111224058 & 20160517165930 \\
+		Attica & 2015-08-01 & 2015-11-03 & 94 \\ 
+		Cornersville & 2015-10-18 & 2015-11-03 & 16 \\ 
+		Frankfort & 2015-10-18 & 2015-11-03 & 16 \\ 
+		Huntingburg & 2015-10-30 & 2015-11-03 & 4 \\ 
+		Indianapolis & 2015-10-16 & 2015-11-03 & 18 \\ 
+		Lake Station & 2015-10-29 & 2015-11-03 & 5 \\ 
+		Linton & 2015-08-01 & 2015-11-03 & 94 \\ 
+		Madison & 2015-09-05 & 2015-11-03 & 59 \\ 
+		Mitchell &  & 2015-11-03 &  \\ 
+		Monticello & 2015-09-08 & 2015-11-03 & 56 \\ 
+		North Vernon & 2015-11-03 & 2015-11-03 & 0 \\ 
+		Richmond & 2015-10-31 & 2015-11-03 & 3 \\ 
+		Rockport & 2015-10-21 & 2015-11-03 & 13 \\ 
+		South Bend & 2015-11-01 & 2015-11-03 & 2 \\ 
+		Union City & 2015-09-25 & 2015-11-03 & 39 \\ 
+		Winchester & 2015-10-26 & 2015-11-03 & 8 \\ 
 		\hline
 	\end{tabular}
-	\caption{Dates of WaybackMachine snapshots 2015-16} 
+	\caption{Closest snapshots to election day} 
 \end{table}

### 2017-04-03 paper/manuscript.tex
added research design based on grimmers expressed agenda model

@@
 
+\subsection{Research Design}
+
+\begin{enumerate}
+\item Corpus:
+\begin{enumerate}
+\item Last snapshots before the election (November 3, 2015 in Indiana; tbd. in Louisiana (probably February))
+\item First snapshot that is at least 2 months after the new government's inauguration (which is in January for Indiana, May for Louisiana)
+\end{enumerate}
+\item Preprocessing:
+\begin{enumerate}
+\item restrict corpus to:
+\begin{enumerate}
+\item documents belonging to cities in which a change of power occurred
+\item documents that were added, deleted or changed between the two snapshots
+\end{enumerate}
+\item words to lowercase
+\item remove punctuation
+\item stemming (Porter stemming algorithm?)
+\item Remove stop words (regular list of stop words is enough, since we use an asymmetric prior)
+\end{enumerate}
+\item Apply Grimmer's expressed agenda model to the corpus
+\begin{enumerate}
+\item Asymmetric prior
+\item Each document can have only one topic (in contrast to the author-topic model)
+\item Cities $i = 1,..., n = 15$
+\item Topic $k(k = 1,..., K )$
+\item Documents $j(j = 1,...,D_i)$ from city i
+\item Party covariate in the prior, where the deleted and unmodified documents are coded as from the first, and the added and modified documents from the second party
+\end{enumerate}
+\item Results
+\begin{enumerate}
+\item Label topics using Grimmer's automatic cluster labeling method, based on most commonly used words in documents belonging to topic
+\item Evaluate topics
+\end{enumerate}
+\end{enumerate}
+
+Validation:
+
+\begin{itemize}
+\item Do the above for cities in which no change of power occurred.
+\item Check whether there is higher than average turnover around the new year by comparing changes to non-election years (and also Louisiana, where elections are later).
+\item Check how long documents stay on websites on average. Use websites with a lot of snapshots for this (these exist for both small and large cities).
+\end{itemize}
+
+Problem with using this model: Grimmer's expressed agenda model uses Senators as the actors.
+Senators is also who he is substantively interested in.
+For us, the equivalent to Senators is cities.
+However, we care about parties, not cities.
+
 \subsection{Topic modeling}
+Note: this chapter is mostly a wordy and less coherent version of the above.
+
 We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas.

### 2017-04-05 paper/manuscript.tex
updated abstract

@@
 We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent.
-To test this theory, we apply an author-topic model [alternatively: structural topic model] to website data acquired from different points in time through the Wayback Machine.
+To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots.
+Snapshots of websites before and after transitions of power are acquired through the Wayback Machine.
+We apply the expressed agenda model (Grimmer 2010) to this corpus.
+This topic model allows us to identify which kinds of documents are prone to being modified, added and removed after transitions of power.
 

### 2017-04-05 paper/manuscript.tex
changed title and abstract

@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Content of Municipal Government Websites }
+\title{\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites }
 
@@
 Snapshots of websites before and after transitions of power are acquired through the Wayback Machine.
-We apply the expressed agenda model (Grimmer 2010) to this corpus.
-This topic model allows us to identify which kinds of documents are prone to being modified, added and removed after transitions of power.
+We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites.
+We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.
 

### 2017-04-12 paper/manuscript.tex
plot with snapshot dates

@@
 
+\subsection{Survival model}
+The existence of individual documents on municipal government websites can be though of as a survival process.
+No document stays on a website forever, and it appears to be a reasonable assumption that as documents get older and thus less relevant, they get replaced.
+The factors determining the steepness of the survival curve are the topic - fire safety regulations likely stay up longer than a bulletin on the annual spring banquet - and the change of party control after an election.
+
+Consequently the covariates include:
+\begin{itemize}
+\item a categorical independent variable, indicating which topic a document gets assigned to under the expressed agenda model
+%\item a variable indicating the change of party control at time $t$
+\item is the party that put the document up still present at time $t$
+\item interaction term between the two above
+\end{itemize}
+This will take up a lot of degrees of freedom.
+
+Proportional hazard? If not, then likely rising, although there might be some documents that really do hardly ever get changed, so it should probably fall again after a few years.
+
+Model document being changed vs. being removed as competing risks.
+
 \subsection{Topic modeling}
@@
 
-% latex table generated in R 3.3.3 by xtable 1.8-2 package
-% Wed Mar 29 11:30:05 2017
-\begin{table}[ht]
+\begin{figure}[!ht]
 	\centering
-	\begin{tabular}{lllr}
-		\hline
-		City & snapshotPrior & electionDay & daysToElection \\ 
-		\hline
-		Attica & 2015-08-01 & 2015-11-03 & 94 \\ 
-		Cornersville & 2015-10-18 & 2015-11-03 & 16 \\ 
-		Frankfort & 2015-10-18 & 2015-11-03 & 16 \\ 
-		Huntingburg & 2015-10-30 & 2015-11-03 & 4 \\ 
-		Indianapolis & 2015-10-16 & 2015-11-03 & 18 \\ 
-		Lake Station & 2015-10-29 & 2015-11-03 & 5 \\ 
-		Linton & 2015-08-01 & 2015-11-03 & 94 \\ 
-		Madison & 2015-09-05 & 2015-11-03 & 59 \\ 
-		Mitchell &  & 2015-11-03 &  \\ 
-		Monticello & 2015-09-08 & 2015-11-03 & 56 \\ 
-		North Vernon & 2015-11-03 & 2015-11-03 & 0 \\ 
-		Richmond & 2015-10-31 & 2015-11-03 & 3 \\ 
-		Rockport & 2015-10-21 & 2015-11-03 & 13 \\ 
-		South Bend & 2015-11-01 & 2015-11-03 & 2 \\ 
-		Union City & 2015-09-25 & 2015-11-03 & 39 \\ 
-		Winchester & 2015-10-26 & 2015-11-03 & 8 \\ 
-		\hline
-	\end{tabular}
-	\caption{Closest snapshots to election day} 
-\end{table}
+	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
+	\label{snapshots}
+	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
+\end{figure}
 

### 2017-04-12 paper/manuscript.tex
added some details on survival model

@@
 
-Consequently the covariates include:
-\begin{itemize}
-\item a categorical independent variable, indicating which topic a document gets assigned to under the expressed agenda model
-%\item a variable indicating the change of party control at time $t$
-\item is the party that put the document up still present at time $t$
-\item interaction term between the two above
-\end{itemize}
-This will take up a lot of degrees of freedom.
+\begin{quote}
+\textit{H1}: The older a document, the more likely it is to be removed.
+\end{quote}
 
-Proportional hazard? If not, then likely rising, although there might be some documents that really do hardly ever get changed, so it should probably fall again after a few years.
+$S(t)$ has a downward slope. Admittedly, this is almost impossible not to be true. Also, test proportional, rising and falling hazard models.
 
-Model document being changed vs. being removed as competing risks.
+\begin{quote}
+\textit{H2}: Documents pertaining to administrative matters are less likely to be removed.
+\end{quote}
+
+Introduce a categorical variable for the top 10(?) topics. A negative coefficient for administrative topics would support this hypothesis.
+
+\begin{quote}
+\textit{H3}: Documents introduced by the opposing party are more likely to be removed.
+\end{quote}
+
+Introduce two variables into the survival model: One variable indicating which party has introduced a document, and a time-varying variable describing which party is currently in government.
+The hypothesis is tested through an interaction term between the two.
+
+\begin{quote}
+\textit{H4a}: Democrats are more likely to remove documents with topics pertaining to private enterprise, private schools.
+\end{quote}
+
+Interaction term between party in power and categorical topic variable.
+
+\begin{quote}
+\textit{H4b}: Republicans are more likely to remove documents with topics pertaining to social justice, equality, taxes, public schools, etc.
+\end{quote}
+
+Interaction term between party in power and categorical topic variable.
+
+\begin{quote}
+\textit{H5}: In line with their commitment to small government, Republicans are more likely than Democrats to remove documents.
+\end{quote}
+
+Party in power variable.\\
+
+This model will take up a lot of degrees of freedom. The rarity of snapshots for some cities might be a problem. Documents being changed and being removed can be modeled as competing risks.
+
+\begin{equation} 
+\label{eq1}
+\begin{split}
+Y & = \text{Party that introduced the document} \\
+ & + \text{Party that is currently in power} \\
+ & + \text{Topic 1, topic 2, ..., topic k} \\
+ & + \text{Party that is currently in power} \times \text{Topic 1, topic 2, ..., topic k} \\
+ & + \text{Days since start of mayoral term (control)}
+\end{split}
+\end{equation}
 

### 2017-04-19 govWebsitesSnapshotsDates.R
added literature on local governments, parties, and policy effects as a super ugly table (haven't thought of a better way so far)

@@ -81,3 +81,30 @@ g1
 
 
 ggsave(g1, file="paper/figures/Snapshots.pdf", height = 10, width = 10)
+
+
+### Count number of snapshots
+Snapshots$one <- 1
+
+indianaS <- aggregate(one ~ City, Snapshots, FUN=sum)
+
+setwd("websites/IndianaTest/")
+#folder size
+#get folder names
+d <- list.files()
+e <- vector()
+#print directory size with Linux command 'du -s'
+for(i in 1:length(d)){
+  e[i] <- system(paste("du",d[i],"-s"), intern=T)
+}
+require(reshape2)
+f <- colsplit(e,"\\t",c("Size (KB)","Website"))
+f$Website <- sub("www.", "", f$Website)
+f$Website <- sub("cityofrockport", "rockport", f$Website)
+f <- f[order(f$Website),]
+
+storagesize <- cbind(indianaS,f)
+
+storagesize$result <- storagesize$`Size (MB)`*storagesize$one
+
+sum(storagesize$result)/1000000 #in gigabyte

### 2017-04-19 paper/manuscript.tex
added literature on local governments, parties, and policy effects as a super ugly table (haven't thought of a better way so far)
added a short note on dynamic representation + regression discontinuity

@@
 \usepackage{times}
+
+\usepackage{lscape}
 % \usepackage{mathptmx}
@@
 For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''
+
+\begin{landscape}
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/literature.png}
+\end{figure}
+\end{landscape}
+
+There doesn't seem to be much literature on transitions of party control, if anything, that question is mostly phrased with regard to political representation.
+However, if we want to tie our paper to a larger theory, we could go with dynamic representation.
+Under dynamic representation, policy-makers are responsive to trends in citizens opinions, which mainly manifest/become apparent through election results, especially when incumbents are voted out of office.
+This fits our topic quite well.
+Also, of the few papers that do exist on the effects of partisan transitions, virtually all use regression discontinuity designs.
 

### 2017-04-19 paper/manuscript.tex
fixed the table with the literature

@@
 \begin{landscape}
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/literature.png}
-\end{figure}
+\begin{table}[htbp]
+	%\caption{}
+	\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+		\hline
+		Names & Year & Journal & Findings & Important? \\ \hline
+		Benedictis-Kessner, Justin De
+		Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
+Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
+		Caughey, Devin
+		Warshaw, Christopher
+		Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
+Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
+& Somewhat \\ \hline
+		Einstein, Katherine Levine
+		Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
+aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
+		Einstein, Katherine Levine
+		Glick, David M.
+& 2015 & Working Paper & Survey of 72 mayors.
+Unlike Republican mayors, roughly half of Democrats seem to agree that cities should aim to reduce inequality.
+Democratic mayors also seem to favor redistribution to accomplish that goal.
+& Somewhat \\ \hline
+		Kiewiet, D Roderick
+		Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
+Spending has thus decreased in general.
+Lack of funds means that there is not much discretion for partisanship.
+& Somewhat \\ \hline
+		Tausanovitch, Chris
+		Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
+Partisan elections do not make cities more or less responsive.
+& Yes \\ \hline
+		Guillamón, Ma Dolores
+		Bastida, Francisco
+		Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
+Conservative parties spend more on police.
+Spending is higher before elections.
+Also contains a useful overview of the literature.
+& Yes \\ \hline
+	\end{tabular}
+	\label{}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+	\begin{table}[htbp]
+		%\caption{}
+		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+			\hline
+			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
+			Names & Year & Journal & Findings & Important? \\ \hline
+			Solé-Ollé, Albert
+			Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
+The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
+Partisanship might also affect housing construction and price growth.
+& Yes \\ \hline
+			Gerber, Elisabeth R.
+			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
+			Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
+Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
+Non-partisan elections favor Republicans/upper class.
+Mixed evidence for whether partisanship of mayor is important for policy.
+& Somewhat \\ \hline
+			Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
+spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
+& Somewhat \\ \hline
+			Ferreira, Fernando
+			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
+			Ansolabehere, Stephen
+			Snyder, James M.
+& 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
+The important finding (for us) is the fact that counties whose government is controlled by the same party as the state government, receive more funding (county's share of state transfers, normalized by county pop.) from the state.
+& Somewhat \\ \hline
+			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
+		\end{tabular}
+		\label{}
+	\end{table}
 \end{landscape}

### 2017-05-18 paper/manuscript.tex
added new WBM downloader code + updated two figures in the manuscript

@@
 
-% latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Wed Feb 22 21:39:50 2017
+% latex table generated in R 3.4.0 by xtable 1.8-2 package
+% Tue May 16 13:38:43 2017
 \begin{table}[ht]
@@
 		\hline
-		File type & Occurrences \\ 
+		Filetype & Frequency \\ 
 		\hline
-		.pdf & 1371 \\ 
-		.html & 819 \\ 
-		.png & 210 \\ 
-		.jpg & 131 \\ 
-		.gif &  99 \\ 
-		.js &  51 \\ 
-		.PDF &  50 \\ 
-		.aspx &  43 \\ 
-		.doc &  35 \\ 
-		.css &  32 \\ 
-		.JPG &  26 \\ 
-		.Net &  12 \\ 
-		.xlsx &   6 \\ 
-		.docx &   5 \\ 
-		.ttf &   3 \\ 
-		.xml &   3 \\ 
-		.htm &   2 \\ 
-		.woff &   2 \\ 
-		.xls &   2 \\ 
-		.asp &   1 \\ 
-		.eot &   1 \\ 
-		.GIF &   1 \\ 
-		.ico &   1 \\ 
-		.PNG &   1 \\ 
-		.ppt &   1 \\ 
-		.swf &   1 \\ 
-		.txt &   1 \\ 
+		& 47652 \\ 
+		pdf & 9486 \\ 
+		jpg & 4342 \\ 
+		html & 3492 \\ 
+		aspx & 2832 \\ 
+		png & 2358 \\ 
+		gif & 1296 \\ 
+		JPG & 545 \\ 
+		css & 385 \\ 
+		1 & 358 \\ 
+		js & 344 \\ 
+		htm & 264 \\ 
+		docx & 202 \\ 
+		dwf & 181 \\ 
+		doc & 168 \\ 
+		asp & 161 \\ 
+		PDF & 103 \\ 
+		php &  83 \\ 
+		egov &  54 \\ 
+		cfm &  45 \\ 
+		4 &  42 \\ 
+		2 &  35 \\ 
+		com &  31 \\ 
+		0 &  29 \\ 
+		3 &  26 \\ 
 		\hline
 	\end{tabular}
-	\caption{File types in scraped websites} 
+	\caption{The 25 most common file types in scraped websites} 
 \end{table}
 
-% latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Wed Feb 22 21:35:10 2017
+% latex table generated in R 3.4.0 by xtable 1.8-2 package
+% Tue May 16 14:05:19 2017
 \begin{table}[ht]
@@
 		\hline
-		Website & Files & Size (MB) \\ 
+		Website & Files & Size (kB) \\ 
 		\hline
-		brownsvilletn.gov & 188 & 14328 \\ 
-		www.centralpointoregon.gov & 150 & 137440 \\ 
-		www.dedham-ma.gov & 603 & 212572 \\ 
-		www.duncanok.gov &  84 & 47064 \\ 
-		www.dutchessny.gov & 110 & 291376 \\ 
-		www.ennistx.gov & 200 & 26244 \\ 
-		www.greenvillenc.gov & 333 & 25732 \\ 
-		www.romi.gov & 491 & 112584 \\ 
-		www.trumbull-ct.gov & 787 & 191540 \\ 
-		www.westonct.gov & 861 & 213140 \\ 
+		attica-in.gov & 1417 & 61988 \\ 
+		bedford.in.us & 560 & 57628 \\ 
+		cityofboonvilleindiana.com & 110 & 9848 \\ 
+		connersvillecommunity.com & 569 & 170684 \\ 
+		frankfort-in.gov & 2652 & 205368 \\ 
+		mitchell-in.com &  50 & 3036 \\ 
+		warsaw.in.gov & 2117 & 298264 \\ 
+		www.batesvilleindiana.us &   1 &  96 \\ 
+		www.bernein.com & 755 & 60836 \\ 
+		www.bloomington.in.gov &   1 &  52 \\ 
+		www.brazil.in.gov &   1 &  36 \\ 
+		www.carmel.in.gov & 8727 & 2267604 \\ 
+		www.ci.auburn.in.us & 1025 & 178496 \\ 
+		www.ci.bluffton.in.us &   1 & 132 \\ 
+		www.cityoffortwayne.org & 4378 & 2134540 \\ 
+		www.cityofhobart.org & 2463 & 718312 \\ 
+		www.cityofrisingsun.com & 3311 & 991736 \\ 
+		www.cityofrockport-in.gov &  98 & 11836 \\ 
+		www.clintonco.com & 524 & 134344 \\ 
+		www.elkhartindiana.org & 2345 & 1132612 \\ 
+		www.elwoodcity-in.org &   1 &  48 \\ 
+		www.evansvillegov.org & 11844 & 6339388 \\ 
+		www.gary.in.us & 1227 & 371480 \\ 
+		www.huntingburg-in.gov & 2496 & 388188 \\ 
+		www.indy.gov & 9675 & 5717888 \\ 
+		www.jasperindiana.gov & 4013 & 561212 \\ 
+		www.lakestation-in.gov &   2 &  40 \\ 
+		www.linton-in.gov &   1 &  32 \\ 
+		www.madison-in.gov & 1848 & 528200 \\ 
+		www.martinsville.in.gov & 1463 & 46544 \\ 
+		www.monticelloin.gov & 753 & 33352 \\ 
+		www.newhavenin.org & 626 & 84176 \\ 
+		www.northvernon-in.gov & 403 & 271452 \\ 
+		www.richmondindiana.gov & 1042 & 250028 \\ 
+		www.southbendin.gov & 4749 & 1252624 \\ 
+		www.tiptongov.com & 1151 & 130404 \\ 
+		www.unioncity-in.gov &   2 &  16 \\ 
+		www.winchester-in.gov & 2480 & 364368 \\ 
 		\hline
 	\end{tabular}
-	\caption{Test websites} 
+	\caption{Number of files and size of websites} 
 \end{table}

### 2017-05-18 govWebsitesFiletypes.R

@@ -1,22 +1,22 @@
+library("tools") #for file_ext()
+require("xtable")
+#require(stringr)
+
 #This script extracts the filetypes, folder sizes, etc.
 #from the 10 test cases scraped from the Wayback Machine
 
-setwd("/home/markus/Dropbox/4_RA/govWebsites/websites/")
+setwd("./websites/current/")
 
 a <- list.files(recursive = T) #create a list of all files in all subdirectories
 
 #file types
-require(stringr)
-#extract file type
-b <- str_extract(a,"(\\.[^.]+)$")
-#create table for file types with at most 5 characters
-c <- data.frame(table(b[which(str_length(b)<6)]))
-names(c) <- c("File type","Occurrences")
-c <- c[order(c$Occurrences, decreasing = T),]
-c <- c[-c(1:8),]
-require(xtable)
-#omit some of the less useful types and turn table into latex object
-print(xtable(c, caption="File types in scraped websites"), include.rownames = F)
+b <- file_ext(a) #get file extension
+b <- data.frame(sort(table(b), decreasing = T)) #turn into table/data frame
+names(b) <- c("Filetype", "Frequency") #rename columns
+b <- b[1:25,] #only get top 10
+
+#turn table into latex object
+print(xtable(b, caption="The 25 most common file types in scraped websites"), include.rownames = F)
 
 
 #folder size
@@ -24,7 +24,7 @@ print(xtable(c, caption="File types in scraped websites"), include.rownames = F)
 d <- list.files()
 e <- vector()
 #print directory size with Linux command 'du -s'
-for(i in 1:10){
+for(i in 1:length(d)){
   e[i] <- system(paste("du",d[i],"-s"), intern=T)
 }
 #split character vector into dataframe
@@ -35,13 +35,13 @@ f <- colsplit(e,"\\t",c("Size (MB)","Website"))
 ##number of files
 g <- vector()
 #number of files per website/folder
-for(i in 1:10){
+for(i in 1:length(d)){
 g[i] <- length(list.files(list.files()[i],recursive = T, all.files=T))
 }
 #add to data frame created above
 f$Files <- g
 #re-order and turn table into latex object
-print(xtable(f[,c(2,3,1)], caption="Test websites"), include.rownames = F)
+print(xtable(f[,c(2,3,1)], caption="Number of files and size of websites"), include.rownames = F)
 
 
 rm(a,b,c,d,e,f,g,i)

### 2017-05-18 govWebsitesWBMDL.R

@@ -1,14 +1,31 @@
 library("stringr")
 
-load(file = "data/URLs2.rdata")
+load(file = "data/URLs_IN.rdata")
 
 source("wbmdownloader.R")
 
-for(i in 1:nrow(URLs)){
-  for(j in 1:length(URLs$snapshots[[i]])){
+#for downloading multiple snapshots
+#for(i in 1:nrow(URLs)){
+#  for(j in 1:length(URLs$snapshots[[i]])){
+#    wbmdownloader(website = URLs$Website[i],
+#                  from = URLs$snapshots[[i]][j],
+#                  to = URLs$snapshots[[i]][j],
+#                  path = str_c("./WBM/", URLs$Name[i], "/", URLs$snapshots[[i]][j]))
+#  }
+#}
+
+#before
+for(i in 16:nrow(URLs)){
     wbmdownloader(website = URLs$Website[i],
-                  from = URLs$snapshots[[i]][j],
-                  to = URLs$snapshots[[i]][j],
-                  path = str_c("./WBM/", URLs$Name[i], "/", URLs$snapshots[[i]][j]))
-  }
+                  from = 20141103,
+                  to = 20151102,
+                  path = str_c("./websites/before/", URLs$foldername[i]))
+}
+
+#after
+for(i in 1:nrow(URLs)){
+    wbmdownloader(website = URLs$Website[i],
+                  from = 20160101,
+                  to = 20161231,
+                  path = str_c("./websites/after/", URLs$foldername[i]))
 }

### 2017-05-18 wbmdownloader.R

@@ -5,19 +5,20 @@
 #https://github.com/hartator/wayback-machine-downloader
 #needs to be installed for this to work
 
-wbmdownloader <- function(website, concurrency = 50, from = 20170401, to = 20170501, path = "./WBM/Misc"){
+wbmdownloader <- function(website, from = 20170401, to = 20170501, pages = 200, path = "./WBM/Misc"){
 
   #pasting input for Ruby package, then executing it
   #--concurrency 20 causes 20 items to be downloaded at the same time
   #the default is 1, this takes WAY too long (i.e. one hour for a website...)
   #--from 201610 downloads a snapshot from October 2016, or, if not available, later
-  WBMD_base <- paste("wayback_machine_downloader --concurrency ", concurrency,
+  WBMD_base <- paste("wayback_machine_downloader",
                      " --from ", from, 
-                     " --to ", from, 
+                     " --to ", to, 
                      " --directory ", path,
+                     #" -a",
+                     " -p ", pages,
                      sep = "")
   WBMD_site <- paste(WBMD_base, website)
-  system(WBMD_site, intern = T) #just ignore the printout if running outside of loop
-
+  system(WBMD_site, intern = F) #just ignore the printout if running outside of loop
 
 }

### 2017-05-24 paper/manuscript.tex
updated tables with before/after/current info on files and filesizes

--- 2017-04-19 paper/manuscript.tex
@@
 
-% latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Wed Feb 22 21:39:50 2017
+% latex table generated in R 3.4.0 by xtable 1.8-2 package
+% Tue May 23 19:28:26 2017
 \begin{table}[ht]
 	\centering
-	\begin{tabular}{lr}
+	\begin{tabular}{lrrr}
 		\hline
-		File type & Occurrences \\ 
+		Filetype & current & before & after \\ 
 		\hline
-		.pdf & 1371 \\ 
-		.html & 819 \\ 
-		.png & 210 \\ 
-		.jpg & 131 \\ 
-		.gif &  99 \\ 
-		.js &  51 \\ 
-		.PDF &  50 \\ 
-		.aspx &  43 \\ 
-		.doc &  35 \\ 
-		.css &  32 \\ 
-		.JPG &  26 \\ 
-		.Net &  12 \\ 
-		.xlsx &   6 \\ 
-		.docx &   5 \\ 
-		.ttf &   3 \\ 
-		.xml &   3 \\ 
-		.htm &   2 \\ 
-		.woff &   2 \\ 
-		.xls &   2 \\ 
-		.asp &   1 \\ 
-		.eot &   1 \\ 
-		.GIF &   1 \\ 
-		.ico &   1 \\ 
-		.PNG &   1 \\ 
-		.ppt &   1 \\ 
-		.swf &   1 \\ 
-		.txt &   1 \\ 
+		& 51455 & 13866 & 19199 \\ 
+		pdf & 9646 & 5489 & 7544 \\ 
+		jpg & 5216 & 1988 & 3512 \\ 
+		html & 3767 & 17842 & 17596 \\ 
+		aspx & 2832 & 4356 & 3271 \\ 
+		png & 2714 & 2327 & 3684 \\ 
+		gif & 1068 & 664 & 1077 \\ 
+		JPG & 478 & 182 & 263 \\ 
+		1 & 443 &  61 &  54 \\ 
+		css & 390 & 265 & 518 \\ 
+		js & 350 & 255 & 468 \\ 
+		htm & 264 & 295 & 256 \\ 
+		docx & 203 & 106 & 120 \\ 
+		doc & 167 &  70 & 130 \\ 
+		asp & 161 & 201 & 211 \\ 
+		svg &  87 &  55 &  69 \\ 
+		php &  83 & 157 & 241 \\ 
 		\hline
 	\end{tabular}
-	\caption{File types in scraped websites} 
+	\caption{The most common file types in scraped websites} 
 \end{table}
 
-% latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Wed Feb 22 21:35:10 2017
+\begin{landscape}
+% latex table generated in R 3.4.0 by xtable 1.8-2 package
+% Tue May 23 19:35:22 2017
 \begin{table}[ht]
 	\centering
-	\begin{tabular}{lrr}
+	\footnotesize
+	\begin{tabular}{lrrrrrrrrr}
 		\hline
-		Website & Files & Size (MB) \\ 
+		Website & current\_size & current\_files & before\_size & before\_files & after\_size & after\_files & size\_change & files\_change & control\_change \\ 
 		\hline
-		brownsvilletn.gov & 188 & 14328 \\ 
-		www.centralpointoregon.gov & 150 & 137440 \\ 
-		www.dedham-ma.gov & 603 & 212572 \\ 
-		www.duncanok.gov &  84 & 47064 \\ 
-		www.dutchessny.gov & 110 & 291376 \\ 
-		www.ennistx.gov & 200 & 26244 \\ 
-		www.greenvillenc.gov & 333 & 25732 \\ 
-		www.romi.gov & 491 & 112584 \\ 
-		www.trumbull-ct.gov & 787 & 191540 \\ 
-		www.westonct.gov & 861 & 213140 \\ 
+		attica-in.gov & 61988 & 1417 & 7528 & 164 & 55956 & 1390 & 7.43 & 8.48 & 0.00 \\ 
+		bedford.in.us & 57628 & 560 & 27452 & 182 & 46388 & 525 & 1.69 & 2.88 & 0.00 \\ 
+		cityofboonvilleindiana.com & 9848 & 110 & 16996 & 172 & 20784 & 229 & 1.22 & 1.33 & 0.00 \\ 
+		frankfort-in.gov & 205368 & 2652 & 12208 & 242 & 138360 & 1077 & 11.33 & 4.45 & 0.00 \\ 
+		warsaw.in.gov & 298440 & 2117 & 26844 & 539 & 360400 & 2036 & 13.43 & 3.78 & 0.00 \\ 
+		www.bloomington.in.gov & 131128 & 2713 & 443360 & 14384 & 247096 & 9640 & 0.56 & 0.67 & 0.00 \\ 
+		www.brazil.in.gov & 43056 & 845 & 34472 & 625 & 55152 & 1214 & 1.60 & 1.94 & 0.00 \\ 
+		www.carmel.in.gov & 2270016 & 8727 & 1919344 & 5361 & 899900 & 2219 & 0.47 & 0.41 & 0.00 \\ 
+		www.ci.auburn.in.us & 183296 & 1025 & 21444 & 345 & 23564 & 211 & 1.10 & 0.61 & 0.00 \\ 
+		www.cityoffortwayne.org & 2136424 & 4378 & 266784 & 3582 & 233600 & 3018 & 0.88 & 0.84 & 0.00 \\ 
+		www.cityofhobart.org & 722000 & 2463 & 44192 & 650 & 62660 & 1037 & 1.42 & 1.60 & 0.00 \\ 
+		www.evansvillegov.org & 6345932 & 11844 & 290784 & 1281 & 1697224 & 6853 & 5.84 & 5.35 & 0.00 \\ 
+		www.gary.in.us & 373888 & 1227 & 121812 & 485 & 157140 & 719 & 1.29 & 1.48 & 0.00 \\ 
+		www.huntingburg-in.gov & 388680 & 2496 & 8644 & 213 & 375900 & 1953 & 43.49 & 9.17 & 0.00 \\ 
+		www.jasperindiana.gov & 561968 & 4013 & 55900 & 460 & 439072 & 2224 & 7.85 & 4.83 & 0.00 \\ 
+		www.lakestation-in.gov &  48 &   2 & 7724 &  84 & 257272 & 1097 & 33.31 & 13.06 & 0.00 \\ 
+		www.linton-in.gov &  32 &   1 &  24 &   2 &  24 &   2 & 1.00 & 1.00 & 0.00 \\ 
+		www.madison-in.gov & 531044 & 1848 & 36636 & 575 & 191624 & 1444 & 5.23 & 2.51 & 0.00 \\ 
+		www.martinsville.in.gov & 46792 & 1463 & 71628 & 1052 & 80944 & 800 & 1.13 & 0.76 & 0.00 \\ 
+		www.monticelloin.gov & 33656 & 753 & 18120 & 448 & 100680 & 2104 & 5.56 & 4.70 & 0.00 \\ 
+		www.newhavenin.org & 84364 & 626 & 2524 &  86 & 6792 & 334 & 2.69 & 3.88 & 0.00 \\ 
+		www.richmondindiana.gov & 250968 & 1042 & 217252 & 918 & 401672 & 2422 & 1.85 & 2.64 & 0.00 \\ 
+		www.southbendin.gov & 1264076 & 4749 & 454456 & 3286 & 1424136 & 2562 & 3.13 & 0.78 & 0.00 \\ 
+		connersvillecommunity.com & 170688 & 569 & 162316 & 815 & 187276 & 808 & 1.15 & 0.99 & 1.00 \\ 
+		www.batesvilleindiana.us & 166564 & 2348 & 39592 & 496 & 95696 & 1310 & 2.42 & 2.64 & 1.00 \\ 
+		www.cityofrisingsun.com & 994956 & 3311 & 321400 & 1268 & 80848 & 868 & 0.25 & 0.68 & 1.00 \\ 
+		www.cityofrockport-in.gov & 12068 &  98 & 5148 &  16 & 12068 &  98 & 2.34 & 6.12 & 1.00 \\ 
+		www.elkhartindiana.org & 1132828 & 2345 & 5588 & 123 & 6204 & 223 & 1.11 & 1.81 & 1.00 \\ 
+		www.elwoodcity-in.org & 224412 & 765 & 5000 & 123 & 139692 & 517 & 27.94 & 4.20 & 1.00 \\ 
+		www.indy.gov & 5726048 & 9675 & 6119260 & 10451 & 4984080 & 7981 & 0.81 & 0.76 & 1.00 \\ 
+		www.northvernon-in.gov & 272016 & 403 & 3132 & 112 & 289336 & 416 & 92.38 & 3.71 & 1.00 \\ 
+		www.winchester-in.gov & 364592 & 2480 & 6508 & 135 & 45488 & 567 & 6.99 & 4.20 & 1.00 \\ 
 		\hline
 	\end{tabular}
-	\caption{Test websites} 
+	\caption{Number of files and size of websites} 
 \end{table}
+\end{landscape}
 
@@
 \subsection{Research Design}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{llr}
+		\hline
+		Variable & Unit & Source \\
+		\hline
+		Population size & 1000 people & Census \\
+		Population growth last 5 years & Percent & Census \\
+		Type of economy (agriculture/industry/services) & ? & Census \\
+		Economic performance (GDP?) & \$ & Census \\
+		Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
+		Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
+		Change of party control & 0/1 & in.gov/sos/elections/ \\
+		Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
+		Unemployment rate & Percent & Census \\
+		Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
+		\hline
+	\end{tabular}
+	\caption{List of covariates} 
+\end{table}
 

### 2017-05-24 govWebsitesFiletypes.R

@@ -1,47 +1,94 @@
 library("tools") #for file_ext()
 require("xtable")
-#require(stringr)
+require('stringr')
 
 #This script extracts the filetypes, folder sizes, etc.
 #from the 10 test cases scraped from the Wayback Machine
 
-setwd("./websites/current/")
+filteypes <- function(wd){
+  
+  a <- list.files(wd, recursive = T) #create a list of all files in all subdirectories
 
-a <- list.files(recursive = T) #create a list of all files in all subdirectories
-
-#file types
-b <- file_ext(a) #get file extension
-b <- data.frame(sort(table(b), decreasing = T)) #turn into table/data frame
-names(b) <- c("Filetype", "Frequency") #rename columns
-b <- b[1:25,] #only get top 10
+  #file types
+  b <- file_ext(a) #get file extension
+  b <- data.frame(sort(table(b), decreasing = T)) #turn into table/data frame
+  names(b) <- c("Filetype", "Frequency") #rename columns
+  b <- b[1:25,] #only get top 25
+  
+  return(b)
+  
+}
 
 #turn table into latex object
-print(xtable(b, caption="The 25 most common file types in scraped websites"), include.rownames = F)
 
 
-#folder size
-#get folder names
-d <- list.files()
-e <- vector()
-#print directory size with Linux command 'du -s'
-for(i in 1:length(d)){
-  e[i] <- system(paste("du",d[i],"-s"), intern=T)
+filetypes_current <- filteypes("./websites/current/")
+filetypes_before <- filteypes("./websites/before/")
+filetypes_after <- filteypes("./websites/after/")
+
+names(filetypes_current)[2] <- "current"
+names(filetypes_before)[2] <- "before"
+names(filetypes_after)[2] <- "after"
+
+filetypes_all <- merge(filetypes_current, filetypes_before, by = "Filetype")
+filetypes_all <- merge(filetypes_all, filetypes_after, by = "Filetype")
+
+filetypes_all <- filetypes_all[order(filetypes_all$current, decreasing = T),]
+
+print(xtable(filetypes_all, caption="The most common file types in scraped websites"), include.rownames = F)
+
+filesfolders <- function(wd){
+
+  #folder size
+  #get folder names
+  d <- list.files(wd) #actually lists the folders
+  e <- vector()
+  #print directory size with Linux command 'du -s'
+  for(i in 1:length(d)){
[…]

### 2017-05-24 paper/manuscript.tex
added section on why the content of city websites matters at the end of background

@@
 Also, of the few papers that do exist on the effects of partisan transitions, virtually all use regression discontinuity designs.
+
+\textbf{Why does the content of city websites matter?} According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
+Official city websites allow mayors to do all three.
+Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate.
+In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents.
+Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
+City websites present an opportunity for local officials to brandish these accomplishments.
+Finally, they also give mayors a platform from which they can advertise their political beliefs.
+On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
+As noted by \cite{Einstein2015a}, there are stark differences in the spending preferences of Democratic and Republican mayors.
+City websites can then be used to communicate the stance of a mayor on social or economic programs.
+Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
+
+In addition to the use of city websites for the politicians that control them, variance in content also matters  with regard to the people who visit them.
+Local residents likely rely on city websites to get news about events, hot-button political issues specific to their city, contact city officials or find out addresses or opening hours of city institutions.
+Visitors use city websites to look up local attractions, which are often described in great detail.
+Similarly, prospective residents looking to move, might rely on city websites to inform their decision on whether to relocate there.
+An inviting website emphasizing the city's receptiveness to new residents might make a real difference here.
+Finally, city websites frequently feature sections on business, but there is a lot of variance in this area: Some emphasize economic development, properties, or transportation, whereas others focus on undeveloped land and other business opportunities.
+Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.
 

### 2017-05-30 paper/manuscript.tex
added literature on website evaluation with regard to transparency etc.

@@
 			\hline
+			Names & Year & Journal & Findings & Important? \\ \hline
 			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
-			Names & Year & Journal & Findings & Important? \\ \hline
 			Solé-Ollé, Albert
@@
 			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
+		\end{tabular}
+		\label{}
+	\end{table}
+\end{landscape}
+
+\begin{landscape}
+	\begin{table}[htbp]
+		%\caption{}
+		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+			\hline
+			Names & Year & Journal & Findings & Important? \\ \hline
+			Armstrong, Cory L.
+& 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
+Manual content analysis (undergrads told to look around for 15 minutes).
+School board websites, more professional websites, and websites in Republican-dominated counties are found to be more transparent.
+& Yes \\ \hline
+			Cegarra-Navarro, Juan
+			Pachón, José
+			Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
+Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
+More sophisticated websites are correlated with greater civic engagement and greater use of e-government functions.
+& Yes \\ \hline
+			Dolson, Jordan
+			Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
+Three categories: e-content (city information on website), e-participation, social media use.
+Tables on page 15 show frequencies of these categories across sites, and might be useful to inform our topics.
+Larger cities have better websites.
+Population growth and immigration are also tested, but the findings are somewhat inconclusive.
+& Yes \\ \hline
+			Feeney, Mary K.
+			Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
+city websites at two points in time (2010-2014).
+Count model of website features regarding information, e-services, utilities, transparency and civic engagement.
+Having a larger population leads to more features.
+Relying on a website contractor leads to more information and transparency.
+The authors say that mayor-councils are negatively correlated with website sophistication, but their regression tables state the opposite.
+& Yes \\ \hline
+			Kaylor, Charles
+			Deshazo, Randy
+			Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
+Table 1 lists a number of possible ways this manifests, could be useful for our theory.
+& Somewhat \\ \hline
+			Ansolabehere, Stephen
+			Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
+Is website content correlated with city characteristics?
+Not particularly systematic, and the findings are inconclusive.
+& Somewhat \\ \hline
+			Jeffres, Leo W.
+			Lin, Carolyn A.
+& 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
+Features include information about city, opportunities for citizen feedback, galleries of photos, links, etc.
+Purely descriptive analysis, doesn't contain anything that isn't covered in any of the other aricles.
+& No \\ \hline
 		\end{tabular}

### 2017-05-30 govWebsitesFiletypes.R

@@ -90,5 +90,6 @@ filesfolders_all$files_change <- filesfolders_all$after_files/filesfolders_all$b
 load('./data/URLs_IN.rdata')
 URLs <- subset(URLs, select = c("foldername", "control_change"))
 filesfolders_all2 <- merge(filesfolders_all, URLs, by.x = "Website", by.y = "foldername")
+filesfolders_all2 <- filesfolders_all2[order(filesfolders_all2$control_change),]
 
-print(xtable(filesfolders_all, caption="Number of files and size of websites"), include.rownames = F)
+print(xtable(filesfolders_all2, caption="Number of files and size of websites"), include.rownames = F)

### 2017-06-19 countLinesSize.R
code to run LDA with mallet + results figure (word-topic probabilities) added to manuscript. I only added the one for the wget website content, the wayback machine ones look strange because they contain words that are too long (and also do not exist)

@@ -1,0 +1,44 @@
+library('readtext')
+library('tools')
+library('tibble')
+library('stringr')
+
+#setwd("~/Dropbox/4_RA/govWebsites")
+setwd("./websites/websites")
+
+
+f <- list.files(recursive = T) #create a list of all files in all subdirectories
+
+#file types
+ext <- file_ext(f) #get file extension
+folder <- str_split(f, "\\/(?=[^\\/]+$)", simplify = T)[,1]
+filename <- str_split(f, "\\/(?=[^\\/]+$)", simplify = T)[,2]
+
+d <- tibble(f, folder, filename, ext)
+d <- d[d$ext%in%c("doc","docx","pdf","html",""),]
+
+#determine the size of the file (in bytes)
+d$filesize <- file.size(f)
+
+#determine the number of lines in the file
+#length(readLines()) is supposed to be the slowest, but for some reason
+#in this case, it is the fastest of the three approaches I tried
+
+#profvis::profvis({
+
+d$numlines <- sapply(f, function(x){length(readLines(x))})
+#a <- sapply(f, R.utils::countLines)
+
+#a <- sapply(f, function(x){
+#  as.integer(system2("wc",
+#                     args = c("-l",
+#                              x,
+#                              " | awk '{print $1}'"),
+#                     stdout = TRUE))
+#}
+#)
+
+
+#})
+
+d$fileratio <- d$filesize/d$numlines

### 2017-06-19 mallet.R

@@ -1,0 +1,234 @@
+#This option has to be set BEFORE loading the rJava package (loaded by mallet)
+#Gives rJava about 8GB to work with
+#So far, I've only needed 2.3GB
+options(java.parameters = "-Xmx8000m")
+
+library('mallet')
+library('tibble')
+library('stringr')
+library('tools')
+library('tm')
+library('ggplot2')
+
+#setwd("./websites/websites")
+#setwd("~/RA4_website_archive/websites/current")
+
+f <- list.files(recursive = T) #create a list of all files in all subdirectories
+
+#file types
+ext <- file_ext(f) #get file extension
+folder <- str_split(f, "\\/(?=[^\\/]+$)", simplify = T)[,1]
+filename <- str_split(f, "\\/(?=[^\\/]+$)", simplify = T)[,2]
+
+d <- tibble(f, folder, filename, ext)
+
+#read in file text
+a <- str_c(readLines(d$f[1]), sep = " ", collapse = " ")
+#a
+d$a <- sapply(d$f, function(x){str_c(readLines(x), sep = " ", collapse = " ")})
+
+d$a <- as.character(d$a)
+
+#write stopwords list from the tm package to a text file
+fileConn <- file("../../stopwords.txt")
+writeLines(stopwords("english"), fileConn)
+close(fileConn)
+
+################################################################################
+
+#Mallet
+
+#Import website text
+mallet.instances <- mallet.import(id.array = make.unique(d$folder),
+                                  text.array = d$a,
+                                  stoplist.file = "../../stopwords.txt",
+                                  token.regexp = "\\p{L}[\\p{L}\\p{P}]+\\p{L}")
+
+#
+n.topics <- 100
+topic.model <- MalletLDA(n.topics)
+
+## Load our documents. We could also pass in the filename of a 
+##  saved instance list file that we build from the command-line tools.
+topic.model$loadDocuments(mallet.instances)
+
+## Get the vocabulary, and some statistics about word frequencies.
+##  These may be useful in further curating the stopword list.
+vocabulary <- topic.model$getVocabulary()
+vocabulary
+
+word.freqs <- mallet.word.freqs(topic.model)
+word.freqs
+
+## Optimize hyperparameters every 20 iterations, 
+##  after 50 burn-in iterations.
+topic.model$setAlphaOptimization(20, 50)
+
+## Now train a model. Note that hyperparameter optimization is on, by default.
+##  We can specify the number of iterations. Here we'll use a large-ish round number.
[…]

### 2017-07-04 hunspellParallel.R
added the mallet and hunspell stuff

@@ -1,0 +1,54 @@
+library('hunspell')
+library('tm')
+library('parallel')
+#library('profvis')
+
+# Calculate the number of cores
+ncores <- detectCores() - 1
+# Initiate cluster
+# type="FORK" is necessary to load all the libraries
+# supposedly only works on Unix systems
+cl <- makeCluster(ncores, type = "FORK")
+
+#setwd("./websites/current")
+load(file = "./rfiles/dd.Rdata")
+
+
+#function to apply spellchecking
+#on each text, apply hunspell, and save the character vector of incorrect words
+#since grep has a limit for how many words it can process,
+#only use removeWords (from the tm package) if the number of errors is less than 1000
+#generally this only happens if a document is completely messed up, in which case
+#it is probably best to discard the whole thing
+#in this case, just insert ERROR instead of the document
+hunRemove <- function(charstring){
+  errors <- unlist(hunspell(charstring))
+  if(length(errors)<1000){
+    output <- removeWords(charstring, errors)
+    return(output)
+  }
+  else{
+    return("ERROR")
+  }
+}
+
+#for testing purposes, only spellcheck some of the documents
+#d <- d[1:200,]
+
+#check duration of running the spellchecking
+ptm <- proc.time()
+#then use parSapply to use it on everything in parallel
+d$doc2 <- parSapply(cl, d$doc, FUN = hunRemove)
+proc.time() - ptm
+#On 6 cores (i.e. 12 threads, of which I used 11)
+#it ended up taking 14 hours
+
+# shut down the workers
+stopCluster(cl)
+
+#record when it did encounter more than 1000 errors
+d$spell_fail <- 0
+d$spell_fail[d$doc2=="ERROR"] <- 1
+
+#save
+save(d, file = "../../docs.Rdata")

### 2017-07-04 websites/batchconversion_docx.sh

@@ -1,1 +1,0 @@
-find ./websites/ -name \*.docx -exec docx2txt "{}" \;

### 2017-07-04 websites/batchconversion_pdf.sh

@@ -1,1 +1,0 @@
-find ./websites/ -name \*.pdf -exec pdftotext "{}" \;

### 2017-07-17 paper/manuscript.tex
code to run LDA with mallet + results figure (word-topic probabilities) added to manuscript. I only added the one for the wget website content, the wayback machine ones look strange because they contain words that are too long (and also do not exist)
added the mallet and hunspell stuff
added comparison of topic prevalence in democratic and republican cities

@@
 	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtpIndy.pdf}
+	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
 \end{figure}
 
-% latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Fri Mar 24 12:52:43 2017
-\begin{table}[ht]
+\begin{figure}[!ht]
 	\centering
-\begin{tabular}{lrrrr}
-  \hline
-File type & oct15 & jan16 & feb16 & mar16 \\ 
-  \hline
-.pdf & 179 & 183 & 111 & 197 \\ 
-  .aspx &  99 & 112 & 116 &  76 \\ 
-  .jpg &  22 &  24 &  17 &  12 \\ 
-  .gif &   3 &   5 &   1 &   5 \\ 
-  .JPG &   3 &   2 &   1 &   5 \\ 
-  .png &   3 &   7 &   2 &   1 \\ 
-  .asmx &   2 &   1 &   1 &   5 \\ 
-  .PDF &   1 &   1 &   1 &   2 \\ 
-   \hline
-\end{tabular}
-\caption{File types of Indy.gov at different points in time} 
-\end{table}
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
+\end{figure}
+
+%\begin{figure}[!ht]
+%	\centering
+	%\caption{Population coverage}
+%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
+%\end{figure}
+
+%\begin{figure}[!ht]
+%	\centering
+	%\caption{Population coverage}
+%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
+%\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
+\end{figure}
 

### 2017-07-17 mallet.R

@@ -118,7 +118,8 @@ mallet.instances <- mallet.import(id.array = make.unique(d$folder),
                                   token.regexp = "\\p{L}[\\p{L}\\p{P}]+\\p{L}")
 
 #Create a Mallet topic model trainer
-topic.model <- MalletLDA(num.topics = 100)
+ntopics <- 100
+topic.model <- MalletLDA(num.topics = ntopics)
 
 ## Load our documents. We could also pass in the filename of a 
 ##  saved instance list file that we build from the command-line tools.
@@ -202,7 +203,7 @@ rep.topic.words <- mallet.subset.topic.words(topic.model, d$winner == "Republica
 df.words.dem <- tibble()
 df.words.rep <- tibble()
 
-for(i in 1:100){
+for(i in 1:ntopics){
   df.words.dem2 <- as.tibble(mallet.top.words(topic.model, dem.topic.words[i,]))
   df.words.rep2 <- as.tibble(mallet.top.words(topic.model, rep.topic.words[i,]))
   df.words.dem2$topic <- str_c("topic_", str_pad(i, 2, pad = "0"))
@@ -279,3 +280,62 @@ plotWTP_dem_rep
 
 #save
 ggsave(plotWTP_dem_rep, file = str_c("./paper/figures/wtp_", corpus, "_dem_rep_large_differences.pdf"), width=7, height=9)
+
+
+
+###What proportion of tokens in docs in Dem-led cities are assigned to topic X, for all X
+
+#Which topic is a word most likely to be assigned to?
+topicnames <- unique(select(df.words.dem, topic))
+topicnames$tokenfreq_dem <- table(apply(dem.topic.words, 2, which.max))
+topicnames$tokenfreq_rep <- table(apply(rep.topic.words, 2, which.max))
+
+#Strikingly, the #1 topic for Republicans includes 17660 tokens (more than half)
+#whereas the #1 topic for Democrats includes only 1324
+#the question is: is this a meaningful diffference, or just a result of the number of topics,
+#which at the moment is only 100
+
+#Create variable to appear as the title in the plot at the end ("topic_number (# tokens)")
+topicnames$topic_tokenfreq_dem <- str_c(topicnames$topic, " (", topicnames$tokenfreq_dem, " tokens)")
+topicnames$topic_tokenfreq_rep <- str_c(topicnames$topic, " (", topicnames$tokenfreq_rep, " tokens)")
+
[…]

### 2017-07-18 paper/manuscript.tex
made multiple changes to the makefile

@@
 
-% latex table generated in R 3.4.0 by xtable 1.8-2 package
-% Tue May 23 19:28:26 2017
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{lrrr}
-		\hline
-		Filetype & current & before & after \\ 
-		\hline
-		& 51455 & 13866 & 19199 \\ 
-		pdf & 9646 & 5489 & 7544 \\ 
-		jpg & 5216 & 1988 & 3512 \\ 
-		html & 3767 & 17842 & 17596 \\ 
-		aspx & 2832 & 4356 & 3271 \\ 
-		png & 2714 & 2327 & 3684 \\ 
-		gif & 1068 & 664 & 1077 \\ 
-		JPG & 478 & 182 & 263 \\ 
-		1 & 443 &  61 &  54 \\ 
-		css & 390 & 265 & 518 \\ 
-		js & 350 & 255 & 468 \\ 
-		htm & 264 & 295 & 256 \\ 
-		docx & 203 & 106 & 120 \\ 
-		doc & 167 &  70 & 130 \\ 
-		asp & 161 & 201 & 211 \\ 
-		svg &  87 &  55 &  69 \\ 
-		php &  83 & 157 & 241 \\ 
-		\hline
-	\end{tabular}
-	\caption{The most common file types in scraped websites} 
-\end{table}
+\input{tables/filetypes.tex}
 
 \begin{landscape}
-% latex table generated in R 3.4.0 by xtable 1.8-2 package
-% Tue May 23 19:35:22 2017
-\begin{table}[ht]
-	\centering
-	\footnotesize
-	\begin{tabular}{lrrrrrrrrr}
-		\hline
-		Website & current\_size & current\_files & before\_size & before\_files & after\_size & after\_files & size\_change & files\_change & control\_change \\ 
-		\hline
-		attica-in.gov & 61988 & 1417 & 7528 & 164 & 55956 & 1390 & 7.43 & 8.48 & 0.00 \\ 
-		bedford.in.us & 57628 & 560 & 27452 & 182 & 46388 & 525 & 1.69 & 2.88 & 0.00 \\ 
-		cityofboonvilleindiana.com & 9848 & 110 & 16996 & 172 & 20784 & 229 & 1.22 & 1.33 & 0.00 \\ 
-		frankfort-in.gov & 205368 & 2652 & 12208 & 242 & 138360 & 1077 & 11.33 & 4.45 & 0.00 \\ 
-		warsaw.in.gov & 298440 & 2117 & 26844 & 539 & 360400 & 2036 & 13.43 & 3.78 & 0.00 \\ 
-		www.bloomington.in.gov & 131128 & 2713 & 443360 & 14384 & 247096 & 9640 & 0.56 & 0.67 & 0.00 \\ 
-		www.brazil.in.gov & 43056 & 845 & 34472 & 625 & 55152 & 1214 & 1.60 & 1.94 & 0.00 \\ 
-		www.carmel.in.gov & 2270016 & 8727 & 1919344 & 5361 & 899900 & 2219 & 0.47 & 0.41 & 0.00 \\ 
-		www.ci.auburn.in.us & 183296 & 1025 & 21444 & 345 & 23564 & 211 & 1.10 & 0.61 & 0.00 \\ 
-		www.cityoffortwayne.org & 2136424 & 4378 & 266784 & 3582 & 233600 & 3018 & 0.88 & 0.84 & 0.00 \\ 
-		www.cityofhobart.org & 722000 & 2463 & 44192 & 650 & 62660 & 1037 & 1.42 & 1.60 & 0.00 \\ 
-		www.evansvillegov.org & 6345932 & 11844 & 290784 & 1281 & 1697224 & 6853 & 5.84 & 5.35 & 0.00 \\ 
-		www.gary.in.us & 373888 & 1227 & 121812 & 485 & 157140 & 719 & 1.29 & 1.48 & 0.00 \\ 
-		www.huntingburg-in.gov & 388680 & 2496 & 8644 & 213 & 375900 & 1953 & 43.49 & 9.17 & 0.00 \\ 
-		www.jasperindiana.gov & 561968 & 4013 & 55900 & 460 & 439072 & 2224 & 7.85 & 4.83 & 0.00 \\ 
-		www.lakestation-in.gov &  48 &   2 & 7724 &  84 & 257272 & 1097 & 33.31 & 13.06 & 0.00 \\ 
-		www.linton-in.gov &  32 &   1 &  24 &   2 &  24 &   2 & 1.00 & 1.00 & 0.00 \\ 
-		www.madison-in.gov & 531044 & 1848 & 36636 & 575 & 191624 & 1444 & 5.23 & 2.51 & 0.00 \\ 
-		www.martinsville.in.gov & 46792 & 1463 & 71628 & 1052 & 80944 & 800 & 1.13 & 0.76 & 0.00 \\ 
-		www.monticelloin.gov & 33656 & 753 & 18120 & 448 & 100680 & 2104 & 5.56 & 4.70 & 0.00 \\ 
-		www.newhavenin.org & 84364 & 626 & 2524 &  86 & 6792 & 334 & 2.69 & 3.88 & 0.00 \\ 
-		www.richmondindiana.gov & 250968 & 1042 & 217252 & 918 & 401672 & 2422 & 1.85 & 2.64 & 0.00 \\ 
-		www.southbendin.gov & 1264076 & 4749 & 454456 & 3286 & 1424136 & 2562 & 3.13 & 0.78 & 0.00 \\ 
-		connersvillecommunity.com & 170688 & 569 & 162316 & 815 & 187276 & 808 & 1.15 & 0.99 & 1.00 \\ 
-		www.batesvilleindiana.us & 166564 & 2348 & 39592 & 496 & 95696 & 1310 & 2.42 & 2.64 & 1.00 \\ 
-		www.cityofrisingsun.com & 994956 & 3311 & 321400 & 1268 & 80848 & 868 & 0.25 & 0.68 & 1.00 \\ 
-		www.cityofrockport-in.gov & 12068 &  98 & 5148 &  16 & 12068 &  98 & 2.34 & 6.12 & 1.00 \\ 
-		www.elkhartindiana.org & 1132828 & 2345 & 5588 & 123 & 6204 & 223 & 1.11 & 1.81 & 1.00 \\ 
-		www.elwoodcity-in.org & 224412 & 765 & 5000 & 123 & 139692 & 517 & 27.94 & 4.20 & 1.00 \\ 
-		www.indy.gov & 5726048 & 9675 & 6119260 & 10451 & 4984080 & 7981 & 0.81 & 0.76 & 1.00 \\ 
-		www.northvernon-in.gov & 272016 & 403 & 3132 & 112 & 289336 & 416 & 92.38 & 3.71 & 1.00 \\ 
-		www.winchester-in.gov & 364592 & 2480 & 6508 & 135 & 45488 & 567 & 6.99 & 4.20 & 1.00 \\ 
-		\hline
-	\end{tabular}
-	\caption{Number of files and size of websites} 
-\end{table}
+\input{tables/filenumbers.tex}
 \end{landscape}
-
-% latex table generated in R 3.3.2 by xtable 1.8-2 package
-% Wed Mar  1 11:55:24 2017
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{rr}
-		\hline
-		& tf \\ 
-		\hline
-		tax & 176324 \\ 
-		date & 98949 \\ 
-		due & 97192 \\ 
-		amt & 96382 \\ 
-		town & 86726 \\ 
-		value & 81119 \\ 
-		total & 70825 \\ 
-		parcel & 63589 \\ 
-		county & 56201 \\ 
-		market & 51758 \\ 
-		east & 51357 \\ 
-		full & 51199 \\ 
-		nrth & 50566 \\ 
-		book & 50306 \\ 
-		deed & 50231 \\ 
-		bill & 49719 \\ 
-		acres & 48935 \\ 
-		acct & 44871 \\ 
-		csd & 43792 \\ 
-		owners & 43510 \\ 
-		res & 41803 \\ 
-		family & 36883 \\ 
-		fire & 35156 \\ 
-		school & 33685 \\ 
-		name & 30382 \\ 
-		red & 30362 \\ 
-		taxable & 30248 \\ 
-		hook & 29902 \\ 
-		homestead & 29287 \\ 
-		outside & 28593 \\ 
-		\hline
-	\end{tabular}
-	\caption{Top term frequencies for 10 test websites} 
-\end{table}
 
@@
 % Wed Mar 22 11:32:43 2017
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{lrrlrrl}
-		\hline
-		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
-		\hline
-		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
-		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
-		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
-		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
-		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
-		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
-		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
-		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
-		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
-		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
-		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
-		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
-		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
-		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
-		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
-		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
-		\hline
-	\end{tabular}
-	\caption{} 
-\end{table}
+%\begin{table}[ht]
+%	\centering
+%	\begin{tabular}{lrrlrrl}
+%		\hline
+%		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
+%		\hline
+%		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
+%		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
+%		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
+%		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
+%		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
+%		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
+%		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
+%		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
+%		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
+%		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
+%		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
+%		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
+%		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
+%		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
+%		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
+%		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
+%		\hline
+%	\end{tabular}
+%	\caption{} 
+%\end{table}
 

### 2017-07-18 govWebsitesVerification.R

@@ -9,16 +9,19 @@ require(stringr)
 require(stringi)
 
 #read in the data created by the python scripts
-results1 <- read.table("results/results1.txt")
-results2 <- read.table("results/results2.txt")
-results3 <- read.table("results/results3.txt")
-results4 <- read.table("results/results4.txt")
-results5 <- read.table("results/results5.txt")
-results6 <- read.table("results/results6.txt")
+#results1 <- read.table("results/results1.txt")
+#results2 <- read.table("results/results2.txt")
+#results3 <- read.table("results/results3.txt")
+#results4 <- read.table("results/results4.txt")
+#results5 <- read.table("results/results5.txt")
+#results6 <- read.table("results/results6.txt")
 
 #crete one data frame
-result <- rbind(results1,results2,results3,results4,results5,results6)
-rm(results1,results2,results3,results4,results5,results6)
+#result <- rbind(results1,results2,results3,results4,results5,results6)
+#rm(results1,results2,results3,results4,results5,results6)
+
+#the same, with only one file
+result <- read.table("data/verified_sites.txt")
 
 #read in original RSA file
 data <- read.csv("data/current-full.csv")

### 2017-07-24 malletAnalysis.R
further analysis of distribution of topics across documents

@@ -1,52 +1,211 @@
+options(java.parameters = "-Xmx3000m")
+
+library('mallet')
+library('tibble')
+library('stringr')
+library('tools')
+library('tm')
+library('ggplot2')
+library('cowplot')
+library('dplyr')
+library('quanteda')
+library('hunspell')
+
+corpus <- "current" #"current", "before", or "after"
+
+#Hunspell
+load(file = str_c("./rfiles/docs_", corpus, ".Rdata"))
+
+#remove documents where spellchecking failed
+d <- d[d$spell_fail==0,]
+
+#remove non-spellchecked text
+d$doc <- d$doc2
+d <- select(d, -doc2)
+
+#Import website text
+mallet.instances <- mallet.import(id.array = make.unique(d$folder),
+                                  text.array = d$doc,
+                                  stoplist.file = "./rfiles/stopwords.txt",
+                                  token.regexp = "\\p{L}[\\p{L}\\p{P}]+\\p{L}")
+
+#Create a Mallet topic model trainer
+ntopics <- 100
+topic.model <- MalletLDA(num.topics = ntopics)
+
+## Load our documents. We could also pass in the filename of a 
+##  saved instance list file that we build from the command-line tools.
+topic.model$loadDocuments(mallet.instances)
+
+## Get the vocabulary (i.e. list of all the words)
+vocabulary <- topic.model$getVocabulary()
+vocabulary
+
+## word frequencies
+## also contains a column with the total number of documents a word appears in
+word.freqs <- mallet.word.freqs(topic.model)
+word.freqs[order(word.freqs$term.freq, decreasing = T),]
+
+## Optimize hyperparameters every 20 iterations, 
+##  after 50 burn-in iterations.
+topic.model$setAlphaOptimization(20, 50)
+
+## Now train a model. Note that hyperparameter optimization is on, by default.
+##  We can specify the number of iterations. Here we'll use a large-ish round number.
+topic.model$train(200)
+
+#R seems to be using about 2.3GB while training the model
+#takes about 5 minutes
+
+## NEW: run through a few iterations where we pick the best topic for each token, 
+##  rather than sampling from the posterior distribution.
+topic.model$maximize(10)
+
+####################################################################
[…]

### 2017-07-25 paper/manuscript.tex
further analysis of distribution of topics across documents
added more analysis of topic weights

@@
 
+%topicweights density
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
+	\label{doctopics_density}
+	\includegraphics[width=\linewidth]{figures/doctopics_density.pdf}
+\end{figure}
+
+Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic.
+Distributions with lower peaks near zero and flatter bodies indicate a topic that is present to varying degrees in multiple documents.
+This shape appears to be more common in documents from Republican cities.
+By contrast, a distribution with a high peak near zero and a very long tail is indicative of a topic that only appears in one specific document.
+This appears to be more common for documents in Democratic cities.
+The substantive conclusion then is that Democrats appear to be more prone to dedicating individual documents to one specific purpose, whereas Republicans produce general-purpose documents more often.
+
+%topicweights density
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
+	\label{topicweights_density}
+	\includegraphics[width=\linewidth]{figures/topicweights_density.pdf}
+\end{figure}
+
+An alternative way to consider topic weights is to aggregate them across documents, in this case through their median or mean.
+Figure \ref{topicweights_density} shows this distribution of topic weights across topics.
+Most topics have a very low weight - meaning that they do not appear in a lot of documents.
+When aggregating across documents via the mean, this effect is more pronounced for Republicans, suggesting that most topics do not feature frequently (or even at all) in their documents.
+Democrats on the other hand appear to have a wider spectrum of topics from which they chose - supporting the hypothesis of Democrats as a 'big tent' party.
+However, this effect is reversed when using the median instead of the mean to aggregate across documents.
+Now, the the distribution has a higher peak and lower tail for Democrats.
+The cause for this stark divergence appears to lie in the fact the mean and median differ enormously - for the range displayed here, the mean is about a hundred times greater.
+Evidently, extremely large weights (i.e.
+some documents fitting specific topics perfectly) distort the picture.
+The median document is a better representation of the corpus as a whole, but the results do not fit our hypothesis.
+Their are however more consistent with figure \ref{topicweights_density}.
+
+%word topic probabilities for topics with big differences
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences}
+	\label{plotWTP_bigdiffs}
+	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs.pdf}
+\end{figure}
+
+%word topic probabilities for topics with big differences
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences}
+	\label{doctopics_density_bigdiffs}
+	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs.pdf}
+\end{figure}
+
 \newpage
 
-%\bibliographystyle{apsr} % apsr stopped working for me
-\bibliographystyle{plainnat}
+\bibliographystyle{apsr} % apsr stopped working for me
+%\bibliographystyle{plainnat}
 \bibliography{ref}

### 2017-07-25 malletAnalysis.R

@@ -102,6 +102,40 @@ democratic <- doc.topics[which(d$winner == "Democratic"),]
 republican <- as.tibble(republican)
 democratic <- as.tibble(democratic)
 
+## For each topic, calculate the median (or mean) weight across documents
+# i.e., on average (or median), documents contain x percent of words belonging to topic y
+rep.topic.prop <- apply(republican, 2, median)
+dem.topic.prop <- apply(democratic, 2, median)
+
+## Plot distribution of both
+weights.tibble <- tibble(Republican = rep.topic.prop, Democratic = dem.topic.prop) %>%
+  gather(Party, weight)
+topicweights_density <- ggplot(weights.tibble, aes(weight, color = Party)) + 
+  geom_density(size=1) + 
+  theme(legend.position="top") +
+  scale_color_manual(values=c("#4286f4", "#f44441")) +
+  ggtitle("Median document")
+#topicweights_density
+#ggsave(topicweights_density, file = str_c("./paper/figures/topicweights_density.pdf"), width=9, height=7)
+
+#Do the same thing, but with the mean instead of the median
+rep.topic.prop2 <- apply(republican, 2, mean)
+dem.topic.prop2 <- apply(democratic, 2, mean)
+## Plot distribution of both
+weights.tibble2 <- tibble(Republican = rep.topic.prop2, Democratic = dem.topic.prop2) %>%
+  gather(Party, weight)
+topicweights_density2 <- ggplot(weights.tibble2, aes(weight, color = Party)) + 
+  geom_density(size=1) + 
+  theme(legend.position="top") +
+  scale_color_manual(values=c("#4286f4", "#f44441")) +
+  ggtitle("Mean document")
+#topicweights_density2
+#ggsave(topicweights_density2, file = str_c("./paper/figures/topicweights_density2.pdf"), width=9, height=7)
+
+#Plot them together
+topicweights_density3 <- plot_grid(topicweights_density, topicweights_density2)
+topicweights_density3
+ggsave(topicweights_density3, file = str_c("./paper/figures/topicweights_density.pdf"), width=9, height=5)
 
 ## Plot the densities of weights across documents for each topic
 # i.e. each line is a topic
[…]

### 2017-07-26 paper/manuscript.tex
more analysis of topic weights + writeup

@@
 
+Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us.
+To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}.
+For the most part, differences are small.
+For a few topics however, a contrasts emerges.
+
+%size of the differences
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences}
+	\label{diffsize}
+	\includegraphics[width=\linewidth]{figures/diffsize.pdf}
+\end{figure}
+
+Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences.
+Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged.
+For the most part however, these topics focus on administrative matters.
+
 %word topic probabilities for topics with big differences
@@
 \end{figure}
+
+To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences.
+It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.
 
@@
 
+To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps.
+Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents.
+Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else.
+One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.
+
+%Heatmaps
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences}
+	\label{heatmaps_weights}
+	\includegraphics[width=\linewidth]{figures/heatmaps_weights.png}
+\end{figure}
+
 \newpage

### 2017-08-04 topicCoherence.R
topic coherence, by number of topics, plotted

@@ -1,10 +1,11 @@
-options(java.parameters = "-Xmx10000m")
+options(java.parameters = "-Xmx5000m")
 
 library('SpeedReader')
 library('mallet')
 library('dplyr')
 library('tibble')
 library('stringr')
+library('ggplot2')
 
 #load data
 load(file = "./rfiles/d.Rdata")
@@ -51,4 +52,17 @@ for(j in 1:length(topicsizes)){
   
 }
 
-plot(coherence_values, topicsizes)
+save(coherence_values, file = "rfiles/coherence_20_50.rdata")
+
+coh <- as.tibble(unlist(coherence_values))
+coh$numtopic <- rep(as.character(topicsizes),
+                    topicsizes)
+
+p <- ggplot(coh, aes(numtopic, value)) + 
+  labs(title = "", x = "Number of topics", y = "Topic coherence") +
+  geom_boxplot() + 
+  stat_summary(fun.y = mean, colour = "red", geom = "line", aes(group = 1))  + 
+  stat_summary(fun.y = mean, colour = "red",  geom = "point")
+p
+
+ggsave(p, file = str_c("./paper/figures/coherence_numberoftopics.pdf"), width = 8, height = 5)

### 2017-08-06 mapIndiana.R
added map of indiana with mayoral partisanship

@@ -1,0 +1,26 @@
+library("dplyr")
+library("ggplot2")
+library("ggmap")
+
+#load data
+load("rfiles/d.Rdata")
+d <- d[!duplicated(d$Name),]
+d$latitude <- as.numeric(d$latitude)
+d$longitude <- as.numeric(d$longitude)
+
+## Indiana
+# get the map from Google maps
+indiana <- subset(states, region %in% c("indiana"))
+map1 <- ggplot(data = indiana) + 
+  geom_polygon(aes(x = long, y = lat, group = group), fill = "papayawhip", color = "black") + 
+  coord_fixed(1.3)
+map1
+#overlay points on map
+map2 <- map1 + 
+  geom_point(data = d, aes(x = longitude, y = latitude, color = winner), size = 2) + 
+  theme(legend.position = "none") + 
+  scale_color_manual(values=c("blue", "red")) +
+  labs(x = "Longitude", y = "Latitude")
+map2
+
+ggsave(filename = "paper/figures/indiana_map.pdf", plot = map2, width = 5, height = 8)

### 2017-08-06 cityCoordinates.R
minor changes to map

@@ -18,8 +18,8 @@ get_link <- function(html_table, team){
 
 df$wiki_link <- sapply(df$City, function(x)get_link(mytable, x))
 
-
-df <- df[df$City%in%unique(d$Name),]
+#load("rfiles/d.Rdata")
+#df <- df[df$City%in%unique(d$Name),]
 
 
 #function to extract the links to the city websites
@@ -37,7 +37,7 @@ df$coords <- sapply(df$wiki_link, extractCoords)
 
 indianacities <- subset(df, select=c("City", "County", "wiki_link", "coords"))
 
-d <- merge(d, indianacities, by.x = "Name", by.y = "City")
+d <- merge(d, indianacities, by.x = "Name", by.y = "City", all = T)
 
 coords <- str_split_fixed(d$coords, "/", 3)[,3] %>% str_split_fixed(";", 2)
 d$latitude <- str_trim(coords[,1])
@@ -46,4 +46,4 @@ d$longitude <- str_trim(coords[,2])
 d <- subset(d, select=-coords)
 
 #save
-save(d, file="rfiles/d.Rdata")
+save(d, file="rfiles/d_coords.Rdata")

### 2017-08-14 paper/manuscript.tex
topic coherence, by number of topics, plotted
added map of indiana with mayoral partisanship
minor changes to map
updated the tex file and delete/moved some other stuff

@@
 	\centering
-	%\caption{Population coverage}
+	\caption{Percentage of state population covered.}
 	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
@@
 
+%Number of topics vs. tophic coherence
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
+	\label{numtopics_coherence}
+	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
+\end{figure}
+
+%Indiana map
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Cities in the corpus, by partisanship of mayor.}
+	\label{indiana_map}
+	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
+\end{figure}
+
+%partisan topics
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{The most partisan topics.
+The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
+	\label{partisan_topics}
+	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
+\end{figure}
+
 \newpage

### 2017-08-14 cleanDocumentsBoilerplate.R

@@ -1,173 +1,0 @@
-library('SpeedReader')
-library('quanteda')
-library('tibble')
-library('dplyr')
-library('stringr')
-
-load("rfiles/d.Rdata")
-d <- d[d$Name%in%c("Attica", "Auburn", "Brazil", "Gary"),]
-
-
-#tf-idf for the whole corpus
-
-#create corpus
-crps <- corpus(d$doc)
-docvars(crps, "City") <- d$Name
-cities <- unique(docvars(crps, "City"))
-remove_words <- list()
-
-for(i in 1:length(cities)){
-  city <- corpus_subset(crps, City == cities[i])
-  city <- dfm(city, ngrams = 3)
-  #binarize document-term matrix
-  city@x <- rep(1, length(city@x))
-  #column sums of binarized dtm
-  binTF <- colSums(city)
-  #how many documents does the city have
-  cityDocs <- dim(city)[1]
-  #remove n-grams which occur in more than 10% of city documents
-  remove <- names(binTF[binTF>(0.1*cityDocs)])
-  remove_words <- c(remove_words, list(remove))
-}
-
-#################
-
-#get rid of underscores
-remove_words2 <- lapply(remove_words, function(X){str_replace_all(X, "_", " ")})
-
-#################
-
-citytable <- sapply(unique(d$Name), function(x){length(d$doc[d$Name==x])})
-citynames <- names(citytable)
-
-##############################################################
-
-cityindex <- rep(names(citytable), each = citytable)
-remove_words2 <- lapply(remove_words, function(X){str_replace_all(X, "_", " ")})
-d$doc2 <- d$doc
-#loop over cities
-for(k in 1:nrow(d)){
-  
-  cityname <- cityindex[k]
-  cityind <- match(cityname, names(citytable))
-  
-  #loop over words to be removed for this document
-  a <- d$doc[k]
-  for(i in 1:length(remove_words2[[cityind]])){
-    a <- clean_document_text(a, regex = remove_words2[[cityind]][i])
-    a <- str_c(a, collapse = " ")
-  }
-  
-  d$doc2[k] <- a
-  
-}
-
-##############################################################
-
-#create a new document variable
-d$doc2 <- d$doc
-
-#loop over cities
-for(k in 1:length(cities)){
-  #if not the first city, start in this row
-  if(k>1){
-    citystart <- sum(citytable[1:(k-1)])+1
-  }
-  #if the first city, start on the first row
-  else{
-    citystart <- 1
-  }
-  
-  #how many documents does the current city have?
[…]

### 2017-08-14 malletTraining.R

@@ -27,7 +27,6 @@ topic.model$loadDocuments(mallet.instances)
 
 ## Get the vocabulary (i.e. list of all the words)
 vocabulary <- topic.model$getVocabulary()
-vocabulary
 
 ## word frequencies
 ## also contains a column with the total number of documents a word appears in

### 2017-08-18 paper/manuscript.tex
added description of preprocessing to paper

@@
 \end{landscape}
+
+For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results. Consequently we restricted our corpus to cities with at least 3 documents.
+
+\section{Preprocessing}
+
+The documents are read in line by line, converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
+At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
+"You are here", "Home", "Directory" etc.) in html documents, or commonly used forms or phrases in pdfs, doc and docx files.
+This is an issue, because it clusters documents around the cities from which they originate in a way that has nothing to do with their actual content.
+In other words, the signal would be drowned out by the noise.
+Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
+We count how many times each line is duplicated for that city.
+We remove any line occuring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times, or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
+Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
+Furthermore, some documents contain gibberish, often as a result of faulty or impartial OCR.
+To combat this problem, we employ two solutions.
+One, we use spellchecking, implemented through the hunspell R package, to remove all non-English words.
+However, hunspell does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
+Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the english alphabet.
+Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to total number of tokens is less than 0.15.
+Furthermore, hunspell does not spellcheck individual characters, so we remove all individual characters appearing as tokens except for "i" and "a".
+Since these pre-processing steps reduce documents which are largely unsuitable to only a few words of texts that don't make much sense, we also remove all remaining documents containing less than 50 tokens.
 
@@
 
+%ldatuning
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{The optimal number of topics for our corpus.
+The measures of Griffths 2004 and Cao 2009 indicate the best number of topics at their minimum, whereas the measure of Arun 2010 points to the best value at its maximum.}
+	\label{ldatuning}
+	\includegraphics[height=0.75\textheight]{figures/topicnumber_ldatuning.pdf}
+\end{figure}
+
 \newpage

### 2017-08-30 paper/manuscript.tex
added removal of terms that are more common in city than in corpus (by a threshold); removal of city names; short addition to paper explaining reason for using Arun et al. 2010 measure

@@
 
+%Justicifcation for Arun 2010 topic number measure
+In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}.
+In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix.
+We find 200 topics to be the best value (see figure \ref{ldatuning}).
+
 %One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.

### 2017-08-30 functions/namedEntityRemover.R

@@ -1,0 +1,30 @@
+library("openNLP")
+library("openNLPmodels.en")
+library("NLP")
+library("tm")
+
+removeNamedEntity <- function(string){
+  s <- as.String(string)
+  ## Need sentence and word token annotations.
+  sent_token_annotator <- Maxent_Sent_Token_Annotator()
+  word_token_annotator <- Maxent_Word_Token_Annotator()
+  a2 <- annotate(s, list(sent_token_annotator, word_token_annotator))
+  ## Entity recognition for persons.
+  entity_annotator <- Maxent_Entity_Annotator()
+  entity_annotator
+  annotate(s, entity_annotator, a2)
+  ## Directly:
+  entity_annotator(s, a2)
+  ## And slice ...
+  namedEntities <- s[entity_annotator(s, a2)]
+  #output <- removeWords(string, namedEntities)
+  #return(output)
+  return(namedEntities)
+}
+
+str_c(d$doc[2], collapse = " ")
+
+for(i in 1:10){
+test <- lapply(d$doc[i], str_c, collapse = " ")
+print(removeNamedEntity(test))
+}

### 2017-08-30 malletAnalysisHeatmap.R

@@ -1,0 +1,30 @@
+library('reshape2')
+library('ggplot2')
+library('cowplot')
+
+doc.topics <- mallet.doc.topics(topic.model, smoothed = T, normalized = T)
+republican <- doc.topics[which(d$winner == "Republican"),]
+democratic <- doc.topics[which(d$winner == "Democratic"),]
+republican <- as.tibble(republican)
+democratic <- as.tibble(democratic)
+
+democratic.melted <- melt(as.matrix(democratic))
+names(democratic.melted) <- c("Document", "Topic", "Weight")
+heatmap_democratic <- ggplot(democratic.melted, aes(x = Topic, y = Document, fill = Weight)) + 
+  geom_tile() + 
+  scale_y_reverse() +
+  theme(axis.text.x = element_blank()) +
+  ggtitle("Democratic")
+
+republican.melted <- melt(as.matrix(republican))
+names(republican.melted) <- c("Document", "Topic", "Weight")
+heatmap_republican <- ggplot(republican.melted, aes(x = Topic, y = Document, fill = Weight)) + 
+  geom_tile() + 
+  scale_y_reverse() +
+  theme(axis.text.x = element_blank()) +
+  ggtitle("Republican")
+
+heatmaps_g <- plot_grid(heatmap_democratic, heatmap_republican, nrow = 2)
+heatmaps_g
+
+ggsave(heatmaps_g, file = str_c("./paper/figures/heatmaps_weights.png"), width=5, height=8)

### 2017-08-30 malletPreprocessing.R

@@ -52,6 +52,7 @@ d$doc <- pbsapply(d$doc, iconv, "UTF-8", "UTF-8")
 date_words <- c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
 date_words <- c(date_words, "January","February","March","April","May","June","July","August","September","October","November","December")
 date_words <- c(date_words, "Mon","Tue","Wed","Thu","Fri","Sat","Sun")
+date_words <- c(date_words, "am", "pm")
 date_words <- c(date_words, tolower(date_words))
 d$doc <- pbsapply(d$doc, removeWords, words = date_words)
 
@@ -129,7 +130,6 @@ d$doc <- as.character(pbsapply(1:nrow(d), cleanup))
 
 ### END OF INTERESTING STUFF
 
-
 d$xml <- str_detect(d$doc, "<?xml version=") #note which docs are xml
 d <- filter(d, d$xml==F) #Drop rows that are xml docs
 d <- select(d, -xml) #Drop xml variable
@@ -206,8 +206,19 @@ save(d, file = "./rfiles/d_noduplicates3.Rdata")
 #merge in original file extension
 d <- merge(d, d2, "path", all.x = T, all.y = F)
 
-#remove a few empty documents that ended up ine there at some point
+#remove a few empty documents that ended up in there at some point
 d <- d[is.na(d$ext)==F,]
+
+#save
+save(d, file = "./rfiles/d_backup.Rdata")
+
+#remove city names
+citynames <- unique(d$Name)
+citynames <- c(citynames, tolower(citynames))
+d$doc <- removeWords(d$doc, citynames)
+
+#removing token types that disproportionately occur in one city's corpus
+source('malletPreprocessingCityWords.R')
 
 #save
 save(d, file = "./rfiles/d.Rdata")

### 2017-09-05 functions/city_entropy.R
multiple changes to incorporate cross-city entropy, experimenting with mallet parameters, top words through aggregated topics, etc.

@@ -1,0 +1,37 @@
+#Function to calculate entropy between cities for each topic
+#based on token assignment
+
+city_entropy <- function(doc.topic.matrix, doc.data.frame){
+
+  #Calculate token assignments per city
+  #The function is called rowsum; BUT it provides
+  #"column sums across rows of a numeric matrix-like 
+  #object for each level of a grouping variable."
+  city.tokens <- rowsum(doc.topic.matrix, group = factor(doc.data.frame$Name))
+  city.tokens.prop <- apply(city.tokens, 2, function(X){X/sum(X)})
+  
+  #add just a little bit to a all values that are equal to zero
+  #so that taking their log won't break the entropy algorithm
+  city.tokens.prop[city.tokens.prop==0] <- 0.00000000001
+  
+  #Shannon-Entropy
+  entropy <- function(freqs){
+   -sum(freqs * log2(freqs))
+  }
+  
+  #calculate entropy for each column of the doc-topic matrix
+  return(apply(city.tokens.prop, 2, entropy))
+
+}
+
+#Use:
+#city.entropy(doc.topics, d)
+
+city_entropy_order <- function(city_entropy_vector){
+
+  return(sort.int(city_entropy(doc.topics, d), decreasing = T, index.return = T)$ix)
+  
+}
+
+#Use:
+#city_entropy_order(city.entropy(doc.topics, d))

### 2017-09-05 malletAnalysisPartisanTopWords.R

@@ -1,0 +1,24 @@
+library('xtable')
+
+#Democratic top words
+dem.topic.words <- topic.words[dem.topics,]
+agg.dem.topic.words <- colSums(dem.topic.words)
+names(agg.dem.topic.words) <- vocabulary
+dem.top.words <- sort(agg.dem.topic.words, decreasing = T)[1:30]
+
+#Republican top words
+rep.topic.words <- topic.words[rep.topics,]
+agg.rep.topic.words <- colSums(rep.topic.words)
+names(agg.rep.topic.words) <- vocabulary
+rep.top.words <- sort(agg.rep.topic.words, decreasing = T)[1:30]
+
+#Create table
+word.table <- tibble(dem.word = names(dem.top.words),
+                     dem.tokens = dem.top.words,
+                     rep.word = names(rep.top.words),
+                     rep.tokens = rep.top.words)
+
+#Write Latex table to file
+writeLines(print.xtable(xtable(word.table, digits = 0),
+                        include.rownames = F),
+           "paper/tables/partisanTopWords.tex")

### 2017-09-05 malletAnalysisPartisanTopics.R

@@ -1,11 +1,18 @@
 source('malletTraining.R')
 
+library('tibble')
+library('stringr')
 library('ggplot2')
 library('cowplot')
 source('functions/mallet_helper_functions.R')
 source('functions/topic_order.R')
 source('functions/coherence_order.R')
 source('functions/comparing_proportions.R')
+source('functions/city_entropy.R')
+
+#doc-topic and topic-word matrices
+doc.topics <- mallet.doc.topics(topic.model, smoothed = F, normalized = F)
+topic.words <- mallet.topic.words(topic.model, smoothed = F, normalized = F)
 
 #How many of the topics with the highest differences should be displayed?
 n_topics <- 24
@@ -14,13 +21,11 @@ n_topics <- 24
 limited_topics <- NULL
 important.topics <- topic_order()
 coherent.topics <- coherence_order(d$doc)
-limited_topics <- intersect(important.topics[1:50], coherent.topics[1:50])
+high.entropy.topics <- city_entropy_order(city_entropy(mallet.doc.topics(topic.model, smoothed = F, normalized = F), d))
+limited_topics <- intersect(important.topics[1:50], coherent.topics[1:50], high.entropy.topics[1:50])
+if(n_topics<length(limited_topics))n_topics <- length(limited_topics)
 
 ## FIND THE TOPICS WITH THE HIGHEST PROPORTIONAL DIFFERENCES
-
-#doc-topic and topic-word matrices
-doc.topics <- mallet.doc.topics(topic.model, smoothed = F, normalized = F)
-topic.words <- mallet.topic.words(topic.model, smoothed = F, normalized = F)
 
 #Split document-topic matrix into Republican and Democratic parts
 republican <- doc.topics[which(d$winner == "Republican"),]
@@ -53,8 +58,8 @@ if(is.null(limited_topics)==F){
 }
 topicnumbers <- props$topic[order(props$prop.diff, decreasing = T)][1:n_topics]
 #Get the same number of topics for both parties
-topicnumbers <- props$topic[order(props$prop.diff, decreasing = T)][props$party=="Democratic"][1:(n_topics/2)]
-topicnumbers <- c(topicnumbers,props$topic[order(props$prop.diff, decreasing = T)][props$party=="Republican"][1:(n_topics/2)])
[…]

### 2017-09-08 descriptiveStatisticsPartisan.R
added some basic descriptive statistics of documents by party; because this keeps coming up

@@ -1,0 +1,35 @@
+#setwd("govWebsites")
+library('xtable')
+
+load('rfiles/d.Rdata')
+
+#Number of cities per party
+ncities <- xtabs(~ Name + winner, d)
+ncities[ncities!=0] <- 1
+ncities <- colSums(ncities)
+
+table1 <- ncities
+
+#Number of citizens per party
+#indiana <- subset(indiana, select = c('District', 'POPESTIMATE2015'))
+#d2 <- merge(d, indiana, by.x = 'Name', by.y = 'District', all.x = T)
+#unique(d2$Name[is.na(d2$POPESTIMATE2015)==T])
+
+#Number of documents per party
+ndocs <- colSums(xtabs(~ Name + winner, d))
+
+table1 <- rbind(table1, ndocs)
+
+#Number of tokens per party
+ntokensD <- sum(d$ntokens[d$winner=="Democratic"])
+ntokensR <- sum(d$ntokens[d$winner=="Republican"])
+
+table1 <- rbind(table1, c(ntokensD, ntokensR))
+
+source('malletAnalysisPartisanTopics.R')
+
+#Number of token assignments
+
+
+#Number of topics
+

### 2017-09-20 paper/manuscript.tex
multiple changes to incorporate cross-city entropy, experimenting with mallet parameters, top words through aggregated topics, etc.
added some basic descriptive statistics of documents by party; because this keeps coming up
a few additions to the paper (STM and SVM) + scripts for those + elasticnet

@@
 We record these URLs, as they are required to retrieve the images websites stored in the Wayback Machine (WbM).
+
+$T_{1}+\beta_1$
 
@@
 
+\subsubsection{LDA diagnostics}
+
 Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic.
@@
 
+\subsubsection{Structural topic model}
+An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
+This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
+However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
+Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
+Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
+The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
+Interestingly the same is true for a number of the cities as well.
+The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
+
+\subsubsection{Prediction with SVM}
+An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
+Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
+Here, we rely on SVM, through three different implementations.
+The SciKitLearn package in Python, the e1071 package as well as the mlr package (relying on the kernlab package) in R.
+Predicting based on the document-term matrix (either in its regular form, or as its tf-idf representation), and using five-fold cros-validation, SciKitLearn produces a predictive accuracy of at most 78\%.
+Parameter tuning did not lead to any improvements.
+The e1071 package in R, relying on the top 5000 features ranked through tf-idf fared slightly better, at 82 percent correctly predicted.
+Finally, the mlr/kernlab implementation (as well as the e1071 implementation through mlr) has not worked at all so far, resulting in stack overflow errors (which appears to be due to memory limitations in R).
+
+Another point worth noting is that \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
 %Heatmaps
@@
 
+%stm results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
+This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
+	\label{stm_results}
+	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
+\end{figure}
+
+%Partisan top words
+\input{tables/partisanTopWords.tex}
+
+%Some basic descriptive statistics of documents by party
+\input{tables/descriptiveStatisticsPartisan.tex}
+
 \newpage

### 2017-09-20 elasticNet.R

@@ -1,0 +1,31 @@
+library('quanteda')
+
+#load data
+load(file = "./rfiles/d.Rdata")
+
+#create corpus
+crps <- corpus(d$doc)
+
+#convert to dfm/dtm
+dfmIN <- dfm(crps)
+dtm <- slam::as.simple_triplet_matrix(dfmIN)
+
+as.sparseMatrix <- function(simple_triplet_matrix_sparse) {
+  retval <-  sparseMatrix(i=as.numeric(simple_triplet_matrix_sparse$i),
+                          j=as.numeric(simple_triplet_matrix_sparse$j),
+                          x=as.numeric(as.character(simple_triplet_matrix_sparse$v)),
+                          dims=c(simple_triplet_matrix_sparse$nrow, 
+                                 simple_triplet_matrix_sparse$ncol),
+                          dimnames = dimnames(simple_triplet_matrix_sparse),
+                          giveCsparse = TRUE)
+}
+
+dtm <- as.sparseMatrix(dtm)
+y <- as.numeric(as.factor(d$winner))-1
+
+##
+#use elastic-net in glmnet
+library('glmnet')
+
+glmnetFit <- glmnet(dtm, y, family = "binomial", maxit = 500000)
+summary(glmnetFit)

### 2017-09-23 elasticNet.R
added elastic-net results (about 70% accuracy for in-sample prediction)

@@ -1,4 +1,8 @@
 library('quanteda')
+library('Matrix')
+library('glmnet')
+
+#setwd('govWebsites')
 
 #load data
 load(file = "./rfiles/d.Rdata")
@@ -23,9 +27,23 @@ as.sparseMatrix <- function(simple_triplet_matrix_sparse) {
 dtm <- as.sparseMatrix(dtm)
 y <- as.numeric(as.factor(d$winner))-1
 
-##
 #use elastic-net in glmnet
-library('glmnet')
 
-glmnetFit <- glmnet(dtm, y, family = "binomial", maxit = 500000)
-summary(glmnetFit)
+#fit the model
+#raises a warning, but increasing maxit does not help
+glmnetFit <- glmnet(dtm, y, family = "binomial", maxit = 500000)  
+
+#in-sample prediction
+a = predict(glmnetFit, type = "class", dtm)
+#a = predict(glmnetFit, type = "response", dtm)
+
+#get majority vote on outcome from 45 factors
+a <- apply(a, 2, as.numeric)
+which.more <- function(X){
+  m <- as.numeric(names(table(X))[which.max(table(X))])
+  return(m)
+}
+a <- apply(a, 1, which.more)
+
+#percent correctly predicted
+mean(a==y)

### 2017-09-24 paper/manuscript.tex
added elastic-net results (about 70% accuracy for in-sample prediction)
added implementation of Burts fightin words method through Matts SpeedReader package
added more detail to description of fightin words method and SVM in the paper; also added a bigger table than the plot for fightin words

@@
 Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
-Here, we rely on SVM, through three different implementations.
-The SciKitLearn package in Python, the e1071 package as well as the mlr package (relying on the kernlab package) in R.
-Predicting based on the document-term matrix (either in its regular form, or as its tf-idf representation), and using five-fold cros-validation, SciKitLearn produces a predictive accuracy of at most 78\%.
-Parameter tuning did not lead to any improvements.
-The e1071 package in R, relying on the top 5000 features ranked through tf-idf fared slightly better, at 82 percent correctly predicted.
-Finally, the mlr/kernlab implementation (as well as the e1071 implementation through mlr) has not worked at all so far, resulting in stack overflow errors (which appears to be due to memory limitations in R).
+Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
+However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
+Instead, we ranked the features according to tf-idf and selected the top 5000.
+These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
+Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
+Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
 
-Another point worth noting is that \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
+\subsubsection{Informative Dirichlet model}
+Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}.
+This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
+Figure \ref{fightinwords} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
+For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly.
+Similarly, 'federal' 'funds' also appear among the Democratic top words.
+By contrast Republicans prefer to devote their attentions to purely local, and for the most part, logistic matters.
+'Trees', 'water', 'street' and 'sign' appear on the list of Republican top words, suggesting that these mayors largely focus on city planning.
+
+These top words also show some degree of overlap with those determined by aggregating over topics in LDA.
 
@@
 
-%Partisan top words
+%fightin words results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Top democratic and Republican words, according to the informed Dirichlet model of Monroe et al. (2008).}
+	\label{fightinwords}
+	\includegraphics[width=\linewidth]{figures/fightinWords.png}
+\end{figure}
+
+%Partisan top words - topic model
 \input{tables/partisanTopWords.tex}
+
+%Partisan top words - fightin words
+\input{tables/fightinwords.tex}
+
+%HOW TO DO THIS???
+%\begin{table}
+%	\input{tables/fightinwords.tex}
+%\end{table}
 

### 2017-09-24 fightinWords.R

@@ -30,7 +30,7 @@ fs <- feature_selection(cgt,
                         rows_to_compare = c(4,1), #Democrat first so it gets colored blue
                         method = "informed Dirichlet")
 
-#make the plot
+#make the funnel plot
 #pdf('paper/figures/fightinWords.pdf', width = 8, height = 8) #shitty quality
 ppi <- 300
 png("paper/figures/fightinWords.png", width=8*ppi, height=8*ppi, res=ppi)
@@ -42,3 +42,12 @@ fightin_words_plot(fs,
                    size_terms_by_frequency = F,
                    right_margin = 6)
 dev.off()
+
+#make a table with the top 50 words
+library('xtable')
+zscoretable <- tibble::tibble(DemocraticWord = fs$Democratic_Democratic$term[1:50],
+                              DemocraticScore = fs$Democratic_Democratic$z_scores[1:50],
+                              RepublicanWord = fs$Republican_Republican$term[1:50],
+                              RepublicanScore = fs$Republican_Republican$z_scores[1:50])
+
+writeLines(print.xtable(xtable(zscoretable), include.rownames = F), con = 'paper/tables/fightinwords.tex')

### 2017-10-03 paper/manuscript.tex
added sections to the paper (abstract, introduction, literature overview of papers that rely on website analysis) associated with the new research design

@@
 
-\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
+Websites have become a prominent source of data for automated text analysis in political science.
+However, extant research lacks common standards and often glosses over the details on how such analyses are conducted, exposing itself to potential pitfalls associated with this process and making replication difficult.
+We develop a set of guidelines and procedures to be followed in order to produce valid results.
+In order to develop a valid research design, the appropriate selection of cases and URLs is crucial.
+For the acquisition of website data, we cover several scraping methods and difficulties that can arise in the process.
+Pre-processing is a common step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
+Finally, we cover several methods of analysis and validation appropriate for this kind of data.
+These steps are illustrated through our creation and exploitation of a new and innovative dataset - the websites of local governments in Indiana and Louisiana.
+We show that if our methodology is followed appropriately, an association between mayoral partisanship and the content of their cities' websites becomes visible.
+
+%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
 We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent.
@@
 \section{Introduction}
+
+\subsection{New Research Design}
+The analysis of entire websites has become more prominent recently, especially in the the text-as-data movement.
+We see great promise in this development, especially as it pertains to the study of governmental branches and agencies, which are often resilient to being studied by other methods.
+However, this line of inquiry comes with a set of particular challenges and pitfalls researchers need to be mindful of.
+We offer solutions to these problems at the four stages of such an analysis.
+
+\begin{enumerate}
+	\item Design
+	\begin{enumerate}
+		\item Choosing the sample
+		\item Finding URLs
+		\item list of .gov websites
+		\item Finding supporting data
+	\end{enumerate}
+	\item Scraping
+		\begin{enumerate}
+			\item wget
+			\item headless browser/Selenium
+			\item Beautifulsoup/rvest
+			\item APIs (httr)
+			\item Wayback Machine
+		\end{enumerate}
+	\item Pre-processing
+		\begin{enumerate}
+			\item Determining document filetype
+			\item File conversion
+			\item Conventional preprocessing (lowercase, numbers, punctuation)
+			\item Stemming and lemmatization
+			\item spellchecking
+			\item Dealing with duplicate text \& html documents in particular
+		\end{enumerate}
+	\item Analysis
+		\begin{enumerate}
+			\item LDA
+			\item Other topic models (structural, author, dynamic -- maybe?)
+			\item SVM (+ other machine learning classifiers?)
+			\item Fightin Words
+		\end{enumerate}
+\end{enumerate}
 
@@
 Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.
+
+\subsection*{Website Analysis}
+The literature making use of scraped websites clusters into a number of categories.
+One, and most pertinent to our own endeavors, the e-governance literature which discusses the online presence of governments from a usability and public service point of view.
+For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep{Urban2002,Armstrong2011,Feeney2017}.
+As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
+To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated.
+The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
+Like most e-government studies however, this publication does not make any use of automated text analysis.
+
+Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
+\cite{Lin2011} provide a good example for a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
+The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased.
+Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
+
+Another well-known example fitting into this area of study is the set of studies conducted by King et al.
+\citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere.
+However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.
+
+The websites of politicians and their parties have also fallen under scholarly scrutiny.
+Researchers have found that in order to identify the constituencies, motives and modes of communication of these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+\cite{Druckman2009,Druckman2010} rely on the Mational Journal to find the websites, then hand-coded them.
+\cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, the webservice of the Internet Archive we discussed recently.
+\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
+\cite{Therriault2010} (a working paper) actually portends to use automated text analysis, and also has the most extensive overview of the associated methodology.
+However, the division of the website into sections (home page, topics, issues, details) is done by hand, and the actual analysis is incomplete.
+The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).
+
+Importantly for us, research analyzing and improving the scraping, pre-processing and analysis methods of this literature is scarce.
+\cite{Eschenfelder2002} provide something of an overview of how how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
 
@@
 	\label{stm_results}
-	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
+%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
 \end{figure}

### 2017-10-11 malletAnalysisPartisanTopicsLA.R
more analysis for louisiana

@@ -1,0 +1,101 @@
+source('malletTraining.R')
+
+library('tibble')
+library('stringr')
+library('ggplot2')
+library('cowplot')
+source('functions/mallet_helper_functions.R')
+source('functions/topic_order.R')
+source('functions/coherence_order.R')
+source('functions/comparing_proportions.R')
+source('functions/entropy.R')
+
+#doc-topic and topic-word matrices
+doc.topics <- mallet.doc.topics(topic.model, smoothed = F, normalized = F)
+topic.words <- mallet.topic.words(topic.model, smoothed = F, normalized = F)
+
+#How many of the topics with the highest differences should be displayed?
+n_topics <- 24
+#In order to consider only a restricted set of topics, enter a vector of their indices here
+#Otherwise, set to NULL
+limited_topics <- NULL
+#important.topics <- topic_order()
+#coherent.topics <- coherence_order(d$doc)
+#high.entropy.topics <- city_entropy_order(city_entropy(mallet.doc.topics(topic.model, smoothed = F, normalized = F), d))
+#limited_topics <- intersect(important.topics[1:50], coherent.topics[1:50], high.entropy.topics[1:50])
+#if(n_topics<length(limited_topics))n_topics <- length(limited_topics)
+
+## FIND THE TOPICS WITH THE HIGHEST PROPORTIONAL DIFFERENCES
+
+#Split document-topic matrix into Republican and Democratic parts
+republican <- doc.topics[which(d$winner == "Republican"),]
+democratic <- doc.topics[which(d$winner == "Democratic"),]
+
+#Democratic words per topic, as a proportion of Republican words per topic
+prop.dem <- (colMeans(democratic)/sum(colMeans(democratic)))/(colMeans(republican)/sum(colMeans(republican)))
+#Republican words per topic, as a proportion of Democraticepublican words per topic
+prop.rep <- (colMeans(republican)/sum(colMeans(republican)))/(colMeans(democratic)/sum(colMeans(democratic)))
+#Create an object in which each value is the proportion of the party which has a higher
+#value for this topic
+props <- prop.dem
+props[prop.dem<1] <- prop.rep[prop.dem<1]
+props <- tibble(topic = 1:length(props), prop.diff = props)
+props$party <- NA
+props$party[prop.dem<1] <- "Republican"
+props$party[prop.dem>1] <- "Democratic"
[…]

### 2017-10-17 paper/manuscript_new.tex
different manuscript to list all the talking points for Wednesday; also very minor changes to the SVM stuff (not finished)

--- 2017-09-20 paper/manuscript.tex
@@
 
-\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
-We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent.
-To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots.
-Snapshots of websites before and after transitions of power are acquired through the Wayback Machine.
-We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites.
-We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.
+Websites have become a prominent source of data for automated text analysis in political science.
+However, extant research lacks common standards and often glosses over the details on how such analyses are conducted, exposing itself to potential pitfalls associated with this process and making replication difficult.
+We develop a set of guidelines and procedures to be followed in order to produce valid results.
+In order to develop a valid research design, the appropriate selection of cases and URLs is crucial.
+For the acquisition of website data, we cover several scraping methods and difficulties that can arise in the process.
+Pre-processing is a common step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
+Finally, we cover several methods of analysis and validation appropriate for this kind of data.
+These steps are illustrated through our creation and exploitation of a new and innovative dataset - the websites of local governments in Indiana and Louisiana.
+We show that if our methodology is followed appropriately, an association between mayoral partisanship and the content of their cities' websites becomes visible.
 
@@
 
-\section{Background}
+The analysis of entire websites has become more prominent recently, especially in the the text-as-data movement.
+We see great promise in this development, especially as it pertains to the study of governmental branches and agencies, which are often resilient to being studied by other methods.
+However, this line of inquiry comes with a set of particular challenges and pitfalls researchers need to be mindful of.
+We offer solutions to these problems at the four stages of such an analysis.
 
-\cite{grimmelikhuijsen2010transparency} run an experiment in which citizens are exposed to randomly selected levels of information about local government council minutes.
-They find a negative relationship between the information level and perceptions of competence in the local government.
-This raises an interesting question regarding whether citizens or more likely to participate when they perceive competence or when they perceive incompetence.
+\newpage
+\tableofcontents
+\newpage
+\section{Research Design}
 
-\cite{wang2005evaluating} present a widely cited `model' for evaluating the accessibility of information on government websites.
-This is an important paper with which we should be familiar at a very detailed level as we use archived web content to assess the volume/accessibility of information provided by local governments.
+\subsection{Sample Selection}
 
-\cite{osman2014cobra} is less relevant, but they develop a multi-item measure to predict the level of citizen satisfaction with e-government services.
+Running example: Why did we pick Indiana and Louisiana?
 
-\cite{grimmelikhuijsen2012developing} conduct an enormously relevant study.
-Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study.
-They focus on Dutch municipal websites, and their approach is fairly limited in scope and highly manual (which we can compliment).
-For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''
+\subsection{Finding \& Verifying URLs}
 
-\begin{landscape}
-\begin{table}[htbp]
-	%\caption{}
-	\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-		\hline
-		Names & Year & Journal & Findings & Important? \\ \hline
-		Benedictis-Kessner, Justin De
-		Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
-Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
-		Caughey, Devin
-		Warshaw, Christopher
-		Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
-Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
-& Somewhat \\ \hline
-		Einstein, Katherine Levine
-		Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
-aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
-		Einstein, Katherine Levine
-		Glick, David M.
-& 2015 & Working Paper & Survey of 72 mayors.
-Unlike Republican mayors, roughly half of Democrats seem to agree that cities should aim to reduce inequality.
-Democratic mayors also seem to favor redistribution to accomplish that goal.
-& Somewhat \\ \hline
-		Kiewiet, D Roderick
-		Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
-Spending has thus decreased in general.
-Lack of funds means that there is not much discretion for partisanship.
-& Somewhat \\ \hline
-		Tausanovitch, Chris
-		Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
-Partisan elections do not make cities more or less responsive.
-& Yes \\ \hline
-		Guillamón, Ma Dolores
-		Bastida, Francisco
-		Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
-Conservative parties spend more on police.
-Spending is higher before elections.
-Also contains a useful overview of the literature.
-& Yes \\ \hline
-	\end{tabular}
-	\label{}
-\end{table}
-\end{landscape}
+Running example: Our URLs are partially from the General Services Administration (GSA), and partially from Wikipedia.
+The GSA data can easily downloaded from GitHub, but contains some errors.
+To at least verify which parts of it work, we open each url in an automatized browser, and test whether it leads to a valid website as well as record the URL it redirects to.
+An explanation of this process is provided in section \ref{selenium}.
+Scraping URLs from Wikipedia will be explained in section \ref{htmlparsing}.
 
-\begin{landscape}
-	\begin{table}[htbp]
-		%\caption{}
-		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-			\hline
-			Names & Year & Journal & Findings & Important? \\ \hline
-			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
-			Solé-Ollé, Albert
-			Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
-The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
-Partisanship might also affect housing construction and price growth.
-& Yes \\ \hline
-			Gerber, Elisabeth R.
-			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
-			Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
-Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
-Non-partisan elections favor Republicans/upper class.
-Mixed evidence for whether partisanship of mayor is important for policy.
-& Somewhat \\ \hline
-			Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
-spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
-& Somewhat \\ \hline
-			Ferreira, Fernando
-			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
-			Ansolabehere, Stephen
-			Snyder, James M.
-& 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
-The important finding (for us) is the fact that counties whose government is controlled by the same party as the state government, receive more funding (county's share of state transfers, normalized by county pop.) from the state.
-& Somewhat \\ \hline
-			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
-		\end{tabular}
-		\label{}
-	\end{table}
-\end{landscape}
+\textbf{Current scripts:}
 
-\begin{landscape}
-	\begin{table}[htbp]
-		%\caption{}
-		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-			\hline
-			Names & Year & Journal & Findings & Important? \\ \hline
-			Armstrong, Cory L.
-& 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
-Manual content analysis (undergrads told to look around for 15 minutes).
-School board websites, more professional websites, and websites in Republican-dominated counties are found to be more transparent.
-& Yes \\ \hline
-			Cegarra-Navarro, Juan
-			Pachón, José
-			Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
-Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
-More sophisticated websites are correlated with greater civic engagement and greater use of e-government functions.
-& Yes \\ \hline
-			Dolson, Jordan
-			Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
-Three categories: e-content (city information on website), e-participation, social media use.
-Tables on page 15 show frequencies of these categories across sites, and might be useful to inform our topics.
-Larger cities have better websites.
-Population growth and immigration are also tested, but the findings are somewhat inconclusive.
-& Yes \\ \hline
-			Feeney, Mary K.
-			Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
-city websites at two points in time (2010-2014).
-Count model of website features regarding information, e-services, utilities, transparency and civic engagement.
-Having a larger population leads to more features.
-Relying on a website contractor leads to more information and transparency.
-The authors say that mayor-councils are negatively correlated with website sophistication, but their regression tables state the opposite.
-& Yes \\ \hline
-			Kaylor, Charles
-			Deshazo, Randy
-			Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
-Table 1 lists a number of possible ways this manifests, could be useful for our theory.
-& Somewhat \\ \hline
-			Ansolabehere, Stephen
-			Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
-Is website content correlated with city characteristics?
-Not particularly systematic, and the findings are inconclusive.
-& Somewhat \\ \hline
-			Jeffres, Leo W.
-			Lin, Carolyn A.
-& 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
-Features include information about city, opportunities for citizen feedback, galleries of photos, links, etc.
-Purely descriptive analysis, doesn't contain anything that isn't covered in any of the other aricles.
-& No \\ \hline
-		\end{tabular}
-		\label{}
-	\end{table}
-\end{landscape}
+%Wikipedia is also a good source for URLs, because it has lists of cities, most of which have
 
-There doesn't seem to be much literature on transitions of party control, if anything, that question is mostly phrased with regard to political representation.
-However, if we want to tie our paper to a larger theory, we could go with dynamic representation.
-Under dynamic representation, policy-makers are responsive to trends in citizens opinions, which mainly manifest/become apparent through election results, especially when incumbents are voted out of office.
-This fits our topic quite well.
-Also, of the few papers that do exist on the effects of partisan transitions, virtually all use regression discontinuity designs.
+\subsection{Supporting Data}
+In our case, this would be the Census and election data. However, this is incredibly case-dependent, so I am not sure whether this really needs its own section.
 
-\textbf{Why does the content of city websites matter?} According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
-Official city websites allow mayors to do all three.
-Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate.
-In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents.
-Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
-City websites present an opportunity for local officials to brandish these accomplishments.
-Finally, they also give mayors a platform from which they can advertise their political beliefs.
-On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
-As noted by \cite{Einstein2015a}, there are stark differences in the spending preferences of Democratic and Republican mayors.
-City websites can then be used to communicate the stance of a mayor on social or economic programs.
-Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
+\textbf{Current scripts}: cityCoordinates.R (scrapes city coordinates from Wikipedia), combineURLs.R (combines Census with GSA data)
 
-In addition to the use of city websites for the politicians that control them, variance in content also matters  with regard to the people who visit them.
-Local residents likely rely on city websites to get news about events, hot-button political issues specific to their city, contact city officials or find out addresses or opening hours of city institutions.
-Visitors use city websites to look up local attractions, which are often described in great detail.
-Similarly, prospective residents looking to move, might rely on city websites to inform their decision on whether to relocate there.
-An inviting website emphasizing the city's receptiveness to new residents might make a real difference here.
-Finally, city websites frequently feature sections on business, but there is a lot of variance in this area: Some emphasize economic development, properties, or transportation, whereas others focus on undeveloped land and other business opportunities.
-Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.
+\section{Scraping Websites}
+\subsection{wget}
 
-\section{Data}
-The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
-This list is updated once per month - we rely on the version released on January 16, 2017.
-The data from the GSA contains the following variables: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV').
-Two, the type of government entity to which the domain is registered, such as city, county, federal agency, etc.
-Three, for federal agencies, the name is specfied.
-Finally, the city in which the domain is registered, is noted.
+wget arguments we are using, and thus might be worth discussing:
 
-Here, we focus only on cities.
-As a first step, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver) to test whether all of the city websites actually work.
-Of the 2425 domains listed by the GSA as cities, 292 are not accessible.
-Furthermore, the .gov domain, as registered at the GSA, is frequently not the website a city actually uses.
-In many cases, these sites redirect to another address, sometimes not a .gov domain (in this case, we simply use this domain).
-We record these URLs, as they are required to retrieve the images websites stored in the Wayback Machine (WbM).
+-r, --recursive, specify recursive download
 
-$T_{1}+\beta_1$
+-N, --timestamping, don't re-retrieve files unless newer than local; alternatively:
 
-In order to provide an overview of our coverage (as not all cities, towns and villages use .gov addresses), we merge this list with U.S.
-Census data\footnote{http://www2.census.gov/programs-surveys/popest/datasets/2010-2015/cities/totals/sub-est2015\_all.csv}.
-Here, several limitations in the GSA data need to be accounted for: One, even though the GSA nominally separates websites of cities and counties, some of the domains categorized as cities actually belong to counties.
-The same is true for townships and boroughs.
-Ergo, we eliminate all websites belonging to these three types of entities by hand.
-Furthermore, the city name, as given by the GSA, refers to the city in which the domain is registered, which is not necessarily equivalent to the city the website serves.
-In many cases, a website of a larger city may be registered to one of its subdivisions (for example, the website of New York is registered to Brooklyn), or vice versa (for example, the website of Homecroftin, a small town within Indianapolis, is registered to the city as a whole).
-Consequently we fix mismatches between websites and cities manually.
-Finally, a number of cities are simply misspelled, which we also correct by hand.
+-nc, --no-clobber, skip downloads that would download to existing files (overwriting them)
 
-After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
+-P,  --directory-prefix=PREFIX, save files to PREFIX/..
 
-These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
+-i, --input-file=FILE, download URLs found in local or external FILE
 
-\begin{figure}[!ht]
-	\centering
-	\caption{Percentage of state population covered.}
-	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
-\end{figure}
+robots=off, we are NOT doing this currently, but I feel we should at least explain it
 
-We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
-To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
-We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
+Functions: Do we write a wrapper for wget here?
 
-<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
-Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
+\textbf{Current scripts}: wgetINLA.R
 
-\input{tables/filetypes.tex}
+\subsection{Parsing HTML with rvest/beautifulsoup} \label{htmlparsing}
 
-\begin{landscape}
-\input{tables/filenumbers.tex}
-\end{landscape}
+Running example: scraping city URLs from Wikipedia.
 
-For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results. Consequently we restricted our corpus to cities with at least 3 documents.
+\subsection{Browser Automation with Selenium} \label{selenium}
 
-\section{Preprocessing}
+Running example: checking whether URLs from Wikipedia/, are valid, and/or whether they redirect somewhere else.
 
-The documents are read in line by line, converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
-At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
-"You are here", "Home", "Directory" etc.) in html documents, or commonly used forms or phrases in pdfs, doc and docx files.
-This is an issue, because it clusters documents around the cities from which they originate in a way that has nothing to do with their actual content.
-In other words, the signal would be drowned out by the noise.
-Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
-We count how many times each line is duplicated for that city.
-We remove any line occuring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times, or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
-Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
-Furthermore, some documents contain gibberish, often as a result of faulty or impartial OCR.
-To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the hunspell R package, to remove all non-English words.
-However, hunspell does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
-Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the english alphabet.
-Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to total number of tokens is less than 0.15.
-Furthermore, hunspell does not spellcheck individual characters, so we remove all individual characters appearing as tokens except for "i" and "a".
-Since these pre-processing steps reduce documents which are largely unsuitable to only a few words of texts that don't make much sense, we also remove all remaining documents containing less than 50 tokens.
+Also very useful for scraping websites that have some kind of scraping protection (we don't do this, but the reader might want to).
 
-\subsection{Indiana City Websites}
+Functions: Note sure. There is an R implementation for selenium, but it is ridiculously difficult to install and still clearly inferior to the Python version.
 
-It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
+\textbf{Current scripts}: govWebsitesVerification.py
 
-\begin{enumerate}
+\subsection{The Wayback Machine and other APIs}
 
-\item For what percentage and number of IN cities can we find data from the WBM?
-\item For how many election cycles can we find political leadership data for these matched cities?
-\item In what number and percentage of cities is the local leadership majority Republican? 
-\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
+This is not part of our running example.
+However, other people might still be able to use the Wayback Machine for their research designs, so we should at least describe it, especially now that we know its downsides.
 
-\end{enumerate}
+To provide an example, we could do what we planned to do, but just for one large city, which has been scraped enough times by the WBM that it would be no problem.
+San Diego is currently the largest city with a Republican mayor, who got elected in 2014 (preceded by a Democrat), and there are enough snapshots around this time, so that would be one option.
+This would allow us to demonstrate how to use an API, which is possibly relevant to a lot of people (but then again, maybe not 100\% relevant since we are focusing on scraping websites).
 
-\begin{enumerate}
+The implementation of this whole part would be a bit of a problem, since we are currently using a Ruby package, and from what I can tell looking at its code, I am not sure if I have the engineering skills to translate it to R.
 
-	\item 30 cities, with a combined population of 1,180,435.
-However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
-	\item 2015, 2011, 2007, 2003.
-	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
-	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
+\section{Pre-processing}
+\subsection{Determining document filetype}
+Determining the format of a file is usually as simple as looking at its file ending.
+However, not all files scraped from websites actually have endings.
+Simply discarding these files would lead to a large and completely unnecessary reduction in the size of the corpus.
+Similarly, xml files are sometimes labeled as html, which, if parsed as such, will lead to the introduction of a set of words into the corpus that have absolutely nothing to do with a website's content.
+Consequently it is imperative to determine a document's type by reading in its first couple of lines and extracting the tag revealing its type.
+In our running example, this leads to an increase of the corpus by X\% for Indiana and Y\% for Louisiana.
 
-\end{enumerate}
+Function to include in the package: Read in a document, do a grep on its first few lines for either ``doctype HTML'' or ''PDF''; then output the correct filetype, and if desired, change the file.
+Currently done in 'renameHTMLs.R'.
 
-% latex table generated in R 3.3.3 by xtable 1.8-2 package
-% Wed Mar 22 11:32:43 2017
-%\begin{table}[ht]
-%	\centering
-%	\begin{tabular}{lrrlrrl}
-%		\hline
-%		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
-%		\hline
-%		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
-%		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
-%		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
-%		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
-%		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
-%		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
-%		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
-%		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
-%		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
-%		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
-%		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
-%		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
-%		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
-%		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
-%		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
-%		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
-%		\hline
-%	\end{tabular}
-%	\caption{} 
-%\end{table}
+Note: I've had some nasty problems with text not being encoded properly, or at least consistently.
+The readtext\footnote{\url{http://cdn.rawgit.com/kbenoit/readtext/master/inst/doc/readtext_vignette.html\#read-files-with-different-encodings}} package seems to have a way for dealing with that, which I haven't looked into so far, but considering the new research design, this might be worth it.
 
-\subsection{Research Design}
+\textbf{Current scripts}: detectOriginalExtensions.R, filetype\_before\_txt.R
 
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{llr}
-		\hline
-		Variable & Unit & Source \\
-		\hline
-		Population size & 1000 people & Census \\
-		Population growth last 5 years & Percent & Census \\
-		Type of economy (agriculture/industry/services) & ? & Census \\
-		Economic performance (GDP?) & \$ & Census \\
-		Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-		Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-		Change of party control & 0/1 & in.gov/sos/elections/ \\
-		Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
-		Unemployment rate & Percent & Census \\
-		Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
-		\hline
-	\end{tabular}
-	\caption{List of covariates} 
-\end{table}
+\subsection{File conversion}
+File conversion can either be done with various Unix packages, or Kenneth Benoit's readtext package.
+Currently, we are doing this with the former, using antiword, docx2txt, html2text and pdftotext (currently done with the shell script ``websites/batchconversion.sh'', which in turns calls four other shell scripts).
+If we are going to make an R package for our paper, it might be easier to do it with readtext instead.
+From what I can tell, readtext uses htmlTreeParse (XML package), pdftools (R package; but they previously used xpdf, which also relies on the same pdftotext we are using), antiword (which we are using too, but they are using the R wrapper for it) and xmlTreeParse for docx (XML package).
+I did try the readtext package at one point, and it lead to fairly comparable results, but I will need to do more testing if we do switch to it to make sure it doesn't mess anything up later.
 
-\begin{enumerate}
-\item Corpus:
-\begin{enumerate}
-\item Last snapshots before the election (November 3, 2015 in Indiana; tbd. in Louisiana (probably February))
-\item First snapshot that is at least 2 months after the new government's inauguration (which is in January for Indiana, May for Louisiana)
-\end{enumerate}
-\item Preprocessing:
-\begin{enumerate}
-\item restrict corpus to:
-\begin{enumerate}
-\item documents belonging to cities in which a change of power occurred
-\item documents that were added, deleted or changed between the two snapshots
-\end{enumerate}
-\item words to lowercase
-\item remove punctuation
-\item stemming (Porter stemming algorithm?)
-\item Remove stop words (regular list of stop words is enough, since we use an asymmetric prior)
-\end{enumerate}
-\item Apply Grimmer's expressed agenda model to the corpus
-\begin{enumerate}
-\item Asymmetric prior
-\item Each document can have only one topic (in contrast to the author-topic model)
-\item Cities $i = 1,..., n = 15$
-\item Topic $k(k = 1,..., K )$
-\item Documents $j(j = 1,...,D_i)$ from city i
-\item Party covariate in the prior, where the deleted and unmodified documents are coded as from the first, and the added and modified documents from the second party
-\end{enumerate}
-\item Results
-\begin{enumerate}
-\item Label topics using Grimmer's automatic cluster labeling method, based on most commonly used words in documents belonging to topic
-\item Evaluate topics
-\end{enumerate}
-\end{enumerate}
+Functions: wrapper for readtext
 
-Validation:
+\textbf{Current scripts}: malletPreprocessing.R
 
-\begin{itemize}
-\item Do the above for cities in which no change of power occurred.
-\item Check whether there is higher than average turnover around the new year by comparing changes to non-election years (and also Louisiana, where elections are later).
-\item Check how long documents stay on websites on average. Use websites with a lot of snapshots for this (these exist for both small and large cities).
-\end{itemize}
+\subsection{Conventional preprocessing (lowercase, numbers, punctuation, stopwords)} \label{preprocessing_conventional}
 
-Problem with using this model: Grimmer's expressed agenda model uses Senators as the actors.
-Senators is also who he is substantively interested in.
-For us, the equivalent to Senators is cities.
-However, we care about parties, not cities.
+\textbf{Package}: Wrapper for quanteda and/or tm package
 
-\subsection{Survival model}
-The existence of individual documents on municipal government websites can be though of as a survival process.
-No document stays on a website forever, and it appears to be a reasonable assumption that as documents get older and thus less relevant, they get replaced.
-The factors determining the steepness of the survival curve are the topic - fire safety regulations likely stay up longer than a bulletin on the annual spring banquet - and the change of party control after an election.
+\textbf{Current scripts}: All of the preprocessing from section \ref{preprocessing_conventional} to \ref{preprocessing_duplicates} is currently done in malletPreprocessing.R (which doesn't require mallet anymore, so it's a bit of a misnomer).
 
-\begin{quote}
-\textit{H1}: The older a document, the more likely it is to be removed.
-\end{quote}
+\subsection{Stemming and/or lemmatization}
+We're currently not doing this and I am wondering if we will get spanked for it by reviewers.
 
-$S(t)$ has a downward slope. Admittedly, this is almost impossible not to be true. Also, test proportional, rising and falling hazard models.
+\subsection{Spellchecking}
 
-\begin{quote}
-\textit{H2}: Documents pertaining to administrative matters are less likely to be removed.
-\end{quote}
+\textbf{Current scripts}: malletPreprocessing.R
 
-Introduce a categorical variable for the top 10(?) topics. A negative coefficient for administrative topics would support this hypothesis.
+\subsection{Dealing with duplicate text \& documents \& html documents in particular} \label{preprocessing_duplicates}
 
-\begin{quote}
-\textit{H3}: Documents introduced by the opposing party are more likely to be removed.
-\end{quote}
+\textbf{Current scripts}: malletPreprocessing.R
 
-Introduce two variables into the survival model: One variable indicating which party has introduced a document, and a time-varying variable describing which party is currently in government.
-The hypothesis is tested through an interaction term between the two.
+\section{Analysis}
+\subsection{LDA}
 
-\begin{quote}
-\textit{H4a}: Democrats are more likely to remove documents with topics pertaining to private enterprise, private schools.
-\end{quote}
+Diagnostics: Topic coherence, optimal number of topics according to Arun et al. (2010).
 
-Interaction term between party in power and categorical topic variable.
+\textbf{Current scripts}: exampleDocuments.R
 
-\begin{quote}
-\textit{H4b}: Republicans are more likely to remove documents with topics pertaining to social justice, equality, taxes, public schools, etc.
-\end{quote}
+\subsection{Other topic models}
+STM, could also mention author-topic and dynamic topic model.
 
-Interaction term between party in power and categorical topic variable.
+\subsection{Machine Learning Classifiers (SVM)}
+Phil Schrodt and Glenn Palmer (+2 other people) wrote a whole paper on why SVM is good for text data, we should cite this here.
 
-\begin{quote}
-\textit{H5}: In line with their commitment to small government, Republicans are more likely than Democrats to remove documents.
-\end{quote}
+We can also mention l1/l2 penalty / elasticnet here.
 
-Party in power variable.\\
+Since the scikitlearn implementations of SVM and elasticnet seem much better than the ones available for R, what do we do here, package-wise?
 
-This model will take up a lot of degrees of freedom. The rarity of snapshots for some cities might be a problem. Documents being changed and being removed can be modeled as competing risks.
+\textbf{Current scripts}: svmSKLN.ipynb (Indiana), svmSKLNLA.ipynb (Louisiana), elasticNet.R (Indiana)
 
-\begin{equation} 
-\label{eq1}
-\begin{split}
-Y & = \text{Party that introduced the document} \\
- & + \text{Party that is currently in power} \\
- & + \text{Topic 1, topic 2, ..., topic k} \\
- & + \text{Party that is currently in power} \times \text{Topic 1, topic 2, ..., topic k} \\
- & + \text{Days since start of mayoral term (control)}
-\end{split}
-\end{equation}
+\subsection{Fightin' Words}
+Make a table comparing the top 50 words for Democrats/Republicans produced by LDA, SVM and Fightin' Words. Probably goes in the appendix.
 
-\subsection{Topic modeling}
-Note: this chapter is mostly a wordy and less coherent version of the above.
+\textbf{Package}: Wrapper for Matt's speedReader package.
 
-We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas.
-Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order.
-Documents uploaded to city websites are expected to be a reflection of these preferences.
+\textbf{Current scripts}: fightinWords.R, fightinWordsLA.R
 
-The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model.
-However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics.
-There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.
-
-The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents.
-Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates.
-In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards).
-Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website.
-Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.
-Further demographic as well as economic data might also be useful to differentiate cities from one another.
-If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.
-
-The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences.
-Unfortunately, we have two types of 'authors' - cities, and parties.
-Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author.
-This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents.
-(Note: In the papers on author-topic models, the intention is often to analyze scientific articles.
-These articles are often co-authored.
-Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)
-
-The critical element in this analysis is to accurately attribute authorship of documents to either party.
-Despite possible changes to websites due to a leadership transition, large parts of the content carry over.
-This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
-But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
-{\em  This is a very important point for municipal websites.
-We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added.
-}
-
-Labeling newly added documents after a change of power is quite simple.
-As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption.
-However, we could, and probably should test how long documents tend to stay on a city website.
-Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient.
-If we want to be really fancy about it, we could create a duration model, with document topics as features.
-This would allow us to measure whether some documents tend to remain longer based on their topic (i.e.
-fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.
-
-If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words.
-After that, we run the actual model.
-This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface.
-It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins.
-'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website.
-Hence, these websites should be filled with purely administrative content.
-
-The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e.
-the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.
-
-Another intervening factor is that for cities in Indiana, mayoral terms begin in January.
-Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year.
-Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity.
-We can test for this by comparing election years to non-election years.
-Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.
-
-Furthermore, if we only investigate cities in which control of government changes from one party to another, we may overestimate its effect.
-Not only does a transition in party control occur, but the person in charge also changes.
-Parties are fairly homogeneous, so that two mayors from the same party may have very different policy preferences and managerial styles.
-To remedy this problem, we [could] utilize matching, pairing our cases with similar cities in which the incumbent does not run for re-election, but party control stays the same nevertheless.
-
-%Justicifcation for Arun 2010 topic number measure
-In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}.
-In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix.
-We find 200 topics to be the best value (see figure \ref{ldatuning}).
-
-%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
-This way, we could identify directly which issues are considered to be the most divisive.
-
-%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
-
-%Traditional author models that rely on lexical or syntactic differences may also be of use.
-Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles.
-However, it seems likely that personal rather than partisan authorship is playing an even larger role here.
-
-%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
-As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
-Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
-In a way, this captures the data-generating process more closely.
-
-%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
-One assumes that multiple authors write one document.
-This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
-This is not as good of a fit for city governments however.
-Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
-For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+
-
-%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
-If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
-The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
-Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.
-
-\begin{figure}[!ht]
-	\centering
-	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
-	\label{snapshots}
-	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
-\end{figure}
-
-%\begin{figure}[!ht]
-%	\centering
-	%\caption{Population coverage}
-%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
-%\end{figure}
-
-%\begin{figure}[!ht]
-%	\centering
-	%\caption{Population coverage}
-%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
-%\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
-\end{figure}
-
-%topicweights density
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
-	\label{doctopics_density}
-	\includegraphics[width=\linewidth]{figures/doctopics_density.pdf}
-\end{figure}
-
-\subsubsection{LDA diagnostics}
-
-Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic.
-Distributions with lower peaks near zero and flatter bodies indicate a topic that is present to varying degrees in multiple documents.
-This shape appears to be more common in documents from Republican cities.
-By contrast, a distribution with a high peak near zero and a very long tail is indicative of a topic that only appears in one specific document.
-This appears to be more common for documents in Democratic cities.
-The substantive conclusion then is that Democrats appear to be more prone to dedicating individual documents to one specific purpose, whereas Republicans produce general-purpose documents more often.
-
-%topicweights density
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
-	\label{topicweights_density}
-	\includegraphics[width=\linewidth]{figures/topicweights_density.pdf}
-\end{figure}
-
-An alternative way to consider topic weights is to aggregate them across documents, in this case through their median or mean.
-Figure \ref{topicweights_density} shows this distribution of topic weights across topics.
-Most topics have a very low weight - meaning that they do not appear in a lot of documents.
-When aggregating across documents via the mean, this effect is more pronounced for Republicans, suggesting that most topics do not feature frequently (or even at all) in their documents.
-Democrats on the other hand appear to have a wider spectrum of topics from which they chose - supporting the hypothesis of Democrats as a 'big tent' party.
-However, this effect is reversed when using the median instead of the mean to aggregate across documents.
-Now, the the distribution has a higher peak and lower tail for Democrats.
-The cause for this stark divergence appears to lie in the fact the mean and median differ enormously - for the range displayed here, the mean is about a hundred times greater.
-Evidently, extremely large weights (i.e.
-some documents fitting specific topics perfectly) distort the picture.
-The median document is a better representation of the corpus as a whole, but the results do not fit our hypothesis.
-Their are however more consistent with figure \ref{topicweights_density}.
-
-Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us.
-To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}.
-For the most part, differences are small.
-For a few topics however, a contrasts emerges.
-
-%size of the differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{diffsize}
-	\includegraphics[width=\linewidth]{figures/diffsize.pdf}
-\end{figure}
-
-Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences.
-Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged.
-For the most part however, these topics focus on administrative matters.
-
-%word topic probabilities for topics with big differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{plotWTP_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs.pdf}
-\end{figure}
-
-To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences.
-It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.
-
-%word topic probabilities for topics with big differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{doctopics_density_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs.pdf}
-\end{figure}
-
-To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps.
-Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents.
-Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else.
-One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.
-
-\subsubsection{Structural topic model}
-An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
-This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
-However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
-Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
-Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
-The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
-Interestingly the same is true for a number of the cities as well.
-The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
-
-\subsubsection{Prediction with SVM}
-An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
-Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
-Here, we rely on SVM, through three different implementations.
-The SciKitLearn package in Python, the e1071 package as well as the mlr package (relying on the kernlab package) in R.
-Predicting based on the document-term matrix (either in its regular form, or as its tf-idf representation), and using five-fold cros-validation, SciKitLearn produces a predictive accuracy of at most 78\%.
-Parameter tuning did not lead to any improvements.
-The e1071 package in R, relying on the top 5000 features ranked through tf-idf fared slightly better, at 82 percent correctly predicted.
-Finally, the mlr/kernlab implementation (as well as the e1071 implementation through mlr) has not worked at all so far, resulting in stack overflow errors (which appears to be due to memory limitations in R).
-
-Another point worth noting is that \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-%Heatmaps
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{heatmaps_weights}
-	\includegraphics[width=\linewidth]{figures/heatmaps_weights.png}
-\end{figure}
-
-%Number of topics vs. tophic coherence
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
-	\label{numtopics_coherence}
-	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
-\end{figure}
-
-%Indiana map
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Cities in the corpus, by partisanship of mayor.}
-	\label{indiana_map}
-	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
-\end{figure}
-
-%partisan topics
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{The most partisan topics.
-The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
-	\label{partisan_topics}
-	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
-\end{figure}
-
-%ldatuning
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{The optimal number of topics for our corpus.
-The measures of Griffths 2004 and Cao 2009 indicate the best number of topics at their minimum, whereas the measure of Arun 2010 points to the best value at its maximum.}
-	\label{ldatuning}
-	\includegraphics[height=0.75\textheight]{figures/topicnumber_ldatuning.pdf}
-\end{figure}
-
-%stm results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
-This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
-	\label{stm_results}
-	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-\end{figure}
-
-%Partisan top words
-\input{tables/partisanTopWords.tex}
-
-%Some basic descriptive statistics of documents by party
-\input{tables/descriptiveStatisticsPartisan.tex}
+\subsection{Non-bag of words models}
+We're only using bag of words models, so do we focus only on them in this paper?
+Either way, we should at least point out that this would change some parts of these procedures, especially during preprocessing.
 
@@
 %\bibliographystyle{plainnat}
-\bibliography{ref}
+%\bibliography{ref}
 

### 2017-10-18 paper/manuscript_new.tex
small update to new research design

@@
 
-\textbf{Current scripts:}
+\textbf{Current scripts:} scrapeLousianaWebsites.R, scrapeIndianaWebsites.R (gets URls from Wikipedia), Indiana.R, Louisiana.R (combine Wikipedia and GSA URLs)
 
@@
 
-\textbf{Current scripts}: cityCoordinates.R (scrapes city coordinates from Wikipedia), combineURLs.R (combines Census with GSA data)
+\textbf{Current scripts}: cityCoordinates.R (scrapes city coordinates from Wikipedia), mapIndiana.R, combineURLs.R (combines Census with GSA data)
 
@@
 
+\textbf{Current scripts}: internetarchive\_webarchive.R
+
 \section{Pre-processing}
@@
 
-\textbf{Current scripts}: All of the preprocessing from section \ref{preprocessing_conventional} to \ref{preprocessing_duplicates} is currently done in malletPreprocessing.R (which doesn't require mallet anymore, so it's a bit of a misnomer).
+\textbf{Current scripts}: All of the preprocessing from section \ref{preprocessing_conventional} to \ref{preprocessing_duplicates} is currently done in malletPreprocessing.R and malletPreprocessingLA.R (which doesn't require mallet anymore, so it's a bit of a misnomer).
 
@@
 
-\textbf{Current scripts}: malletPreprocessing.R
+\textbf{Current scripts}: malletPreprocessing.R, malletPreprocessingLA.R, hunspellParallel.R
 
@@
 
-\textbf{Current scripts}: malletPreprocessing.R
+\textbf{Current scripts}: malletPreprocessing.R, malletPreprocessingLA.R
 
@@
 
-\textbf{Current scripts}: exampleDocuments.R
+\textbf{Current scripts}: exampleDocuments.R, topicCoherence.R, topicCoherenceNew.R, topicCoherenceTop10Topics.R, ldatuning.R (optimal number of topics), malletAnalysis.R, malletAnalysisDocumentEntropy.R, malletAnalysisHeatmap.R, malletAnalysisLA.R, malletAnalysisPartisanTopWords.R, malletAnalysisPartisanTopWordsLA.R, malletAnalysisPartisanTopics.R, malletAnalysisPartisanTopicsLA.R, malletTestParameters.R, malletTopWords.R, malletTraining.R
 
@@
 STM, could also mention author-topic and dynamic topic model.
+
+\textbf{Current scripts}: stmAnalysis.R
 
@@
 
-\textbf{Current scripts}: svmSKLN.ipynb (Indiana), svmSKLNLA.ipynb (Louisiana), elasticNet.R (Indiana)
+\textbf{Current scripts}: svmSKLN.ipynb (Indiana), svmSKLNLA.ipynb (Louisiana), elasticNet.R (Indiana), elasticSKLN.ipynb (Indiana), predictPartisanDocuments.R, predictPartisanDocumentsMLR.R
 

### 2017-10-18 paper/manuscript.tex
forgot to actually add the LA plots and tables to the manuscript

@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words, according to the informed Dirichlet model of Monroe et al. (2008).}
+	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008).}
 	\label{fightinwords}
 	\includegraphics[width=\linewidth]{figures/fightinWords.png}
+\end{figure}
+
+%fightin words results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008).}
+	\label{fightinwordsLA}
+	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
 \end{figure}
@@
 \input{tables/fightinwords.tex}
+
+%Partisan top words - topic model
+\input{tables/partisanTopWordsLA.tex}
+
+%Partisan top words - fightin words
+\input{tables/fightinwordsLA.tex}
 

### 2017-10-27 paper/tables/descriptiveStatisticsPartisanIN.tex

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Fri Oct 20 13:41:38 2017
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Democratic & Republican \\ 
  \hline
Cities & 15 & 17 \\ 
  Documents & 10257 & 5859 \\ 
  Tokens & 6101752 & 2310072 \\ 
  Token assignments & 6006202 & 2259362 \\ 
  Topics & 103 & 97 \\ 
   \hline
\end{tabular}
\caption{Descriptive statistics for Indiana. ``Tokens'' describes the number
             of words in each party's documents, ``token assignments'' the tokens assigned
             to each party in the topic model depending on the ratio of Democratic to Republican 
             tokens in it (both weighted by the total number of tokens per party).} 
\label{tabDescriptiveIN}
\end{table}

### 2017-10-29 stmIN.R
credible intervals for stm results

@@ -33,6 +33,9 @@ prep <- estimateEffect(1:numtopics ~ winner, stmFit,
                        meta = out$meta, uncertainty = "Global")
 
 #save the results, since training takes some time
+#the results are so large, we only retain the
+#objects necessary for the rest of the analysis
+rm(list = ls()[!ls()%in% c("stmFit", "prep", "out", "numtopics")])
 save.image('rfiles/stmSessionIN_Party.RData')
 load('rfiles/stmSessionIN_Party.RData')
 
@@ -99,3 +102,118 @@ writeLines(xt,
 #  labs(x = "Topic", y = "Variable") +
 #  labs(fill='p-value')
 #ggsave("paper/figures/stm_results.pdf", width = 8, height = 6)
+
+
+
+#Credible interval
+
+#1. Take 1000 draws from the posterior
+#2. Decide on a level of confidence, here 1%
+#3. For each topic, from the 1000 estimated coefficients, take the ones
+## lying between its 0.005 and .995 quantile
+#4. If this range of values does not include 0, it the coefficient is statistically significant
+#5. Take the mean from these values to get the estimated coefficient?
+
+sims <- 1000
+
+#re-estimate the effects, this time do 1000 draws from the posterior
+prep <- estimateEffect(formula = 1:numtopics ~ winner, 
+                       stmobj = stmFit,
+                       meta = out$meta, 
+                       uncertainty = "Global",
+                       nsims = sims)
+
+#make a dataframe to store the results in
+df <- data.frame(coef = rep(0, numtopics), sig = rep(FALSE, numtopics),
+                 lower = rep(0, numtopics), upper = rep(0, numtopics),
+                 topic = 1:numtopics)
+
+conf_level <- 1 #in percent
+conf_level <- conf_level/100 #as a fraction
+conf_level <- conf_level/2 #two-sided
+
+conf_lower <- 0 + conf_level
+conf_upper <- 1 - conf_level
+
+for(j in 1:numtopics){
+  
+  coefs <- list()
+  
+  for(i in 1:sims){
+    coefs[[i]] <- prep$parameters[[j]][[i]]$est[2]
+  }
+  
+  coefs <- do.call(c, coefs)
+  coefs <- quantile(coefs, c(conf_lower, conf_upper))
+  
+  df$lower[j] <- coefs[1]
+  df$upper[j] <- coefs[2]
+  df$sig[j] <- all(coefs>0) | all(coefs<0)
[…]

### 2017-10-29 stmLA.R

@@ -30,9 +30,11 @@ stmFit <- stm(documents = out$documents, vocab = out$vocab,
 
 #Estimate effects from the model outputs
 prep <- estimateEffect(1:numtopics ~ winner, stmFit,
-                       meta = out$meta, uncertainty = "Global")
+                       meta = out$meta, uncertainty = "Global",
+                       nsims = 500)
 
 #save the results, since training takes some time
+rm(list = ls()[!ls()%in% c("stmFit", "prep", "out", "numtopics")])
 save.image('rfiles/stmSessionLA_Party.RData')
 load('rfiles/stmSessionLA_Party.RData')
 
@@ -100,3 +102,117 @@ writeLines(xt,
 #  labs(x = "Topic", y = "Variable") +
 #  labs(fill='p-value')
 #ggsave("paper/figures/stm_results.pdf", width = 8, height = 6)
+
+
+#Credible interval
+
+#1. Take 1000 draws from the posterior
+#2. Decide on a level of confidence, here 1%
+#3. For each topic, from the 1000 estimated coefficients, take the ones
+## lying between its 0.005 and .995 quantile
+#4. If this range of values does not include 0, it the coefficient is statistically significant
+#5. Take the mean from these values to get the estimated coefficient?
+
+sims <- 1000
+
+#re-estimate the effects, this time do 1000 draws from the posterior
+prep <- estimateEffect(formula = 1:numtopics ~ winner, 
+                       stmobj = stmFit,
+                       meta = out$meta, 
+                       uncertainty = "Global",
+                       nsims = sims)
+
+#make a dataframe to store the results in
+df <- data.frame(coef = rep(0, numtopics), sig = rep(FALSE, numtopics),
+                 lower = rep(0, numtopics), upper = rep(0, numtopics),
+                 topic = 1:numtopics)
+
+conf_level <- 1 #in percent
+conf_level <- conf_level/100 #as a fraction
+conf_level <- conf_level/2 #two-sided
+
+conf_lower <- 0 + conf_level
+conf_upper <- 1 - conf_level
+
+for(j in 1:numtopics){
+  
+  coefs <- list()
+  
+  for(i in 1:sims){
+    coefs[[i]] <- prep$parameters[[j]][[i]]$est[2]
+  }
+  
+  coefs <- do.call(c, coefs)
+  coefs <- quantile(coefs, c(conf_lower, conf_upper))
+  
[…]

### 2017-11-08 paper/manuscript.tex
hierarchical clustering, improved stm table, some other things

@@
 
-\author{ Markus Neumann \and Bruce Desmarais \and Hanna Wallach} \date{\today}
+\author{ Markus Neumann \and Bruce Desmarais \and Hanna Wallach \and Fridolin Linder} \date{\today}
 
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008).}
+	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
 	\label{fightinwords}
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008).}
+	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
 	\label{fightinwordsLA}
@@
 
-%Partisan top words - topic model
-\input{tables/partisanTopWords.tex}
+%Partisan top words - topic model Indiana
+\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
 
-%Partisan top words - fightin words
-\input{tables/fightinwords.tex}
+%Partisan top words - topic model Louisiana
+\input{tables/partisanTopWordsLA.tex} %tabLDALA
 
-%Partisan top words - topic model
-\input{tables/partisanTopWordsLA.tex}
+%Partisan top words - fightin words Indiana
+\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
 
-%Partisan top words - fightin words
-\input{tables/fightinwordsLA.tex}
+%Partisan top words - fightin words Louisiana
+\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
 
-%HOW TO DO THIS???
-%\begin{table}
-%	\input{tables/fightinwords.tex}
-%\end{table}
+%Partisan top words - stm Indiana
+\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
+
+%Partisan top words - stm Louisiana
+\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
 
 %Some basic descriptive statistics of documents by party
-\input{tables/descriptiveStatisticsPartisan.tex}
+\input{tables/descriptiveStatisticsPartisanIN.tex}
+
+%Some basic descriptive statistics of documents by party
+\input{tables/descriptiveStatisticsPartisanLA.tex}
+
+%fightin words results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
+	\label{linesCutoff}
+	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Hierarchical clustering (Indiana).}
+	\label{hclustIN}
+	\includegraphics[width=\linewidth]{figures/clusteringIN.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Hierarchical clustering (Louisiana).}
+	\label{hclustLA}
+	\includegraphics[width=\linewidth]{figures/clusteringLA.png}
+\end{figure}
 

### 2017-11-08 hierarchicalClusteringIN.R

@@ -1,0 +1,41 @@
+library('quanteda')
+library('dendextend')
+library('magrittr')
+library('lsa')
+
+# load data
+load("rfiles/d.Rdata")
+
+# convert to quanteda dfm
+crps <- corpus(d$doc)
+docvars(crps, "Party") <- d$winner
+dfmLA <- dfm(crps)
+
+# tf-idf representation
+dfmLA <- tfidf(dfmLA)
+m <- as.matrix(dfmLA)
+
+# euclidean distance
+distMatrix <- dist(m, method="euclidean")
+
+# cosine similarity (requires term-document matrix, so transpose first)
+#distMatrix <- cosine(t(m))
+
+# hierarchical clustering
+groups <- hclust(distMatrix, method="ward.D")
+groups$labels <- d$winner
+groups$labels[groups$labels=="Republican"] <- "R"
+groups$labels[groups$labels=="Democratic"] <- "D"
+hcd <- as.dendrogram(groups)
+# color by document party and plot
+colr <- rep("blue", nrow(d))
+colr[d$winner=="Republican"] <- "red"
+ppi <- 300
+png("paper/figures/clusteringIN.png", width=8*ppi, height=6*ppi, res=ppi)
+hcd %>% set("labels_col", colr) %>% # change color
+  set("labels_cex", .2) %>% # Change size
+  plot()
+dev.off()
+
+#everything takes quite a while, so save the results
+save.image("rfiles/hclustIN.rdata")

### 2017-11-08 stmIN.R

@@ -29,91 +29,6 @@ stmFit <- stm(documents = out$documents, vocab = out$vocab,
               init.type = "Spectral")
 
 #Estimate effects from the model outputs
-prep <- estimateEffect(1:numtopics ~ winner, stmFit,
-                       meta = out$meta, uncertainty = "Global")
-
-#save the results, since training takes some time
-#the results are so large, we only retain the
-#objects necessary for the rest of the analysis
-rm(list = ls()[!ls()%in% c("stmFit", "prep", "out", "numtopics")])
-save.image('rfiles/stmSessionIN_Party.RData')
-load('rfiles/stmSessionIN_Party.RData')
-
-# Analyze results
-a <- summary(prep)
-
-#coefficient is in Republican direction
-coefs <- data.frame(topic = 1:60, coefficient = 0, pval = 0)
-for(i in 1:nrow(coefs)){
-  coefs$coefficient[i] <- a$tables[[i]][2]
-  coefs$pval[i] <- a$tables[[i]][8]
-}
-
-#order by coefficient size
-coefs <- coefs[order(coefs$coefficient, decreasing = T),]
-
-#only keep coefficients that are statistically significant at 95% level
-coefs <- coefs[coefs$pval<0.05,]
-
-#most Republican/Democratic topics, determined by coefficient size
-repTopics <- coefs$topic[1:5]
-demTopics <- coefs$topic[(nrow(coefs)-4):nrow(coefs)]
-
-#topicLabels
-repWords <- labelTopics(stmFit, n = 10)
-repWords <- repWords$prob[repTopics,]
-repWords <- as.vector(repWords)
-
-demWords <- labelTopics(stmFit, n = 10)
-demWords <- demWords$prob[demTopics,]
-demWords <- as.vector(demWords)
-
-library("xtable")
-
-xt <- data.frame(Democratic = demWords, Republican = repWords)
-
-xt <- xtable(xt,
-             caption = "Top 50 Democratic and Republican words (Indiana), according to STM. 
-             The words are the top words for the most Democratic/Republican topic, determined
-             by the size (and significance) of the coefficient of the party covariate.",
-             label = "tabSTMIN")
-
-xt <- print.xtable(xt, 
-                   include.rownames = F,
-                   size = "\\fontsize{9pt}{10pt}\\selectfont")
-
-writeLines(xt, 
-           con = 'paper/tables/stmTopWordsIN.tex')
-
[…]

### 2017-11-15 paper/tables/stmTopWordsINDem.tex
improvements to stm, hclust, and some other stuff

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
-0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 & -0.011 & -0.011 \\ 
  \hline
fort & propos & said & prosecutor & digest & fund & servic & plan \\ 
  citi & author & ask & charg & introduc & grant & inform & develop \\ 
  ordin & district & state & feloni & author & budget & board & communiti \\ 
  approv & street & will & counti & counti & counti & applic & citi \\ 
  purchas & public & chair & case & appoint & state & project & neighborhood \\ 
  depart & control & propos & crime & board & feder & approv & program \\ 
  properti & amend & year & crimin & approv & depart & technolog & provid \\ 
  will & intersect & move & offic & district & appropri & system & public \\ 
  resolut & counti & need & victim & fund & increas & manag & resourc \\ 
  contract & committe & council & sentenc & street & agenc & agreement & area \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words (Indiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

### 2017-11-15 paper/tables/stmTopWordsINRep.tex
improvements to stm, hclust, and some other stuff

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 & 0.015 & 0.014 \\ 
  \hline
motion & plan & inc & request & council & traffic & build & inform \\ 
  second & zone & electr & board & citi & amp & histor & pleas \\ 
  made & applic & build & member & ordin & vehicl & preserv & will \\ 
  approv & properti & construct & servic & common & stop & wall & contact \\ 
  mayor & approv & home & street & councilor & sign & materi & use \\ 
  present & sign & street & approv & amend & road & paint & can \\ 
  state & site & meridian & purchas & resolut & block & roof & email \\ 
  will & locat & servic & citi & adopt & signal & structur & site \\ 
  citi & commiss & west & move & wherea & street & locat & phone \\ 
  council & file & main & good & approv & driver & window & card \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Indiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}

### 2017-11-15 paper/tables/stmTopWordsLADem.tex
improvements to stm, hclust, and some other stuff

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 18:17:05 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
-0.144 & -0.077 & -0.039 & -0.02 & -0.018 & -0.015 & -0.012 & -0.011 \\ 
  \hline
stream & obj & otherwis & polic & wherea & type & communiti & art \\ 
  length & ascent & provid & crime & ordin & content & neighborhood & call \\ 
  predictor & flag & respect & investig & citi & width & citi & cost \\ 
  acrobat & descent & thereto & offic & resolut & pdf & program & sponsor \\ 
  librari & encod & author & arrest & provid & height & public & free \\ 
  pdf & interpol & citi & inform & code & filter & develop & amp \\ 
  ash & matrix & district & suspect & street & parent & opportun & music \\ 
  hum & kid & ordin & victim & shall & count & particip & artist \\ 
  gym & baa & amend & block & chapter & resourc & creat & museum \\ 
  parent & filter & locat & street & provis & size & provid & home \\ 
   \hline
\end{tabular}
\caption{Top Democratic topics and words (Louisiana), according to STM. 
             The words are the top words for the most Democratic/Republican topic, determined
             by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLADem}
\end{table}

### 2017-11-15 paper/tables/stmTopWordsLARep.tex
improvements to stm, hclust, and some other stuff

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 18:17:04 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.085 & 0.062 & 0.062 & 0.057 & 0.021 & 0.019 & 0.018 & 0.017 \\ 
  \hline
event & ordin & citi & flood & west & properti & park & councilman \\ 
  park & bid & mayor & emerg & north & plan & street & said \\ 
  inform & summari & said & citi & east & zone & citi & citi \\ 
  food & amount & year & storm & south & lot & improv & mayor \\ 
  music & citi & state & resid & traffic & applic & recreat & want \\ 
  show & depart & announc & weather & boulevard & shall & work & council \\ 
  visit & public & work & inform & parish & requir & public & just \\ 
  market & contract & offici & hurrican & drive & approv & repair & think \\ 
  weekend & approv & resid & disast & road & use & program & vote \\ 
  begin & accord & million & power & locat & site & includ & thank \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Louisiana), according to STM. 
             The words are the top words for the most Democratic/Republican topic, determined
             by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLARep}
\end{table}

### 2017-11-15 duplicateLinesTesting.R

@@ -1,0 +1,46 @@
+library('pbapply')
+library('tidyr')
+library('ggplot2')
+
+# Load the documents
+load("rfiles/dIN2.rdata")
+# Load the duplicates indicators
+load("rfiles/docDuplicatesMatch.Rdata")
+
+#try out the function at different thresholds
+cleanupTest <- function(i, k = 10){
+  keep <- which(docDuplicates[[i]]<=k)
+  cleanedDoc <- d$doc[[i]][keep]
+  return(cleanedDoc)
+}
+
+kCutoffs <- 1:20
+kLinesKept <- rep(0, length(kCutoffs))
+for(i in 1:length(kCutoffs)){
+  test <- pblapply(1:nrow(d), cleanupTest, k = kCutoffs[i])
+  kLinesKept[i] <- sum(unlist(lapply(test, length)))
+}
+
+kLinesKeptMatch <- kLinesKept
+
+#Do the same, but for the hashmap version
+
+# Load the documents
+#load("rfiles/dIN2.rdata")
+# Load the duplicates indicators
+load("rfiles/docDuplicatesHash.Rdata")
+
+kCutoffs <- 1:20
+kLinesKept <- rep(0, length(kCutoffs))
+for(i in 1:length(kCutoffs)){
+  test <- pblapply(1:nrow(d), cleanupTest, k = kCutoffs[i])
+  kLinesKept[i] <- sum(unlist(lapply(test, length)))
+}
+
+# Plot the cutoff against the number of lines kept
+LinesCutoff <- data.frame(kCutoffs, hashmap = kLinesKept, match = kLinesKeptMatch)
+LinesCutoff <- gather(LinesCutoff, Method, LinesKept, hashmap, match)
+ggplot(LinesCutoff, aes(x = kCutoffs, y = LinesKept, color = Method)) +
+  geom_point() +
+  labs(x = "Cutoff", y = "Number of lines kept")
+ggsave(file = "paper/figures/linesCutoffIN.pdf", width = 8, height = 6)

### 2017-11-15 duplicateLinesTestingCharactes.R

@@ -1,0 +1,41 @@
+library('pbapply')
+library('tidyr')
+
+# Load the documents
+load("rfiles/dIN2.rdata")
+load("rfiles/docDuplicatesHash.Rdata")
+
+kCutoffs <- 1:20
+kLinesKept <- rep(0, length(kCutoffs))
+kCharsKept <- list()
+
+for(i in 1:length(kCutoffs)){
+  test <- pblapply(1:nrow(d), cleanupTest, k = kCutoffs[i])
+  kLinesKept[i] <- sum(unlist(lapply(test, length)))
+  kCharsKept[[i]] <- as.numeric(sapply(unlist(test), nchar))
+}
+
+#----------------------------------------------------------
+# Plot the cutoff against the number of characters kept
+charsCutoff <- data.frame(chars = unlist(lapply(kCharsKept, length)),
+                          cutoff = 1:20)
+ggplot(charsCutoff, aes(x = kCutoffs, y = chars)) +
+  geom_point() +
+  labs(x = "Cutoff", y = "Number of characters kept")
+ggsave(file = "paper/figures/charsCutoffIN.pdf", width = 8, height = 6)
+
+#----------------------------------------------------------
+#create a density plot with one line for each cutoff value
+kCharsKeptVector <- unlist(kCharsKept)
+#repeat the cutoff values, as many times as there are lines left at that cutoff
+kCutoffsVector <- rep(1:20, unlist(lapply(kCharsKept, length)))
+#put in dataframe
+charsCutoffLines <- data.frame(linelength = kCharsKeptVector,
+                          cutoff = kCutoffsVector)
+#plot
+m1 <- ggplot(charsCutoffLines, aes(x=kCharsKeptVector, colour=kCutoffsVector, 
+                                   group=kCutoffsVector))
+m1 <- m1 + geom_density(fill=NA, size=.2, alpha=0.1)
+m1 <- m1 + xlim(0, 150)
+m1 <- m1 + labs(x = "Line length (characters)", y = "Density", color = "Cutoff")
+ggsave(filename = "paper/figures/linesCutoffIN.pdf", plot = m1, width = 8, height = 6)

### 2017-11-15 hierarchicalClusteringLA.R

@@ -23,15 +23,19 @@ distMatrix <- dist(m, method="euclidean")
 
 # hierarchical clustering
 groups <- hclust(distMatrix, method="ward.D")
+#sub_grp <- cutree(groups, k = 4)
 groups$labels <- d$winner
 groups$labels[groups$labels=="Republican"] <- "R"
 groups$labels[groups$labels=="Democratic"] <- "D"
-hcd <- as.dendrogram(groups)
+groups2 <- groups
+groups2$height <- log(groups2$height)
+hcd <- as.dendrogram(groups2)
 # color by document party and plot
 colr <- rep("blue", nrow(d))
 colr[d$winner=="Republican"] <- "red"
 ppi <- 300
 png("paper/figures/clusteringLA.png", width=8*ppi, height=6*ppi, res=ppi)
+par(las = 1)
 hcd %>% set("labels_col", colr) %>% # change color
   set("labels_cex", .2) %>% # Change size
   plot()

### 2017-11-15 stmIN.R

@@ -81,9 +81,10 @@ sum(df$sig)
 #sort data frame by coefficient size
 df <- df[order(df$coef, decreasing = T),]
 
-#get the 5 topics with the highest/lowest significant coefficients
-repTopics <- df$topic[df$sig==T][1:5]
-demTopics <- rev(df$topic[df$sig==T][(nrow(df[df$sig==T,])-4):nrow(df[df$sig==T,])])
+#get the topics with the highest/lowest significant coefficients
+tableTopicNum <- 8
+repTopics <- df$topic[df$sig==T][1:tableTopicNum]
+demTopics <- rev(df$topic[df$sig==T][(nrow(df[df$sig==T,])-(tableTopicNum-1)):nrow(df[df$sig==T,])])
 
 #sort data frame by topic number
 df <- df[order(df$topic, decreasing = F),]
@@ -94,56 +95,41 @@ nTopWords <- 10
 #topicLabels
 repWords <- labelTopics(stmFit, n = nTopWords)
 repWords <- repWords$prob[repTopics,]
-repWords <- c(apply(repWords, 1, c))
+repWords <- t(repWords)
+colnames(repWords) <- round(df$coef[repTopics], 3)
 
 demWords <- labelTopics(stmFit, n = nTopWords)
 demWords <- demWords$prob[demTopics,]
-demWords <- c(apply(demWords, 1, c))
+demWords <- t(demWords)
+colnames(demWords) <- round(df$coef[demTopics], 3)
 
-#create data frame for xtable
-xt <- data.frame(demTopic = rep(demTopics, each = nTopWords),
-                 demTopicCoeff = round(rep(df$coef[demTopics], each = nTopWords), 3),
-                 Democratic = demWords,
-                 repTopic = rep(repTopics, each = nTopWords),
-                 repTopicCoeff = round(rep(df$coef[repTopics], each = nTopWords), 3),
-                 Republican = repWords)
+xtRep <- repWords
+xtDem <- demWords
+
+strCaptionRep <- "Top Republican topics and words (Indiana), according to STM. 
+The words are the top words for the most Democratic/Republican topic, determined
+by the size (and significance) of the coefficient (see table header) of the party covariate."
+
+strCaptionDem <- "Top Democratic topics and words (Indiana), according to STM. 
+The words are the top words for the most Democratic/Republican topic, determined
+by the size (and significance) of the coefficient (see table header) of the party covariate."
+
+xtRep <- print(xtable(repWords,
+                      digits = 3, 
[…]

### 2017-11-15 stmLA.R

@@ -3,6 +3,7 @@ library('tidyr')
 library('ggplot2')
 library('scales')
 library('stringr')
+library("xtable")
 
 load("rfiles/dLA.rdata")
 
@@ -25,7 +26,7 @@ numtopics <- 60
 #Train the model
 stmFit <- stm(documents = out$documents, vocab = out$vocab,
               K = numtopics, prevalence =~ winner,
-              max.em.its = 75, data = out$meta,
+              max.em.its = 1000, data = out$meta,
               init.type = "Spectral")
 
 #Estimate effects from the model outputs
@@ -81,9 +82,10 @@ sum(df$sig)
 #sort data frame by coefficient size
 df <- df[order(df$coef, decreasing = T),]
 
-#get the 5 topics with the highest/lowest significant coefficients
-repTopics <- df$topic[df$sig==T][1:5]
-demTopics <- rev(df$topic[df$sig==T][(nrow(df[df$sig==T,])-4):nrow(df[df$sig==T,])])
+#get the topics with the highest/lowest significant coefficients
+tableTopicNum <- 8
+repTopics <- df$topic[df$sig==T][1:tableTopicNum]
+demTopics <- rev(df$topic[df$sig==T][(nrow(df[df$sig==T,])-(tableTopicNum-1)):nrow(df[df$sig==T,])])
 
 #sort data frame by topic number
 df <- df[order(df$topic, decreasing = F),]
@@ -94,56 +96,41 @@ nTopWords <- 10
 #topicLabels
 repWords <- labelTopics(stmFit, n = nTopWords)
 repWords <- repWords$prob[repTopics,]
-repWords <- c(apply(repWords, 1, c))
+repWords <- t(repWords)
+colnames(repWords) <- round(df$coef[repTopics], 3)
 
 demWords <- labelTopics(stmFit, n = nTopWords)
 demWords <- demWords$prob[demTopics,]
-demWords <- c(apply(demWords, 1, c))
+demWords <- t(demWords)
+colnames(demWords) <- round(df$coef[demTopics], 3)
 
-#create data frame for xtable
-xt <- data.frame(demTopic = rep(demTopics, each = nTopWords),
-                 demTopicCoeff = round(rep(df$coef[demTopics], each = nTopWords), 3),
-                 Democratic = demWords,
-                 repTopic = rep(repTopics, each = nTopWords),
-                 repTopicCoeff = round(rep(df$coef[repTopics], each = nTopWords), 3),
[…]

### 2017-11-26 paper/manuscript.tex
improvements to stm, hclust, and some other stuff
added fightinwords and stm to the new scheme of state-agnostic scripts

@@
 This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Figure \ref{fightinwords} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
+Figure \ref{fightinwordsIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
 For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly.
@@
 	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
-	\label{fightinwords}
-	\includegraphics[width=\linewidth]{figures/fightinWords.png}
+	\label{fightinwordsIN}
+	\includegraphics[width=\linewidth]{figures/fightinWordsIN.png}
 \end{figure}
@@
 %Partisan top words - stm Indiana
-\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
+%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
 
 %Partisan top words - stm Louisiana
-\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
+%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
+
+%Partisan top words - stm Louisiana -- Rep
+\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
+
+%Partisan top words - stm Louisiana -- Dem
+\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
+
+%Partisan top words - stm Louisiana -- Rep
+\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
+
+%Partisan top words - stm Louisiana -- Dem
+\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
 

### 2017-11-26 stm.R

@@ -4,12 +4,23 @@ library('ggplot2')
 library('scales')
 library('stringr')
 
-load("rfiles/d.Rdata")
+# if no state data is loaded, default to Indiana
+if(exists("d")==F){
+  load(file = "./rfiles/d.Rdata")
+}
+
+if(exists("state")==F){
+  state <- "Indiana"
+}
+
+if(exists("stateAbb")==F){
+  stateAbb <- "IN"
+}
 
 #get the data ready for preprocessing
-docsIN <- d$doc
-meta <- subset(d, select = c('Name', 'winner'))
-processed <- textProcessor(docsIN, metadata = meta)
+docs <- d$doc
+meta <- subset(d, select = c('City', 'Party'))
+processed <- textProcessor(docs, metadata = meta)
 out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
 docs <- out$documents
 vocab <- out$vocab
@@ -42,8 +53,8 @@ prep <- estimateEffect(formula = 1:numtopics ~ winner,
 #the results are so large, we only retain the
 #objects necessary for the rest of the analysis
 rm(list = ls()[!ls()%in% c("stmFit", "prep", "out", "numtopics")])
-save.image('rfiles/stmSessionIN_Party.RData')
-load('rfiles/stmSessionIN_Party.RData')
+save.image(paste0("rfiles/stmSession", stateAbb, ", _Party.rdata"))
+load(paste0("rfiles/stmSession", stateAbb, ", _Party.rdata"))
 
 #make a dataframe to store the results in
 df <- data.frame(coef = rep(0, numtopics), sig = rep(FALSE, numtopics),
@@ -106,30 +117,30 @@ colnames(demWords) <- round(df$coef[demTopics], 3)
 xtRep <- repWords
 xtDem <- demWords
 
-strCaptionRep <- "Top Republican topics and words (Indiana), according to STM. 
+strCaptionRep <- paste0("Top Republican topics and words (", state, "), according to STM. 
 The words are the top words for the most Democratic/Republican topic, determined
-by the size (and significance) of the coefficient (see table header) of the party covariate."
+by the size (and significance) of the coefficient (see table header) of the party covariate.")
 
-strCaptionDem <- "Top Democratic topics and words (Indiana), according to STM. 
+strCaptionDem <- paste0("Top Democratic topics and words (", state, "), according to STM. 
 The words are the top words for the most Democratic/Republican topic, determined
-by the size (and significance) of the coefficient (see table header) of the party covariate."
[…]

### 2017-11-26 stmLA.R

@@ -1,136 +1,0 @@
-library('stm')
-library('tidyr')
-library('ggplot2')
-library('scales')
-library('stringr')
-library("xtable")
-
-load("rfiles/dLA.rdata")
-
-#get the data ready for preprocessing
-docsLA <- d$doc
-meta <- subset(d, select = c('City', 'winner'))
-processed <- textProcessor(docsLA, metadata = meta)
-out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-docs <- out$documents
-vocab <- out$vocab
-meta <- out$meta
-
-#the stm package has its own preprocessing function
-out <- prepDocuments(processed$documents, processed$vocab,
-                     processed$meta, lower.thresh = 15)
-
-#Number of topics
-numtopics <- 60
-
-#Train the model
-stmFit <- stm(documents = out$documents, vocab = out$vocab,
-              K = numtopics, prevalence =~ winner,
-              max.em.its = 1000, data = out$meta,
-              init.type = "Spectral")
-
-#Estimate effects from the model outputs
-sims <- 1000
-
-#re-estimate the effects, this time do 1000 draws from the posterior
-prep <- estimateEffect(formula = 1:numtopics ~ winner, 
-                       stmobj = stmFit,
-                       meta = out$meta, 
-                       uncertainty = "Global",
-                       nsims = sims)
-
-#save the results, since training takes some time
-#the results are so large, we only retain the
-#objects necessary for the rest of the analysis
-rm(list = ls()[!ls()%in% c("stmFit", "prep", "out", "numtopics")])
-save.image('rfiles/stmSessionLA_Party.RData')
-load('rfiles/stmSessionLA_Party.RData')
-
-#make a dataframe to store the results in
-df <- data.frame(coef = rep(0, numtopics), sig = rep(FALSE, numtopics),
-                 lower = rep(0, numtopics), upper = rep(0, numtopics),
-                 topic = 1:numtopics)
-
-conf_level <- 1 #in percent
-conf_level <- conf_level/100 #as a fraction
-conf_level <- conf_level/2 #two-sided
-
-conf_lower <- 0 + conf_level
-conf_upper <- 1 - conf_level
-
-for(j in 1:numtopics){
-  
-  coefs <- list()
-  
-  for(i in 1:sims){
-    coefs[[i]] <- prep$parameters[[j]][[i]]$est[2]
-  }
-  
-  coefs <- do.call(c, coefs)
[…]

### 2017-11-26 paper/manuscript.tex
starting to add the LDA stuff to the new state-agnostic scripts

@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
+	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
 	\label{doctopics_density}
-	\includegraphics[width=\linewidth]{figures/doctopics_density.pdf}
+	\includegraphics[width=\linewidth]{figures/doctopics_density_IN.pdf}
 \end{figure}
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities.}
+	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
 	\label{topicweights_density}
-	\includegraphics[width=\linewidth]{figures/topicweights_density.pdf}
+	\includegraphics[width=\linewidth]{figures/topicweights_density_IN.pdf}
 \end{figure}
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
+	\caption{Word-topic probabilities for topics with big partisan differences (Indiana).}
 	\label{diffsize}
-	\includegraphics[width=\linewidth]{figures/diffsize.pdf}
+	\includegraphics[width=\linewidth]{figures/diffsize_IN.pdf}
 \end{figure}
@@
 	\label{plotWTP_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs.pdf}
+	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs_IN.pdf}
 \end{figure}
@@
 	\label{doctopics_density_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs.pdf}
+	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs_IN.pdf}
 \end{figure}
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
+	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
 	\label{heatmaps_weights}
-	\includegraphics[width=\linewidth]{figures/heatmaps_weights.png}
+	\includegraphics[width=\linewidth]{figures/heatmaps_weights_IN.png}
 \end{figure}

### 2017-11-26 Indiana.R

@@ -1,5 +1,8 @@
 setwd("govWebsites")
 
+state <- "Indiana"
+stateAbb <- "IN"
+
 # ------------- #
 # Preprocessing #
 # ------------- #
@@ -16,16 +19,39 @@ docDuplicates <- findDuplicates(d)
 # Use the counts of duplicate lines found above to remove them over a certain threshold
 d$doc <- as.character(pbsapply(1:nrow(d), removeDuplicates))
 
-save.image("rfiles/backup_d.rdata")
+#save.image("rfiles/backup_d.rdata")
 
 # Do the rest of the preprocessing
 d <- preprocessing_2(d)
+
+save(d, file = paste0("rfiles/d_", stateAbb, ".rdata"))
+load(paste0("rfiles/d_", stateAbb, ".rdata"))
 
 # ------------- #
 #      LDA      #
 # ------------- #
 
-source("malletTraining.R")
+# Train LDA
+source("functions/malletTraining.R")
+
+# 6 (mostly diagnostic) figures:
+#Densities of topic weights for documents in Republican and Democratic cities.
+#\label{topicweights_density}
+# Densities of topic weights for documents in Republican and Democratic cities.
+#\label{doctopics_density}
+#Word-topic probabilities for topics with big partisan differences
+#\label{diffsize}
+#Word-topic probabilities for topics with big partisan differences
+#\label{plotWTP_bigdiffs}
+#Word-topic probabilities for topics with big partisan differences
+#\label{doctopics_density_bigdiffs}
+#Word-topic probabilities for topics with big partisan differences, across documents
+#\label{heatmaps_weights}
+source("malletAnalysis.R")
+
+#source("malletAnalysisPartisanTopicsLA.R")
+#source("malletAnalysisPartisanTopWordsLA.R")
+#source("descriptiveStatisticsPartisan.R")
 
 # -----------------------#
 # Structural Topic Model #
@@ -42,3 +68,5 @@ source("fightinWords.R")
 # ------------- #
 #  Clustering   #
 # ------------- #
+
+#source("hierarchicalClustering.R")

### 2017-11-26 functions/preprocessing.R

@@ -255,11 +255,11 @@ preprocessing_2 <- function(d){
   #remove documents in which too many words are the same
   print("Removing documents in which too many words are the same.")
   countTokens <- function(doc){
-    doc <- tokenize(doc, simplify = T)
+    doc <- as.character(tokens(doc))
     l <- length(doc)
   }
   countUniqueTokens <- function(doc){
-    doc <- tokenize(doc, simplify = T)
+    doc <- as.character(tokens(doc))
     l <- length(unique(doc))
   }
   d$ntokens <- sapply(d$doc, countTokens)

### 2017-11-26 malletAnalysisLA.R

@@ -1,201 +1,0 @@
-source("malletTrain.R")
-
-options(java.parameters = "-Xmx3000m")
-
-library('mallet')
-library('tibble')
-library('stringr')
-library('tools')
-library('tm')
-library('ggplot2')
-library('cowplot')
-library('dplyr')
-library('quanteda')
-library('hunspell')
-library('tidyr')
-
-## Retrieve a matrix of topic weights for every document
-## Rows are documents
-## Columns are topics
-## If normalized is set to FALSE, this is the actual number of words of each topic in the documents
-# For example, document 2 (second row) contains 37 words of topic 2 (second column)
-# Note that in order for actual integers to be displayed, smoothed also needs to be set to false
-## If normalized is set to TRUE, each document sums to one
-# For example, 6.855605e-02 of all words in document 2 (second row) belong to topic 2 (second column)
-doc.topics <- mallet.doc.topics(topic.model, smoothed = T, normalized = T)
-#dim(doc.topics) #12397 documents; 100 topics
-#as.tibble(doc.topics)
-
-## Retrieve a matrix of words weights for topics
-## Rows are topics
-## Columns are word types
-## If normalized is set to FALSE, this is the actual number of words of each type in the topics
-# For example, topic 1 (first row) contains 4379 token instances of word type 2 (second column)
-# Note that in order for actual integers to be displayed, smoothed also needs to be set to false
-## If normalized is set to TRUE, each topic (row) sums to one
-# For example, 3.105702e-02 of all token instances in topic 1 (first row) are made up by word type 2 (second column)
-topic.words <- mallet.topic.words(topic.model, smoothed = T, normalized = T)
-#dim(topic.words) #100 topics; 31472 word types
-#as.tibble(topic.words)
-
-## Subset the matrix into two matrices, one containing
-# documents from Democratic cities, the other from Republican cities
-republican <- doc.topics[which(d$winner == "Republican"),]
-democratic <- doc.topics[which(d$winner == "Democratic"),]
-
-republican <- as.tibble(republican)
[…]

### 2017-11-29 CutoffCityEntropy.R
finally managed to get the cross city entropy for different duplicate lines removal cutoffs to work

@@ -1,12 +1,16 @@
 
+city.entropies <- list()
+
 for(i in 1:20){
   
-  load("rfiles/docDuplicatesHash.Rdata")
-  load("rfiles/dIN2.rdata")
+  #load("rfiles/docDuplicatesHash.Rdata")
+  #load("rfiles/dIN2.rdata")
   
   cutoff <- i
   
-  source("functions/preprocessingTesting.R")
+  #source("functions/preprocessingTesting.R")
+  
+  load(paste0("./../Dropbox/govWebsitesMovingVan/d_test_K", cutoff, ".rdata"))
   
   source("functions/malletTraining.R")
   
@@ -16,7 +20,6 @@ for(i in 1:20){
   
   city.entr <- data.frame(x = city_entropy(doc.topics, d))
   
-  city.entropies <- list()
   city.entropies[[i]] <- city.entr
 
 }
@@ -24,17 +27,16 @@ for(i in 1:20){
 #create a density plot with one line for each cutoff value
 kCityEntropyVector <- unlist(city.entropies)
 #repeat the cutoff values, as many times as there are lines left at that cutoff
-kCutoffsVector <- rep(1:2, 200)
+kCutoffsVector <- rep(1:20, 200)
 #put in dataframe
 entropy.df <- data.frame(Entropy = kCityEntropyVector,
                          Cutoff = kCutoffsVector)
 
 save.image("rfiles/CutoffCityEntropy.rdata")
 
-#m1 <- ggplot(entropy.df, aes(x = kCityEntropyVector, 
-#                                   colour=kCutoffsVector, 
-#                                   group=kCutoffsVector))
-#m1 <- m1 + geom_density(fill = NA, size = .2, alpha = 0.1)
-#m1 <- m1 + xlim(0, 150)
-#m1 <- m1 + labs(x = "Line length (characters)", y = "Density", color = "Cutoff")
+m1 <- ggplot(entropy.df, aes(x = kCityEntropyVector, 
+                                   colour=kCutoffsVector, 
+                                   group=kCutoffsVector))
+m1 <- m1 + geom_density(fill = NA, size = .2, alpha = 0.1)
+m1 <- m1 + labs(x = "Entropy (between cities, for each topic)", y = "Density", color = "Cutoff")
 #ggsave(filename = "paper/figures/CutoffCityEntropy.pdf", plot = m1, width = 8, height = 6)

### 2017-12-06 paper/manuscript.tex
finally managed to get the cross city entropy for different duplicate lines removal cutoffs to work
cutoffs entropy with topic weights + improvements to clusters more plots, etc.

@@
 
+%Heatmaps with no duplicate line removal (threshold set at 999999999)
+%also, since the duplicate line removal didn't get rid of as much crap,
+%it was necessary to remove non [A-Za-z] characters before hunspell
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana). No duplicate line removal.}
+	\label{heatmaps_weights}
+	\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
+\end{figure}
+
 %Number of topics vs. tophic coherence
@@
 
+%Entropy by cutoff
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Entropy (between cities, for each topic).}
+	\label{cutoffEntropy}
+	\includegraphics[width=\linewidth]{figures/CutoffCityEntropy.pdf}
+\end{figure}
+
+%Weighted entropy by cutoff
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Weighted (multiplied by tokens assigned to the topic) entropy (between cities, for each topic).}
+	\label{cutoffEntropy}
+	\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity10}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_10.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity20}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_20.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity30}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_30.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity40}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_40.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity50}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_50.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity100}
+	\includegraphics[height = 1.2\textheight]{figures/heatmap_hclust_100.png}
+\end{figure}
+
 \newpage

### 2017-12-06 CutoffCityEntropy.R

@@ -40,3 +40,30 @@ m1 <- ggplot(entropy.df, aes(x = kCityEntropyVector,
 m1 <- m1 + geom_density(fill = NA, size = .2, alpha = 0.1)
 m1 <- m1 + labs(x = "Entropy (between cities, for each topic)", y = "Density", color = "Cutoff")
 #ggsave(filename = "paper/figures/CutoffCityEntropy.pdf", plot = m1, width = 8, height = 6)
+
+#multiply entropy values by number of tokens assigned to topic
+
+topic.tokens <- apply(doc.topics, 2, sum)
+
+city.entropies.weighted <- city.entropies
+
+for(i in 1:length(city.entropies)){
+  
+  city.entropies.weighted[[i]] <- city.entropies[[i]]*topic.tokens
+  
+}
+
+#create a density plot with one line for each cutoff value
+kCityEntropyVector <- unlist(city.entropies.weighted)
+#repeat the cutoff values, as many times as there are lines left at that cutoff
+kCutoffsVector <- rep(1:20, 200)
+#put in dataframe
+entropy.df <- data.frame(Entropy = kCityEntropyVector,
+                         Cutoff = kCutoffsVector)
+
+m1 <- ggplot(entropy.df, aes(x = kCityEntropyVector, 
+                             colour = kCutoffsVector, 
+                             group = kCutoffsVector))
+m1 <- m1 + geom_density(fill = NA, size = .2, alpha = 0.1)
+m1 <- m1 + labs(x = "Weighted entropy (between cities, for each topic)", y = "Density", color = "Cutoff")
+#ggsave(filename = "paper/figures/CutoffCityEntropyWeighted.pdf", plot = m1, width = 8, height = 6)

### 2017-12-06 hierarchicalClusteringIN.R

@@ -51,7 +51,7 @@ entropy <- function(freqs){
 # =============================================================================
 
 #explore what the documents cluster into if k = 10
-nclust <- 10
+nclust <- 32
 groups$labels <- 1:nrow(d)
 test <- cutree(groups, k = nclust)
 test.names <- names(test)
@@ -102,9 +102,11 @@ for(j in 1:length(ind)){
 
 groups$labels <- d$Name
 
-nclust <- 50
+nclust <- 100
 
 entropy.values <- list()
+
+chisq.pval <- list()
 
 for(i in 1:nclust){
   #cuttree to decide number clusters
@@ -114,17 +116,122 @@ for(i in 1:nclust){
   #cluster according to party/city
   cluster.categories <- data.frame(cluster = test, category = test.names)
   test2 <- xtabs(~ category + cluster, data = cluster.categories)
-  #add a bit of noise to the frequencies that are 0
-  test2[test2==0] <- test2[test2==0]+0.0000000000000001
-  #represent as proportions instead of frequencies
-  props <- as.numeric(test2/sum(test2))
-  #calculate entropy and save in list
-  entropy.values[[i]] <- entropy(props)
+  
+  chisq.pval[[i]] <- chisq.test(test2)$p.value
+  
+  
+  # #add a bit of noise to the frequencies that are 0
+  # test2[test2==0] <- test2[test2==0]+0.0000000000000001
+  # #represent as proportions instead of frequencies
+  # props <- as.numeric(test2/sum(test2))
+  # #calculate entropy and save in list
+  # entropy.values[[i]] <- entropy(props)
 }
 
-library("ggplot2")
+chisq.df <- data.frame(clusters = 1:100, pvalues = unlist(chisq.pval))
 
-df <- data.frame(Entropy = unlist(entropy.values), Clusters = 1:nclust)
+#ggplot(chisq.df, aes(x = clusters, y = pvalues)) + geom_point() + 
+#  ylim(0,10e-200)
 
-ggplot(df, aes(x = Clusters, y = Entropy)) +
-  geom_point()
+# library("ggplot2")
+# 
+# df <- data.frame(Entropy = unlist(entropy.values), Clusters = 1:nclust)
+# 
+# ggplot(df, aes(x = Clusters, y = Entropy)) +
+#   geom_point()
+
+#------------------------------------------------------------------------------
+
+# Make heatmaps for city documents per cluster, for different numbers of clusters
+
+library(reshape2)
+library(ggplot2)
+
[…]

### 2017-12-06 malletAnalysis.R

@@ -213,4 +213,4 @@ heatmaps_g <- plot_grid(heatmap_democratic, heatmap_republican, nrow = 2)
 #save; plot takes up a lot of space as pdf, so save as png instead
 ggsave(heatmaps_g, 
        file = str_c("./paper/figures/heatmaps_weights_", stateAbb, ".png"), 
-       width=5, height=8)
+       width=5, height=7.5)

### 2017-12-14 paper/newResearchDesign.tex
new abstract

--- 2017-10-18 paper/manuscript_new.tex
@@
 
-Websites have become a prominent source of data for automated text analysis in political science.
-However, extant research lacks common standards and often glosses over the details on how such analyses are conducted, exposing itself to potential pitfalls associated with this process and making replication difficult.
+Government websites are vital for transparency and have become a prominent source of data for automated text analysis in public administration research as well as political science at large.
+However, extant scholarship lacks common standards and often glosses over the details of how such analyses are conducted.
 We develop a set of guidelines and procedures to be followed in order to produce valid results.
-In order to develop a valid research design, the appropriate selection of cases and URLs is crucial.
 For the acquisition of website data, we cover several scraping methods and difficulties that can arise in the process.
-Pre-processing is a common step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
-Finally, we cover several methods of analysis and validation appropriate for this kind of data.
+Pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
+We propose a new method for dealing with the kind of duplicated content that is commonly found in this type of data.
+Finally, we compare several methods of analysis and validation appropriate in this context.
 These steps are illustrated through our creation and exploitation of a new and innovative dataset - the websites of local governments in Indiana and Louisiana.

### 2017-12-17 paper/presentation/Markus_Presentation_MA_Thesis.tex
presentation

\documentclass[12pt]{beamer}
\setbeamertemplate{navigation symbols}{}
%\usepackage[latin1]{inputenc}
\usepackage{pgfplots}
\usepackage{adjustbox}
\usepackage{graphicx}
%\usepackage{draftwatermark}
\usepackage{tikz}
\usepackage{subfigure}
\usetheme{Amsterdam}
\usecolortheme{default}
\title[]{The effects of transitions of power on the contents of
	municipal government websites}
\author{Markus Neumann \\ Bruce Desmarais \\ Hanna Wallach \\ Fridolin Linder}
\institute{The Pennsylvania State University}
\date{January 6, 2018}

\makeatletter
\defbeamertemplate*{footline}{myminiframes theme}
{%
	\begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
	\end{beamercolorbox}
	\hbox{%
		\begin{beamercolorbox}[wd=.1\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}\insertframenumber/\inserttotalframenumber}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.75\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			\leavevmode{\usebeamerfont{title in head/foot}\insertshorttitle}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.15\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}\insertshortauthor}
		\end{beamercolorbox}%
	}%
	\begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
	\end{beamercolorbox}
}
\makeatother

\begin{document}

\section{Introduction}
\begin{frame}
\titlepage
\end{frame}

%\begin{frame}{Spot the difference}
%\begin{figure}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{Images/Clinton_Rally_cr.jpg}}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{Images/Trump_Rally_cr.jpg}}
%\end{figure}
%\end{frame}

\begin{frame}{Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
	\item Transparency
	\end{itemize}
	}
\end{frame}

\section{Data Collection}
\begin{frame}{wget}
\end{frame}

\section{Preprocessing}

\begin{frame}{Document filetype \& conversion}
\begin{itemize}
	\item Websites contain a number of different filetypes
	\item txt, pdf, html, doc and docx are useable
	\item convert everything to txt
	\item the file ENDING does not always 
\end{itemize}
\end{frame}

\begin{frame}{Duplicate Line Removal}
\includegraphics[width = \linewidth]{duplicateLines.png}
\end{frame}

\begin{frame}{Duplicate Line Removal}
	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
\end{frame}

\begin{frame}{Duplicate Line Removal}
\begin{itemize}
	\item Within each city, there is a lot of shared text
	\begin{itemize}
		\item Boilerplate
		\item Website elements
	\end{itemize}
	\item If not removed, the text clusters into cities
\end{itemize}
\begin{itemize}
	\item Solution: Compare each line in each document to every other line in every document of that city
	\item Count duplicates
	\item Remove a line if it is duplicated within a city above some threshold
	\item Hash tables for computational efficiency
\end{itemize}
\end{frame}

\begin{frame}{Other preprocessing}
\begin{itemize}
	\item Remove:
	\begin{itemize}
		\item Dates
		\item Numbers
		\item Punctuation
		\item Words not recognized by an English dictionary
		\item Stopwords
		\item Documents with too few unique words
	\end{itemize}
\item Set to lowercase
\item Lemmatization
\end{itemize}
\end{frame}

\section{Analysis}
\begin{frame}{Hierarchical Clustering}
\end{frame}

\begin{frame}{Fightin' Words}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
	\hfill
	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
\end{figure}
\end{frame}

\begin{frame}{Latent Dirichlet Allocation}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
\end{frame}

\end{document}

### 2017-12-18 paper/presentation/Markus_SPSA_2018_Presentation.tex
presentation

--- 2017-12-17 paper/presentation/Markus_Presentation_MA_Thesis.tex
@@
 \usepackage{subfigure}
-\usetheme{Amsterdam}
+%\usetheme{Amsterdam}
 \usecolortheme{default}
@@
 	municipal government websites}
-\author{Markus Neumann \\ Bruce Desmarais \\ Hanna Wallach \\ Fridolin Linder}
+\author{Markus Neumann \\ Fridolin Linder \\ Bruce Desmarais}
 \institute{The Pennsylvania State University}
@@
 			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
-			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}\insertframenumber/\inserttotalframenumber}%
+			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertframenumber/\inserttotalframenumber}%
 		\end{beamercolorbox}%
@@
 			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
-			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}\insertshortauthor}
+			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertshortauthor}
 		\end{beamercolorbox}%
@@
 	\begin{itemize}
-	\item Transparency
+		\item Content of government websites is an important source of information \& transparency
+		\item After coming into power, the Trump administration  has made some controversial changes to the websites of federal agencies
+		\item Website content is political
+		\item Partisanship of city government is expected to have an effect
 	\end{itemize}
+
 }
@@
 
-\section{Data Collection}
-\begin{frame}{wget}
+\begin{frame}{Government Websites}
+\linespread{1.5}
+{\large
+	\begin{itemize}
+		\item Most local (i.e. mayoral) elections are non-partisan
+		\item Few states have exclusively partisan local elections
+		\item Data for these elections can be difficult to find
+		\item We selected Indiana and Louisiana
+	\end{itemize}
+
+	}
+\end{frame}
+
+\begin{frame}{Maps}
+\begin{figure}
+	\hfill
+	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
+	\hfill
+	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
+\end{figure}
+\end{frame}
+
+\begin{frame}{The Pipeline}
+	\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
+\begin{columns}
+	\column{0.33\textwidth}
+	%Data Collection
+	\vspace{5mm}
+	\begin{itemize}
+		\item Scraping URLs
+		\item Browser automation to verify URLs
+		\item Download sites with wget
+		\item Determine file type
+		\item Convert to txt
+	\end{itemize}		
+	\column{0.33\textwidth}
+	%Preprocessing
+	\vspace{5mm}
+	\begin{itemize}
+		\item Remove punctuation, dates, etc.
+		\item To lowercase
+		\item Duplicate content removal
+		\item Spellchecking
+		\item Lemmatization
+	\end{itemize}
+	\column{0.33\textwidth}
+	%Analysis
+	\vspace{5mm}
+	\begin{itemize}
+		\item Hierarchical clustering
+		\item Fightin' Words
+		\item Topic models
+		\begin{itemize}
+			\item LDA
+			\item STM
+		\end{itemize}
+	\end{itemize}
+\end{columns}
+\end{frame}
+
+\begin{frame}{The Pipeline}
+\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
+\begin{columns}
+	\column{0.33\textwidth}
+	%Data Collection
+	\vspace{5mm}
+	\begin{itemize}
+		\item Scraping URLs
+		\item Browser automation to verify URLs
+		\item Download sites with wget
+		\item Determine file type
+		\item Convert to txt
+	\end{itemize}		
+	\column{0.33\textwidth}
+	%Preprocessing
+	\vspace{5mm}
+	\begin{itemize}
+		\item Remove punctuation, dates, etc.
+		\item To lowercase
+		\item \textbf{Duplicate content removal}
+		\item Spellchecking
+		\item Lemmatization
+	\end{itemize}
+	\column{0.33\textwidth}
+	%Analysis
+	\vspace{5mm}
+	\begin{itemize}
+		\item Hierarchical clustering
+		\item Fightin' Words
+		\item Topic models
+		\begin{itemize}
+			\item LDA
+			\item STM
+		\end{itemize}
+	\end{itemize}
+\end{columns}
 \end{frame}
@@
 
-\begin{frame}{Document filetype \& conversion}
-\begin{itemize}
-	\item Websites contain a number of different filetypes
-	\item txt, pdf, html, doc and docx are useable
-	\item convert everything to txt
-	\item the file ENDING does not always 
-\end{itemize}
+%\begin{frame}{Document filetype \& conversion}
+%\begin{itemize}
+%	\item Websites contain a number of different filetypes
+%	\item txt, pdf, html, doc and docx are useable
+%	\item convert everything to txt
+%	\item the file ENDING does not always 
+%\end{itemize}
+%\end{frame}
+
+\begin{frame}{Duplicate Content Removal}
+\includegraphics[width = \linewidth]{arcadia_water.png}
 \end{frame}
 
-\begin{frame}{Duplicate Line Removal}
+\begin{frame}{Duplicate Content Removal}
 \includegraphics[width = \linewidth]{duplicateLines.png}
@@
 
-\begin{frame}{Duplicate Line Removal}
+\begin{frame}{Duplicate Content Removal}
 	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
@@
 
-\begin{frame}{Duplicate Line Removal}
+\begin{frame}{Duplicate Content Removal}
 \begin{itemize}
@@
 
-\begin{frame}{Other preprocessing}
+\begin{frame}{The Pipeline}
+\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
+\begin{columns}
+	\column{0.33\textwidth}
+	%Data Collection
+	\vspace{5mm}
 	\begin{itemize}
-	\item Remove:
+		\item Scraping URLs
+		\item Browser automation to verify URLs
+		\item Download sites with wget
+		\item Determine file type
+		\item Convert to txt
+	\end{itemize}		
+	\column{0.33\textwidth}
+	%Preprocessing
+	\vspace{5mm}
 	\begin{itemize}
-		\item Dates
-		\item Numbers
-		\item Punctuation
-		\item Words not recognized by an English dictionary
-		\item Stopwords
-		\item Documents with too few unique words
-	\end{itemize}
-\item Set to lowercase
+		\item Remove punctuation, dates, etc.
+		\item To lowercase
+		\item Duplicate content removal
+		\item Spellchecking
 		\item Lemmatization
 	\end{itemize}
+	\column{0.33\textwidth}
+	%Analysis
+	\vspace{5mm}
+	\begin{itemize}
+		\item Hierarchical clustering
+		\item Fightin' Words
+		\item Topic models
+		\begin{itemize}
+			\item LDA
+			\item STM
+		\end{itemize}
+	\end{itemize}
+\end{columns}
 \end{frame}
+
+%\begin{frame}{Other preprocessing}
+%\begin{itemize}
+%	\item Remove:
+%	\begin{itemize}
+%		\item Dates
+%		\item Numbers
+%		\item Punctuation
+%		\item Words not recognized by an English dictionary
+%		\item Stopwords
+%		\item Documents with too few unique words
+%	\end{itemize}
+%\item Set to lowercase
+%\item Lemmatization
+%\end{itemize}
+%\end{frame}
 
@@
 \begin{frame}{Hierarchical Clustering}
+\centering
+\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
 \end{frame}
@@
 \begin{frame}{Latent Dirichlet Allocation}
+
+\input{partisanTopWords.tex}
+
+\end{frame}
+
+\begin{frame}{Structural Topic Model}
+\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
+\end{frame}
+
+\begin{frame}{Structural Topic Model}
+\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
 \end{frame}
@@
 \begin{frame}{Conclusion}
+%\linespread{1.5}
+\large
+\begin{itemize}
+	\item Hierarchical clustering only creates 'topics' if content is VERY similar
+	\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
+	\item LDA is sensitive to preprocessing, but the most flexible
+	\item STM works too, but also very sensitive to duplicate content
+	\vspace{5mm}
+	\item Democrats focus on raising and spending money, Republicans on infrastructure and basic utilities
+\end{itemize}
 \end{frame}

### 2017-12-18 paper/presentation/stmTopWordsINDem.tex
presentation

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
-0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 \\ 
  \hline
fort & propos & said & prosecutor & digest & fund \\ 
  citi & author & ask & charg & introduc & grant \\ 
  ordin & district & state & feloni & author & budget \\ 
  approv & street & will & counti & counti & counti \\ 
  purchas & public & chair & case & appoint & state \\ 
  depart & control & propos & crime & board & feder \\ 
  properti & amend & year & crimin & approv & depart \\ 
  will & intersect & move & offic & district & appropri \\ 
  resolut & counti & need & victim & fund & increas  \\ 
  contract & committe & council & sentenc & street & agenc \\ 
   \hline
\end{tabular}
%\caption{Top Democratic topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

### 2017-12-18 paper/presentation/stmTopWordsINRep.tex
presentation

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 \\ 
  \hline
motion & plan & inc & request & council & traffic \\ 
  second & zone & electr & board & citi & amp \\ 
  made & applic & build & member & ordin & vehicl \\ 
  approv & properti & construct & servic & common & stop \\ 
  mayor & approv & home & street & councilor & sign \\ 
  present & sign & street & approv & amend & road \\ 
  state & site & meridian & purchas & resolut & block \\ 
  will & locat & servic & citi & adopt & signal \\ 
  citi & commiss & west & move & wherea & street \\ 
  council & file & main & good & approv & driver \\ 
   \hline
\end{tabular}
%\caption{Top Republican topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}

### 2017-12-18 hierarchicalClusteringIN.R

@@ -51,17 +51,21 @@ entropy <- function(freqs){
 # =============================================================================
 
 #explore what the documents cluster into if k = 10
-nclust <- 32
-groups$labels <- 1:nrow(d)
+nclust <- 100
+groups$labels <- d$Name
 test <- cutree(groups, k = nclust)
 test.names <- names(test)
-cluster.categories <- data.frame(cluster = test, category = test.names)
+cluster.categories <- data.frame(cluster = test, category = test.names, ind = 1:length(test.names))
 #test2 <- xtabs(~ category + cluster, data = cluster.categories)
+
+diag.files <- list.files("diagnostics/hclustering", full.names = T)
+diag.files <- diag.files[diag.files!="diagnostics/hclustering/_comments.txt"]
+file.remove(diag.files)
 
 #for each cluster
 for(i in 1:nclust){
 
-clust.indices <- cluster.categories$category[cluster.categories$cluster==i]
+clust.indices <- cluster.categories$ind[cluster.categories$cluster==i]
   
 ind <- sample(clust.indices, ifelse(length(clust.indices)>=10, 10, length(clust.indices)))
 
@@ -95,6 +99,10 @@ for(j in 1:length(ind)){
   
   
 }}
+
+#For testing purposes
+#look at the d dataframea only for the documents in a specific cluster
+#d_test = d[cluster.categories$ind[cluster.categories$cluster==59],]
 
 # =============================================================================
 

### 2017-12-18 mapLouisiana.R

@@ -9,7 +9,7 @@ d$latitude <- as.numeric(d$latitude)
 d$longitude <- as.numeric(d$longitude)
 d$winner[is.na(d$winner)==T] <- "NA"
 
-## Indiana
+## Louisiana
 # get the map from Google maps
 states <- map_data("state")
 louisiana <- subset(states, region %in% c("louisiana"))
@@ -22,7 +22,8 @@ map2 <- map1 +
   geom_point(data = d, aes(x = longitude, y = latitude, color = winner), size = 2) + 
   theme(legend.position = "none") + 
   scale_color_manual(values=c("blue", "gray", "red")) +
-  labs(x = "Longitude", y = "Latitude")
+  labs(x = "Longitude", y = "Latitude") +
+  theme_void() + theme(legend.position = "none")
 map2
 
-ggsave(filename = "paper/figures/louisiana_map.pdf", plot = map2, width = 5, height = 8)
+ggsave(filename = "paper/figures/louisiana_map.pdf", plot = map2, width = 5, height = 5)

### 2017-12-18 paper/manuscript.tex
updating with JPART revisions

@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites }
-
-\author{ Markus Neumann \and Bruce Desmarais \and Hanna Wallach \and Fridolin Linder} \date{\today}
+\title{\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis }
+
+\author{ Markus Neumann \and Fridolin Linder \and Bruce Desmarais} \date{\today}
 
@@
 
-Websites have become a prominent source of data for automated text analysis in political science.
-However, extant research lacks common standards and often glosses over the details on how such analyses are conducted, exposing itself to potential pitfalls associated with this process and making replication difficult.
-We develop a set of guidelines and procedures to be followed in order to produce valid results.
-In order to develop a valid research design, the appropriate selection of cases and URLs is crucial.
-For the acquisition of website data, we cover several scraping methods and difficulties that can arise in the process.
-Pre-processing is a common step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
-Finally, we cover several methods of analysis and validation appropriate for this kind of data.
-These steps are illustrated through our creation and exploitation of a new and innovative dataset - the websites of local governments in Indiana and Louisiana.
-We show that if our methodology is followed appropriately, an association between mayoral partisanship and the content of their cities' websites becomes visible.
-
+A local government's website is a standard and general source of information for citizens and other community stakeholders.
+Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science.
+Existing research has relied on manual methods of website data collection of processing.
+Reliance on manual collection and processing limits the scale and scope of website content analysis.
+We develop a methodological pipeline that researchers can followed in order to gather, process, and analyze website content with established text analysis techniques.
+First, for the acquisition of website data, we cover approaches to automated scraping methods.
+Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
+We propose a new method for dealing with the kind of duplicated content that is commonly found in government websites.
+Finally, we illustrate methods of text analysis using automatically gathered and pre-processed website content.
+We illustrate our methodological pipeline through a new and innovative dataset---the websites of local governments in Indiana and Louisiana.
+We build upon recent research that analyzes how change and variation in the partisan control of government relates to content made available on the government's website.
+We explore the association between mayoral partisanship and the content of city websites.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.

### 2017-12-18 paper/manuscript.tex
revised to present a basic introduction

@@
 
-\subsection{New Research Design}
-The analysis of entire websites has become more prominent recently, especially in the the text-as-data movement.
-We see great promise in this development, especially as it pertains to the study of governmental branches and agencies, which are often resilient to being studied by other methods.
-However, this line of inquiry comes with a set of particular challenges and pitfalls researchers need to be mindful of.
-We offer solutions to these problems at the four stages of such an analysis.
-
-\begin{enumerate}
-	\item Design
-	\begin{enumerate}
-		\item Choosing the sample
-		\item Finding URLs
-		\item list of .gov websites
-		\item Finding supporting data
-	\end{enumerate}
-	\item Scraping
-		\begin{enumerate}
-			\item wget
-			\item headless browser/Selenium
-			\item Beautifulsoup/rvest
-			\item APIs (httr)
-			\item Wayback Machine
-		\end{enumerate}
-	\item Pre-processing
-		\begin{enumerate}
-			\item Determining document filetype
-			\item File conversion
-			\item Conventional preprocessing (lowercase, numbers, punctuation)
-			\item Stemming and lemmatization
-			\item spellchecking
-			\item Dealing with duplicate text \& html documents in particular
-		\end{enumerate}
-	\item Analysis
-		\begin{enumerate}
-			\item LDA
-			\item Other topic models (structural, author, dynamic -- maybe?)
-			\item SVM (+ other machine learning classifiers?)
-			\item Fightin Words
-		\end{enumerate}
-\end{enumerate}
+Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
+The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites [CITE].
+Despite the potential for automated scraping of website contents, the conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
+Though highly accurate, the manual approach to data collection is costly, and cannot be scaled to capture even a fraction of the volume of content available on government websites.
+In this paper we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis.
+We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in Indiana and Louisiana correlate with the partisanship of the city mayor.
+
+Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website [CITE], raw website downloads have to be processed significantly before the files are adequately prepared for text analysis.
+We describe and provide solutions to two central challenges in automatically gathering and analyzing website textual contents.
+First, plain text must be extracted from the files.
+This involves purging the files of syntax in HTML and other programming languages, and discarding any other character encoding errors that result from reading the files.
+This challenge would arise in any context in which researchers sought to study the textual contents of websites, and is not unique to comparative analysis of government websites.
+The second challenge we address in our methodological pipeline is, however, specific to the research objective of comparing websites on the basis of a common lexicon.
+For any two governments, the textual signatures that most dramatically differentiate the textual contents of their websites consist of what we can call ``boilerplate'' text---header, footer, or other titling text that is designed to identify the website as being associated with a specific government entity (e.g., ``Welcome to the city of Santa Cruz'', ``The City of Los Angeles welcomes you'').
+This boilerplate text is replicated across many files that are associated with a government's website, but it provides little information regarding the form and/or function of the government.
+The second methodological innovation we offer in our pipeline is designed to minimize the impact of this boilerplate text on the comparative analysis of government website content.
+
+Government websites provide information about how public policies shape the lives of local residents, and how local residents can engage with government to shape public policy.
+As such, government websites reflect both the results of, and inputs to, the political leadership in the city.
+In our illustrative application we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
+A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including [CITE], [CITE], [CITE].
+We study whether significant differences between city governments based on mayoral partisanship are reflected in the contents of city websites.
 
@@
 \end{document}
+
+\begin{enumerate}
+	\item Design
+	\begin{enumerate}
+		\item Choosing the sample
+		\item Finding URLs
+		\item list of .gov websites
+		\item Finding supporting data
+	\end{enumerate}
+	\item Scraping
+		\begin{enumerate}
+			\item wget
+			\item headless browser/Selenium
+			\item Beautifulsoup/rvest
+			\item APIs (httr)
+			\item Wayback Machine
+		\end{enumerate}
+	\item Pre-processing
+		\begin{enumerate}
+			\item Determining document filetype
+			\item File conversion
+			\item Conventional preprocessing (lowercase, numbers, punctuation)
+			\item Stemming and lemmatization
+			\item spellchecking
+			\item Dealing with duplicate text \& html documents in particular
+		\end{enumerate}
+	\item Analysis
+		\begin{enumerate}
+			\item LDA
+			\item Other topic models (structural, author, dynamic -- maybe?)
+			\item SVM (+ other machine learning classifiers?)
+			\item Fightin Words
+		\end{enumerate}
+\end{enumerate}

### 2017-12-18 paper/manuscript.tex
re-ordering sections
reorganized into a basic paper structure

@@
 A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including [CITE], [CITE], [CITE].
+Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public [CITE].
 We study whether significant differences between city governments based on mayoral partisanship are reflected in the contents of city websites.
 
-\section{Background}
+\section{Background: The Study of Government Websites}
 
@@
 For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''
+
+\textbf{Why does the content of city websites matter?} According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
+Official city websites allow mayors to do all three.
+Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate.
+In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents.
+Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
+City websites present an opportunity for local officials to brandish these accomplishments.
+Finally, they also give mayors a platform from which they can advertise their political beliefs.
+On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
+As noted by \cite{Einstein2015a}, there are stark differences in the spending preferences of Democratic and Republican mayors.
+City websites can then be used to communicate the stance of a mayor on social or economic programs.
+Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
+
+In addition to the use of city websites for the politicians that control them, variance in content also matters  with regard to the people who visit them.
+Local residents likely rely on city websites to get news about events, hot-button political issues specific to their city, contact city officials or find out addresses or opening hours of city institutions.
+Visitors use city websites to look up local attractions, which are often described in great detail.
+Similarly, prospective residents looking to move, might rely on city websites to inform their decision on whether to relocate there.
+An inviting website emphasizing the city's receptiveness to new residents might make a real difference here.
+Finally, city websites frequently feature sections on business, but there is a lot of variance in this area: Some emphasize economic development, properties, or transportation, whereas others focus on undeveloped land and other business opportunities.
+Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.
+
+The literature making use of scraped websites clusters into a number of categories.
+One, and most pertinent to our own endeavors, the e-governance literature which discusses the online presence of governments from a usability and public service point of view.
+For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep{Urban2002,Armstrong2011,Feeney2017}.
+As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
+To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated.
+The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
+Like most e-government studies however, this publication does not make any use of automated text analysis.
+
+Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
+\cite{Lin2011} provide a good example for a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
+The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased.
+Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
+
+Another well-known example fitting into this area of study is the set of studies conducted by King et al.
+\citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere.
+However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.
+
+The websites of politicians and their parties have also fallen under scholarly scrutiny.
+Researchers have found that in order to identify the constituencies, motives and modes of communication of these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+\cite{Druckman2009,Druckman2010} rely on the Mational Journal to find the websites, then hand-coded them.
+\cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, the webservice of the Internet Archive we discussed recently.
+\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
+\cite{Therriault2010} (a working paper) actually portends to use automated text analysis, and also has the most extensive overview of the associated methodology.
+However, the division of the website into sections (home page, topics, issues, details) is done by hand, and the actual analysis is incomplete.
+The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).
+
+Importantly for us, research analyzing and improving the scraping, pre-processing and analysis methods of this literature is scarce.
+\cite{Eschenfelder2002} provide something of an overview of how how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
+
+\section{Running Application: Party Differences in Municipal Websites}
 
@@
 
-\textbf{Why does the content of city websites matter?} According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
-Official city websites allow mayors to do all three.
-Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate.
-In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents.
-Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
-City websites present an opportunity for local officials to brandish these accomplishments.
-Finally, they also give mayors a platform from which they can advertise their political beliefs.
-On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
-As noted by \cite{Einstein2015a}, there are stark differences in the spending preferences of Democratic and Republican mayors.
-City websites can then be used to communicate the stance of a mayor on social or economic programs.
-Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
-
-In addition to the use of city websites for the politicians that control them, variance in content also matters  with regard to the people who visit them.
-Local residents likely rely on city websites to get news about events, hot-button political issues specific to their city, contact city officials or find out addresses or opening hours of city institutions.
-Visitors use city websites to look up local attractions, which are often described in great detail.
-Similarly, prospective residents looking to move, might rely on city websites to inform their decision on whether to relocate there.
-An inviting website emphasizing the city's receptiveness to new residents might make a real difference here.
-Finally, city websites frequently feature sections on business, but there is a lot of variance in this area: Some emphasize economic development, properties, or transportation, whereas others focus on undeveloped land and other business opportunities.
-Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.
-
-\subsection*{Website Analysis}
-The literature making use of scraped websites clusters into a number of categories.
-One, and most pertinent to our own endeavors, the e-governance literature which discusses the online presence of governments from a usability and public service point of view.
-For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep{Urban2002,Armstrong2011,Feeney2017}.
-As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
-To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated.
-The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
-Like most e-government studies however, this publication does not make any use of automated text analysis.
-
-Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
-\cite{Lin2011} provide a good example for a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
-The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased.
-Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
-
-Another well-known example fitting into this area of study is the set of studies conducted by King et al.
-\citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere.
-However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.
-
-The websites of politicians and their parties have also fallen under scholarly scrutiny.
-Researchers have found that in order to identify the constituencies, motives and modes of communication of these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-\cite{Druckman2009,Druckman2010} rely on the Mational Journal to find the websites, then hand-coded them.
-\cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, the webservice of the Internet Archive we discussed recently.
-\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
-\cite{Therriault2010} (a working paper) actually portends to use automated text analysis, and also has the most extensive overview of the associated methodology.
-However, the division of the website into sections (home page, topics, issues, details) is done by hand, and the actual analysis is incomplete.
-The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).
-
-Importantly for us, research analyzing and improving the scraping, pre-processing and analysis methods of this literature is scarce.
-\cite{Eschenfelder2002} provide something of an overview of how how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
-
-\section{Data}
+\subsection{Data}
 The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
@@
 
+It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
+
+\begin{enumerate}
+
+\item For what percentage and number of IN cities can we find data from the WBM?
+\item For how many election cycles can we find political leadership data for these matched cities?
+\item In what number and percentage of cities is the local leadership majority Republican? 
+\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
+
+\end{enumerate}
+
+\begin{enumerate}
+
+	\item 30 cities, with a combined population of 1,180,435.
+However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
+	\item 2015, 2011, 2007, 2003.
+	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
+	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
+
+\end{enumerate}
+
 \input{tables/filetypes.tex}
@@
 
-\section{Preprocessing}
+\section{The Web to Text Pipeline}
+
+In the methodological pipeline from native website files to text data that is appropriate for comparative analysis we address two methodological challenges.
+First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
+Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
+The first step in the methodological pipeline is aimed simply at extracting clean plain text from this heterogeneous file base.
+The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another, but is uninformative regarding policy or process differences between governments.
+We describe these methodological steps in this section.
+
+\subsection{Site to Text Conversion}
 
@@
 In other words, the signal would be drowned out by the noise.
-Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
-We count how many times each line is duplicated for that city.
-We remove any line occuring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times, or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
 Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
@@
 
-\subsection{Indiana City Websites}
-
-It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
-
-\begin{enumerate}
-
-\item For what percentage and number of IN cities can we find data from the WBM?
-\item For how many election cycles can we find political leadership data for these matched cities?
-\item In what number and percentage of cities is the local leadership majority Republican? 
-\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
-
-\end{enumerate}
-
-\begin{enumerate}
-
-	\item 30 cities, with a combined population of 1,180,435.
-However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
-	\item 2015, 2011, 2007, 2003.
-	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
-	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
-
+\subsection{Boilerplate Removal}
+
+Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
+We count how many times each line is duplicated for that city.
+We remove any line occuring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times, or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
+
+\section{Bag-of-Words Text Analysis}
+
+\subsection{Topic modeling}
+Note: this chapter is mostly a wordy and less coherent version of the above.
+
+We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas.
+Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order.
+Documents uploaded to city websites are expected to be a reflection of these preferences.
+
+The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model.
+However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics.
+There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.
+
+The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents.
+Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates.
+In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards).
+Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website.
+Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.
+Further demographic as well as economic data might also be useful to differentiate cities from one another.
+If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.
+
+The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences.
+Unfortunately, we have two types of 'authors' - cities, and parties.
+Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author.
+This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents.
+(Note: In the papers on author-topic models, the intention is often to analyze scientific articles.
+These articles are often co-authored.
+Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)
+
+The critical element in this analysis is to accurately attribute authorship of documents to either party.
+Despite possible changes to websites due to a leadership transition, large parts of the content carry over.
+This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
+But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
+{\em  This is a very important point for municipal websites.
+We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added.
+}
+
+Labeling newly added documents after a change of power is quite simple.
+As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption.
+However, we could, and probably should test how long documents tend to stay on a city website.
+Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient.
+If we want to be really fancy about it, we could create a duration model, with document topics as features.
+This would allow us to measure whether some documents tend to remain longer based on their topic (i.e.
+fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.
+
+If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words.
+After that, we run the actual model.
+This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface.
+It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins.
+'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website.
+Hence, these websites should be filled with purely administrative content.
+
+The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e.
+the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.
+
+Another intervening factor is that for cities in Indiana, mayoral terms begin in January.
+Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year.
+Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity.
+We can test for this by comparing election years to non-election years.
+Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.
+
+Furthermore, if we only investigate cities in which control of government changes from one party to another, we may overestimate its effect.
+Not only does a transition in party control occur, but the person in charge also changes.
+Parties are fairly homogeneous, so that two mayors from the same party may have very different policy preferences and managerial styles.
+To remedy this problem, we [could] utilize matching, pairing our cases with similar cities in which the incumbent does not run for re-election, but party control stays the same nevertheless.
+
+%Justicifcation for Arun 2010 topic number measure
+In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}.
+In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix.
+We find 200 topics to be the best value (see figure \ref{ldatuning}).
+
+%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
+This way, we could identify directly which issues are considered to be the most divisive.
+
+%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
+
+%Traditional author models that rely on lexical or syntactic differences may also be of use.
+Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles.
+However, it seems likely that personal rather than partisan authorship is playing an even larger role here.
+
+%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
+As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
+Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
+In a way, this captures the data-generating process more closely.
+
+%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
+One assumes that multiple authors write one document.
+This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
+This is not as good of a fit for city governments however.
+Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
+For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+
+
+%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
+If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
+The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
+Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.
+
+\begin{figure}[!ht]
+	\centering
+	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
+	\label{snapshots}
+	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
+\end{figure}
+
+%\begin{figure}[!ht]
+%	\centering
+	%\caption{Population coverage}
+%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
+%\end{figure}
+
+%\begin{figure}[!ht]
+%	\centering
+	%\caption{Population coverage}
+%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
+%\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	%\caption{Population coverage}
+	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
+\end{figure}
+
+%topicweights density
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
+	\label{doctopics_density}
+	\includegraphics[width=\linewidth]{figures/doctopics_density_IN.pdf}
+\end{figure}
+
+\subsubsection{LDA diagnostics}
+
+Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic.
+Distributions with lower peaks near zero and flatter bodies indicate a topic that is present to varying degrees in multiple documents.
+This shape appears to be more common in documents from Republican cities.
+By contrast, a distribution with a high peak near zero and a very long tail is indicative of a topic that only appears in one specific document.
+This appears to be more common for documents in Democratic cities.
+The substantive conclusion then is that Democrats appear to be more prone to dedicating individual documents to one specific purpose, whereas Republicans produce general-purpose documents more often.
+
+%topicweights density
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
+	\label{topicweights_density}
+	\includegraphics[width=\linewidth]{figures/topicweights_density_IN.pdf}
+\end{figure}
+
+An alternative way to consider topic weights is to aggregate them across documents, in this case through their median or mean.
+Figure \ref{topicweights_density} shows this distribution of topic weights across topics.
+Most topics have a very low weight - meaning that they do not appear in a lot of documents.
+When aggregating across documents via the mean, this effect is more pronounced for Republicans, suggesting that most topics do not feature frequently (or even at all) in their documents.
+Democrats on the other hand appear to have a wider spectrum of topics from which they chose - supporting the hypothesis of Democrats as a 'big tent' party.
+However, this effect is reversed when using the median instead of the mean to aggregate across documents.
+Now, the the distribution has a higher peak and lower tail for Democrats.
+The cause for this stark divergence appears to lie in the fact the mean and median differ enormously - for the range displayed here, the mean is about a hundred times greater.
+Evidently, extremely large weights (i.e.
+some documents fitting specific topics perfectly) distort the picture.
+The median document is a better representation of the corpus as a whole, but the results do not fit our hypothesis.
+Their are however more consistent with figure \ref{topicweights_density}.
+
+Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us.
+To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}.
+For the most part, differences are small.
+For a few topics however, a contrasts emerges.
+
+%size of the differences
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences (Indiana).}
+	\label{diffsize}
+	\includegraphics[width=\linewidth]{figures/diffsize_IN.pdf}
+\end{figure}
+
+Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences.
+Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged.
+For the most part however, these topics focus on administrative matters.
+
+%word topic probabilities for topics with big differences
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences}
+	\label{plotWTP_bigdiffs}
+	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs_IN.pdf}
+\end{figure}
+
+To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences.
+It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.
+
+%word topic probabilities for topics with big differences
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences}
+	\label{doctopics_density_bigdiffs}
+	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs_IN.pdf}
+\end{figure}
+
+To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps.
+Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents.
+Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else.
+One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.
+
+\subsubsection{Structural topic model}
+An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
+This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
+However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
+Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
+Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
+The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
+Interestingly the same is true for a number of the cities as well.
+The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
+
+%\subsubsection{Prediction with SVM}
+%An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
+Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
+Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
+However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
+Instead, we ranked the features according to tf-idf and selected the top 5000.
+These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
+Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
+Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
+
+%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
+\subsection{Informative Dirichlet model}
+However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
+Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}.
+This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
+Figure \ref{fightinwordsIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
+For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly.
+Similarly, 'federal' 'funds' also appear among the Democratic top words.
+By contrast Republicans prefer to devote their attentions to purely local, and for the most part, logistic matters.
+'Trees', 'water', 'street' and 'sign' appear on the list of Republican top words, suggesting that these mayors largely focus on city planning.
+
+These top words also show some degree of overlap with those determined by aggregating over topics in LDA.
+
+%Heatmaps
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
+	\label{heatmaps_weights}
+	\includegraphics[width=\linewidth]{figures/heatmaps_weights_IN.png}
+\end{figure}
+
+%Heatmaps with no duplicate line removal (threshold set at 999999999)
+%also, since the duplicate line removal didn't get rid of as much crap,
+%it was necessary to remove non [A-Za-z] characters before hunspell
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana). No duplicate line removal.}
+	\label{heatmaps_weights}
+	\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
+\end{figure}
+
+%Number of topics vs. tophic coherence
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
+	\label{numtopics_coherence}
+	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
+\end{figure}
+
+%Indiana map
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Cities in the corpus, by partisanship of mayor.}
+	\label{indiana_map}
+	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
+\end{figure}
+
+%partisan topics
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{The most partisan topics.
+The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
+	\label{partisan_topics}
+	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
+\end{figure}
+
+%ldatuning
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{The optimal number of topics for our corpus.
+The measures of Griffths 2004 and Cao 2009 indicate the best number of topics at their minimum, whereas the measure of Arun 2010 points to the best value at its maximum.}
+	\label{ldatuning}
+	\includegraphics[height=0.75\textheight]{figures/topicnumber_ldatuning.pdf}
+\end{figure}
+
+%stm results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
+This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
+	\label{stm_results}
+%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
+\end{figure}
+
+%fightin words results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
+	\label{fightinwordsIN}
+	\includegraphics[width=\linewidth]{figures/fightinWordsIN.png}
+\end{figure}
+
+%fightin words results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
+	\label{fightinwordsLA}
+	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
+\end{figure}
+
+%Partisan top words - topic model Indiana
+\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
+
+%Partisan top words - topic model Louisiana
+\input{tables/partisanTopWordsLA.tex} %tabLDALA
+
+%Partisan top words - fightin words Indiana
+\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
+
+%Partisan top words - fightin words Louisiana
+\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
+
+%Partisan top words - stm Indiana
+%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
+
+%Partisan top words - stm Louisiana
+%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
+
+%Partisan top words - stm Louisiana -- Rep
+\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
+
+%Partisan top words - stm Louisiana -- Dem
+\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
+
+%Partisan top words - stm Louisiana -- Rep
+\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
+
+%Partisan top words - stm Louisiana -- Dem
+\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
+
+%Some basic descriptive statistics of documents by party
+\input{tables/descriptiveStatisticsPartisanIN.tex}
+
+%Some basic descriptive statistics of documents by party
+\input{tables/descriptiveStatisticsPartisanLA.tex}
+
+%fightin words results
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
+	\label{linesCutoff}
+	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Hierarchical clustering (Indiana).}
+	\label{hclustIN}
+	\includegraphics[width=\linewidth]{figures/clusteringIN.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Hierarchical clustering (Louisiana).}
+	\label{hclustLA}
+	\includegraphics[width=\linewidth]{figures/clusteringLA.png}
+\end{figure}
+
+%Entropy by cutoff
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Entropy (between cities, for each topic).}
+	\label{cutoffEntropy}
+	\includegraphics[width=\linewidth]{figures/CutoffCityEntropy.pdf}
+\end{figure}
+
+%Weighted entropy by cutoff
+\begin{figure}[!ht]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Weighted (multiplied by tokens assigned to the topic) entropy (between cities, for each topic).}
+	\label{cutoffEntropy}
+	\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity10}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_10.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity20}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_20.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity30}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_30.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity40}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_40.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity50}
+	\includegraphics[width=\linewidth]{figures/heatmap_hclust_50.png}
+\end{figure}
+
+%Clustering
+\begin{figure}[!ht]
+	\centering
+	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
+	\label{hclustCity100}
+	\includegraphics[height = 1.2\textheight]{figures/heatmap_hclust_100.png}
+\end{figure}
+
+\section{Conclusion}
+
+We have developed a methodological pipleine for automatically gathering and preparing government websites for comparative analysis.
+This methodology holds the potential to vastly scale up the data collection efforts underpinning the rapidly growing body of research that is focused on government website analysis.
+Through an application to the analysis of municipal websites in Indiana and Louisiana, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
+
+\newpage
+
+\bibliographystyle{apsr} % apsr stopped working for me
+%\bibliographystyle{plainnat}
+\bibliography{ref}
+
+\end{document}
+
+\begin{enumerate}
+	\item Design
+	\begin{enumerate}
+		\item Choosing the sample
+		\item Finding URLs
+		\item list of .gov websites
+		\item Finding supporting data
+	\end{enumerate}
+	\item Scraping
+		\begin{enumerate}
+			\item wget
+			\item headless browser/Selenium
+			\item Beautifulsoup/rvest
+			\item APIs (httr)
+			\item Wayback Machine
+		\end{enumerate}
+	\item Pre-processing
+		\begin{enumerate}
+			\item Determining document filetype
+			\item File conversion
+			\item Conventional preprocessing (lowercase, numbers, punctuation)
+			\item Stemming and lemmatization
+			\item spellchecking
+			\item Dealing with duplicate text \& html documents in particular
+		\end{enumerate}
+	\item Analysis
+		\begin{enumerate}
+			\item LDA
+			\item Other topic models (structural, author, dynamic -- maybe?)
+			\item SVM (+ other machine learning classifiers?)
+			\item Fightin Words
+		\end{enumerate}
 \end{enumerate}
@@
 \end{equation}
-
-\subsection{Topic modeling}
-Note: this chapter is mostly a wordy and less coherent version of the above.
-
-We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas.
-Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order.
-Documents uploaded to city websites are expected to be a reflection of these preferences.
-
-The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model.
-However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics.
-There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.
-
-The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents.
-Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates.
-In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards).
-Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website.
-Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.
-Further demographic as well as economic data might also be useful to differentiate cities from one another.
-If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.
-
-The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences.
-Unfortunately, we have two types of 'authors' - cities, and parties.
-Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author.
-This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents.
-(Note: In the papers on author-topic models, the intention is often to analyze scientific articles.
-These articles are often co-authored.
-Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)
-
-The critical element in this analysis is to accurately attribute authorship of documents to either party.
-Despite possible changes to websites due to a leadership transition, large parts of the content carry over.
-This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
-But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
-{\em  This is a very important point for municipal websites.
-We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added.
-}
-
-Labeling newly added documents after a change of power is quite simple.
-As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption.
-However, we could, and probably should test how long documents tend to stay on a city website.
-Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient.
-If we want to be really fancy about it, we could create a duration model, with document topics as features.
-This would allow us to measure whether some documents tend to remain longer based on their topic (i.e.
-fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.
-
-If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words.
-After that, we run the actual model.
-This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface.
-It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins.
-'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website.
-Hence, these websites should be filled with purely administrative content.
-
-The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e.
-the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.
-
-Another intervening factor is that for cities in Indiana, mayoral terms begin in January.
-Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year.
-Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity.
-We can test for this by comparing election years to non-election years.
-Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.
-
-Furthermore, if we only investigate cities in which control of government changes from one party to another, we may overestimate its effect.
-Not only does a transition in party control occur, but the person in charge also changes.
-Parties are fairly homogeneous, so that two mayors from the same party may have very different policy preferences and managerial styles.
-To remedy this problem, we [could] utilize matching, pairing our cases with similar cities in which the incumbent does not run for re-election, but party control stays the same nevertheless.
-
-%Justicifcation for Arun 2010 topic number measure
-In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}.
-In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix.
-We find 200 topics to be the best value (see figure \ref{ldatuning}).
-
-%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
-This way, we could identify directly which issues are considered to be the most divisive.
-
-%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
-
-%Traditional author models that rely on lexical or syntactic differences may also be of use.
-Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles.
-However, it seems likely that personal rather than partisan authorship is playing an even larger role here.
-
-%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
-As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
-Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
-In a way, this captures the data-generating process more closely.
-
-%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
-One assumes that multiple authors write one document.
-This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
-This is not as good of a fit for city governments however.
-Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
-For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+
-
-%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
-If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
-The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
-Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.
-
-\begin{figure}[!ht]
-	\centering
-	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
-	\label{snapshots}
-	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
-\end{figure}
-
-%\begin{figure}[!ht]
-%	\centering
-	%\caption{Population coverage}
-%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
-%\end{figure}
-
-%\begin{figure}[!ht]
-%	\centering
-	%\caption{Population coverage}
-%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
-%\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
-\end{figure}
-
-%topicweights density
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
-	\label{doctopics_density}
-	\includegraphics[width=\linewidth]{figures/doctopics_density_IN.pdf}
-\end{figure}
-
-\subsubsection{LDA diagnostics}
-
-Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic.
-Distributions with lower peaks near zero and flatter bodies indicate a topic that is present to varying degrees in multiple documents.
-This shape appears to be more common in documents from Republican cities.
-By contrast, a distribution with a high peak near zero and a very long tail is indicative of a topic that only appears in one specific document.
-This appears to be more common for documents in Democratic cities.
-The substantive conclusion then is that Democrats appear to be more prone to dedicating individual documents to one specific purpose, whereas Republicans produce general-purpose documents more often.
-
-%topicweights density
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
-	\label{topicweights_density}
-	\includegraphics[width=\linewidth]{figures/topicweights_density_IN.pdf}
-\end{figure}
-
-An alternative way to consider topic weights is to aggregate them across documents, in this case through their median or mean.
-Figure \ref{topicweights_density} shows this distribution of topic weights across topics.
-Most topics have a very low weight - meaning that they do not appear in a lot of documents.
-When aggregating across documents via the mean, this effect is more pronounced for Republicans, suggesting that most topics do not feature frequently (or even at all) in their documents.
-Democrats on the other hand appear to have a wider spectrum of topics from which they chose - supporting the hypothesis of Democrats as a 'big tent' party.
-However, this effect is reversed when using the median instead of the mean to aggregate across documents.
-Now, the the distribution has a higher peak and lower tail for Democrats.
-The cause for this stark divergence appears to lie in the fact the mean and median differ enormously - for the range displayed here, the mean is about a hundred times greater.
-Evidently, extremely large weights (i.e.
-some documents fitting specific topics perfectly) distort the picture.
-The median document is a better representation of the corpus as a whole, but the results do not fit our hypothesis.
-Their are however more consistent with figure \ref{topicweights_density}.
-
-Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us.
-To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}.
-For the most part, differences are small.
-For a few topics however, a contrasts emerges.
-
-%size of the differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences (Indiana).}
-	\label{diffsize}
-	\includegraphics[width=\linewidth]{figures/diffsize_IN.pdf}
-\end{figure}
-
-Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences.
-Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged.
-For the most part however, these topics focus on administrative matters.
-
-%word topic probabilities for topics with big differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{plotWTP_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs_IN.pdf}
-\end{figure}
-
-To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences.
-It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.
-
-%word topic probabilities for topics with big differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{doctopics_density_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs_IN.pdf}
-\end{figure}
-
-To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps.
-Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents.
-Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else.
-One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.
-
-\subsubsection{Structural topic model}
-An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
-This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
-However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
-Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
-Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
-The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
-Interestingly the same is true for a number of the cities as well.
-The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
-
-\subsubsection{Prediction with SVM}
-An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
-Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
-Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
-However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
-Instead, we ranked the features according to tf-idf and selected the top 5000.
-These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
-Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
-Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
-
-However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-\subsubsection{Informative Dirichlet model}
-Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}.
-This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Figure \ref{fightinwordsIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
-For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly.
-Similarly, 'federal' 'funds' also appear among the Democratic top words.
-By contrast Republicans prefer to devote their attentions to purely local, and for the most part, logistic matters.
-'Trees', 'water', 'street' and 'sign' appear on the list of Republican top words, suggesting that these mayors largely focus on city planning.
-
-These top words also show some degree of overlap with those determined by aggregating over topics in LDA.
-
-%Heatmaps
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
-	\label{heatmaps_weights}
-	\includegraphics[width=\linewidth]{figures/heatmaps_weights_IN.png}
-\end{figure}
-
-%Heatmaps with no duplicate line removal (threshold set at 999999999)
-%also, since the duplicate line removal didn't get rid of as much crap,
-%it was necessary to remove non [A-Za-z] characters before hunspell
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana). No duplicate line removal.}
-	\label{heatmaps_weights}
-	\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
-\end{figure}
-
-%Number of topics vs. tophic coherence
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
-	\label{numtopics_coherence}
-	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
-\end{figure}
-
-%Indiana map
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Cities in the corpus, by partisanship of mayor.}
-	\label{indiana_map}
-	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
-\end{figure}
-
-%partisan topics
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{The most partisan topics.
-The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
-	\label{partisan_topics}
-	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
-\end{figure}
-
-%ldatuning
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{The optimal number of topics for our corpus.
-The measures of Griffths 2004 and Cao 2009 indicate the best number of topics at their minimum, whereas the measure of Arun 2010 points to the best value at its maximum.}
-	\label{ldatuning}
-	\includegraphics[height=0.75\textheight]{figures/topicnumber_ldatuning.pdf}
-\end{figure}
-
-%stm results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
-This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
-	\label{stm_results}
-%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-\end{figure}
-
-%fightin words results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
-	\label{fightinwordsIN}
-	\includegraphics[width=\linewidth]{figures/fightinWordsIN.png}
-\end{figure}
-
-%fightin words results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
-	\label{fightinwordsLA}
-	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
-\end{figure}
-
-%Partisan top words - topic model Indiana
-\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
-
-%Partisan top words - topic model Louisiana
-\input{tables/partisanTopWordsLA.tex} %tabLDALA
-
-%Partisan top words - fightin words Indiana
-\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
-
-%Partisan top words - fightin words Louisiana
-\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
-
-%Partisan top words - stm Indiana
-%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
-
-%Partisan top words - stm Louisiana
-%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
-
-%Partisan top words - stm Louisiana -- Rep
-\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
-
-%Partisan top words - stm Louisiana -- Dem
-\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
-
-%Partisan top words - stm Louisiana -- Rep
-\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
-
-%Partisan top words - stm Louisiana -- Dem
-\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
-
-%Some basic descriptive statistics of documents by party
-\input{tables/descriptiveStatisticsPartisanIN.tex}
-
-%Some basic descriptive statistics of documents by party
-\input{tables/descriptiveStatisticsPartisanLA.tex}
-
-%fightin words results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
-	\label{linesCutoff}
-	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Hierarchical clustering (Indiana).}
-	\label{hclustIN}
-	\includegraphics[width=\linewidth]{figures/clusteringIN.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Hierarchical clustering (Louisiana).}
-	\label{hclustLA}
-	\includegraphics[width=\linewidth]{figures/clusteringLA.png}
-\end{figure}
-
-%Entropy by cutoff
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Entropy (between cities, for each topic).}
-	\label{cutoffEntropy}
-	\includegraphics[width=\linewidth]{figures/CutoffCityEntropy.pdf}
-\end{figure}
-
-%Weighted entropy by cutoff
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Weighted (multiplied by tokens assigned to the topic) entropy (between cities, for each topic).}
-	\label{cutoffEntropy}
-	\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity10}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_10.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity20}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_20.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity30}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_30.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity40}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_40.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity50}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_50.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity100}
-	\includegraphics[height = 1.2\textheight]{figures/heatmap_hclust_100.png}
-\end{figure}
-
-\newpage
-
-\bibliographystyle{apsr} % apsr stopped working for me
-%\bibliographystyle{plainnat}
-\bibliography{ref}
-
-\end{document}
-
-\begin{enumerate}
-	\item Design
-	\begin{enumerate}
-		\item Choosing the sample
-		\item Finding URLs
-		\item list of .gov websites
-		\item Finding supporting data
-	\end{enumerate}
-	\item Scraping
-		\begin{enumerate}
-			\item wget
-			\item headless browser/Selenium
-			\item Beautifulsoup/rvest
-			\item APIs (httr)
-			\item Wayback Machine
-		\end{enumerate}
-	\item Pre-processing
-		\begin{enumerate}
-			\item Determining document filetype
-			\item File conversion
-			\item Conventional preprocessing (lowercase, numbers, punctuation)
-			\item Stemming and lemmatization
-			\item spellchecking
-			\item Dealing with duplicate text \& html documents in particular
-		\end{enumerate}
-	\item Analysis
-		\begin{enumerate}
-			\item LDA
-			\item Other topic models (structural, author, dynamic -- maybe?)
-			\item SVM (+ other machine learning classifiers?)
-			\item Fightin Words
-		\end{enumerate}
-\end{enumerate}

### 2017-12-18 paper/manuscript.tex
filling out references in the introduction

@@
 Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites [CITE].
+The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g., ][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra}.
 Despite the potential for automated scraping of website contents, the conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
@@
 
-Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website [CITE], raw website downloads have to be processed significantly before the files are adequately prepared for text analysis.
+Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for text analysis.
 We describe and provide solutions to two central challenges in automatically gathering and analyzing website textual contents.
@@
 In our illustrative application we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
-A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including [CITE], [CITE], [CITE].
-Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public [CITE].
+A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
+Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public \citep{sharfstein2017science,kirby2017trump,duarte2017deniable} .
 We study whether significant differences between city governments based on mayoral partisanship are reflected in the contents of city websites.
@@
 On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
-As noted by \cite{Einstein2015a}, there are stark differences in the spending preferences of Democratic and Republican mayors.
+As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors.
 City websites can then be used to communicate the stance of a mayor on social or economic programs.
@@
 	\label{heatmaps_weights}
-	\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
+	%\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
 \end{figure}
@@
 	\label{cutoffEntropy}
-	\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
+	%\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
 \end{figure}

### 2017-12-19 paper/presentation/Markus_SPSA_2018_Presentation.tex
updates to the presentation

@@
 \usepackage{tikz}
+\usepackage{colortbl}
 \usepackage{subfigure}
@@
 \usecolortheme{default}
-\title[]{The effects of transitions of power on the contents of
-	municipal government websites}
+\title[]{Government websites as data: A methodological pipeline for
+collection, processing, and text analysis}
 \author{Markus Neumann \\ Fridolin Linder \\ Bruce Desmarais}
@@
 			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
-			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertframenumber/\inserttotalframenumber}%
+			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}{\insertframenumber}%/\inserttotalframenumber}%
 		\end{beamercolorbox}%
@@
 
-\begin{frame}{Government Websites}
+\begin{frame}{Example Website}
+	\includegraphics[width = \linewidth]{arcadia_water.png}
+\end{frame}
+
+\begin{frame}{Local Government Websites}
 \linespread{1.5}
@@
 
-\begin{frame}{Maps}
+\begin{frame}{Data Overview}
 \begin{figure}
 	\hfill
+	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
+	\hfill
 	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
-	\hfill
-	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
 \end{figure}
@@
 \begin{frame}{The Pipeline}
-	\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
+	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
 \begin{columns}
@@
 	\begin{itemize}
-		\item Scraping URLs
-		\item Browser automation to verify URLs
-		\item Download sites with wget
+		\item Identify URLs
+		\item Verify URLs (browser automation)
+		\item Download websites
 		\item Determine file type
@@
 		\item To lowercase
-		\item Duplicate content removal
+		\item Boilerplate removal
 		\item Spellchecking
-		\item Lemmatization
+		\item Lemmatization \\ (city \& cities = city)
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Hierarchical clustering
+		%\item Hierarchical clustering
 		\item Fightin' Words
-		\item Topic models
-		\begin{itemize}
-			\item LDA
-			\item STM
-		\end{itemize}
+		\item Structural topic model
+		%\begin{itemize}
+		%	\item LDA
+		%	\item STM
+		%\end{itemize}
 	\end{itemize}
@@
 \begin{frame}{The Pipeline}
-\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
+	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
 	\begin{columns}
@@
 		\begin{itemize}
-		\item Scraping URLs
-		\item Browser automation to verify URLs
-		\item Download sites with wget
+			\item Identify URLs
+			\item Verify URLs (browser automation)
+			\item Download websites
 			\item Determine file type
@@
 			\item To lowercase
-		\item \textbf{Duplicate content removal}
+			\item \textbf{Boilerplate removal}
 			\item Spellchecking
-		\item Lemmatization
+			\item Lemmatization \\ (city \& cities = city)
 		\end{itemize}
@@
 		\begin{itemize}
-		\item Hierarchical clustering
+			%\item Hierarchical clustering
 			\item Fightin' Words
-		\item Topic models
-		\begin{itemize}
-			\item LDA
-			\item STM
-		\end{itemize}
+			\item Structural topic model
+			%\begin{itemize}
+			%	\item LDA
+			%	\item STM
+			%\end{itemize}
 		\end{itemize}
@@
 
-\begin{frame}{Duplicate Content Removal}
+\begin{frame}{Boilerplate Removal}
 \includegraphics[width = \linewidth]{arcadia_water.png}
@@
 
-\begin{frame}{Duplicate Content Removal}
+\begin{frame}{Boilerplate Removal}
 \includegraphics[width = \linewidth]{duplicateLines.png}
@@
 
-\begin{frame}{Duplicate Content Removal}
+\begin{frame}{Boilerplate Removal}
 	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
@@
 
-\begin{frame}{Duplicate Content Removal}
+\begin{frame}{Boilerplate Removal}
 \begin{itemize}
 	\item Within each city, there is a lot of shared text
-	\begin{itemize}
-		\item Boilerplate
-		\item Website elements
-	\end{itemize}
 	\item If not removed, the text clusters into cities
@@
 	\item Remove a line if it is duplicated within a city above some threshold
-	\item Hash tables for computational efficiency
+	\item Fast \& efficient implementation
 \end{itemize}
@@
 			\item To lowercase
-		\item Duplicate content removal
+			\item Boilerplate removal
 			\item Spellchecking
-		\item Lemmatization
+			\item Lemmatization \\ (city \& cities = city)
 		\end{itemize}
@@
 \section{Analysis}
-\begin{frame}{Hierarchical Clustering}
-\centering
-\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
+%\begin{frame}{Hierarchical Clustering}
+%\centering
+%\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
+%\end{frame}
+
+%\begin{frame}{Fightin' Words}
+%\begin{figure}
+%	\hfill
+%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
+%	\hfill
+%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
+%\end{figure}
+%\end{frame}
+
+\begin{frame}{Fightin' Words}
+	\input{fightinwordsIN.tex} %../tables/stmTopWordsINDem.tex
 \end{frame}
 
-\begin{frame}{Fightin' Words}
-\begin{figure}
-	\hfill
-	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
-	\hfill
-	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Latent Dirichlet Allocation}
-
-\input{partisanTopWords.tex}
-
-\end{frame}
+%\begin{frame}{Latent Dirichlet Allocation}
+%\input{partisanTopWords.tex}
+%\end{frame}
 
@@
 \begin{frame}{Conclusion}
-%\linespread{1.5}
+\linespread{1.5}
 \large
 \begin{itemize}
-	\item Hierarchical clustering only creates 'topics' if content is VERY similar
-	\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
-	\item LDA is sensitive to preprocessing, but the most flexible
-	\item STM works too, but also very sensitive to duplicate content
+	%\item Hierarchical clustering only creates 'topics' if content is VERY similar
+	%\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
+	%\item LDA is sensitive to preprocessing, but the most flexible
+	%\item STM works too, but also very sensitive to duplicate content
+	\item Manual vs. automatic analysis of government websites
+	\item Our pipeline facilities scalable comparative analysis
+
 	\vspace{5mm}
-	\item Democrats focus on raising and spending money, Republicans on infrastructure and basic utilities
+	\item Partisanship affects website content:
+	\item Democrats focus on raising and spending money
+	\item Republicans focus on infrastructure and utilities
 \end{itemize}

### 2017-12-19 paper/presentation/stmTopWordsINDem.tex
updates to the presentation

@@
+%\usepackage[table]{xcolor}
 % latex table generated in R 3.4.2 by xtable 1.8-2 package
@@
   \hline
-fort & propos & said & prosecutor & digest & fund \\ 
-  citi & author & ask & charg & introduc & grant \\ 
-  ordin & district & state & feloni & author & budget \\ 
+fort & propos & said & prosecutor & digest & \cellcolor{blue!25} fund \\ 
+  citi & author & ask & charg & introduc & \cellcolor{blue!25} grant \\ 
+  ordin & district & state & feloni & author & \cellcolor{blue!25} budget \\ 
   approv & street & will & counti & counti & counti \\ 
-  purchas & public & chair & case & appoint & state \\ 
+  \cellcolor{blue!25} purchas & public & chair & case & appoint & state \\ 
   depart & control & propos & crime & board & feder \\ 
@@
   will & intersect & move & offic & district & appropri \\ 
-  resolut & counti & need & victim & fund & increas  \\ 
+  resolut & counti & need & victim & \cellcolor{blue!25} fund & increas  \\ 
   contract & committe & council & sentenc & street & agenc \\ 

### 2017-12-19 paper/presentation/stmTopWordsINRep.tex
updates to the presentation

@@
   \hline
-motion & plan & inc & request & council & traffic \\ 
-  second & zone & electr & board & citi & amp \\ 
+motion & plan & inc & request & council & \cellcolor{red!25} traffic \\ 
+  second & \cellcolor{red!25} zone & electr & board & citi & amp \\ 
   made & applic & build & member & ordin & vehicl \\ 
-  approv & properti & construct & servic & common & stop \\ 
-  mayor & approv & home & street & councilor & sign \\ 
-  present & sign & street & approv & amend & road \\ 
-  state & site & meridian & purchas & resolut & block \\ 
+  approv & \cellcolor{red!25} properti & construct & servic & common & stop \\ 
+  mayor & approv & home & \cellcolor{red!25} street & councilor & sign \\ 
+  present & sign & street & approv & amend & \cellcolor{red!25} road \\ 
+  state & \cellcolor{red!25} site & meridian & purchas & resolut & block \\ 
   will & locat & servic & citi & adopt & signal \\ 
-  citi & commiss & west & move & wherea & street \\ 
+  citi & commiss & west & move & wherea & \cellcolor{red!25} street \\ 
   council & file & main & good & approv & driver \\ 

### 2017-12-25 paper/tables/stmTopWordsLADem.tex
LA is finally working completely, results are much better

@@
-% latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Nov 13 18:17:05 2017
+% latex table generated in R 3.4.3 by xtable 1.8-2 package
+% Mon Dec 25 01:20:56 2017
 \begin{table}[ht]
@@
   \hline
--0.144 & -0.077 & -0.039 & -0.02 & -0.018 & -0.015 & -0.012 & -0.011 \\ 
+-0.044 & -0.04 & -0.021 & -0.019 & -0.016 & -0.012 & -0.011 & -0.01 \\ 
   \hline
-stream & obj & otherwis & polic & wherea & type & communiti & art \\ 
-  length & ascent & provid & crime & ordin & content & neighborhood & call \\ 
-  predictor & flag & respect & investig & citi & width & citi & cost \\ 
-  acrobat & descent & thereto & offic & resolut & pdf & program & sponsor \\ 
-  librari & encod & author & arrest & provid & height & public & free \\ 
-  pdf & interpol & citi & inform & code & filter & develop & amp \\ 
-  ash & matrix & district & suspect & street & parent & opportun & music \\ 
-  hum & kid & ordin & victim & shall & count & particip & artist \\ 
-  gym & baa & amend & block & chapter & resourc & creat & museum \\ 
-  parent & filter & locat & street & provis & size & provid & home \\ 
+owner & provide & victim & application & employee & city & revenue & community \\ 
+  applicant & otherwise & crime & motion & policy & ordinance & fund & neighborhood \\ 
+  new & respect & violence & second & city & whereas & tax & district \\ 
+  application & thereto & arrest & street & report & bond & budget & police \\ 
+  per & city & domestic & favor & department & resolution & million & public \\ 
+  exist & authorize & officer & retention & audit & code & total & meeting \\ 
+  build & ordinance & suspect & john & review & provide & year & engagement \\ 
+  proposal & amend & report & arc & management & shall & general & crime \\ 
+  receive & district & child & window & procedure & provision & service & officer \\ 
+  construction & locate & police & heather & work & fund & forecast & department \\ 
    \hline

### 2017-12-25 paper/tables/stmTopWordsLARep.tex
LA is finally working completely, results are much better

@@
-% latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Nov 13 18:17:04 2017
+% latex table generated in R 3.4.3 by xtable 1.8-2 package
+% Mon Dec 25 01:20:56 2017
 \begin{table}[ht]
@@
   \hline
-0.085 & 0.062 & 0.062 & 0.057 & 0.021 & 0.019 & 0.018 & 0.017 \\ 
+0.08 & 0.069 & 0.065 & 0.038 & 0.03 & 0.015 & 0.012 & 0.009 \\ 
   \hline
-event & ordin & citi & flood & west & properti & park & councilman \\ 
-  park & bid & mayor & emerg & north & plan & street & said \\ 
-  inform & summari & said & citi & east & zone & citi & citi \\ 
-  food & amount & year & storm & south & lot & improv & mayor \\ 
-  music & citi & state & resid & traffic & applic & recreat & want \\ 
-  show & depart & announc & weather & boulevard & shall & work & council \\ 
-  visit & public & work & inform & parish & requir & public & just \\ 
-  market & contract & offici & hurrican & drive & approv & repair & think \\ 
-  weekend & approv & resid & disast & road & use & program & vote \\ 
-  begin & accord & million & power & locat & site & includ & thank \\ 
+emergency & call & ordinance & say & say & city & home & school \\ 
+  city & art & bid & city & councilman & mayor & church & program \\ 
+  resident & event & city & new & mayor & council & house & youth \\ 
+  weather & sponsor & summary & make & city & member & building & student \\ 
+  storm & cost & authorize & work & council & board & build & recreation \\ 
+  area & free & resolution & can & ordinance & commission & state & community \\ 
+  official & music & amount & year & budget & director & old & child \\ 
+  hurricane & show & department & take & meeting & office & first & high \\ 
+  work & information & public & get & ask & district & store & city \\ 
+  mayor & feature & contract & one & follow & public & one & center \\ 
    \hline

### 2017-12-25 functions/preprocessing.R

@@ -324,6 +324,11 @@ preprocessing_2 <- function(d){
     return(output)
   }
   
+  ncores <- detectCores() - 1
+  cl <- makeCluster(ncores, type = "FORK")
+  d$doc <- parSapply(cl, d$doc, FUN = tokenLenRemove)
+  stopCluster(cl)
+  
   return(d)
   
 }

### 2017-12-26 paper/tables/stmTopWordsLADem.tex
results for LA (with population in the stm)

@@
 % latex table generated in R 3.4.3 by xtable 1.8-2 package
-% Mon Dec 25 01:20:56 2017
+% Tue Dec 26 15:50:18 2017
 \begin{table}[ht]
@@
   \hline
--0.044 & -0.04 & -0.021 & -0.019 & -0.016 & -0.012 & -0.011 & -0.01 \\ 
+-0.136 & -0.102 & -0.043 & -0.02 & -0.02 & -0.012 & -0.012 & -0.012 \\ 
   \hline
-owner & provide & victim & application & employee & city & revenue & community \\ 
-  applicant & otherwise & crime & motion & policy & ordinance & fund & neighborhood \\ 
-  new & respect & violence & second & city & whereas & tax & district \\ 
-  application & thereto & arrest & street & report & bond & budget & police \\ 
-  per & city & domestic & favor & department & resolution & million & public \\ 
-  exist & authorize & officer & retention & audit & code & total & meeting \\ 
-  build & ordinance & suspect & john & review & provide & year & engagement \\ 
-  proposal & amend & report & arc & management & shall & general & crime \\ 
-  receive & district & child & window & procedure & provision & service & officer \\ 
-  construction & locate & police & heather & work & fund & forecast & department \\ 
+art & otherwise & whereas & water & street & shall & police & event \\ 
+  call & provide & city & main & inc & city & crime & city \\ 
+  cost & respect & ordinance & sewer & drive & agreement & officer & park \\ 
+  home & city & bond & project & construction & party & suspect & rental \\ 
+  sponsor & thereto & provide & infrastructure & permit & provide & arrest & use \\ 
+  church & authorize & resolution & street & service & property & report & hour \\ 
+  amp & ordinance & code & system & avenue & owner & victim & hotel \\ 
+  free & district & chapter & improvement & oak & provision & information & public \\ 
+  museum & amend & shall & remark & park & section & murder & provide \\ 
+  artist & locate & otherwise & phase & lane & agree & block & term \\ 
    \hline

### 2017-12-26 stm.R

@@ -19,7 +19,7 @@ if(exists("stateAbb")==F){
 
 #get the data ready for preprocessing
 docs <- d$doc
-meta <- subset(d, select = c('City', 'Party'))
+meta <- subset(d, select = c('City', 'Party', 'POPESTIMATE'))
 processed <- textProcessor(docs, metadata = meta, 
                            lowercase = F,
                            removestopwords = F, 

### 2017-12-27 paper/tables/stmTopWordsINRep.tex
results for IN (with population in the stm)

@@
-% latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Nov 13 15:36:58 2017
+% latex table generated in R 3.4.3 by xtable 1.8-2 package
+% Tue Dec 26 20:59:22 2017
 \begin{table}[ht]
@@
   \hline
-0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 & 0.015 & 0.014 \\ 
+0.023 & 0.021 & 0.019 & 0.017 & 0.017 & 0.014 & 0.013 & 0.012 \\ 
   \hline
-motion & plan & inc & request & council & traffic & build & inform \\ 
-  second & zone & electr & board & citi & amp & histor & pleas \\ 
-  made & applic & build & member & ordin & vehicl & preserv & will \\ 
-  approv & properti & construct & servic & common & stop & wall & contact \\ 
-  mayor & approv & home & street & councilor & sign & materi & use \\ 
-  present & sign & street & approv & amend & road & paint & can \\ 
-  state & site & meridian & purchas & resolut & block & roof & email \\ 
-  will & locat & servic & citi & adopt & signal & structur & site \\ 
-  citi & commiss & west & move & wherea & street & locat & phone \\ 
-  council & file & main & good & approv & driver & window & card \\ 
+library & foot & team & ave & request & board & amp & building \\ 
+  stream & sign & game & inc & board & meeting & traffic & historic \\ 
+  obj & use & play & cross & member & member & stop & build \\ 
+  length & lot & league & creek & service & committee & vehicle & material \\ 
+  branch & building & camp & construction & street & council & block & preservation \\ 
+  type & zone & class & blvd & approve & commission & sign & wall \\ 
+  flag & area & age & park & city & meet & airport & roof \\ 
+  filter & district & must & lake & purchase & public & ave & window \\ 
+  rim & parking & child & hill & move & director & theft & floor \\ 
+  page & residential & participant & ridge & good & president & signal & new \\ 
    \hline

### 2017-12-27 Indiana.R

@@ -1,4 +1,4 @@
-setwd("govWebsites")
+#setwd("govWebsites")
 
 state <- "Indiana"
 stateAbb <- "IN"

### 2017-12-28 paper/presentation/Markus_SPSA_2018_Presentation.tex
presentation

@@
 \end{figure}
+\end{frame}
+
+\begin{frame}{Data Overview}
+\input{descriptiveStatsIN.tex}
+\input{descriptiveStatsLA.tex}
 \end{frame}
@@
 
-\begin{frame}{Fightin' Words}
-	\input{fightinwordsIN.tex} %../tables/stmTopWordsINDem.tex
+\begin{frame}{Fightin' Words - Monroe et al. (2008)}
+\linespread{1.5}
+\begin{itemize}
+	\item Goal: Split words based on one binary variable (party)
+	\item Find the most Democratic and most Republican words
+	\item Problem: Text mostly consists of meaningless words
+	\item Solution: Set prior based on expected distribution of words in random text
+	\item Method provides a z-Score indicating the degree to which a word is preferred by one party
+	\item Very fast to compute
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Fightin' Words (Indiana)}
+	\input{fightinwordsIN.tex}
+%	\input{../tables/fightinwordsIN.tex}
 \end{frame}
@@
 
-\begin{frame}{Structural Topic Model}
+\begin{frame}{Structural Topic Model - Roberts et al. (2014)}
+\linespread{1.5}
+\begin{itemize}
+	\item Topic models find clusters of semantically related words in texts --> i.e. topics
+	\item As a clustering method, LDA doesn't explicitly allow for covariates (although post-hoc comparison is possible)
+	\item The structural topic model extends this approach to explicitly include (multiple) covariates
+	\item Our covariates: Party + City Population
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Structural Topic Model (Indiana)}
 \input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
@@
 
-\begin{frame}{Structural Topic Model}
+\begin{frame}{Structural Topic Model (Indiana)}
 \input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex

### 2017-12-28 presentationDescriptiveStatistics.R

@@ -1,0 +1,51 @@
+library(quanteda)
+library(xtable)
+
+state <- "Indiana"
+stateAbb <- "IN"
+
+state <- "Louisiana"
+stateAbb <- "LA"
+
+load(paste0("rfiles/d_", stateAbb, ".rdata"))
+
+#Number of cities per party
+ncities <- xtabs(~ City + Party, d)
+ncities[ncities!=0] <- 1
+ncities <- colSums(ncities)
+
+#Number of documents per party
+ndocs <- colSums(xtabs(~ City + Party, d))
+
+#Number of token instances and types per party
+crpsD <- corpus(d$doc[d$Party=="Democratic"])
+crpsR <- corpus(d$doc[d$Party=="Republican"])
+dtmD <- dfm(crpsD)
+dtmR <- dfm(crpsR)
+toksD <- tokens(crpsD)
+toksR <- tokens(crpsR)
+ntokenTypesD <- length(types(toksD))
+ntokenTypesR <- length(types(toksR))
+ntokenInstancesD <- length(unlist(toksD))
+ntokenInstancesR <- length(unlist(toksR))
+
+xtab <- matrix(nrow = 4, ncol = 3)
+
+colnames(xtab) <- c("Democratic", "Republican", "Total")
+rownames(xtab) <- c("Cities", "Documents", "Token types", "Token instances")
+
+xtab[1,c(1,2)] <- ncities
+xtab[2,c(1,2)] <- ndocs
+xtab[3,1] <- ntokenTypesD
+xtab[3,2] <- ntokenTypesR
+xtab[4,1] <- ntokenInstancesD
+xtab[4,2] <- ntokenInstancesR
+xtab[,3] <- apply(xtab[,c(1,2)], 1, sum)
+
+crps <- corpus(d$doc)
+toks <- tokens(crps)
+ntokenTypes <- length(types(toks))
+xtab[3,3] <- ntokenTypes
+
+writeLines(print.xtable(xtable(xtab, digits = 0, caption = state)),
+           paste0("paper/presentation/descriptiveStats", stateAbb, ".tex"))

### 2017-12-29 paper/manuscript.tex
updates to the results and preprocessing sections of the manuscript

@@
 Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to total number of tokens is less than 0.15.
-Furthermore, hunspell does not spellcheck individual characters, so we remove all individual characters appearing as tokens except for "i" and "a".
+Furthermore, hunspell does not spellcheck individual characters or two-character words, so we remove these token types entirely (none of these words are of any substantive relevance to our research question).
 Since these pre-processing steps reduce documents which are largely unsuitable to only a few words of texts that don't make much sense, we also remove all remaining documents containing less than 50 tokens.
+Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive to our models while increasing their computational cost, we also discard any token types that occur in only one document.
 
@@
 We remove any line occuring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times, or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
+We implement this algorithm through hash tables, which reduces the computational complexity from O($N^2$) to O($N$).
 
@@
 
+\subsection{Informative Dirichlet model}
+However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
+Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}.
+This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
+Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
+
+In Indiana, Democrats exhibit a preference for words related to public finance, such as 'fund', 'budget', or 'tax', indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
+This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
+Beyond the focus on public finance, the words preferably used by Democrats do not fall into any particularly congruent categories, and largely sort into various areas related to city administration - i.e.
+`council', `services', `budget', `committee', `contract', etc.
+If there is theme around the words preferred by Republicans, it seems to center around city planning - street, fire, water, building, construction, park.
+These words suggest that the hands-off approach favored by Republicans results in a focus on supporting infrastructure and logistics.
+
+%Partisan top words - fightin words Indiana
+\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
+
+For Lousiana, the results (see table \ref{tabFightinLA}) are less coherent.
+Only one of the finance-related terms appears again for Democrats - specifically `fund', although `rate' might also be used in a financial context.
+Beyond that, some focus on a `historic' `'district of a city seems evident, as is the use of some words - `infrastructure', `water', `building' that were used for Republicans in Indiana.
+Conversely, Republicans are now missing these words, and their preferred terms generally do not seem to follow any particular theme.
+
+%Partisan top words - fightin words Louisiana
+\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
+
+The weakness of the fightin' words method is evident here, as a list of words does not necessarily provide sufficient information to glean preferred topics from.
+This is especially the case when the texts are spread across a broad number of issue-areas, with little semantic similarity.
+In \citep{Monroe2008}, the authors focus on the fairly constrained corpus of U.S.
+Senate speeches with respect to abortion - our context, by comparison, is far more eclectic.
+
 \subsubsection{Structural topic model}
-An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
+A more powerful approach with the capacity of addressing this problem is the use of topic models.
+This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics.
+In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}.
+Theoretically, the most widely-used form of topic model, latent dirichlet allocation, can also be used to test for the impact of a single covariate through a post-hoc comparison, but the structural topic model allows for multiple covariates, and also produced more meaningful topics in our experiments.
+
+We use 60 topics - the number recommended by the authors for medium- to large-sized corpora, and party as well as city population (the literature frequently emphasizes city size as a determinant of the issues it faces - see, for example, \cite{Guillamon2013}) as covariates.
+The results are shown in tables \ref{tabSTMINRep} to \ref{tabSTMLADem}.
+The coefficients in the table headers describe the size of the party covariate on a given topic.
+In order to test statistical significance, we calculated credible intervals - the topics shown here are all significant at the 0.1\% level.
+
+In Indiana, some of the topics associated with Democrats - one related to education, one to recycling  - clearly seem to match the party brand.
+Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}.
+However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
+Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Repuiblican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted html, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
+
+When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
+Furthermore, as with the fightin' words approach, some smaller degree of focus on money (see topic 1) is still evident.
+For Republicans, topics 2 to 4 seem to be, once again about infrastructure and utilities, pointing to a certain degree of robustness in these results, as well as the emergence of a trend.
+The results produced by the structural topic model are not flawless, but the two parties do seem to have somewhat consistent themes on which they focus on in both states.
+Furthermore, in comparison to the fightin' words approach, the ability of the structural topic model to form coherent topics is quite evident and helpful in the interpretation of the results.
+
+%An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
 This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
@@
 The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
+
+%Partisan top words - stm Louisiana -- Rep
+\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
+
+%Partisan top words - stm Louisiana -- Dem
+\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
+
+%Partisan top words - stm Louisiana -- Rep
+\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
+
+%Partisan top words - stm Louisiana -- Dem
+\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
 
@@
 
-\subsection{Informative Dirichlet model}
-However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}.
-This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Figure \ref{fightinwordsIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
-For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly.
-Similarly, 'federal' 'funds' also appear among the Democratic top words.
-By contrast Republicans prefer to devote their attentions to purely local, and for the most part, logistic matters.
-'Trees', 'water', 'street' and 'sign' appear on the list of Republican top words, suggesting that these mayors largely focus on city planning.
-
-These top words also show some degree of overlap with those determined by aggregating over topics in LDA.
-
 %Heatmaps
@@
 
-%Partisan top words - fightin words Indiana
-\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
-
-%Partisan top words - fightin words Louisiana
-\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
-
 %Partisan top words - stm Indiana
@@
 %\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
-
-%Partisan top words - stm Louisiana -- Rep
-\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
-
-%Partisan top words - stm Louisiana -- Dem
-\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
-
-%Partisan top words - stm Louisiana -- Rep
-\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
-
-%Partisan top words - stm Louisiana -- Dem
-\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
 
@@
 
-We have developed a methodological pipleine for automatically gathering and preparing government websites for comparative analysis.
+We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative analysis.
 This methodology holds the potential to vastly scale up the data collection efforts underpinning the rapidly growing body of research that is focused on government website analysis.

### 2017-12-30 paper/manuscript.tex
more updates to the presentation and manuscript

@@
 \subsection{Site to Text Conversion}
-
-The documents are read in line by line, converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
+For the most part, the file type of a document can be correctly determined through its ending.
+However, there are exceptions to this, which, if ignored, can lead to large amounts of garbage text, stemming from incorrectly converted documents, as well as a general decrease in the amount of usable data.
+Two issues in particular need to be addressed: One, HTML files on city websites frequently do not have an ending, but are still perfectly readable if correctly identified as such.
+Second, some documents contain the incorrect file ending - for example, we found thousands of documents on the New Orleans city website that ended in .html, when they were actually PDFs.
+To accurately assess their type, we read in the first line of each document, which, if it is an HTML or PDF file, contains a string indicating as much.
+Consequently we rename all documents so that their file ending reflects their actual file type.
+This is strictly necessary, because we rely on the readText R package\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results.} - which determines a document's type solely through its ending - to convert the files to plain text.
+
+The text documents are then read into R line by line, converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
 At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
@@
 In other words, the signal would be drowned out by the noise.
+Our solution to this problem is described in more detail in section \ref{boilerplate}.
 Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
@@
 However, hunspell does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
-Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the english alphabet.
+Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
 Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to total number of tokens is less than 0.15.
@@
 
-\subsection{Boilerplate Removal}
-
+\subsection{Boilerplate Removal}\label{boilerplate}
+As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods.
 Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
@@
 We implement this algorithm through hash tables, which reduces the computational complexity from O($N^2$) to O($N$).
+Before this step is taken, we remove numbers and dates from the documents because they frequently make lines unique, despite the fact that they are virtually the same (for example different days on a city calendar).
 
@@
 \subsection{Informative Dirichlet model}
-However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}.
+%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
+For the analysis of the data, we present two approaches, the first being the informative dirichlet model developed by \citep{Monroe2008}.
 This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning.
+Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them with text with greater semantic, and in our case, partisan meaning.
 

### 2018-01-02 paper/manuscript.tex
finished revisions for SPSA

@@
 Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science.
-Existing research has relied on manual methods of website data collection of processing.
+Existing research has relied on manual methods of website data collection and processing.
 Reliance on manual collection and processing limits the scale and scope of website content analysis.
-We develop a methodological pipeline that researchers can followed in order to gather, process, and analyze website content with established text analysis techniques.
+We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques.
 First, for the acquisition of website data, we cover approaches to automated scraping methods.
@@
 Finally, we illustrate methods of text analysis using automatically gathered and pre-processed website content.
-We illustrate our methodological pipeline through a new and innovative dataset---the websites of local governments in Indiana and Louisiana.
+We illustrate our methodological pipeline through a new and innovative dataset---the websites of municipal governments in Indiana and Louisiana.
 We build upon recent research that analyzes how change and variation in the partisan control of government relates to content made available on the government's website.
@@
 
-\section{Background: The Study of Government Websites}
-
-\cite{grimmelikhuijsen2010transparency} run an experiment in which citizens are exposed to randomly selected levels of information about local government council minutes.
-They find a negative relationship between the information level and perceptions of competence in the local government.
-This raises an interesting question regarding whether citizens or more likely to participate when they perceive competence or when they perceive incompetence.
-
-\cite{wang2005evaluating} present a widely cited `model' for evaluating the accessibility of information on government websites.
-This is an important paper with which we should be familiar at a very detailed level as we use archived web content to assess the volume/accessibility of information provided by local governments.
-
-\cite{osman2014cobra} is less relevant, but they develop a multi-item measure to predict the level of citizen satisfaction with e-government services.
-
-\cite{grimmelikhuijsen2012developing} conduct an enormously relevant study.
+\section{The Significance of Government Website Content}
+% \cite{grimmelikhuijsen2012developing} conduct an enormously relevant study.
 Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study.
@@
 
-\textbf{Why does the content of city websites matter?} According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
+ According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
 Official city websites allow mayors to do all three.
@@
 
-\section{Running Application: Party Differences in Municipal Websites}
-
-\begin{landscape}
-\begin{table}[htbp]
-	%\caption{}
-	\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-		\hline
-		Names & Year & Journal & Findings & Important? \\ \hline
-		Benedictis-Kessner, Justin De
-		Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
-Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
-		Caughey, Devin
-		Warshaw, Christopher
-		Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
-Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
-& Somewhat \\ \hline
-		Einstein, Katherine Levine
-		Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
-aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
-		Einstein, Katherine Levine
-		Glick, David M.
-& 2015 & Working Paper & Survey of 72 mayors.
-Unlike Republican mayors, roughly half of Democrats seem to agree that cities should aim to reduce inequality.
-Democratic mayors also seem to favor redistribution to accomplish that goal.
-& Somewhat \\ \hline
-		Kiewiet, D Roderick
-		Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
-Spending has thus decreased in general.
-Lack of funds means that there is not much discretion for partisanship.
-& Somewhat \\ \hline
-		Tausanovitch, Chris
-		Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
-Partisan elections do not make cities more or less responsive.
-& Yes \\ \hline
-		Guillamón, Ma Dolores
-		Bastida, Francisco
-		Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
-Conservative parties spend more on police.
-Spending is higher before elections.
-Also contains a useful overview of the literature.
-& Yes \\ \hline
-	\end{tabular}
-	\label{}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-	\begin{table}[htbp]
-		%\caption{}
-		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-			\hline
-			Names & Year & Journal & Findings & Important? \\ \hline
-			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
-			Solé-Ollé, Albert
-			Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
-The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
-Partisanship might also affect housing construction and price growth.
-& Yes \\ \hline
-			Gerber, Elisabeth R.
-			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
-			Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
-Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
-Non-partisan elections favor Republicans/upper class.
-Mixed evidence for whether partisanship of mayor is important for policy.
-& Somewhat \\ \hline
-			Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
-spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
-& Somewhat \\ \hline
-			Ferreira, Fernando
-			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
-			Ansolabehere, Stephen
-			Snyder, James M.
-& 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
-The important finding (for us) is the fact that counties whose government is controlled by the same party as the state government, receive more funding (county's share of state transfers, normalized by county pop.) from the state.
-& Somewhat \\ \hline
-			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
-		\end{tabular}
-		\label{}
-	\end{table}
-\end{landscape}
-
-\begin{landscape}
-	\begin{table}[htbp]
-		%\caption{}
-		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-			\hline
-			Names & Year & Journal & Findings & Important? \\ \hline
-			Armstrong, Cory L.
-& 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
-Manual content analysis (undergrads told to look around for 15 minutes).
-School board websites, more professional websites, and websites in Republican-dominated counties are found to be more transparent.
-& Yes \\ \hline
-			Cegarra-Navarro, Juan
-			Pachón, José
-			Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
-Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
-More sophisticated websites are correlated with greater civic engagement and greater use of e-government functions.
-& Yes \\ \hline
-			Dolson, Jordan
-			Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
-Three categories: e-content (city information on website), e-participation, social media use.
-Tables on page 15 show frequencies of these categories across sites, and might be useful to inform our topics.
-Larger cities have better websites.
-Population growth and immigration are also tested, but the findings are somewhat inconclusive.
-& Yes \\ \hline
-			Feeney, Mary K.
-			Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
-city websites at two points in time (2010-2014).
-Count model of website features regarding information, e-services, utilities, transparency and civic engagement.
-Having a larger population leads to more features.
-Relying on a website contractor leads to more information and transparency.
-The authors say that mayor-councils are negatively correlated with website sophistication, but their regression tables state the opposite.
-& Yes \\ \hline
-			Kaylor, Charles
-			Deshazo, Randy
-			Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
-Table 1 lists a number of possible ways this manifests, could be useful for our theory.
-& Somewhat \\ \hline
-			Ansolabehere, Stephen
-			Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
-Is website content correlated with city characteristics?
-Not particularly systematic, and the findings are inconclusive.
-& Somewhat \\ \hline
-			Jeffres, Leo W.
-			Lin, Carolyn A.
-& 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
-Features include information about city, opportunities for citizen feedback, galleries of photos, links, etc.
-Purely descriptive analysis, doesn't contain anything that isn't covered in any of the other aricles.
-& No \\ \hline
-		\end{tabular}
-		\label{}
-	\end{table}
-\end{landscape}
-
-There doesn't seem to be much literature on transitions of party control, if anything, that question is mostly phrased with regard to political representation.
-However, if we want to tie our paper to a larger theory, we could go with dynamic representation.
-Under dynamic representation, policy-makers are responsive to trends in citizens opinions, which mainly manifest/become apparent through election results, especially when incumbents are voted out of office.
-This fits our topic quite well.
-Also, of the few papers that do exist on the effects of partisan transitions, virtually all use regression discontinuity designs.
-
-\subsection{Data}
+\section{Data}
+In this section we introduce the data we use in our application---the analysis of municipal websites in Louisiana and Indiana.
 The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
@@
 In many cases, these sites redirect to another address, sometimes not a .gov domain (in this case, we simply use this domain).
-We record these URLs, as they are required to retrieve the images websites stored in the Wayback Machine (WbM).
-
-$T_{1}+\beta_1$
+We record these URLs.
 
@@
 Finally, a number of cities are simply misspelled, which we also correct by hand.
-
-After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
-
-These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
-
-\begin{figure}[!ht]
-	\centering
-	\caption{Percentage of state population covered.}
-	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
-\end{figure}
-
-We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
-To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
-We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
-
-<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
-Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
-
-It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
-
-\begin{enumerate}
-
-\item For what percentage and number of IN cities can we find data from the WBM?
-\item For how many election cycles can we find political leadership data for these matched cities?
-\item In what number and percentage of cities is the local leadership majority Republican? 
-\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
-
-\end{enumerate}
-
-\begin{enumerate}
-
-	\item 30 cities, with a combined population of 1,180,435.
-However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
-	\item 2015, 2011, 2007, 2003.
-	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
-	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
-
-\end{enumerate}
 
@@
 
-\subsection{Topic modeling}
-Note: this chapter is mostly a wordy and less coherent version of the above.
-
-We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas.
-Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order.
-Documents uploaded to city websites are expected to be a reflection of these preferences.
-
-The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model.
-However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics.
-There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.
-
-The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents.
-Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates.
-In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards).
-Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website.
-Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.
-Further demographic as well as economic data might also be useful to differentiate cities from one another.
-If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.
-
-The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences.
-Unfortunately, we have two types of 'authors' - cities, and parties.
-Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author.
-This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents.
-(Note: In the papers on author-topic models, the intention is often to analyze scientific articles.
-These articles are often co-authored.
-Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)
-
-The critical element in this analysis is to accurately attribute authorship of documents to either party.
-Despite possible changes to websites due to a leadership transition, large parts of the content carry over.
-This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'.
-But the reverse is not possible, because the predecessor government can't choose to retain documents from the future.
-{\em  This is a very important point for municipal websites.
-We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added.
-}
-
-Labeling newly added documents after a change of power is quite simple.
-As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption.
-However, we could, and probably should test how long documents tend to stay on a city website.
-Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient.
-If we want to be really fancy about it, we could create a duration model, with document topics as features.
-This would allow us to measure whether some documents tend to remain longer based on their topic (i.e.
-fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.
-
-If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words.
-After that, we run the actual model.
-This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface.
-It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins.
-'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website.
-Hence, these websites should be filled with purely administrative content.
-
-The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e.
-the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.
-
-Another intervening factor is that for cities in Indiana, mayoral terms begin in January.
-Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year.
-Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity.
-We can test for this by comparing election years to non-election years.
-Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.
-
-Furthermore, if we only investigate cities in which control of government changes from one party to another, we may overestimate its effect.
-Not only does a transition in party control occur, but the person in charge also changes.
-Parties are fairly homogeneous, so that two mayors from the same party may have very different policy preferences and managerial styles.
-To remedy this problem, we [could] utilize matching, pairing our cases with similar cities in which the incumbent does not run for re-election, but party control stays the same nevertheless.
-
-%Justicifcation for Arun 2010 topic number measure
-In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}.
-In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix.
-We find 200 topics to be the best value (see figure \ref{ldatuning}).
-
-%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences.
-This way, we could identify directly which issues are considered to be the most divisive.
-
-%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.
-
-%Traditional author models that rely on lexical or syntactic differences may also be of use.
-Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles.
-However, it seems likely that personal rather than partisan authorship is playing an even larger role here.
-
-%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes.
-As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''.
-Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership.
-In a way, this captures the data-generating process more closely.
-
-%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites.
-One assumes that multiple authors write one document.
-This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors.
-This is not as good of a fit for city governments however.
-Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics.
-For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+
-
-%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government.
-If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2.
-The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues.
-Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.
-
-\begin{figure}[!ht]
-	\centering
-	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
-	\label{snapshots}
-	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
-\end{figure}
-
-%\begin{figure}[!ht]
-%	\centering
-	%\caption{Population coverage}
-%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
-%\end{figure}
-
-%\begin{figure}[!ht]
-%	\centering
-	%\caption{Population coverage}
-%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
-%\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	%\caption{Population coverage}
-	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
-\end{figure}
-
-%topicweights density
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
-	\label{doctopics_density}
-	\includegraphics[width=\linewidth]{figures/doctopics_density_IN.pdf}
-\end{figure}
-
-\subsubsection{LDA diagnostics}
-
-Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic.
-Distributions with lower peaks near zero and flatter bodies indicate a topic that is present to varying degrees in multiple documents.
-This shape appears to be more common in documents from Republican cities.
-By contrast, a distribution with a high peak near zero and a very long tail is indicative of a topic that only appears in one specific document.
-This appears to be more common for documents in Democratic cities.
-The substantive conclusion then is that Democrats appear to be more prone to dedicating individual documents to one specific purpose, whereas Republicans produce general-purpose documents more often.
-
-%topicweights density
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
-	\label{topicweights_density}
-	\includegraphics[width=\linewidth]{figures/topicweights_density_IN.pdf}
-\end{figure}
-
-An alternative way to consider topic weights is to aggregate them across documents, in this case through their median or mean.
-Figure \ref{topicweights_density} shows this distribution of topic weights across topics.
-Most topics have a very low weight - meaning that they do not appear in a lot of documents.
-When aggregating across documents via the mean, this effect is more pronounced for Republicans, suggesting that most topics do not feature frequently (or even at all) in their documents.
-Democrats on the other hand appear to have a wider spectrum of topics from which they chose - supporting the hypothesis of Democrats as a 'big tent' party.
-However, this effect is reversed when using the median instead of the mean to aggregate across documents.
-Now, the the distribution has a higher peak and lower tail for Democrats.
-The cause for this stark divergence appears to lie in the fact the mean and median differ enormously - for the range displayed here, the mean is about a hundred times greater.
-Evidently, extremely large weights (i.e.
-some documents fitting specific topics perfectly) distort the picture.
-The median document is a better representation of the corpus as a whole, but the results do not fit our hypothesis.
-Their are however more consistent with figure \ref{topicweights_density}.
-
-Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us.
-To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}.
-For the most part, differences are small.
-For a few topics however, a contrasts emerges.
-
-%size of the differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences (Indiana).}
-	\label{diffsize}
-	\includegraphics[width=\linewidth]{figures/diffsize_IN.pdf}
-\end{figure}
-
-Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences.
-Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged.
-For the most part however, these topics focus on administrative matters.
-
-%word topic probabilities for topics with big differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{plotWTP_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs_IN.pdf}
-\end{figure}
-
-To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences.
-It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.
-
-%word topic probabilities for topics with big differences
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences}
-	\label{doctopics_density_bigdiffs}
-	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs_IN.pdf}
-\end{figure}
-
-To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps.
-Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents.
-Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else.
-One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.
+We illustrate the analysis of municipal website content using bag-of-words (BoW) methods.
+BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
 
@@
 %Heatmaps
-\begin{figure}[!ht]
+\begin{figure}[htp]
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
@@
 	\label{heatmaps_weights}
-	\includegraphics[width=\linewidth]{figures/heatmaps_weights_IN.png}
-\end{figure}
-
-%Heatmaps with no duplicate line removal (threshold set at 999999999)
-%also, since the duplicate line removal didn't get rid of as much crap,
-%it was necessary to remove non [A-Za-z] characters before hunspell
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana). No duplicate line removal.}
-	\label{heatmaps_weights}
-	%\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
-\end{figure}
-
-%Number of topics vs. tophic coherence
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
-	\label{numtopics_coherence}
-	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
+	\includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
 \end{figure}
@@
 %Indiana map
-\begin{figure}[!ht]
+\begin{figure}[htp]
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
@@
 
-%partisan topics
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{The most partisan topics.
-The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
-	\label{partisan_topics}
-	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
-\end{figure}
-
-%ldatuning
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{The optimal number of topics for our corpus.
-The measures of Griffths 2004 and Cao 2009 indicate the best number of topics at their minimum, whereas the measure of Arun 2010 points to the best value at its maximum.}
-	\label{ldatuning}
-	\includegraphics[height=0.75\textheight]{figures/topicnumber_ldatuning.pdf}
-\end{figure}
-
 %stm results
-\begin{figure}[!ht]
+\begin{figure}[htp]
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
@@
 %	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-\end{figure}
-
-%fightin words results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
-	\label{fightinwordsIN}
-	\includegraphics[width=\linewidth]{figures/fightinWordsIN.png}
-\end{figure}
-
-%fightin words results
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
-	\label{fightinwordsLA}
-	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
 \end{figure}
@@
 %fightin words results
-\begin{figure}[!ht]
+\begin{figure}[htp]
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
 		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
 	\label{linesCutoff}
-	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Hierarchical clustering (Indiana).}
-	\label{hclustIN}
-	\includegraphics[width=\linewidth]{figures/clusteringIN.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Hierarchical clustering (Louisiana).}
-	\label{hclustLA}
-	\includegraphics[width=\linewidth]{figures/clusteringLA.png}
-\end{figure}
-
-%Entropy by cutoff
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Entropy (between cities, for each topic).}
-	\label{cutoffEntropy}
-	\includegraphics[width=\linewidth]{figures/CutoffCityEntropy.pdf}
-\end{figure}
-
-%Weighted entropy by cutoff
-\begin{figure}[!ht]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Weighted (multiplied by tokens assigned to the topic) entropy (between cities, for each topic).}
-	\label{cutoffEntropy}
-	%\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity10}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_10.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity20}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_20.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity30}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_30.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity40}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_40.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity50}
-	\includegraphics[width=\linewidth]{figures/heatmap_hclust_50.png}
-\end{figure}
-
-%Clustering
-\begin{figure}[!ht]
-	\centering
-	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
-	\label{hclustCity100}
-	\includegraphics[height = 1.2\textheight]{figures/heatmap_hclust_100.png}
 \end{figure}
@@
 \end{equation}
+
+After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
+
+These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
+
+\begin{figure}[htp]
+	\centering
+	\caption{Percentage of state population covered.}
+	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
+\end{figure}
+
+We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
+To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
+We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
+
+<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
+Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
+
+It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
+
+\begin{enumerate}
+
+\item For what percentage and number of IN cities can we find data from the WBM?
+\item For how many election cycles can we find political leadership data for these matched cities?
+\item In what number and percentage of cities is the local leadership majority Republican? 
+\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
+
+\end{enumerate}
+
+\begin{enumerate}
+
+	\item 30 cities, with a combined population of 1,180,435.
+However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
+	\item 2015, 2011, 2007, 2003.
+	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
+	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
+
+\end{enumerate}
+
+\section{Running Application: Party Differences in Municipal Websites}
+
+\begin{landscape}
+\begin{table}[htbp]
+	%\caption{}
+	\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+		\hline
+		Names & Year & Journal & Findings & Important? \\ \hline
+		Benedictis-Kessner, Justin De
+		Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
+Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
+		Caughey, Devin
+		Warshaw, Christopher
+		Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
+Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
+& Somewhat \\ \hline
+		Einstein, Katherine Levine
+		Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
+aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
+		Einstein, Katherine Levine
+		Glick, David M.
+& 2015 & Working Paper & Survey of 72 mayors.
+Unlike Republican mayors, roughly half of Democrats seem to agree that cities should aim to reduce inequality.
+Democratic mayors also seem to favor redistribution to accomplish that goal.
+& Somewhat \\ \hline
+		Kiewiet, D Roderick
+		Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
+Spending has thus decreased in general.
+Lack of funds means that there is not much discretion for partisanship.
+& Somewhat \\ \hline
+		Tausanovitch, Chris
+		Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
+Partisan elections do not make cities more or less responsive.
+& Yes \\ \hline
+		Guillamón, Ma Dolores
+		Bastida, Francisco
+		Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
+Conservative parties spend more on police.
+Spending is higher before elections.
+Also contains a useful overview of the literature.
+& Yes \\ \hline
+	\end{tabular}
+	\label{}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+	\begin{table}[htbp]
+		%\caption{}
+		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+			\hline
+			Names & Year & Journal & Findings & Important? \\ \hline
+			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
+			Solé-Ollé, Albert
+			Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
+The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
+Partisanship might also affect housing construction and price growth.
+& Yes \\ \hline
+			Gerber, Elisabeth R.
+			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
+			Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
+Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
+Non-partisan elections favor Republicans/upper class.
+Mixed evidence for whether partisanship of mayor is important for policy.
+& Somewhat \\ \hline
+			Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
+spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
+& Somewhat \\ \hline
+			Ferreira, Fernando
+			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
+			Ansolabehere, Stephen
+			Snyder, James M.
+& 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
+The important finding (for us) is the fact that counties whose government is controlled by the same party as the state government, receive more funding (county's share of state transfers, normalized by county pop.) from the state.
+& Somewhat \\ \hline
+			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
+		\end{tabular}
+		\label{}
+	\end{table}
+\end{landscape}
+
+\begin{landscape}
+	\begin{table}[htbp]
+		%\caption{}
+		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+			\hline
+			Names & Year & Journal & Findings & Important? \\ \hline
+			Armstrong, Cory L.
+& 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
+Manual content analysis (undergrads told to look around for 15 minutes).
+School board websites, more professional websites, and websites in Republican-dominated counties are found to be more transparent.
+& Yes \\ \hline
+			Cegarra-Navarro, Juan
+			Pachón, José
+			Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
+Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
+More sophisticated websites are correlated with greater civic engagement and greater use of e-government functions.
+& Yes \\ \hline
+			Dolson, Jordan
+			Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
+Three categories: e-content (city information on website), e-participation, social media use.
+Tables on page 15 show frequencies of these categories across sites, and might be useful to inform our topics.
+Larger cities have better websites.
+Population growth and immigration are also tested, but the findings are somewhat inconclusive.
+& Yes \\ \hline
+			Feeney, Mary K.
+			Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
+city websites at two points in time (2010-2014).
+Count model of website features regarding information, e-services, utilities, transparency and civic engagement.
+Having a larger population leads to more features.
+Relying on a website contractor leads to more information and transparency.
+The authors say that mayor-councils are negatively correlated with website sophistication, but their regression tables state the opposite.
+& Yes \\ \hline
+			Kaylor, Charles
+			Deshazo, Randy
+			Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
+Table 1 lists a number of possible ways this manifests, could be useful for our theory.
+& Somewhat \\ \hline
+			Ansolabehere, Stephen
+			Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
+Is website content correlated with city characteristics?
+Not particularly systematic, and the findings are inconclusive.
+& Somewhat \\ \hline
+			Jeffres, Leo W.
+			Lin, Carolyn A.
+& 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
+Features include information about city, opportunities for citizen feedback, galleries of photos, links, etc.
+Purely descriptive analysis, doesn't contain anything that isn't covered in any of the other aricles.
+& No \\ \hline
+		\end{tabular}
+		\label{}
+	\end{table}
+\end{landscape}

### 2018-01-30 paper/manuscript.tex
justification for and explanation of the ground truth test

@@
 
+\section{Ground truth test}
+In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
+Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
+However, the aspirations some mayors have shown towards higher offices - in some cases even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
+One of the most vicious and blatantly partisan cleavages in current U.S.
+politics - the debate surrounding sanctuary cities - has seen mayors in a central role.
+Research into local politics has shown that partisan elections consistently have greater turnout \citep{Schaffner2001}.
+When voters are denied this cue, they make use of other, and considerably more irrational heuristics, such as name, gender, or occupation of the contenders.
+Consequently it only makes sense for any office-seeking politician to emphasize their partisanship.
+Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
+
+In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
+As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
+Consequently they are very likely to emphasize conservative/liberal values on this platform.
+If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
+
+Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
+We do the same for the city documents, and the compare the four document collections using cosine similarity.
+This measure is the cosine between the angle of two vectors, in this case the frequencies of all words in the two vocabularies.
+Compared to a simple euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
+The cosine measure between two documents ranges between 0 and 1, 0 signifying absolutely no correlation, and 1 perfect overlap.
+Figure \ref{groundtruth} shows the result of this test.
+The expectation is for a greater similarity between Republican cities and the Republican ground truth, than Republican cities and Democratic ground truth - and vice versa.
+At present however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
+
+%ground truth test
+\begin{figure}[htp]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
+	\caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
+	\label{groundtruth}
+\end{figure}
+
 \section{Conclusion}

### 2018-02-13 paper/tables/groundtruth_bootstrapped.tex
A LOT of changes, additions and fixes to the whole city and mayor scraping, processing, analyzing, etc.

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Feb 13 10:36:40 2018
\begin{table}[ht]
\centering
\begin{tabular}{rllll}
  \hline
 & dem.groundtruth & rep.groundtruth & dem.cities & rep.cities \\ 
  \hline
dem.groundtruth & 1, 1 & 0.807, 0.896 & 0.714, 0.729 & 0.68, 0.698 \\ 
  rep.groundtruth & 0.807, 0.896 & 1, 1 & 0.647, 0.697 & 0.641, 0.693 \\ 
  dem.cities & 0.714, 0.729 & 0.647, 0.697 & 1, 1 & 0.937, 0.944 \\ 
  rep.cities & 0.68, 0.698 & 0.641, 0.693 & 0.937, 0.944 & 1, 1 \\ 
   \hline
\end{tabular}
\caption{Ground truth test, comparing campaign websites of mayors of the 100 largest cities in the US and cities in Indiana and Louisiana. The values are bootstrapped confidence bounds for cosine similarities between concatenated document collections.} 
\label{groundtruth_bootstrapped}
\end{table}

### 2018-02-13 MayorsBigCities.R

@@ -1,0 +1,232 @@
+library("stringr")
+library("tools")
+library("tibble")
+library('pbapply')
+
+# ------------- #
+# Preprocessing #
+# ------------- #
+
+source("./preprocessing.R")
+
+# Read in the data from txt files
+d <- readCityDocuments("websites/bigcitymayors2TXT", "mayor_site")
+
+# Do all the preprocessing that needs to be done before removing duplicate lines
+d <- preprocessing_1(d, "mayor_site")
+
+# Find duplicate lines
+docDuplicates <- findDuplicates(d, "mayor_site", nthreads = 6)
+
+# Use the counts of duplicate lines found above to remove them over a certain threshold
+d$doc <- as.character(pbsapply(1:nrow(d), removeDuplicates))
+
+# Do the rest of the preprocessing
+d <- preprocessing_2(d, remove.city.names = T)
+
+d <- as.data.frame(d)
+save(d, file = "rfiles/d_bigcitymayors.rdata")
+
+#lemmatization
+#Note: due to memory constraints, it may be necessary to close R here, then run
+# python3 lemmatization.py rfiles/d_IN.rdata
+#from the console instead, open R again and continue on the next line (i.e. load)
+#but don't forget to set the following againa after restarting R
+#state <- "Indiana"
+#stateAbb <- "LA"
+system(paste0("python3 lemmatization.py ", "rfiles/d_bigcitymayors.rdata"))
+load("rfiles/d_bigcitymayors.rdata")
+#spacy puts -PRON- in place of pronouns since they can't be lemmatized
+#we don't really care about pronouns, so we just remove them
+d$doc <- str_replace_all(d$doc, "-PRON- ", "")
+
+#Hunspell and removal of terms occuring in only one document
+#these were originally in preprocessing.R, but were not working correctly
+#functionally there is no downside to them being here, it just doesn't look as nice
+source("hunspellParallel.R")
+source('functions/occuranceRemove.R')
+
+save(d, file = "rfiles/d_bigcitymayors.rdata")
+
+# merge in partisanship
+load("./rfiles/campaign_websites.rdata")
+df$campaign_website <- str_replace(df$campaign_website, "https?://", "")
[…]

### 2018-02-13 dataCollectionBigCities.R

@@ -1,0 +1,23 @@
+# Pipeline file to do the data collection part of the pipeline
+
+source("wget.R")
+source("fixExtensions.R")
+source("convertToText.R")
+
+# Example: mayors
+
+#load URLs
+load("rfiles/campaign_websites.rdata")
+
+#use wget function to download everything
+wget(df$city_website, "~/hd1/govWebsites/websites/bigcities")
+
+#use the fixExtensions function to make sure all the file types (i.e. endings) are correct
+#this is necessary because readtext determines file type by extension
+fixExtensions("./websites/bigcitymayors")
+
+#some websites have linux invalid filenames, fix them
+fixFileNames("./websites/bigcitymayors")
+
+#use the readtext package to convert everything to text (in a new folder)
+convertToText("./websites/bigcitymayors", "./websites/bigcitymayorsTXT")

### 2018-02-13 dataCollectionBigCityMayors.R

@@ -1,0 +1,28 @@
+# Pipeline file to do the data collection part of the pipeline
+
+source("wget.R")
+source("fixExtensions.R")
+source("convertToText.R")
+
+# Example: mayors
+
+#load URLs
+load("rfiles/campaign_websites.rdata")
+#remove mayors without a campaign website
+df <- df[is.na(df$campaign_website)==F,]
+#remove independent mayors
+df <- df[is.na(df$party)==F,]
+df <- df[df$party!="(I)",]
+
+#use wget function to download everything
+wget(df$campaign_website, "./websites/bigcitymayors2")
+
+#use the fixExtensions function to make sure all the file types (i.e. endings) are correct
+#this is necessary because readtext determines file type by extension
+fixExtensions("./websites/bigcitymayors2")
+
+#some websites have linux invalid filenames, fix them
+#fixFileNames("./websites/bigcitymayors2")
+
+#use the readtext package to convert everything to text (in a new folder)
+convertToText("./websites/bigcitymayors2", "./websites/bigcitymayors2TXT")

### 2018-02-13 scrapeCampaignWebsites.R

@@ -1,0 +1,72 @@
+library("rvest")
+library("stringr")
+
+#City websites
+url <- "https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States"
+mytable <- read_html(url) %>% html_nodes("table") %>% .[[2]]
+df <- mytable %>% html_table(fill=T)
+names(df) <- df[1,]
+df <- df[-1,]
+df$party <- str_extract(df$Mayor, "\\(([^\\)]+)\\)")
+df$Mayor2 <- str_extract(df$Mayor, "[^(]*")
+df$Mayor2 <- str_trim(df$Mayor2)
+
+#get the link to the city's Wikipedia page
+get_link <- function(html_table, team){
+  html_table %>% 
+    html_nodes(xpath=paste0("//a[text()='", team, "']")) %>% 
+    .[[1]] %>% 
+    html_attr("href")
+}
+
+df$wiki_link <- sapply(df$City, function(x)get_link(mytable, x))
+df$wiki_link2 <- sapply(df$Mayor2, function(x)get_link(mytable, x))
+
+
+#function to extract the links to the campaign websites
+extractWebsite <- function(wikipage){
+  link <- str_c("https://ballotpedia.org", wikipage)
+  citylink <- read_html(link) %>% html_nodes(xpath=paste0("//a[text()='", "Campaign website", "']")) %>% html_attr("href")
+  if(identical(citylink, character(0))){
+    citylink <- NA #NA if no link
+  }
+  citylink <- citylink[[1]] #in some cases, it returns the link twice, this takes care of that
+  return(citylink)
+}
+df$campaign_website <- sapply(df$wiki_link2, extractWebsite)
+
+#function to extract the links to the campaign websites
+extractCityWebsite <- function(wikipage){
+  link <- str_c("https://ballotpedia.org", wikipage)
+  citylink <- read_html(link) %>% html_nodes(xpath=paste0("//a[text()='", "City website", "']")) %>% html_attr("href")
+  if(identical(citylink, character(0))){
+    citylink <- NA #NA if no link
+  }
+  citylink <- citylink[[1]] #in some cases, it returns the link twice, this takes care of that
+  return(citylink)
+}
+df$city_website <- sapply(df$wiki_link, extractCityWebsite)
+
+
+#remove independent mayors
+df <- df[is.na(df$party)==F,]
[…]

### 2018-02-13 scrapeMayorsNYWikipedia.R

@@ -73,4 +73,25 @@ filer <- data2$`Filer Name`
 
 library(stringr)
 
-str_replace(filer, paste0(del, collapse = "|"), "")
+data2$filer_name <- data2$`Filer Name`
+
+
+data2$cand_num <- 1:nrow(data2)
+
+
+data2$wiki_link['/wiki/Oswego_County,_New_York'] <- "/wiki/Oswego,_New_York"
+
+#ambiguous: 123,124, picked 123
+#175, 176, picked 175 because donation
+
+#mayors_numL <- list(10,16,19,21,NA,31,43,48,NA,NA,62,NA,71,83,NA,85,88,94,99,105,NA,110,123,NA,128,134,135,141,147,NA,162,NA,170,175,181,187,192,195,200,209,NA,220,NA,226,235,240,259,269,277,289,290,293,305)
+mayors_num <- c(10,16,19,21,NA,31,43,48,NA,NA,62,NA,71,83,NA,85,88,94,99,105,NA,110,123,NA,128,134,135,141,147,NA,162,NA,170,175,181,187,192,195,200,209,NA,220,NA,226,235,240,259,269,277,289,290,293,305)
+
+data <- data.frame(city = unique(data2$Municipality), wiki = unique(data2$wiki_link))
+data$REP <- data2$REP[mayors_num]
+data$DEM <- data2$DEM[mayors_num]
+data$NEITHER <- data2$NEITHER[mayors_num]
+data$mayor <- data2$mayor[mayors_num]
+
+table(data$DEM)
+table(data$REP)

### 2018-03-03 mergeDocsWithCensusData.R
finished up collating the URLs and party information from all the data sources we have right now; everything is now combined; created two tables with summary statistics and put them in the manuscript

@@ -3,17 +3,18 @@ library("stringr")
 
 #read in the census data
 census <- fread("data/sub-est2015_all.csv")
-census <- subset(census, STNAME == state)
+#census <- subset(census, STNAME == state)
 
 #alter city names to make them fit
 census$NAME <- str_replace(census$NAME, "town", "")
 census$NAME <- str_replace(census$NAME, "village", "")
 census$NAME <- str_replace(census$NAME, "city", "")
 census$NAME <- str_trim(census$NAME)
+census$State_City <- paste(census$STNAME, census$NAME, sep = "_")
 
 #merge
-census <- subset(census, select = c("NAME","CENSUS2010POP", paste0("POPESTIMATE", unique(d$Year))))
-census <- census[!duplicated(paste0(census$NAME,census$CENSUS2010POP))]
-d <- base::merge(d, census, by.x = "City", by.y = "NAME", all.x = T, all.y = F)
+census <- subset(census, select = c("State_City","CENSUS2010POP"))
+census <- census[!duplicated(paste0(census$State_City,census$CENSUS2010POP))]
+d <- base::merge(websiteUrls, census, by = "State_City", all.x = T, all.y = F)
 
 save(d, file = paste0("rfiles/d_", stateAbb, ".rdata"))

### 2018-03-03 mergeStatesURLs.R

@@ -1,6 +1,5 @@
 library(stringr)
 
-
 #Load Indiana website data
 #(file is created in scrapeIndianaURLsNew.R)
 load("rfiles/indianaWebsiteURLs.rdata")
@@ -22,30 +21,52 @@ load("rfiles/washingtonWebsiteURLs.rdata")
 washingtonWebsiteUrls$State <- "Washington"
 
 #Load 100 largest cities website data
-load("./rfiles/campaign_websites.rdata")
-df$State <- str_split_fixed(df$City, ",", 2)[,2]
-df$City <- str_split_fixed(df$City, ",", 2)[,1]
-df$Mayor <- str_replace(df$Mayor, " (\\(.*?\\))", "")
-df$party <- str_replace(df$party, "\\(", "")
-df$party <- str_replace(df$party, "\\)", "")
-names(df) <- c("Rank", "City", "ballotpMayor", "ballotpTermBegin", "ballotpTermEnd", "ballotpGovType", "ballotpParty", "ballotpCityPage", "ballotpMayor2", "ballotpMayorPage", "ballotpCampaign_website", "ballotpCity_website", "State")
-bigcityWebsiteUrls <- df
-rm(df)
+load("rfiles/bigcityWebsiteURLs.rdata")
 
 ## Combine everything
 library('dplyr')
-
 websiteUrls <- bind_rows(indianaWebsiteUrls,louisianaWebsiteUrls)
 websiteUrls <- bind_rows(websiteUrls, newyorkWebsiteUrls)
 websiteUrls <- bind_rows(websiteUrls, washingtonWebsiteUrls)
-websiteUrls <- bind_rows(websiteUrls, bigcityWebsiteUrls)
+
+#before merging with the big city data, clean up the strings
+websiteUrls$State <- str_trim(websiteUrls$State)
+websiteUrls$State_City <- paste(websiteUrls$State, websiteUrls$City, sep = "_")
+
+#merge, then delete the duplicate variables
+websiteUrls <- merge(websiteUrls, bigcityWebsiteUrls, by = "State_City", all = T)
+websiteUrls$City.x[is.na(websiteUrls$City.y)==F] <- websiteUrls$City.y[is.na(websiteUrls$City.y)==F]
+websiteUrls$State.x[is.na(websiteUrls$State.y)==F] <- websiteUrls$State.y[is.na(websiteUrls$State.y)==F]
[…]

### 2018-03-20 paper/presentation/govWebsites_spring_2018_Presentation.tex
presentation

--- 2017-12-19 paper/presentation/Markus_SPSA_2018_Presentation.tex
@@
 
-%\begin{frame}{Spot the difference}
-%\begin{figure}
-%	\hfill
-%	\subfigure{\includegraphics[width=5cm]{Images/Clinton_Rally_cr.jpg}}
-%	\hfill
-%	\subfigure{\includegraphics[width=5cm]{Images/Trump_Rally_cr.jpg}}
-%\end{figure}
-%\end{frame}
-
-\begin{frame}{Government Websites}
-\linespread{1.5}
-{\large
-	\begin{itemize}
-		\item Content of government websites is an important source of information \& transparency
-		\item After coming into power, the Trump administration  has made some controversial changes to the websites of federal agencies
-		\item Website content is political
-		\item Partisanship of city government is expected to have an effect
-	\end{itemize}
-
-}
-\end{frame}
-
-\begin{frame}{Example Website}
-	\includegraphics[width = \linewidth]{arcadia_water.png}
-\end{frame}
-
-\begin{frame}{Local Government Websites}
-\linespread{1.5}
-{\large
-	\begin{itemize}
-		\item Most local (i.e. mayoral) elections are non-partisan
-		\item Few states have exclusively partisan local elections
-		\item Data for these elections can be difficult to find
-		\item We selected Indiana and Louisiana
-	\end{itemize}
-
-	}
-\end{frame}
-
-\begin{frame}{Data Overview}
-\begin{figure}
-	\hfill
-	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
-	\hfill
-	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
-\end{figure}
-\end{frame}
-
-\begin{frame}{The Pipeline}
+\begin{frame}{Presented at SPSA}
 	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
@@
 
-\begin{frame}{The Pipeline}
-	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
-	\begin{columns}
-		\column{0.33\textwidth}
-		%Data Collection
-		\vspace{5mm}
-		\begin{itemize}
-			\item Identify URLs
-			\item Verify URLs (browser automation)
-			\item Download websites
-			\item Determine file type
-			\item Convert to txt
-		\end{itemize}		
-		\column{0.33\textwidth}
-		%Preprocessing
-		\vspace{5mm}
-		\begin{itemize}
-			\item Remove punctuation, dates, etc.
-			\item To lowercase
-			\item \textbf{Boilerplate removal}
-			\item Spellchecking
-			\item Lemmatization \\ (city \& cities = city)
-		\end{itemize}
-		\column{0.33\textwidth}
-		%Analysis
-		\vspace{5mm}
-		\begin{itemize}
-			%\item Hierarchical clustering
-			\item Fightin' Words
-			\item Structural topic model
-			%\begin{itemize}
-			%	\item LDA
-			%	\item STM
-			%\end{itemize}
-		\end{itemize}
-	\end{columns}
+\begin{frame}{Presented at SPSA}
+\input{descriptiveStatsIN.tex}
+\input{descriptiveStatsLA.tex}
 \end{frame}
 
-\section{Preprocessing}
-
-%\begin{frame}{Document filetype \& conversion}
-%\begin{itemize}
-%	\item Websites contain a number of different filetypes
-%	\item txt, pdf, html, doc and docx are useable
-%	\item convert everything to txt
-%	\item the file ENDING does not always 
-%\end{itemize}
-%\end{frame}
-
-\begin{frame}{Boilerplate Removal}
-\includegraphics[width = \linewidth]{arcadia_water.png}
+\begin{frame}{Presented at SPSA}
+\begin{figure}
+	\hfill
+	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
+	\hfill
+	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
+\end{figure}
 \end{frame}
 
-\begin{frame}{Boilerplate Removal}
-\includegraphics[width = \linewidth]{duplicateLines.png}
+\begin{frame}{Presented at SPSA}
+	\input{fightinwordsIN.tex}
 \end{frame}
 
-\begin{frame}{Boilerplate Removal}
-	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
+\begin{frame}{Presented at SPSA}
+\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
 \end{frame}
 
-\begin{frame}{Boilerplate Removal}
+\begin{frame}{Presented at SPSA}
+\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
+\end{frame}
+
+\begin{frame}{SPSA feedback}
 \begin{itemize}
-	\item Within each city, there is a lot of shared text
-	\item If not removed, the text clusters into cities
-\end{itemize}
-\begin{itemize}
-	\item Solution: Compare each line in each document to every other line in every document of that city
-	\item Count duplicates
-	\item Remove a line if it is duplicated within a city above some threshold
-	\item Fast \& efficient implementation
+	\item overall quite positive
+	\item there seems to be some demand in publican administration for this kind of research
+	\item threshold of ten for duplicates
+	\item the usual concerns with bag-of-words
+	\item describe methods more clearly
+	\item \textbf{``Does your method improve the external validity so greatly that the internal validity becomes less of a concern?''}
+	\item comparison with non-partisan cities/websites
+	\item city covariates
 \end{itemize}
@@
 
-\begin{frame}{The Pipeline}
-	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
-	\begin{columns}
-		\column{0.33\textwidth}
-		%Data Collection
-		\vspace{5mm}
+\begin{frame}{Planned covariates}
 \begin{itemize}
-			\item Identify URLs
-			\item Verify URLs (browser automation)
-			\item Download websites
-			\item Determine file type
-			\item Convert to txt
+	\item population
+	\item GDP per capita
+	\item percent non-white
+	\item City area
+	\item democratic vote share/magnitude of victory
+	\item log median house price
+	\item (most of these are from Einstein \& Glick 2015)
 \end{itemize}
-		\column{0.33\textwidth}
-		%Preprocessing
-		\vspace{5mm}
-		\begin{itemize}
-			\item Remove punctuation, dates, etc.
-			\item To lowercase
-			\item Boilerplate removal
-			\item Spellchecking
-			\item Lemmatization \\ (city \& cities = city)
-		\end{itemize}
-		\column{0.33\textwidth}
-		%Analysis
-		\vspace{5mm}
-		\begin{itemize}
-			%\item Hierarchical clustering
-			\item Fightin' Words
-			\item Structural topic model
-			%\begin{itemize}
-			%	\item LDA
-			%	\item STM
-			%\end{itemize}
-		\end{itemize}
-	\end{columns}
 \end{frame}
 
-%\begin{frame}{Other preprocessing}
-%\begin{itemize}
-%	\item Remove:
-%	\begin{itemize}
-%		\item Dates
-%		\item Numbers
-%		\item Punctuation
-%		\item Words not recognized by an English dictionary
-%		\item Stopwords
-%		\item Documents with too few unique words
-%	\end{itemize}
-%\item Set to lowercase
-%\item Lemmatization
-%\end{itemize}
-%\end{frame}
-
-\section{Analysis}
-%\begin{frame}{Hierarchical Clustering}
-%\centering
-%\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
-%\end{frame}
-
-%\begin{frame}{Fightin' Words}
-%\begin{figure}
-%	\hfill
-%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
-%	\hfill
-%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
-%\end{figure}
-%\end{frame}
-
-\begin{frame}{Fightin' Words}
-	\input{fightinwordsIN.tex} %../tables/stmTopWordsINDem.tex
+\begin{frame}{Since SPSA - ground truth test}
+\begin{itemize}
+	\item party manifestos (didn't work - not enough data)
+	\item mayors' campaign websites (LA/IN - didn't work - not much data, and strange results)
+	\item mayors' campaign websites (top 100 cities - worked somewhat)
+\end{itemize}
+{\renewcommand\normalsize{\tiny}%
+	\small
+	\input{../tables/groundtruth_bootstrapped.tex}}
 \end{frame}
 
-%\begin{frame}{Latent Dirichlet Allocation}
-%\input{partisanTopWords.tex}
-%\end{frame}
-
-\begin{frame}{Structural Topic Model}
-\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
+\begin{frame}{Since SPSA - extending the sample}
+\begin{itemize}
+	\item New York
+	\item big cities
+	\item Washington
+	\item Oregon (unsuccessful)
+	\item extended LA/IN (55 -> 165)
+	\item 314 cities total, 230 downloaded so far
+\end{itemize}
 \end{frame}
 
-\begin{frame}{Structural Topic Model}
-\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
+\begin{frame}{wget and www}
+\begin{itemize}
+	\item www.townoflockport.com/ -- doesn't work
+	\item http://townoflockport.com/ -- works
+	\item inconsistent across websites
+	\item solution: check every website with Selenium, record the url it redirects to
+	\item currently re-scraping the 84 websites still missing
+\end{itemize}
 \end{frame}
 
-\section{Conclusion}
-\begin{frame}{Conclusion}
-\linespread{1.5}
-\large
+\begin{frame}{Next steps: compression}
 \begin{itemize}
-	%\item Hierarchical clustering only creates 'topics' if content is VERY similar
-	%\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
-	%\item LDA is sensitive to preprocessing, but the most flexible
-	%\item STM works too, but also very sensitive to duplicate content
-	\item Manual vs. automatic analysis of government websites
-	\item Our pipeline facilities scalable comparative analysis
+	\item Since, so far, something has always gone wrong when adjusting file endings and converting files to text, I've always made zipped backups so far
+	\item compression of millions of files of more than 1TB
+	\begin{itemize}
+		\item time
+		\item some paths are too long
+		\item some filenames have non-ascii characters
+	\end{itemize}
+\end{itemize}
+\end{frame}
 
-	\vspace{5mm}
-	\item Partisanship affects website content:
-	\item Democrats focus on raising and spending money
-	\item Republicans focus on infrastructure and utilities
+\begin{frame}{Next steps: map}
+\includegraphics[width=\linewidth, height = .99\textheight]{../figures/us_map.pdf}
+\end{frame}
+
+\begin{frame}{Next steps: covariates}
+\begin{itemize}
+	\item I already downloaded the above some time ago, but only for LA and IN
+	\item this was already a little convoluted, I'll have to automate it for it to work with all states
+	\item there is a problem with the census data:
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Next steps: covariates}
+\begin{itemize}
+	\item I already downloaded the above some time ago, but only for LA and IN
+	\item this was already a little convoluted, I'll have to automate it for it to work with all states
+	\item there is a problem with the census data:
+\end{itemize}
+\includegraphics[width=\linewidth]{census_problem.png}
+\begin{itemize}
+	\item Not a priority right now, need to finish all the document-related stuff first
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Next steps: optimize code}
+\begin{itemize}
+	\item preprocessing already took 4-5 hours for 25000 documents
+	\item we currently have 1.3 million; this will get reduced a bit, but it will still be a huge increase
+	\item the functions that aren't already vectorized are currently ``sapply'd''
+	\item with this much data, parallelization is probably worth it (currently only hashtables, spellchecking and some other more computationally intensive stuff is parallelized)
+	\item MAYBE it would be worth it to translate everything to quanteda - but unfortunately that won't work with the hashtables stuff
+	\item fightin' words is pretty fast, but stm also took hours already
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Next steps: structural topic model}
+\begin{itemize}
+	\item currently we use separate models for IN, LA
+	\item state fixed effects
+	\item package has problems with overly complex models
+	\item maybe use stm only for IN, LA, NY, WA, CA
 \end{itemize}

### 2018-04-23 paper/tables/stmTopWords.tex
new results table for stm run on new data

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Mon Apr 23 14:12:56 2018
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lllllll}
  \hline
1 & 2 & 3 & 4 & 5 & 6 & 7 \\ 
  \hline
\cellcolor{red!10}yon & \cellcolor{red!10}borough & \cellcolor{red!10}port & \cellcolor{red!10}waterfront & \cellcolor{red!10}queens & \cellcolor{red!10}boroughs & \cellcolor{red!10}island \\ 
  \cellcolor{blue!10}noise & \cellcolor{blue!10}impacts & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}vibration & \cellcolor{blue!10}ambient & \cellcolor{blue!10}adverse & \cellcolor{blue!10}thresholds \\ 
  \cellcolor{red!10}tax & \cellcolor{red!10}exemption & \cellcolor{red!10}taxes & \cellcolor{red!10}estate & \cellcolor{red!10}assessed & \cellcolor{red!10}real & \cellcolor{red!10}taxpayer \\ 
  \cellcolor{red!10}para & \cellcolor{red!10}personas & \cellcolor{red!10}antes & \cellcolor{red!10}persona & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}con \\ 
  \cellcolor{blue!10}election & \cellcolor{blue!10}ethics & \cellcolor{blue!10}appointed & \cellcolor{blue!10}elections & \cellcolor{blue!10}ballot & \cellcolor{blue!10}charter & \cellcolor{blue!10}elected \\ 
  \cellcolor{red!10}wetland & \cellcolor{red!10}habitats & \cellcolor{red!10}riparian & \cellcolor{red!10}habitat & \cellcolor{red!10}wetlands & \cellcolor{red!10}tidal & \cellcolor{red!10}freshwater \\ 
  \cellcolor{blue!10}parking & \cellcolor{blue!10}bus & \cellcolor{blue!10}transit & \cellcolor{blue!10}mall & \cellcolor{blue!10}buses & \cellcolor{blue!10}campus & \cellcolor{blue!10}arena \\ 
  \cellcolor{red!30}click & \cellcolor{red!30}download & \cellcolor{red!30}online & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}website & \cellcolor{red!30}visit \\ 
  \cellcolor{blue!10}draft & \cellcolor{blue!10}comments & \cellcolor{blue!10}comment & \cellcolor{blue!10}meetings & \cellcolor{blue!10}update & \cellcolor{blue!10}presentation & \cellcolor{blue!10}briefing \\ 
  \cellcolor{blue!10}ave & \cellcolor{blue!10}blvd & \cellcolor{blue!10}glen & \cellcolor{blue!10}pkwy & \cellcolor{blue!10}hwy & \cellcolor{blue!10}cove & \cellcolor{blue!10}fwy \\ 
  \cellcolor{blue!20}neighborhoods & \cellcolor{blue!20}strategy & \cellcolor{blue!20}vision & \cellcolor{blue!20}strategies & \cellcolor{blue!20}businesses & \cellcolor{blue!20}opportunities & \cellcolor{blue!20}vibrant \\ 
  \cellcolor{white}bid & \cellcolor{white}contract & \cellcolor{white}invoices & \cellcolor{white}procurement & \cellcolor{white}purchasing & \cellcolor{white}bids & \cellcolor{white}vendor \\ 
  \cellcolor{white}marijuana & \cellcolor{white}cannabis & \cellcolor{white}licensee & \cellcolor{white}taxicab & \cellcolor{white}license & \cellcolor{white}mischief & \cellcolor{white}citation \\ 
  \cellcolor{blue!10}complaint & \cellcolor{blue!10}discrimination & \cellcolor{blue!10}defendants & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}trial & \cellcolor{blue!10}harassment & \cellcolor{blue!10}defendant \\ 
  \cellcolor{red!10}rouge & \cellcolor{red!10}baton & \cellcolor{red!10}foods & \cellcolor{red!10}parish & \cellcolor{red!10}vegetables & \cellcolor{red!10}vending & \cellcolor{red!10}cooked \\ 
  \cellcolor{red!10}child & \cellcolor{red!10}violence & \cellcolor{red!10}abuse & \cellcolor{red!10}mental & \cellcolor{red!10}clients & \cellcolor{red!10}inmates & \cellcolor{red!10}homelessness \\ 
  \cellcolor{red!10}applicants & \cellcolor{red!10}landlord & \cellcolor{red!10}tenant & \cellcolor{red!10}rent & \cellcolor{red!10}exam & \cellcolor{red!10}tenants & \cellcolor{red!10}applications \\ 
  \cellcolor{red!10}think & \cellcolor{red!10}say & \cellcolor{red!10}really & \cellcolor{red!10}thing & \cellcolor{red!10}okay & \cellcolor{red!10}got & \cellcolor{red!10}maybe \\ 
  \cellcolor{blue!20}setback & \cellcolor{blue!20}fence & \cellcolor{blue!20}yard & \cellcolor{blue!20}zoned & \cellcolor{blue!20}front & \cellcolor{blue!20}height & \cellcolor{blue!20}accessory \\ 
  \cellcolor{red!10}shall & \cellcolor{red!10}subsection & \cellcolor{red!10}article & \cellcolor{red!10}provisions & \cellcolor{red!10}pursuant & \cellcolor{red!10}thereof & \cellcolor{red!10}forth \\ 
  \cellcolor{red!20}explained & \cellcolor{red!20}asked & \cellcolor{red!20}said & \cellcolor{red!20}legislator & \cellcolor{red!20}commented & \cellcolor{red!20}advised & \cellcolor{red!20}leg \\ 
  \cellcolor{blue!10}respondents & \cellcolor{blue!10}census & \cellcolor{blue!10}population & \cellcolor{blue!10}compared & \cellcolor{blue!10}average & \cellcolor{blue!10}trends & \cellcolor{blue!10}comparison \\ 
  \cellcolor{red!20}infection & \cellcolor{red!20}symptoms & \cellcolor{red!20}breastfeeding & \cellcolor{red!20}syphilis & \cellcolor{red!20}doses & \cellcolor{red!20}asthma & \cellcolor{red!20}tuberculosis \\ 
  \cellcolor{red!20}yes & \cellcolor{red!20}name & \cellcolor{red!20}signature & \cellcolor{red!20}mailing & \cellcolor{red!20}zip & \cellcolor{red!20}attach & \cellcolor{red!20}form \\ 
  \cellcolor{red!30}games & \cellcolor{red!30}tournament & \cellcolor{red!30}swim & \cellcolor{red!30}players & \cellcolor{red!30}player & \cellcolor{red!30}camp & \cellcolor{red!30}game \\ 
  \cellcolor{blue!10}goals & \cellcolor{blue!10}implementation & \cellcolor{blue!10}policies & \cellcolor{blue!10}policy & \cellcolor{blue!10}specific & \cellcolor{blue!10}implement & \cellcolor{blue!10}comprehensive \\ 
  \cellcolor{red!20}ems & \cellcolor{red!20}fires & \cellcolor{red!20}preparedness & \cellcolor{red!20}disaster & \cellcolor{red!20}evacuation & \cellcolor{red!20}fire & \cellcolor{red!20}firefighters \\ 
  \cellcolor{red!10}subcontractor & \cellcolor{red!10}subcontractors & \cellcolor{red!10}agrees & \cellcolor{red!10}proposer & \cellcolor{red!10}contractor & \cellcolor{red!10}grantee & \cellcolor{red!10}breach \\ 
  \cellcolor{blue!10}realm & \cellcolor{blue!10}massing & \cellcolor{blue!10}facades & \cellcolor{blue!10}entrances & \cellcolor{blue!10}plazas & \cellcolor{blue!10}elements & \cellcolor{blue!10}proponents \\ 
  \cellcolor{blue!10}employee & \cellcolor{blue!10}allegation & \cellcolor{blue!10}overtime & \cellcolor{blue!10}named & \cellcolor{blue!10}leave & \cellcolor{blue!10}grievance & \cellcolor{blue!10}wage \\ 
  \cellcolor{blue!10}parks & \cellcolor{blue!10}playground & \cellcolor{blue!10}beach & \cellcolor{blue!10}park & \cellcolor{blue!10}picnic & \cellcolor{blue!10}marina & \cellcolor{blue!10}trails \\ 
  \cellcolor{blue!10}lanes & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}intersections & \cellcolor{blue!10}bicyclists & \cellcolor{blue!10}roadway & \cellcolor{blue!10}pedestrians \\ 
  \cellcolor{blue!20}absent & \cellcolor{blue!20}aye & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \cellcolor{blue!20}berry & \cellcolor{blue!20}nays & \cellcolor{blue!20}tagged \\ 
  \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}million & \cellcolor{blue!20}revenues & \cellcolor{blue!20}budgeted & \cellcolor{blue!20}fund & \cellcolor{blue!20}expenditures \\ 
  \cellcolor{blue!10}whereas & \cellcolor{blue!10}resolution & \cellcolor{blue!10}amending & \cellcolor{blue!10}resolved & \cellcolor{blue!10}hereby & \cellcolor{blue!10}authorizes & \cellcolor{blue!10}digest \\ 
  \cellcolor{blue!10}assets & \cellcolor{blue!10}statements & \cellcolor{blue!10}governmental & \cellcolor{blue!10}accounting & \cellcolor{blue!10}liabilities & \cellcolor{blue!10}net & \cellcolor{blue!10}financial \\ 
  \cellcolor{red!30}honored & \cellcolor{red!30}joined & \cellcolor{red!30}proud & \cellcolor{red!30}fort & \cellcolor{red!30}announces & \cellcolor{red!30}won & \cellcolor{red!30}worth \\ 
  \cellcolor{white}analyst & \cellcolor{white}technician & \cellcolor{white}specialist & \cellcolor{white}performs & \cellcolor{white}prepares & \cellcolor{white}coordinates & \cellcolor{white}assists \\ 
  \cellcolor{white}server & \cellcolor{white}wireless & \cellcolor{white}software & \cellcolor{white}aircraft & \cellcolor{white}servers & \cellcolor{white}airport & \cellcolor{white}technology \\ 
  \cellcolor{blue!10}improvements & \cellcolor{blue!10}project & \cellcolor{blue!10}projects & \cellcolor{blue!10}phase & \cellcolor{blue!10}replacement & \cellcolor{blue!10}reconstruction & \cellcolor{blue!10}upgrades \\ 
  \cellcolor{red!10}recycling & \cellcolor{red!10}recycle & \cellcolor{red!10}garbage & \cellcolor{red!10}bags & \cellcolor{red!10}waste & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables \\ 
  \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}households & \cellcolor{blue!10}affordability & \cellcolor{blue!10}income & \cellcolor{blue!10}moderate & \cellcolor{blue!10}homeless \\ 
  \cellcolor{red!20}effluent & \cellcolor{red!20}wastewater & \cellcolor{red!20}discharges & \cellcolor{red!20}contaminants & \cellcolor{red!20}sludge & \cellcolor{red!20}infiltration & \cellcolor{red!20}solids \\ 
  \cellcolor{red!10}fee & \cellcolor{red!10}permit & \cellcolor{red!10}inspection & \cellcolor{red!10}permits & \cellcolor{red!10}inspections & \cellcolor{red!10}fees & \cellcolor{red!10}occupancy \\ 
  \cellcolor{blue!10}uses & \cellcolor{blue!10}mixed & \cellcolor{blue!10}density & \cellcolor{blue!10}land & \cellcolor{blue!10}industrial & \cellcolor{blue!10}residential & \cellcolor{blue!10}commercial \\ 
  \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}coal & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \cellcolor{red!10}solar & \cellcolor{red!10}greenhouse \\ 
  \cellcolor{blue!10}bonds & \cellcolor{blue!10}refunding & \cellcolor{blue!10}securities & \cellcolor{blue!10}bond & \cellcolor{blue!10}debt & \cellcolor{blue!10}issuer & \cellcolor{blue!10}maturity \\ 
  \cellcolor{red!20}artists & \cellcolor{red!20}artist & \cellcolor{red!20}performances & \cellcolor{red!20}music & \cellcolor{red!20}orchestra & \cellcolor{red!20}symphony & \cellcolor{red!20}arts \\ 
  \cellcolor{blue!80}arrested & \cellcolor{blue!80}suspect & \cellcolor{blue!80}homicide & \cellcolor{blue!80}suspects & \cellcolor{blue!80}shooting & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrests \\ 
  \cellcolor{white}retiree & \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}deductible & \cellcolor{white}retirees & \cellcolor{white}copay & \cellcolor{white}dental \\ 
  \cellcolor{red!10}ferrets & \cellcolor{red!10}dogs & \cellcolor{red!10}cats & \cellcolor{red!10}rabies & \cellcolor{red!10}pets & \cellcolor{red!10}spay & \cellcolor{red!10}stray \\ 
  \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}audits & \cellcolor{blue!10}procedures & \cellcolor{blue!10}controls & \cellcolor{blue!10}implemented & \cellcolor{blue!10}accountability \\ 
  \cellcolor{blue!10}avenue & \cellcolor{blue!10}west & \cellcolor{blue!10}east & \cellcolor{blue!10}south & \cellcolor{blue!10}north & \cellcolor{blue!10}thence & \cellcolor{blue!10}street \\ 
  \cellcolor{white}historic & \cellcolor{white}revival & \cellcolor{white}landmarks & \cellcolor{white}landmark & \cellcolor{white}craftsman & \cellcolor{white}bungalow & \cellcolor{white}style \\ 
  \cellcolor{red!10}remodel & \cellcolor{red!10}monoxide & \cellcolor{red!10}alarms & \cellcolor{red!10}roofing & \cellcolor{red!10}heater & \cellcolor{red!10}description & \cellcolor{red!10}bathroom \\ 
  \cellcolor{red!10}motion & \cellcolor{red!10}alderman & \cellcolor{red!10}seconded & \cellcolor{red!10}carried & \cellcolor{red!10}whiting & \cellcolor{red!10}unanimously & \cellcolor{red!10}ayes \\ 
  \cellcolor{white}pruning & \cellcolor{white}tree & \cellcolor{white}forestry & \cellcolor{white}trees & \cellcolor{white}mulch & \cellcolor{white}planting & \cellcolor{white}planted \\ 
  \cellcolor{red!10}fittings & \cellcolor{red!10}joints & \cellcolor{red!10}thickness & \cellcolor{red!10}pipe & \cellcolor{red!10}trench & \cellcolor{red!10}valve & \cellcolor{red!10}psi \\ 
  \cellcolor{white}students & \cellcolor{white}learning & \cellcolor{white}schools & \cellcolor{white}student & \cellcolor{white}academic & \cellcolor{white}career & \cellcolor{white}education \\ 
  \cellcolor{red!20}plat & \cellcolor{red!20}sign & \cellcolor{red!20}pud & \cellcolor{red!20}petitioner & \cellcolor{red!20}petition & \cellcolor{red!20}variance & \cellcolor{red!20}subdivision \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

### 2018-04-30 paper/manuscript.tex
A LOT of changes, additions and fixes to the whole city and mayor scraping, processing, analyzing, etc.
finished up collating the URLs and party information from all the data sources we have right now; everything is now combined; created two tables with summary statistics and put them in the manuscript
new results table for stm run on new data
added discussion of the boilerplate classifier to the manuscript

@@
 \usepackage{comment}
+\usepackage{xcolor, colortbl}
 %\usepackage{fullwidth}
@@
 
+\subsection*{Boilerplate Classification}
+
+In order to determine whether a line should be discarded, we train a simple classifier.
+We sampled 100 lines from documents from Anchorage, Alaska - 20 of which ocurred 1-4, 5-9, 10-19, 20-39 and over 40 times within the city\footnote{For the paper, we should increase the sample size sample lines from more than just one city.
+But I don't want to go through the effort of doing all this hand-coding until we're actually sure if and how we are going to use this.}.
+These lines were hand-coded as either substantively useful or useless.
+Then we trained a logit model with this usefulness measure as the dependent variable.
+The independent variables were: (1) number of times the line was duplicated within the city, (2) length of the line, in characters, (3) number of tokens in the line, and (4) the average keyness of the terms in the line.
+The purpose of these covariates is as following:
+
+The length of the line and the number of tokens are a way to find lines consisting of only a word or two.
+This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us.
+These terms also happen to be fairly common, which causes them to be overweighted by the topic model.
+
+To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included.
+Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to create topics that are highly correlated with cities.
+
+Finally, the keyness measure: This indicator shows whether a term occurs disproportionally frequently in one document collection, compared to another.
+In our case, this would be one city's documents, compared to all others.
+Mathematically, this is a simple chi-square test, asserting whether the frequency of a word in a city is greater than its expected count, as determined by its count in all other documents, and the number of tokens in the city.
+The variable used in the model is the chi-square value of this test for each word (which varies and is therefore calculated individually for each city).\footnote{Or alternatively, the log of the absolute chi-square value, after which the previously negative values are made negative again.}
+
+A regression table for this model can be found in table 3.
+The associated accuracy in 5-fold cross-validation is 0.8325.
+The cross-validation accuracy of a simplified model with only the number of characters as a covariate is 0.825 (table 4).
+A model with the four covariates described above as well as interaction terms between each of them yields an accuracy of 0.885 (table 5).
+
+\input{tables/boilerplateClassifier1.tex}
+\input{tables/boilerplateClassifier2.tex}
+\input{tables/boilerplateClassifier3.tex}
+
+Although not implemented yet, the idea is to use this classifier to flag and remove all lines that are not classified as substantively useful (if we want to be cautious, we could choose to only do that for lines that are classified as, for example, having a 60\% chance (or some other number greater than 50\%) of not being substantively useful).
+
 \section{Bag-of-Words Text Analysis}
@@
 
+%ground truth test
+\begin{figure}[htp]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
+	\caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
+	\label{groundtruth}
+\end{figure}
+
+%Ground truth test between top100 mayors and IN + LA; with bootstrapped confidence bounds
+% label: groundtruth_bootstrapped
+\input{tables/groundtruth_bootstrapped.tex}
+
+\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
+
 \section{Conclusion}
@@
 Through an application to the analysis of municipal websites in Indiana and Louisiana, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
+
+\input{tables/urlSummary.tex}
+\input{tables/stateUrlSummary.tex}
 

### 2018-04-30 thresholdClassification.R

@@ -1,0 +1,113 @@
+testDF <- data.frame(linesRemove)
+
+test1_4 <- as.character(sample(test$linesRemove[test$Freq>=1 & test$Freq<=4], 100, F))
+test5_9 <- as.character(sample(test$linesRemove[test$Freq>=5 & test$Freq<=9], 100, F))
+test10_19 <- as.character(sample(test$linesRemove[test$Freq>=10 & test$Freq<=19], 100, F))
+test20_39 <- as.character(sample(test$linesRemove[test$Freq>=20 & test$Freq<=39], 100, F))
+test40 <- as.character(sample(test$linesRemove[test$Freq>=40], 100, F))
+
+test <- c(test1_4, test5_9, test10_19, test20_39, test40)
+test <- tibble::tibble(text = test, number = rep(c("1-4", "5-9", "10-19", "20-39", "40plus"), each = 100))
+
+test.ind <- sample(c(1:500), 500, F)
+
+test.text <- test$text[test.ind]
+test.number <- test$number[test.ind]
+test.text <- as.data.frame(test.text)
+
+test.text$class <- NA
+
+test.text.class <- c(F,T,T,F,T,F,F,F,T,T,F,F,T,F,F,F,T,F,F,F,F,F,F,F,F,F,T,F,T,F,F,F,T,T,F,F,F,T,F,F,F,F,F,T,T,T,T,F,F,T,T,F,T,F,T,F,F,T,T,F,F,T,T,F,T,F,T,F,T,T,T,T,T,T,T,T,F,T,F,F,T,F,T,F,F,F,F,T,F,T,T,T,T,F,T,T,F,T,T,T)
+
+library(ggplot2)
+
+results <- tibble::tibble(number = test.number[1:100], substantive = test.text.class)
+
+ggplot(results, aes(x = substantive, color = number)) + geom_bar()
+ggsave("../Dropbox/govWebsitesMovingVan/numberDuplicate_substantive.pdf")
+
+results2 <- tibble::tibble(textlength = nchar(as.character(test.text$test.text[1:100])), substantive = test.text.class)
+
+ggplot(results2, aes(x = substantive, y = textlength)) + geom_point()
+ggsave("../Dropbox/govWebsitesMovingVan/nchar_substantive.pdf")
+
+results3 <- cbind(results, results2)
+results3 <- results3[,1:3]
+results3$text <- as.character(test.text$test.text[1:100])
+results3$realDuplicate <- NA
+for(i in 1:100){
[…]

### 2018-05-09 paper/manuscript.tex
added background on the significance of gov website use

@@
 Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
+
+Some papers on how government websites are used
+\begin{itemize}
+\item \cite{sandoval2012government}, p.S74, ``Usually citizens access government websites to find information and
+data for decision making''.
+\item In a survey conducted among a random sample of citizens in the state of Georgia in 2000, \cite{thomas2003new} found that nearly 25\% of internet users in the sample reported visiting a local government website in the previous twelve months to gather information.
+We would expect that number to be even larger nearly two decades later.
+\item \cite{tolbert2006effects} p.
+355, ``We ?nd that users of local government Web sites are more likely to trust local governments, controlling for other demo-graphic factors, and that the use of government Web sites is associated with other positive attitudes, espe-cially for federal and local governments.
+''
+\end{itemize}
 

### 2018-05-22 boilerplateClassifier.R
hand-coded training data; applied classifier; results in the manuscript

@@ -1,0 +1,55 @@
+library(stargazer)
+library(quanteda)
+
+trainingData <- read.csv("data/classifierTrainingDataCoded.csv")
+trainingData$linesRemove <- as.character(trainingData$linesRemove)
+trainingData$nchar <- nchar(trainingData$linesRemove)
+#count the number of tokens
+tks <- tokens(trainingData$linesRemove)
+trainingData$nwords <- unlist(lapply(tks, length))
+rm(tks)
+names(trainingData) <- c("id", "text", "freq", "class", "city", "prob", "medianDocMidDist", "nchars", "nwords")
+#
+
+# Classifier
+
+#new model
+
+trainingData$folds <- sample(rep(1:5, 100), 500, replace = F)
+crossval_results <- list()
+for(i in 1:5){
+  m1 <- glm(class ~ nchars + nwords + medianDocMidDist + prob + freq, data = trainingData[trainingData$folds!=i,])
+  #summary(m1)
+  
+  #true values
+  true0id <- which(trainingData$class[trainingData$folds!=i]==0)
+  true1id <- which(trainingData$class[trainingData$folds!=i]==1)
+  
+  #predicted
+  predProbs <- predict(m1, trainingData[trainingData$folds!=i,])
+  pred1id <- which(predProbs>=0.5)
+  pred0id <- which(predProbs<=0.5)
+  
+  #percent correctly predicted
+  pcp <- mean(as.logical(predProbs>=0.5) == as.logical(trainingData$class[trainingData$folds!=i]==1))
+  #true positives
+  tp <- length(which(pred1id%in%true1id))
+  #false positives
+  fp <- length(which(pred1id%in%true0id))
+  #false negatives
+  fn <- length(which(pred0id%in%true1id))
+  #precision
+  prec <- tp/(tp+fp)
+  #recall
+  rec <- tp/(tp+fn)
+  #f1 score
+  f1 <- 2*((prec*rec)/(prec+rec))
+  #add to results list
+  crossval_results[[i]] <- c(pcp, prec, rec, f1)
+  names(crossval_results[[i]]) <- c("pcp", "prec", "rec", "f1")
+}
+apply(do.call(rbind, crossval_results), 2, mean)
+stargazer(m1)
+writeLines(stargazer(m1), "paper/tables/boilerplateClassifier1.tex")
+
+write.csv(trainingData, "data/classifierTrainingDataCoded2.csv", row.names = F)

### 2018-05-23 paper/manuscript.tex
revised section on boilerplate text
hand-coded training data; applied classifier; results in the manuscript
added random forest with inverse probability weighting

@@
 To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the hunspell R package, to remove all non-English words.
-However, hunspell does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
+One, we use spellchecking, implemented through the hunspell R package, to remove all non-English words.\footnote{Some of the cities, for example Los Angeles, do contain a sizable proportion of Spanish content.
+The analysis of this content is beyond the scope of this paper, but could be explored in future work, for example relying on multilingual word embeddings.
+Since the removal of non-English words is very computationally-intensive, we only take this step at the end of the preprocessing process, the result of which might be a slightly adverse effect on the accuracy of the boilerplate classifier.} However, hunspell does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
 Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
@@
 As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods.
+This is a common issue with textual data in which informative content is embedded in technically structured documents.
+See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
 Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
@@
 \input{tables/boilerplateClassifier1.tex}
-\input{tables/boilerplateClassifier2.tex}
-\input{tables/boilerplateClassifier3.tex}
+\input{tables/boilerplateClassifierRFMetrics.tex}
+\input{tables/boilerplateClassifierRFImportance.tex}
 

### 2018-05-23 paper/tables/boilerplateClassifierRFMetrics.tex
added random forest with inverse probability weighting

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Wed May 23 15:57:06 2018
\begin{table}[ht]
\centering
\begin{tabular}{rr}
  \hline
 & Value \\ 
  \hline
Percent Correctly Predicted & 0.88 \\ 
  Precision & 0.88 \\ 
  Recall & 0.91 \\ 
  F1-Score & 0.89 \\ 
   \hline
\end{tabular}
\caption{Performance metrics for random forest boilerplate classifier, with IPW weighting.} 
\end{table}

### 2018-05-23 boilerplateClassifierTrainingData.R

@@ -36,6 +36,11 @@ for(city in 1:length(f)){
   
   #remove empty lines
   linesTable <- linesTable[linesTable$linesRemove!="",]
+  
+  #record the total number of lines per city
+  lineInfo <- paste(str_replace(f_file[city], ".rdata", ""), sum(linesTable$Freq), length(linesTable$Freq), sep = ",")
+  write.table(lineInfo, file = "data/cityLines.txt", append = T, col.names = F, row.names = F, quote = F)
+
   #create the variable to be coded
   linesTable$class <- 0
   #include the city name

### 2018-05-23 paper/tables/boilerplateClassifierRFMetrics.tex
comparison between weighting schemes for RF. Differences are fairly small.

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Wed May 23 15:57:06 2018
+% Wed May 23 16:31:52 2018
 \begin{table}[ht]
 \centering
-\begin{tabular}{rr}
+\begin{tabular}{rrrr}
   \hline
- & Value \\ 
+ & IPW & Prob & No Weight \\ 
   \hline
-Percent Correctly Predicted & 0.88 \\ 
-  Precision & 0.88 \\ 
-  Recall & 0.91 \\ 
-  F1-Score & 0.89 \\ 
+Percent Correctly Predicted & 0.88 & 0.89 & 0.89 \\ 
+  Precision & 0.88 & 0.89 & 0.89 \\ 
+  Recall & 0.91 & 0.92 & 0.91 \\ 
+  F1-Score & 0.90 & 0.90 & 0.90 \\ 
    \hline
 \end{tabular}
-\caption{Performance metrics for random forest boilerplate classifier, with IPW weighting.} 
+\caption{Performance metrics for random forest boilerplate classifier, with either Inverse Probability Weights (IPW), probabilty (of being in the training sample) (prob), or no weighting.} 
 \end{table}

### 2018-05-25 paper/manuscript.tex
included inverse probability weights in the calculation of performance metrics for the random forest and updated the description in the paper

@@
 Existing research has relied on manual methods of website data collection and processing.
-Reliance on manual collection and processing limits the scale and scope of website content analysis.
+However, reliance on manual collection and processing limits the scale and scope of website content analysis.
 We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques.
@@
 \subsection*{Boilerplate Classification}
+In order to determine whether a line should be discarded, we train a simple classifier.
+We sampled 100 lines from documents each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
+To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.
+To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in the classifier.\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
 
-In order to determine whether a line should be discarded, we train a simple classifier.
-We sampled 100 lines from documents from Anchorage, Alaska - 20 of which ocurred 1-4, 5-9, 10-19, 20-39 and over 40 times within the city\footnote{For the paper, we should increase the sample size sample lines from more than just one city.
-But I don't want to go through the effort of doing all this hand-coding until we're actually sure if and how we are going to use this.}.
-These lines were hand-coded as either substantively useful or useless.
-Then we trained a logit model with this usefulness measure as the dependent variable.
-The independent variables were: (1) number of times the line was duplicated within the city, (2) length of the line, in characters, (3) number of tokens in the line, and (4) the average keyness of the terms in the line.
+These 500 lines were then hand-coded as either substantively useful or useless.
+Then we trained a random forest with this usefulness measure as the dependent variable.
+The independent variables were: (1) number of times the line was duplicated within the city, (2) length of the line, in characters, (3) number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself.
 The purpose of these covariates is as following:
@@
 
-Finally, the keyness measure: This indicator shows whether a term occurs disproportionally frequently in one document collection, compared to another.
+Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
+Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures.
+Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.
+
+We rely on random forests as a classifier, which offer slightly better performance than logit\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} and have the added benefit of giving estimates of variable importance.
+Performance of this classifier was assessed through five-fold cross-validation, the results of which can be found in table \ref{randomForest}.
+
+%Finally, the keyness measure: This indicator shows whether a term occurs disproportionally frequently in one document collection, compared to another.
 In our case, this would be one city's documents, compared to all others.
@@
 
-A regression table for this model can be found in table 3.
+%A regression table for this model can be found in table 3.
 The associated accuracy in 5-fold cross-validation is 0.8325.
@@
 
-\input{tables/boilerplateClassifier1.tex}
+%\input{tables/boilerplateClassifier1.tex}
 \input{tables/boilerplateClassifierRFMetrics.tex}
-\input{tables/boilerplateClassifierRFImportance.tex}
+%\input{tables/boilerplateClassifierRFImportance.tex}
 
@@
 BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
+As noted by \cite{GrimmerStewart2013}, for most applications, bag-of-words approaches have been found to be more than sufficient.
+Furthermore, there is reason to believe that city government websites are a particularly `safe' case for bag-of-words methods due to their informative, manner-of-fact based language.
+It is extremely unlikely for these pages to feature ambiguous language such as an abundance of negation or even sarcasm.
 

### 2018-05-25 paper/tables/boilerplateClassifierRFMetrics.tex
included inverse probability weights in the calculation of performance metrics for the random forest and updated the description in the paper

--- 2018-05-23 paper/tables/boilerplateClassifierRFMetrics.tex
@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Wed May 23 15:57:06 2018
+% Fri May 25 13:34:16 2018
 \begin{table}[ht]
@@
   \hline
-Percent Correctly Predicted & 0.88 \\ 
-  Precision & 0.88 \\ 
-  Recall & 0.91 \\ 
-  F1-Score & 0.89 \\ 
+Percent Correctly Predicted & 0.89 \\ 
+  Precision & 0.89 \\ 
+  Recall & 0.94 \\ 
+  F1-Score & 0.92 \\ 
    \hline
 \end{tabular}
-\caption{Performance metrics for random forest boilerplate classifier, with IPW weighting.} 
+\caption{Performance metrics for random forest boilerplate classifier, with inverse probability weights.} 
+\label{randomForest}
 \end{table}

### 2018-05-25 boilerplateClassifier.R

@@ -12,7 +12,7 @@ rm(tks)
 names(trainingData) <- c("id", "text", "freq", "class", "city", "prob", "medianDocMidDist", "nchars", "nwords")
 #
 
-# Classifier
+# Logit Classifier
 
 #new model
 trainingData$folds <- sample(rep(1:5, 100), 500, replace = F)
@@ -120,7 +120,7 @@ trainingDataRF$class <- as.factor(trainingDataRF$class)
 
 crossval_results <- list()
 for(i in 1:5){
-
+  
   mRF <- train(class ~ freq + medianDocMidDist + nchars + nwords, 
                data = trainingDataRF[trainingData$folds!=i,], 
                method = "ranger",
@@ -138,13 +138,15 @@ for(i in 1:5){
   pred0id <- which(predClasses==0)
   
   #percent correctly predicted
-  pcp <- mean(as.logical(predClasses==1) == as.logical(trainingData$class[trainingData$folds==i]==1))
+  true_weight <- sum(trainingDataRF$ipw_scaled[trainingData$folds==i][as.logical(predClasses==1) == as.logical(trainingData$class[trainingData$folds==i]==1)])
+  false_weight <- sum(trainingDataRF$ipw_scaled[trainingData$folds==i][as.logical(predClasses==1) != as.logical(trainingData$class[trainingData$folds==i]==1)])
+  pcp <- true_weight/(true_weight+false_weight)
   #true positives
-  tp <- length(which(pred1id%in%true1id))
+  tp <- sum(trainingDataRF$ipw_scaled[trainingData$folds==i][which(pred1id%in%true1id)])
   #false positives
-  fp <- length(which(pred1id%in%true0id))
+  fp <- sum(trainingDataRF$ipw_scaled[trainingData$folds==i][which(pred1id%in%true0id)])
   #false negatives
-  fn <- length(which(pred0id%in%true1id))
+  fn <- sum(trainingDataRF$ipw_scaled[trainingData$folds==i][which(pred0id%in%true1id)])
   #precision
   prec <- tp/(tp+fp)
   #recall
@@ -156,12 +158,12 @@ for(i in 1:5){
   names(crossval_results[[i]]) <- c("pcp", "prec", "rec", "f1")
 }
 
-# export metrix as a latex table
 metrics_mRF <- data.frame(round(apply(do.call(rbind, crossval_results), 2, mean), 3))
 names(metrics_mRF) <- "Value"
[…]

### 2018-06-03 paper/tables/stmTopWords2.tex
stm results

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Sun Jun  3 16:16:27 2018
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllllll}
  \hline
1 & 2 & 3 & 4 & 5 & 6 & 7 \\ 
  \hline
\cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \cellcolor{red!10}sediment \\ 
  \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \cellcolor{red!10}bldg \\ 
  \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \cellcolor{white}portfolio \\ 
  \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \cellcolor{red!10}sin \\ 
  \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \cellcolor{red!30}form \\ 
  \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \cellcolor{blue!10}phase \\ 
  \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \cellcolor{red!10}efficiency \\ 
  \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \cellcolor{white}unfunded \\ 
  \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \cellcolor{white}wall \\ 
  \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \cellcolor{blue!10}mix \\ 
  \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \cellcolor{blue!10}taxi \\ 
  \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \cellcolor{red!10}desktop \\ 
  \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \cellcolor{blue!10}compliance \\ 
  \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \cellcolor{red!10}transgender \\ 
  \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \cellcolor{white}floodplain \\ 
  \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \cellcolor{white}tennis \\ 
  \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \cellcolor{blue!10}statement \\ 
  \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \cellcolor{blue!10}deciduous \\ 
  \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration \\ 
  \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \cellcolor{red!20}spray \\ 
  \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \cellcolor{red!10}solicitation \\ 
  \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \cellcolor{blue!20}allocation \\ 
  \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \cellcolor{white}tourism \\ 
  \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}engagement \\ 
  \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \cellcolor{white}ability \\ 
  \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \cellcolor{red!10}coal \\ 
  \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \cellcolor{red!10}upcoming \\ 
  \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}plaintiff \\ 
  \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \cellcolor{blue!20}commission \\ 
  \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \cellcolor{blue!10}survey \\ 
  \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \cellcolor{red!10}dentist \\ 
  \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \cellcolor{red!20}nice \\ 
  \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue \\ 
  \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \cellcolor{red!10}monthly \\ 
  \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \cellcolor{red!10}classroom \\ 
  \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \cellcolor{red!10}construe \\ 
  \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \cellcolor{blue!10}timely \\ 
  \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \cellcolor{red!40}player \\ 
  \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \cellcolor{blue!10}revision \\ 
  \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}null \\ 
  \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}crossing \\ 
  \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \cellcolor{white}appraisal \\ 
  \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \cellcolor{red!20}symptom \\ 
  \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \cellcolor{blue!10}rent \\ 
  \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \cellcolor{blue!10}lot \\ 
  \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \cellcolor{blue!10}grievance \\ 
  \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \cellcolor{blue!20}reinvestment \\ 
  \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \cellcolor{red!10}violation \\ 
  \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \cellcolor{red!10}bag \\ 
  \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \cellcolor{blue!20}berry \\ 
  \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \cellcolor{red!20}disinfection \\ 
  \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \cellcolor{red!20}spay \\ 
  \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}artifact \\ 
  \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \cellcolor{red!10}fitting \\ 
  \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \cellcolor{red!10}amend \\ 
  \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \cellcolor{red!10}city \\ 
  \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \cellcolor{blue!80}burglary \\ 
  \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \cellcolor{red!10}news \\ 
  \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \cellcolor{red!10}prince \\ 
  \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \cellcolor{white}header \\ 
   \hline
\end{tabular}
\endgroup
\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics. Based on data preprocessed with the classifier.} 
\end{table}

### 2018-06-03 colorTable.R

@@ -20,10 +20,10 @@ cellcolors <- lapply(df$coef, function(x) paste0("\\cellcolor{", f(x), "}"))
 cellcolors[which(df$sig==F)] <- "\\cellcolor{white}"
 topwords3 <- apply(topwords[,1:7], 2, function(x)paste(cellcolors, x, sep = ""))
 
-xtTopwords <- print(xtable(topwords3), 
+xtTopwords <- print(xtable(topwords3, caption = "Top words from a structural topic model with 60 topics and FREX scoring. Based on data preprocessed with the classifier. Colors depict partisanship based on coefficient size. White cells are non-significant topics."), 
       sanitize.text.function = identity,
       label = "tabSTMtopwords",
-      size = "footnotesize",
+      size = "scriptsize",
       include.rownames = FALSE)
 
-writeLines(xtTopwords, con = 'paper/tables/stmTopWords.tex')
+writeLines(xtTopwords, con = 'paper/tables/stmTopWords2.tex')

### 2018-06-14 paper/manuscript.tex
stm results
revising abstract and second section

@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis }
+\title{\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States}
 
@@
 
-A local government's website is a standard and general source of information for citizens and other community stakeholders.
+A local government's website is arguably the most important general source of information about city policies and processes for residents and other community stakeholders.
 Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science.
@@
 However, reliance on manual collection and processing limits the scale and scope of website content analysis.
+Relying on manual data collection requires that researchers focus on a limited number of websites and/or limited types of site content.
 We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques.
@@
 Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
-We propose a new method for dealing with the kind of duplicated content that is commonly found in government websites.
-Finally, we illustrate methods of text analysis using automatically gathered and pre-processed website content.
-We illustrate our methodological pipeline through a new and innovative dataset---the websites of municipal governments in Indiana and Louisiana.
-We build upon recent research that analyzes how change and variation in the partisan control of government relates to content made available on the government's website.
-We explore the association between mayoral partisanship and the content of city websites.
+We propose a new method for dealing with the types of duplicated and boilerplate contents that are commonly found in government websites.
+We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
+We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
+Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about .
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 \section{The Significance of Government Website Content}
-% \cite{grimmelikhuijsen2012developing} conduct an enormously relevant study.
-Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study.
-They focus on Dutch municipal websites, and their approach is fairly limited in scope and highly manual (which we can compliment).
-For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''
 
  According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
-Official city websites allow mayors to do all three.
-Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate.
+Official city websites allow mayors to perform all three of these functions.
+Their offices frequently take a prominent position on the front page, and many websites also feature a picture of the mayor.
+We present an example of this in Figure \ref{fig:eriemayor}.
+The Erie, Pennsylvania website homepage presents an image of Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
 In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents.
@@
 
-Some papers on how government websites are used
-\begin{itemize}
-\item \cite{sandoval2012government}, p.S74, ``Usually citizens access government websites to find information and
-data for decision making''.
-\item In a survey conducted among a random sample of citizens in the state of Georgia in 2000, \cite{thomas2003new} found that nearly 25\% of internet users in the sample reported visiting a local government website in the previous twelve months to gather information.
-We would expect that number to be even larger nearly two decades later.
-\item \cite{tolbert2006effects} p.
-355, ``We ?nd that users of local government Web sites are more likely to trust local governments, controlling for other demo-graphic factors, and that the use of government Web sites is associated with other positive attitudes, espe-cially for federal and local governments.
-''
-\end{itemize}
+\begin{figure}
+\centering
+\includegraphics[scale=0.35]{figures/eriemayor}
+\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
+\label{fig:eriemayor}
+\end{figure}
 
-In addition to the use of city websites for the politicians that control them, variance in content also matters  with regard to the people who visit them.
-Local residents likely rely on city websites to get news about events, hot-button political issues specific to their city, contact city officials or find out addresses or opening hours of city institutions.
-Visitors use city websites to look up local attractions, which are often described in great detail.
-Similarly, prospective residents looking to move, might rely on city websites to inform their decision on whether to relocate there.
-An inviting website emphasizing the city's receptiveness to new residents might make a real difference here.
-Finally, city websites frequently feature sections on business, but there is a lot of variance in this area: Some emphasize economic development, properties, or transportation, whereas others focus on undeveloped land and other business opportunities.
-Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.
+Members of the public visit municipal government websites for a wide variety of purposes \citet{sandoval2012government}, and with significant regularity.
+In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
+Furthermore, the use of a local government website is associated with an individual's perspective on government.
+\citet{tolbert2006effects} finds that users of local government Web sites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
+Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
 
@@
 \input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
+
+\input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
 

### 2018-06-14 paper/manuscript.tex
changes to the results table; last sentence of the abstract

@@
 We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
-Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about .
+Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about the provision of basic utilities and services such as water, electricity, garbage removal and fire safety.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.

### 2018-06-14 paper/tables/stmTopWords2.tex
changes to the results table; last sentence of the abstract

@@
-% latex table generated in R 3.5.0 by xtable 1.8-2 package
-% Sun Jun  3 16:16:27 2018
+% latex table generated in R 3.4.4 by xtable 1.8-2 package
+% Thu Jun 14 14:34:01 2018
 \begin{table}[ht]
@@
 \begingroup\scriptsize
-\begin{tabular}{lllllll}
+\begin{tabular}{rlllllllr}
   \hline
-1 & 2 & 3 & 4 & 5 & 6 & 7 \\ 
+Topic & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & Top Word 7 & Tokens assigned \\ 
   \hline
-\cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \cellcolor{red!10}sediment \\
-  \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \cellcolor{red!10}bldg \\ 
-  \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \cellcolor{white}portfolio \\ 
-  \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \cellcolor{red!10}sin \\ 
-  \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \cellcolor{red!30}form \\ 
-  \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \cellcolor{blue!10}phase \\
-  \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \cellcolor{red!10}efficiency \\
-  \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \cellcolor{white}unfunded \\
-  \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \cellcolor{white}wall \\ 
-  \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \cellcolor{blue!10}mix \\ 
-  \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \cellcolor{blue!10}taxi \\ 
-  \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \cellcolor{red!10}desktop \\
-  \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \cellcolor{blue!10}compliance \\
-  \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \cellcolor{red!10}transgender \\
-  \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \cellcolor{white}floodplain \\ 
-  \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \cellcolor{white}tennis \\ 
-  \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \cellcolor{blue!10}statement \\
-  \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \cellcolor{blue!10}deciduous \\ 
-  \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration \\
-  \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \cellcolor{red!20}spray \\ 
-  \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \cellcolor{red!10}solicitation \\
-  \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \cellcolor{blue!20}allocation \\
-  \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \cellcolor{white}tourism \\
-  \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}engagement \\
-  \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \cellcolor{white}ability \\
-  \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \cellcolor{red!10}coal \\
-  \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \cellcolor{red!10}upcoming \\ 
-  \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}plaintiff \\
-  \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \cellcolor{blue!20}commission \\
-  \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \cellcolor{blue!10}survey \\
-  \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \cellcolor{red!10}dentist \\
-  \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \cellcolor{red!20}nice \\ 
-  \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue \\ 
-  \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \cellcolor{red!10}monthly \\ 
-  \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \cellcolor{red!10}classroom \\ 
-  \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \cellcolor{red!10}construe \\ 
-  \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \cellcolor{blue!10}timely \\
-  \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \cellcolor{red!40}player \\ 
-  \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \cellcolor{blue!10}revision \\
-  \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}null \\ 
-  \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}crossing \\
-  \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \cellcolor{white}appraisal \\ 
-  \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \cellcolor{red!20}symptom \\
-  \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \cellcolor{blue!10}rent \\
-  \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \cellcolor{blue!10}lot \\ 
-  \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \cellcolor{blue!10}grievance \\
-  \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \cellcolor{blue!20}reinvestment \\
-  \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \cellcolor{red!10}violation \\
-  \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \cellcolor{red!10}bag \\ 
-  \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \cellcolor{blue!20}berry \\ 
-  \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \cellcolor{red!20}disinfection \\
-  \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \cellcolor{red!20}spay \\ 
-  \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}artifact \\
-  \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \cellcolor{red!10}fitting \\ 
-  \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \cellcolor{red!10}amend \\ 
-  \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \cellcolor{red!10}city \\ 
-  \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \cellcolor{blue!80}burglary \\
-  \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \cellcolor{red!10}news \\ 
-  \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \cellcolor{red!10}prince \\ 
-  \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \cellcolor{white}header \\ 
+ 38 & \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \cellcolor{red!40}player & 3770 \\
+    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \cellcolor{red!30}form & 260 \\ 
+   43 & \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \cellcolor{red!20}symptom & 2469 \\
+   20 & \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \cellcolor{red!20}spray & 1290 \\
+   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \cellcolor{red!20}spay & 1152 \\
+   51 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \cellcolor{red!20}disinfection & 487 \\
+   32 & \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \cellcolor{red!20}nice & 1940 \\ 
+   36 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \cellcolor{red!10}construe & 433 \\
+   27 & \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \cellcolor{red!10}upcoming & 302 \\
+   58 & \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \cellcolor{red!10}news & 1298 \\
+   33 & \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue & 459 \\
+   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \cellcolor{red!10}monthly & 241 \\ 
+   35 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \cellcolor{red!10}classroom & 710 \\
+   56 & \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \cellcolor{red!10}city & 229 \\
+   21 & \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \cellcolor{red!10}solicitation & 485 \\
+   59 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \cellcolor{red!10}prince & 487 \\
+   49 & \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \cellcolor{red!10}bag & 1635 \\
+   31 & \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \cellcolor{red!10}dentist & 706 \\
+   54 & \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \cellcolor{red!10}fitting & 1477 \\
+   14 & \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \cellcolor{red!10}transgender & 1095 \\
+    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \cellcolor{red!10}sediment & 490 \\
+    2 & \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \cellcolor{red!10}bldg & 1317 \\ 
+    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \cellcolor{red!10}sin & 1377 \\ 
+   55 & \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \cellcolor{red!10}amend & 457 \\
+   26 & \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \cellcolor{red!10}coal & 1278 \\
+   48 & \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \cellcolor{red!10}violation & 489 \\
+   12 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \cellcolor{red!10}desktop & 917 \\
+    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \cellcolor{red!10}efficiency & 740 \\
+   16 & \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \cellcolor{white}tennis & 702 \\ 
+   60 & \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \cellcolor{white}header & 316 \\ 
+    3 & \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \cellcolor{white}portfolio & 502 \\ 
+   23 & \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \cellcolor{white}tourism & 862 \\
+   25 & \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \cellcolor{white}ability & 683 \\
+    8 & \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \cellcolor{white}unfunded & 289 \\
+    9 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \cellcolor{white}wall & 1103 \\ 
+   15 & \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \cellcolor{white}floodplain & 1454 \\
+   42 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \cellcolor{white}appraisal & 343 \\
+   30 & \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \cellcolor{blue!10}survey & 540 \\
+   53 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}artifact & 2518 \\
+   11 & \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \cellcolor{blue!10}taxi & 435 \\
+   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \cellcolor{blue!10}deciduous & 2279 \\
+   45 & \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \cellcolor{blue!10}lot & 300 \\
+   19 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration & 360 \\
+   13 & \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \cellcolor{blue!10}compliance & 239 \\
+    6 & \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \cellcolor{blue!10}phase & 189 \\
+   46 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \cellcolor{blue!10}grievance & 398 \\
+   28 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}plaintiff & 1747 \\
+   40 & \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}null & 257 \\
+   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \cellcolor{blue!10}mix & 336 \\
+   39 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \cellcolor{blue!10}revision & 274 \\
+   37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \cellcolor{blue!10}timely & 402 \\
+   44 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \cellcolor{blue!10}rent & 340 \\
+   17 & \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \cellcolor{blue!10}statement & 259 \\
+   41 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}crossing & 527 \\
+   24 & \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}engagement & 313 \\
+   50 & \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \cellcolor{blue!20}berry & 674 \\
+   22 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \cellcolor{blue!20}allocation & 236 \\
+   47 & \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \cellcolor{blue!20}reinvestment & 215 \\
+   29 & \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \cellcolor{blue!20}commission & 353 \\
+   57 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \cellcolor{blue!80}burglary & 1255 \\
    \hline

### 2018-06-14 paper/tables/stmTopWords2.tex
added barplot to the results table

--- 2018-06-03 paper/tables/stmTopWords2.tex
@@
-% latex table generated in R 3.5.0 by xtable 1.8-2 package
-% Sun Jun  3 16:16:27 2018
+% latex table generated in R 3.4.4 by xtable 1.8-2 package
+% Thu Jun 14 16:31:41 2018
 \begin{table}[ht]
@@
 \begingroup\scriptsize
-\begin{tabular}{lllllll}
+\begin{tabular}{rllllllll}
   \hline
-1 & 2 & 3 & 4 & 5 & 6 & 7 \\ 
+ \# & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & \multicolumn{2}{c}{Tokens assigned} \\ 
   \hline
-\cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \cellcolor{red!10}sediment \\
-  \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \cellcolor{red!10}bldg \\ 
-  \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \cellcolor{white}portfolio \\ 
-  \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \cellcolor{red!10}sin \\ 
-  \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \cellcolor{red!30}form \\ 
-  \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \cellcolor{blue!10}phase \\
-  \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \cellcolor{red!10}efficiency \\
-  \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \cellcolor{white}unfunded \\
-  \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \cellcolor{white}wall \\ 
-  \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \cellcolor{blue!10}mix \\ 
-  \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \cellcolor{blue!10}taxi \\ 
-  \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \cellcolor{red!10}desktop \\
-  \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \cellcolor{blue!10}compliance \\
-  \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \cellcolor{red!10}transgender \\
-  \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \cellcolor{white}floodplain \\ 
-  \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \cellcolor{white}tennis \\ 
-  \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \cellcolor{blue!10}statement \\
-  \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \cellcolor{blue!10}deciduous \\ 
-  \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration \\
-  \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \cellcolor{red!20}spray \\ 
-  \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \cellcolor{red!10}solicitation \\
-  \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \cellcolor{blue!20}allocation \\
-  \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \cellcolor{white}tourism \\
-  \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}engagement \\
-  \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \cellcolor{white}ability \\
-  \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \cellcolor{red!10}coal \\
-  \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \cellcolor{red!10}upcoming \\ 
-  \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}plaintiff \\
-  \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \cellcolor{blue!20}commission \\
-  \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \cellcolor{blue!10}survey \\
-  \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \cellcolor{red!10}dentist \\
-  \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \cellcolor{red!20}nice \\ 
-  \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue \\ 
-  \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \cellcolor{red!10}monthly \\ 
-  \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \cellcolor{red!10}classroom \\ 
-  \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \cellcolor{red!10}construe \\ 
-  \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \cellcolor{blue!10}timely \\
-  \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \cellcolor{red!40}player \\ 
-  \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \cellcolor{blue!10}revision \\
-  \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}null \\ 
-  \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}crossing \\
-  \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \cellcolor{white}appraisal \\ 
-  \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \cellcolor{red!20}symptom \\
-  \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \cellcolor{blue!10}rent \\
-  \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \cellcolor{blue!10}lot \\ 
-  \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \cellcolor{blue!10}grievance \\
-  \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \cellcolor{blue!20}reinvestment \\
-  \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \cellcolor{red!10}violation \\
-  \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \cellcolor{red!10}bag \\ 
-  \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \cellcolor{blue!20}berry \\ 
-  \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \cellcolor{red!20}disinfection \\
-  \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \cellcolor{red!20}spay \\ 
-  \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}artifact \\
-  \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \cellcolor{red!10}fitting \\ 
-  \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \cellcolor{red!10}amend \\ 
-  \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \cellcolor{red!10}city \\ 
-  \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \cellcolor{blue!80}burglary \\
-  \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \cellcolor{red!10}news \\ 
-  \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \cellcolor{red!10}prince \\ 
-  \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \cellcolor{white}header \\ 
+ 38 & \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \mybar{3770} \\ 
+    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \mybar{260} \\ 
+   43 & \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \mybar{2469} \\ 
+   20 & \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \mybar{1290} \\ 
+   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \mybar{1152} \\ 
+   51 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \mybar{487} \\ 
+   32 & \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \mybar{1940} \\ 
+   36 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \mybar{433} \\ 
+   27 & \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \mybar{302} \\ 
+   58 & \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \mybar{1298} \\ 
+   33 & \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \mybar{459} \\ 
+   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \mybar{241} \\ 
+   35 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \mybar{710} \\ 
+   56 & \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \mybar{229} \\ 
+   21 & \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \mybar{485} \\ 
+   59 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \mybar{487} \\ 
+   49 & \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \mybar{1635} \\ 
+   31 & \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \mybar{706} \\ 
+   54 & \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \mybar{1477} \\ 
+   14 & \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \mybar{1095} \\
+    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \mybar{490} \\ 
+    2 & \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \mybar{1317} \\ 
+    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \mybar{1377} \\ 
+   55 & \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \mybar{457} \\ 
+   26 & \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \mybar{1278} \\
+   48 & \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \mybar{489} \\ 
+   12 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \mybar{917} \\
+    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \mybar{740} \\ 
+   16 & \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{702} \\ 
+   60 & \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \mybar{316} \\ 
+    3 & \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \mybar{502} \\ 
+   23 & \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \mybar{862} \\ 
+   25 & \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \mybar{683} \\ 
+    8 & \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \mybar{289} \\ 
+    9 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1103} \\ 
+   15 & \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \mybar{1454} \\ 
+   42 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \mybar{343} \\ 
+   30 & \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \mybar{540} \\
+   53 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \mybar{2518} \\
+   11 & \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \mybar{435} \\ 
+   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \mybar{2279} \\ 
+   45 & \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \mybar{300} \\ 
+   19 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \mybar{360} \\
+   13 & \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \mybar{239} \\ 
+    6 & \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \mybar{189} \\
+   46 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \mybar{398} \\ 
+   28 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \mybar{1747} \\
+   40 & \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \mybar{257} \\ 
+   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \mybar{336} \\ 
+   39 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \mybar{274} \\ 
+   37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \mybar{402} \\
+   44 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \mybar{340} \\
+   17 & \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{259} \\
+   41 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \mybar{527} \\
+   24 & \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \mybar{313} \\
+   50 & \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \mybar{674} \\ 
+   22 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \mybar{236} \\
+   47 & \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \mybar{215} \\
+   29 & \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \mybar{353} \\ 
+   57 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \mybar{1255} \\ 
    \hline

### 2018-06-24 paper/manuscript.tex
added barplot to the results table
revisions to the data seection

@@
 \usepackage{comment}
+\usepackage{pgf}
 \usepackage{xcolor, colortbl}
+\usepackage{array}
+
+\def\mybar#1{%%
+	#1 & {\color{red}\pgfmathsetlengthmacro\x{#1*0.006mm}\rule{\x}{4pt}}}
+
+%\pgfmathsetlengthmacro\x{#1^0.1mm}
+%\show\x -> 25.0pt
+
 %\usepackage{fullwidth}
@@
 Researchers have found that in order to identify the constituencies, motives and modes of communication of these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-\cite{Druckman2009,Druckman2010} rely on the Mational Journal to find the websites, then hand-coded them.
+\cite{Druckman2009,Druckman2010} rely on the National Journal to find the websites, then hand-coded them.
 \cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, the webservice of the Internet Archive we discussed recently.
@@
 \section{Data}
-In this section we introduce the data we use in our application---the analysis of municipal websites in Louisiana and Indiana.
+In this section we introduce the data we use in our application---the analysis of municipal websites in six states - Indiana, Louisiana, New York, Washington, California and Texas.
+These states provide us with a sample that is well-balanced on a number of theoretically important indicators.
+One, each of the four geographic regions is represented with at least one state.
+Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities less densely populated areas are covered.
+Furthermore, the sample is politically balanced -  we have three blue states (CA, WA, NY) and three red states (TX, IN, LA).
+Finally, our dataset contains some of the wealthiest states (NY, CA, WA and TX are \#2, \#8, \#9 and \#16 respectively, by GDP per capita \citep{BureauofEconomicAnalysis2017}), but also some of the poorer ones (IN and LA).
+In terms of pure GDP per capita, the sample is on the less affluent side - however, wealth is also correlated with poverty: CA is the state with the highest poverty rate in the country, and LA, NY and TX follow closely \citep{Fox2017}.
+
 The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.

### 2018-06-24 paper/manuscript.tex
revisions to sections 1 and 2

@@
 Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g., ][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra}.
+The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra}.
 Despite the potential for automated scraping of website contents, the conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
@@
 In this paper we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis.
-We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in Indiana and Louisiana correlate with the partisanship of the city mayor.
+We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states (IN, LA, NY, WA, CA and TX) correlate with the partisanship of the city mayor.
 
@@
 Researchers have found that in order to identify the constituencies, motives and modes of communication of these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-\cite{Druckman2009,Druckman2010} rely on the National Journal to find the websites, then hand-coded them.
-\cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, the webservice of the Internet Archive we discussed recently.
+\cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them.
+\cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, a webservice of the Internet Archive.
+Unfortunately we found the data provided by the Internet Archive to not be sufficiently reliable and well-documented for our own purpose.
 \cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.

### 2018-06-24 paper/manuscript.tex
further revisions to the data section (scraping from Wikipedia, description of how the partisanship information was acquired, Census API)

@@
 \cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, a webservice of the Internet Archive.
-Unfortunately we found the data provided by the Internet Archive to not be sufficiently reliable and well-documented for our own purpose.
+Unfortunately we found the data provided by the Internet Archive to not be sufficiently reliable and well-documented for our own purposes.
 \cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
@@
 
-The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
-This list is updated once per month - we rely on the version released on January 16, 2017.
-The data from the GSA contains the following variables: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV').
+We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
+This method proved to be very reliable.
+Two, the General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}\footnote{This list is updated once per month - we rely on the version released on January 16, 2017.
+The data from the GSA contains the following data: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV').
 Two, the type of government entity to which the domain is registered, such as city, county, federal agency, etc.
 Three, for federal agencies, the name is specfied.
-Finally, the city in which the domain is registered, is noted.
+Finally, the city in which the domain is registered, is noted.}.
+Naturally, this list does not contain cities which do not use a .gov website (or, in many cases, a city owns a registered .gov address, but uses a different one),.
+Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
 
-Here, we focus only on cities.
-As a first step, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver) to test whether all of the city websites actually work.
-Of the 2425 domains listed by the GSA as cities, 292 are not accessible.
-Furthermore, the .gov domain, as registered at the GSA, is frequently not the website a city actually uses.
-In many cases, these sites redirect to another address, sometimes not a .gov domain (in this case, we simply use this domain).
-We record these URLs.
+Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former, and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
 
-In order to provide an overview of our coverage (as not all cities, towns and villages use .gov addresses), we merge this list with U.S.
-Census data\footnote{http://www2.census.gov/programs-surveys/popest/datasets/2010-2015/cities/totals/sub-est2015\_all.csv}.
-Here, several limitations in the GSA data need to be accounted for: One, even though the GSA nominally separates websites of cities and counties, some of the domains categorized as cities actually belong to counties.
-The same is true for townships and boroughs.
-Ergo, we eliminate all websites belonging to these three types of entities by hand.
-Furthermore, the city name, as given by the GSA, refers to the city in which the domain is registered, which is not necessarily equivalent to the city the website serves.
-In many cases, a website of a larger city may be registered to one of its subdivisions (for example, the website of New York is registered to Brooklyn), or vice versa (for example, the website of Homecroftin, a small town within Indianapolis, is registered to the city as a whole).
-Consequently we fix mismatches between websites and cities manually.
-Finally, a number of cities are simply misspelled, which we also correct by hand.
+To test whether the websites we found actually work, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver).
+This is necessary because a) some city websites simply don't work, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
+A webdriver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
+This allows us to subsequently record and use the new URL for the actual website scraping.
+
+The partisanship of each city is coded in different ways, depending on the state.
+For Indiana, where elections are nominally partisan, this information is accessible through the state government's website\footnote{\url{http://www.in.gov/apps/sos/election/general/general2015?page=office&countyID=1&officeID=32&districtID=-1&candidate=}}.
+For Louisiana, we received data on the outcomes of mayoral elections from the LEAP project\footnote{\url{http://www.leap-elections.org/}}.
+For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and recorded candidates who received money from party committees.
+For California and Texas, where our data consists of major cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
+Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
+When compared to the other data sources above, (and manual searches in case of conflicts) this method once again proved to be very reliable, and added additional cases to our dataset even for Indiana and Louisiana.
+Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
+
+Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
+Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
 

### 2018-06-24 paper/manuscript.tex
removed a bunch of old tables and figures - further revisions necessary

@@
 
-\begin{landscape}
-\input{tables/filenumbers.tex}
-\end{landscape}
-
 For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results. Consequently we restricted our corpus to cities with at least 3 documents.
@@
 %Partisan top words - stm Louisiana -- Rep
-\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
+%\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
 
 %Partisan top words - stm Louisiana -- Dem
-\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
+%\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
 
 %Partisan top words - stm Louisiana -- Rep
-\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
+%\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
 
 %Partisan top words - stm Louisiana -- Dem
-\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
+%\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
 
@@
 %Heatmaps
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
+%	\label{heatmaps_weights}
+%	\includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
+%\end{figure}
+
+%US map
 \begin{figure}[htp]
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
-	\label{heatmaps_weights}
-	\includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
-\end{figure}
-
-%Indiana map
-\begin{figure}[htp]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Cities in the corpus, by partisanship of mayor.}
-	\label{indiana_map}
-	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
+	\caption{Cities in the corpus, by partisanship of mayor. \textbf{REVISE to remove everything not in our six states.}}
+	\label{us_map}
+	\includegraphics[width=\linewidth]{figures/us_map.pdf}
 \end{figure}
@@
 %stm results
-\begin{figure}[htp]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
 This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
-	\label{stm_results}
-%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-\end{figure}
+%	\label{stm_results}
+%%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
+%\end{figure}
 
 %Partisan top words - topic model Indiana
-\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
+%\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
 
 %Partisan top words - topic model Louisiana
-\input{tables/partisanTopWordsLA.tex} %tabLDALA
+%\input{tables/partisanTopWordsLA.tex} %tabLDALA
 
@@
 %Some basic descriptive statistics of documents by party
-\input{tables/descriptiveStatisticsPartisanIN.tex}
+%\input{tables/descriptiveStatisticsPartisanIN.tex}
 
 %Some basic descriptive statistics of documents by party
-\input{tables/descriptiveStatisticsPartisanLA.tex}
+%\input{tables/descriptiveStatisticsPartisanLA.tex}
 
 %fightin words results
-\begin{figure}[htp]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
-	\label{linesCutoff}
-\end{figure}
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
+%		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
+%	\label{linesCutoff}
+%\end{figure}
 
@@
 %ground truth test
-\begin{figure}[htp]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
-	\caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
-	\label{groundtruth}
-\end{figure}
-
-%ground truth test
-\begin{figure}[htp]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
-	\caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
-	\label{groundtruth}
-\end{figure}
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
+%	\caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
+%	\label{groundtruth}
+%\end{figure}
+%
+%%ground truth test
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
+%	\caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
+%	\label{groundtruth}
+%\end{figure}
 
@@
 % label: groundtruth_bootstrapped
-\input{tables/groundtruth_bootstrapped.tex}
+%\input{tables/groundtruth_bootstrapped.tex}
 
-\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
+%\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
 

### 2018-06-24 paper/manuscript.tex
revised section 4 (web to text pipeline) and removd section 6 (since we decided to hold off on the ground truth test for now)

@@
 \section{The Web to Text Pipeline}
-
-In the methodological pipeline from native website files to text data that is appropriate for comparative analysis we address two methodological challenges.
+In this methodological pipeline from native website files to text data that is appropriate for comparative analysis, we address two methodological challenges.
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
@@
 For the most part, the file type of a document can be correctly determined through its ending.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of garbage text, stemming from incorrectly converted documents, as well as a general decrease in the amount of usable data.
+However, there are exceptions to this, which, if ignored, can lead to large amounts of garbage text, arising from incorrectly converted documents, which leads to a general decrease in the amount of usable data.
 Two issues in particular need to be addressed: One, HTML files on city websites frequently do not have an ending, but are still perfectly readable if correctly identified as such.
-Second, some documents contain the incorrect file ending - for example, we found thousands of documents on the New Orleans city website that ended in .html, when they were actually PDFs.
-To accurately assess their type, we read in the first line of each document, which, if it is an HTML or PDF file, contains a string indicating as much.
+Second, some documents contain the incorrect file ending - for example, we found thousands of documents that ended in .html, when they were actually PDFs.
+To accurately assess their type, we rely on the R package wand, which is an R interface to the Unix library libmagic, which determines the type of a file on the basis of its file signature.
 Consequently we rename all documents so that their file ending reflects their actual file type.
@@
 Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive to our models while increasing their computational cost, we also discard any token types that occur in only one document.
+We also conduct lemmatization to reduce words to their basic form.
 
@@
 See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
-Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
+In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at this level.
+
+%this is outdated; not deleting it yet in case we need it for further reference
+%Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
 We count how many times each line is duplicated for that city.
@@
 
-Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
+Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
 Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures.
@@
 
-Although not implemented yet, the idea is to use this classifier to flag and remove all lines that are not classified as substantively useful (if we want to be cautious, we could choose to only do that for lines that are classified as, for example, having a 60\% chance (or some other number greater than 50\%) of not being substantively useful).
+This classifier is then used to flag and remove all lines that are not classified as substantively useful.
+The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e.
+a city that isn't part of our sample used in the analysis) as an example in figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4} in the appendix.
+Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common.
+After the removal, the distribution looks more like what it should be - lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
+Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}).
+Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results.
+However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
 
@@
 
-\section{Ground truth test}
-In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
+%\section{Ground truth test}
+%In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
 Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
@@
 Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
-
-In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
+%
+%In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
 As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
@@
 If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
-
-Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
+%
+%Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
 We do the same for the city documents, and the compare the four document collections using cosine similarity.
@@
 \bibliography{ref}
+
+\newpage
+\section*{Appendix}
+\begin{figure}[htp]
+	\centering
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
+	\label{boilerplate_before_after1}
+	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
+\end{figure}
+\begin{figure}[htp]
+	\centering
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
+	\label{boilerplate_before_after2}
+	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
+\end{figure}
+\begin{figure}[htp]
+	\centering
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
+	\label{boilerplate_before_after3}
+	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
+\end{figure}
+\begin{figure}[htp]
+	\centering
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
+	\label{boilerplate_before_after4}
+	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
+\end{figure}
 

### 2018-06-26 paper/tables/stmTopWords120.tex
stm with 120 topics, similar findings as the one with 60

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Jun 26 15:42:11 2018
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{rllllllll}
  \hline
 \# & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & \multicolumn{2}{c}{Tokens assigned} \\ 
  \hline
 93 & \cellcolor{red!30}kindness & \cellcolor{red!30}winner & \cellcolor{red!30}hero & \cellcolor{red!30}famous & \cellcolor{red!30}tribute & \cellcolor{red!30}wager & \mybar{3042} \\ 
   36 & \cellcolor{red!20}copy & \cellcolor{red!20}record & \cellcolor{red!20}request & \cellcolor{red!20}mail & \cellcolor{red!20}submit & \cellcolor{red!20}fax & \mybar{111} \\ 
   98 & \cellcolor{red!20}community & \cellcolor{red!20}resident & \cellcolor{red!20}mission & \cellcolor{red!20}quality & \cellcolor{red!20}excellent & \cellcolor{red!20}life & \mybar{78} \\ 
   52 & \cellcolor{red!20}county & \cellcolor{red!20}leg & \cellcolor{red!20}legislator & \cellcolor{red!20}legislature & \cellcolor{red!20}town & \cellcolor{red!20}municipality & \mybar{132} \\ 
   18 & \cellcolor{red!20}often & \cellcolor{red!20}always & \cellcolor{red!20}sometimes & \cellcolor{red!20}never & \cellcolor{red!20}easy & \cellcolor{red!20}even & \mybar{505} \\ 
   20 & \cellcolor{red!20}click & \cellcolor{red!20}blog & \cellcolor{red!20}email & \cellcolor{red!20}copyright & \cellcolor{red!20}dream & \cellcolor{red!20}sorry & \mybar{336} \\ 
   38 & \cellcolor{red!10}camp & \cellcolor{red!10}yoga & \cellcolor{red!10}library & \cellcolor{red!10}camper & \cellcolor{red!10}fun & \cellcolor{red!10}librarian & \mybar{1009} \\ 
   43 & \cellcolor{red!10}antibody & \cellcolor{red!10}infection & \cellcolor{red!10}hepatitis & \cellcolor{red!10}tuberculosis & \cellcolor{red!10}infect & \cellcolor{red!10}viral & \mybar{1551} \\ 
   66 & \cellcolor{red!10}drinking & \cellcolor{red!10}water & \cellcolor{red!10}reservoir & \cellcolor{red!10}contaminant & \cellcolor{red!10}irrigation & \cellcolor{red!10}tap & \mybar{228} \\ 
   68 & \cellcolor{red!10}spray & \cellcolor{red!10}mosquito & \cellcolor{red!10}pesticide & \cellcolor{red!10}pest & \cellcolor{red!10}repellent & \cellcolor{red!10}soap & \mybar{898} \\ 
   33 & \cellcolor{red!10}fire & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue & \cellcolor{red!10}apparatus & \cellcolor{red!10}emergency & \mybar{271} \\ 
   56 & \cellcolor{red!10}holiday & \cellcolor{red!10}weekend & \cellcolor{red!10}parade & \cellcolor{red!10}event & \cellcolor{red!10}auburn & \cellcolor{red!10}host & \mybar{283} \\ 
   44 & \cellcolor{red!10}microchip & \cellcolor{red!10}cat & \cellcolor{red!10}euthanasia & \cellcolor{red!10}spay & \cellcolor{red!10}rabies & \cellcolor{red!10}neuter & \mybar{1229} \\ 
   70 & \cellcolor{red!10}election & \cellcolor{red!10}ethic & \cellcolor{red!10}ballot & \cellcolor{red!10}political & \cellcolor{red!10}candidate & \cellcolor{red!10}lobbyist & \mybar{382} \\ 
   60 & \cellcolor{red!10}shall & \cellcolor{red!10}unless & \cellcolor{red!10}except & \cellcolor{red!10}mean & \cellcolor{red!10}deem & \cellcolor{red!10}forth & \mybar{103} \\ 
   59 & \cellcolor{red!10}motion & \cellcolor{red!10}unanimously & \cellcolor{red!10}adjourn & \cellcolor{red!10}prince & \cellcolor{red!10}carry & \cellcolor{red!10}ken & \mybar{220} \\ 
   81 & \cellcolor{red!10}effluent & \cellcolor{red!10}sludge & \cellcolor{red!10}wastewater & \cellcolor{red!10}mercury & \cellcolor{red!10}lbs & \cellcolor{red!10}gal & \mybar{537} \\ 
   89 & \cellcolor{red!10}ask & \cellcolor{red!10}explain & \cellcolor{red!10}say & \cellcolor{red!10}reply & \cellcolor{red!10}suggest & \cellcolor{red!10}ruff & \mybar{427} \\ 
    5 & \cellcolor{red!10}home & \cellcolor{red!10}family & \cellcolor{red!10}homeowner & \cellcolor{red!10}single & \cellcolor{red!10}residence & \cellcolor{red!10}cottage & \mybar{94} \\ 
  105 & \cellcolor{red!10}proposer & \cellcolor{red!10}breach & \cellcolor{red!10}franchisee & \cellcolor{red!10}indemnify & \cellcolor{red!10}agree & \cellcolor{red!10}hereunder & \mybar{273} \\ 
  119 & \cellcolor{red!10}alderman & \cellcolor{red!10}councilor & \cellcolor{red!10}councilwoman & \cellcolor{red!10}alderwoman & \cellcolor{red!10}common & \cellcolor{red!10}roll & \mybar{260} \\ 
   14 & \cellcolor{red!10}borough & \cellcolor{red!10}exam & \cellcolor{red!10}trademark & \cellcolor{red!10}veteran & \cellcolor{red!10}immigrant & \cellcolor{red!10}new & \mybar{359} \\ 
  116 & \cellcolor{red!10}asthma & \cellcolor{red!10}overdose & \cellcolor{red!10}diabetes & \cellcolor{red!10}obesity & \cellcolor{red!10}hospitalization & \cellcolor{red!10}prevalence & \mybar{609} \\ 
   37 & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}deductible & \cellcolor{red!10}coinsurance & \cellcolor{red!10}prescription & \cellcolor{red!10}copay & \mybar{444} \\ 
   67 & \cellcolor{red!10}plat & \cellcolor{red!10}thence & \cellcolor{red!10}easement & \cellcolor{red!10}pud & \cellcolor{red!10}petitioner & \cellcolor{red!10}annexation & \mybar{271} \\ 
   35 & \cellcolor{red!10}parent & \cellcolor{red!10}youth & \cellcolor{red!10}child & \cellcolor{red!10}mentor & \cellcolor{red!10}literacy & \cellcolor{red!10}foster & \mybar{326} \\ 
   75 & \cellcolor{red!10}website & \cellcolor{red!10}plain & \cellcolor{red!10}please & \cellcolor{red!10}online & \cellcolor{red!10}customize & \cellcolor{red!10}contact & \mybar{98} \\ 
   21 & \cellcolor{red!10}bid & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontractor & \cellcolor{red!10}contract & \cellcolor{red!10}procurement & \mybar{238} \\ 
   95 & \cellcolor{red!10}duct & \cellcolor{red!10}valve & \cellcolor{red!10}splice & \cellcolor{red!10}piping & \cellcolor{red!10}conduit & \cellcolor{red!10}conductor & \mybar{850} \\ 
   83 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}sewer & \cellcolor{red!10}sanitary & \cellcolor{red!10}infiltration & \mybar{224} \\ 
   64 & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}disability & \cellcolor{red!10}race & \cellcolor{red!10}religion & \cellcolor{red!10}racial & \mybar{437} \\ 
   32 & \cellcolor{red!10}think & \cellcolor{red!10}really & \cellcolor{red!10}thing & \cellcolor{red!10}something & \cellcolor{red!10}maybe & \cellcolor{red!10}just & \mybar{899} \\ 
   49 & \cellcolor{red!10}recycling & \cellcolor{red!10}recycle & \cellcolor{red!10}garbage & \cellcolor{red!10}trash & \cellcolor{red!10}waste & \cellcolor{red!10}bin & \mybar{405} \\ 
    3 & \cellcolor{red!10}maturity & \cellcolor{red!10}portfolio & \cellcolor{red!10}rating & \cellcolor{red!10}jun & \cellcolor{red!10}yield & \cellcolor{red!10}investment & \mybar{276} \\ 
    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}payment & \cellcolor{red!10}card & \cellcolor{red!10}cash & \cellcolor{red!10}account & \cellcolor{red!10}amt & \mybar{222} \\ 
   12 & \cellcolor{red!10}password & \cellcolor{red!10}header & \cellcolor{red!10}archive & \cellcolor{red!10}browser & \cellcolor{red!10}folder & \cellcolor{red!10}text & \mybar{552} \\ 
   90 & \cellcolor{red!10}student & \cellcolor{red!10}school & \cellcolor{red!10}elementary & \cellcolor{red!10}college & \cellcolor{red!10}academic & \cellcolor{red!10}graduate & \mybar{303} \\ 
   48 & \cellcolor{red!10}application & \cellcolor{red!10}applicant & \cellcolor{red!10}must & \cellcolor{red!10}certificate & \cellcolor{red!10}license & \cellcolor{red!10}proof & \mybar{150} \\ 
   92 & \cellcolor{red!10}food & \cellcolor{red!10}calorie & \cellcolor{red!10}meat & \cellcolor{red!10}vend & \cellcolor{red!10}utensil & \cellcolor{red!10}salad & \mybar{1291} \\ 
   86 & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}resolve & \cellcolor{red!10}bond & \cellcolor{red!10}anticipation & \cellcolor{red!10}redemption & \mybar{194} \\ 
   26 & \cellcolor{red!10}petroleum & \cellcolor{red!10}spill & \cellcolor{red!10}contamination & \cellcolor{red!10}asbestos & \cellcolor{red!10}contaminate & \cellcolor{red!10}radioactive & \mybar{444} \\ 
    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}sin & \mybar{644} \\ 
    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \cellcolor{red!10}efficiency & \mybar{416} \\ 
   22 & \cellcolor{red!10}wireless & \cellcolor{red!10}server & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}cable & \cellcolor{red!10}technology & \mybar{376} \\ 
   76 & \cellcolor{red!10}year & \cellcolor{red!10}fiscal & \cellcolor{red!10}five & \cellcolor{red!10}annual & \cellcolor{red!10}last & \cellcolor{red!10}three & \mybar{50} \\ 
   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}cost & \cellcolor{red!10}plus & \cellcolor{red!10}hourly & \mybar{109} \\ 
  109 & \cellcolor{red!10}city & \cellcolor{red!10}fort & \cellcolor{red!10}manager & \cellcolor{red!10}worth & \cellcolor{red!10}hall & \cellcolor{red!10}municipal & \mybar{10} \\ 
  103 & \cellcolor{red!10}com & \cellcolor{red!10}perm & \cellcolor{red!10}tor & \cellcolor{red!10}cigarette & \cellcolor{red!10}loo & \cellcolor{red!10}comm & \mybar{1386} \\ 
   79 & \cellcolor{red!10}tow & \cellcolor{red!10}plow & \cellcolor{red!10}vehicle & \cellcolor{red!10}trailer & \cellcolor{red!10}motor & \cellcolor{red!10}truck & \mybar{594} \\ 
   54 & \cellcolor{red!10}dwell & \cellcolor{red!10}building & \cellcolor{red!10}remodel & \cellcolor{red!10}unit & \cellcolor{red!10}occupancy & \cellcolor{red!10}alteration & \mybar{132} \\ 
   23 & \cellcolor{red!10}name & \cellcolor{red!10}address & \cellcolor{red!10}description & \cellcolor{red!10}number & \cellcolor{red!10}list & \cellcolor{red!10}zip & \mybar{92} \\ 
   69 & \cellcolor{red!10}vista & \cellcolor{red!10}ranch & \cellcolor{red!10}suite & \cellcolor{red!10}trinity & \cellcolor{red!10}coliseum & \cellcolor{red!10}mesa & \mybar{657} \\ 
   61 & \cellcolor{red!10}cannabis & \cellcolor{red!10}marijuana & \cellcolor{red!10}cultivation & \cellcolor{red!10}dispensary & \cellcolor{red!10}collective & \cellcolor{red!10}liquor & \mybar{470} \\ 
  114 & \cellcolor{red!10}beach & \cellcolor{red!10}orange & \cellcolor{red!10}platinum & \cellcolor{red!10}resort & \cellcolor{red!10}ocean & \cellcolor{red!10}angel & \mybar{517} \\ 
    1 & \cellcolor{red!10}landlord & \cellcolor{red!10}tenant & \cellcolor{red!10}lease & \cellcolor{red!10}lessee & \cellcolor{red!10}golf & \cellcolor{red!10}rent & \mybar{288} \\ 
  118 & \cellcolor{white}flood & \cellcolor{white}earthquake & \cellcolor{white}floodplain & \cellcolor{white}hurricane & \cellcolor{white}tornado & \cellcolor{white}disaster & \mybar{513} \\ 
   99 & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}awning & \cellcolor{white}masonry & \cellcolor{white}brick & \cellcolor{white}vinyl & \mybar{729} \\ 
  111 & \cellcolor{white}buffalo & \cellcolor{white}player & \cellcolor{white}league & \cellcolor{white}ballpark & \cellcolor{white}baseball & \cellcolor{white}football & \mybar{542} \\ 
  112 & \cellcolor{white}excavation & \cellcolor{white}trench & \cellcolor{white}excavate & \cellcolor{white}gravel & \cellcolor{white}silt & \cellcolor{white}concrete & \mybar{696} \\ 
   53 & \cellcolor{white}downtown & \cellcolor{white}mall & \cellcolor{white}hotel & \cellcolor{white}midtown & \cellcolor{white}uptown & \cellcolor{white}shopping & \mybar{531} \\ 
   \hline
\end{tabular}
\endgroup
\caption{Top words from a structural topic model with 120 topics (first 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
\end{table}

### 2018-06-26 paper/tables/stmTopWords120_2.tex
stm with 120 topics, similar findings as the one with 60

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Jun 26 15:42:11 2018
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{rllllllll}
  \hline
 \# & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & \multicolumn{2}{c}{Tokens assigned} \\ 
  \hline
 53 & \cellcolor{white}downtown & \cellcolor{white}mall & \cellcolor{white}hotel & \cellcolor{white}midtown & \cellcolor{white}uptown & \cellcolor{white}shopping & \mybar{531} \\ 
  117 & \cellcolor{white}police & \cellcolor{white}patrol & \cellcolor{white}chief & \cellcolor{white}lieutenant & \cellcolor{white}captain & \cellcolor{white}swear & \mybar{283} \\ 
    2 & \cellcolor{red!10}page & \cellcolor{red!10}yon & \cellcolor{red!10}rev & \cellcolor{red!10}sou & \cellcolor{red!10}spec & \cellcolor{red!10}gen & \mybar{165} \\ 
  100 & \cellcolor{white}senate & \cellcolor{white}house & \cellcolor{white}butler & \cellcolor{white}hook & \cellcolor{white}rep & \cellcolor{white}haven & \mybar{590} \\ 
   55 & \cellcolor{white}chapter & \cellcolor{white}code & \cellcolor{white}section & \cellcolor{white}subsection & \cellcolor{white}article & \cellcolor{white}amend & \mybar{124} \\ 
   19 & \cellcolor{white}fugitive & \cellcolor{white}noise & \cellcolor{white}exhaust & \cellcolor{white}receptor & \cellcolor{white}coal & \cellcolor{white}ozone & \mybar{437} \\ 
   31 & \cellcolor{white}aviation & \cellcolor{white}taxicab & \cellcolor{white}airport & \cellcolor{white}runway & \cellcolor{white}airline & \cellcolor{white}hangar & \mybar{498} \\ 
   85 & \cellcolor{white}homeless & \cellcolor{white}homelessness & \cellcolor{white}supportive & \cellcolor{white}client & \cellcolor{white}transitional & \cellcolor{white}encampment & \mybar{232} \\ 
   42 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}deduction & \cellcolor{white}taxpayer & \cellcolor{white}appraisal & \mybar{160} \\ 
   80 & \cellcolor{white}artist & \cellcolor{white}artwork & \cellcolor{white}art & \cellcolor{white}exhibition & \cellcolor{white}gallery & \cellcolor{white}artistic & \mybar{1060} \\ 
   65 & \cellcolor{white}density & \cellcolor{white}land & \cellcolor{white}us & \cellcolor{white}urban & \cellcolor{white}village & \cellcolor{white}growth & \mybar{102} \\ 
  101 & \cellcolor{white}marsh & \cellcolor{white}riparian & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}grassland & \cellcolor{white}freshwater & \mybar{1110} \\ 
  120 & \cellcolor{blue!10}bend & \cellcolor{blue!10}rogers & \cellcolor{blue!10}walnut & \cellcolor{blue!10}grape & \cellcolor{blue!10}parenthood & \cellcolor{blue!10}shalom & \mybar{315} \\ 
  108 & \cellcolor{blue!10}owner & \cellcolor{blue!10}inspector & \cellcolor{blue!10}property & \cellcolor{blue!10}inspection & \cellcolor{blue!10}unsafe & \cellcolor{blue!10}nuisance & \mybar{156} \\ 
  110 & \cellcolor{white}incumbent & \cellcolor{white}ability & \cellcolor{white}supervise & \cellcolor{white}knowledge & \cellcolor{white}supervision & \cellcolor{white}essential & \mybar{378} \\ 
  102 & \cellcolor{blue!10}parking & \cellcolor{blue!10}space & \cellcolor{blue!10}height & \cellcolor{blue!10}garage & \cellcolor{blue!10}foot & \cellcolor{blue!10}lot & \mybar{83} \\ 
   30 & \cellcolor{blue!10}figure & \cellcolor{blue!10}census & \cellcolor{blue!10}population & \cellcolor{blue!10}respondent & \cellcolor{blue!10}comparison & \cellcolor{blue!10}table & \mybar{240} \\ 
   71 & \cellcolor{blue!10}economic & \cellcolor{blue!10}workforce & \cellcolor{blue!10}economy & \cellcolor{blue!10}industry & \cellcolor{blue!10}sector & \cellcolor{blue!10}job & \mybar{312} \\ 
   91 & \cellcolor{blue!10}prune & \cellcolor{blue!10}forestry & \cellcolor{blue!10}tree & \cellcolor{blue!10}planting & \cellcolor{blue!10}shrub & \cellcolor{blue!10}root & \mybar{1092} \\ 
   28 & \cellcolor{blue!10}conviction & \cellcolor{blue!10}guilty & \cellcolor{blue!10}offense & \cellcolor{blue!10}convict & \cellcolor{blue!10}misdemeanor & \cellcolor{blue!10}felony & \mybar{762} \\ 
  115 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}mitigate & \cellcolor{blue!10}measure & \mybar{135} \\ 
   27 & \cellcolor{blue!10}workshop & \cellcolor{blue!10}learn & \cellcolor{blue!10}tour & \cellcolor{blue!10}upcoming & \cellcolor{blue!10}get & \cellcolor{blue!10}view & \mybar{119} \\ 
   16 & \cellcolor{blue!10}park & \cellcolor{blue!10}recreation & \cellcolor{blue!10}playground & \cellcolor{blue!10}picnic & \cellcolor{blue!10}trail & \cellcolor{blue!10}zoo & \mybar{253} \\ 
   15 & \cellcolor{blue!10}landmark & \cellcolor{blue!10}historic & \cellcolor{blue!10}revival & \cellcolor{blue!10}preservation & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}historical & \mybar{936} \\ 
   10 & \cellcolor{blue!10}ave & \cellcolor{blue!10}rainier & \cellcolor{blue!10}beacon & \cellcolor{blue!10}aurora & \cellcolor{blue!10}greenwood & \cellcolor{blue!10}capitol & \mybar{353} \\ 
   51 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}boat & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}maritime & \cellcolor{blue!10}dock & \cellcolor{blue!10}port & \mybar{788} \\ 
   82 & \cellcolor{blue!10}avenue & \cellcolor{blue!10}east & \cellcolor{blue!10}west & \cellcolor{blue!10}north & \cellcolor{blue!10}street & \cellcolor{blue!10}south & \mybar{78} \\ 
   73 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}pension & \cellcolor{blue!10}retirement & \cellcolor{blue!10}retiree & \cellcolor{blue!10}unfunded & \cellcolor{blue!10}contribution & \mybar{181} \\ 
    6 & \cellcolor{blue!10}variance & \cellcolor{blue!10}setback & \cellcolor{blue!10}fence & \cellcolor{blue!10}exception & \cellcolor{blue!10}yard & \cellcolor{blue!10}nonconforming & \mybar{122} \\ 
   46 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}complaint & \cellcolor{blue!10}bias & \cellcolor{blue!10}allege & \mybar{631} \\ 
   25 & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}plaintiff & \cellcolor{blue!10}examiner & \cellcolor{blue!10}creditor & \cellcolor{blue!10}trial & \cellcolor{blue!10}appeal & \mybar{843} \\ 
   78 & \cellcolor{blue!10}violent & \cellcolor{blue!10}gang & \cellcolor{blue!10}violence & \cellcolor{blue!10}inmate & \cellcolor{blue!10}crime & \cellcolor{blue!10}offender & \mybar{710} \\ 
   97 & \cellcolor{blue!10}employee & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}overtime & \mybar{243} \\ 
   77 & \cellcolor{blue!10}board & \cellcolor{blue!10}appoint & \cellcolor{blue!10}chairperson & \cellcolor{blue!10}secretary & \cellcolor{blue!10}member & \cellcolor{blue!10}vice & \mybar{137} \\ 
   24 & \cellcolor{blue!10}grant & \cellcolor{blue!10}funding & \cellcolor{blue!10}program & \cellcolor{blue!10}fund & \cellcolor{blue!10}federal & \cellcolor{blue!10}match & \mybar{49} \\ 
  104 & \cellcolor{blue!10}project & \cellcolor{blue!10}improvement & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}replacement & \cellcolor{blue!10}phase & \cellcolor{blue!10}appropriated & \mybar{84} \\ 
   94 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditing & \cellcolor{blue!10}deficiency & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}weakness & \mybar{195} \\ 
   13 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}successor & \cellcolor{blue!10}redevelopment & \cellcolor{blue!10}oversight & \cellcolor{blue!10}disposition & \mybar{128} \\ 
    9 & \cellcolor{blue!10}realm & \cellcolor{blue!10}design & \cellcolor{blue!10}proponent & \cellcolor{blue!10}courtyard & \cellcolor{blue!10}facade & \cellcolor{blue!10}concept & \mybar{468} \\ 
   96 & \cellcolor{blue!10}propose & \cellcolor{blue!10}draft & \cellcolor{blue!10}comment & \cellcolor{blue!10}alternative & \cellcolor{blue!10}plan & \cellcolor{blue!10}planning & \mybar{68} \\ 
  106 & \cellcolor{blue!10}sidewalk & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}signal & \cellcolor{blue!10}traffic & \cellcolor{blue!10}intersection & \cellcolor{blue!10}curb & \mybar{269} \\ 
   41 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}transit & \cellcolor{blue!10}bus & \cellcolor{blue!10}route & \cellcolor{blue!10}mobility & \mybar{279} \\ 
   63 & \cellcolor{blue!10}memorandum & \cellcolor{blue!10}council & \cellcolor{blue!10}resolution & \cellcolor{blue!10}negotiation & \cellcolor{blue!10}manager & \cellcolor{blue!10}ward & \mybar{132} \\ 
   39 & \cellcolor{blue!10}commission & \cellcolor{blue!10}committee & \cellcolor{blue!10}commissioner & \cellcolor{blue!10}advisory & \cellcolor{blue!10}chair & \cellcolor{blue!10}discussion & \mybar{126} \\ 
   84 & \cellcolor{blue!10}implement & \cellcolor{blue!10}monitor & \cellcolor{blue!10}performance & \cellcolor{blue!10}inventory & \cellcolor{blue!10}process & \cellcolor{blue!10}track & \mybar{146} \\ 
  107 & \cellcolor{blue!10}budget & \cellcolor{blue!10}appropriation & \cellcolor{blue!10}fund & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}adopt & \cellcolor{blue!10}levy & \mybar{99} \\ 
   62 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}household & \cellcolor{blue!10}income & \cellcolor{blue!10}renter & \mybar{224} \\ 
   17 & \cellcolor{blue!10}million & \cellcolor{blue!10}revenue & \cellcolor{blue!10}forecast & \cellcolor{blue!10}offset & \cellcolor{blue!10}deficit & \cellcolor{blue!10}projection & \mybar{187} \\ 
   74 & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}vision & \cellcolor{blue!10}attractive & \cellcolor{blue!10}node & \cellcolor{blue!10}amenity & \cellcolor{blue!10}corridor & \mybar{351} \\ 
   45 & \cellcolor{blue!10}zoning & \cellcolor{blue!10}district & \cellcolor{blue!10}zone & \cellcolor{blue!10}acre & \cellcolor{blue!10}dist & \cellcolor{blue!10}rezoning & \mybar{71} \\ 
  113 & \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}asset & \cellcolor{blue!10}net & \cellcolor{blue!10}statement & \cellcolor{blue!10}obligation & \mybar{133} \\ 
   72 & \cellcolor{blue!10}rouge & \cellcolor{blue!10}parish & \cellcolor{blue!10}baton & \cellcolor{blue!10}hogan & \cellcolor{blue!10}councilman & \cellcolor{blue!10}bowman & \mybar{528} \\ 
   88 & \cellcolor{blue!10}position & \cellcolor{blue!10}staffing & \cellcolor{blue!10}citywide & \cellcolor{blue!10}analyst & \cellcolor{blue!10}strategic & \cellcolor{blue!10}allocation & \mybar{111} \\ 
   40 & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}mode & \cellcolor{blue!10}false & \cellcolor{blue!10}null & \cellcolor{blue!10}else & \cellcolor{blue!10}tab & \mybar{105} \\ 
   11 & \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}strategic & \cellcolor{blue!10}engagement & \cellcolor{blue!10}outreach & \mybar{168} \\ 
   58 & \cellcolor{blue!10}news & \cellcolor{blue!10}warren & \cellcolor{blue!10}announce & \cellcolor{blue!10}lovely & \cellcolor{blue!10}release & \cellcolor{blue!10}today & \mybar{501} \\ 
   50 & \cellcolor{blue!10}aye & \cellcolor{blue!10}absent & \cellcolor{blue!10}khan & \cellcolor{blue!10}nay & \cellcolor{blue!10}berry & \cellcolor{blue!10}voting & \mybar{318} \\ 
   87 & \cellcolor{blue!20}digest & \cellcolor{blue!20}proposal & \cellcolor{blue!20}reappoints & \cellcolor{blue!20}sander & \cellcolor{blue!20}gray & \cellcolor{blue!20}metropolitan & \mybar{232} \\ 
   29 & \cellcolor{blue!20}agenda & \cellcolor{blue!20}speaker & \cellcolor{blue!20}item & \cellcolor{blue!20}divided & \cellcolor{blue!20}speak & \cellcolor{blue!20}refrain & \mybar{146} \\ 
   47 & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}reinvestment & \cellcolor{blue!20}contingency & \cellcolor{blue!20}contract & \cellcolor{blue!20}authorize & \cellcolor{blue!20}engineering & \mybar{131} \\ 
   57 & \cellcolor{blue!80}suspect & \cellcolor{blue!80}fatal & \cellcolor{blue!80}shoot & \cellcolor{blue!80}pronounce & \cellcolor{blue!80}stopper & \cellcolor{blue!80}gunshot & \mybar{500} \\ 
   \hline
\end{tabular}
\endgroup
\caption{Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
\end{table}

### 2018-07-04 paper/manuscript.tex
stm with 120 topics, similar findings as the one with 60
removed the fightin words section
updated the section on the structural topic model results

@@
 
-\subsection{Informative Dirichlet model}
-%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-For the analysis of the data, we present two approaches, the first being the informative dirichlet model developed by \citep{Monroe2008}.
-This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them with text with greater semantic, and in our case, partisan meaning.
-
-In Indiana, Democrats exhibit a preference for words related to public finance, such as 'fund', 'budget', or 'tax', indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
-This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-Beyond the focus on public finance, the words preferably used by Democrats do not fall into any particularly congruent categories, and largely sort into various areas related to city administration - i.e.
-`council', `services', `budget', `committee', `contract', etc.
-If there is theme around the words preferred by Republicans, it seems to center around city planning - street, fire, water, building, construction, park.
-These words suggest that the hands-off approach favored by Republicans results in a focus on supporting infrastructure and logistics.
-
-%Partisan top words - fightin words Indiana
-\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
-
-For Lousiana, the results (see table \ref{tabFightinLA}) are less coherent.
-Only one of the finance-related terms appears again for Democrats - specifically `fund', although `rate' might also be used in a financial context.
-Beyond that, some focus on a `historic' `'district of a city seems evident, as is the use of some words - `infrastructure', `water', `building' that were used for Republicans in Indiana.
-Conversely, Republicans are now missing these words, and their preferred terms generally do not seem to follow any particular theme.
-
-%Partisan top words - fightin words Louisiana
-\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
-
-The weakness of the fightin' words method is evident here, as a list of words does not necessarily provide sufficient information to glean preferred topics from.
-This is especially the case when the texts are spread across a broad number of issue-areas, with little semantic similarity.
-In \citep{Monroe2008}, the authors focus on the fairly constrained corpus of U.S.
-Senate speeches with respect to abortion - our context, by comparison, is far more eclectic.
-
 \subsubsection{Structural topic model}
-A more powerful approach with the capacity of addressing this problem is the use of topic models.
+A powerful and frequently used approach within the family of BoW methods is the use of topic models.
 This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics.
@@
 
-We use 60 topics - the number recommended by the authors for medium- to large-sized corpora, and party as well as city population (the literature frequently emphasizes city size as a determinant of the issues it faces - see, for example, \cite{Guillamon2013}) as covariates.
-The results are shown in tables \ref{tabSTMINRep} to \ref{tabSTMLADem}.
-The coefficients in the table headers describe the size of the party covariate on a given topic.
-In order to test statistical significance, we calculated credible intervals - the topics shown here are all significant at the 0.1\% level.
+We use 60 topics - the number recommended by the authors for medium- to large-sized corpora.
+Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
+We use four covariates: First, \textit{party}, to test our main hypothesis.
+Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
+Third, we control for wealth by relying on \textit{median income} as a covariate.
+Fourth and finally, we include a \textit{state} variable.
 
-In Indiana, some of the topics associated with Democrats - one related to education, one to recycling  - clearly seem to match the party brand.
-Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}.
+The results are shown in table \ref{stmResultsTable}.
+The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
+The topics that are entirely white are not statistically significant for the party covariate.
+In order to test statistical significance, we calculated credible intervals - the threshold chosen here is the 1\% level.
+
+Many of the topics associated with Democrats - one related to education, one to recycling  - clearly seem to match the party brand.
+For example, topic 44 on affordable housing clearly resonates with the Democratic party's appeal to low-income voters.
+Similarly, employee rights are represented in topic 46.
+Democrats also exhibit a strong preference for words related to public finances, such as topic 22 ('budget', 'revenue', 'expenditure') as well as topic 17 ('debt', 'bond', 'financial').
+We hypothesize that this is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
+This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
+Democrats are the party of big government, and this clearly also shows at the city level.
+A second, conistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement - a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}).
+Finally, Democrats also focus more on the deliberative process of good governance, as topics 29 ('election', 'agenda', 'committee') and 37 ('audit', 'procedure', 'oversight') attest to.
+
+Republicans, meanwhile, live up to their reputation as the party of small government.
+Many topics prevalent in Republican cities focus on the bare essentials.
+Basic utilities such as energy (topic 7), fire protection (topic 33), drinking water (51) and garbage removal (topic 49) are ubiquitous here.
+Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 20 ('snow', 'hurricane', 'tornado') is an important issue.
+
+%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}.
 However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
@@
 
-When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
+%When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
 Furthermore, as with the fightin' words approach, some smaller degree of focus on money (see topic 1) is still evident.
@@
 \input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
+\input{tables/stmTopWords120.tex}
+\input{tables/stmTopWords120_2.tex}
 
@@
 This methodology holds the potential to vastly scale up the data collection efforts underpinning the rapidly growing body of research that is focused on government website analysis.
-Through an application to the analysis of municipal websites in Indiana and Louisiana, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
+Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
 
 \input{tables/urlSummary.tex}
-\input{tables/stateUrlSummary.tex}
+%\input{tables/stateUrlSummary.tex}
 
@@
 
+\begin{figure}[htp]
+	\centering
+	\caption{Five largest topic effects for the population covariate. The fact that the population and epidemiology topics are positively correlated with city size is indicative of the model's validity.}
+	\label{stmEffectPop}
+	\includegraphics[width=\linewidth]{figures/stm_effect_pop.pdf}
+\end{figure}
+
+\begin{figure}[htp]
+	\centering
+	\caption{Five largest topic effects for the median income covariate.
+The fact that the crime topic is most prevalent in poorer cities, good governance is the most positively correlated with income is indicative of the model's validity.}
+	\label{stmEffectIncome}
+	\includegraphics[width=\linewidth]{figures/stm_effect_income.pdf}
+\end{figure}
+
 \end{document}
 
-\begin{enumerate}
-	\item Design
-	\begin{enumerate}
-		\item Choosing the sample
-		\item Finding URLs
-		\item list of .gov websites
-		\item Finding supporting data
-	\end{enumerate}
-	\item Scraping
-		\begin{enumerate}
-			\item wget
-			\item headless browser/Selenium
-			\item Beautifulsoup/rvest
-			\item APIs (httr)
-			\item Wayback Machine
-		\end{enumerate}
-	\item Pre-processing
-		\begin{enumerate}
-			\item Determining document filetype
-			\item File conversion
-			\item Conventional preprocessing (lowercase, numbers, punctuation)
-			\item Stemming and lemmatization
-			\item spellchecking
-			\item Dealing with duplicate text \& html documents in particular
-		\end{enumerate}
-	\item Analysis
-		\begin{enumerate}
-			\item LDA
-			\item Other topic models (structural, author, dynamic -- maybe?)
-			\item SVM (+ other machine learning classifiers?)
-			\item Fightin Words
-		\end{enumerate}
-\end{enumerate}
-
-% latex table generated in R 3.3.3 by xtable 1.8-2 package
-% Wed Mar 22 11:32:43 2017
+%\begin{enumerate}
+%	\item Design
+%	\begin{enumerate}
+%		\item Choosing the sample
+%		\item Finding URLs
+%		\item list of .gov websites
+%		\item Finding supporting data
+%	\end{enumerate}
+%	\item Scraping
+%		\begin{enumerate}
+%			\item wget
+%			\item headless browser/Selenium
+%			\item Beautifulsoup/rvest
+%			\item APIs (httr)
+%			\item Wayback Machine
+%		\end{enumerate}
+%	\item Pre-processing
+%		\begin{enumerate}
+%			\item Determining document filetype
+%			\item File conversion
+%			\item Conventional preprocessing (lowercase, numbers, punctuation)
+%			\item Stemming and lemmatization
+%			\item spellchecking
+%			\item Dealing with duplicate text \& html documents in particular
+%		\end{enumerate}
+%	\item Analysis
+%		\begin{enumerate}
+%			\item LDA
+%			\item Other topic models (structural, author, dynamic -- maybe?)
+%			\item SVM (+ other machine learning classifiers?)
+%			\item Fightin Words
+%		\end{enumerate}
+%\end{enumerate}
+%
+%
+%
+%
+%
+%
+%% latex table generated in R 3.3.3 by xtable 1.8-2 package
+%% Wed Mar 22 11:32:43 2017
+%%\begin{table}[ht]
+%%	\centering
+%%	\begin{tabular}{lrrlrrl}
+%%		\hline
+%%		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
+%%		\hline
+%%		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
+%%		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
+%%		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
+%%		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
+%%		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
+%%		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
+%%		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
+%%		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
+%%		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
+%%		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
+%%		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
+%%		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
+%%		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
+%%		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
+%%		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
+%%		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
+%%		\hline
+%%	\end{tabular}
+%%	\caption{} 
+%%\end{table}
+%
+%\subsection{Research Design}
+%
 %\begin{table}[ht]
 %	\centering
-%	\begin{tabular}{lrrlrrl}
+%	\begin{tabular}{llr}
 %		\hline
-%		City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
+%		Variable & Unit & Source \\
 %		\hline
-%		Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
-%		Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
-%		Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
-%		Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
-%		Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
-%		Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
-%		Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
-%		Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
-%		Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
-%		Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
-%		North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
-%		Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
-%		Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
-%		South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
-%		Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
-%		Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
+%		Population size & 1000 people & Census \\
+%		Population growth last 5 years & Percent & Census \\
+%		Type of economy (agriculture/industry/services) & ? & Census \\
+%		Economic performance (GDP?) & \$ & Census \\
+%		Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
+%		Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
+%		Change of party control & 0/1 & in.gov/sos/elections/ \\
+%		Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
+%		Unemployment rate & Percent & Census \\
+%		Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
 %		\hline
 %	\end{tabular}
-%	\caption{} 
+%	\caption{List of covariates} 
 %\end{table}
-
-\subsection{Research Design}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{llr}
-		\hline
-		Variable & Unit & Source \\
-		\hline
-		Population size & 1000 people & Census \\
-		Population growth last 5 years & Percent & Census \\
-		Type of economy (agriculture/industry/services) & ? & Census \\
-		Economic performance (GDP?) & \$ & Census \\
-		Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-		Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-		Change of party control & 0/1 & in.gov/sos/elections/ \\
-		Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
-		Unemployment rate & Percent & Census \\
-		Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
-		\hline
-	\end{tabular}
-	\caption{List of covariates} 
-\end{table}
-
-\begin{enumerate}
-\item Corpus:
-\begin{enumerate}
-\item Last snapshots before the election (November 3, 2015 in Indiana; tbd. in Louisiana (probably February))
-\item First snapshot that is at least 2 months after the new government's inauguration (which is in January for Indiana, May for Louisiana)
-\end{enumerate}
-\item Preprocessing:
-\begin{enumerate}
-\item restrict corpus to:
-\begin{enumerate}
-\item documents belonging to cities in which a change of power occurred
-\item documents that were added, deleted or changed between the two snapshots
-\end{enumerate}
-\item words to lowercase
-\item remove punctuation
-\item stemming (Porter stemming algorithm?)
-\item Remove stop words (regular list of stop words is enough, since we use an asymmetric prior)
-\end{enumerate}
-\item Apply Grimmer's expressed agenda model to the corpus
-\begin{enumerate}
-\item Asymmetric prior
-\item Each document can have only one topic (in contrast to the author-topic model)
-\item Cities $i = 1,..., n = 15$
-\item Topic $k(k = 1,..., K )$
-\item Documents $j(j = 1,...,D_i)$ from city i
-\item Party covariate in the prior, where the deleted and unmodified documents are coded as from the first, and the added and modified documents from the second party
-\end{enumerate}
-\item Results
-\begin{enumerate}
-\item Label topics using Grimmer's automatic cluster labeling method, based on most commonly used words in documents belonging to topic
-\item Evaluate topics
-\end{enumerate}
-\end{enumerate}
-
-Validation:
-
-\begin{itemize}
-\item Do the above for cities in which no change of power occurred.
-\item Check whether there is higher than average turnover around the new year by comparing changes to non-election years (and also Louisiana, where elections are later).
-\item Check how long documents stay on websites on average. Use websites with a lot of snapshots for this (these exist for both small and large cities).
-\end{itemize}
-
-Problem with using this model: Grimmer's expressed agenda model uses Senators as the actors.
+%
+%
+%
+%\begin{enumerate}
+%\item Corpus:
+%\begin{enumerate}
+%\item Last snapshots before the election (November 3, 2015 in Indiana; tbd. in Louisiana (probably February))
+%\item First snapshot that is at least 2 months after the new government's inauguration (which is in January for Indiana, May for Louisiana)
+%\end{enumerate}
+%\item Preprocessing:
+%\begin{enumerate}
+%\item restrict corpus to:
+%\begin{enumerate}
+%\item documents belonging to cities in which a change of power occurred
+%\item documents that were added, deleted or changed between the two snapshots
+%\end{enumerate}
+%\item words to lowercase
+%\item remove punctuation
+%\item stemming (Porter stemming algorithm?)
+%\item Remove stop words (regular list of stop words is enough, since we use an asymmetric prior)
+%\end{enumerate}
+%\item Apply Grimmer's expressed agenda model to the corpus
+%\begin{enumerate}
+%\item Asymmetric prior
+%\item Each document can have only one topic (in contrast to the author-topic model)
+%\item Cities $i = 1,..., n = 15$
+%\item Topic $k(k = 1,..., K )$
+%\item Documents $j(j = 1,...,D_i)$ from city i
+%\item Party covariate in the prior, where the deleted and unmodified documents are coded as from the first, and the added and modified documents from the second party
+%\end{enumerate}
+%\item Results
+%\begin{enumerate}
+%\item Label topics using Grimmer's automatic cluster labeling method, based on most commonly used words in documents belonging to topic
+%\item Evaluate topics
+%\end{enumerate}
+%\end{enumerate}
+%
+%Validation:
+%
+%\begin{itemize}
+%\item Do the above for cities in which no change of power occurred.
+%\item Check whether there is higher than average turnover around the new year by comparing changes to non-election years (and also Louisiana, where elections are later).
+%\item Check how long documents stay on websites on average. Use websites with a lot of snapshots for this (these exist for both small and large cities).
+%\end{itemize}
+%
+%Problem with using this model: Grimmer's expressed agenda model uses Senators as the actors.
 Senators is also who he is substantively interested in.
@@
 However, we care about parties, not cities.
-
-\subsection{Survival model}
-The existence of individual documents on municipal government websites can be though of as a survival process.
+%
+%\subsection{Survival model}
+%The existence of individual documents on municipal government websites can be though of as a survival process.
 No document stays on a website forever, and it appears to be a reasonable assumption that as documents get older and thus less relevant, they get replaced.
 The factors determining the steepness of the survival curve are the topic - fire safety regulations likely stay up longer than a bulletin on the annual spring banquet - and the change of party control after an election.
-
-\begin{quote}
-\textit{H1}: The older a document, the more likely it is to be removed.
-\end{quote}
-
-$S(t)$ has a downward slope. Admittedly, this is almost impossible not to be true. Also, test proportional, rising and falling hazard models.
-
-\begin{quote}
-\textit{H2}: Documents pertaining to administrative matters are less likely to be removed.
-\end{quote}
-
-Introduce a categorical variable for the top 10(?) topics. A negative coefficient for administrative topics would support this hypothesis.
-
-\begin{quote}
-\textit{H3}: Documents introduced by the opposing party are more likely to be removed.
-\end{quote}
-
-Introduce two variables into the survival model: One variable indicating which party has introduced a document, and a time-varying variable describing which party is currently in government.
+%
+%\begin{quote}
+%\textit{H1}: The older a document, the more likely it is to be removed.
+%\end{quote}
+%
+%$S(t)$ has a downward slope. Admittedly, this is almost impossible not to be true. Also, test proportional, rising and falling hazard models.
+%
+%\begin{quote}
+%\textit{H2}: Documents pertaining to administrative matters are less likely to be removed.
+%\end{quote}
+%
+%Introduce a categorical variable for the top 10(?) topics. A negative coefficient for administrative topics would support this hypothesis.
+%
+%\begin{quote}
+%\textit{H3}: Documents introduced by the opposing party are more likely to be removed.
+%\end{quote}
+%
+%Introduce two variables into the survival model: One variable indicating which party has introduced a document, and a time-varying variable describing which party is currently in government.
 The hypothesis is tested through an interaction term between the two.
-
-\begin{quote}
-\textit{H4a}: Democrats are more likely to remove documents with topics pertaining to private enterprise, private schools.
-\end{quote}
-
-Interaction term between party in power and categorical topic variable.
-
-\begin{quote}
-\textit{H4b}: Republicans are more likely to remove documents with topics pertaining to social justice, equality, taxes, public schools, etc.
-\end{quote}
-
-Interaction term between party in power and categorical topic variable.
-
-\begin{quote}
-\textit{H5}: In line with their commitment to small government, Republicans are more likely than Democrats to remove documents.
-\end{quote}
-
-Party in power variable.\\
-
-This model will take up a lot of degrees of freedom. The rarity of snapshots for some cities might be a problem. Documents being changed and being removed can be modeled as competing risks.
-
-\begin{equation} 
-\label{eq1}
-\begin{split}
-Y & = \text{Party that introduced the document} \\
- & + \text{Party that is currently in power} \\
- & + \text{Topic 1, topic 2, ..., topic k} \\
- & + \text{Party that is currently in power} \times \text{Topic 1, topic 2, ..., topic k} \\
- & + \text{Days since start of mayoral term (control)}
-\end{split}
-\end{equation}
-
-After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
-
-These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
-
-\begin{figure}[htp]
-	\centering
-	\caption{Percentage of state population covered.}
-	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
-\end{figure}
-
-We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
+%
+%\begin{quote}
+%\textit{H4a}: Democrats are more likely to remove documents with topics pertaining to private enterprise, private schools.
+%\end{quote}
+%
+%Interaction term between party in power and categorical topic variable.
+%
+%\begin{quote}
+%\textit{H4b}: Republicans are more likely to remove documents with topics pertaining to social justice, equality, taxes, public schools, etc.
+%\end{quote}
+%
+%Interaction term between party in power and categorical topic variable.
+%
+%\begin{quote}
+%\textit{H5}: In line with their commitment to small government, Republicans are more likely than Democrats to remove documents.
+%\end{quote}
+%
+%Party in power variable.\\
+%
+%
+%This model will take up a lot of degrees of freedom. The rarity of snapshots for some cities might be a problem. Documents being changed and being removed can be modeled as competing risks.
+%
+%
+%\begin{equation} 
+%\label{eq1}
+%\begin{split}
+%Y & = \text{Party that introduced the document} \\
+% & + \text{Party that is currently in power} \\
+% & + \text{Topic 1, topic 2, ..., topic k} \\
+% & + \text{Party that is currently in power} \times \text{Topic 1, topic 2, ..., topic k} \\
+% & + \text{Days since start of mayoral term (control)}
+%\end{split}
+%\end{equation}
+%
+%
+%
+%
+%
+%After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
+%
+%These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
+%
+%\begin{figure}[htp]
+%	\centering
+%	\caption{Percentage of state population covered.}
+%	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
+%\end{figure}
+%
+%We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
 To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
 We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
-
-<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
+%
+%<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
 Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
-
-It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
-
-\begin{enumerate}
-
-\item For what percentage and number of IN cities can we find data from the WBM?
-\item For how many election cycles can we find political leadership data for these matched cities?
-\item In what number and percentage of cities is the local leadership majority Republican? 
-\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D).
-
-\end{enumerate}
-
-\begin{enumerate}
-
-	\item 30 cities, with a combined population of 1,180,435.
+%
+%It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
+%
+%\begin{enumerate}
+%
+%\item For what percentage and number of IN cities can we find data from the WBM?
+%\item For how many election cycles can we find political leadership data for these matched cities?
+%\item In what number and percentage of cities is the local leadership majority Republican? 
+%\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D). 
+%
+%\end{enumerate}
+%
+%\begin{enumerate}
+%	
+%	\item 30 cities, with a combined population of 1,180,435.
 However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
-	\item 2015, 2011, 2007, 2003.
-	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
-	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic.
-
-\end{enumerate}
-
-\section{Running Application: Party Differences in Municipal Websites}
-
-\begin{landscape}
-\begin{table}[htbp]
-	%\caption{}
-	\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-		\hline
-		Names & Year & Journal & Findings & Important? \\ \hline
-		Benedictis-Kessner, Justin De
-		Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
+%	\item 2015, 2011, 2007, 2003.
+%	\item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
+%	\item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic. 
+%	
+%\end{enumerate}
+%
+%
+%
+%
+%\section{Running Application: Party Differences in Municipal Websites}
+%
+%
+%\begin{landscape}
+%\begin{table}[htbp]
+%	%\caption{}
+%	\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+%		\hline
+%		Names & Year & Journal & Findings & Important? \\ \hline
+%		Benedictis-Kessner, Justin De
+%		Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
 Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
-		Caughey, Devin
-		Warshaw, Christopher
-		Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
+%		Caughey, Devin
+%		Warshaw, Christopher
+%		Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
 Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
 & Somewhat \\ \hline
-		Einstein, Katherine Levine
-		Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
+%		Einstein, Katherine Levine
+%		Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
 aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
-		Einstein, Katherine Levine
-		Glick, David M.
+%		Einstein, Katherine Levine
+%		Glick, David M.
 & 2015 & Working Paper & Survey of 72 mayors.
@@
 & Somewhat \\ \hline
-		Kiewiet, D Roderick
-		Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
+%		Kiewiet, D Roderick
+%		Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
 Spending has thus decreased in general.
@@
 & Somewhat \\ \hline
-		Tausanovitch, Chris
-		Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
+%		Tausanovitch, Chris
+%		Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
 Partisan elections do not make cities more or less responsive.
 & Yes \\ \hline
-		Guillamón, Ma Dolores
-		Bastida, Francisco
-		Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
+%		Guillamón, Ma Dolores
+%		Bastida, Francisco
+%		Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
 Conservative parties spend more on police.
@@
 & Yes \\ \hline
-	\end{tabular}
-	\label{}
-\end{table}
-\end{landscape}
-
-\begin{landscape}
-	\begin{table}[htbp]
-		%\caption{}
-		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-			\hline
-			Names & Year & Journal & Findings & Important? \\ \hline
-			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
-			Solé-Ollé, Albert
-			Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
+%	\end{tabular}
+%	\label{}
+%\end{table}
+%\end{landscape}
+%
+%\begin{landscape}
+%	\begin{table}[htbp]
+%		%\caption{}
+%		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+%			\hline
+%			Names & Year & Journal & Findings & Important? \\ \hline
+%			Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
+%			Solé-Ollé, Albert
+%			Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
 The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
@@
 & Yes \\ \hline
-			Gerber, Elisabeth R.
-			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
-			Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
+%			Gerber, Elisabeth R.
+%			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
+%			Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
 Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
@@
 & Somewhat \\ \hline
-			Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
+%			Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
 spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
 & Somewhat \\ \hline
-			Ferreira, Fernando
-			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
-			Ansolabehere, Stephen
-			Snyder, James M.
+%			Ferreira, Fernando
+%			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
+%			Ansolabehere, Stephen
+%			Snyder, James M.
 & 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
@@
 & Somewhat \\ \hline
-			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
-		\end{tabular}
-		\label{}
-	\end{table}
-\end{landscape}
-
-\begin{landscape}
-	\begin{table}[htbp]
-		%\caption{}
-		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-			\hline
-			Names & Year & Journal & Findings & Important? \\ \hline
-			Armstrong, Cory L.
+%			Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
+%		\end{tabular}
+%		\label{}
+%	\end{table}
+%\end{landscape}
+%
+%\begin{landscape}
+%	\begin{table}[htbp]
+%		%\caption{}
+%		\begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
+%			\hline
+%			Names & Year & Journal & Findings & Important? \\ \hline
+%			Armstrong, Cory L.
 & 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
@@
 & Yes \\ \hline
-			Cegarra-Navarro, Juan
-			Pachón, José
-			Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
+%			Cegarra-Navarro, Juan
+%			Pachón, José
+%			Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
 Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
@@
 & Yes \\ \hline
-			Dolson, Jordan
-			Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
+%			Dolson, Jordan
+%			Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
 Three categories: e-content (city information on website), e-participation, social media use.
@@
 & Yes \\ \hline
-			Feeney, Mary K.
-			Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
+%			Feeney, Mary K.
+%			Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
 city websites at two points in time (2010-2014).
@@
 & Yes \\ \hline
-			Kaylor, Charles
-			Deshazo, Randy
-			Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
+%			Kaylor, Charles
+%			Deshazo, Randy
+%			Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
 Table 1 lists a number of possible ways this manifests, could be useful for our theory.
 & Somewhat \\ \hline
-			Ansolabehere, Stephen
-			Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
+%			Ansolabehere, Stephen
+%			Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
 Is website content correlated with city characteristics?
@@
 & Somewhat \\ \hline
-			Jeffres, Leo W.
-			Lin, Carolyn A.
+%			Jeffres, Leo W.
+%			Lin, Carolyn A.
 & 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
@@
 & No \\ \hline
-		\end{tabular}
-		\label{}
-	\end{table}
-\end{landscape}
+%		\end{tabular}
+%		\label{}
+%	\end{table}
+%\end{landscape}
+%
+%\subsection{Informative Dirichlet model}
+%%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+%
+%For the analysis of the data, we present two approaches, the first being the informative dirichlet model developed by \citep{Monroe2008}.
+This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
+Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them with text with greater semantic, and in our case, partisan meaning.
+%
+%In Indiana, Democrats exhibit a preference for words related to public finance, such as 'fund', 'budget', or 'tax', indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
+This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
+Beyond the focus on public finance, the words preferably used by Democrats do not fall into any particularly congruent categories, and largely sort into various areas related to city administration - i.e.
+`council', `services', `budget', `committee', `contract', etc.
+If there is theme around the words preferred by Republicans, it seems to center around city planning - street, fire, water, building, construction, park.
+These words suggest that the hands-off approach favored by Republicans results in a focus on supporting infrastructure and logistics.
+%
+%%Partisan top words - fightin words Indiana
+%\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
+%
+%For Lousiana, the results (see table \ref{tabFightinLA}) are less coherent.
+Only one of the finance-related terms appears again for Democrats - specifically `fund', although `rate' might also be used in a financial context.
+Beyond that, some focus on a `historic' `'district of a city seems evident, as is the use of some words - `infrastructure', `water', `building' that were used for Republicans in Indiana.
+Conversely, Republicans are now missing these words, and their preferred terms generally do not seem to follow any particular theme.
+%
+%%Partisan top words - fightin words Louisiana
+%\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
+%
+%The weakness of the fightin' words method is evident here, as a list of words does not necessarily provide sufficient information to glean preferred topics from.
+This is especially the case when the texts are spread across a broad number of issue-areas, with little semantic similarity.
+In \citep{Monroe2008}, the authors focus on the fairly constrained corpus of U.S.
+Senate speeches with respect to abortion - our context, by comparison, is far more eclectic.

### 2018-07-13 paper/manuscript.tex
updated the table describing how many republican/democratic cities we have per state
added a note about the size of our corpus (259,099 documents)
moving stuff around and shaping for PA

@@
 % Description of the possible challenges
+\doublespacing
 \section{Introduction}
@@
 Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
+\input{tables/tabCitiesStatesParties.tex}
 
@@
 The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e.
-a city that isn't part of our sample used in the analysis) as an example in figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4} in the appendix.
+a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}.
 Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common.
@@
 However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
-
-\section{Bag-of-Words Text Analysis}
-
-We illustrate the analysis of municipal website content using bag-of-words (BoW) methods.
-BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
-As noted by \cite{GrimmerStewart2013}, for most applications, bag-of-words approaches have been found to be more than sufficient.
-Furthermore, there is reason to believe that city government websites are a particularly `safe' case for bag-of-words methods due to their informative, manner-of-fact based language.
-It is extremely unlikely for these pages to feature ambiguous language such as an abundance of negation or even sarcasm.
-
-\subsubsection{Structural topic model}
-A powerful and frequently used approach within the family of BoW methods is the use of topic models.
-This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics.
-In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}.
-Theoretically, the most widely-used form of topic model, latent dirichlet allocation, can also be used to test for the impact of a single covariate through a post-hoc comparison, but the structural topic model allows for multiple covariates, and also produced more meaningful topics in our experiments.
-
-We use 60 topics - the number recommended by the authors for medium- to large-sized corpora.
-Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
-We use four covariates: First, \textit{party}, to test our main hypothesis.
-Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
-Third, we control for wealth by relying on \textit{median income} as a covariate.
-Fourth and finally, we include a \textit{state} variable.
-
-The results are shown in table \ref{stmResultsTable}.
-The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
-The topics that are entirely white are not statistically significant for the party covariate.
-In order to test statistical significance, we calculated credible intervals - the threshold chosen here is the 1\% level.
-
-Many of the topics associated with Democrats - one related to education, one to recycling  - clearly seem to match the party brand.
-For example, topic 44 on affordable housing clearly resonates with the Democratic party's appeal to low-income voters.
-Similarly, employee rights are represented in topic 46.
-Democrats also exhibit a strong preference for words related to public finances, such as topic 22 ('budget', 'revenue', 'expenditure') as well as topic 17 ('debt', 'bond', 'financial').
-We hypothesize that this is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
-This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-Democrats are the party of big government, and this clearly also shows at the city level.
-A second, conistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement - a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}).
-Finally, Democrats also focus more on the deliberative process of good governance, as topics 29 ('election', 'agenda', 'committee') and 37 ('audit', 'procedure', 'oversight') attest to.
-
-Republicans, meanwhile, live up to their reputation as the party of small government.
-Many topics prevalent in Republican cities focus on the bare essentials.
-Basic utilities such as energy (topic 7), fire protection (topic 33), drinking water (51) and garbage removal (topic 49) are ubiquitous here.
-Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 20 ('snow', 'hurricane', 'tornado') is an important issue.
-
-%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}.
-However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
-Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Repuiblican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted html, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
-
-%When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
-Furthermore, as with the fightin' words approach, some smaller degree of focus on money (see topic 1) is still evident.
-For Republicans, topics 2 to 4 seem to be, once again about infrastructure and utilities, pointing to a certain degree of robustness in these results, as well as the emergence of a trend.
-The results produced by the structural topic model are not flawless, but the two parties do seem to have somewhat consistent themes on which they focus on in both states.
-Furthermore, in comparison to the fightin' words approach, the ability of the structural topic model to form coherent topics is quite evident and helpful in the interpretation of the results.
-
-%An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
-This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
-However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
-Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
-Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
-The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
-Interestingly the same is true for a number of the cities as well.
-The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
-
-%Partisan top words - stm Louisiana -- Rep
-%\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
-
-%Partisan top words - stm Louisiana -- Dem
-%\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
-
-%Partisan top words - stm Louisiana -- Rep
-%\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
-
-%Partisan top words - stm Louisiana -- Dem
-%\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
-
-%\subsubsection{Prediction with SVM}
-%An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
-Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
-Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
-However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
-Instead, we ranked the features according to tf-idf and selected the top 5000.
-These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
-Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
-Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
-
-%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-%Heatmaps
-%\begin{figure}[htp]
-%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
-%	\label{heatmaps_weights}
-%	\includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
-%\end{figure}
-
-%US map
-\begin{figure}[htp]
-	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Cities in the corpus, by partisanship of mayor. \textbf{REVISE to remove everything not in our six states.}}
-	\label{us_map}
-	\includegraphics[width=\linewidth]{figures/us_map.pdf}
-\end{figure}
-
-%stm results
-%\begin{figure}[htp]
-%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
-This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
-%	\label{stm_results}
-%%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-%\end{figure}
-
-%Partisan top words - topic model Indiana
-%\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
-
-%Partisan top words - topic model Louisiana
-%\input{tables/partisanTopWordsLA.tex} %tabLDALA
-
-%Partisan top words - stm Indiana
-%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
-
-%Partisan top words - stm Louisiana
-%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
-
-%Some basic descriptive statistics of documents by party
-%\input{tables/descriptiveStatisticsPartisanIN.tex}
-
-%Some basic descriptive statistics of documents by party
-%\input{tables/descriptiveStatisticsPartisanLA.tex}
-
-%fightin words results
-%\begin{figure}[htp]
-%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-%		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
-%	\label{linesCutoff}
-%\end{figure}
-
-%\section{Ground truth test}
-%In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
-Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
-However, the aspirations some mayors have shown towards higher offices - in some cases even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
-One of the most vicious and blatantly partisan cleavages in current U.S.
-politics - the debate surrounding sanctuary cities - has seen mayors in a central role.
-Research into local politics has shown that partisan elections consistently have greater turnout \citep{Schaffner2001}.
-When voters are denied this cue, they make use of other, and considerably more irrational heuristics, such as name, gender, or occupation of the contenders.
-Consequently it only makes sense for any office-seeking politician to emphasize their partisanship.
-Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
-%
-%In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
-As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
-Consequently they are very likely to emphasize conservative/liberal values on this platform.
-If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
-%
-%Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
-We do the same for the city documents, and the compare the four document collections using cosine similarity.
-This measure is the cosine between the angle of two vectors, in this case the frequencies of all words in the two vocabularies.
-Compared to a simple euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
-The cosine measure between two documents ranges between 0 and 1, 0 signifying absolutely no correlation, and 1 perfect overlap.
-Figure \ref{groundtruth} shows the result of this test.
-The expectation is for a greater similarity between Republican cities and the Republican ground truth, than Republican cities and Democratic ground truth - and vice versa.
-At present however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
-
-%ground truth test
-%\begin{figure}[htp]
-%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%	\includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
-%	\caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
-%	\label{groundtruth}
-%\end{figure}
-%
-%%ground truth test
-%\begin{figure}[htp]
-%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%	\includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
-%	\caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
-%	\label{groundtruth}
-%\end{figure}
-
-%Ground truth test between top100 mayors and IN + LA; with bootstrapped confidence bounds
-% label: groundtruth_bootstrapped
-%\input{tables/groundtruth_bootstrapped.tex}
-
-%\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
-
-\input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
-\input{tables/stmTopWords120.tex}
-\input{tables/stmTopWords120_2.tex}
-
-\section{Conclusion}
-
-We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative analysis.
-This methodology holds the potential to vastly scale up the data collection efforts underpinning the rapidly growing body of research that is focused on government website analysis.
-Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
-
-\input{tables/urlSummary.tex}
-%\input{tables/stateUrlSummary.tex}
-
-\newpage
-
-\bibliographystyle{apsr} % apsr stopped working for me
-%\bibliographystyle{plainnat}
-\bibliography{ref}
-
-\newpage
-\section*{Appendix}
+After all the preprocessing is set and done, our corpus consists of 259,099 documents.
+
 \begin{figure}[htp]
@@
 \end{figure}
+
+\section{Bag-of-Words Text Analysis}
+
+We illustrate the analysis of municipal website content using bag-of-words (BoW) methods.
+BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
+As noted by \cite{GrimmerStewart2013}, for most applications, bag-of-words approaches have been found to be more than sufficient.
+Furthermore, there is reason to believe that city government websites are a particularly `safe' case for bag-of-words methods due to their informative, manner-of-fact based language.
+It is extremely unlikely for these pages to feature ambiguous language such as an abundance of negation or even sarcasm.
+
+\subsubsection{Structural topic model}
+A powerful and frequently used approach within the family of BoW methods is the use of topic models.
+This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics.
+In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}.
+Theoretically, the most widely-used form of topic model, latent dirichlet allocation, can also be used to test for the impact of a single covariate through a post-hoc comparison, but the structural topic model allows for multiple covariates, and also produced more meaningful topics in our experiments.
+
+We use 60 topics - the number recommended by the authors for medium- to large-sized corpora.
+Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
+We use four covariates: First, \textit{party}, to test our main hypothesis.
+Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
+Third, we control for wealth by relying on \textit{median income} as a covariate.
+Fourth and finally, we include a \textit{state} variable.
+
+The results are shown in table \ref{stmResultsTable}.
+The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
+The topics that are entirely white are not statistically significant for the party covariate.
+In order to test statistical significance, we calculated credible intervals - the threshold chosen here is the 1\% level.
+
+Many of the topics associated with Democrats - one related to education, one to recycling  - clearly seem to match the party brand.
+For example, topic 44 on affordable housing clearly resonates with the Democratic party's appeal to low-income voters.
+Similarly, employee rights are represented in topic 46.
+Democrats also exhibit a strong preference for words related to public finances, such as topic 22 ('budget', 'revenue', 'expenditure') as well as topic 17 ('debt', 'bond', 'financial').
+We hypothesize that this is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
+This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
+Democrats are the party of big government, and this clearly also shows at the city level.
+A second, conistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement - a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}).
+Finally, Democrats also focus more on the deliberative process of good governance, as topics 29 ('election', 'agenda', 'committee') and 37 ('audit', 'procedure', 'oversight') attest to.
+
+Republicans, meanwhile, live up to their reputation as the party of small government.
+Many topics prevalent in Republican cities focus on the bare essentials.
+Basic utilities such as energy (topic 7), fire protection (topic 33), drinking water (51) and garbage removal (topic 49) are ubiquitous here.
+Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 20 ('snow', 'hurricane', 'tornado') is an important issue.
+
+%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}.
+However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
+Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Repuiblican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted html, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
+
+%When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
+Furthermore, as with the fightin' words approach, some smaller degree of focus on money (see topic 1) is still evident.
+For Republicans, topics 2 to 4 seem to be, once again about infrastructure and utilities, pointing to a certain degree of robustness in these results, as well as the emergence of a trend.
+The results produced by the structural topic model are not flawless, but the two parties do seem to have somewhat consistent themes on which they focus on in both states.
+Furthermore, in comparison to the fightin' words approach, the ability of the structural topic model to form coherent topics is quite evident and helpful in the interpretation of the results.
+
+%An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
+This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
+However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
+Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
+Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
+The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
+Interestingly the same is true for a number of the cities as well.
+The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
+
+%Partisan top words - stm Louisiana -- Rep
+%\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
+
+%Partisan top words - stm Louisiana -- Dem
+%\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
+
+%Partisan top words - stm Louisiana -- Rep
+%\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
+
+%Partisan top words - stm Louisiana -- Dem
+%\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
+
+%\subsubsection{Prediction with SVM}
+%An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
+Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
+Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
+However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
+Instead, we ranked the features according to tf-idf and selected the top 5000.
+These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
+Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
+Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
+
+%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+
+%Heatmaps
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
+%	\label{heatmaps_weights}
+%	\includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
+%\end{figure}
+
+%US map
+\begin{figure}[htp]
+	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\caption{Cities in the corpus, by partisanship of mayor. \textbf{REVISE to remove everything not in our six states.}}
+	\label{us_map}
+	\includegraphics[width=\linewidth]{figures/us_map.pdf}
+\end{figure}
+
+%stm results
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
+This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
+%	\label{stm_results}
+%%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
+%\end{figure}
+
+%Partisan top words - topic model Indiana
+%\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
+
+%Partisan top words - topic model Louisiana
+%\input{tables/partisanTopWordsLA.tex} %tabLDALA
+
+%Partisan top words - stm Indiana
+%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
+
+%Partisan top words - stm Louisiana
+%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
+
+%Some basic descriptive statistics of documents by party
+%\input{tables/descriptiveStatisticsPartisanIN.tex}
+
+%Some basic descriptive statistics of documents by party
+%\input{tables/descriptiveStatisticsPartisanLA.tex}
+
+%fightin words results
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
+%		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
+%	\label{linesCutoff}
+%\end{figure}
+
+%\section{Ground truth test}
+%In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
+Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
+However, the aspirations some mayors have shown towards higher offices - in some cases even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
+One of the most vicious and blatantly partisan cleavages in current U.S.
+politics - the debate surrounding sanctuary cities - has seen mayors in a central role.
+Research into local politics has shown that partisan elections consistently have greater turnout \citep{Schaffner2001}.
+When voters are denied this cue, they make use of other, and considerably more irrational heuristics, such as name, gender, or occupation of the contenders.
+Consequently it only makes sense for any office-seeking politician to emphasize their partisanship.
+Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
+%
+%In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
+As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
+Consequently they are very likely to emphasize conservative/liberal values on this platform.
+If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
+%
+%Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
+We do the same for the city documents, and the compare the four document collections using cosine similarity.
+This measure is the cosine between the angle of two vectors, in this case the frequencies of all words in the two vocabularies.
+Compared to a simple euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
+The cosine measure between two documents ranges between 0 and 1, 0 signifying absolutely no correlation, and 1 perfect overlap.
+Figure \ref{groundtruth} shows the result of this test.
+The expectation is for a greater similarity between Republican cities and the Republican ground truth, than Republican cities and Democratic ground truth - and vice versa.
+At present however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
+
+%ground truth test
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
+%	\caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
+%	\label{groundtruth}
+%\end{figure}
+%
+%%ground truth test
+%\begin{figure}[htp]
+%	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+%	\includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
+%	\caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
+%	\label{groundtruth}
+%\end{figure}
+
+%Ground truth test between top100 mayors and IN + LA; with bootstrapped confidence bounds
+% label: groundtruth_bootstrapped
+%\input{tables/groundtruth_bootstrapped.tex}
+
+%\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
+
+\input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
+\input{tables/stmTopWords120.tex}
+\input{tables/stmTopWords120_2.tex}
+
+\section{Conclusion}
+
+We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative analysis.
+This methodology holds the potential to vastly scale up the data collection efforts underpinning the rapidly growing body of research that is focused on government website analysis.
+Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
+
+%\input{tables/tabCitiesStatesParties.tex}
+%\input{tables/stateUrlSummary.tex}
+
+\newpage
+
+\bibliographystyle{apsr} % apsr stopped working for me
+%\bibliographystyle{plainnat}
+\bibliography{ref}
+
+\newpage
+\section*{Appendix}
 

### 2018-07-13 paper/manuscript.tex
revised abstract

@@
 
-A local government's website is arguably the most important general source of information about city policies and processes for residents and other community stakeholders.
+A local government's website is arguably the most important general source of information about policies and procedures for residents and other community stakeholders.
 Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science.
@@
 However, reliance on manual collection and processing limits the scale and scope of website content analysis.
-Relying on manual data collection requires that researchers focus on a limited number of websites and/or limited types of site content.
 We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques.
@@
 We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
-Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about the provision of basic utilities and services such as water, electricity, garbage removal and fire safety.
+Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about the provision of basic utilities and services such as water, electricity, garbage removal and fire safety; and information on municipal ordinances and policies.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.

### 2018-07-13 paper/tables/tabFiletypeFrequencies.tex
updated the table describing filetypes

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Jul 13 15:10:43 2018
\begin{table}[ht]
\centering
\begin{tabular}{lll}
  \hline
Filetype & Occurances After & Occurances After \\ 
  \hline
html & 211682 & 887362 \\ 
  pdf & 464842 & 638802 \\ 
  jpg & 0 & 36958 \\ 
  xml & 0 & 29638 \\ 
  Other & 162681 & 9475 \\ 
  ics & 435 & 8950 \\ 
  png & 0 & 8863 \\ 
  doc & 6972 & 8430 \\ 
  txt & 317 & 6025 \\ 
   & 793990 & 5234 \\ 
  docx & 3137 & 4319 \\ 
  TOTAL & 1644056 & 1644056 \\ 
   \hline
\end{tabular}
\caption{Number of files per type, before and after detecing them via their magic number. The table shows that a lot of files originally have the wrong type, and that converting them correctly has a large impact on how many of them end up being usable.} 
\end{table}

### 2018-07-13 tabFiletypeFrequencies.R

@@ -1,0 +1,56 @@
+# Purpose of the script:
+# make the table in the paper that shows the distribution of file types
+
+library(xtable)
+
+#re-use the script to detect filetypes
+source_lines <- function(file, lines){
+  source(textConnection(readLines(file)[lines]))
+}
+source_lines(inferFiletype, c(21,66))
+
+#create tables of filetype frequencies
+filetypes_after <- data.frame(sort(table(magicResults$extensions), decreasing = T), stringsAsFactors = F)
+filetypes_before <- data.frame(sort(table(magicResults$ext), decreasing = T), stringsAsFactors = F)
+names(filetypes_after) <- c("Filetype", "Occurances")
+names(filetypes_before) <- c("Filetype", "Occurances")
+filetypes_after$Filetype <- as.character(filetypes_after$Filetype)
+filetypes_before$Filetype <- as.character(filetypes_before$Filetype)
+
+#only show the top 10 types, everything else into an 'other' category
+#get the top 10
+top10types <- c(filetypes_after$Filetype[1:10], "")
+
+#put everything else into the other category, then delete everything else
+filetypes_after <- rbind(filetypes_after, c("Other", sum(filetypes_after$Occurances[!filetypes_after$Filetype%in%top10types])))
+filetypes_after <- filetypes_after[-which(!filetypes_after$Filetype%in%c(top10types, "Other")),]
+filetypes_after$Filetype[filetypes_after$Filetype=="NA"] <- NA
+
+#same for the before filetypes
+filetypes_before <- rbind(filetypes_before, c("Other", sum(filetypes_before$Occurances[!filetypes_before$Filetype%in%top10types])))
+filetypes_before <- filetypes_before[-which(!filetypes_before$Filetype%in%c(top10types, "Other")),]
+filetypes_before$Filetype[filetypes_before$Filetype==""] <- NA
+
+#merge the two to go into one table
+filetypes_before_after <- merge(filetypes_before, filetypes_after, by = "Filetype", all = T)
+filetypes_before_after$Occurances.x[is.na(filetypes_before_after$Occurances.x)==T] <- 0
+
+filetypes_before_after$Occurances.x <- as.numeric(as.character(filetypes_before_after$Occurances.x))
+filetypes_before_after$Occurances.y <- as.numeric(as.character(filetypes_before_after$Occurances.y))
+filetypes_before_after <- filetypes_before_after[order(filetypes_before_after$Occurances.y, decreasing = T),]
+
[…]

### 2018-07-18 paper/manuscript.tex
updated the table describing filetypes
added a paragraph on the weak/strong mayor/city council issue -- to the data section -- maybe this should be in the conclusion instead

@@
 
+One of the more subtle aspects of local government is the presence of different types of government structures.
+Between council-manager governments and mayor-council governments - either in the weak or strong mayor variant - there is a certain degree of variance in where a city's executive authority lies.
+Unfortunately we do not have access to information about the type of governments across the breadth of our dataset and therefore have to assume that the partisanship of a city's mayor corresponds to the partisanship of the entity responsible for determining the content on its website.
+Given the prominent place of mayors tend to have on their cities' websites, as well as the fact that council-manager city governments tend to appoint mayors rather than elect them (meaning there are unlikely to be many in our dataset), we feel that any bias arising from this nuance should be minor at the most.
+
 Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
@@
 
-\input{tables/filetypes.tex}
+\input{tables/tabFiletypeFrequencies.tex}
 

### 2018-07-19 paper/manuscript.tex
some revisions to the first two sections

@@
 
-Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for text analysis.
+Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for content (e.g., text, image) analysis.
 We describe and provide solutions to two central challenges in automatically gathering and analyzing website textual contents.
@@
 The Erie, Pennsylvania website homepage presents an image of Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
-In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents.
+In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies.
 Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
@@
 Furthermore, the use of a local government website is associated with an individual's perspective on government.
-\citet{tolbert2006effects} finds that users of local government Web sites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
+\citet{tolbert2006effects} finds that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
 Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
@@
 The literature making use of scraped websites clusters into a number of categories.
-One, and most pertinent to our own endeavors, the e-governance literature which discusses the online presence of governments from a usability and public service point of view.
-For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep{Urban2002,Armstrong2011,Feeney2017}.
+The most pertinent to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
+For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
@@
 Like most e-government studies however, this publication does not make any use of automated text analysis.
+
+% BRUCE HERE
 

### 2018-07-20 paper/manuscript.tex
finished revisions to Section 2

@@
 
-The literature making use of scraped websites clusters into a number of categories.
-The most pertinent to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
+The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents produced by governments, public officials, and candidates for office.
+The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
 For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}.
@@
 Like most e-government studies however, this publication does not make any use of automated text analysis.
-
-% BRUCE HERE
-
-Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
+%Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
 \cite{Lin2011} provide a good example for a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
@@
 Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
-
-Another well-known example fitting into this area of study is the set of studies conducted by King et al.
+%Another well-known example fitting into this area of study is the set of studies conducted by King et al.
 \citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere.
@@
 \cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them.
-\cite{Cryer2017} provides fairly little information, but does mention the fact that she relied on Archive-it, a webservice of the Internet Archive.
-Unfortunately we found the data provided by the Internet Archive to not be sufficiently reliable and well-documented for our own purposes.
+\cite{Cryer2017} mentions that she relied on Archive-it, a webservice of the Internet Archive.
+Though the Internet Archive may provide extensive coverage of high profile officials or national governments, we found that its coverage of municipal government websites was sparse and irregular.
 \cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
-\cite{Therriault2010} (a working paper) actually portends to use automated text analysis, and also has the most extensive overview of the associated methodology.
-However, the division of the website into sections (home page, topics, issues, details) is done by hand, and the actual analysis is incomplete.
+\cite{Therriault2010} use automated text analysis, and also has the most extensive overview of the associated methodology.
+However, the division of the website into sections (home page, topics, issues, details) is done by hand.
 The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).
 
-Importantly for us, research analyzing and improving the scraping, pre-processing and analysis methods of this literature is scarce.
+Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
 \cite{Eschenfelder2002} provide something of an overview of how how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
-
-\section{Data}
+In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
+We then define a pipeline for data collection and analysis that includes methods to access government website URLs, scrape their raw contents from the World Wide Web, gather plain text from the website files, and identify boilerplate text within the plain text contents.
+Lastly, we illustrate the analysis of municipal government website text by exploring the relationship between the city mayors' party affiliations and the topical contents of the websites.
+
+\section{Data: US Municipal Government Website Text}
+
+% BRUCE HERE
 In this section we introduce the data we use in our application---the analysis of municipal websites in six states - Indiana, Louisiana, New York, Washington, California and Texas.

### 2018-07-20 paper/manuscript.tex
finished revisions to data section

@@
 
-% BRUCE HERE
-In this section we introduce the data we use in our application---the analysis of municipal websites in six states - Indiana, Louisiana, New York, Washington, California and Texas.
+In this section we introduce the data we use in our application.
+For data availability reasons, on which we elaborate below, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California and Texas.
 These states provide us with a sample that is well-balanced on a number of theoretically important indicators.
 One, each of the four geographic regions is represented with at least one state.
-Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities less densely populated areas are covered.
-Furthermore, the sample is politically balanced -  we have three blue states (CA, WA, NY) and three red states (TX, IN, LA).
+Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered.
+Furthermore, the sample is politically balanced---we have three blue states (CA, WA, NY) and three red states (TX, IN, LA).
 Finally, our dataset contains some of the wealthiest states (NY, CA, WA and TX are \#2, \#8, \#9 and \#16 respectively, by GDP per capita \citep{BureauofEconomicAnalysis2017}), but also some of the poorer ones (IN and LA).
-In terms of pure GDP per capita, the sample is on the less affluent side - however, wealth is also correlated with poverty: CA is the state with the highest poverty rate in the country, and LA, NY and TX follow closely \citep{Fox2017}.
 
 We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
-This method proved to be very reliable.
-Two, the General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}\footnote{This list is updated once per month - we rely on the version released on January 16, 2017.
-The data from the GSA contains the following data: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV').
-Two, the type of government entity to which the domain is registered, such as city, county, federal agency, etc.
-Three, for federal agencies, the name is specfied.
-Finally, the city in which the domain is registered, is noted.}.
-Naturally, this list does not contain cities which do not use a .gov website (or, in many cases, a city owns a registered .gov address, but uses a different one),.
+Two, the General Services Administration (GSA) maintains all .gov addresses, and provides a complete list of all such domains to the public.
+\footnote{ The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
+This list is updated once per month---we rely on the version released on January 16, 2017.} The data from the GSA contains the following variables: (1) domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'); (2) the type of government entity to which the domain is registered, such as city, county, federal agency, etc; (3) for federal agencies, the name is specified; (4) the city in which the domain is registered.
+Naturally, the GSA's list does not contain cities which do not use a .gov website (or, in many cases, a city owns a registered .gov address, but uses a different one).
 Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
-
 Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former, and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
 
-To test whether the websites we found actually work, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver).
-This is necessary because a) some city websites simply don't work, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
+To test whether the websites we found actually work, we use a webdriver-controlled browser [@markus, please define ``webdriver-controlled''] (Firefox/Selenium/Geckodriver).
+This is necessary because a) some city websites simply don't work  [@markus, why is it advantageous to use a webdriver-controlled browser for when a city website doesn't work?], and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
 A webdriver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
 This allows us to subsequently record and use the new URL for the actual website scraping.
-
-The partisanship of each city is coded in different ways, depending on the state.
+[@markus, would you add a few sentences documenting what we did to scrape the web files (i.e., used wget).
+Considering this section and the next one, its not clear how you get from a list of tested URLs to the website files being on your hard drive].
+For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results.
+Consequently we restricted our corpus to cities with at least 3 documents.
+
+The partisanship of the mayor of each city is coded in different ways, depending on the state.
 For Indiana, where elections are nominally partisan, this information is accessible through the state government's website\footnote{\url{http://www.in.gov/apps/sos/election/general/general2015?page=office&countyID=1&officeID=32&districtID=-1&candidate=}}.
-For Louisiana, we received data on the outcomes of mayoral elections from the LEAP project\footnote{\url{http://www.leap-elections.org/}}.
-For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and recorded candidates who received money from party committees.
-For California and Texas, where our data consists of major cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
+For Louisiana, we received data on the outcomes of mayoral elections from the Local Elections in America Project (LEAP) \citep{marschall2013local}.
+For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and coded the parties of the candidates based on the party committees from which they received donations.
+For California and Texas, where our data consists of highly populated cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
 Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
-When compared to the other data sources above, (and manual searches in case of conflicts) this method once again proved to be very reliable, and added additional cases to our dataset even for Indiana and Louisiana.
+When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable, and added additional cases to our dataset even for Indiana and Louisiana.
 Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
+The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
+The dataset is has a relative party balance, with variation in each state.
+
+\input{tables/tabCitiesStatesParties.tex}
 
 One of the more subtle aspects of local government is the presence of different types of government structures.
-Between council-manager governments and mayor-council governments - either in the weak or strong mayor variant - there is a certain degree of variance in where a city's executive authority lies.
-Unfortunately we do not have access to information about the type of governments across the breadth of our dataset and therefore have to assume that the partisanship of a city's mayor corresponds to the partisanship of the entity responsible for determining the content on its website.
-Given the prominent place of mayors tend to have on their cities' websites, as well as the fact that council-manager city governments tend to appoint mayors rather than elect them (meaning there are unlikely to be many in our dataset), we feel that any bias arising from this nuance should be minor at the most.
-
+Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies.
+Unfortunately we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant.
+Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
 Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
 Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
-\input{tables/tabCitiesStatesParties.tex}
-
-\input{tables/tabFiletypeFrequencies.tex}
-
-For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results. Consequently we restricted our corpus to cities with at least 3 documents.
 
 \section{The Web to Text Pipeline}
+
+% BRUCE HERE
 In this methodological pipeline from native website files to text data that is appropriate for comparative analysis, we address two methodological challenges.
@@
 This is strictly necessary, because we rely on the readText R package\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results.} - which determines a document's type solely through its ending - to convert the files to plain text.
+
+\input{tables/tabFiletypeFrequencies.tex}
 

### 2018-07-20 paper/manuscript.tex
revising Section 4

@@
 
-% BRUCE HERE
-In this methodological pipeline from native website files to text data that is appropriate for comparative analysis, we address two methodological challenges.
+Once we have gathered the website files, we have the raw data necessary for text analysis, but it is not yet formatted effectively.
+In this section we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
+In this methodological pipeline we address two methodological challenges.
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
@@
 The first step in the methodological pipeline is aimed simply at extracting clean plain text from this heterogeneous file base.
-The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another, but is uninformative regarding policy or process differences between governments.
-We describe these methodological steps in this section.
+The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another, but is uninformative regarding policy or politics differences between governments.
 
 \subsection{Site to Text Conversion}
-For the most part, the file type of a document can be correctly determined through its ending.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of garbage text, arising from incorrectly converted documents, which leads to a general decrease in the amount of usable data.
+For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
+However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text, arising from incorrectly converted documents, which leads to a general decrease in the amount of usable data.
 Two issues in particular need to be addressed: One, HTML files on city websites frequently do not have an ending, but are still perfectly readable if correctly identified as such.
-Second, some documents contain the incorrect file ending - for example, we found thousands of documents that ended in .html, when they were actually PDFs.
-To accurately assess their type, we rely on the R package wand, which is an R interface to the Unix library libmagic, which determines the type of a file on the basis of its file signature.
+Second, some documents contain the incorrect file ending.
+For example, we found thousands of documents that ended in .html, when they were actually PDFs.
+To accurately assess their type, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature.
 Consequently we rename all documents so that their file ending reflects their actual file type.
-This is strictly necessary, because we rely on the readText R package\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results.} - which determines a document's type solely through its ending - to convert the files to plain text.
+This is strictly necessary, because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.}
 
 \input{tables/tabFiletypeFrequencies.tex}
+
+% BRUCE HERE
 

### 2018-07-20 paper/manuscript.tex
working on S4

@@
 Consequently we rename all documents so that their file ending reflects their actual file type.
-This is strictly necessary, because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.}
+This is strictly necessary, because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
+[@markus, would you please clarify the column headers and "magic number" in the caption?]  The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
+Files of type XML, DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
 
 \input{tables/tabFiletypeFrequencies.tex}
-
-% BRUCE HERE
 
@@
 "You are here", "Home", "Directory" etc.) in html documents, or commonly used forms or phrases in pdfs, doc and docx files.
-This is an issue, because it clusters documents around the cities from which they originate in a way that has nothing to do with their actual content.
+This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate, and not the substantive features of their contents.
 In other words, the signal would be drowned out by the noise.
-Our solution to this problem is described in more detail in section \ref{boilerplate}.
+Our solution to this problem is described in more detail in Section \ref{boilerplate}.
 Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
-Furthermore, some documents contain gibberish, often as a result of faulty or impartial OCR.
+Furthermore, some documents contain gibberish, often as a result of faulty or impartial optical character recognition applied to text that was produced through a non-machine-readable medium.
 To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the hunspell R package, to remove all non-English words.\footnote{Some of the cities, for example Los Angeles, do contain a sizable proportion of Spanish content.
-The analysis of this content is beyond the scope of this paper, but could be explored in future work, for example relying on multilingual word embeddings.
-Since the removal of non-English words is very computationally-intensive, we only take this step at the end of the preprocessing process, the result of which might be a slightly adverse effect on the accuracy of the boilerplate classifier.} However, hunspell does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
+One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example Los Angeles, do contain a sizable proportion of Spanish content.
+The analysis of this content is beyond the scope of this paper, but could be explored in future work, for example relying on multilingual word embeddings.} However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
 Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
 Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to total number of tokens is less than 0.15.
-Furthermore, hunspell does not spellcheck individual characters or two-character words, so we remove these token types entirely (none of these words are of any substantive relevance to our research question).
-Since these pre-processing steps reduce documents which are largely unsuitable to only a few words of texts that don't make much sense, we also remove all remaining documents containing less than 50 tokens.
+Furthermore, \texttt{hunspell} does not spellcheck individual characters or two-character words, so we remove these token types entirely.
+Since these pre-processing steps reduce documents which are largely unsuitable to only a few tokens (i.e., word occurrences), we also remove all remaining documents containing less than 50 tokens.
 Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive to our models while increasing their computational cost, we also discard any token types that occur in only one document.
-We also conduct lemmatization to reduce words to their basic form.
+We also conduct lemmatization [@markus, please define lemmatization] to reduce words to their basic form.
 
 \subsection{Boilerplate Removal}\label{boilerplate}
+% BRUCE HERE
 As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods.

### 2018-07-20 paper/manuscript.tex
nearly finished Section 4

@@
 \subsection{Boilerplate Removal}\label{boilerplate}
-% BRUCE HERE
 As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods.
@@
 See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
-In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at this level.
+In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at the line level.
 
@@
 \subsection*{Boilerplate Classification}
-In order to determine whether a line should be discarded, we train a simple classifier.
-We sampled 100 lines from documents each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
-To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.
-To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in the classifier.\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
-
-These 500 lines were then hand-coded as either substantively useful or useless.
-Then we trained a random forest with this usefulness measure as the dependent variable.
-The independent variables were: (1) number of times the line was duplicated within the city, (2) length of the line, in characters, (3) number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself.
-The purpose of these covariates is as following:
-
-The length of the line and the number of tokens are a way to find lines consisting of only a word or two.
+In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
+We sampled 100 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
+To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type [@markus, please add an example here of a line that occurs a lot (e.g., "abc def" occurs in X documents in LA) to help the reader understand the concept of boilerplate lines happening frequently].
+To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
+
+These 500 lines were then hand-coded as either substantively informative or not [@markus, how many were coded as boilerplate?].
+We then trained a number of different classifiers with this informativeness measure as the dependent variable.
+The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself.
+The purpose of these covariates is as follows:
+
+% BRUCE HERE
+\begin{itemize}
+\item The length of the line and the number of tokens are a way to find lines consisting of only a word or two.
 This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us.
@@
 
-To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included.
+\item To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included.
 Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to create topics that are highly correlated with cities.
 
-Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
+\item Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
 Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures.
 Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.
+\end{itemize}
 

### 2018-07-23 paper/manuscript.tex
finished revising the boilerplate section

@@
 \begin{itemize}
-\item The length of the line and the number of tokens are a way to find lines consisting of only a word or two.
-This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us.
+\item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two.
+This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us, but are very effective at differentiating cities.
 These terms also happen to be fairly common, which causes them to be overweighted by the topic model.
 
-\item To directly address the latter problem, a measure for the number of times a line is duplicated within a city is included.
-Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to create topics that are highly correlated with cities.
-
-\item Finally, the distance measure: Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
+\item {\bf Number of line duplications:} To directly address the latter problem, we include a measure of the number of times a line is duplicated within a city.
+Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to find topics that are highly predictive of cities, but not substantively informative.
+
+\item {\bf Line position in the document} Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
 Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures.
@@
 \end{itemize}
-
-We rely on random forests as a classifier, which offer slightly better performance than logit\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} and have the added benefit of giving estimates of variable importance.
-Performance of this classifier was assessed through five-fold cross-validation, the results of which can be found in table \ref{randomForest}.
 
@@
 
-This classifier is then used to flag and remove all lines that are not classified as substantively useful.
+We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assessed performance of this classifier through five-fold cross-validation [@markus, please add another sentence describing the five-fold CV], the results of which can be found in Table \ref{randomForest} [@markus, what package was used for this RF?].
+[@markus, check that your writing is consistent with first-person plural] We use this classifier to flag and remove all lines that are not classified as substantively meaningful [@markus, how is the RF used to flag boilerplate lines (e.g., using a threshold of p = 0.5?].
 The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e.
@@
 Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common.
-After the removal, the distribution looks more like what it should be - lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
+After the removal, the distribution looks more like what it should be [@markus, why is this what it "should be"]---lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
 Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}).
@@
 However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
-After all the preprocessing is set and done, our corpus consists of 259,099 documents.
+[@markus, this is an excellent demonstration of the effect of the classifier.
+When you get a chance, would you also add a table listing the top 10 most likely boilerplate lines---to provide face validity that we are accurately flagging boilerplate?] After all the preprocessing is set and done, our corpus consists of 259,099 documents.
 

### 2018-07-23 paper/manuscript.tex
final section revision
explanation for the use of a webdriver-controlled browser and wget

@@
 
-To test whether the websites we found actually work, we use a webdriver-controlled browser [@markus, please define ``webdriver-controlled''] (Firefox/Selenium/Geckodriver).
-This is necessary because a) some city websites simply don't work  [@markus, why is it advantageous to use a webdriver-controlled browser for when a city website doesn't work?], and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
+To test whether the websites we found actually work, we use a webdriver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
+We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the webdriver  \texttt{Geckodriver}.
+This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers.
+Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
+Scrapers can perform most, but not all of such operations.
+The use of a webdriver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
 A webdriver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
 This allows us to subsequently record and use the new URL for the actual website scraping.
-[@markus, would you add a few sentences documenting what we did to scrape the web files (i.e., used wget).
-Considering this section and the next one, its not clear how you get from a list of tested URLs to the website files being on your hard drive].
+Consequently, an automated browser allows us to robustly answer the following questions: Is the website actually there?
+Does it work?
+If not, is it somewhere else or is it broken?
+We record this information and construct a list of verified URLs.
+
+To download the websites, we rely on the Unix command line tool \texttt{wget}.
+This program is used to download files from the Internet, and with the use of a recursive option, acts like a webcrawler and scraper.
+This means that \texttt{wget} scrapes HTML files, parses them and then follows the links contained therein.
+Then it follows those links, and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain).
+This way, all the files that make up a website are downloaded.
 For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results.
@@
 
-% BRUCE HERE
 \begin{itemize}
@@
 \section{Bag-of-Words Text Analysis}
+
+% BRUCE HERE
 

### 2018-07-23 paper/manuscript.tex
explanation of file signatures/magic numbers and corrected an error in the table headers and corresponding R-script

@@
 For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-To accurately assess their type, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature.
+To accurately assess their type, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature - or ``magic number''.
+This short sequence of bytes at the start (and sometimes end) of files is unique for each file type and therefore allows its correct identification through computer forensics tools such as \texttt{libmagic}.
+
 Consequently we rename all documents so that their file ending reflects their actual file type.
 This is strictly necessary, because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
-[@markus, would you please clarify the column headers and "magic number" in the caption?]  The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
+The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
 Files of type XML, DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.

### 2018-07-23 paper/manuscript.tex
explained lemmatization

@@
 Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive to our models while increasing their computational cost, we also discard any token types that occur in only one document.
-We also conduct lemmatization [@markus, please define lemmatization] to reduce words to their basic form.
+We also conduct lemmatization to reduce words to their basic form.
+Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
+For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
+Thus, lemmatization makes the results more easily comprehensible.
+To this end, we rely on the R package \texttt{spacyr}, which provides an R implementation of the Python library \texttt{spaCy}.
 

### 2018-07-23 paper/manuscript.tex
made most of the requested changes for the explanation of the random forest classifier

@@
 We sampled 100 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
-To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type [@markus, please add an example here of a line that occurs a lot (e.g., "abc def" occurs in X documents in LA) to help the reader understand the concept of boilerplate lines happening frequently].
+To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.
+As an example, the most common line throughout all pages of the city of Seattle consists only of the word ``total'' and occurs 103,068 times.
+Similarly, the line ``page'' occurs 58,833 times.
+Even something completely nonsensical such as ``a a'' still appears on 376 occasions.
 To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
 
-These 500 lines were then hand-coded as either substantively informative or not [@markus, how many were coded as boilerplate?].
+These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines).
 We then trained a number of different classifiers with this informativeness measure as the dependent variable.
@@
 
-We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assessed performance of this classifier through five-fold cross-validation [@markus, please add another sentence describing the five-fold CV], the results of which can be found in Table \ref{randomForest} [@markus, what package was used for this RF?].
-[@markus, check that your writing is consistent with first-person plural] We use this classifier to flag and remove all lines that are not classified as substantively meaningful [@markus, how is the RF used to flag boilerplate lines (e.g., using a threshold of p = 0.5?].
+We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess performance of this classifier through five-fold cross-validation.
+This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score.
+This procedure is carried out five times, so that each sample is part of the test set once.
+The aggregated (mean) results of this process can be found in Table \ref{randomForest}.
+For the implementation of this method, we rely on the R package \texttt{caret}, whose random forest classifier is based on the package \texttt{ranger}.
+We use this classifier to flag and remove all lines that are not classified (based on a threshold of $p = 0.5$) as substantively meaningful.
 The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e.
@@
 Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common.
-After the removal, the distribution looks more like what it should be [@markus, why is this what it "should be"]---lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
+After the removal, the distribution has changed---lines of medium length now occur more frequently than extremely short ones, which are unlikely to be substantively meaningful (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
 Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}).

### 2018-07-25 paper/manuscript.tex
working through the STM section

@@
 
-\section{Bag-of-Words Text Analysis}
-
-% BRUCE HERE
-
-We illustrate the analysis of municipal website content using bag-of-words (BoW) methods.
-BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
+\section{Partisan Language on Municipal Websites}
+
+We illustrate the analysis of municipal website content by studying differences in website content based on the party of the mayor.
+As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance.
+However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance.
+They find that cities with Democratic mayors spend a smaller share of their budgets on public safety, but that mayoral partisanship does not appear to be significantly related to spending in most other areas, where cities have less discretion.
+As opposed to budget allocation or even the presence/absence of policies, cities have a great deal of discretion regarding what is emphasized on their websites, and how policies are framed.
+Since (1) city governments have great discretion in composing their websites, (2) modifying website content is low cos relative to other policy changes, and (3), as reviewed above, city websites provide an effective and often-used means of communication with city residents.
+
+%BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
 As noted by \cite{GrimmerStewart2013}, for most applications, bag-of-words approaches have been found to be more than sufficient.
@@
 \subsubsection{Structural topic model}
+% BRUCE HERE
 A powerful and frequently used approach within the family of BoW methods is the use of topic models.

### 2018-07-25 paper/manuscript.tex
revisions to STM section

@@
 
-\subsubsection{Structural topic model}
+\subsubsection{Analytical approach: Structural topic modeling}
 % BRUCE HERE
-A powerful and frequently used approach within the family of BoW methods is the use of topic models.
-This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics.
+In order to analyze content differences of government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citep{Roberts2014}.
+Topic.
 In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}.

### 2018-07-26 paper/manuscript.tex
updating STM section

--- 2018-07-25 paper/manuscript.tex
@@
 
-\subsubsection{Structural topic model}
+\subsubsection{Analytical approach: Structural topic modeling}
+In order to analyze content differences of government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citep{Roberts2014}.
+Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the structural topic model a topic is a multinomial distribution defined on the word types in the dictionary.
+Each word occurrence in a document is attributed with a single topic label.
+The word topic assignments are also drawn from a multinomial distribution.
+The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics.
+For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic.
+For our primary empirical investigation, the structural topic model provides with a tool with which to estimate the relationship between the party of the city's mayor and the prevalence of each topic we estimate.
+A topic interpreted through post-hoc analysis of the collective meaning of the most likely words to be drawn from the multinomial distribution defined by the respective topic.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
+
 % BRUCE HERE
-A powerful and frequently used approach within the family of BoW methods is the use of topic models.
-This class of clustering methods relies on the co-occurrence of words within documents to form a set of semantically coherent topics.
-In order to compare the degree to which Republicans and Democrats prefer specific topics, we rely on the structural topic model, developed by \citep{Roberts2014}.
-Theoretically, the most widely-used form of topic model, latent dirichlet allocation, can also be used to test for the impact of a single covariate through a post-hoc comparison, but the structural topic model allows for multiple covariates, and also produced more meaningful topics in our experiments.
-
-We use 60 topics - the number recommended by the authors for medium- to large-sized corpora.
+The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
+We use 60 topics---the number recommended by the authors [@markus, please add a cite to the specific document in which this number is suggested.
+] for medium- to large-sized corpora.
 Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.

### 2018-07-26 paper/manuscript.tex
finished revising STM section, now on to conclusion

@@
 
-% BRUCE HERE
 The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors [@markus, please add a cite to the specific document in which this number is suggested.
-] for medium- to large-sized corpora.
+We use 60 topics---the number recommended by the authors [@markus, please add a cite to the specific document in which this number is suggested?] for medium- to large-sized corpora.
 Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
-We use four covariates: First, \textit{party}, to test our main hypothesis.
+We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
 Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
-Third, we control for wealth by relying on \textit{median income} as a covariate.
-Fourth and finally, we include a \textit{state} variable.
+Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city.
+Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.
+
+\subsubsection{Structural topic model results}
 
 The results are shown in table \ref{stmResultsTable}.
-The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
-The topics that are entirely white are not statistically significant for the party covariate.
-In order to test statistical significance, we calculated credible intervals - the threshold chosen here is the 1\% level.
-
-Many of the topics associated with Democrats - one related to education, one to recycling  - clearly seem to match the party brand.
-For example, topic 44 on affordable housing clearly resonates with the Democratic party's appeal to low-income voters.
-Similarly, employee rights are represented in topic 46.
-Democrats also exhibit a strong preference for words related to public finances, such as topic 22 ('budget', 'revenue', 'expenditure') as well as topic 17 ('debt', 'bond', 'financial').
-We hypothesize that this is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
+The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom [@markus, would you please add a sentence indicating how we measured how R/D a topic was (e.g., the magnitude of the coefficient)?].
+The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.
+
+Many of the topics associated with Democrats fit with what we understand to be national party priorities [@markus, please reference topic numbers in the next two sentences].
+Topic [@markus] is related to education.
+Topic [@markus]  is related to recycling.
+Topic 44, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
+Similarly, employee rights are represented in Topic 46.
+Democrats also exhibit a strong preference for words related to public finances, such as Topic 22 ('budget', 'revenue', 'expenditure') as well as Topic 17 ('debt', 'bond', 'financial').
+We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
 This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-Democrats are the party of big government, and this clearly also shows at the city level.
-A second, conistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement - a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}).
-Finally, Democrats also focus more on the deliberative process of good governance, as topics 29 ('election', 'agenda', 'committee') and 37 ('audit', 'procedure', 'oversight') attest to.
-
-Republicans, meanwhile, live up to their reputation as the party of small government.
-Many topics prevalent in Republican cities focus on the bare essentials.
-Basic utilities such as energy (topic 7), fire protection (topic 33), drinking water (51) and garbage removal (topic 49) are ubiquitous here.
-Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 20 ('snow', 'hurricane', 'tornado') is an important issue.
+A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement---a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}).
+[@markus, would you please elaborate on why this is "complicated"].
+Finally, Democrats also focus more on the deliberative process of policymaking, as topics 29 ('election', 'agenda', 'committee'), 39 ( `comment', `draft', `review'), 50 (`aye', `absent', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.
+This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
+
+City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government.
+Basic utilities such as energy (Topic 7), fire protection (Topic 33), drinking water (51), and garbage removal (Topic 49) are included among those topics that are more prevalent in  cities with Democratic mayors.
+Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 20 ('snow', 'hurricane', 'tornado') is an important issue, which may reflect the greater prevalence of Republican mayors in hurricane-affected areas in the southeast.
 
@@
 \section{Conclusion}
+
+% BRUCE HERE
 

### 2018-07-26 paper/manuscript.tex
finished revision pass

@@
 The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.
+[@markus, do the results from the stm package allow us to say anything about whether the overall fit of the model improved from adding party?
+if so, can we mention that?].
 
@@
 \input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
-\input{tables/stmTopWords120.tex}
-\input{tables/stmTopWords120_2.tex}
 
@@
 
-We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative analysis.
-This methodology holds the potential to vastly scale up the data collection efforts underpinning the rapidly growing body of research that is focused on government website analysis.
+We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
+This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
+The methods involved in the pipeline include checking the integrity of the site addresses, extracting english language from website contents, identifying document types, and removing boilerplate language.
 Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
+We find that government website contents is associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
+
+We offer several contributions that will be valuable in future research endeavors.
+First, the data collected in the current study can be used for comparative analysis of US city website contents.
+Second, the pipeline we present can be used as a set of procedures to follow in gathering large scale datasets of textual contents from other samples of governments.
+Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.
 
@@
 \section*{Appendix}
+
+\input{tables/stmTopWords120.tex}
+\input{tables/stmTopWords120_2.tex}
 

### 2018-07-26 paper/manuscript.tex
made most of the requested changes with respect to the stm

@@
 The results are shown in table \ref{stmResultsTable}.
-The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom [@markus, would you please add a sentence indicating how we measured how R/D a topic was (e.g., the magnitude of the coefficient)?].
+The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
+The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic.
 The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.
@@
 
-Many of the topics associated with Democrats fit with what we understand to be national party priorities [@markus, please reference topic numbers in the next two sentences].
-Topic [@markus] is related to education.
-Topic [@markus]  is related to recycling.
+Many of the topics associated with Democrats fit with what we understand to be national party priorities.
 Topic 44, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
@@
 This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement---a finding that is not entirely without precedent in the literature (see \citep{Einstein2015}).
-[@markus, would you please elaborate on why this is "complicated"].
+A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
+On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
+On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}.
 Finally, Democrats also focus more on the deliberative process of policymaking, as topics 29 ('election', 'agenda', 'committee'), 39 ( `comment', `draft', `review'), 50 (`aye', `absent', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.

### 2018-07-27 paper/tables/tabBoilerplateIllustration.tex
split off the figures illustrating the boilerplate classifier into their own Rscript and added the table with the highest/lowest probability of being boilerplate lines to it

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Jul 27 16:07:13 2018
\begin{table}[ht]
\centering
\begingroup\small
\begin{tabular}{lrr}
  \hline
Line & Substantive & Boilerplate \\ 
  \hline
address other than your mailing address where you  & 1.00 & 0.00 \\ 
  unsworn falsification a person commits the crime o & 1.00 & 0.00 \\ 
  such as the subdivision name lot and block highway & 1.00 & 0.00 \\ 
  o if you are registered to vote in anchorage and y & 1.00 & 0.00 \\ 
  absentee ballots are mailed in the order that appl & 1.00 & 0.00 \\ 
  return your ballot as soon as possible voted ballo & 1.00 & 0.00 \\ 
  parks and recreation is committed to providing rea & 1.00 & 0.00 \\ 
  parks and recreation is committed to providing rea & 1.00 & 0.00 \\ 
  this request type is to log track inspections for  & 1.00 & 0.00 \\ 
  chief doll has been with apd since and has served  & 1.00 & 0.00 \\ 
  walker jack & 0.00 & 1.00 \\ 
  jones jewel & 0.00 & 1.00 \\ 
  acda conference room & 0.00 & 1.00 \\ 
  sec ptn of & 0.00 & 1.00 \\ 
  mh property llc & 0.00 & 1.00 \\ 
  friends of pets & 0.00 & 1.00 \\ 
  change of address & 0.00 & 1.00 \\ 
  municipal code mobile & 0.00 & 1.00 \\ 
  register your vehicle & 0.00 & 1.00 \\ 
  contact phone number & 0.00 & 1.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest and lowed probabilities of being classified as boilerplate.} 
\end{table}

### 2018-07-29 boilerplateClassifierRF.R
updated random forest classifier

@@ -1,0 +1,124 @@
+#Purpose of the script:
+#Train a random forest with ipw weighting on 500 hand-coded samples from 5 cities
+#5-fold cross-validation with a 400/100 split
+#Create a final model from the full sample of 500 and save the weights for later use
+
+library("stargazer")
+library("quanteda")
+library("xtable")
+library("caret")
+library("ranger")
+library("data.table")
+
+set.seed(1)
+
+#Prepare the training data
+trainingData <- fread("data/classifierTrainingDataCoded.csv")
+#convert lines to character
+trainingData$linesRemove <- as.character(trainingData$linesRemove)
+#count the number of characters per line
+trainingData$nchar <- nchar(trainingData$linesRemove)
+#count the number of tokens
+tks <- tokens(trainingData$linesRemove)
+trainingData$nwords <- unlist(lapply(tks, length))
+rm(tks)
+#rename the important variables
+names(trainingData) <- c("id", "text", "freq", "class", "city", "prob", "medianDocMidDist", "nchars", "nwords")
+#add a variable indicating the fold of a sample
+trainingData$folds <- sample(rep(1:5, 100), 500, replace = F)
+write.csv(trainingData, "data/classifierTrainingDataCoded2.csv", row.names = F)
+
+#Add inverse probability weights to the dataset
+cityLineInfo <- read.csv("data/cityLines.txt", header = F)
+names(cityLineInfo) <- c("city", "nlines", "nlinetypes")
+trainingData <- merge(trainingData, cityLineInfo, by = "city")
+#add inverse probability weights
+trainingData$ipw <- 1/((trainingData$nlines/sum(cityLineInfo$nlines))*(trainingData$freq/trainingData$nlines))
+
+#keep only the important variables
+trainingDataRF <- trainingData[,c('freq', 'prob', 'ipw', 'medianDocMidDist', 'nchars', 'nwords', 'class')]
+#for a binary outcome variable, the caret package requires it to be a factor
+trainingDataRF$class <- as.factor(trainingDataRF$class)
+levels(trainingDataRF$class) <- c("substantive", "boilerplate")
+
+
+## Random forest with inverse probability weighting:
+
+#5-fold cross validation
+crossval_results <- list()
+for(i in 1:5){
+  
+  mRF <- train(class ~ freq + medianDocMidDist + nchars + nwords, 
+               data = trainingDataRF[trainingData$folds!=i,], 
+               method = "ranger",
[…]

### 2018-07-29 paper/tables/tabBoilerplateIllustration.tex
updated the boilerplate illustration figures and table to the new weights

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Fri Jul 27 16:07:13 2018
+% Sat Jul 28 20:51:59 2018
 \begin{table}[ht]
@@
   \hline
-address other than your mailing address where you  & 1.00 & 0.00 \\ 
-  unsworn falsification a person commits the crime o & 1.00 & 0.00 \\ 
-  such as the subdivision name lot and block highway & 1.00 & 0.00 \\ 
-  o if you are registered to vote in anchorage and y & 1.00 & 0.00 \\ 
-  absentee ballots are mailed in the order that appl & 1.00 & 0.00 \\ 
-  return your ballot as soon as possible voted ballo & 1.00 & 0.00 \\ 
-  parks and recreation is committed to providing rea & 1.00 & 0.00 \\ 
-  parks and recreation is committed to providing rea & 1.00 & 0.00 \\ 
-  this request type is to log track inspections for  & 1.00 & 0.00 \\ 
-  chief doll has been with apd since and has served  & 1.00 & 0.00 \\ 
-  walker jack & 0.00 & 1.00 \\ 
-  jones jewel & 0.00 & 1.00 \\ 
-  acda conference room & 0.00 & 1.00 \\ 
-  sec ptn of & 0.00 & 1.00 \\ 
-  mh property llc & 0.00 & 1.00 \\ 
-  friends of pets & 0.00 & 1.00 \\ 
-  change of address & 0.00 & 1.00 \\ 
-  municipal code mobile & 0.00 & 1.00 \\ 
-  register your vehicle & 0.00 & 1.00 \\ 
-  contact phone number & 0.00 & 1.00 \\ 
+have questions & 0.00 & 1.00 \\ 
+  stay connected & 0.00 & 1.00 \\ 
+  accident or injury & 0.00 & 1.00 \\ 
+  fire damaged buildings & 0.00 & 1.00 \\ 
+  gas connections & 0.00 & 1.00 \\ 
+  harboring of vagrants & 0.00 & 1.00 \\ 
+  roof system problem & 0.00 & 1.00 \\ 
+  violation plat note & 0.00 & 1.00 \\ 
+  violation setback & 0.00 & 1.00 \\ 
+  violation site plan & 0.00 & 1.00 \\ 
    \hline
@@
 \endgroup
-\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest and lowed probabilities of being classified as boilerplate.} 
+\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.} 
 \end{table}

### 2018-07-29 boilerplateClassifierRF_Anchorage_AK_demonstration.R

@@ -109,10 +109,13 @@ rm(testDataAfter, testDataBefore, testDataBeforeAfter)
 predictedProbabilities <- predict(mRF, testData, type = "prob")
 predictedProbabilities$Text <- testData$text
 names(predictedProbabilities)[1:2] <- c("Substantive", "Boilerplate")
-predictedProbabilities <- predictedProbabilities[order(predictedProbabilities$Boilerplate),]
-#Put the 10 examples with the lowest and highest probabilities in a table
-tabBoilerplateIllustration <- predictedProbabilities[1:10,]
-tabBoilerplateIllustration <- rbind(tabBoilerplateIllustration, predictedProbabilities[(nrow(predictedProbabilities)-9):nrow(predictedProbabilities),])
+predictedProbabilities <- predictedProbabilities[order(predictedProbabilities$Boilerplate, decreasing = T),]
+#Put the 10 examples with the highest probabilities in a table
+tabBoilerplateIllustration <- predictedProbabilities
+tabBoilerplateIllustration <- tabBoilerplateIllustration[!duplicated(tabBoilerplateIllustration$Text),]
+tabBoilerplateIllustration <- tabBoilerplateIllustration[1:10,]
+#uncomment the next line to also add the 10 lowest
+#tabBoilerplateIllustration <- rbind(tabBoilerplateIllustration, predictedProbabilities[(nrow(predictedProbabilities)-9):nrow(predictedProbabilities),])
 #switch around the variables so the text comes first
 tabBoilerplateIllustration <- data.frame(Line = substring(tabBoilerplateIllustration$Text, 1, 50),
                                          Substantive = tabBoilerplateIllustration$Substantive,
@@ -120,7 +123,7 @@ tabBoilerplateIllustration <- data.frame(Line = substring(tabBoilerplateIllustra
 
 xtTabBoilerplateIllustration <- print(xtable(tabBoilerplateIllustration,
                                              digits = 2,
-                                             caption = "Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest and lowed probabilities of being classified as boilerplate."), 
+                                             caption = "Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate."), 
                                       label = "tabBoilerplateIllustration",
                                       size = "small",
                                       include.rownames = FALSE)

### 2018-08-03 paper/manuscript.tex
split off the figures illustrating the boilerplate classifier into their own Rscript and added the table with the highest/lowest probability of being boilerplate lines to it
updated results for the stm

@@
 Many of the topics associated with Democrats fit with what we understand to be national party priorities.
-Topic 44, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
-Similarly, employee rights are represented in Topic 46.
-Democrats also exhibit a strong preference for words related to public finances, such as Topic 22 ('budget', 'revenue', 'expenditure') as well as Topic 17 ('debt', 'bond', 'financial').
+Topic 21, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
+Similarly, employee rights are represented in Topic 47.
+Democrats also exhibit a strong preference for words related to public finances, such as Topic 32 ('budget', 'revenue', 'expenditure') as well as Topic 19 ('debt', 'bond', 'financial').
 We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
 This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 57 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
+A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 55 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
 On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
 On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}.
-Finally, Democrats also focus more on the deliberative process of policymaking, as topics 29 ('election', 'agenda', 'committee'), 39 ( `comment', `draft', `review'), 50 (`aye', `absent', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.
+Finally, Democrats also focus more on the deliberative process of policymaking, as topics 31 ('agenda', 'committee'), 34 ( `comment', `draft', `feedback'), 48 (`absent', `aye', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.
 This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
@@
 City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government.
-Basic utilities such as energy (Topic 7), fire protection (Topic 33), drinking water (51), and garbage removal (Topic 49) are included among those topics that are more prevalent in  cities with Democratic mayors.
-Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 20 ('snow', 'hurricane', 'tornado') is an important issue, which may reflect the greater prevalence of Republican mayors in hurricane-affected areas in the southeast.
+Basic utilities such as energy (Topic 7), fire protection (Topic 17), drinking water (53), and garbage removal (Topic 49) are included among those topics that are more prevalent in  cities with Democratic mayors.
+Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 42 ('breastfeed', 'infection', 'mosquito' -- and so, essentially, about the Zika virus), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.
 
@@
 \end{figure}
+
+\input{tables/tabBoilerplateIllustration.tex}
 

### 2018-08-03 paper/tables/stmTopWords2.tex
updated the section on the structural topic model results
moving stuff around and shaping for PA
updated results for the stm

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Thu Jun 14 16:31:41 2018
+% Fri Aug  3 14:57:28 2018
 \begin{table}[ht]
@@
   \hline
- 38 & \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \mybar{3770} \\ 
-    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \mybar{260} \\ 
-   43 & \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \mybar{2469} \\ 
-   20 & \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \mybar{1290} \\ 
-   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \mybar{1152} \\ 
-   51 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \mybar{487} \\ 
-   32 & \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \mybar{1940} \\ 
-   36 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \mybar{433} \\ 
-   27 & \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \mybar{302} \\ 
-   58 & \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \mybar{1298} \\ 
-   33 & \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \mybar{459} \\ 
-   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \mybar{241} \\ 
-   35 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \mybar{710} \\ 
-   56 & \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \mybar{229} \\ 
-   21 & \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \mybar{485} \\ 
-   59 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \mybar{487} \\ 
-   49 & \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \mybar{1635} \\ 
-   31 & \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \mybar{706} \\ 
-   54 & \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \mybar{1477} \\ 
-   14 & \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \mybar{1095} \\
-    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \mybar{490} \\ 
-    2 & \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \mybar{1317} \\ 
-    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \mybar{1377} \\ 
-   55 & \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \mybar{457} \\ 
-   26 & \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \mybar{1278} \\
-   48 & \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \mybar{489} \\ 
-   12 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \mybar{917} \\
-    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \mybar{740} \\ 
-   16 & \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{702} \\ 
-   60 & \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \mybar{316} \\ 
-    3 & \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \mybar{502} \\ 
-   23 & \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \mybar{862} \\ 
-   25 & \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \mybar{683} \\ 
-    8 & \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \mybar{289} \\ 
-    9 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1103} \\ 
-   15 & \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \mybar{1454} \\ 
-   42 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \mybar{343} \\ 
-   30 & \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \mybar{540} \\
-   53 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \mybar{2518} \\
-   11 & \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \mybar{435} \\ 
-   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \mybar{2279} \\ 
-   45 & \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \mybar{300} \\ 
-   19 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \mybar{360} \\
-   13 & \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \mybar{239} \\ 
-    6 & \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \mybar{189} \\
-   46 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \mybar{398} \\ 
-   28 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \mybar{1747} \\
-   40 & \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \mybar{257} \\ 
-   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \mybar{336} \\ 
-   39 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \mybar{274} \\ 
-   37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \mybar{402} \\
-   44 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \mybar{340} \\
-   17 & \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{259} \\
-   41 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \mybar{527} \\
-   24 & \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \mybar{313} \\
-   50 & \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \mybar{674} \\ 
-   22 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \mybar{236} \\
-   47 & \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \mybar{215} \\
-   29 & \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \mybar{353} \\ 
-   57 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \mybar{1255} \\ 
+ 43 & \cellcolor{red!50}fun & \cellcolor{red!50}player & \cellcolor{red!50}dream & \cellcolor{red!50}celebration & \cellcolor{red!50}favorite & \cellcolor{red!50}blog & \mybar{3460} \\ 
+    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}contact & \cellcolor{red!30}copy & \cellcolor{red!30}mail & \cellcolor{red!30}click & \mybar{201} \\ 
+   42 & \cellcolor{red!20}breastfeed & \cellcolor{red!20}vaccine & \cellcolor{red!20}infection & \cellcolor{red!20}symptom & \cellcolor{red!20}asthma & \cellcolor{red!20}mosquito & \mybar{2497} \\ 
+   17 & \cellcolor{red!20}alarm & \cellcolor{red!20}disaster & \cellcolor{red!20}fire & \cellcolor{red!20}rescue & \cellcolor{red!20}preparedness & \cellcolor{red!20}evacuation & \mybar{989} \\ 
+   53 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pipeline & \cellcolor{red!20}pump & \cellcolor{red!20}disinfection & \mybar{461} \\ 
+   50 & \cellcolor{red!20}buffalo & \cellcolor{red!20}news & \cellcolor{red!20}honor & \cellcolor{red!20}warren & \cellcolor{red!20}announce & \cellcolor{red!20}lovely & \mybar{1106} \\ 
+   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}digest & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}legislator & \cellcolor{red!20}sander & \mybar{997} \\ 
+   33 & \cellcolor{red!20}really & \cellcolor{red!20}think & \cellcolor{red!20}something & \cellcolor{red!20}thing & \cellcolor{red!20}somebody & \cellcolor{red!20}anybody & \mybar{1873} \\ 
+   44 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}pursuant & \mybar{405} \\ 
+    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}card & \cellcolor{red!10}amt & \cellcolor{red!10}filer & \cellcolor{red!10}debit & \cellcolor{red!10}officeholder & \mybar{527} \\ 
+   26 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}billing & \cellcolor{red!10}per & \cellcolor{red!10}meter & \cellcolor{red!10}monthly & \mybar{233} \\ 
+    2 & \cellcolor{red!10}yon & \cellcolor{red!10}borough & \cellcolor{red!10}comm & \cellcolor{red!10}gen & \cellcolor{red!10}sou & \cellcolor{red!10}spec & \mybar{709} \\ 
+   49 & \cellcolor{red!10}bin & \cellcolor{red!10}recycling & \cellcolor{red!10}garbage & \cellcolor{red!10}recyclables & \cellcolor{red!10}recyclable & \cellcolor{red!10}bag & \mybar{1791} \\ 
+    7 & \cellcolor{red!10}energy & \cellcolor{red!10}garland & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \mybar{742} \\ 
+   23 & \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontractor & \cellcolor{red!10}contract & \mybar{447} \\ 
+   57 & \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}fitting & \mybar{1373} \\ 
+   13 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}subscriber & \cellcolor{red!10}desktop & \mybar{1092} \\
+   54 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}second & \cellcolor{red!10}unanimously & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \mybar{474} \\ 
+    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}infiltration & \cellcolor{red!10}discharge & \cellcolor{red!10}drainage & \cellcolor{red!10}drain & \mybar{516} \\ 
+   38 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}teacher & \cellcolor{red!10}immigrant & \cellcolor{red!10}literacy & \mybar{714} \\ 
+   35 & \cellcolor{red!10}artist & \cellcolor{red!10}rouge & \cellcolor{red!10}baton & \cellcolor{red!10}art & \cellcolor{red!10}artwork & \cellcolor{red!10}exhibition & \mybar{1632} \\ 
+   59 & \cellcolor{red!10}sampling & \cellcolor{red!10}sample & \cellcolor{red!10}analytical & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}toxicity & \mybar{1241} \\
+    3 & \cellcolor{red!10}portfolio & \cellcolor{red!10}yield & \cellcolor{red!10}jun & \cellcolor{red!10}maturity & \cellcolor{red!10}investment & \cellcolor{red!10}rating & \mybar{544} \\ 
+   45 & \cellcolor{red!10}premise & \cellcolor{red!10}licensee & \cellcolor{red!10}violation & \cellcolor{red!10}license & \cellcolor{red!10}permit & \cellcolor{red!10}inspection & \mybar{509} \\ 
+    9 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \mybar{1469} \\ 
+   60 & \cellcolor{red!10}exhaust & \cellcolor{red!10}fugitive & \cellcolor{red!10}aircraft & \cellcolor{red!10}airport & \cellcolor{red!10}aviation & \cellcolor{red!10}diesel & \mybar{731} \\ 
+   30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
+   58 & \cellcolor{white}councilor & \cellcolor{white}auburn & \cellcolor{white}plain & \cellcolor{white}ward & \cellcolor{white}beech & \cellcolor{white}glen & \mybar{480} \\ 
+   51 & \cellcolor{white}whereas & \cellcolor{white}councilman & \cellcolor{white}alderman & \cellcolor{white}ordain & \cellcolor{white}hereby & \cellcolor{white}resolution & \mybar{420} \\ 
+   16 & \cellcolor{white}recreation & \cellcolor{white}park & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{682} \\ 
+   36 & \cellcolor{white}retiree & \cellcolor{white}retirement & \cellcolor{white}actuarial & \cellcolor{white}deductible & \cellcolor{white}dental & \cellcolor{white}pension & \mybar{470} \\ 
+   27 & \cellcolor{white}exam & \cellcolor{white}incumbent & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}examination & \cellcolor{white}knowledge & \mybar{687} \\ 
+   56 & \cellcolor{white}historic & \cellcolor{white}landmark & \cellcolor{white}revival & \cellcolor{white}archaeological & \cellcolor{white}century & \cellcolor{white}historian & \mybar{2587} \\ 
+   12 & \cellcolor{white}parking & \cellcolor{white}hotel & \cellcolor{white}garage & \cellcolor{white}space & \cellcolor{white}retail & \cellcolor{white}square & \mybar{321} \\ 
+   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 
+    4 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}porch & \cellcolor{white}roof & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1108} \\ 
+   28 & \cellcolor{blue!10}census & \cellcolor{blue!10}population & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}percent & \cellcolor{blue!10}margin & \mybar{541} \\ 
+   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}deer & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}bulrush & \mybar{2522} \\ 
+   15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \cellcolor{blue!10}discrimination & \mybar{1384} \\
+   20 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration & \mybar{325} \\
+   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}federal & \cellcolor{blue!10}recipient & \cellcolor{blue!10}compliance & \cellcolor{blue!10}entity & \mybar{205} \\ 
+   46 & \cellcolor{blue!10}variance & \cellcolor{blue!10}setback & \cellcolor{blue!10}plat & \cellcolor{blue!10}zoning & \cellcolor{blue!10}yard & \cellcolor{blue!10}fence & \mybar{289} \\ 
+   29 & \cellcolor{blue!10}learn & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}graffito & \cellcolor{blue!10}event & \cellcolor{blue!10}resident & \cellcolor{blue!10}online & \mybar{196} \\ 
+   25 & \cellcolor{blue!10}cannabis & \cellcolor{blue!10}marijuana & \cellcolor{blue!10}senate & \cellcolor{blue!10}dispensary & \cellcolor{blue!10}ballot & \cellcolor{blue!10}cultivation & \mybar{1188} \\
+   22 & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}ongoing & \cellcolor{blue!10}goal & \cellcolor{blue!10}implementation & \cellcolor{blue!10}implement & \mybar{141} \\
+    6 & \cellcolor{blue!10}project & \cellcolor{blue!10}improvement & \cellcolor{blue!10}phase & \cellcolor{blue!10}replacement & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \mybar{174} \\
+   11 & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}beach & \cellcolor{blue!10}marina & \cellcolor{blue!10}coastal & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}salmon & \mybar{1069} \\ 
+   24 & \cellcolor{blue!10}attract & \cellcolor{blue!10}economy & \cellcolor{blue!10}workforce & \cellcolor{blue!10}innovation & \cellcolor{blue!10}sector & \cellcolor{blue!10}economic & \mybar{748} \\
+   47 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{511} \\ 
+   39 & \cellcolor{blue!10}tab & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}mode & \cellcolor{blue!10}var & \cellcolor{blue!10}alt & \cellcolor{blue!10}false & \mybar{259} \\ 
+   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}corridor & \mybar{358} \\ 
+   37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}accountability & \cellcolor{blue!10}oversight & \mybar{420} \\
+   21 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}affordability & \cellcolor{blue!10}landlord & \mybar{318} \\
+   34 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}feedback & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}suggest & \cellcolor{blue!10}discussion & \mybar{289} \\
+   19 & \cellcolor{blue!10}debt & \cellcolor{blue!10}bond & \cellcolor{blue!10}governmental & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{251} \\
+   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}bicyclist & \mybar{574} \\ 
+   32 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}fund & \cellcolor{blue!20}million & \mybar{242} \\
+   48 & \cellcolor{blue!20}absent & \cellcolor{blue!20}aye & \cellcolor{blue!20}khan & \cellcolor{blue!20}nay & \cellcolor{blue!20}berry & \cellcolor{blue!20}voting & \mybar{528} \\ 
+   31 & \cellcolor{blue!20}chair & \cellcolor{blue!20}agenda & \cellcolor{blue!20}commission & \cellcolor{blue!20}speaker & \cellcolor{blue!20}chairperson & \cellcolor{blue!20}committee & \mybar{314} \\
+   55 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}arrest & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}suspect & \cellcolor{blue!80}burglary & \mybar{1395} \\ 
    \hline

### 2018-08-05 paper/tables/stmTopWords120.tex
updated the section on the structural topic model results
moving stuff around and shaping for PA
updated the model with 120 topics

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Tue Jun 26 15:42:11 2018
+% Sun Aug  5 19:54:59 2018
 \begin{table}[ht]
@@
   \hline
- 93 & \cellcolor{red!30}kindness & \cellcolor{red!30}winner & \cellcolor{red!30}hero & \cellcolor{red!30}famous & \cellcolor{red!30}tribute & \cellcolor{red!30}wager & \mybar{3042} \\ 
-   36 & \cellcolor{red!20}copy & \cellcolor{red!20}record & \cellcolor{red!20}request & \cellcolor{red!20}mail & \cellcolor{red!20}submit & \cellcolor{red!20}fax & \mybar{111} \\ 
-   98 & \cellcolor{red!20}community & \cellcolor{red!20}resident & \cellcolor{red!20}mission & \cellcolor{red!20}quality & \cellcolor{red!20}excellent & \cellcolor{red!20}life & \mybar{78} \\ 
-   52 & \cellcolor{red!20}county & \cellcolor{red!20}leg & \cellcolor{red!20}legislator & \cellcolor{red!20}legislature & \cellcolor{red!20}town & \cellcolor{red!20}municipality & \mybar{132} \\ 
-   18 & \cellcolor{red!20}often & \cellcolor{red!20}always & \cellcolor{red!20}sometimes & \cellcolor{red!20}never & \cellcolor{red!20}easy & \cellcolor{red!20}even & \mybar{505} \\ 
-   20 & \cellcolor{red!20}click & \cellcolor{red!20}blog & \cellcolor{red!20}email & \cellcolor{red!20}copyright & \cellcolor{red!20}dream & \cellcolor{red!20}sorry & \mybar{336} \\ 
-   38 & \cellcolor{red!10}camp & \cellcolor{red!10}yoga & \cellcolor{red!10}library & \cellcolor{red!10}camper & \cellcolor{red!10}fun & \cellcolor{red!10}librarian & \mybar{1009} \\ 
-   43 & \cellcolor{red!10}antibody & \cellcolor{red!10}infection & \cellcolor{red!10}hepatitis & \cellcolor{red!10}tuberculosis & \cellcolor{red!10}infect & \cellcolor{red!10}viral & \mybar{1551} \\ 
-   66 & \cellcolor{red!10}drinking & \cellcolor{red!10}water & \cellcolor{red!10}reservoir & \cellcolor{red!10}contaminant & \cellcolor{red!10}irrigation & \cellcolor{red!10}tap & \mybar{228} \\ 
-   68 & \cellcolor{red!10}spray & \cellcolor{red!10}mosquito & \cellcolor{red!10}pesticide & \cellcolor{red!10}pest & \cellcolor{red!10}repellent & \cellcolor{red!10}soap & \mybar{898} \\ 
-   33 & \cellcolor{red!10}fire & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue & \cellcolor{red!10}apparatus & \cellcolor{red!10}emergency & \mybar{271} \\ 
-   56 & \cellcolor{red!10}holiday & \cellcolor{red!10}weekend & \cellcolor{red!10}parade & \cellcolor{red!10}event & \cellcolor{red!10}auburn & \cellcolor{red!10}host & \mybar{283} \\ 
-   44 & \cellcolor{red!10}microchip & \cellcolor{red!10}cat & \cellcolor{red!10}euthanasia & \cellcolor{red!10}spay & \cellcolor{red!10}rabies & \cellcolor{red!10}neuter & \mybar{1229} \\ 
-   70 & \cellcolor{red!10}election & \cellcolor{red!10}ethic & \cellcolor{red!10}ballot & \cellcolor{red!10}political & \cellcolor{red!10}candidate & \cellcolor{red!10}lobbyist & \mybar{382} \\ 
-   60 & \cellcolor{red!10}shall & \cellcolor{red!10}unless & \cellcolor{red!10}except & \cellcolor{red!10}mean & \cellcolor{red!10}deem & \cellcolor{red!10}forth & \mybar{103} \\ 
-   59 & \cellcolor{red!10}motion & \cellcolor{red!10}unanimously & \cellcolor{red!10}adjourn & \cellcolor{red!10}prince & \cellcolor{red!10}carry & \cellcolor{red!10}ken & \mybar{220} \\ 
-   81 & \cellcolor{red!10}effluent & \cellcolor{red!10}sludge & \cellcolor{red!10}wastewater & \cellcolor{red!10}mercury & \cellcolor{red!10}lbs & \cellcolor{red!10}gal & \mybar{537} \\ 
-   89 & \cellcolor{red!10}ask & \cellcolor{red!10}explain & \cellcolor{red!10}say & \cellcolor{red!10}reply & \cellcolor{red!10}suggest & \cellcolor{red!10}ruff & \mybar{427} \\ 
-    5 & \cellcolor{red!10}home & \cellcolor{red!10}family & \cellcolor{red!10}homeowner & \cellcolor{red!10}single & \cellcolor{red!10}residence & \cellcolor{red!10}cottage & \mybar{94} \\ 
-  105 & \cellcolor{red!10}proposer & \cellcolor{red!10}breach & \cellcolor{red!10}franchisee & \cellcolor{red!10}indemnify & \cellcolor{red!10}agree & \cellcolor{red!10}hereunder & \mybar{273} \\ 
-  119 & \cellcolor{red!10}alderman & \cellcolor{red!10}councilor & \cellcolor{red!10}councilwoman & \cellcolor{red!10}alderwoman & \cellcolor{red!10}common & \cellcolor{red!10}roll & \mybar{260} \\ 
-   14 & \cellcolor{red!10}borough & \cellcolor{red!10}exam & \cellcolor{red!10}trademark & \cellcolor{red!10}veteran & \cellcolor{red!10}immigrant & \cellcolor{red!10}new & \mybar{359} \\ 
-  116 & \cellcolor{red!10}asthma & \cellcolor{red!10}overdose & \cellcolor{red!10}diabetes & \cellcolor{red!10}obesity & \cellcolor{red!10}hospitalization & \cellcolor{red!10}prevalence & \mybar{609} \\
-   37 & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}deductible & \cellcolor{red!10}coinsurance & \cellcolor{red!10}prescription & \cellcolor{red!10}copay & \mybar{444} \\
-   67 & \cellcolor{red!10}plat & \cellcolor{red!10}thence & \cellcolor{red!10}easement & \cellcolor{red!10}pud & \cellcolor{red!10}petitioner & \cellcolor{red!10}annexation & \mybar{271} \\ 
-   35 & \cellcolor{red!10}parent & \cellcolor{red!10}youth & \cellcolor{red!10}child & \cellcolor{red!10}mentor & \cellcolor{red!10}literacy & \cellcolor{red!10}foster & \mybar{326} \\ 
-   75 & \cellcolor{red!10}website & \cellcolor{red!10}plain & \cellcolor{red!10}please & \cellcolor{red!10}online & \cellcolor{red!10}customize & \cellcolor{red!10}contact & \mybar{98} \\ 
-   21 & \cellcolor{red!10}bid & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontractor & \cellcolor{red!10}contract & \cellcolor{red!10}procurement & \mybar{238} \\ 
-   95 & \cellcolor{red!10}duct & \cellcolor{red!10}valve & \cellcolor{red!10}splice & \cellcolor{red!10}piping & \cellcolor{red!10}conduit & \cellcolor{red!10}conductor & \mybar{850} \\ 
-   83 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}sewer & \cellcolor{red!10}sanitary & \cellcolor{red!10}infiltration & \mybar{224} \\ 
-   64 & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}disability & \cellcolor{red!10}race & \cellcolor{red!10}religion & \cellcolor{red!10}racial & \mybar{437} \\ 
-   32 & \cellcolor{red!10}think & \cellcolor{red!10}really & \cellcolor{red!10}thing & \cellcolor{red!10}something & \cellcolor{red!10}maybe & \cellcolor{red!10}just & \mybar{899} \\ 
-   49 & \cellcolor{red!10}recycling & \cellcolor{red!10}recycle & \cellcolor{red!10}garbage & \cellcolor{red!10}trash & \cellcolor{red!10}waste & \cellcolor{red!10}bin & \mybar{405} \\ 
-    3 & \cellcolor{red!10}maturity & \cellcolor{red!10}portfolio & \cellcolor{red!10}rating & \cellcolor{red!10}jun & \cellcolor{red!10}yield & \cellcolor{red!10}investment & \mybar{276} \\ 
-    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}payment & \cellcolor{red!10}card & \cellcolor{red!10}cash & \cellcolor{red!10}account & \cellcolor{red!10}amt & \mybar{222} \\ 
-   12 & \cellcolor{red!10}password & \cellcolor{red!10}header & \cellcolor{red!10}archive & \cellcolor{red!10}browser & \cellcolor{red!10}folder & \cellcolor{red!10}text & \mybar{552} \\ 
-   90 & \cellcolor{red!10}student & \cellcolor{red!10}school & \cellcolor{red!10}elementary & \cellcolor{red!10}college & \cellcolor{red!10}academic & \cellcolor{red!10}graduate & \mybar{303} \\ 
-   48 & \cellcolor{red!10}application & \cellcolor{red!10}applicant & \cellcolor{red!10}must & \cellcolor{red!10}certificate & \cellcolor{red!10}license & \cellcolor{red!10}proof & \mybar{150} \\ 
-   92 & \cellcolor{red!10}food & \cellcolor{red!10}calorie & \cellcolor{red!10}meat & \cellcolor{red!10}vend & \cellcolor{red!10}utensil & \cellcolor{red!10}salad & \mybar{1291} \\ 
-   86 & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}resolve & \cellcolor{red!10}bond & \cellcolor{red!10}anticipation & \cellcolor{red!10}redemption & \mybar{194} \\ 
-   26 & \cellcolor{red!10}petroleum & \cellcolor{red!10}spill & \cellcolor{red!10}contamination & \cellcolor{red!10}asbestos & \cellcolor{red!10}contaminate & \cellcolor{red!10}radioactive & \mybar{444} \\
-    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}sin & \mybar{644} \\ 
-    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \cellcolor{red!10}efficiency & \mybar{416} \\ 
-   22 & \cellcolor{red!10}wireless & \cellcolor{red!10}server & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}cable & \cellcolor{red!10}technology & \mybar{376} \\
-   76 & \cellcolor{red!10}year & \cellcolor{red!10}fiscal & \cellcolor{red!10}five & \cellcolor{red!10}annual & \cellcolor{red!10}last & \cellcolor{red!10}three & \mybar{50} \\ 
-   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}cost & \cellcolor{red!10}plus & \cellcolor{red!10}hourly & \mybar{109} \\ 
-  109 & \cellcolor{red!10}city & \cellcolor{red!10}fort & \cellcolor{red!10}manager & \cellcolor{red!10}worth & \cellcolor{red!10}hall & \cellcolor{red!10}municipal & \mybar{10} \\ 
-  103 & \cellcolor{red!10}com & \cellcolor{red!10}perm & \cellcolor{red!10}tor & \cellcolor{red!10}cigarette & \cellcolor{red!10}loo & \cellcolor{red!10}comm & \mybar{1386} \\ 
-   79 & \cellcolor{red!10}tow & \cellcolor{red!10}plow & \cellcolor{red!10}vehicle & \cellcolor{red!10}trailer & \cellcolor{red!10}motor & \cellcolor{red!10}truck & \mybar{594} \\ 
-   54 & \cellcolor{red!10}dwell & \cellcolor{red!10}building & \cellcolor{red!10}remodel & \cellcolor{red!10}unit & \cellcolor{red!10}occupancy & \cellcolor{red!10}alteration & \mybar{132} \\ 
-   23 & \cellcolor{red!10}name & \cellcolor{red!10}address & \cellcolor{red!10}description & \cellcolor{red!10}number & \cellcolor{red!10}list & \cellcolor{red!10}zip & \mybar{92} \\ 
-   69 & \cellcolor{red!10}vista & \cellcolor{red!10}ranch & \cellcolor{red!10}suite & \cellcolor{red!10}trinity & \cellcolor{red!10}coliseum & \cellcolor{red!10}mesa & \mybar{657} \\ 
-   61 & \cellcolor{red!10}cannabis & \cellcolor{red!10}marijuana & \cellcolor{red!10}cultivation & \cellcolor{red!10}dispensary & \cellcolor{red!10}collective & \cellcolor{red!10}liquor & \mybar{470} \\
-  114 & \cellcolor{red!10}beach & \cellcolor{red!10}orange & \cellcolor{red!10}platinum & \cellcolor{red!10}resort & \cellcolor{red!10}ocean & \cellcolor{red!10}angel & \mybar{517} \\ 
-    1 & \cellcolor{red!10}landlord & \cellcolor{red!10}tenant & \cellcolor{red!10}lease & \cellcolor{red!10}lessee & \cellcolor{red!10}golf & \cellcolor{red!10}rent & \mybar{288} \\ 
-  118 & \cellcolor{white}flood & \cellcolor{white}earthquake & \cellcolor{white}floodplain & \cellcolor{white}hurricane & \cellcolor{white}tornado & \cellcolor{white}disaster & \mybar{513} \\ 
-   99 & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}awning & \cellcolor{white}masonry & \cellcolor{white}brick & \cellcolor{white}vinyl & \mybar{729} \\ 
-  111 & \cellcolor{white}buffalo & \cellcolor{white}player & \cellcolor{white}league & \cellcolor{white}ballpark & \cellcolor{white}baseball & \cellcolor{white}football & \mybar{542} \\ 
-  112 & \cellcolor{white}excavation & \cellcolor{white}trench & \cellcolor{white}excavate & \cellcolor{white}gravel & \cellcolor{white}silt & \cellcolor{white}concrete & \mybar{696} \\ 
-   53 & \cellcolor{white}downtown & \cellcolor{white}mall & \cellcolor{white}hotel & \cellcolor{white}midtown & \cellcolor{white}uptown & \cellcolor{white}shopping & \mybar{531} \\ 
+115 & \cellcolor{red!40}garland & \cellcolor{red!40}celebration & \cellcolor{red!40}blog & \cellcolor{red!40}dream & \cellcolor{red!40}sorry & \cellcolor{red!40}copyright & \mybar{994} \\ 
+   52 & \cellcolor{red!20}dog & \cellcolor{red!20}legislator & \cellcolor{red!20}spay & \cellcolor{red!20}neuter & \cellcolor{red!20}animal & \cellcolor{red!20}microchip & \mybar{761} \\ 
+   44 & \cellcolor{red!20}copy & \cellcolor{red!20}record & \cellcolor{red!20}mail & \cellcolor{red!20}request & \cellcolor{red!20}notice & \cellcolor{red!20}notify & \mybar{120} \\ 
+   98 & \cellcolor{red!20}neighborhood & \cellcolor{red!20}community & \cellcolor{red!20}resident & \cellcolor{red!20}safe & \cellcolor{red!20}life & \cellcolor{red!20}quality & \mybar{95} \\ 
+   88 & \cellcolor{red!20}war & \cellcolor{red!20}professor & \cellcolor{red!20}sister & \cellcolor{red!20}bachelor & \cellcolor{red!20}daughter & \cellcolor{red!20}soldier & \mybar{2516} \\ 
+   43 & \cellcolor{red!20}camp & \cellcolor{red!20}yoga & \cellcolor{red!20}camper & \cellcolor{red!20}fun & \cellcolor{red!20}librarian & \cellcolor{red!20}library & \mybar{1080} \\ 
+   42 & \cellcolor{red!10}infection & \cellcolor{red!10}tuberculosis & \cellcolor{red!10}breastfeed & \cellcolor{red!10}hepatitis & \cellcolor{red!10}vaccine & \cellcolor{red!10}condom & \mybar{1608} \\
+   72 & \cellcolor{red!10}drinking & \cellcolor{red!10}water & \cellcolor{red!10}contaminant & \cellcolor{red!10}reservoir & \cellcolor{red!10}pipeline & \cellcolor{red!10}irrigation & \mybar{216} \\ 
+   84 & \cellcolor{red!10}say & \cellcolor{red!10}ask & \cellcolor{red!10}explain & \cellcolor{red!10}reply & \cellcolor{red!10}horn & \cellcolor{red!10}advise & \mybar{454} \\ 
+   18 & \cellcolor{red!10}player & \cellcolor{red!10}coach & \cellcolor{red!10}game & \cellcolor{red!10}umpire & \cellcolor{red!10}ball & \cellcolor{red!10}shirt & \mybar{1595} \\ 
+   61 & \cellcolor{red!10}unanimously & \cellcolor{red!10}motion & \cellcolor{red!10}prince & \cellcolor{red!10}adjourn & \cellcolor{red!10}carry & \cellcolor{red!10}ken & \mybar{192} \\ 
+   63 & \cellcolor{red!10}mosquito & \cellcolor{red!10}spray & \cellcolor{red!10}rodent & \cellcolor{red!10}pesticide & \cellcolor{red!10}repellent & \cellcolor{red!10}pest & \mybar{851} \\ 
+   81 & \cellcolor{red!10}effluent & \cellcolor{red!10}sludge & \cellcolor{red!10}lbs & \cellcolor{red!10}mercury & \cellcolor{red!10}wastewater & \cellcolor{red!10}gal & \mybar{540} \\ 
+   60 & \cellcolor{red!10}shall & \cellcolor{red!10}deem & \cellcolor{red!10}forth & \cellcolor{red!10}unless & \cellcolor{red!10}except & \cellcolor{red!10}thereof & \mybar{119} \\ 
+   69 & \cellcolor{red!10}ethic & \cellcolor{red!10}candidate & \cellcolor{red!10}lobbyist & \cellcolor{red!10}filer & \cellcolor{red!10}political & \cellcolor{red!10}officeholder & \mybar{355} \\ 
+   33 & \cellcolor{red!10}think & \cellcolor{red!10}really & \cellcolor{red!10}something & \cellcolor{red!10}thing & \cellcolor{red!10}just & \cellcolor{red!10}go & \mybar{826} \\ 
+  119 & \cellcolor{red!10}firefighter & \cellcolor{red!10}fire & \cellcolor{red!10}chief & \cellcolor{red!10}police & \cellcolor{red!10}captain & \cellcolor{red!10}patrol & \mybar{248} \\ 
+   37 & \cellcolor{red!10}physician & \cellcolor{red!10}nursing & \cellcolor{red!10}medical & \cellcolor{red!10}nurse & \cellcolor{red!10}outpatient & \cellcolor{red!10}medicaid & \mybar{352} \\ 
+    5 & \cellcolor{red!10}home & \cellcolor{red!10}homeowner & \cellcolor{red!10}alarm & \cellcolor{red!10}detector & \cellcolor{red!10}monoxide & \cellcolor{red!10}header & \mybar{209} \\ 
+   23 & \cellcolor{red!10}proposer & \cellcolor{red!10}bidder & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bid & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \mybar{239} \\ 
+  116 & \cellcolor{red!10}councilor & \cellcolor{red!10}alderman & \cellcolor{red!10}councilwoman & \cellcolor{red!10}alderwoman & \cellcolor{red!10}quill & \cellcolor{red!10}councilors & \mybar{268} \\
+   15 & \cellcolor{red!10}trademark & \cellcolor{red!10}borough & \cellcolor{red!10}new & \cellcolor{red!10}immigration & \cellcolor{red!10}immigrant & \cellcolor{red!10}pour & \mybar{274} \\ 
+   67 & \cellcolor{red!10}discrimination & \cellcolor{red!10}disability & \cellcolor{red!10}gender & \cellcolor{red!10}religion & \cellcolor{red!10}accommodation & \cellcolor{red!10}origin & \mybar{373} \\
+  117 & \cellcolor{red!10}asthma & \cellcolor{red!10}overdose & \cellcolor{red!10}obesity & \cellcolor{red!10}hospitalization & \cellcolor{red!10}diabetes & \cellcolor{red!10}prevalence & \mybar{659} \\
+   94 & \cellcolor{red!10}duct & \cellcolor{red!10}valve & \cellcolor{red!10}sprinkler & \cellcolor{red!10}combustible & \cellcolor{red!10}splice & \cellcolor{red!10}conductor & \mybar{778} \\ 
+   58 & \cellcolor{red!10}event & \cellcolor{red!10}firework & \cellcolor{red!10}parade & \cellcolor{red!10}press & \cellcolor{red!10}holiday & \cellcolor{red!10}troy & \mybar{335} \\ 
+   70 & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}resolve & \cellcolor{red!10}duly & \cellcolor{red!10}authorize & \cellcolor{red!10}therefore & \mybar{202} \\ 
+   30 & \cellcolor{red!10}disaster & \cellcolor{red!10}emergency & \cellcolor{red!10}preparedness & \cellcolor{red!10}evacuation & \cellcolor{red!10}dispatch & \cellcolor{red!10}homeland & \mybar{365} \\
+   38 & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \cellcolor{red!10}youth & \mybar{354} \\ 
+   93 & \cellcolor{red!10}city & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}manager & \cellcolor{red!10}hall & \cellcolor{red!10}charter & \mybar{16} \\ 
+   75 & \cellcolor{red!10}online & \cellcolor{red!10}click & \cellcolor{red!10}plain & \cellcolor{red!10}website & \cellcolor{red!10}download & \cellcolor{red!10}learn & \mybar{165} \\ 
+    3 & \cellcolor{red!10}value & \cellcolor{red!10}market & \cellcolor{red!10}productivity & \cellcolor{red!10}customize & \cellcolor{red!10}yrs & \cellcolor{red!10}index & \mybar{126} \\ 
+   49 & \cellcolor{red!10}recycling & \cellcolor{red!10}recycle & \cellcolor{red!10}garbage & \cellcolor{red!10}waste & \cellcolor{red!10}trash & \cellcolor{red!10}landfill & \mybar{408} \\ 
+  111 & \cellcolor{red!10}franchisee & \cellcolor{red!10}indemnify & \cellcolor{red!10}arise & \cellcolor{red!10}harmless & \cellcolor{red!10}breach & \cellcolor{red!10}party & \mybar{307} \\ 
+   17 & \cellcolor{red!10}snow & \cellcolor{red!10}plow & \cellcolor{red!10}tornado & \cellcolor{red!10}flood & \cellcolor{red!10}pothole & \cellcolor{red!10}crew & \mybar{552} \\ 
+   89 & \cellcolor{red!10}vend & \cellcolor{red!10}food & \cellcolor{red!10}meat & \cellcolor{red!10}utensil & \cellcolor{red!10}calorie & \cellcolor{red!10}vending & \mybar{1174} \\ 
+   45 & \cellcolor{red!10}application & \cellcolor{red!10}applicant & \cellcolor{red!10}certificate & \cellcolor{red!10}must & \cellcolor{red!10}license & \cellcolor{red!10}permit & \mybar{151} \\ 
+   85 & \cellcolor{red!10}runoff & \cellcolor{red!10}sanitary & \cellcolor{red!10}infiltration & \cellcolor{red!10}storm & \cellcolor{red!10}drainage & \cellcolor{red!10}drain & \mybar{241} \\ 
+  106 & \cellcolor{red!10}equipment & \cellcolor{red!10}boiler & \cellcolor{red!10}fleet & \cellcolor{red!10}crane & \cellcolor{red!10}mechanic & \cellcolor{red!10}fuel & \mybar{539} \\ 
+    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}payment & \cellcolor{red!10}card & \cellcolor{red!10}credit & \cellcolor{red!10}account & \cellcolor{red!10}cash & \mybar{187} \\ 
+   13 & \cellcolor{red!10}class & \cellcolor{red!10}test & \cellcolor{red!10}adobe & \cellcolor{red!10}embed & \cellcolor{red!10}reader & \cellcolor{red!10}acrobat & \mybar{312} \\ 
+  108 & \cellcolor{red!10}cigarette & \cellcolor{red!10}senate & \cellcolor{red!10}tobacco & \cellcolor{red!10}consumer & \cellcolor{red!10}smoking & \cellcolor{red!10}ban & \mybar{542} \\ 
+   25 & \cellcolor{red!10}coal & \cellcolor{red!10}hazard & \cellcolor{red!10}hazardous & \cellcolor{red!10}toxic & \cellcolor{red!10}radiation & \cellcolor{red!10}substance & \mybar{288} \\ 
+   86 & \cellcolor{red!10}groundwater & \cellcolor{red!10}sample & \cellcolor{red!10}asbestos & \cellcolor{red!10}analytical & \cellcolor{red!10}remediation & \cellcolor{red!10}remedial & \mybar{345} \\
+    1 & \cellcolor{red!10}golf & \cellcolor{red!10}exhibit & \cellcolor{red!10}lessee & \cellcolor{red!10}course & \cellcolor{red!10}lessor & \cellcolor{red!10}lease & \mybar{401} \\ 
+    9 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}sin & \mybar{635} \\ 
+   24 & \cellcolor{red!10}phone & \cellcolor{red!10}name & \cellcolor{red!10}page & \cellcolor{red!10}address & \cellcolor{red!10}glen & \cellcolor{red!10}cove & \mybar{158} \\ 
+    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \cellcolor{red!10}efficiency & \mybar{399} \\ 
+   66 & \cellcolor{red!10}plat & \cellcolor{red!10}thence & \cellcolor{red!10}easement & \cellcolor{red!10}pud & \cellcolor{red!10}tract & \cellcolor{red!10}subdivision & \mybar{230} \\ 
+   57 & \cellcolor{red!10}dwell & \cellcolor{red!10}unit & \cellcolor{red!10}remodel & \cellcolor{red!10}condominium & \cellcolor{red!10}dwelling & \cellcolor{red!10}residential & \mybar{167} \\ 
+   95 & \cellcolor{red!10}roof & \cellcolor{red!10}masonry & \cellcolor{red!10}porch & \cellcolor{red!10}exterior & \cellcolor{red!10}would & \cellcolor{red!10}brick & \mybar{611} \\ 
+   26 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}cost & \cellcolor{red!10}plus & \cellcolor{red!10}rate & \mybar{102} \\ 
+   51 & \cellcolor{red!10}chapter & \cellcolor{red!10}code & \cellcolor{red!10}violation & \cellcolor{red!10}subsection & \cellcolor{red!10}article & \cellcolor{red!10}sec & \mybar{151} \\ 
+   59 & \cellcolor{white}zoning & \cellcolor{white}conditional & \cellcolor{white}zone & \cellcolor{white}cannabis & \cellcolor{white}overlay & \cellcolor{white}district & \mybar{241} \\ 
+  101 & \cellcolor{white}height & \cellcolor{white}foot & \cellcolor{white}square & \cellcolor{white}feet & \cellcolor{white}setback & \cellcolor{white}frontage & \mybar{124} \\ 
+   96 & \cellcolor{red!10}house & \cellcolor{red!10}cemetery & \cellcolor{red!10}burial & \cellcolor{red!10}butler & \cellcolor{red!10}funeral & \cellcolor{red!10}barber & \mybar{472} \\ 
+   65 & \cellcolor{red!10}ballot & \cellcolor{red!10}vista & \cellcolor{red!10}ranch & \cellcolor{red!10}canyon & \cellcolor{red!10}silicon & \cellcolor{red!10}voter & \mybar{518} \\ 
+  120 & \cellcolor{red!10}bend & \cellcolor{red!10}fir & \cellcolor{red!10}hometown & \cellcolor{red!10}twelfth & \cellcolor{red!10}exceptional & \cellcolor{red!10}rodeo & \mybar{271} \\ 
+   36 & \cellcolor{white}aviation & \cellcolor{white}airport & \cellcolor{white}airline & \cellcolor{white}runway & \cellcolor{white}aircraft & \cellcolor{white}hangar & \mybar{429} \\ 
+   34 & \cellcolor{white}plan & \cellcolor{white}planning & \cellcolor{white}comprehensive & \cellcolor{white}master & \cellcolor{white}review & \cellcolor{white}amendment & \mybar{42} \\ 
    \hline

### 2018-08-05 paper/tables/stmTopWords120_2.tex
updated the section on the structural topic model results
moving stuff around and shaping for PA
updated the model with 120 topics

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Tue Jun 26 15:42:11 2018
+% Sun Aug  5 19:55:00 2018
 \begin{table}[ht]
@@
   \hline
- 53 & \cellcolor{white}downtown & \cellcolor{white}mall & \cellcolor{white}hotel & \cellcolor{white}midtown & \cellcolor{white}uptown & \cellcolor{white}shopping & \mybar{531} \\ 
-  117 & \cellcolor{white}police & \cellcolor{white}patrol & \cellcolor{white}chief & \cellcolor{white}lieutenant & \cellcolor{white}captain & \cellcolor{white}swear & \mybar{283} \\ 
-    2 & \cellcolor{red!10}page & \cellcolor{red!10}yon & \cellcolor{red!10}rev & \cellcolor{red!10}sou & \cellcolor{red!10}spec & \cellcolor{red!10}gen & \mybar{165} \\ 
-  100 & \cellcolor{white}senate & \cellcolor{white}house & \cellcolor{white}butler & \cellcolor{white}hook & \cellcolor{white}rep & \cellcolor{white}haven & \mybar{590} \\ 
-   55 & \cellcolor{white}chapter & \cellcolor{white}code & \cellcolor{white}section & \cellcolor{white}subsection & \cellcolor{white}article & \cellcolor{white}amend & \mybar{124} \\ 
-   19 & \cellcolor{white}fugitive & \cellcolor{white}noise & \cellcolor{white}exhaust & \cellcolor{white}receptor & \cellcolor{white}coal & \cellcolor{white}ozone & \mybar{437} \\ 
-   31 & \cellcolor{white}aviation & \cellcolor{white}taxicab & \cellcolor{white}airport & \cellcolor{white}runway & \cellcolor{white}airline & \cellcolor{white}hangar & \mybar{498} \\ 
-   85 & \cellcolor{white}homeless & \cellcolor{white}homelessness & \cellcolor{white}supportive & \cellcolor{white}client & \cellcolor{white}transitional & \cellcolor{white}encampment & \mybar{232} \\
-   42 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}deduction & \cellcolor{white}taxpayer & \cellcolor{white}appraisal & \mybar{160} \\ 
-   80 & \cellcolor{white}artist & \cellcolor{white}artwork & \cellcolor{white}art & \cellcolor{white}exhibition & \cellcolor{white}gallery & \cellcolor{white}artistic & \mybar{1060} \\ 
-   65 & \cellcolor{white}density & \cellcolor{white}land & \cellcolor{white}us & \cellcolor{white}urban & \cellcolor{white}village & \cellcolor{white}growth & \mybar{102} \\ 
-  101 & \cellcolor{white}marsh & \cellcolor{white}riparian & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}grassland & \cellcolor{white}freshwater & \mybar{1110} \\ 
-  120 & \cellcolor{blue!10}bend & \cellcolor{blue!10}rogers & \cellcolor{blue!10}walnut & \cellcolor{blue!10}grape & \cellcolor{blue!10}parenthood & \cellcolor{blue!10}shalom & \mybar{315} \\ 
-  108 & \cellcolor{blue!10}owner & \cellcolor{blue!10}inspector & \cellcolor{blue!10}property & \cellcolor{blue!10}inspection & \cellcolor{blue!10}unsafe & \cellcolor{blue!10}nuisance & \mybar{156} \\
-  110 & \cellcolor{white}incumbent & \cellcolor{white}ability & \cellcolor{white}supervise & \cellcolor{white}knowledge & \cellcolor{white}supervision & \cellcolor{white}essential & \mybar{378} \\ 
-  102 & \cellcolor{blue!10}parking & \cellcolor{blue!10}space & \cellcolor{blue!10}height & \cellcolor{blue!10}garage & \cellcolor{blue!10}foot & \cellcolor{blue!10}lot & \mybar{83} \\ 
-   30 & \cellcolor{blue!10}figure & \cellcolor{blue!10}census & \cellcolor{blue!10}population & \cellcolor{blue!10}respondent & \cellcolor{blue!10}comparison & \cellcolor{blue!10}table & \mybar{240} \\
-   71 & \cellcolor{blue!10}economic & \cellcolor{blue!10}workforce & \cellcolor{blue!10}economy & \cellcolor{blue!10}industry & \cellcolor{blue!10}sector & \cellcolor{blue!10}job & \mybar{312} \\ 
-   91 & \cellcolor{blue!10}prune & \cellcolor{blue!10}forestry & \cellcolor{blue!10}tree & \cellcolor{blue!10}planting & \cellcolor{blue!10}shrub & \cellcolor{blue!10}root & \mybar{1092} \\ 
-   28 & \cellcolor{blue!10}conviction & \cellcolor{blue!10}guilty & \cellcolor{blue!10}offense & \cellcolor{blue!10}convict & \cellcolor{blue!10}misdemeanor & \cellcolor{blue!10}felony & \mybar{762} \\
-  115 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}mitigate & \cellcolor{blue!10}measure & \mybar{135} \\
-   27 & \cellcolor{blue!10}workshop & \cellcolor{blue!10}learn & \cellcolor{blue!10}tour & \cellcolor{blue!10}upcoming & \cellcolor{blue!10}get & \cellcolor{blue!10}view & \mybar{119} \\ 
-   16 & \cellcolor{blue!10}park & \cellcolor{blue!10}recreation & \cellcolor{blue!10}playground & \cellcolor{blue!10}picnic & \cellcolor{blue!10}trail & \cellcolor{blue!10}zoo & \mybar{253} \\ 
-   15 & \cellcolor{blue!10}landmark & \cellcolor{blue!10}historic & \cellcolor{blue!10}revival & \cellcolor{blue!10}preservation & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}historical & \mybar{936} \\
-   10 & \cellcolor{blue!10}ave & \cellcolor{blue!10}rainier & \cellcolor{blue!10}beacon & \cellcolor{blue!10}aurora & \cellcolor{blue!10}greenwood & \cellcolor{blue!10}capitol & \mybar{353} \\ 
-   51 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}boat & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}maritime & \cellcolor{blue!10}dock & \cellcolor{blue!10}port & \mybar{788} \\ 
-   82 & \cellcolor{blue!10}avenue & \cellcolor{blue!10}east & \cellcolor{blue!10}west & \cellcolor{blue!10}north & \cellcolor{blue!10}street & \cellcolor{blue!10}south & \mybar{78} \\ 
-   73 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}pension & \cellcolor{blue!10}retirement & \cellcolor{blue!10}retiree & \cellcolor{blue!10}unfunded & \cellcolor{blue!10}contribution & \mybar{181} \\
-    6 & \cellcolor{blue!10}variance & \cellcolor{blue!10}setback & \cellcolor{blue!10}fence & \cellcolor{blue!10}exception & \cellcolor{blue!10}yard & \cellcolor{blue!10}nonconforming & \mybar{122} \\
-   46 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}complaint & \cellcolor{blue!10}bias & \cellcolor{blue!10}allege & \mybar{631} \\
-   25 & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}plaintiff & \cellcolor{blue!10}examiner & \cellcolor{blue!10}creditor & \cellcolor{blue!10}trial & \cellcolor{blue!10}appeal & \mybar{843} \\
-   78 & \cellcolor{blue!10}violent & \cellcolor{blue!10}gang & \cellcolor{blue!10}violence & \cellcolor{blue!10}inmate & \cellcolor{blue!10}crime & \cellcolor{blue!10}offender & \mybar{710} \\ 
-   97 & \cellcolor{blue!10}employee & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}overtime & \mybar{243} \\ 
-   77 & \cellcolor{blue!10}board & \cellcolor{blue!10}appoint & \cellcolor{blue!10}chairperson & \cellcolor{blue!10}secretary & \cellcolor{blue!10}member & \cellcolor{blue!10}vice & \mybar{137} \\ 
-   24 & \cellcolor{blue!10}grant & \cellcolor{blue!10}funding & \cellcolor{blue!10}program & \cellcolor{blue!10}fund & \cellcolor{blue!10}federal & \cellcolor{blue!10}match & \mybar{49} \\ 
-  104 & \cellcolor{blue!10}project & \cellcolor{blue!10}improvement & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}replacement & \cellcolor{blue!10}phase & \cellcolor{blue!10}appropriated & \mybar{84} \\
-   94 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditing & \cellcolor{blue!10}deficiency & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}weakness & \mybar{195} \\
-   13 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}successor & \cellcolor{blue!10}redevelopment & \cellcolor{blue!10}oversight & \cellcolor{blue!10}disposition & \mybar{128} \\
-    9 & \cellcolor{blue!10}realm & \cellcolor{blue!10}design & \cellcolor{blue!10}proponent & \cellcolor{blue!10}courtyard & \cellcolor{blue!10}facade & \cellcolor{blue!10}concept & \mybar{468} \\ 
-   96 & \cellcolor{blue!10}propose & \cellcolor{blue!10}draft & \cellcolor{blue!10}comment & \cellcolor{blue!10}alternative & \cellcolor{blue!10}plan & \cellcolor{blue!10}planning & \mybar{68} \\ 
-  106 & \cellcolor{blue!10}sidewalk & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}signal & \cellcolor{blue!10}traffic & \cellcolor{blue!10}intersection & \cellcolor{blue!10}curb & \mybar{269} \\
-   41 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}transit & \cellcolor{blue!10}bus & \cellcolor{blue!10}route & \cellcolor{blue!10}mobility & \mybar{279} \\ 
-   63 & \cellcolor{blue!10}memorandum & \cellcolor{blue!10}council & \cellcolor{blue!10}resolution & \cellcolor{blue!10}negotiation & \cellcolor{blue!10}manager & \cellcolor{blue!10}ward & \mybar{132} \\
-   39 & \cellcolor{blue!10}commission & \cellcolor{blue!10}committee & \cellcolor{blue!10}commissioner & \cellcolor{blue!10}advisory & \cellcolor{blue!10}chair & \cellcolor{blue!10}discussion & \mybar{126} \\
-   84 & \cellcolor{blue!10}implement & \cellcolor{blue!10}monitor & \cellcolor{blue!10}performance & \cellcolor{blue!10}inventory & \cellcolor{blue!10}process & \cellcolor{blue!10}track & \mybar{146} \\
-  107 & \cellcolor{blue!10}budget & \cellcolor{blue!10}appropriation & \cellcolor{blue!10}fund & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}adopt & \cellcolor{blue!10}levy & \mybar{99} \\ 
-   62 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}household & \cellcolor{blue!10}income & \cellcolor{blue!10}renter & \mybar{224} \\
-   17 & \cellcolor{blue!10}million & \cellcolor{blue!10}revenue & \cellcolor{blue!10}forecast & \cellcolor{blue!10}offset & \cellcolor{blue!10}deficit & \cellcolor{blue!10}projection & \mybar{187} \\ 
-   74 & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}vision & \cellcolor{blue!10}attractive & \cellcolor{blue!10}node & \cellcolor{blue!10}amenity & \cellcolor{blue!10}corridor & \mybar{351} \\
-   45 & \cellcolor{blue!10}zoning & \cellcolor{blue!10}district & \cellcolor{blue!10}zone & \cellcolor{blue!10}acre & \cellcolor{blue!10}dist & \cellcolor{blue!10}rezoning & \mybar{71} \\ 
-  113 & \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}asset & \cellcolor{blue!10}net & \cellcolor{blue!10}statement & \cellcolor{blue!10}obligation & \mybar{133} \\ 
-   72 & \cellcolor{blue!10}rouge & \cellcolor{blue!10}parish & \cellcolor{blue!10}baton & \cellcolor{blue!10}hogan & \cellcolor{blue!10}councilman & \cellcolor{blue!10}bowman & \mybar{528} \\ 
-   88 & \cellcolor{blue!10}position & \cellcolor{blue!10}staffing & \cellcolor{blue!10}citywide & \cellcolor{blue!10}analyst & \cellcolor{blue!10}strategic & \cellcolor{blue!10}allocation & \mybar{111} \\
-   40 & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}mode & \cellcolor{blue!10}false & \cellcolor{blue!10}null & \cellcolor{blue!10}else & \cellcolor{blue!10}tab & \mybar{105} \\ 
-   11 & \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}strategic & \cellcolor{blue!10}engagement & \cellcolor{blue!10}outreach & \mybar{168} \\
-   58 & \cellcolor{blue!10}news & \cellcolor{blue!10}warren & \cellcolor{blue!10}announce & \cellcolor{blue!10}lovely & \cellcolor{blue!10}release & \cellcolor{blue!10}today & \mybar{501} \\ 
-   50 & \cellcolor{blue!10}aye & \cellcolor{blue!10}absent & \cellcolor{blue!10}khan & \cellcolor{blue!10}nay & \cellcolor{blue!10}berry & \cellcolor{blue!10}voting & \mybar{318} \\ 
-   87 & \cellcolor{blue!20}digest & \cellcolor{blue!20}proposal & \cellcolor{blue!20}reappoints & \cellcolor{blue!20}sander & \cellcolor{blue!20}gray & \cellcolor{blue!20}metropolitan & \mybar{232} \\
-   29 & \cellcolor{blue!20}agenda & \cellcolor{blue!20}speaker & \cellcolor{blue!20}item & \cellcolor{blue!20}divided & \cellcolor{blue!20}speak & \cellcolor{blue!20}refrain & \mybar{146} \\ 
-   47 & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}reinvestment & \cellcolor{blue!20}contingency & \cellcolor{blue!20}contract & \cellcolor{blue!20}authorize & \cellcolor{blue!20}engineering & \mybar{131} \\
-   57 & \cellcolor{blue!80}suspect & \cellcolor{blue!80}fatal & \cellcolor{blue!80}shoot & \cellcolor{blue!80}pronounce & \cellcolor{blue!80}stopper & \cellcolor{blue!80}gunshot & \mybar{500} \\ 
+ 34 & \cellcolor{white}plan & \cellcolor{white}planning & \cellcolor{white}comprehensive & \cellcolor{white}master & \cellcolor{white}review & \cellcolor{white}amendment & \mybar{42} \\ 
+   82 & \cellcolor{white}com & \cellcolor{white}mar & \cellcolor{white}spec & \cellcolor{white}jun & \cellcolor{white}est & \cellcolor{white}comm & \mybar{1388} \\ 
+   22 & \cellcolor{white}server & \cellcolor{white}software & \cellcolor{white}wireless & \cellcolor{white}technology & \cellcolor{white}desktop & \cellcolor{white}broadband & \mybar{430} \\ 
+   80 & \cellcolor{white}artist & \cellcolor{white}art & \cellcolor{white}artwork & \cellcolor{white}exhibition & \cellcolor{white}artistic & \cellcolor{white}sculpture & \mybar{1099} \\ 
+  113 & \cellcolor{white}trench & \cellcolor{white}thickness & \cellcolor{white}compaction & \cellcolor{white}concrete & \cellcolor{white}slab & \cellcolor{white}excavation & \mybar{766} \\ 
+   87 & \cellcolor{white}respondent & \cellcolor{white}survey & \cellcolor{white}census & \cellcolor{white}racial & \cellcolor{white}demographic & \cellcolor{white}score & \mybar{427} \\ 
+   83 & \cellcolor{white}homeless & \cellcolor{white}homelessness & \cellcolor{white}supportive & \cellcolor{white}client & \cellcolor{white}transitional & \cellcolor{white}encampment & \mybar{229} \\
+   20 & \cellcolor{white}noise & \cellcolor{white}fugitive & \cellcolor{white}receptor & \cellcolor{white}exhaust & \cellcolor{white}vibration & \cellcolor{white}emission & \mybar{376} \\ 
+   35 & \cellcolor{white}landlord & \cellcolor{white}tenant & \cellcolor{white}owner & \cellcolor{white}property & \cellcolor{white}rent & \cellcolor{white}lien & \mybar{205} \\ 
+  105 & \cellcolor{white}beach & \cellcolor{white}orange & \cellcolor{white}arena & \cellcolor{white}rainier & \cellcolor{white}ocean & \cellcolor{white}resort & \mybar{457} \\ 
+    2 & \cellcolor{blue!10}yon & \cellcolor{blue!10}bay & \cellcolor{blue!10}gen & \cellcolor{blue!10}sou & \cellcolor{blue!10}coliseum & \cellcolor{blue!10}estuary & \mybar{385} \\ 
+    6 & \cellcolor{white}redevelopment & \cellcolor{white}land & \cellcolor{white}developer & \cellcolor{white}parcel & \cellcolor{white}development & \cellcolor{white}area & \mybar{70} \\ 
+  104 & \cellcolor{white}riparian & \cellcolor{white}wetland & \cellcolor{white}habitat & \cellcolor{white}marsh & \cellcolor{white}floodplain & \cellcolor{white}grassland & \mybar{968} \\ 
+   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}deduction & \cellcolor{white}levy & \cellcolor{white}taxpayer & \mybar{172} \\ 
+   68 & \cellcolor{white}economy & \cellcolor{white}workforce & \cellcolor{white}economic & \cellcolor{white}sector & \cellcolor{white}industry & \cellcolor{white}innovation & \mybar{332} \\ 
+   28 & \cellcolor{white}figure & \cellcolor{white}table & \cellcolor{white}scenario & \cellcolor{white}margin & \cellcolor{white}analysis & \cellcolor{white}appendix & \mybar{207} \\ 
+  110 & \cellcolor{white}bond & \cellcolor{white}maturity & \cellcolor{white}debt & \cellcolor{white}issuer & \cellcolor{white}redemption & \cellcolor{white}obligation & \mybar{232} \\ 
+  102 & \cellcolor{white}sidewalk & \cellcolor{white}curb & \cellcolor{white}pole & \cellcolor{white}crosswalk & \cellcolor{white}ramp & \cellcolor{white}sign & \mybar{237} \\ 
+  118 & \cellcolor{blue!10}project & \cellcolor{blue!10}phase & \cellcolor{blue!10}construction & \cellcolor{blue!10}completion & \cellcolor{blue!10}improvement & \cellcolor{blue!10}complete & \mybar{45} \\
+   78 & \cellcolor{blue!10}parking & \cellcolor{blue!10}tow & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}garage & \cellcolor{blue!10}car & \cellcolor{blue!10}motor & \mybar{210} \\ 
+   71 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}retiree & \cellcolor{blue!10}retirement & \cellcolor{blue!10}pension & \cellcolor{blue!10}deductible & \cellcolor{blue!10}unfunded & \mybar{239} \\
+   91 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}deer & \cellcolor{blue!10}shrub & \cellcolor{blue!10}planting & \mybar{1240} \\ 
+  114 & \cellcolor{blue!10}incumbent & \cellcolor{blue!10}exam & \cellcolor{blue!10}supervision & \cellcolor{blue!10}supervise & \cellcolor{blue!10}examination & \cellcolor{blue!10}ability & \mybar{432} \\
+   16 & \cellcolor{blue!10}park & \cellcolor{blue!10}recreation & \cellcolor{blue!10}playground & \cellcolor{blue!10}zoo & \cellcolor{blue!10}trail & \cellcolor{blue!10}picnic & \mybar{290} \\ 
+   53 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}boat & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}maritime & \cellcolor{blue!10}dock & \cellcolor{blue!10}barge & \mybar{800} \\ 
+   76 & \cellcolor{blue!10}felony & \cellcolor{blue!10}violent & \cellcolor{blue!10}offender & \cellcolor{blue!10}gang & \cellcolor{blue!10}theft & \cellcolor{blue!10}inmate & \mybar{783} \\ 
+    4 & \cellcolor{blue!10}courtyard & \cellcolor{blue!10}realm & \cellcolor{blue!10}design & \cellcolor{blue!10}facade & \cellcolor{blue!10}proponent & \cellcolor{blue!10}articulation & \mybar{608} \\
+  100 & \cellcolor{blue!10}division & \cellcolor{blue!10}manage & \cellcolor{blue!10}staffing & \cellcolor{blue!10}oversee & \cellcolor{blue!10}management & \cellcolor{blue!10}analyst & \mybar{100} \\
+   97 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}alternative & \cellcolor{blue!10}propose & \mybar{132} \\
+   11 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}preservation & \cellcolor{blue!10}historical & \mybar{876} \\
+   77 & \cellcolor{blue!10}million & \cellcolor{blue!10}fiscal & \cellcolor{blue!10}forecast & \cellcolor{blue!10}revenue & \cellcolor{blue!10}quarter & \cellcolor{blue!10}billion & \mybar{138} \\ 
+   74 & \cellcolor{blue!10}board & \cellcolor{blue!10}chairperson & \cellcolor{blue!10}secretary & \cellcolor{blue!10}member & \cellcolor{blue!10}appoint & \cellcolor{blue!10}executive & \mybar{118} \\
+   47 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}bias & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \mybar{580} \\
+   92 & \cellcolor{blue!10}sick & \cellcolor{blue!10}employee & \cellcolor{blue!10}wage & \cellcolor{blue!10}overtime & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{260} \\ 
+   10 & \cellcolor{blue!10}ave & \cellcolor{blue!10}avenue & \cellcolor{blue!10}south & \cellcolor{blue!10}east & \cellcolor{blue!10}west & \cellcolor{blue!10}blvd & \mybar{189} \\ 
+  112 & \cellcolor{blue!10}grant & \cellcolor{blue!10}loan & \cellcolor{blue!10}funding & \cellcolor{blue!10}program & \cellcolor{blue!10}recipient & \cellcolor{blue!10}federal & \mybar{85} \\ 
+   56 & \cellcolor{blue!10}downtown & \cellcolor{blue!10}mall & \cellcolor{blue!10}midtown & \cellcolor{blue!10}uptown & \cellcolor{blue!10}hotel & \cellcolor{blue!10}shopping & \mybar{414} \\ 
+   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}successor & \cellcolor{blue!10}oversight & \cellcolor{blue!10}attachment & \cellcolor{blue!10}describe & \mybar{125} \\ 
+   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}transit & \cellcolor{blue!10}bicyclist & \cellcolor{blue!10}lane & \cellcolor{blue!10}bus & \mybar{315} \\ 
+   62 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}income & \cellcolor{blue!10}household & \cellcolor{blue!10}moderate & \mybar{188} \\
+   99 & \cellcolor{blue!10}memorandum & \cellcolor{blue!10}resolution & \cellcolor{blue!10}council & \cellcolor{blue!10}legislation & \cellcolor{blue!10}entitle & \cellcolor{blue!10}commission & \mybar{173} \\
+   19 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}accounting & \cellcolor{blue!10}asset & \cellcolor{blue!10}statement & \cellcolor{blue!10}financial & \cellcolor{blue!10}net & \mybar{156} \\
+  103 & \cellcolor{blue!10}permission & \cellcolor{blue!10}ayes & \cellcolor{blue!10}correspondence & \cellcolor{blue!10}bid & \cellcolor{blue!10}smith & \cellcolor{blue!10}demolition & \mybar{203} \\
+  107 & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}dollars & \cellcolor{blue!10}thousand & \cellcolor{blue!10}ongoing & \cellcolor{blue!10}matrix & \cellcolor{blue!10}justification & \mybar{117} \\
+   12 & \cellcolor{blue!10}approach & \cellcolor{blue!10}difficult & \cellcolor{blue!10}achieve & \cellcolor{blue!10}challenge & \cellcolor{blue!10}critical & \cellcolor{blue!10}often & \mybar{257} \\
+   46 & \cellcolor{blue!10}variance & \cellcolor{blue!10}fence & \cellcolor{blue!10}setback & \cellcolor{blue!10}exception & \cellcolor{blue!10}yard & \cellcolor{blue!10}applicant & \mybar{136} \\ 
+   90 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}procedure & \cellcolor{blue!10}internal & \cellcolor{blue!10}auditing & \cellcolor{blue!10}documentation & \mybar{226} \\
+   64 & \cellcolor{blue!10}density & \cellcolor{blue!10}urban & \cellcolor{blue!10}corridor & \cellcolor{blue!10}village & \cellcolor{blue!10}orient & \cellcolor{blue!10}transit & \mybar{165} \\ 
+   21 & \cellcolor{blue!10}goal & \cellcolor{blue!10}strategy & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}implementation & \mybar{105} \\
+   73 & \cellcolor{blue!10}parish & \cellcolor{blue!10}rouge & \cellcolor{blue!10}baton & \cellcolor{blue!10}hogan & \cellcolor{blue!10}councilman & \cellcolor{blue!10}thereto & \mybar{482} \\ 
+   29 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}discussion & \cellcolor{blue!10}feedback & \cellcolor{blue!10}discuss & \cellcolor{blue!10}presentation & \mybar{168} \\
+   32 & \cellcolor{blue!10}budget & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}appropriation & \cellcolor{blue!10}fund & \cellcolor{blue!10}endorse & \cellcolor{blue!10}balance & \mybar{129} \\
+   54 & \cellcolor{blue!10}aye & \cellcolor{blue!10}absent & \cellcolor{blue!10}khan & \cellcolor{blue!10}nay & \cellcolor{blue!10}berry & \cellcolor{blue!10}voting & \mybar{344} \\ 
+   39 & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}tab & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}alt & \mybar{117} \\ 
+  109 & \cellcolor{blue!10}auburn & \cellcolor{blue!10}buffalo & \cellcolor{blue!10}ward & \cellcolor{blue!10}brown & \cellcolor{blue!10}announce & \cellcolor{blue!10}casino & \mybar{177} \\ 
+   50 & \cellcolor{blue!10}news & \cellcolor{blue!10}warren & \cellcolor{blue!10}lovely & \cellcolor{blue!10}release & \cellcolor{blue!10}leader & \cellcolor{blue!10}proud & \mybar{498} \\ 
+   79 & \cellcolor{blue!20}digest & \cellcolor{blue!20}proposal & \cellcolor{blue!20}sander & \cellcolor{blue!20}reappoints & \cellcolor{blue!20}metropolitan & \cellcolor{blue!20}gray & \mybar{236} \\
+   27 & \cellcolor{blue!20}bankruptcy & \cellcolor{blue!20}plaintiff & \cellcolor{blue!20}creditor & \cellcolor{blue!20}trial & \cellcolor{blue!20}court & \cellcolor{blue!20}supreme & \mybar{810} \\ 
+   31 & \cellcolor{blue!20}agenda & \cellcolor{blue!20}speaker & \cellcolor{blue!20}item & \cellcolor{blue!20}committee & \cellcolor{blue!20}chair & \cellcolor{blue!20}divided & \mybar{146} \\ 
+   48 & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}reinvestment & \cellcolor{blue!20}inc & \cellcolor{blue!20}contract & \cellcolor{blue!20}authorize & \mybar{134} \\
+   55 & \cellcolor{blue!80}suspect & \cellcolor{blue!80}shoot & \cellcolor{blue!80}fatal & \cellcolor{blue!80}homicide & \cellcolor{blue!80}stopper & \cellcolor{blue!80}pronounce & \mybar{512} \\ 
    \hline

### 2018-08-10 paper/manuscript.tex
fixed a small problem with the tex table labels and renamed some stuff for more sensible file names and table labels

@@
 
-The results are shown in table \ref{stmResultsTable}.
+The results are shown in table \ref{tabSTMtopwords60}.
 The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
@@
 This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 55 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{stmResultsTable120_1} and \ref{stmResultsTable120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
+A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 55 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
 On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
@@
 
-\input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
+\input{tables/stmTopWords60.tex} %\ref{tabSTMtopwords2}
 
@@
 
-\input{tables/stmTopWords120.tex}
+\input{tables/stmTopWords120_1.tex}
 \input{tables/stmTopWords120_2.tex}

### 2018-08-10 stm_results120.R

@@ -78,9 +78,9 @@ topwords3 <- topwords3[order(df$coef, decreasing = T),]
 #remove the last topic
 topwords3 <- topwords3[,-8]
 
-xtTopwords <- print(xtable(topwords3[1:60,], caption = "Top words from a structural topic model with 120 topics (first 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics."), 
+xtTopwords <- print(xtable(topwords3[1:60,], caption = "Top words from a structural topic model with 120 topics (first 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.", 
+                           label = "tabSTMtopwords120_1"), 
                     sanitize.text.function = identity,
-                    label = "tabSTMtopwords2",
                     size = "scriptsize",
                     include.rownames = FALSE)
 
@@ -88,11 +88,11 @@ xtTopwords <- str_replace(xtTopwords, "rlllllll", "rllllllll")
 xtTopwords <- str_replace(xtTopwords, "& Tokens assigned", "& \\\\multicolumn{2}{c}{Tokens assigned}")
 xtTopwords <- str_replace(xtTopwords, "\nTopic &", "\n \\\\# &")
 
-writeLines(xtTopwords, con = 'paper/tables/stmTopWords120.tex')
+writeLines(xtTopwords, con = 'paper/tables/stmTopWords120_1.tex')
 
-xtTopwords <- print(xtable(topwords3[60:120,], caption = "Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics."), 
+xtTopwords <- print(xtable(topwords3[61:120,], caption = "Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.", 
+                           label = "tabSTMtopwords120_2"), 
                     sanitize.text.function = identity,
-                    label = "tabSTMtopwords2",
                     size = "scriptsize",
                     include.rownames = FALSE)
 

### 2018-08-10 paper/manuscript.tex
fixed the same issue for table 7 and removed the last few @markus from the manuscript

@@
 However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
-[@markus, this is an excellent demonstration of the effect of the classifier.
-When you get a chance, would you also add a table listing the top 10 most likely boilerplate lines---to provide face validity that we are accurately flagging boilerplate?] After all the preprocessing is set and done, our corpus consists of 259,099 documents.
+Table \ref{tabBoilerplateIllustration} provides further illustration by listing the top 10 most likely boilerplate lines (in Anchorage, AK) -- all of which were flagged as such with a probability of 1.
+After all the preprocessing is set and done, our corpus consists of 259,099 documents.
 
@@
 The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors [@markus, please add a cite to the specific document in which this number is suggested?] for medium- to large-sized corpora.
+We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.
 Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
@@
 
-The results are shown in table \ref{tabSTMtopwords60}.
+The results are shown in Table \ref{tabSTMtopwords60}.
 The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
@@
 The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.
-[@markus, do the results from the stm package allow us to say anything about whether the overall fit of the model improved from adding party?
-if so, can we mention that?].
 
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
-	\caption{Cities in the corpus, by partisanship of mayor. \textbf{REVISE to remove everything not in our six states.}}
+	\caption{Cities in the corpus, by partisanship of mayor.}
 	\label{us_map}

### 2018-08-30 paper/manuscript.tex
revising results and intro

@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
 
@@
 Once we have gathered the website files, we have the raw data necessary for text analysis, but it is not yet formatted effectively.
+As is common in text analysis applications, we need to pre-process our data \citep{denny2018text}.
 In this section we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
@@
 \subsection{Boilerplate Removal}\label{boilerplate}
-As noted above, city websites contain a large amount of text that is uninformative for its actual content and therefore a hindrance to correct analysis by automatic text processing methods.
+As noted above, city websites contain a large amount of text that is uninformative for its actual content, and therefore a hindrance to understanding through algorithmic text analysis.
 This is a common issue with textual data in which informative content is embedded in technically structured documents.
@@
 \subsubsection{Analytical approach: Structural topic modeling}
-In order to analyze content differences of government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citep{Roberts2014}.
+In order to analyze content differences of government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citet{Roberts2014}.
 Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the structural topic model a topic is a multinomial distribution defined on the word types in the dictionary.
@@
 	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
+	\includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
 		\caption{Cities in the corpus, by partisanship of mayor.}
 	\label{us_map}
-	\includegraphics[width=\linewidth]{figures/us_map.pdf}
 \end{figure}

### 2018-08-30 paper/manuscript.tex
added a reference

@@
 One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example Los Angeles, do contain a sizable proportion of Spanish content.
-The analysis of this content is beyond the scope of this paper, but could be explored in future work, for example relying on multilingual word embeddings.} However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
+The analysis of this content is beyond the scope of this paper, but could be explored in future work, for example using methods of text processing that are applicable to multilingual corpora \citep{lucas2015computer}.
+} However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
 Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.

### 2018-08-30 paper/manuscript.tex
improved captions and re-ordered figures 2-5

@@
 	\centering
-	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
 	\label{boilerplate_before_after1}
@@
 	\centering
-	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
 	\label{boilerplate_before_after2}
+	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
+\end{figure}
+\begin{figure}[htp]
+	\centering
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.
+After the boilerplate content is removed, lines that are duplicated hundreds or thousands of times are less common.}
+	\label{boilerplate_before_after3}
 	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
@@
 	\centering
-	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
-	\label{boilerplate_before_after3}
+	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, lines at the beginning and end of documents are less common.}
+	\label{boilerplate_before_after4}
 	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
-\end{figure}
-\begin{figure}[htp]
-	\centering
-	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
-	\label{boilerplate_before_after4}
-	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
 \end{figure}

### 2018-08-30 paper/manuscript.tex
improved caption for figure 6

@@
 	\includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
-		\caption{Cities in the corpus, by partisanship of mayor.}
+		\caption{Map of the cities in the corpus in the contiguous U.S.
+The corpus also includes Alaska.
+In the analysis, only cities in California, Indiana, Louisiana, New York, Texas and Washington are used.
+The colors represent the partisanship of the mayor (blue corresponding to Democrats and red to Republicans).}
 	\label{us_map}

### 2018-09-01 paper/manuscript.tex
some minor edits to the paper

@@
 First, plain text must be extracted from the files.
-This involves purging the files of syntax in HTML and other programming languages, and discarding any other character encoding errors that result from reading the files.
+This involves purging the files of syntax in HTML or other markup and programming languages, and discarding any character encoding errors that result from reading in files with incorrectly specified character encodings.
 This challenge would arise in any context in which researchers sought to study the textual contents of websites, and is not unique to comparative analysis of government websites.
@@
 A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
-Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public \citep{sharfstein2017science,kirby2017trump,duarte2017deniable} .
+Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public \citep{sharfstein2017science,kirby2017trump,duarte2017deniable}.
 We study whether significant differences between city governments based on mayoral partisanship are reflected in the contents of city websites.
@@
 \cite{Eschenfelder2002} provide something of an overview of how how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
-In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
+%In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
 We then define a pipeline for data collection and analysis that includes methods to access government website URLs, scrape their raw contents from the World Wide Web, gather plain text from the website files, and identify boilerplate text within the plain text contents.
@@
 
-In this section we introduce the data we use in our application.
 For data availability reasons, on which we elaborate below, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California and Texas.
@@
 We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
-Two, the General Services Administration (GSA) maintains all .gov addresses, and provides a complete list of all such domains to the public.
-\footnote{ The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
+Two, the General Services Administration (GSA) maintains all `.gov' addresses, and provides a complete list of all such domains to the public.\footnote{The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
 This list is updated once per month---we rely on the version released on January 16, 2017.} The data from the GSA contains the following variables: (1) domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'); (2) the type of government entity to which the domain is registered, such as city, county, federal agency, etc; (3) for federal agencies, the name is specified; (4) the city in which the domain is registered.
-Naturally, the GSA's list does not contain cities which do not use a .gov website (or, in many cases, a city owns a registered .gov address, but uses a different one).
+Naturally, the GSA's list does not contain cities which do not use a `.gov' website (or, in many cases, a city owns a registered `.gov' address, but uses a different one).
 Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
@@
 
-To test whether the websites we found actually work, we use a webdriver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
+Not all of the URLS contained in these archives are functional.
+To test the URLs' functionality, we use a webdriver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
 We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the webdriver  \texttt{Geckodriver}.
@@
 Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
-Scrapers can perform most, but not all of such operations.
 The use of a webdriver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
@@
 This program is used to download files from the Internet, and with the use of a recursive option, acts like a webcrawler and scraper.
-This means that \texttt{wget} scrapes HTML files, parses them and then follows the links contained therein.
-Then it follows those links, and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain).
+This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
+Then it follows those links, and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
+it does not follow external links).
 This way, all the files that make up a website are downloaded.
-For some cities, whose websites make heavy use of JavaScript, this method does not lead to satisfying results.
-Consequently we restricted our corpus to cities with at least 3 documents.
+For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
+For this paper we ignore such sites and restricte our corpus to cities with at least three successfully downloaded pages.
 
@@
 
-The text documents are then read into R line by line, converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
+We then take several steps to pre-processing the data as required for subsequent the subsequent analysis.
+Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}.
+The steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
+
+The text documents are converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
 At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
 "You are here", "Home", "Directory" etc.) in html documents, or commonly used forms or phrases in pdfs, doc and docx files.
-This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate, and not the substantive features of their contents.
-In other words, the signal would be drowned out by the noise.
+This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate (through their unique boilerplate structure, e.g.
+a menu with certain terms repeated on every site of the domain), and not the substantive features of their contents.
 Our solution to this problem is described in more detail in Section \ref{boilerplate}.
+
 Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
@@
 In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
-We sampled 100 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
+We sampled 500 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
 To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.

### 2018-09-01 paper/manuscript.tex
spelling and grammar edits

@@
 Though highly accurate, the manual approach to data collection is costly, and cannot be scaled to capture even a fraction of the volume of content available on government websites.
-In this paper we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis.
+In this paper, we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis.
 We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states (IN, LA, NY, WA, CA and TX) correlate with the partisanship of the city mayor.
@@
 First, plain text must be extracted from the files.
-This involves purging the files of syntax in HTML or other markup and programming languages, and discarding any character encoding errors that result from reading in files with incorrectly specified character encodings.
+This involves purging the files of syntax in HTML or other markup and programming languages and discarding any character encoding errors that result from reading in files with incorrectly specified character encodings.
 This challenge would arise in any context in which researchers sought to study the textual contents of websites, and is not unique to comparative analysis of government websites.
@@
 Government websites provide information about how public policies shape the lives of local residents, and how local residents can engage with government to shape public policy.
-As such, government websites reflect both the results of, and inputs to, the political leadership in the city.
-In our illustrative application we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
+As such, government websites reflect both the results of and inputs to, the political leadership in the city.
+In our illustrative application, we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
 A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
@@
 We present an example of this in Figure \ref{fig:eriemayor}.
-The Erie, Pennsylvania website homepage presents an image of Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
+The Erie, Pennsylvania website homepage presents an image of the Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
 In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies.
@@
 The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
-For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}.
+For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use, and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
@@
 The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
-Like most e-government studies however, this publication does not make any use of automated text analysis.
+Like most e-government studies, however, this publication does not make any use of automated text analysis.
 %Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
-\cite{Lin2011} provide a good example for a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
+\cite{Lin2011} provide a good example of a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
 The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased.
@@
 The websites of politicians and their parties have also fallen under scholarly scrutiny.
-Researchers have found that in order to identify the constituencies, motives and modes of communication of these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
 \cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them.
-\cite{Cryer2017} mentions that she relied on Archive-it, a webservice of the Internet Archive.
+\cite{Cryer2017} mentions that she relied on Archive-it, a web service of the Internet Archive.
 Though the Internet Archive may provide extensive coverage of high profile officials or national governments, we found that its coverage of municipal government websites was sparse and irregular.
@@
 Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
-\cite{Eschenfelder2002} provide something of an overview of how how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
+\cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
 %In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
@@
 
-For data availability reasons, on which we elaborate below, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California and Texas.
+For data availability reasons, on which we elaborate below, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
 These states provide us with a sample that is well-balanced on a number of theoretically important indicators.
-One, each of the four geographic regions is represented with at least one state.
+One, each of the four geographic regions are represented with at least one state.
 Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered.
@@
 Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
-Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former, and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
-
-Not all of the URLS contained in these archives are functional.
-To test the URLs' functionality, we use a webdriver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
-We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the webdriver  \texttt{Geckodriver}.
+Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
+
+Not all of the URLs contained in these archives are functional.
+To test the URLs' functionality, we use a web driver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
+We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the web driver  \texttt{Geckodriver}.
 This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers.
 Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
-The use of a webdriver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
-A webdriver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
+The use of a web drive-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
+A web driver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
 This allows us to subsequently record and use the new URL for the actual website scraping.
@@
 To download the websites, we rely on the Unix command line tool \texttt{wget}.
-This program is used to download files from the Internet, and with the use of a recursive option, acts like a webcrawler and scraper.
+This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
 This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
-Then it follows those links, and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
+Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
 it does not follow external links).
@@
 For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
-For this paper we ignore such sites and restricte our corpus to cities with at least three successfully downloaded pages.
+For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.
 
@@
 Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
-When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable, and added additional cases to our dataset even for Indiana and Louisiana.
+When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
 Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
@@
 Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies.
-Unfortunately we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant.
+Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant.
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
@@
 As is common in text analysis applications, we need to pre-process our data \citep{denny2018text}.
-In this section we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
-In this methodological pipeline we address two methodological challenges.
+In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
+In this methodological pipeline, we address two methodological challenges.
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
@@
 The first step in the methodological pipeline is aimed simply at extracting clean plain text from this heterogeneous file base.
-The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another, but is uninformative regarding policy or politics differences between governments.
+The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
 
@@
 However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text, arising from incorrectly converted documents, which leads to a general decrease in the amount of usable data.
-Two issues in particular need to be addressed: One, HTML files on city websites frequently do not have an ending, but are still perfectly readable if correctly identified as such.
+Two issues, in particular, need to be addressed: One, HTML files on city websites frequently do not have an ending but are still perfectly readable if correctly identified as such.
 Second, some documents contain the incorrect file ending.
@@
 
-Consequently we rename all documents so that their file ending reflects their actual file type.
-This is strictly necessary, because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
+Consequently, we rename all documents so that their file ending reflects their actual file type.
+This is strictly necessary because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
 The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
@@
 
-We then take several steps to pre-processing the data as required for subsequent the subsequent analysis.
+We then take several steps to pre-process the data as required for subsequent the subsequent analysis.
 Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}.
@@
 
-The text documents are converted to UTF-8 and then stripped of dates, punctuation, numbers and words connected by underscores.
+The text documents are converted to UTF-8 and then stripped of dates, punctuation, numbers, and words connected by underscores.
 At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
-"You are here", "Home", "Directory" etc.) in html documents, or commonly used forms or phrases in pdfs, doc and docx files.
+"You are here", "Home", "Directory" etc.) in HTML documents, or commonly used forms or phrases in pdf, doc and docx files.
 This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate (through their unique boilerplate structure, e.g.
@@
 
-Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in html documents, extraneous whitespace, xml documents mislabeled as html files, and empty documents.
+Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
 Furthermore, some documents contain gibberish, often as a result of faulty or impartial optical character recognition applied to text that was produced through a non-machine-readable medium.
 To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example Los Angeles, do contain a sizable proportion of Spanish content.
-The analysis of this content is beyond the scope of this paper, but could be explored in future work, for example using methods of text processing that are applicable to multilingual corpora \citep{lucas2015computer}.
+One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example, Los Angeles, do contain a sizable proportion of Spanish content.
+The analysis of this content is beyond the scope of this paper but could be explored in future work, for example using methods of text processing that are applicable to multilingual corpora \citep{lucas2015computer}.
 } However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
 Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
-Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to total number of tokens is less than 0.15.
+Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to the total number of tokens is less than 0.15.
 Furthermore, \texttt{hunspell} does not spellcheck individual characters or two-character words, so we remove these token types entirely.
@@
 We also conduct lemmatization to reduce words to their basic form.
-Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
+Lemmatization is similar to stemming but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
 For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
@@
 %this is outdated; not deleting it yet in case we need it for further reference
-%Consequently we remove this content as following: Each line of every document is compared to every line in every other document belonging to the same city.
+%Consequently we remove this content as follows: Each line of every document is compared to every line in every other document belonging to the same city.
 We count how many times each line is duplicated for that city.
-We remove any line occuring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times, or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
+We remove any line occurring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
 We implement this algorithm through hash tables, which reduces the computational complexity from O($N^2$) to O($N$).
@@
 \item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two.
-This is highly predictive of lines which are used as website headers and navigational elements, which are of of zero substantive interest to us, but are very effective at differentiating cities.
+This is highly predictive of lines which are used as website headers and navigational elements, which are of zero substantive interest to us but are very effective at differentiating cities.
 These terms also happen to be fairly common, which causes them to be overweighted by the topic model.
@@
 \item {\bf Number of line duplications:} To directly address the latter problem, we include a measure of the number of times a line is duplicated within a city.
-Many lines occur hundreds or even thousands of times on a single website, and therefore are terms that are highly predictive of the website, which causes the topic model to find topics that are highly predictive of cities, but not substantively informative.
+Many lines occur hundreds or even thousands of times on a single website and therefore are terms that are highly predictive of the website, which causes the topic model to find topics that are highly predictive of cities, but not substantively informative.
 
 \item {\bf Line position in the document} Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
-Since lines can occur in multiple documents, or multiple times in the same document, we take the median of these measures.
-Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus be indicative of more relevant content, might be scored with a 0.11 instead.
+Since lines can occur in multiple documents or multiple times in the same document, we take the median of these measures.
+Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus is indicative of more relevant content, might be scored with a 0.11 instead.
 \end{itemize}
@@
 
-We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess performance of this classifier through five-fold cross-validation.
+We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess the performance of this classifier through five-fold cross-validation.
 This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score.
-This procedure is carried out five times, so that each sample is part of the test set once.
+This procedure is carried out five times so that each sample is part of the test set once.
 The aggregated (mean) results of this process can be found in Table \ref{randomForest}.
@@
 Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}).
-Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results.
+Finally, the position of the line in the documents is not as important to the random forest, and this also shows in the results.
 However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
@@
 As opposed to budget allocation or even the presence/absence of policies, cities have a great deal of discretion regarding what is emphasized on their websites, and how policies are framed.
-Since (1) city governments have great discretion in composing their websites, (2) modifying website content is low cos relative to other policy changes, and (3), as reviewed above, city websites provide an effective and often-used means of communication with city residents.
+Since (1) city governments have great discretion in composing their websites, (2) modifying website content is low cost relative to other policy changes, and (3), as reviewed above, city websites provide an effective and often-used means of communication with city residents.
 
@@
 \subsubsection{Analytical approach: Structural topic modeling}
-In order to analyze content differences of government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citet{Roberts2014}.
+In order to analyze content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citet{Roberts2014}.
 Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the structural topic model a topic is a multinomial distribution defined on the word types in the dictionary.
@@
 The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic.
-The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.
+The topics that are entirely white have 90\% credible intervals on the effect of the mayoral party that include zero.
 
@@
 However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
-Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Repuiblican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted html, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
+Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Republican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted HTML, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
 
@@
 %An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
-This is facilitated by the structural topic model, which uses metadata on the document to account for variation in topics \citep{Roberts2014}.
+This is facilitated by the structural topic model, which uses document metadata t to account for variation in topics \citep{Roberts2014}.
 However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
@@
 %\subsubsection{Prediction with SVM}
-%An alternative approach to the problem is to ignore topics entirely, and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
+%An alternative approach to the problem is to ignore topics entirely and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
 Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
@@
 Instead, we ranked the features according to tf-idf and selected the top 5000.
-These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
+These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross-validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
 Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
@@
 
-%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
+%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backward: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
 
@@
 %    \includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-%		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
+%        \caption{Total number of lines retained at a given threshold for removing duplicated lines.
+For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
 %    \label{linesCutoff}
@@
 Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
-However, the aspirations some mayors have shown towards higher offices - in some cases even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
+However, the aspirations some mayors have shown towards higher offices - in some cases, even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
 One of the most vicious and blatantly partisan cleavages in current U.S.
@@
 When voters are denied this cue, they make use of other, and considerably more irrational heuristics, such as name, gender, or occupation of the contenders.
-Consequently it only makes sense for any office-seeking politician to emphasize their partisanship.
+Consequently, it only makes sense for any office-seeking politician to emphasize their partisanship.
 Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
@@
 As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
-Consequently they are very likely to emphasize conservative/liberal values on this platform.
+Consequently, they are very likely to emphasize conservative/liberal values on this platform.
 If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
@@
 %Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
-We do the same for the city documents, and the compare the four document collections using cosine similarity.
-This measure is the cosine between the angle of two vectors, in this case the frequencies of all words in the two vocabularies.
-Compared to a simple euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
+We do the same for the city documents, and then compare the four document collections using cosine similarity.
+This measure is the cosine between the angle of two vectors, in this case, the frequencies of all words in the two vocabularies.
+Compared to a simple Euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
 The cosine measure between two documents ranges between 0 and 1, 0 signifying absolutely no correlation, and 1 perfect overlap.
 Figure \ref{groundtruth} shows the result of this test.
-The expectation is for a greater similarity between Republican cities and the Republican ground truth, than Republican cities and Democratic ground truth - and vice versa.
-At present however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
+The expectation is for a greater similarity between Republican cities and the Republican ground truth than Republican cities and Democratic ground truth - and vice versa.
+At present, however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
 
@@
 This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
-The methods involved in the pipeline include checking the integrity of the site addresses, extracting english language from website contents, identifying document types, and removing boilerplate language.
+The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language.
 Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
-We find that government website contents is associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
+We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
 
@@
 First, the data collected in the current study can be used for comparative analysis of US city website contents.
-Second, the pipeline we present can be used as a set of procedures to follow in gathering large scale datasets of textual contents from other samples of governments.
+Second, the pipeline we present can be used as a set of procedures to follow in gathering large-scale datasets of textual contents from other samples of governments.
 Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.
@@
     \centering
-	\caption{Five largest topic effects for the population covariate. The fact that the population and epidemiology topics are positively correlated with city size is indicative of the model's validity.}
+    \caption{Five largest topic effects for the population covariate.
+The fact that the population and epidemiology topics are positively correlated with city size is indicative of the model's validity.}
     \label{stmEffectPop}
@@
 %            Gerber, Elisabeth R.
-%			Hopkins, Daniel J. & 2011 & AJPS & Regression discontinuity design. Democratic mayors spend less on public safety. All other policy areas (including taxation) are unaffected. & Yes \\ \hline
+%            Hopkins, Daniel J.
+& 2011 & AJPS & Regression discontinuity design.
+Democratic mayors spend less on public safety.
+All other policy areas (including taxation) are unaffected.
+& Yes \\ \hline
 %            Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
@@
 %            Ferreira, Fernando
-%			Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design. Null results for spending and city gov. size with regard to mayor partisanship. & Yes \\ \hline
+%            Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design.
+Null results for spending and city gov.
+size with regard to mayor partisanship.
+& Yes \\ \hline
 %            Ansolabehere, Stephen

### 2018-09-01 paper/manuscript.tex
removed covariate tables

@@
 
-\begin{figure}[htp]
-    \centering
-    \caption{Five largest topic effects for the population covariate.
+%\begin{figure}[htp]
+  %  \centering
+   % \caption{Five largest topic effects for the population covariate.
 The fact that the population and epidemiology topics are positively correlated with city size is indicative of the model's validity.}
-    \label{stmEffectPop}
-    \includegraphics[width=\linewidth]{figures/stm_effect_pop.pdf}
-\end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \caption{Five largest topic effects for the median income covariate.
+    %  \label{stmEffectPop}
+    % \includegraphics[width=\linewidth]{figures/stm_effect_pop.pdf}
+% \end{figure}
+
+% \begin{figure}[htp]
+  %  \centering
+   % \caption{Five largest topic effects for the median income covariate.
 The fact that the crime topic is most prevalent in poorer cities, good governance is the most positively correlated with income is indicative of the model's validity.}
-    \label{stmEffectIncome}
-    \includegraphics[width=\linewidth]{figures/stm_effect_income.pdf}
-\end{figure}
+   % \label{stmEffectIncome}
+    %\includegraphics[width=\linewidth]{figures/stm_effect_income.pdf}
+%\end{figure}
 

### 2018-09-12 paper/TADA2018_Poster/main.tex
poster for TADA

\documentclass{beamer}
%% Possible paper sizes: a0, a0b, a1, a2, a3, a4.
%% Possible orientations: portrait, landscape
%% Font sizes can be changed using the scale option.
\usepackage[size=a3,orientation=landscape,scale=3.75]{beamerposter}
\usetheme{LLT-poster}
%\usecolortheme{ComingClean}
\usecolortheme{Entrepreneur}
%\usecolortheme{ConspicuousCreep}  %% VERY garish.
\usepackage{graphicx}
\usepackage{xcolor, colortbl}
\usepackage{array}

\def\mybar#1{%%
    #1 & {\color{red}\pgfmathsetlengthmacro\x{#1*0.006mm}\rule{\x}{4pt}}}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[scaled=0.92]{inconsolata}
\usepackage[libertine]{newtxmath}
\usepackage{geometry}
\geometry{paperwidth=32in,paperheight=40in,margin=3cm}
\usepackage{multicol}
\usepackage{mwe}

\author[mvn5218@psu.edu]{Markus Neumann}
\title{Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States \\ \vspace{10mm} \small{Markus Neumann,  Fridolin Linder,  Bruce Desmarais \\ Department of Political Science - Penn State University}}
\institute{The Pennsylvania State University}
% Optional foot image
%\footimage{\includegraphics[width=4cm]{IMG_1934.jpg}}

\begin{document}
\beamertemplatenavigationsymbolsempty
\begin{frame}[fragile]
\begin{columns}[T]

%%%% 1st Column
\begin{column}{.4\textwidth}

\begin{block}{Overview}
\begin{itemize}
\item Websites of local governments are an important source of information for citizens
\item Extant research of government websites has largely relied on manual coding
\item We develop a methodological pipeline for the automated analysis of government websites
\item We demonstrate the use of this pipeline on the websites of 234 municipal websites in CA, IN, LA, NY, TX and WA. 
\item We show that content varies with the partisanship of the mayor.
\end{itemize}
\end{block}

\begin{block}{Data Collection}
\begin{itemize}
\item Scraping city URLs from Wikipedia and the General Services Administration, which keeps a list of all .gov addresses
\item Verification of which websites actually work through an automated browser
\item Downloading the websites through \texttt{wget}
\item Information on mayoral partisanship from state websites, the LEAP project, Ballotpedia and Wikipedia
%\item 234 Websites in CA, IN, LA, NY, TX and WA.
\end{itemize}
\end{block}

\begin{block}{Site to Text Conversion}
\begin{itemize}
\item The file endings from open data sources such as governmental websites are sometimes wrong. This causes problems when converting to text.
\item We use file signatures to identify the correct type before conversion with \texttt{readtext}.
\item Used file types: Html, xml, pdf, doc, docx, txt
\item Everything is converted to .txt
\item Preprocessing: Lowercase; removal of punctuation, numbers, dates, etc.; spellchecking/Removal of non-English words; Lemmatization
\end{itemize}
\end{block}

\begin{block}{Boilerplate Removal}
\begin{itemize}
\item Websites contain a lot of text that is not substantively interesting
\item This text is often repeated on each page of a site - for example website elements such as ``You are here'', ''Home'', or the names of city officials and offices.
\item If this content is not removed, the tool of analysis will associate specific patterns of boilerplate with the respective cities
\item Problem: how to remove boilerplate content without dropping useful information?
\end{itemize}
\end{block}

\begin{block}{Boilerplate Classifier}
\begin{itemize}
\item Solution: Train a classifier (random forest) on manually annotated lines of website content. A line can be flagged as either substantively useful or boilerplate.
\item The classifier relies on the following features:
\begin{itemize}
\item Line length (number of words & characters)
\item Number of line duplications within a website
\item Line position in the document (median distance of a line to the document midpoint)
\end{itemize}
\end{itemize}
\end{block}

\end{column}

%\begin{column}{.63\textwidth}
%\begin{block}{Additional Preprocessing}
%\begin{itemize}
%\item Lowercase; removal of punctuation, numbers, dates, etc.
%\item Spellchecking/Removal of non-English words
%\item Lemmatization
%\end{itemize}
%\end{block}
%\end{column}

%%%% 2nd Column

\begin{column}{.6\textwidth}

%\begin{column}{.23\textwidth}

%\end{column}

%%%%  3rd column

%\begin{column}{.23\textwidth}

\begin{block}{Analysis}

\begin{center}
\begin{itemize}
\item Structural topic model with 60 topics
\item Covariates: Party, state, population, median income
\end{itemize}

\vspace{5mm}

\input{stmTopWords60.tex}

%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{stm_test.png}
%    %\caption{Caption}
%    \label{fig:my_label}
%\end{figure}

\end{center}

\end{block}

\begin{block}{Conclusion}
\begin{itemize}
\item Cities with Republican mayors provide more information about basic utilities such as water, energy, fire safety, or  natural disaster protection.
\item Cities with Democratic mayors provide more information about policy deliberation, crime control, or public housing.
\item These findings call into question the commonly held notion that politics at the municipal level is largely non-partisan.
\item We plan to implement the pipeline in an R package
\end{itemize}
\end{block}

%\end{column}
\end{column}

\end{columns}

\end{frame}
\end{document}

### 2018-09-12 paper/TADA2018_Poster/stmTopWords60.tex
poster for TADA

--- 2018-08-03 paper/tables/stmTopWords2.tex
@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Fri Aug  3 14:57:28 2018
+% Fri Aug 10 15:33:35 2018
 \begin{table}[ht]
 \centering
-\begingroup\scriptsize
+\begingroup\footnotesize
 \begin{tabular}{rllllllll}
@@
    60 & \cellcolor{red!10}exhaust & \cellcolor{red!10}fugitive & \cellcolor{red!10}aircraft & \cellcolor{red!10}airport & \cellcolor{red!10}aviation & \cellcolor{red!10}diesel & \mybar{731} \\ 
-   30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
-   58 & \cellcolor{white}councilor & \cellcolor{white}auburn & \cellcolor{white}plain & \cellcolor{white}ward & \cellcolor{white}beech & \cellcolor{white}glen & \mybar{480} \\ 
-   51 & \cellcolor{white}whereas & \cellcolor{white}councilman & \cellcolor{white}alderman & \cellcolor{white}ordain & \cellcolor{white}hereby & \cellcolor{white}resolution & \mybar{420} \\ 
-   16 & \cellcolor{white}recreation & \cellcolor{white}park & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{682} \\ 
-   36 & \cellcolor{white}retiree & \cellcolor{white}retirement & \cellcolor{white}actuarial & \cellcolor{white}deductible & \cellcolor{white}dental & \cellcolor{white}pension & \mybar{470} \\ 
-   27 & \cellcolor{white}exam & \cellcolor{white}incumbent & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}examination & \cellcolor{white}knowledge & \mybar{687} \\ 
-   56 & \cellcolor{white}historic & \cellcolor{white}landmark & \cellcolor{white}revival & \cellcolor{white}archaeological & \cellcolor{white}century & \cellcolor{white}historian & \mybar{2587} \\ 
-   12 & \cellcolor{white}parking & \cellcolor{white}hotel & \cellcolor{white}garage & \cellcolor{white}space & \cellcolor{white}retail & \cellcolor{white}square & \mybar{321} \\ 
-   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 
+   %30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
+   %58 & \cellcolor{white}councilor & \cellcolor{white}auburn & \cellcolor{white}plain & \cellcolor{white}ward & \cellcolor{white}beech & \cellcolor{white}glen & \mybar{480} \\ 
+   %51 & \cellcolor{white}whereas & \cellcolor{white}councilman & \cellcolor{white}alderman & \cellcolor{white}ordain & \cellcolor{white}hereby & \cellcolor{white}resolution & \mybar{420} \\ 
+   %16 & \cellcolor{white}recreation & \cellcolor{white}park & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{682} \\ 
+   %36 & \cellcolor{white}retiree & \cellcolor{white}retirement & \cellcolor{white}actuarial & \cellcolor{white}deductible & \cellcolor{white}dental & \cellcolor{white}pension & \mybar{470} \\ 
+   %27 & \cellcolor{white}exam & \cellcolor{white}incumbent & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}examination & \cellcolor{white}knowledge & \mybar{687} \\ 
+   %56 & \cellcolor{white}historic & \cellcolor{white}landmark & \cellcolor{white}revival & \cellcolor{white}archaeological & \cellcolor{white}century & \cellcolor{white}historian & \mybar{2587} \\ 
+   %12 & \cellcolor{white}parking & \cellcolor{white}hotel & \cellcolor{white}garage & \cellcolor{white}space & \cellcolor{white}retail & \cellcolor{white}square & \mybar{321} \\ 
+   %41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 
     4 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}porch & \cellcolor{white}roof & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1108} \\ 
@@
 \endgroup
-\caption{Top words from a structural topic model with 60 topics and FREX scoring.
-Colors depict partisanship based on coefficient size.
-White cells are non-significant topics.
-Based on data preprocessed with the classifier.}
+%\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
+\label{tabSTMtopwords60}
 \end{table}

### 2018-09-14 paper/TADA2018_Poster/main.tex
updates to the poster (not done yet)

@@
 \usepackage{geometry}
-\geometry{paperwidth=32in,paperheight=40in,margin=3cm}
+\geometry{paperwidth=32in,paperheight=40in,margin=2cm}
 \usepackage{multicol}
@@
 \author[mvn5218@psu.edu]{Markus Neumann}
-\title{Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States \\ \vspace{10mm} \small{Markus Neumann,  Fridolin Linder,  Bruce Desmarais \\ Department of Political Science - Penn State University}}
+\title{Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States \\ \vspace{10mm} \small{Markus Neumann (mvn5218@psu.edu),  Fridolin Linder (flinder@gmail.com),  Bruce Desmarais (brucedesmarais@psu.edu) \\ Department of Political Science - Penn State University}}
 \institute{The Pennsylvania State University}
@@
 \begin{block}{Overview}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{eriemayor.png}
+    %\caption{Caption}
+    %\label{fig:my_label}
+\end{figure}
 \begin{itemize}
-\item Websites of local governments are an important source of information for citizens
-\item Extant research of government websites has largely relied on manual coding
-\item We develop a methodological pipeline for the automated analysis of government websites
-\item We demonstrate the use of this pipeline on the websites of 234 municipal websites in CA, IN, LA, NY, TX and WA. 
-\item We show that content varies with the partisanship of the mayor.
+\item Government websites contain important information
+\item Research has largely relied on manual coding
+\item Our contribution: pipeline for automated analysis
+\item Application: websites of partisan municipalities
 \end{itemize}
@@
 \begin{itemize}
-\item Scraping city URLs from Wikipedia and the General Services Administration, which keeps a list of all .gov addresses
-\item Verification of which websites actually work through an automated browser
-\item Downloading the websites through \texttt{wget}
-\item Information on mayoral partisanship from state websites, the LEAP project, Ballotpedia and Wikipedia
-%\item 234 Websites in CA, IN, LA, NY, TX and WA.
+\item City URLs are scraped from Wikipedia and the GSA
 \end{itemize}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{us_map_resized.png}
+    %\caption{Caption}
+    %\label{fig:my_label}
+\end{figure}
+%\include{tabCitiesStatesParties.tex}
 \end{block}
@@
 \begin{block}{Site to Text Conversion}
+\input{tabFiletypeFrequencies.tex}
 \begin{itemize}
-\item The file endings from open data sources such as governmental websites are sometimes wrong. This causes problems when converting to text.
-\item We use file signatures to identify the correct type before conversion with \texttt{readtext}.
-\item Used file types: Html, xml, pdf, doc, docx, txt
-\item Everything is converted to .txt
-\item Preprocessing: Lowercase; removal of punctuation, numbers, dates, etc.; spellchecking/Removal of non-English words; Lemmatization
-\end{itemize}
-\end{block}
-
-\begin{block}{Boilerplate Removal}
-\begin{itemize}
-\item Websites contain a lot of text that is not substantively interesting
-\item This text is often repeated on each page of a site - for example website elements such as ``You are here'', ''Home'', or the names of city officials and offices.
-\item If this content is not removed, the tool of analysis will associate specific patterns of boilerplate with the respective cities
-\item Problem: how to remove boilerplate content without dropping useful information?
-\end{itemize}
-\end{block}
-
-\begin{block}{Boilerplate Classifier}
-\begin{itemize}
-\item Solution: Train a classifier (random forest) on manually annotated lines of website content. A line can be flagged as either substantively useful or boilerplate.
-\item The classifier relies on the following features:
-\begin{itemize}
-\item Line length (number of words & characters)
-\item Number of line duplications within a website
-\item Line position in the document (median distance of a line to the document midpoint)
-\end{itemize}
+\item The file endings from city websites are sometimes wrong
+\item We use file signatures to identify the correct type
+\item Preprocessing: lowercase; removal of punctuation, numbers, dates, etc.; removal of non-English words; lemmatization
 \end{itemize}
@@
 \end{column}
+\begin{column}{.6\textwidth}
+\begin{block}{Boilerplate Removal}
+\begin{itemize}
+\item Websites contain a lot repetitive and uninformative content
+\end{itemize}
+\begin{figure}
+    \centering
+    \includegraphics[width=.8\linewidth]{arcadia_water_TADA_rect.png}
+    %\caption{Caption}
+    %\label{fig:my_label}
+\end{figure}
+\begin{itemize}
+\item A classifier (random forest) is trained to identify and remove boilerplate lines
+\end{itemize}
+\begin{minipage}{\textwidth}
+  \begin{minipage}[b]{0.49\textwidth}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.85\linewidth]{boilerplateBeforeAfterNwords.pdf}
+        %\caption{Caption}
+        %\label{fig:my_label}
+    \end{figure}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.49\textwidth}
+    \input{boilerplateClassifierRFMetrics.tex}
+    \end{minipage}
+  \end{minipage}
+\end{block}
 
@@
 %%%% 2nd Column
-
-\begin{column}{.6\textwidth}
 
@@
 \begin{itemize}
-\item Cities with Republican mayors provide more information about basic utilities such as water, energy, fire safety, or  natural disaster protection.
-\item Cities with Democratic mayors provide more information about policy deliberation, crime control, or public housing.
-\item These findings call into question the commonly held notion that politics at the municipal level is largely non-partisan.
+\item Republican cities feature information on basic utilities and protection from natural disasters
+\item Democratic cities feature information on policy deliberation, crime control and city budgeting
+\item Politics at the municipal level is not entirely non-partisan
 \item We plan to implement the pipeline in an R package

### 2018-09-14 paper/TADA2018_Poster/stmTopWords60.tex
updates to the poster (not done yet)

@@
   \hline
- 43 & \cellcolor{red!50}fun & \cellcolor{red!50}player & \cellcolor{red!50}dream & \cellcolor{red!50}celebration & \cellcolor{red!50}favorite & \cellcolor{red!50}blog & \mybar{3460} \\ 
-    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}contact & \cellcolor{red!30}copy & \cellcolor{red!30}mail & \cellcolor{red!30}click & \mybar{201} \\ 
    42 & \cellcolor{red!20}breastfeed & \cellcolor{red!20}vaccine & \cellcolor{red!20}infection & \cellcolor{red!20}symptom & \cellcolor{red!20}asthma & \cellcolor{red!20}mosquito & \mybar{2497} \\ 
@@
    53 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pipeline & \cellcolor{red!20}pump & \cellcolor{red!20}disinfection & \mybar{461} \\
-   50 & \cellcolor{red!20}buffalo & \cellcolor{red!20}news & \cellcolor{red!20}honor & \cellcolor{red!20}warren & \cellcolor{red!20}announce & \cellcolor{red!20}lovely & \mybar{1106} \\ 
-   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}digest & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}legislator & \cellcolor{red!20}sander & \mybar{997} \\ 
-   33 & \cellcolor{red!20}really & \cellcolor{red!20}think & \cellcolor{red!20}something & \cellcolor{red!20}thing & \cellcolor{red!20}somebody & \cellcolor{red!20}anybody & \mybar{1873} \\ 
-   44 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}pursuant & \mybar{405} \\ 
-    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}card & \cellcolor{red!10}amt & \cellcolor{red!10}filer & \cellcolor{red!10}debit & \cellcolor{red!10}officeholder & \mybar{527} \\ 
-   26 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}billing & \cellcolor{red!10}per & \cellcolor{red!10}meter & \cellcolor{red!10}monthly & \mybar{233} \\ 
-    2 & \cellcolor{red!10}yon & \cellcolor{red!10}borough & \cellcolor{red!10}comm & \cellcolor{red!10}gen & \cellcolor{red!10}sou & \cellcolor{red!10}spec & \mybar{709} \\ 
+
    49 & \cellcolor{red!10}bin & \cellcolor{red!10}recycling & \cellcolor{red!10}garbage & \cellcolor{red!10}recyclables & \cellcolor{red!10}recyclable & \cellcolor{red!10}bag & \mybar{1791} \\ 
@@
    13 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}subscriber & \cellcolor{red!10}desktop & \mybar{1092} \\
-   54 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}second & \cellcolor{red!10}unanimously & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \mybar{474} \\ 
     1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}infiltration & \cellcolor{red!10}discharge & \cellcolor{red!10}drainage & \cellcolor{red!10}drain & \mybar{516} \\ 
    38 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}teacher & \cellcolor{red!10}immigrant & \cellcolor{red!10}literacy & \mybar{714} \\ 
-   35 & \cellcolor{red!10}artist & \cellcolor{red!10}rouge & \cellcolor{red!10}baton & \cellcolor{red!10}art & \cellcolor{red!10}artwork & \cellcolor{red!10}exhibition & \mybar{1632} \\ 
    59 & \cellcolor{red!10}sampling & \cellcolor{red!10}sample & \cellcolor{red!10}analytical & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}toxicity & \mybar{1241} \\
-    3 & \cellcolor{red!10}portfolio & \cellcolor{red!10}yield & \cellcolor{red!10}jun & \cellcolor{red!10}maturity & \cellcolor{red!10}investment & \cellcolor{red!10}rating & \mybar{544} \\ 
    45 & \cellcolor{red!10}premise & \cellcolor{red!10}licensee & \cellcolor{red!10}violation & \cellcolor{red!10}license & \cellcolor{red!10}permit & \cellcolor{red!10}inspection & \mybar{509} \\ 
-    9 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \mybar{1469} \\ 
    60 & \cellcolor{red!10}exhaust & \cellcolor{red!10}fugitive & \cellcolor{red!10}aircraft & \cellcolor{red!10}airport & \cellcolor{red!10}aviation & \cellcolor{red!10}diesel & \mybar{731} \\ 
@@
     4 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}porch & \cellcolor{white}roof & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1108} \\
-   28 & \cellcolor{blue!10}census & \cellcolor{blue!10}population & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}percent & \cellcolor{blue!10}margin & \mybar{541} \\ 
-   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}deer & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}bulrush & \mybar{2522} \\ 
+
    15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \cellcolor{blue!10}discrimination & \mybar{1384} \\
-   20 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration & \mybar{325} \\
+
    14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}federal & \cellcolor{blue!10}recipient & \cellcolor{blue!10}compliance & \cellcolor{blue!10}entity & \mybar{205} \\
-   46 & \cellcolor{blue!10}variance & \cellcolor{blue!10}setback & \cellcolor{blue!10}plat & \cellcolor{blue!10}zoning & \cellcolor{blue!10}yard & \cellcolor{blue!10}fence & \mybar{289} \\ 
-   29 & \cellcolor{blue!10}learn & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}graffito & \cellcolor{blue!10}event & \cellcolor{blue!10}resident & \cellcolor{blue!10}online & \mybar{196} \\ 
+
    25 & \cellcolor{blue!10}cannabis & \cellcolor{blue!10}marijuana & \cellcolor{blue!10}senate & \cellcolor{blue!10}dispensary & \cellcolor{blue!10}ballot & \cellcolor{blue!10}cultivation & \mybar{1188} \\
-   22 & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}ongoing & \cellcolor{blue!10}goal & \cellcolor{blue!10}implementation & \cellcolor{blue!10}implement & \mybar{141} \\
-    6 & \cellcolor{blue!10}project & \cellcolor{blue!10}improvement & \cellcolor{blue!10}phase & \cellcolor{blue!10}replacement & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \mybar{174} \\
-   11 & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}beach & \cellcolor{blue!10}marina & \cellcolor{blue!10}coastal & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}salmon & \mybar{1069} \\ 
-   24 & \cellcolor{blue!10}attract & \cellcolor{blue!10}economy & \cellcolor{blue!10}workforce & \cellcolor{blue!10}innovation & \cellcolor{blue!10}sector & \cellcolor{blue!10}economic & \mybar{748} \\
+
    47 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{511} \\
-   39 & \cellcolor{blue!10}tab & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}mode & \cellcolor{blue!10}var & \cellcolor{blue!10}alt & \cellcolor{blue!10}false & \mybar{259} \\ 
-   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}corridor & \mybar{358} \\ 
+
    37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}accountability & \cellcolor{blue!10}oversight & \mybar{420} \\

### 2018-09-14 paper/manuscript.tex
moved Table 7
added tags for stm / web preprocessing

@@
 \subsection{Site to Text Conversion}
+{\bf WEB}
 For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
@@
 
+{\bf STM}
 The text documents are converted to UTF-8 and then stripped of dates, punctuation, numbers, and words connected by underscores.
@@
 
+{\bf STM}
 Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
@@
 
+\input{tables/tabBoilerplateIllustration.tex}
+
 \subsubsection{Analytical approach: Structural topic modeling}
@@
 %\end{figure}
-
-\input{tables/tabBoilerplateIllustration.tex}
 

### 2018-09-15 paper/TADA2018_Poster/stmTopWords60.tex
updates to the TADA poster, only PSU and NSF logo missing now

@@
   \hline
-   42 & \cellcolor{red!20}breastfeed & \cellcolor{red!20}vaccine & \cellcolor{red!20}infection & \cellcolor{red!20}symptom & \cellcolor{red!20}asthma & \cellcolor{red!20}mosquito & \mybar{2497} \\ 
-   17 & \cellcolor{red!20}alarm & \cellcolor{red!20}disaster & \cellcolor{red!20}fire & \cellcolor{red!20}rescue & \cellcolor{red!20}preparedness & \cellcolor{red!20}evacuation & \mybar{989} \\ 
+  \multicolumn{9}{c}{\textbf{Republican - Infrastructure}}\\
   53 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pipeline & \cellcolor{red!20}pump & \cellcolor{red!20}disinfection & \mybar{461} \\
-
   49 & \cellcolor{red!10}bin & \cellcolor{red!10}recycling & \cellcolor{red!10}garbage & \cellcolor{red!10}recyclables & \cellcolor{red!10}recyclable & \cellcolor{red!10}bag & \mybar{1791} \\ 
@@
    13 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}subscriber & \cellcolor{red!10}desktop & \mybar{1092} \\
-    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}infiltration & \cellcolor{red!10}discharge & \cellcolor{red!10}drainage & \cellcolor{red!10}drain & \mybar{516} \\ 
-   38 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}teacher & \cellcolor{red!10}immigrant & \cellcolor{red!10}literacy & \mybar{714} \\ 
-   59 & \cellcolor{red!10}sampling & \cellcolor{red!10}sample & \cellcolor{red!10}analytical & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}toxicity & \mybar{1241} \\
    45 & \cellcolor{red!10}premise & \cellcolor{red!10}licensee & \cellcolor{red!10}violation & \cellcolor{red!10}license & \cellcolor{red!10}permit & \cellcolor{red!10}inspection & \mybar{509} \\ 
    60 & \cellcolor{red!10}exhaust & \cellcolor{red!10}fugitive & \cellcolor{red!10}aircraft & \cellcolor{red!10}airport & \cellcolor{red!10}aviation & \cellcolor{red!10}diesel & \mybar{731} \\ 
+   %\multicolumn{9}{|c|}{Sets}\\
+   \multicolumn{9}{c}{\textbf{Republican - Natural Disasters}}\\
+   42 & \cellcolor{red!20}breastfeed & \cellcolor{red!20}vaccine & \cellcolor{red!20}infection & \cellcolor{red!20}symptom & \cellcolor{red!20}asthma & \cellcolor{red!20}mosquito & \mybar{2497} \\ 
+   17 & \cellcolor{red!20}alarm & \cellcolor{red!20}disaster & \cellcolor{red!20}fire & \cellcolor{red!20}rescue & \cellcolor{red!20}preparedness & \cellcolor{red!20}evacuation & \mybar{989} \\
+
+    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}infiltration & \cellcolor{red!10}discharge & \cellcolor{red!10}drainage & \cellcolor{red!10}drain & \mybar{516} \\ 
+   59 & \cellcolor{red!10}sampling & \cellcolor{red!10}sample & \cellcolor{red!10}analytical & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}toxicity & \mybar{1241} \\
+
    %30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
@@
    %41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 
-    4 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}porch & \cellcolor{white}roof & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1108} \\
-
-   15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \cellcolor{blue!10}discrimination & \mybar{1384} \\
-
-   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}federal & \cellcolor{blue!10}recipient & \cellcolor{blue!10}compliance & \cellcolor{blue!10}entity & \mybar{205} \\
-
-   25 & \cellcolor{blue!10}cannabis & \cellcolor{blue!10}marijuana & \cellcolor{blue!10}senate & \cellcolor{blue!10}dispensary & \cellcolor{blue!10}ballot & \cellcolor{blue!10}cultivation & \mybar{1188} \\
-
-   47 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{511} \\
-
+   \multicolumn{9}{c}{\textbf{Democratic - Governance \& Deliberation}}\\
    37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}accountability & \cellcolor{blue!10}oversight & \mybar{420} \\
-   21 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}affordability & \cellcolor{blue!10}landlord & \mybar{318} \\
    34 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}feedback & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}suggest & \cellcolor{blue!10}discussion & \mybar{289} \\
-   19 & \cellcolor{blue!10}debt & \cellcolor{blue!10}bond & \cellcolor{blue!10}governmental & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{251} \\
-   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}bicyclist & \mybar{574} \\ 
-   32 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}fund & \cellcolor{blue!20}million & \mybar{242} \\
    48 & \cellcolor{blue!20}absent & \cellcolor{blue!20}aye & \cellcolor{blue!20}khan & \cellcolor{blue!20}nay & \cellcolor{blue!20}berry & \cellcolor{blue!20}voting & \mybar{528} \\ 
    31 & \cellcolor{blue!20}chair & \cellcolor{blue!20}agenda & \cellcolor{blue!20}commission & \cellcolor{blue!20}speaker & \cellcolor{blue!20}chairperson & \cellcolor{blue!20}committee & \mybar{314} \\
+   \multicolumn{9}{c}{\textbf{Democratic - City Budget}}\\
+   19 & \cellcolor{blue!10}debt & \cellcolor{blue!10}bond & \cellcolor{blue!10}governmental & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{251} \\
+   32 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}fund & \cellcolor{blue!20}million & \mybar{242} \\
+   \multicolumn{9}{c}{\textbf{Democratic - Crime Control}}\\
    55 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}arrest & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}suspect & \cellcolor{blue!80}burglary & \mybar{1395} \\ 
+   \multicolumn{9}{c}{\textbf{Democratic - Miscellaneous}}\\
+   25 & \cellcolor{blue!10}cannabis & \cellcolor{blue!10}marijuana & \cellcolor{blue!10}senate & \cellcolor{blue!10}dispensary & \cellcolor{blue!10}ballot & \cellcolor{blue!10}cultivation & \mybar{1188} \\
+   15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \cellcolor{blue!10}discrimination & \mybar{1384} \\
+   47 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{511} \\
+   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}federal & \cellcolor{blue!10}recipient & \cellcolor{blue!10}compliance & \cellcolor{blue!10}entity & \mybar{205} \\ 
+   21 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}affordability & \cellcolor{blue!10}landlord & \mybar{318} \\
+   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}bicyclist & \mybar{574} \\
+
    \hline

### 2018-09-28 paper/manuscript.tex
addressing a comment, adding memo

@@
 The Erie, Pennsylvania website homepage presents an image of the Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
-In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies.
+In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies \citep{stanyer2008elected}.
 Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.

### 2018-09-28 paper/manuscript.tex
addressed two points

@@
 Like most e-government studies, however, this publication does not make any use of automated text analysis.
+Branching out of the topic of e-government service provision, \citet{mcnutt2010virtual} uses Canadian government websites to study how well-connected government websites are to non-profits and intergovernmental organizations in different public policy domains.
 %Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
@@
 
-The websites of politicians and their parties have also fallen under scholarly scrutiny.
+The websites of politicians and their parties have also been the object of research.
 Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
@@
 
-% BRUCE HERE
-
 We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
@@
 The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language.
+Government website contents can, and have been, used to study questions related representation, government transparency, and public policy priorities.
+The methods we develop can be used to scale up projects involving website data collection by automating the process.
 Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
@@
 Second, the pipeline we present can be used as a set of procedures to follow in gathering large-scale datasets of textual contents from other samples of governments.
+For example, the pipeline we have developed could be used to build comparative datasets of state or federal bureaucratic agencies.
 Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.

### 2018-09-28 paper/manuscript.tex
addressed point on sample selection

@@
 
-For data availability reasons, on which we elaborate below, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
-These states provide us with a sample that is well-balanced on a number of theoretically important indicators.
+For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
+The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
+Municipal elections in Indiana and Louisiana are partisan across the board,\footnote{In Indiana, this includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.} so our sample is primarily focused on these two states.
+Here, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
+New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see below for more detail on how we use this data).
+Finally, California and Texas contain a number of large cities, whose mayors are sufficiently well-known for their partisanship to be available.
+These six states also provide us with a sample that is well-balanced on a number of theoretically important indicators.
 One, each of the four geographic regions are represented with at least one state.

### 2018-09-28 paper/manuscript.tex
addressed the point on the type of city government (mayor/city manager/city council) by referring to a comparable paper where it makes no difference

@@
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
+\citep{Gerber2011a}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
 Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.

### 2018-09-28 paper/manuscript.tex
addressed the point on javascript by stating in a footnote that this problem, if anything, should lead to a more balanced sample

@@
 For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
-For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.
+For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites.
+However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
 

### 2018-09-28 paper/manuscript.tex
addressed a point about a sentence that looked like it might imply that there are scenarios where our method doesn't work by simply removing the sentence (see comment in revision memo for an explanation)

@@
 
-We then take several steps to pre-process the data as required for subsequent the subsequent analysis.
+We then take several steps to pre-process the data as required for the subsequent analysis.
 Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}.
-The steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
+%With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
 

### 2018-09-28 paper/manuscript.tex
addressed point on removal of rare words by adding a footnote

@@
 Since these pre-processing steps reduce documents which are largely unsuitable to only a few tokens (i.e., word occurrences), we also remove all remaining documents containing less than 50 tokens.
-Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive to our models while increasing their computational cost, we also discard any token types that occur in only one document.
+Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive\footnote{Topic models essentially do not pick up on extremely rare words, so their inclusion is a waste of computational resources.
+Removing them in this manner is also the default preprocessing choice in the \texttt{stm} package.} to our models while increasing their computational cost, we also discard any token types that occur in only one document.
 We also conduct lemmatization to reduce words to their basic form.

### 2018-09-28 paper/manuscript.tex
addressed the point about the admittedly flawed boilerplate illustration table by making a (hopefully) better one

@@
 Furthermore, the use of a local government website is associated with an individual's perspective on government.
-\citet{tolbert2006effects} finds that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
+\citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
 Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
@@
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\citep{Gerber2011a}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
+\citep{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
 Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
@@
 
-%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{Gerber2011a}.
+%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{gerber2011mayors}.
 However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).

### 2018-09-28 paper/tables/tabBoilerplateIllustration.tex
fixed the same issue for table 7 and removed the last few @markus from the manuscript
moved Table 7
addressed the point about the admittedly flawed boilerplate illustration table by making a (hopefully) better one

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Sat Jul 28 20:51:59 2018
+% Fri Sep 28 17:14:46 2018
 \begin{table}[ht]
@@
 \begingroup\small
-\begin{tabular}{lrr}
+\begin{tabular}{rl}
   \hline
-Line & Substantive & Boilerplate \\ 
+Boilerplate Probability & Text \\ 
   \hline
-have questions & 0.00 & 1.00 \\ 
-  stay connected & 0.00 & 1.00 \\ 
-  accident or injury & 0.00 & 1.00 \\ 
-  fire damaged buildings & 0.00 & 1.00 \\ 
-  gas connections & 0.00 & 1.00 \\ 
-  harboring of vagrants & 0.00 & 1.00 \\ 
-  roof system problem & 0.00 & 1.00 \\ 
-  violation plat note & 0.00 & 1.00 \\ 
-  violation setback & 0.00 & 1.00 \\ 
-  violation site plan & 0.00 & 1.00 \\ 
+1.00 & ri ng h i l \\ 
+  1.00 & any others \\ 
+  1.00 & premium for \\ 
+  1.00 & ra tr \\ 
+  1.00 & oa od \\ 
+  1.00 & te pos \\ 
+  1.00 & design to \\ 
+  1.00 & i pli \\ 
+  1.00 & wherever possible \\ 
+  1.00 & public nuisances \\ 
+  1.00 & prime movers \\ 
+  1.00 & of the offense \\ 
+  1.00 & d nonconformities \\ 
+  1.00 & yearshasexceeded costs \\ 
+  1.00 & f street \\ 
    \hline
@@
 \endgroup
-\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.} 
+\caption{Lines in the corpus of Anchorage, AK, with a probability of 1 of being classified as boilerplate.
+This table illustrates that lines which get classified as boilerplate largely consist of irrelevant nonsense which needs to be removed.}
+\label{tabBoilerplateIllustration}
 \end{table}

### 2018-09-28 boilerplateClassifierRF_Anchorage_AK_demonstration.R

@@ -113,17 +113,19 @@ predictedProbabilities <- predictedProbabilities[order(predictedProbabilities$Bo
 #Put the 10 examples with the highest probabilities in a table
 tabBoilerplateIllustration <- predictedProbabilities
 tabBoilerplateIllustration <- tabBoilerplateIllustration[!duplicated(tabBoilerplateIllustration$Text),]
-tabBoilerplateIllustration <- tabBoilerplateIllustration[1:10,]
-#uncomment the next line to also add the 10 lowest
-#tabBoilerplateIllustration <- rbind(tabBoilerplateIllustration, predictedProbabilities[(nrow(predictedProbabilities)-9):nrow(predictedProbabilities),])
-#switch around the variables so the text comes first
-tabBoilerplateIllustration <- data.frame(Line = substring(tabBoilerplateIllustration$Text, 1, 50),
-                                         Substantive = tabBoilerplateIllustration$Substantive,
-                                         Boilerplate = tabBoilerplateIllustration$Boilerplate)
+#the top ~14k are all probability = 1, so get only these
+tabBoilerplateIllustration <- tabBoilerplateIllustration[tabBoilerplateIllustration$Boilerplate==1,]
+#re-set the random seed so this is easily re-doable without having to re-do all of the above
+set.seed(1)
+#make a table with the lines and their probabilities
+#the probabilities are all 1, so just setting them like this here for ease of use
+tabBoilerplateIllustration <- data.frame(tabBoilerplateIllustration[sample(1:nrow(tabBoilerplateIllustration), size = 15),])
+tabBoilerplateIllustration <- subset(tabBoilerplateIllustration, select = -Substantive)
+names(tabBoilerplateIllustration)[1] <- "Boilerplate Probability"
 
 xtTabBoilerplateIllustration <- print(xtable(tabBoilerplateIllustration,
                                              digits = 2,
-                                             caption = "Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.",
+                                             caption = "Lines in the corpus of Anchorage, AK, with a probability of 1 of being classified as boilerplate. This table illustrates that lines which get classified as boilerplate largely consist of irrelevant nonsense which needs to be removed.",
                                              label = "tabBoilerplateIllustration"),
                                       size = "small",
                                       include.rownames = FALSE)

### 2018-09-28 paper/manuscript.tex
added a paragraph to the conclusion with a bit of bragging about the scaleability of our approach

@@
 The methods we develop can be used to scale up projects involving website data collection by automating the process.
+
+In terms of pure scope, our method is superior to the existing approaches.
+Manual content analysis (see, for example, \cite{Druckman2009}) relies on research assistants reading and evaluating websites, and therefore might struggle to provide a complete understanding of even individual websites, which often contain thousands of pages.
+Scrapers conventionally used in the social sciences (see, for example, \citealt{Cryer2017}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
+By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
+Consequently, our approach facilitates the kind of bulk data collection and analysis necessitated by an ever-growing web.
+
 Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.

### 2018-10-03 paper/tables/tabBoilerplateIllustration.tex
updated table 4; now shows the 20 most frequent lines, sorted according to their boilerplate probability

--- 2018-07-29 paper/tables/tabBoilerplateIllustration.tex
@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Sat Jul 28 20:51:59 2018
+% Tue Oct  2 23:59:06 2018
 \begin{table}[ht]
@@
   \hline
-Line & Substantive & Boilerplate \\ 
+Line & Boilerplate Probability & Line Frequency \\ 
   \hline
-have questions & 0.00 & 1.00 \\ 
-  stay connected & 0.00 & 1.00 \\ 
-  accident or injury & 0.00 & 1.00 \\ 
-  fire damaged buildings & 0.00 & 1.00 \\ 
-  gas connections & 0.00 & 1.00 \\ 
-  harboring of vagrants & 0.00 & 1.00 \\ 
-  roof system problem & 0.00 & 1.00 \\ 
-  violation plat note & 0.00 & 1.00 \\ 
-  violation setback & 0.00 & 1.00 \\ 
-  violation site plan & 0.00 & 1.00 \\ 
+elections & 0.92 & 4895 \\ 
+  assembly & 0.91 & 6996 \\ 
+  library & 0.91 & 4888 \\ 
+  ombudsman & 0.90 & 2930 \\ 
+  of & 0.90 & 2767 \\ 
+  police department & 0.90 & 5101 \\ 
+  office & 0.90 & 2926 \\ 
+  fire department & 0.90 & 5047 \\ 
+  municipal clerk & 0.89 & 3440 \\ 
+  parks and recreation & 0.89 & 5397 \\ 
+  assembly memorandum no & 0.89 & 4827 \\ 
+  boards and commissions & 0.89 & 3012 \\ 
+  municipality of anchorage & 0.89 & 3357 \\ 
+   & 0.88 & 461487 \\ 
+  anchorage alaska page & 0.88 & 5684 \\ 
+  resolution no ar & 0.88 & 4627 \\ 
+  a assembly memorandum no & 0.86 & 4579 \\ 
+  health and human services & 0.84 & 2863 \\ 
+  regular assembly meeting page & 0.81 & 3080 \\ 
+  economic and community development & 0.74 & 2891 \\ 
    \hline
@@
 \endgroup
-\caption{Lines (or the first 50 characters of a line) in the corpus of Anchorage, AK, with the 10 highest probabilities of being classified as boilerplate.} 
+\caption{The 20 most frequent lines in the corpus of Anchorage, AK, sorted according to the probability with which the classifier identifies them as boilerplate.
+This table illustrates that the boilerplate classifier correctly flags and removes interpretable but unimportant content which would otherwise have a disproportionate impact on the topic model.}
+\label{tabBoilerplateIllustration}
 \end{table}

### 2018-10-03 paper/manuscript.tex
revising re WEB/STM

@@
 In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
-In this methodological pipeline, we address two methodological challenges.
+In this pipeline, we address two methodological challenges.
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
@@
 The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
+Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
+We will clarify this distinction as we describe steps in our pipeline.
 
 \subsection{Site to Text Conversion}
-{\bf WEB}
+The format of a file has a major impact on whether and how textual data can be extracted from a document.
+For all text analysis projects, researchers need to consider file formats.
 For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
@@
 Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}.
+The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
 %With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
 
-{\bf STM}
-The text documents are converted to UTF-8 and then stripped of dates, punctuation, numbers, and words connected by underscores.
+The text documents are converted to UTF-8 character encoding and then stripped of dates, punctuation, numbers, and words connected by underscores.
 At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
@@
 a menu with certain terms repeated on every site of the domain), and not the substantive features of their contents.
+Boilerplate removal is a useful step in many forms of text analysis, as the analysis is focused in on text that varies above and beyond a standard template for textual content.
 Our solution to this problem is described in more detail in Section \ref{boilerplate}.
 
-{\bf STM}
-Preprocessing further includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
+The last round of preprocessing is intended to remove everything from the file that is not an English word.
+This step is tailored to our intention to use the text for topic modeling.
+The final preprocessing round includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
 Furthermore, some documents contain gibberish, often as a result of faulty or impartial optical character recognition applied to text that was produced through a non-machine-readable medium.

### 2018-10-03 paper/manuscript.tex
fixed a few spelling errors and cited the gerber & hopkins paper in the introduction

@@
 In our illustrative application, we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
-A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
+A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{gerber2011mayors,de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
 Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public \citep{sharfstein2017science,kirby2017trump,duarte2017deniable}.
@@
 
-Members of the public visit municipal government websites for a wide variety of purposes \citet{sandoval2012government}, and with significant regularity.
+Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
 In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
@@
 Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
-The use of a web drive-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
+The use of a web driver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
 A web driver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
@@
 The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
-The dataset is has a relative party balance, with variation in each state.
+The dataset has a relative party balance, with variation in each state.
 
@@
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\citep{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
+\cite{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
 Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.

### 2018-10-05 paper/manuscript.tex
cut down the abstract to 186 words

@@
 
-A local government's website is arguably the most important general source of information about policies and procedures for residents and other community stakeholders.
-Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science.
-Existing research has relied on manual methods of website data collection and processing.
-However, reliance on manual collection and processing limits the scale and scope of website content analysis.
-We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques.
-First, for the acquisition of website data, we cover approaches to automated scraping methods.
-Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias.
-We propose a new method for dealing with the types of duplicated and boilerplate contents that are commonly found in government websites.
+A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars.
+Existing research in public administration, public policy, and political science has relied on manual methods of website data collection and processing, limiting the scale and scope of website content analysis.
+We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content.
+Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information through a new method of boilerplate removal.
 We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
 We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
-Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about the provision of basic utilities and services such as water, electricity, garbage removal and fire safety; and information on municipal ordinances and policies.
+Using a structural topic model, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity and fire safety.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.

### 2018-10-06 paper/manuscript.tex
went through abstract

@@
 A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars.
-Existing research in public administration, public policy, and political science has relied on manual methods of website data collection and processing, limiting the scale and scope of website content analysis.
+Existing research in public administration, public policy, and political science has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
 We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content.

### 2018-10-06 paper/manuscript.tex
added author contact information

@@
 
-\author{ Markus Neumann \and Fridolin Linder \and Bruce Desmarais} \date{\today}
+\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+Email: mvn5218@psu.edu} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA.
+Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+Email: bdesmarais@psu.edu}} \date{\today}
 

### 2018-10-06 paper/manuscript.tex
listed myself as corresponding author for now

@@
 \author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
-Email: mvn5218@psu.edu} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA.
+Email: mvn5218@psu.edu.
+Corresponding author.} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA.
 Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.

### 2018-12-16 paper/presentation/stmTopWordsINDem.tex
new structure

--- 2017-12-18 paper/presentation/stmTopWordsINDem.tex
@@
-% latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Nov 13 15:36:58 2017
+% latex table generated in R 3.4.3 by xtable 1.8-2 package
+% Tue Dec 26 20:59:22 2017
 \begin{table}[ht]
 \centering
+\scriptsize
 \begin{tabular}{llllll}
   \hline
--0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 \\ 
+-0.027 & -0.022 & -0.016 & -0.011 & -0.011 & -0.01 \\ 
   \hline
-fort & propos & said & prosecutor & digest & fund \\ 
-  citi & author & ask & charg & introduc & grant \\ 
-  ordin & district & state & feloni & author & budget \\ 
-  approv & street & will & counti & counti & counti \\ 
-  purchas & public & chair & case & appoint & state \\ 
-  depart & control & propos & crime & board & feder \\ 
-  properti & amend & year & crimin & approv & depart \\ 
-  will & intersect & move & offic & district & appropri \\ 
-  resolut & counti & need & victim & fund & increas  \\ 
-  contract & committe & council & sentenc & street & agenc \\ 
+city & school & downtown & city & \cellcolor{blue!25}trash & \cellcolor{blue!25}housing \\ 
+  ordinance & community & business & department & city & property \\ 
+  approve & program & project & mayor & \cellcolor{blue!25}waste & program \\ 
+  resolution & student & city & police & day & \cellcolor{blue!25}fund \\ 
+  property & \cellcolor{blue!25}education & \cellcolor{blue!25}development & officer & \cellcolor{blue!25}recycle & home \\ 
+  purchase & \cellcolor{blue!25}university & new & public & street & city \\ 
+  area & national & center & citizen & collection & project \\ 
+  department & award & \cellcolor{blue!25}economic & work & resident & neighborhood \\ 
+  contract & high & company & safety & \cellcolor{blue!25}recycling & \cellcolor{blue!25}grant \\ 
+  service & year & community & resident & snow & unit \\ 
    \hline
 \end{tabular}
-%\caption{Top Democratic topics and words (Indiana), according to STM. 
+\caption{Top Democratic topics and words}%\caption{Top Democratic topics and words (Indiana), according to STM. 
 %The words are the top words for the most Democratic/Republican topic, determined

### 2018-12-16 paper/presentation/stmTopWordsINRep.tex
new structure

--- 2017-12-18 paper/presentation/stmTopWordsINRep.tex
@@
-% latex table generated in R 3.4.2 by xtable 1.8-2 package
-% Mon Nov 13 15:36:58 2017
+% latex table generated in R 3.4.3 by xtable 1.8-2 package
+% Tue Dec 26 20:59:22 2017
 \begin{table}[ht]
 \centering
-\begin{tabular}{llllll}
+\scriptsize
+\begin{tabular}{lllllll}
   \hline
-0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 \\ 
+ 0.021 & 0.019 & 0.017 & 0.017 & 0.013 & 0.012 \\ 
   \hline
-motion & plan & inc & request & council & traffic \\ 
-  second & zone & electr & board & citi & amp \\ 
-  made & applic & build & member & ordin & vehicl \\ 
-  approv & properti & construct & servic & common & stop \\ 
-  mayor & approv & home & street & councilor & sign \\ 
-  present & sign & street & approv & amend & road \\ 
-  state & site & meridian & purchas & resolut & block \\ 
-  will & locat & servic & citi & adopt & signal \\ 
-  citi & commiss & west & move & wherea & street \\ 
-  council & file & main & good & approv & driver \\ 
+ foot & team & ave & request & amp & \cellcolor{red!25}building \\ 
+   \cellcolor{red!25}sign & game & inc & board &\cellcolor{red!25} traffic & historic \\ 
+   use & play & cross & member & stop & \cellcolor{red!25}build \\ 
+   lot & league & creek & service & vehicle & material \\ 
+   \cellcolor{red!25}building & camp & \cellcolor{red!25}construction & \cellcolor{red!25}street & block & preservation \\ 
+   \cellcolor{red!25}zone & class & blvd & approve & sign & \cellcolor{red!25}wall \\ 
+   area & age & park & city &  \cellcolor{red!25}airport & \cellcolor{red!25}roof \\ 
+   district & must & lake & purchase & ave & window \\ 
+   \cellcolor{red!25}parking & child & hill & move & theft & \cellcolor{red!25}floor \\ 
+   residential & participant & ridge & good & signal & new \\ 
    \hline
 \end{tabular}
-%\caption{Top Republican topics and words (Indiana), according to STM. 
+\caption{Top Republican topics and words}%, according to STM. 
 %The words are the top words for the most Democratic/Republican topic, determined

### 2018-12-16 paper/presentation/stmTopWordsLARep.tex
new structure

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Dec 26 15:50:18 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
0.071 & 0.054 & 0.054 & 0.034 & 0.033 & 0.024 & 0.023 & 0.02 \\ 
  \hline
event & ordinance & water & street & say & city & city & mayor \\ 
  information & department & emergency & traffic & can & business & meeting & city \\ 
  show & summary & city & parking & make & new & council & parish \\ 
  park & amount & resident & lane & get & mayor & commission & town \\ 
  music & bid & storm & project & take & development & plan & office \\ 
  food & city & weather & work & people & economic & member & hall \\ 
  visit & public & waste & bike & work & million & public & contact \\ 
  weekend & police & system & downtown & need & continue & board & day \\ 
  festival & approve & power & public & city & work & committee & official \\ 
  begin & inc & service & bicycle & help & local & planning & state \\ 
   \hline
\end{tabular}
\caption{Top Republican topics and words (Louisiana), according to STM. 
The words are the top words for the most Democratic/Republican topic, determined
by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMLARep}
\end{table}

### 2018-12-16 paper/tables/stmTopWordsINDem.tex
new structure

@@
   \hline
--0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 & -0.011 & -0.011 \\ 
+-0.027 & -0.022 & -0.016 & -0.015 & -0.012 & -0.011 & -0.011 & -0.01 \\ 
   \hline
-fort & propos & said & prosecutor & digest & fund & servic & plan \\ 
-  citi & author & ask & charg & introduc & grant & inform & develop \\ 
-  ordin & district & state & feloni & author & budget & board & communiti \\ 
-  approv & street & will & counti & counti & counti & applic & citi \\ 
-  purchas & public & chair & case & appoint & state & project & neighborhood \\ 
-  depart & control & propos & crime & board & feder & approv & program \\ 
-  properti & amend & year & crimin & approv & depart & technolog & provid \\ 
-  will & intersect & move & offic & district & appropri & system & public \\ 
-  resolut & counti & need & victim & fund & increas & manag & resourc \\ 
-  contract & committe & council & sentenc & street & agenc & agreement & area \\ 
+city & school & downtown & service & contract & city & trash & housing \\ 
+  ordinance & community & business & division & bid & department & city & property \\ 
+  approve & program & project & provide & contractor & mayor & waste & program \\ 
+  resolution & student & city & city & city & police & day & fund \\ 
+  property & education & development & management & agreement & officer & recycle & home \\ 
+  purchase & university & new & public & work & public & street & city \\ 
+  area & national & center & department & service & citizen & collection & project \\ 
+  department & award & economic & program & department & work & resident & neighborhood \\ 
+  contract & high & company & include & bidder & safety & recycling & grant \\ 
+  service & year & community & office & move & resident & snow & unit \\ 
    \hline

### 2018-12-16 paper/tables/stmTopWordsIN_LADem.tex
new structure

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Mar 20 09:25:03 2018
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{llllllll}
  \hline
-0.036 & -0.024 & -0.024 & -0.012 & -0.009 & -0.008 & -0.008 & -0.007 \\ 
  \hline
provide & applicant & community & council & department & shall & business & day \\ 
  otherwise & owner & city & councilman & division & city & development & contract \\ 
  city & application & neighborhood & rise & service & contractor & economic & total \\ 
  respect & new & public & mayor & police & agreement & downtown & payment \\ 
  authorize & building & mayor & city & city & person & job & invoice \\ 
  ordinance & exist & work & state & provide & provide & new & process \\ 
  thereto & proposal & program & grant & public & upon & city & department \\ 
  councilman & retention & resident & street & management & term & project & approval \\ 
  district & per & effort & fund & operation & provision & center & complete \\ 
  property & build & new & discussion & office & time & service & procurement \\ 
   \hline
\end{tabular}
\endgroup
\caption{Republican} 
\label{tabSTMIN_LADem}
\end{table}

### 2018-12-16 paper/tables/stmTopWordsIN_LARep.tex
new structure

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Tue Mar 20 09:25:03 2018
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{llllllll}
  \hline
0.019 & 0.018 & 0.016 & 0.015 & 0.015 & 0.013 & 0.012 & 0.01 \\ 
  \hline
library & park & motion & inc & proposal & say & lot & city \\ 
  stream & recreation & second & cross & digest & ask & district & information \\ 
  length & pool & make & construction & fund & state & use & day \\ 
  obj & facility & present & drive & grant & proposal & foot & contact \\ 
  pdf & center & approve & street & county & make & zone & can \\ 
  type & program & state & creek & authorize & get & street & resident \\ 
  branch & golf & minute & park & introduce & can & square & please \\ 
  unknown & playground & meeting & hill & district & need & area & department \\ 
  flag & trail & pass & ave & public & go & building & call \\ 
  image & play & mayor & oak & department & work & parking & amp \\ 
   \hline
\end{tabular}
\endgroup
\caption{Democratic} 
\label{tabSTMIN_LARep}
\end{table}

### 2018-12-16 00_scrapeCovariates/censusAPI.R

@@ -1,0 +1,100 @@
+#use the census API to get the covariates needed for the stm
+
+install.packages("censusapi")
+library(censusapi)
+
+# Add key to .Renviron
+Sys.setenv(CENSUS_KEY="a7bf6f7b2b4796a05a13827bfe3d5c1b7dc78405")
+# Check to see that the expected key is output in your R console
+Sys.getenv("CENSUS_KEY")
+
+varsbds <- listCensusMetadata(name="acs5", vintage = 2015, type = "v")
+
+#Variables:
+
+#B01001_001E -- total population
+#B01001_002E -- male
+#B01001A_001E -- white
+#B01001B_001E -- African American
+#B03001_001E -- Hispanic or Latino
+
+#B07001. Geographical Mobility in the Past Year
+#B07001_017E -- Same house 1 year ago
+#B07001_033E -- Moved within same county
+#B07001_065E -- Moved from different state
+
+#B08128. MEANS OF TRANSPORTATION TO WORK
+#B08128_031E -- Public transportation (excluding taxicab)
+
+#B10054. Lang and Ability to Speak Eng
+#B10054_002E -- Speak only English
+
+#B17001F. POVERTY STATUS IN THE PAST 12 MONTH
+#B17001F_002E -- Income in the past 12 months below poverty level
+
+#B19013. Median Household Income in the Past 12 Months
+#B19013_001E -- Median household income in the past 12 months (in 2015 Inflation-adjusted dollars)
+
+#B15003. Educational Attainment for the Population over 25 years
+#B15003_002E -- No schooling completed
+#B15003_017E -- Regular high school diploma
+#B15003_018E -- GED or alternative credential
+#B15003_022E -- Bachelor's degree
+#B15003_023E -- Master's degree
+#B15003_025E -- Doctorate degree
+
+#B25077. Median Value (Dollars) for Owner-Occupied Housing Units
+#B25077_001E -- Median value (dollars)
+
+variables <- c("NAME", "B01001_001E", "B01001_002E", "B01001A_001E", "B01001B_001E", "B03001_001E",
+               "B07001_017E", "B07001_033E", "B07001_033E", "B07001_065E",
+               "B08128_031E", "B10054_002E", "B17001F_002E", "B19013_001E",
[…]

### 2018-12-16 00_scrapeCovariates/cityCoordinates.R

@@ -1,0 +1,30 @@
+#scrape the GPS coordiantes for each city from Wikipedia
+
+library("rvest")
+library("stringr")
+
+load("rfiles/allURLs.rdata")
+
+extractCoords <- function(wikipage){
+  link <- str_c("https://en.wikipedia.org", wikipage)
+  citylink <- read_html(link) %>% html_nodes("#coordinates span") %>% html_text()
+  if(identical(citylink, character(0))){
+    citylink <- NA #NA if no link
+  }
+  citylink <- citylink[[1]] #in some cases, it returns the link twice, this takes care of that
+  return(citylink)
+}
+websiteUrls$coords <- sapply(websiteUrls$wiki_link, extractCoords)
+
+coords <- str_split_fixed(websiteUrls$coords, "/", 3)[,3] %>% str_split_fixed(";", 2)
+websiteUrls$latitude <- str_trim(coords[,1])
+websiteUrls$longitude <- str_trim(coords[,2])
+
+#change to numeric
+websiteUrls$latitude <- as.numeric(websiteUrls$latitude)
+#fix an error where a coordinate contained "(Virginia Beach)"
+websiteUrls$longitude <- gsub("\\s\\((.*?)\\)", "", websiteUrls$longitude)
+websiteUrls$longitude <- gsub("[^0-9\\-\\.]", "", websiteUrls$longitude)
+websiteUrls$longitude <- as.numeric(as.character(websiteUrls$longitude))
+
+save(websiteUrls, file = "rfiles/allURLs.rdata")

### 2018-12-16 03_correctFiletypeErrors/01_correctFiletype.R

@@ -1,0 +1,94 @@
+#devtools::install_github("hrbrmstr/wand")
+
+library(wand)
+
+path = "/home/mneumann/hd2/govWebsites/"
+f <- list.files(path, recursive = T) #create a list of all files in all subdirectories
+#ignore files whose names can't be read
+f <- f[!stringr::str_detect(f, "[^\\x00-\\x7F]")]
+#absolute file paths
+fAbs <- paste(path, f, sep = "")
+
+#determine file type with the wand pagacke (relying on libmagic)
+#and check how long it takes
+start.time <- Sys.time()
+magicResults <- incant(fAbs)
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+print(time.taken)
+
+save(magicResults, file = "rfiles/trueFileTypes.rdata")
+load("rfiles/trueFileTypes.rdata")
+
+library(tools)
+
+magicResults$ext <- file_ext(magicResults$file)
+magicResults$extensions <- as.character(magicResults$extensions)
+#magicResults$inferredExt[magicResults$extensions=="pdf"] <- "pdf"
+#magicResults$inferredExt[magicResults$extensions=="docx"] <- "docx"
+#magicResults$inferredExt[magicResults$extensions=="c(\\\"ttc\\\", \\\"ttf\\\")"] <- "ttf"
+
+#magicresultsDoc <- magicResults[magicResults$extensions=="c(\\\"doc\\\", \\\"dot\\\")",]
+
+library(stringr)
+#magicResults$mime <- str_replace(magicResults$mime_type, "^(.+?)/", "")
+
+#changes that need to be made:
+#files that currently have a pdf/txt/html/doc/docx extension and shouldn't have one
+#files that currently have a no extension and should have a pdf/txt/html/doc/docx
+#files that have the wrong pdf/txt/html/doc/docx extension
+
+magicResults$extensions <- str_replace_all(magicResults$extensions, "\"", "")
+magicResults$extensions <- str_replace_all(magicResults$extensions, "c\\(", "")
+magicResults$extensions <- str_replace_all(magicResults$extensions, "\\)", "")
+
+
+magicResults$extensions[magicResults$extensions=="ai, eps, ps"] <- "ps"
+magicResults$extensions[magicResults$extensions=="asf, asx"] <- "asf"
+magicResults$extensions[magicResults$extensions=="asm, s"] <- "asm"
[…]

### 2018-12-16 04_parseText/01_preprocessingPart1.R

@@ -1,0 +1,129 @@
+# This document creates a list of all the files that were downloaded with wget
+# and then merges it with the city metadata
+# the resultant citydocs.rdata file should be used as input for convertToText.R
+# the resultant city-specific rdata files will then further be processed in preprocessingPart2.R
+
+#setwd("govWebsites")
+
+library('stringr')
+library('urltools') #used toget the domain from each url
+library('tools')
+
+# ---- #
+
+#get metadata
+load("rfiles/allURLs.rdata")
+
+#get URLs verified through Python Selenium
+websiteUrls$urls_verified <- readLines("websites/urls_verified.txt")
+#get the domain from each url
+websiteUrls$urls_verified <- url_parse(websiteUrls$urls_verified)$domain
+#make some corrections
+websiteUrls$urls_verified[websiteUrls$urls_verified=="www.atticaonline.com"] <- "attica-in.gov"
+websiteUrls$urls_verified[websiteUrls$urls_verified=="www.unioncity-in.gov"] <- "unioncity-in.com"
+
+# ---- #
+
+path <- "/home/mneumann/hd2/govWebsites"
+
+f <- list.files(path, recursive = T) #create a list of all files in all subdirectories
+f <- f[!stringr::str_detect(f, "[^\\x00-\\x7F]")]
+
+#file types
+ext <- file_ext(f) #get file extension
+folder <- str_split(f, "\\/(?=[^\\/]+$)", simplify = T)[,1]
+filename <- str_split(f, "\\/(?=[^\\/]+$)", simplify = T)[,2]
+
+#store objects in a data frame
+d <- data.frame(path = str_c(path, f, sep = "/"), 
+                folder = str_c(path, folder, sep = "/"),
+                filename,
+                ext,
+                stringsAsFactors = F)
+d <- subset(d, filename != "")
+
+#new files
+
+#only txt, pdf, html, doc, or docx
+d <- d[d$ext %in% c('txt', 'pdf', 'html', 'doc', 'docx'),]
+
+#remove some files that crash readtext
+#everything in this folder causes some problems
+d <- d[-which(str_detect(d$path, "/home/mneumann/hd2/govWebsites/bloomington.in.gov/trades/parcel/(.*?).pdf")),]
+
+d$path <- str_replace_all(d$path, "\\[", "\\\\[")
[…]

### 2018-12-16 05_boilerplateRemoval/03_testBoilerplateClassifier.R

@@ -1,0 +1,134 @@
+#Purpose of the script: 
+#Illustrate the effectiveness of the classifier by:
+#1. Comparing the lines left over after it is applied to every line, from before
+#2. Creating a table of the lines with the highest and lowest probabilities of being boilerplate
+#Both are done on the corpus of Anchorage, AK.
+
+library('stringr')
+library('caret')
+library('ranger')
+library('quanteda')
+library('xtable')
+
+set.seed(1)
+
+# ----
+
+f <- list.files("rfiles/city_chunks_unprocessed", full.names = T)
+f_file <- list.files("rfiles/city_chunks_unprocessed")
+
+#load the data for Anchroage
+city = 1
+  
+load(f[city])
+a <- a[!a$text=="",]
+a <- a[!a$text==" ",]
+
+load(file = paste("rfiles/city_chunks_part1_processed/", f_file[city], sep = ""))
+
+#Preprocessing until the point where the classifier comes in
+tt3 <- unlist(tt2)
+
+#create the new X'
+testData <- data.frame(text = tt3, stringsAsFactors = F)
+testDataTextTable <- data.frame(table(testData$text), stringsAsFactors = F)
+testDataTextTable$Var1 <- as.character(testDataTextTable$Var1)
+testData$lineID <- 1:nrow(testData)
+testData <- merge(testData, testDataTextTable, by.x = "text", by.y = "Var1", all.x = T)
+rm(testDataTextTable, tt3)
+testData <- testData[order(testData$lineID),]
+
+#create the variables necessary to create the variables used in the classifier
+docLengths <- as.numeric(unlist(lapply(tt2, length)))
+testData$docID <- rep(1:length(tt2), docLengths)
+testData$docLengths <- rep(docLengths, docLengths)
+testData$linePosition <- unlist(sapply(docLengths, seq, from = 1))
+
+#calculate distance to document midpoint
+docMidpoint <- testData$docLengths/2
+docLineMidpointDist <- abs(docMidpoint-testData$linePosition)
+docLineMidpointDistRelative <- docLineMidpointDist/testData$docLengths
+testData$medianDocMidDist <- docLineMidpointDistRelative
+rm(docMidpoint,docLineMidpointDist,docLineMidpointDistRelative)
+
+#calculate nunber of characters
+testData$nchars <- nchar(testData$text)
+#count the number of tokens
+tks <- tokens(testData$text)
+testData$nwords <- unlist(lapply(tks, length))
+rm(tks)
+
[…]

### 2018-12-16 06_preprocessing/02_preprocessingPart2.R

@@ -1,0 +1,28 @@
+# -------------------
+# PREPROCESSING
+# iterate over cities
+# -------------------
+
+library('stringr')
+library('caret')
+library('ranger')
+library('quanteda')
+
+set.seed(1)
+
+# ----
+
+f <- list.files("rfiles/city_chunks_unprocessed", full.names = T)
+f_file <- list.files("rfiles/city_chunks_unprocessed")
+
+#loop over cities
+for(city in 1:length(f)){
+  
+  load(f[city])
+  a <- a[!a$text=="",]
+  a <- a[!a$text==" ",]
+  
+  load(file = paste("rfiles/city_chunks_part1_processed/", f_file[city], sep = ""))
+  source("preprocessCityPart2.R")
+  save(a, file = paste("rfiles/city_chunks_part2_classifier_processed/", f_file[city], sep = ""))
+}

### 2018-12-16 06_preprocessing/04_preprocessing_merge.R

@@ -1,0 +1,26 @@
+# -------------------
+# PREPROCESSING
+# iterate over cities
+# merge the text with the covariates
+# -------------------
+
+library('stringr')
+
+# ----
+
+f <- list.files("rfiles/city_chunks_part3_lemmatized", full.names = T)
+f_file <- list.files("rfiles/city_chunks_part3_lemmatized")
+
+d <- list()
+for(city in 1:length(f)){
+  
+  load(f[city])
+  a$city <- str_replace(f_file[city], ".rdata", "") 
+  d[[city]] <- a
+  
+}
+
+d <- do.call(rbind, d)
+
+
+save(d, file = "rfiles/allDocuments.rdata")

### 2018-12-16 06_preprocessing/preprocessCityPart1.R

@@ -1,0 +1,120 @@
+library('quanteda')
+
+#tokenize, removing numbers, punctuations, symbols, twitter symbols, hyphens and urls
+# we do NOT remove separators, because we need the \n newline indicators
+# (note that this is because what = "word" and remove_punct = T, which renders
+# remove_separators = F redundant; it is here only for clarity)
+tt = tokens(a$text, what = "word",
+       remove_numbers = T, remove_punct = T,
+       remove_symbols = T, remove_separators = F,
+       remove_twitter = T, remove_hyphens = T, remove_url = T)
+
+#since we didn't remove separators, remove spaces
+tt = tokens_select(tt, " ", "remove")
+
+#remove date-related words
+date_words <- c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
+date_words <- c(date_words, "January","February","March","April","May","June","July","August","September","October","November","December")
+date_words <- c(date_words, "Mon","Tue","Wed","Thu","Fri","Sat","Sun")
+date_words <- c(date_words, "am", "pm")
+date_words <- c(date_words, tolower(date_words))
+tt = tokens_select(tt, date_words, "remove")
+rm(date_words)
+
+#removing words containing underscores
+tt = tokens_select(tt, "\\w*_\\w*", "remove", valuetype = "regex")
+
+#remove all remaining non-character tokens
+tt = tokens_select(tt, "[^A-Za-z\n]", "remove", valuetype = "regex")
+
+#set everything to lowercase
+tt = tokens_tolower(tt)
+
+## Duplicate line removal
+
+#convert from tokens object to list of character vectors
+tt2 <- lapply(tt, paste, collapse = " ")
+#split on newlines; creates nested list (unnecessarily)
+tt2 <- lapply(tt2, str_split, "\n")
+#unnest - back to a list of character vectors
+tt2 <- lapply(tt2, unlist)
+#remove empty spaces at the ends
+tt2 <- lapply(tt2, str_trim)
+
+#concatenate all lines of a city's documents
+linesRemove <- as.character(unlist(tt2))
+#create table
+linesRemove <- table(linesRemove)
+#get the lines that occur more than duplicateLinesThreshold times
+duplicateLinesThreshold <- 10
+linesRemove <- linesRemove[linesRemove>duplicateLinesThreshold]
+#linesRemove <- sort(linesRemove, decreasing = T)
[…]

### 2018-12-16 06_preprocessing/preprocessCityPart2.R

@@ -1,0 +1,121 @@
+set.seed(1)
+
+tt3 <- unlist(tt2)
+
+#create the new X'
+testData <- data.frame(text = tt3, stringsAsFactors = F)
+testDataTextTable <- data.frame(table(testData$text), stringsAsFactors = F)
+testDataTextTable$Var1 <- as.character(testDataTextTable$Var1)
+testData$lineID <- 1:nrow(testData)
+testData <- merge(testData, testDataTextTable, by.x = "text", by.y = "Var1", all.x = T)
+rm(testDataTextTable, tt3)
+testData <- testData[order(testData$lineID),]
+
+#create the variables necessary to create the variables used in the classifier
+docLengths <- as.numeric(unlist(lapply(tt2, length)))
+testData$docID <- rep(1:length(tt2), docLengths)
+testData$docLengths <- rep(docLengths, docLengths)
+testData$linePosition <- unlist(sapply(docLengths, seq, from = 1))
+
+#calculate distance to document midpoint
+docMidpoint <- testData$docLengths/2
+docLineMidpointDist <- abs(docMidpoint-testData$linePosition)
+docLineMidpointDistRelative <- docLineMidpointDist/testData$docLengths
+testData$medianDocMidDist <- docLineMidpointDistRelative
+rm(docMidpoint,docLineMidpointDist,docLineMidpointDistRelative)
+
+#calculate nunber of characters
+testData$nchars <- nchar(testData$text)
+#count the number of tokens
+tks <- tokens(testData$text)
+testData$nwords <- unlist(lapply(tks, length))
+rm(tks)
+
+#rename variables so they match up with those in the random forest weights
+names(testData)[names(testData)=="Freq"] <- "freq"
+
+#load the weights from the random forest
+load('rfiles/boilerplateClassifierWeights.rdata')
+
+if(nrow(testData)<=10000){
+  testData$predictedClass <- predict(mRF, testData)
+}else{
+  chunks <- seq(0,nrow(testData), 10000)
+  chunks <- c(chunks, nrow(testData))
+  
+  #start_time <- Sys.time()
+  testResults <- list()
+  for(i in 1:(length(chunks)-1)){
+    testData2 <- testData[(chunks[i]+1):chunks[i+1],]
+    testResults[[i]] <- predict(mRF, testData2)
+  }
+  #end_time <- Sys.time()
+  #end_time - start_time
+  testResults <- unlist(testResults)
+  testData$predictedClass <- testResults
+}
+
[…]

### 2018-12-16 07_topicModel/01_stm_estimation.R

@@ -1,0 +1,46 @@
+library('quanteda')
+library('stm')
+library('tidyr')
+library('ggplot2')
+library('scales')
+library('stringr')
+
+set.seed(1)
+
+load(file = "./rfiles/websiteMetadata.rdata")
+load(file = "rfiles/allDocuments.rdata")
+
+d <- merge(d, websiteMeta, by.x = "city", by.y = "State_City")
+d <- subset(d, State %in% c("Indiana", "Louisiana", "New York", "California", "Washington", "Texas"))
+
+d$doc_id <- paste("doc", 1:nrow(d))
+crps <- corpus(d)
+dtm <- dfm(crps)
+
+#Number of topics
+numtopics <- 60
+
+#Train the model
+stmFit <- stm(documents = dtm,
+              K = numtopics, 
+              prevalence =~ party + State + B01001_001E + B19013_001E,
+              max.em.its = 9999,
+              init.type = "Spectral")
+
+#save.image("rfiles/stmSession2, _Party.rdata")
+save.image(paste("rfiles/stmSession_model_", numtopics, ".rdata", sep = ""))
+
+#set seed again in case the script was restarted from here
+set.seed(1)
+
+#Estimate effects from the model outputs
+sims <- 1000
+
+#re-estimate the effects, this time do 1000 draws from the posterior
+prep <- estimateEffect(formula = 1:numtopics ~ party + State + B01001_001E + B19013_001E, 
+                       stmobj = stmFit,
+                       meta = d, 
+                       uncertainty = "Global",
+                       nsims = sims)
+
+save.image(paste("rfiles/stmSession_sim_", numtopics, ".rdata", sep = ""))

### 2018-12-16 07_topicModel/02_stm_results.R

@@ -1,0 +1,93 @@
+library(stm)
+
+set.seed(1)
+
+load("rfiles/stmSession_sim_60.rdata")
+
+#make a dataframe to store the results in
+df <- data.frame(coef = rep(0, numtopics), sig = rep(FALSE, numtopics),
+                 lower = rep(0, numtopics), upper = rep(0, numtopics),
+                 topic = 1:numtopics)
+
+conf_level <- 1 #in percent
+conf_level <- conf_level/100 #as a fraction
+conf_level <- conf_level/2 #two-sided
+
+conf_lower <- 0 + conf_level
+conf_upper <- 1 - conf_level
+
+for(j in 1:numtopics){
+
+  coefs <- list()
+
+  for(i in 1:sims){
+    coefs[[i]] <- prep$parameters[[j]][[i]]$est[2]
+  }
+
+  coefs <- do.call(c, coefs)
+  coefs <- quantile(coefs, c(conf_lower, conf_upper))
+
+  df$lower[j] <- coefs[1]
+  df$upper[j] <- coefs[2]
+  df$sig[j] <- all(coefs>0) | all(coefs<0)
+  df$coef[j] <- mean(coefs)
+
+}
+
+#number of significant topics
+sum(df$sig)
+
+topwords <- stm::labelTopics(stmFit, topics = NULL, n = 7, frexweight = 0.5)
+topwords <- topwords$frex
+
+library(stringr)
+library(xtable)
+
+coeffBatches <- seq(-max(abs(df$coef)), max(abs(df$coef)), length.out = 17)
+blues <- rev(c("blue!10", "blue!20", "blue!30", "blue!40", "blue!50", "blue!60", "blue!70", "blue!80"))
+reds <- c("red!10", "red!20", "red!30", "red!40", "red!50", "red!60", "red!70", "red!80")
+
+f <- function(x) cut(x, coeffBatches, 
+                     labels= c(blues, reds),
+                     include.lowest = T, right = TRUE)
+
+f(-max(abs(df$coef)))
+
+topwords2 <- as.data.frame(topwords[,1:7])
+
+#tab = data.frame(category = c("A","B","C"), groupA = c(.2,.3,.5), groupB= c(.6,.7,.9))
+cellcolors <- lapply(df$coef, function(x) paste0("\\cellcolor{", f(x), "}"))
+cellcolors[which(df$sig==F)] <- "\\cellcolor{white}"
[…]

### 2018-12-16 10_otherPlots/mapUS.R

@@ -1,0 +1,44 @@
+library("dplyr")
+library("ggplot2")
+library("ggmap")
+
+#load data
+load("rfiles/allURLs.rdata")
+websiteUrls <- websiteUrls[!websiteUrls$State=="Alaska",]
+websiteUrls <- websiteUrls[!websiteUrls$State=="Hawaii",]
+websiteUrls$latitude <- as.numeric(as.character(websiteUrls$latitude))
+websiteUrls$longitude <- as.numeric(as.character(websiteUrls$longitude))
+websiteUrls <- websiteUrls[is.na(websiteUrls$longitude)==F,]
+websiteUrls <- websiteUrls[is.na(websiteUrls$latitude)==F,]
+
+# make a basic map of the us states
+states <- map_data("state")
+map1 <- ggplot(data = states) + 
+  geom_polygon(aes(x = long, y = lat, group = group), fill = "papayawhip", color = "black") + 
+  coord_fixed(1.3)
+map1
+#overlay points on map
+map2 <- map1 + 
+  geom_point(data = websiteUrls, aes(x = longitude, y = latitude, color = party), size = .5) + 
+  theme(legend.position = "none") + 
+  scale_color_manual(values=c("blue", "red")) +
+  labs(x = "Longitude", y = "Latitude") +
+  theme_void() + theme(legend.position = "none")
+map2
+
+ggsave(filename = "paper/figures/us_map.pdf", plot = map2, width = 8, height = 6)
+
+#same map, but only the states we use
+states_use <- c("Indiana", "Louisiana", "Texas", "New York", "Washington", "California")
+websiteUrls <- websiteUrls[websiteUrls$State%in%states_use,]
+
+#overlay points on map
+map2 <- map1 + 
+  geom_point(data = websiteUrls, aes(x = longitude, y = latitude, color = party), size = .5) + 
+  theme(legend.position = "none") + 
+  scale_color_manual(values=c("blue", "red")) +
+  labs(x = "Longitude", y = "Latitude") +
+  theme_void() + theme(legend.position = "none")
+map2
+
+ggsave(filename = "paper/figures/us_map_sample_states.pdf", plot = map2, width = 8, height = 6)

### 2018-12-16 10_otherTables/tabCitiesStatesParties.R

@@ -1,0 +1,22 @@
+library(tidyr)
+library(xtable)
+
+load("rfiles/stmSession_sim.rdata")
+d <- subset(d, select = c(party, State, city))
+rm(list = ls()[ls()!="d"])
+
+d2 <- d[!duplicated(d$city),]
+d2$State <- as.character(d2$State)
+
+cities_states_parties <- xtabs(~party + State, d2)
+cities_states_parties <- as.data.frame(cities_states_parties)
+cities_states_parties <- spread(cities_states_parties, party, Freq)
+
+xtTopwords <- print(xtable(cities_states_parties, 
+                           caption = "Descriptive statistics on the partisanship of the cities in the corpus."), 
+                    sanitize.text.function = identity,
+                    label = "tabCitiesStatesParties",
+                    #size = "scriptsize",
+                    include.rownames = FALSE)
+
+writeLines(xtTopwords, con = 'paper/tables/tabCitiesStatesParties.tex')

### 2018-12-16 10_otherTables/tabFiletypeFrequencies.R

@@ -1,0 +1,56 @@
+# Purpose of the script:
+# make the table in the paper that shows the distribution of file types
+
+library(xtable)
+
+#re-use the script to detect filetypes
+source_lines <- function(file, lines){
+  source(textConnection(readLines(file)[lines]))
+}
+source_lines("inferFiletype.R", c(21,66))
+
+#create tables of filetype frequencies
+filetypes_after <- data.frame(sort(table(magicResults$extensions), decreasing = T), stringsAsFactors = F)
+filetypes_before <- data.frame(sort(table(magicResults$ext), decreasing = T), stringsAsFactors = F)
+names(filetypes_after) <- c("Filetype", "Occurances")
+names(filetypes_before) <- c("Filetype", "Occurances")
+filetypes_after$Filetype <- as.character(filetypes_after$Filetype)
+filetypes_before$Filetype <- as.character(filetypes_before$Filetype)
+
+#only show the top 10 types, everything else into an 'other' category
+#get the top 10
+top10types <- c(filetypes_after$Filetype[1:10], "")
+
+#put everything else into the other category, then delete everything else
+filetypes_after <- rbind(filetypes_after, c("Other", sum(filetypes_after$Occurances[!filetypes_after$Filetype%in%top10types])))
+filetypes_after <- filetypes_after[-which(!filetypes_after$Filetype%in%c(top10types, "Other")),]
+filetypes_after$Filetype[filetypes_after$Filetype=="NA"] <- NA
+
+#same for the before filetypes
+filetypes_before <- rbind(filetypes_before, c("Other", sum(filetypes_before$Occurances[!filetypes_before$Filetype%in%top10types])))
+filetypes_before <- filetypes_before[-which(!filetypes_before$Filetype%in%c(top10types, "Other")),]
+filetypes_before$Filetype[filetypes_before$Filetype==""] <- NA
+
+#merge the two to go into one table
+filetypes_before_after <- merge(filetypes_before, filetypes_after, by = "Filetype", all = T)
+filetypes_before_after$Occurances.x[is.na(filetypes_before_after$Occurances.x)==T] <- 0
+
+filetypes_before_after$Occurances.x <- as.numeric(as.character(filetypes_before_after$Occurances.x))
+filetypes_before_after$Occurances.y <- as.numeric(as.character(filetypes_before_after$Occurances.y))
+filetypes_before_after <- filetypes_before_after[order(filetypes_before_after$Occurances.y, decreasing = T),]
+
[…]

### 2019-05-01 paper/manuscript_paNote.tex
quick test & added PA note requirements in manuscript (will remove later)

--- 2018-10-06 paper/manuscript.tex
@@
 \doublespacing
+
+\noindent PA Letter Requirements:\\
+2-4 pages\\
+no longer than 1500-3000 words\\
+1-3 small display items (figures, tables, or equations)\\
+200-300 word abstract\\
+
 \section{Introduction}
-
 Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
@@
 Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.
+
+\section*{Funding}
+This work was supported by the National Science Foundation [1320219, 1637089, 1641047].
 

### 2019-05-06 paper/manuscript_paNote.tex
trimming down

@@
 Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra}.
+The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
 Despite the potential for automated scraping of website contents, the conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
-Though highly accurate, the manual approach to data collection is costly, and cannot be scaled to capture even a fraction of the volume of content available on government websites.
-In this paper, we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis.
+Though accurate, the manual approach to data collection is costly, and cannot be scaled to capture even a fraction of the volume of content available on government websites.
+In this paper, we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
 We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states (IN, LA, NY, WA, CA and TX) correlate with the partisanship of the city mayor.
 
-Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for content (e.g., text, image) analysis.
+%Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for content (e.g., text, image) analysis.
 We describe and provide solutions to two central challenges in automatically gathering and analyzing website textual contents.
 First, plain text must be extracted from the files.
-This involves purging the files of syntax in HTML or other markup and programming languages and discarding any character encoding errors that result from reading in files with incorrectly specified character encodings.
-This challenge would arise in any context in which researchers sought to study the textual contents of websites, and is not unique to comparative analysis of government websites.
+This challenge would arise in any context in which researchers sought to study the textual contents of websites.
 The second challenge we address in our methodological pipeline is, however, specific to the research objective of comparing websites on the basis of a common lexicon.
 For any two governments, the textual signatures that most dramatically differentiate the textual contents of their websites consist of what we can call ``boilerplate'' text---header, footer, or other titling text that is designed to identify the website as being associated with a specific government entity (e.g., ``Welcome to the city of Santa Cruz'', ``The City of Los Angeles welcomes you'').
-This boilerplate text is replicated across many files that are associated with a government's website, but it provides little information regarding the form and/or function of the government.
 The second methodological innovation we offer in our pipeline is designed to minimize the impact of this boilerplate text on the comparative analysis of government website content.
 
-Government websites provide information about how public policies shape the lives of local residents, and how local residents can engage with government to shape public policy.
-As such, government websites reflect both the results of and inputs to, the political leadership in the city.
-In our illustrative application, we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
-A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{gerber2011mayors,de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
-Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public \citep{sharfstein2017science,kirby2017trump,duarte2017deniable}.
-We study whether significant differences between city governments based on mayoral partisanship are reflected in the contents of city websites.
-
-\section{The Significance of Government Website Content}
-
- According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
-Official city websites allow mayors to perform all three of these functions.
-Their offices frequently take a prominent position on the front page, and many websites also feature a picture of the mayor.
-We present an example of this in Figure \ref{fig:eriemayor}.
-The Erie, Pennsylvania website homepage presents an image of the Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
+\section{Mayoral Politics and City Government Website Content}
+
+ A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep{gerber2011mayors,de2016mayoral,einstein2016mayors,marion2013mayor}.
+Official city websites allow mayors to present their views and policy priorities to the public.
 In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies \citep{stanyer2008elected}.
-Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
-City websites present an opportunity for local officials to brandish these accomplishments.
-Finally, they also give mayors a platform from which they can advertise their political beliefs.
-On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
-As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors.
-City websites can then be used to communicate the stance of a mayor on social or economic programs.
-Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.35]{figures/eriemayor}
-\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
-\label{fig:eriemayor}
-\end{figure}
-
-Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
+Local government websites are frequently visited by the public \citep{thomas2003new}.
+City websites can be used to communicate the stance of a mayor on social or economic programs.
+In the current paper, we evaluate the feasibility and performance of text analysis of city government websites in discerning differences in city governments based on mayoral partisanship.
+
+%\begin{figure}
+%\centering
+%\includegraphics[scale=0.35]{figures/eriemayor}
+%\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
+%\label{fig:eriemayor}
+%\end{figure}
+
+%Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
 In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
-Furthermore, the use of a local government website is associated with an individual's perspective on government.
+%Furthermore, the use of a local government website is associated with an individual's perspective on government.
 \citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
@@
 
-The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents produced by governments, public officials, and candidates for office.
+The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
 The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
-For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use, and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}.
+Research in this category evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
@@
 The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
-Like most e-government studies, however, this publication does not make any use of automated text analysis.
-Branching out of the topic of e-government service provision, \citet{mcnutt2010virtual} uses Canadian government websites to study how well-connected government websites are to non-profits and intergovernmental organizations in different public policy domains.
-%Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
-\cite{Lin2011} provide a good example of a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
-The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased.
-Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
-%Another well-known example fitting into this area of study is the set of studies conducted by King et al.
-\citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere.
-However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.
 
@@
 Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-\cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them.
-\cite{Cryer2017} mentions that she relied on Archive-it, a web service of the Internet Archive.
-Though the Internet Archive may provide extensive coverage of high profile officials or national governments, we found that its coverage of municipal government websites was sparse and irregular.
-\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
-\cite{Therriault2010} use automated text analysis, and also has the most extensive overview of the associated methodology.
-However, the division of the website into sections (home page, topics, issues, details) is done by hand.
-The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).
-
-Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
+For example, \citep{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
+Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.
+
+%mportant to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
 \cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
@@
 For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
+[{\bf Markus, when were the websites scarped---need to indicate year and/or month}].
 The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
 Municipal elections in Indiana and Louisiana are partisan across the board,\footnote{In Indiana, this includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.} so our sample is primarily focused on these two states.
-Here, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
+For Indiana and Louisiana, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
 New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see below for more detail on how we use this data).
@@
 These six states also provide us with a sample that is well-balanced on a number of theoretically important indicators.
-One, each of the four geographic regions are represented with at least one state.
+One, each of the four geographic regions [{\bf Markus, are these census regions?}] are represented with at least one state.
 Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered.
 Furthermore, the sample is politically balanced---we have three blue states (CA, WA, NY) and three red states (TX, IN, LA).
-Finally, our dataset contains some of the wealthiest states (NY, CA, WA and TX are \#2, \#8, \#9 and \#16 respectively, by GDP per capita \citep{BureauofEconomicAnalysis2017}), but also some of the poorer ones (IN and LA).
-
-We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
-Two, the General Services Administration (GSA) maintains all `.gov' addresses, and provides a complete list of all such domains to the public.\footnote{The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
-This list is updated once per month---we rely on the version released on January 16, 2017.} The data from the GSA contains the following variables: (1) domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'); (2) the type of government entity to which the domain is registered, such as city, county, federal agency, etc; (3) for federal agencies, the name is specified; (4) the city in which the domain is registered.
-Naturally, the GSA's list does not contain cities which do not use a `.gov' website (or, in many cases, a city owns a registered `.gov' address, but uses a different one).
-Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
-Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
-
-Not all of the URLs contained in these archives are functional.
-To test the URLs' functionality, we use a web driver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
-We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the web driver  \texttt{Geckodriver}.
-This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers.
-Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
-The use of a web driver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
-A web driver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
-This allows us to subsequently record and use the new URL for the actual website scraping.
-Consequently, an automated browser allows us to robustly answer the following questions: Is the website actually there?
-Does it work?
-If not, is it somewhere else or is it broken?
-We record this information and construct a list of verified URLs.
-
-To download the websites, we rely on the Unix command line tool \texttt{wget}.
-This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
-This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
-Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
-it does not follow external links).
-This way, all the files that make up a website are downloaded.
-For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
-For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites.
-However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
-
-The partisanship of the mayor of each city is coded in different ways, depending on the state.
-For Indiana, where elections are nominally partisan, this information is accessible through the state government's website\footnote{\url{http://www.in.gov/apps/sos/election/general/general2015?page=office&countyID=1&officeID=32&districtID=-1&candidate=}}.
-For Louisiana, we received data on the outcomes of mayoral elections from the Local Elections in America Project (LEAP) \citep{marschall2013local}.
-For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and coded the parties of the candidates based on the party committees from which they received donations.
-For California and Texas, where our data consists of highly populated cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
-Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
-When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
-Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
 The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
 The dataset has a relative party balance, with variation in each state.
+Details on the sources and methods of raw data collection can be found in the Appendix.
 
@@
 Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies.
-Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant.
+Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset.
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\cite{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
-Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
-Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
+\cite{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities.
 
@@
 
-Once we have gathered the website files, we have the raw data necessary for text analysis, but it is not yet formatted effectively.
-As is common in text analysis applications, we need to pre-process our data \citep{denny2018text}.
+Once we have gathered the website files we need to pre-process the data \citep{denny2018text}.
 In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
@@
 However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance.
-They find that cities with Democratic mayors spend a smaller share of their budgets on public safety, but that mayoral partisanship does not appear to be significantly related to spending in most other areas, where cities have less discretion.
-As opposed to budget allocation or even the presence/absence of policies, cities have a great deal of discretion regarding what is emphasized on their websites, and how policies are framed.
-Since (1) city governments have great discretion in composing their websites, (2) modifying website content is low cost relative to other policy changes, and (3), as reviewed above, city websites provide an effective and often-used means of communication with city residents.
+These constraints do not apply to website contents.
+City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.
 
@@
 
-\subsubsection{Analytical approach: Structural topic modeling}
-In order to analyze content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citet{Roberts2014}.
-Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the structural topic model a topic is a multinomial distribution defined on the word types in the dictionary.
-Each word occurrence in a document is attributed with a single topic label.
-The word topic assignments are also drawn from a multinomial distribution.
+In order to analyze content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
+Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary.
 The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics.
 For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic.
-For our primary empirical investigation, the structural topic model provides with a tool with which to estimate the relationship between the party of the city's mayor and the prevalence of each topic we estimate.
-A topic interpreted through post-hoc analysis of the collective meaning of the most likely words to be drawn from the multinomial distribution defined by the respective topic.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
-
-The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.
-Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
-We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
-Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
-Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city.
-Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.
+For our primary empirical investigation, the STM provides with a tool with which to estimate the relationship between the party of the city's mayor and the prevalence of each topic we estimate.
+Further details on our STM specification can be found in the appendix.
 
@@
 The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
-The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic.
 The topics that are entirely white have 90\% credible intervals on the effect of the mayoral party that include zero.
@@
 %US map
-\begin{figure}[htp]
-    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-    \includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
-        \caption{Map of the cities in the corpus in the contiguous U.S.
+%\begin{figure}[htp]
+  %  \centering % Using \begin{figure*} makes the figure take up the entire width of the page
+    %\includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
+       % \caption{Map of the cities in the corpus in the contiguous U.S.
 The corpus also includes Alaska.
@@
 The colors represent the partisanship of the mayor (blue corresponding to Democrats and red to Republicans).}
-    \label{us_map}
-\end{figure}
+    %\label{us_map}
+%\end{figure}
 
@@
 This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
-The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language.
-Government website contents can, and have been, used to study questions related representation, government transparency, and public policy priorities.
-The methods we develop can be used to scale up projects involving website data collection by automating the process.
-
-In terms of pure scope, our method is superior to the existing approaches.
-Manual content analysis (see, for example, \cite{Druckman2009}) relies on research assistants reading and evaluating websites, and therefore might struggle to provide a complete understanding of even individual websites, which often contain thousands of pages.
-Scrapers conventionally used in the social sciences (see, for example, \citealt{Cryer2017}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
-By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
-Consequently, our approach facilitates the kind of bulk data collection and analysis necessitated by an ever-growing web.
-
 Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
@@
 
-We offer several contributions that will be valuable in future research endeavors.
+%We offer several contributions that will be valuable in future research endeavors.
 First, the data collected in the current study can be used for comparative analysis of US city website contents.
@@
 \section*{Appendix}
+
+\subsection*{Raw data collection methods and sources}
+
+We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
+Two, the General Services Administration (GSA) maintains all `.gov' addresses, and provides a complete list of all such domains to the public.\footnote{The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
+This list is updated once per month---we rely on the version released on January 16, 2017.} The data from the GSA contains the following variables: (1) domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'); (2) the type of government entity to which the domain is registered, such as city, county, federal agency, etc; (3) for federal agencies, the name is specified; (4) the city in which the domain is registered.
+Naturally, the GSA's list does not contain cities which do not use a `.gov' website (or, in many cases, a city owns a registered `.gov' address, but uses a different one).
+Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
+Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
+
+Not all of the URLs contained in these archives are functional.
+To test the URLs' functionality, we use a web driver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
+We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the web driver  \texttt{Geckodriver}.
+This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers.
+Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
+The use of a web driver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
+A web driver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
+This allows us to subsequently record and use the new URL for the actual website scraping.
+Consequently, an automated browser allows us to robustly answer the following questions: Is the website actually there?
+Does it work?
+If not, is it somewhere else or is it broken?
+We record this information and construct a list of verified URLs.
+
+To download the websites, we rely on the Unix command line tool \texttt{wget}.
+This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
+This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
+Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
+it does not follow external links).
+This way, all the files that make up a website are downloaded.
+For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
+For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites.
+However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
+
+The partisanship of the mayor of each city is coded in different ways, depending on the state.
+For Indiana, where elections are nominally partisan, this information is accessible through the state government's website\footnote{\url{http://www.in.gov/apps/sos/election/general/general2015?page=office&countyID=1&officeID=32&districtID=-1&candidate=}}.
+For Louisiana, we received data on the outcomes of mayoral elections from the Local Elections in America Project (LEAP) \citep{marschall2013local}.
+For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and coded the parties of the candidates based on the party committees from which they received donations.
+For California and Texas, where our data consists of highly populated cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
+Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
+When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
+Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
+
+Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
+Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
+
+\section*{Details on STM specification}
+
+The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
+We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.
+Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
+We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
+Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
+Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city.
+Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
 

### 2019-05-06 paper/manuscript_paNote.tex

@@
 The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
-Despite the potential for automated scraping of website contents, the conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
-Though accurate, the manual approach to data collection is costly, and cannot be scaled to capture even a fraction of the volume of content available on government websites.
-In this paper, we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
-We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states (IN, LA, NY, WA, CA and TX) correlate with the partisanship of the city mayor.
+The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
+Though accurate, the manual approach to data collection is costly for large-scale analysis.
+We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
+We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
 
@@
 City websites can be used to communicate the stance of a mayor on social or economic programs.
-In the current paper, we evaluate the feasibility and performance of text analysis of city government websites in discerning differences in city governments based on mayoral partisanship.
 
@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
-Research in this category evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
-As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
-To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated.
-The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
-
-The websites of politicians and their parties have also been the object of research.
-Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+Research `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
+As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
+The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
 For example, \citep{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
@@
 The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
-Municipal elections in Indiana and Louisiana are partisan across the board,\footnote{In Indiana, this includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.} so our sample is primarily focused on these two states.
+Municipal elections in Indiana and Louisiana are partisan across the board, so our sample is primarily focused on these two states.
 For Indiana and Louisiana, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
-New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see below for more detail on how we use this data).
-Finally, California and Texas contain a number of large cities, whose mayors are sufficiently well-known for their partisanship to be available.
-These six states also provide us with a sample that is well-balanced on a number of theoretically important indicators.
+New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see appendix for more detail).
+California and Texas contain a number of large cities whose mayors are sufficiently well-known for their partisanship to be available.
+Our sample is well-balanced on a number of theoretically important dimension.
 One, each of the four geographic regions [{\bf Markus, are these census regions?}] are represented with at least one state.
-Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered.
-Furthermore, the sample is politically balanced---we have three blue states (CA, WA, NY) and three red states (TX, IN, LA).
+Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage.
+Furthermore, the sample is politically balanced---we have three blue states, and three red states.
 The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
-The dataset has a relative party balance, with variation in each state.
 Details on the sources and methods of raw data collection can be found in the Appendix.
@@
 One of the more subtle aspects of local government is the presence of different types of government structures.
-Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies.
-Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset.
+Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
+We do not have access to information about the type of governments across the breadth of our dataset.
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
@@
 The results are shown in Table \ref{tabSTMtopwords60}.
-The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
-The topics that are entirely white have 90\% credible intervals on the effect of the mayoral party that include zero.
-
 Many of the topics associated with Democrats fit with what we understand to be national party priorities.
@@
 When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
-Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
+Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.\footnote{In Indiana, the data includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.}
 

### 2019-05-07 paper/manuscript_paNote.tex
got started on pipeline section, not done yet

@@
 Once we have gathered the website files we need to pre-process the data \citep{denny2018text}.
-In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
+In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents that are suitable for comparative analysis with text as data methods.
 In this pipeline, we address two methodological challenges.
@@
 The first step in the methodological pipeline is aimed simply at extracting clean plain text from this heterogeneous file base.
-The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
+The second step in our methodological pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
 Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
@@
 This short sequence of bytes at the start (and sometimes end) of files is unique for each file type and therefore allows its correct identification through computer forensics tools such as \texttt{libmagic}.
-
-Consequently, we rename all documents so that their file ending reflects their actual file type.
-This is strictly necessary because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
+Files with incorrect endings are subsequently renamed.
+
+\subsubsection{Extracting Text from HTML}
+The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus and navigational elements.
+We leverage methods developed in the information retrieval literature to deal with this problem.
+These so-called 'boilerplate detection' tools rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful.
+We rely on the method described in \cite{Kohlschuetter2010}, which has been published in a reputable conference, is widely cited and can easily be implemented through the R package \texttt{boilerpipeR}.
+
+\subsubsection{Extracting Text from PDF, XML, DOC, DOCX and TXT}
+Other files are read in through the \texttt{readtext} R package\footnote{\texttt{readtext} determines a document's type solely through its ending -- so the conversion described above is strictly necessary for the package to work correctly.} \citep{readtext}, which is a wrapper for a set of parsers.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.}\footnote{\texttt{readtext} also contains an HTML parser, but this tool simply extracts all text and is therefore inferior to boilerpipe.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
 The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
@@
 %With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
+
+For preprocessing, we rely on a set of tools which are used much more commonly in natural langauge processing than political methodology -- part-of-speech (POS) tagging and named entity recognition (NER), as these procedures perform very well in separating substantively interesting information from any remaining boilerplate.
+Names of city officials and citizen petitioners feature frequently in city documents.
+The same is true for streets, locations and not least of all, the city itself.
+Since individual names recur at a much higher rate within a city than across the entire corpus, this causes a topic model to cluster its topics by city.
+As these names convey no substantive information, we rely on NER to remove them.
+Specifically we use \texttt{spacyR} to detect and remove all entities except X, Y and Z, as well.
+Similarly we remove words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, adjectives.
+Furthermore, we keep proper nouns that also occur as nouns -- this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
+
+We also conduct lemmatization to reduce words to their basic form.
+Lemmatization is similar to stemming but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
+For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
+Thus, lemmatization makes the results more easily comprehensible.
+
+Furthermore, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyR} with an English tagger, non-English words are erroneously categorized as (proper) nouns.}.
+
+A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
+In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
+The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
+For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus.
+These short and repetitive texts would pose severe problems to a topic model.
+Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.
 
@@
 Removing them in this manner is also the default preprocessing choice in the \texttt{stm} package.} to our models while increasing their computational cost, we also discard any token types that occur in only one document.
-We also conduct lemmatization to reduce words to their basic form.
-Lemmatization is similar to stemming but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
-For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
-Thus, lemmatization makes the results more easily comprehensible.
-To this end, we rely on the R package \texttt{spacyr}, which provides an R implementation of the Python library \texttt{spaCy}.
 
@@
 See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
-In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at the line level.
-
-%this is outdated; not deleting it yet in case we need it for further reference
-%Consequently we remove this content as follows: Each line of every document is compared to every line in every other document belonging to the same city.
-We count how many times each line is duplicated for that city.
-We remove any line occurring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
-We implement this algorithm through hash tables, which reduces the computational complexity from O($N^2$) to O($N$).
-Before this step is taken, we remove numbers and dates from the documents because they frequently make lines unique, despite the fact that they are virtually the same (for example different days on a city calendar).
-
-\subsection*{Boilerplate Classification}
-In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
+
+%\subsection*{Boilerplate Classification}
+%In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
 We sampled 500 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
@@
 
-These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines).
+%These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines).
 We then trained a number of different classifiers with this informativeness measure as the dependent variable.
@@
 
-\begin{itemize}
-\item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two.
-This is highly predictive of lines which are used as website headers and navigational elements, which are of zero substantive interest to us but are very effective at differentiating cities.
-These terms also happen to be fairly common, which causes them to be overweighted by the topic model.
-
-\item {\bf Number of line duplications:} To directly address the latter problem, we include a measure of the number of times a line is duplicated within a city.
-Many lines occur hundreds or even thousands of times on a single website and therefore are terms that are highly predictive of the website, which causes the topic model to find topics that are highly predictive of cities, but not substantively informative.
-
-\item {\bf Line position in the document} Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
-Since lines can occur in multiple documents or multiple times in the same document, we take the median of these measures.
-Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus is indicative of more relevant content, might be scored with a 0.11 instead.
-\end{itemize}
-
-%Finally, the keyness measure: This indicator shows whether a term occurs disproportionally frequently in one document collection, compared to another.
-In our case, this would be one city's documents, compared to all others.
-Mathematically, this is a simple chi-square test, asserting whether the frequency of a word in a city is greater than its expected count, as determined by its count in all other documents, and the number of tokens in the city.
-The variable used in the model is the chi-square value of this test for each word (which varies and is therefore calculated individually for each city).\footnote{Or alternatively, the log of the absolute chi-square value, after which the previously negative values are made negative again.}
-
-%A regression table for this model can be found in table 3.
-The associated accuracy in 5-fold cross-validation is 0.8325.
-The cross-validation accuracy of a simplified model with only the number of characters as a covariate is 0.825 (table 4).
-A model with the four covariates described above as well as interaction terms between each of them yields an accuracy of 0.885 (table 5).
-
-%\input{tables/boilerplateClassifier1.tex}
-\input{tables/boilerplateClassifierRFMetrics.tex}
-%\input{tables/boilerplateClassifierRFImportance.tex}
-
-We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess the performance of this classifier through five-fold cross-validation.
-This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score.
-This procedure is carried out five times so that each sample is part of the test set once.
-The aggregated (mean) results of this process can be found in Table \ref{randomForest}.
-For the implementation of this method, we rely on the R package \texttt{caret}, whose random forest classifier is based on the package \texttt{ranger}.
-We use this classifier to flag and remove all lines that are not classified (based on a threshold of $p = 0.5$) as substantively meaningful.
-The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e.
-a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}.
-Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common.
-After the removal, the distribution has changed---lines of medium length now occur more frequently than extremely short ones, which are unlikely to be substantively meaningful (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
-Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}).
-Finally, the position of the line in the documents is not as important to the random forest, and this also shows in the results.
-However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
-Table \ref{tabBoilerplateIllustration} provides further illustration by listing the top 10 most likely boilerplate lines (in Anchorage, AK) -- all of which were flagged as such with a probability of 1.
 After all the preprocessing is set and done, our corpus consists of 259,099 documents.
-
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
-    \label{boilerplate_before_after1}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
-\end{figure}
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
-    \label{boilerplate_before_after2}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
-\end{figure}
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.
-After the boilerplate content is removed, lines that are duplicated hundreds or thousands of times are less common.}
-    \label{boilerplate_before_after3}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
-\end{figure}
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, lines at the beginning and end of documents are less common.}
-    \label{boilerplate_before_after4}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
-\end{figure}
 

### 2019-05-08 paper/manuscript_paNote.tex
first pass at pipeline section

@@
 
-%mportant to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
+%Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
 \cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
@@
 \section{The Web to Text Pipeline}
-
-Once we have gathered the website files we need to pre-process the data \citep{denny2018text}.
-In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents that are suitable for comparative analysis with text as data methods.
-In this pipeline, we address two methodological challenges.
+In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents that are suitable for comparative analysis with text as data methods.
+Here, we address three methodological challenges.
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
 Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
-The first step in the methodological pipeline is aimed simply at extracting clean plain text from this heterogeneous file base.
-The second step in our methodological pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
-Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
+The first step is aimed at extracting clean plain text from this heterogeneous file base.
+The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
+Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.%Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
 We will clarify this distinction as we describe steps in our pipeline.
@@
 \subsection{Site to Text Conversion}
+\subsubsection{File Type Detection}
 The format of a file has a major impact on whether and how textual data can be extracted from a document.
-For all text analysis projects, researchers need to consider file formats.
 For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
@@
 \subsubsection{Extracting Text from HTML}
-The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus and navigational elements.
+The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate.
+In theory, HTML tags intended to mark text content  exist to prevent this problem.
+In practice, not every web developer adheres to this standard, and even when they do, there is a large degree of variation in the way it is implemented.
+Parsing any one website is fairly straightforward, but parsing the 283 different websites in our sample in a consistent and comparable manner makes a rule-based approach impossible.
+
 We leverage methods developed in the information retrieval literature to deal with this problem.
-These so-called 'boilerplate detection' tools rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful.
-We rely on the method described in \cite{Kohlschuetter2010}, which has been published in a reputable conference, is widely cited and can easily be implemented through the R package \texttt{boilerpipeR}.
+These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful.
+We rely on the method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited and can easily be implemented through the R package \texttt{boilerpipeR}.
 
 \subsubsection{Extracting Text from PDF, XML, DOC, DOCX and TXT}
-Other files are read in through the \texttt{readtext} R package\footnote{\texttt{readtext} determines a document's type solely through its ending -- so the conversion described above is strictly necessary for the package to work correctly.} \citep{readtext}, which is a wrapper for a set of parsers.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.}\footnote{\texttt{readtext} also contains an HTML parser, but this tool simply extracts all text and is therefore inferior to boilerpipe.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
-The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
+Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending -- so the conversion described above is strictly necessary for the package to work correctly.}$^{,}$\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but this tool simply extracts all text and is therefore inferior to boilerpipe.} The breakdown of all files by type is given in Table \ref{tab:filetypes}.
+The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
 Files of type XML, DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
@@
 
-We then take several steps to pre-process the data as required for the subsequent analysis.
-Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}.
-The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
+\subsection{Preprocessing}
+Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}.
+The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites.
+Some of it is substantively informative and some of it is completely irrelevant.
+As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents.
+The same is true for streets, locations and not least of all, the city itself.
+Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city.
+Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.
+
+%The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
 %With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
 
-For preprocessing, we rely on a set of tools which are used much more commonly in natural langauge processing than political methodology -- part-of-speech (POS) tagging and named entity recognition (NER), as these procedures perform very well in separating substantively interesting information from any remaining boilerplate.
-Names of city officials and citizen petitioners feature frequently in city documents.
-The same is true for streets, locations and not least of all, the city itself.
-Since individual names recur at a much higher rate within a city than across the entire corpus, this causes a topic model to cluster its topics by city.
-As these names convey no substantive information, we rely on NER to remove them.
-Specifically we use \texttt{spacyR} to detect and remove all entities except X, Y and Z, as well.
-Similarly we remove words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, adjectives.
+To this end, we turn to to an approach that is much more common in natural langauge processing than political methodology -- part-of-speech (POS) tagging and named entity recognition (NER).
+While not their original purpose, these procedures perform very well in separating the wheat from the chaff.
+As names convey no substantive information, we NER is used to detect to remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient with respect to immigration and identity) as well as works of art (which frequently feature statutes, plans, etc.)} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, adjectives.
 Furthermore, we keep proper nouns that also occur as nouns -- this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
-
-We also conduct lemmatization to reduce words to their basic form.
-Lemmatization is similar to stemming but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
+Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
 For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
-Thus, lemmatization makes the results more easily comprehensible.
-
-Furthermore, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyR} with an English tagger, non-English words are erroneously categorized as (proper) nouns.}.
+Thus, lemmatization makes the results more easily comprehensible.} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyR}.
+This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources, as the grammatical rules of the English language remain their common denominator.
+To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyR} with an English parser, non-English words tend to be erroneously categorized as (proper) nouns.}.
 
@@
 For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus.
-These short and repetitive texts would pose severe problems to a topic model.
+These short and repetitive -- but numerous -- texts would pose severe problems to a topic model.
 Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.
 
-The text documents are converted to UTF-8 character encoding and then stripped of dates, punctuation, numbers, and words connected by underscores.
+After all the preprocessing is set and done, our corpus consists of 259,099 documents.
+
+%The text documents are converted to UTF-8 character encoding and then stripped of dates, punctuation, numbers, and words connected by underscores.
 At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
@@
 
-The last round of preprocessing is intended to remove everything from the file that is not an English word.
+%The last round of preprocessing is intended to remove everything from the file that is not an English word.
 This step is tailored to our intention to use the text for topic modeling.
@@
 
-\subsection{Boilerplate Removal}\label{boilerplate}
-As noted above, city websites contain a large amount of text that is uninformative for its actual content, and therefore a hindrance to understanding through algorithmic text analysis.
+%\subsection{Boilerplate Removal}\label{boilerplate}
+%As noted above, city websites contain a large amount of text that is uninformative for its actual content, and therefore a hindrance to understanding through algorithmic text analysis.
 This is a common issue with textual data in which informative content is embedded in technically structured documents.
@@
 The purpose of these covariates is as follows:
-
-After all the preprocessing is set and done, our corpus consists of 259,099 documents.
 

### 2019-05-08 paper/manuscript_paNote.tex
filled in two fields (yes it is a Census region & websites were scraped march 2018)

@@
 For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
-[{\bf Markus, when were the websites scarped---need to indicate year and/or month}].
+The websites were scraped in March 2018.
 The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
@@
 Our sample is well-balanced on a number of theoretically important dimension.
-One, each of the four geographic regions [{\bf Markus, are these census regions?}] are represented with at least one state.
+One, each of the four Census regions are represented with at least one state.
 Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage.

### 2019-05-12 07_topicModel/01_stm_estimation.R
new stm results

@@ -6,19 +6,22 @@ library('scales')
 library('stringr')
 set.seed(1)
 
-load(file = "../06_preprocessing/out/preprocessed_tks.rdata")
+load(file = "../06_preprocessing/out/preprocessing_finished.rdata")
 #merge in census covariates
-d <- docvars(tks)
+load("../04_parseText/out/citydocs.rdata")
 load("../00_scrapeCovariates/out/websiteMetadata_Census.rdata")
 websiteMeta <- subset(websiteMeta, select = c(State_City, B01001_001E, B19013_001E))
 d <- merge(d, websiteMeta, by = "State_City")
-docvars(tks) <- d
-rm(websiteMeta, d)
+d_reordered <- d[match(names(tks_all), d$id),]
+docvars(tks_all) <- d_reordered
+rm(websiteMeta, d, d_reordered)
 #use only the states for which we have data on multiple cities
-tks <- tokens_subset(tks, State %in% c("Indiana", "Louisiana", "New York", "California", "Washington", "Texas"))
+tks_all <- tokens_subset(tks_all, State %in% c("Indiana", "Louisiana", "New York", "California", "Washington", "Texas"))
 #convert to dfm and then stm
-d_dfm <- dfm(tks)
+d_dfm <- dfm(tks_all)
 d_stm <- convert(d_dfm, to = "stm")
+save(d_stm, file = "out/ready_for_stm.rdata")
+load("out/ready_for_stm.rdata")
 
 #Number of topics
 numtopics <- 60
@@ -44,7 +47,7 @@ sims <- 1000
 #re-estimate the effects, this time do 1000 draws from the posterior
 prep <- estimateEffect(formula = 1:numtopics ~ party + State + B01001_001E + B19013_001E, 
                        stmobj = stmFit,
-                       meta = d, 
+                       metadata = d_stm$meta, 
                        uncertainty = "Global",
                        nsims = sims)
 

### 2019-05-15 paper/manuscript_paNote.tex
new stm results
fixed some minor errors in the manuscript

@@
 We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content.
-Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information through a new method of boilerplate removal.
+Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
 We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
 The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-For example, \citep{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
+For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
 Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.
@@
 California and Texas contain a number of large cities whose mayors are sufficiently well-known for their partisanship to be available.
-Our sample is well-balanced on a number of theoretically important dimension.
+Our sample is well-balanced on a number of theoretically important dimensions.
 One, each of the four Census regions are represented with at least one state.
@@
 Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\cite{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities.
+\cite{gerber2011mayors}, whose theory is somewhat comparable to ours, find that the inclusion of this potential confounder does not affect the results.
 
@@
 
-\input{tables/tabBoilerplateIllustration.tex}
+%\input{tables/tabBoilerplateIllustration.tex}
 
@@
 \input{tables/stmTopWords60.tex} %\ref{tabSTMtopwords2}
+\input{tables/stmTopWords60New.tex}
 
@@
 Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
-Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the former and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
+Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the latter and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
 
@@
 
-Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
+Information on other covariates (population and median household income - from the American Community Survey 5-Year Data (2015)) was acquired through the API of the U.S.
 Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
@@
 The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.
-Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
-We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
+We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.\footnote{Since our corpus is at the larger end of that spectrum, we also estimated a model with 120 topics, but found no notable differences.} We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
 Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).

### 2019-05-17 paper/tables/stmTopWords120_2.tex
new structure
new results

@@
 % latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Sun Aug  5 19:55:00 2018
+% Fri Aug 10 15:26:58 2018
 \begin{table}[ht]
@@
   \hline
- 34 & \cellcolor{white}plan & \cellcolor{white}planning & \cellcolor{white}comprehensive & \cellcolor{white}master & \cellcolor{white}review & \cellcolor{white}amendment & \mybar{42} \\ 
  82 & \cellcolor{white}com & \cellcolor{white}mar & \cellcolor{white}spec & \cellcolor{white}jun & \cellcolor{white}est & \cellcolor{white}comm & \mybar{1388} \\ 
@@
 \endgroup
-\caption{Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring.
+\caption{OLD: Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring.
 Colors depict partisanship based on coefficient size.
 White cells are non-significant topics.}
+\label{tabSTMtopwords120_2}
 \end{table}

### 2019-05-17 paper/tables/stmTopWords60.tex
fixed a small problem with the tex table labels and renamed some stuff for more sensible file names and table labels
new results

--- 2018-06-14 paper/tables/stmTopWords2.tex
@@
-% latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Thu Jun 14 16:31:41 2018
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Fri May 17 09:59:58 2019
 \begin{table}[ht]
@@
   \hline
- 38 & \cellcolor{red!40}artist & \cellcolor{red!40}poetry & \cellcolor{red!40}music & \cellcolor{red!40}fun & \cellcolor{red!40}dance & \cellcolor{red!40}exhibition & \mybar{3770} \\ 
-    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}mail & \cellcolor{red!30}copy & \cellcolor{red!30}contact & \cellcolor{red!30}click & \mybar{260} \\ 
-   43 & \cellcolor{red!20}epidemiology & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}antibody & \cellcolor{red!20}asthma & \cellcolor{red!20}hygiene & \mybar{2469} \\ 
-   20 & \cellcolor{red!20}snow & \cellcolor{red!20}hurricane & \cellcolor{red!20}tornado & \cellcolor{red!20}plow & \cellcolor{red!20}evacuate & \cellcolor{red!20}pothole & \mybar{1290} \\ 
-   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}legislator & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}sander & \cellcolor{red!20}dog & \mybar{1152} \\ 
-   51 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pump & \cellcolor{red!20}sludge & \cellcolor{red!20}sewage & \mybar{487} \\ 
-   32 & \cellcolor{red!20}think & \cellcolor{red!20}really & \cellcolor{red!20}okay & \cellcolor{red!20}thing & \cellcolor{red!20}something & \cellcolor{red!20}seem & \mybar{1940} \\ 
-   36 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}hereunder & \mybar{433} \\ 
-   27 & \cellcolor{red!10}library & \cellcolor{red!10}branch & \cellcolor{red!10}learn & \cellcolor{red!10}book & \cellcolor{red!10}online & \cellcolor{red!10}view & \mybar{302} \\ 
-   58 & \cellcolor{red!10}buffalo & \cellcolor{red!10}announce & \cellcolor{red!10}warren & \cellcolor{red!10}lovely & \cellcolor{red!10}honor & \cellcolor{red!10}ceremony & \mybar{1298} \\ 
-   33 & \cellcolor{red!10}fire & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}beach & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \mybar{459} \\ 
-   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}billing & \cellcolor{red!10}bill & \cellcolor{red!10}refund & \mybar{241} \\ 
-   35 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}school & \cellcolor{red!10}teacher & \cellcolor{red!10}academic & \mybar{710} \\ 
-   56 & \cellcolor{red!10}garland & \cellcolor{red!10}auburn & \cellcolor{red!10}councilor & \cellcolor{red!10}plain & \cellcolor{red!10}hall & \cellcolor{red!10}ward & \mybar{229} \\ 
-   21 & \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}subcontractor & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontract & \mybar{485} \\ 
-   59 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}unanimously & \cellcolor{red!10}second & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \mybar{487} \\ 
-   49 & \cellcolor{red!10}garbage & \cellcolor{red!10}recycling & \cellcolor{red!10}bin & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}cart & \mybar{1635} \\ 
-   31 & \cellcolor{red!10}deductible & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}coinsurance & \cellcolor{red!10}copay & \cellcolor{red!10}aircraft & \mybar{706} \\ 
-   54 & \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}piping & \mybar{1477} \\ 
-   14 & \cellcolor{red!10}immigrant & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}immigration & \cellcolor{red!10}racial & \cellcolor{red!10}refugee & \mybar{1095} \\
-    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}infiltration & \cellcolor{red!10}drain & \cellcolor{red!10}discharge & \mybar{490} \\ 
-    2 & \cellcolor{red!10}yon & \cellcolor{red!10}ave & \cellcolor{red!10}blvd & \cellcolor{red!10}greenwood & \cellcolor{red!10}suite & \cellcolor{red!10}comm & \mybar{1317} \\ 
-    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \mybar{1377} \\ 
-   55 & \cellcolor{red!10}alderman & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}ordain & \cellcolor{red!10}resolution & \cellcolor{red!10}resolve & \mybar{457} \\ 
-   26 & \cellcolor{red!10}sampling & \cellcolor{red!10}petroleum & \cellcolor{red!10}sample & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}pesticide & \mybar{1278} \\
-   48 & \cellcolor{red!10}premise & \cellcolor{red!10}marijuana & \cellcolor{red!10}permit & \cellcolor{red!10}licensee & \cellcolor{red!10}license & \cellcolor{red!10}cannabis & \mybar{489} \\ 
-   12 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}digital & \cellcolor{red!10}telecommunication & \cellcolor{red!10}technology & \mybar{917} \\
-    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}climate & \cellcolor{red!10}electricity & \cellcolor{red!10}greenhouse & \mybar{740} \\ 
-   16 & \cellcolor{white}recreation & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}park & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{702} \\ 
-   60 & \cellcolor{white}exhaust & \cellcolor{white}air & \cellcolor{white}boiler & \cellcolor{white}diesel & \cellcolor{white}ozone & \cellcolor{white}fuel & \mybar{316} \\ 
-    3 & \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}issuer & \cellcolor{white}maturity & \cellcolor{white}parish & \cellcolor{white}jun & \mybar{502} \\ 
-   23 & \cellcolor{white}economic & \cellcolor{white}attract & \cellcolor{white}downtown & \cellcolor{white}economy & \cellcolor{white}industry & \cellcolor{white}revitalization & \mybar{862} \\ 
-   25 & \cellcolor{white}incumbent & \cellcolor{white}exam & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}knowledge & \cellcolor{white}examination & \mybar{683} \\ 
-    8 & \cellcolor{white}actuarial & \cellcolor{white}retirement & \cellcolor{white}pension & \cellcolor{white}contribution & \cellcolor{white}retiree & \cellcolor{white}valuation & \mybar{289} \\ 
-    9 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1103} \\ 
-   15 & \cellcolor{white}shoreline & \cellcolor{white}marsh & \cellcolor{white}coastal & \cellcolor{white}habitat & \cellcolor{white}wetland & \cellcolor{white}salmon & \mybar{1454} \\ 
-   42 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}real & \cellcolor{white}abatement & \cellcolor{white}property & \mybar{343} \\ 
-   30 & \cellcolor{blue!10}population & \cellcolor{blue!10}census & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}comparison & \mybar{540} \\
-   53 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}century & \cellcolor{blue!10}historian & \cellcolor{blue!10}archaeological & \mybar{2518} \\
-   11 & \cellcolor{blue!10}parking & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}passenger & \cellcolor{blue!10}tow & \cellcolor{blue!10}garage & \cellcolor{blue!10}taxicab & \mybar{435} \\ 
-   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}deer & \cellcolor{blue!10}planting & \mybar{2279} \\ 
-   45 & \cellcolor{blue!10}variance & \cellcolor{blue!10}plat & \cellcolor{blue!10}setback & \cellcolor{blue!10}zoning & \cellcolor{blue!10}fence & \cellcolor{blue!10}yard & \mybar{300} \\ 
-   19 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \mybar{360} \\
-   13 & \cellcolor{blue!10}agency & \cellcolor{blue!10}yes & \cellcolor{blue!10}federal & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}deficiency & \mybar{239} \\ 
-    6 & \cellcolor{blue!10}improvement & \cellcolor{blue!10}project & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}replacement & \mybar{189} \\
-   46 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}wage & \cellcolor{blue!10}salary & \mybar{398} \\ 
-   28 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}allege & \cellcolor{blue!10}bankruptcy & \mybar{1747} \\
-   40 & \cellcolor{blue!10}tab & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}false & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \mybar{257} \\ 
-   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}orient & \mybar{336} \\ 
-   39 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}review & \cellcolor{blue!10}preliminary & \cellcolor{blue!10}planning & \cellcolor{blue!10}propose & \mybar{274} \\ 
-   37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}implement & \cellcolor{blue!10}oversight & \mybar{402} \\
-   44 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}landlord & \cellcolor{blue!10}affordability & \mybar{340} \\
-   17 & \cellcolor{blue!10}debt & \cellcolor{blue!10}governmental & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{259} \\
-   41 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}intersection & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}crosswalk & \mybar{527} \\
-   24 & \cellcolor{blue!10}strategy & \cellcolor{blue!10}goal & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}stakeholder & \mybar{313} \\
-   50 & \cellcolor{blue!20}aye & \cellcolor{blue!20}absent & \cellcolor{blue!20}nay & \cellcolor{blue!20}councilman & \cellcolor{blue!20}khan & \cellcolor{blue!20}voting & \mybar{674} \\ 
-   22 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}million & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}forecast & \mybar{236} \\
-   47 & \cellcolor{blue!20}digest & \cellcolor{blue!20}authorize & \cellcolor{blue!20}inc & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}agreement & \mybar{215} \\
-   29 & \cellcolor{blue!20}chair & \cellcolor{blue!20}election & \cellcolor{blue!20}agenda & \cellcolor{blue!20}committee & \cellcolor{blue!20}speaker & \cellcolor{blue!20}ballot & \mybar{353} \\ 
-   57 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}arrest & \cellcolor{blue!80}suspect & \cellcolor{blue!80}crime & \mybar{1255} \\ 
+ 49 & \cellcolor{red!50}artist & \cellcolor{red!50}fun & \cellcolor{red!50}music & \cellcolor{red!50}beginner & \cellcolor{red!50}player & \cellcolor{red!50}prize & \mybar{4565} \\ 
+   46 & \cellcolor{red!40}chair & \cellcolor{red!40}subcommittee & \cellcolor{red!40}speaker & \cellcolor{red!40}agenda & \cellcolor{red!40}committee & \cellcolor{red!40}commission & \mybar{446} \\ 
+   16 & \cellcolor{red!30}motion & \cellcolor{red!30}second & \cellcolor{red!30}adjourn & \cellcolor{red!30}carry & \cellcolor{red!30}unanimous & \cellcolor{red!30}chairman & \mybar{419} \\ 
+   47 & \cellcolor{red!20}effluent & \cellcolor{red!20}inf & \cellcolor{red!20}eff & \cellcolor{red!20}infiltration & \cellcolor{red!20}discharge & \cellcolor{red!20}sludge & \mybar{751} \\ 
+   21 & \cellcolor{red!20}everybody & \cellcolor{red!20}think & \cellcolor{red!20}something & \cellcolor{red!20}thing & \cellcolor{red!20}try & \cellcolor{red!20}want & \mybar{2609} \\ 
+    2 & \cellcolor{red!20}influenza & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}patient & \cellcolor{red!20}tuberculosis & \cellcolor{red!20}hepatitis & \mybar{2980} \\
+   27 & \cellcolor{red!20}article & \cellcolor{red!20}subsection & \cellcolor{red!20}shall & \cellcolor{red!20}franchisee & \cellcolor{red!20}paragraph & \cellcolor{red!20}meaning & \mybar{658} \\ 
+   30 & \cellcolor{red!20}subcontractor & \cellcolor{red!20}bid & \cellcolor{red!20}bidder & \cellcolor{red!20}proposer & \cellcolor{red!20}subcontract & \cellcolor{red!20}bidding & \mybar{512} \\ 
+   12 & \cellcolor{red!10}craftsman & \cellcolor{red!10}architecture & \cellcolor{red!10}brick & \cellcolor{red!10}distinctive & \cellcolor{red!10}revival & \cellcolor{red!10}storefront & \mybar{1731} \\
+   24 & \cellcolor{red!10}mail & \cellcolor{red!10}fax & \cellcolor{red!10}application & \cellcolor{red!10}click & \cellcolor{red!10}applicant & \cellcolor{red!10}copy & \mybar{367} \\ 
+   34 & \cellcolor{red!10}playground & \cellcolor{red!10}recreation & \cellcolor{red!10}picnic & \cellcolor{red!10}park & \cellcolor{red!10}restroom & \cellcolor{red!10}zoo & \mybar{546} \\ 
+   19 & \cellcolor{red!10}setback & \cellcolor{red!10}variance & \cellcolor{red!10}zoning & \cellcolor{red!10}height & \cellcolor{red!10}yard & \cellcolor{red!10}accessory & \mybar{453} \\ 
+   26 & \cellcolor{red!10}mesa & \cellcolor{red!10}canyon & \cellcolor{red!10}via & \cellcolor{red!10}odd & \cellcolor{red!10}unidentified & \cellcolor{red!10}paradise & \mybar{1886} \\ 
+   23 & \cellcolor{red!10}bag & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}reusable & \cellcolor{red!10}vegetable & \cellcolor{red!10}bait & \mybar{2254} \\ 
+   20 & \cellcolor{red!10}customer & \cellcolor{red!10}renewable & \cellcolor{red!10}efficiency & \cellcolor{red!10}energy & \cellcolor{red!10}saving & \cellcolor{red!10}conservation & \mybar{652} \\ 
+   31 & \cellcolor{red!10}student & \cellcolor{red!10}teacher & \cellcolor{red!10}preschool & \cellcolor{red!10}academic & \cellcolor{red!10}kindergarten & \cellcolor{red!10}youth & \mybar{855} \\ 
+   28 & \cellcolor{red!10}garland & \cellcolor{red!10}assoc & \cellcolor{red!10}association & \cellcolor{red!10}firefighter & \cellcolor{red!10}duke & \cellcolor{red!10}xerox & \mybar{480} \\ 
+   50 & \cellcolor{red!10}trench & \cellcolor{red!10}manhole & \cellcolor{red!10}ductile & \cellcolor{red!10}excavation & \cellcolor{red!10}pipe & \cellcolor{red!10}grout & \mybar{1436} \\ 
+   32 & \cellcolor{red!10}canceled & \cellcolor{red!10}dwelling & \cellcolor{red!10}suite & \cellcolor{red!10}ave & \cellcolor{red!10}tad & \cellcolor{red!10}alteration & \mybar{491} \\ 
+   51 & \cellcolor{red!10}vent & \cellcolor{red!10}combustible & \cellcolor{red!10}flammable & \cellcolor{red!10}egress & \cellcolor{red!10}ceiling & \cellcolor{red!10}extinguisher & \mybar{1160} \\ 
+   44 & \cellcolor{red!10}findings & \cellcolor{red!10}tank & \cellcolor{red!10}string & \cellcolor{red!10}carcinogen & \cellcolor{red!10}lust & \cellcolor{red!10}sic & \mybar{255} \\ 
+   17 & \cellcolor{red!10}portfolio & \cellcolor{red!10}micron & \cellcolor{red!10}maturity & \cellcolor{red!10}treasury & \cellcolor{red!10}yield & \cellcolor{red!10}investment & \mybar{538} \\ 
+   48 & \cellcolor{red!10}contributor & \cellcolor{red!10}filer & \cellcolor{red!10}officeholder & \cellcolor{red!10}political & \cellcolor{red!10}rouge & \cellcolor{red!10}payee & \mybar{293} \\ 
+    5 & \cellcolor{red!10}draft & \cellcolor{red!10}comment & \cellcolor{red!10}review & \cellcolor{red!10}revision & \cellcolor{red!10}clarify & \cellcolor{red!10}process & \mybar{356} \\ 
+   37 & \cellcolor{red!10}endorsed & \cellcolor{red!10}endorse & \cellcolor{red!10}rescue & \cellcolor{red!10}assistant & \cellcolor{red!10}analyst & \cellcolor{red!10}technician & \mybar{355} \\ 
+    9 & \cellcolor{red!10}trust & \cellcolor{red!10}revocable & \cellcolor{red!10}planned & \cellcolor{red!10}mfr & \cellcolor{red!10}apportionment & \cellcolor{red!10}exhibit & \mybar{361} \\ 
+    8 & \cellcolor{red!10}imp & \cellcolor{red!10}assessor & \cellcolor{red!10}taxpayer & \cellcolor{red!10}petition & \cellcolor{red!10}preliminary & \cellcolor{red!10}determination & \mybar{91} \\ 
+   40 & \cellcolor{white}amt & \cellcolor{white}invoice & \cellcolor{white}acct & \cellcolor{white}exp & \cellcolor{white}unencumbered & \cellcolor{white}encumbrance & \mybar{116} \\ 
+   57 & \cellcolor{white}councilman & \cellcolor{white}introduced & \cellcolor{white}alderman & \cellcolor{white}whereas & \cellcolor{white}resolved & \cellcolor{white}councilwoman & \mybar{615} \\ 
+   11 & \cellcolor{white}obesity & \cellcolor{white}sugary & \cellcolor{white}epidemic & \cellcolor{white}drink & \cellcolor{white}calorie & \cellcolor{white}sensible & \mybar{96} \\ 
+   15 & \cellcolor{white}credit & \cellcolor{white}docket & \cellcolor{white}app & \cellcolor{white}post & \cellcolor{white}download & \cellcolor{white}month & \mybar{61} \\ 
+    3 & \cellcolor{white}wetland & \cellcolor{white}specie & \cellcolor{white}species & \cellcolor{white}vernal & \cellcolor{white}ecological & \cellcolor{white}riparian & \mybar{2293} \\ 
+   29 & \cellcolor{blue!10}margin & \cellcolor{blue!10}error & \cellcolor{blue!10}disability & \cellcolor{blue!10}speak & \cellcolor{blue!10}employed & \cellcolor{blue!10}language & \mybar{180} \\ 
+   43 & \cellcolor{white}medicare & \cellcolor{white}payroll & \cellcolor{white}blanket & \cellcolor{white}contractual & \cellcolor{white}undistributed & \cellcolor{white}dept & \mybar{322} \\ 
+   42 & \cellcolor{white}incumbent & \cellcolor{white}prep & \cellcolor{white}batch & \cellcolor{white}qualifier & \cellcolor{white}analytical & \cellcolor{white}examination & \mybar{1091} \\ 
+   55 & \cellcolor{blue!10}taxable & \cellcolor{blue!10}deed & \cellcolor{blue!10}res & \cellcolor{blue!10}homestead & \cellcolor{blue!10}value & \cellcolor{blue!10}book & \mybar{87} \\ 
+   22 & \cellcolor{blue!10}allocation & \cellcolor{blue!10}subtotal & \cellcolor{blue!10}admin & \cellcolor{blue!10}cost & \cellcolor{blue!10}yon & \cellcolor{blue!10}allocate & \mybar{190} \\ 
+   25 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}significant & \cellcolor{blue!10}adverse & \cellcolor{blue!10}environmental & \cellcolor{blue!10}measure & \mybar{217} \\
+   56 & \cellcolor{blue!10}savings & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}village & \cellcolor{blue!10}excise & \cellcolor{blue!10}ltd & \cellcolor{blue!10}matrix & \mybar{131} \\ 
+   33 & \cellcolor{blue!10}thence & \cellcolor{blue!10}east & \cellcolor{blue!10}south & \cellcolor{blue!10}corner & \cellcolor{blue!10}west & \cellcolor{blue!10}avenue & \mybar{340} \\ 
+    7 & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}bio & \cellcolor{blue!10}emission & \cellcolor{blue!10}coal & \cellcolor{blue!10}unmitigated & \cellcolor{blue!10}exhaust & \mybar{773} \\ 
+   18 & \cellcolor{blue!10}perm & \cellcolor{blue!10}queue & \cellcolor{blue!10}delay & \cellcolor{blue!10}peak & \cellcolor{blue!10}adj & \cellcolor{blue!10}flt & \mybar{187} \\ 
+   54 & \cellcolor{blue!10}license & \cellcolor{blue!10}licensee & \cellcolor{blue!10}citation & \cellcolor{blue!10}tow & \cellcolor{blue!10}fee & \cellcolor{blue!10}taxicab & \mybar{710} \\ 
+    6 & \cellcolor{blue!10}race & \cellcolor{blue!10}householder & \cellcolor{blue!10}islander & \cellcolor{blue!10}census & \cellcolor{blue!10}occupied & \cellcolor{blue!10}female & \mybar{160} \\ 
+   60 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}route & \cellcolor{blue!10}sidewalk & \cellcolor{blue!10}bicyclist & \mybar{561} \\ 
+   14 & \cellcolor{blue!10}accomplishment & \cellcolor{blue!10}grantee & \cellcolor{blue!10}narrative & \cellcolor{blue!10}outcome & \cellcolor{blue!10}grant & \cellcolor{blue!10}recipient & \mybar{255} \\
+   53 & \cellcolor{blue!10}applied & \cellcolor{blue!10}col & \cellcolor{blue!10}dist & \cellcolor{blue!10}occupancy & \cellcolor{blue!10}monoxide & \cellcolor{blue!10}valuation & \mybar{128} \\ 
+    4 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}procedure & \cellcolor{blue!10}timely & \cellcolor{blue!10}implemented & \cellcolor{blue!10}oversight & \mybar{472} \\
+   35 & \cellcolor{blue!10}redemption & \cellcolor{blue!10}bond & \cellcolor{blue!10}increment & \cellcolor{blue!10}obligation & \cellcolor{blue!10}proceeds & \cellcolor{blue!10}lease & \mybar{339} \\
+   39 & \cellcolor{blue!10}downtown & \cellcolor{blue!10}mixed & \cellcolor{blue!10}retail & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}orient & \cellcolor{blue!10}density & \mybar{419} \\ 
+   10 & \cellcolor{blue!10}grievance & \cellcolor{blue!10}deductible & \cellcolor{blue!10}coinsurance & \cellcolor{blue!10}dependent & \cellcolor{blue!10}employee & \cellcolor{blue!10}copay & \mybar{583} \\
+   38 & \cellcolor{blue!10}para & \cellcolor{blue!10}persona & \cellcolor{blue!10}horas & \cellcolor{blue!10}bud & \cellcolor{blue!10}contracted & \cellcolor{blue!10}ante & \mybar{1334} \\ 
+   36 & \cellcolor{blue!10}respondent & \cellcolor{blue!10}compare & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}appendix & \cellcolor{blue!10}satisfied & \mybar{696} \\ 
+   45 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}asset & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}liability & \cellcolor{blue!10}financial & \cellcolor{blue!10}statement & \mybar{235} \\
+   41 & \cellcolor{blue!20}complainant & \cellcolor{blue!20}allegation & \cellcolor{blue!20}defendant & \cellcolor{blue!20}offender & \cellcolor{blue!20}commander & \cellcolor{blue!20}complaint & \mybar{1695} \\
+   52 & \cellcolor{blue!20}homeless & \cellcolor{blue!20}homelessness & \cellcolor{blue!20}affordable & \cellcolor{blue!20}supportive & \cellcolor{blue!20}housing & \cellcolor{blue!20}affordability & \mybar{394} \\
+   58 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}adopted & \cellcolor{blue!20}balance & \cellcolor{blue!20}transfer & \cellcolor{blue!20}expenditure & \mybar{176} \\
+   13 & \cellcolor{blue!20}initiative & \cellcolor{blue!20}outreach & \cellcolor{blue!20}strategy & \cellcolor{blue!20}leadership & \cellcolor{blue!20}engagement & \cellcolor{blue!20}focus & \mybar{502} \\
+    1 & \cellcolor{blue!30}absent & \cellcolor{blue!30}preside & \cellcolor{blue!30}authorize & \cellcolor{blue!30}ordained & \cellcolor{blue!30}int & \cellcolor{blue!30}tag & \mybar{377} \\ 
+   59 & \cellcolor{blue!80}burglary & \cellcolor{blue!80}robbery & \cellcolor{blue!80}theft & \cellcolor{blue!80}homicide & \cellcolor{blue!80}murder & \cellcolor{blue!80}gunshot & \mybar{945} \\ 
    \hline
@@
 \endgroup
-\caption{Top words from a structural topic model with 60 topics and FREX scoring.
-Colors depict partisanship based on coefficient size.
-White cells are non-significant topics.
-Based on data preprocessed with the classifier.}
+\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
+\label{tabSTMtopwords60}
 \end{table}

### 2019-05-17 07_topicModel/02_stm_results.R

@@ -78,8 +78,8 @@ topwords3 <- topwords3[order(df$coef, decreasing = T),]
 #remove the last topic
 topwords3 <- topwords3[,-8]
 
-xtTopwords <- print(xtable(topwords3, caption = "NEW: Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.",
-                           label = "tabSTMtopwords60New"), 
+xtTopwords <- print(xtable(topwords3, caption = "Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.",
+                           label = "tabSTMtopwords60"), 
                     sanitize.text.function = identity,
                     size = "scriptsize",
                     include.rownames = FALSE)
@@ -89,5 +89,5 @@ xtTopwords <- str_replace(xtTopwords, "& Tokens assigned", "& \\\\multicolumn{2}
 xtTopwords <- str_replace(xtTopwords, "\nTopic &", "\n \\\\# &")
 
 
-writeLines(xtTopwords, con = '../paper/tables/stmTopWords60New.tex')
+writeLines(xtTopwords, con = '../paper/tables/stmTopWords60.tex')
 

### 2019-05-17 10_otherTables/tabCitiesStatesParties.R

@@ -14,9 +14,9 @@ cities_states_parties <- as.data.frame(cities_states_parties)
 cities_states_parties <- spread(cities_states_parties, party, Freq)
 
 xtTopwords <- print(xtable(cities_states_parties, 
-                           caption = "Descriptive statistics on the partisanship of the cities in the corpus."), 
+                           caption = "Descriptive statistics on the partisanship of the cities in the corpus.",
+                           label = "tab:cityparties"),
                     sanitize.text.function = identity,
-                    label = "tabCitiesStatesParties",
                     #size = "scriptsize",
                     include.rownames = FALSE)
 

### 2019-05-17 paper/manuscript_paNote.tex
new results
highlighted changes in the results

@@
 Many of the topics associated with Democrats fit with what we understand to be national party priorities.
-Topic 21, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
-Similarly, employee rights are represented in Topic 47.
-Democrats also exhibit a strong preference for words related to public finances, such as Topic 32 ('budget', 'revenue', 'expenditure') as well as Topic 19 ('debt', 'bond', 'financial').
+Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
+Similarly, employee rights are represented in topics \textbf{10} and \textbf{29} \textbf{[DEBATABLE]}.
+Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), \textbf{topic 45 ('asset', 'actuarial', 'liability', 'financial')}, \textbf{topic 35 ('bond', 'obligation', 'proceeds')} as well as \textbf{topic 55 ('taxable', 'deed', 'value')}.
 We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
 This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 55 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
+A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') depicts Democrats' complicated relationship with law enforcement \textbf{[This used to be about police as well, but now it's more of a crime topic]}.
 On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
 On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}.
-Finally, Democrats also focus more on the deliberative process of policymaking, as topics 31 ('agenda', 'committee'), 34 ( `comment', `draft', `feedback'), 48 (`absent', `aye', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.
-This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
+Finally, Democrats also focus more on the deliberative process of policymaking, as \underline{topics 31 ('agenda', 'committee') \textbf{[This is now the second-most REPUBLICAN topic 46]}}, \underline{34 (`comment', `draft', `feedback') \textbf{[This is now REPUBLICAN topic 5]}}, \textbf{1} (`absent', `preside', `authorized'), and \textbf{4} ('audit', 'procedure', 'oversight') attest to.
+\textbf{[Republicans also have topic 16]}  This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
 
 City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government.
-Basic utilities such as energy (Topic 7), fire protection (Topic 17), drinking water (53), and garbage removal (Topic 49) are included among those topics that are more prevalent in cities with Democratic mayors.
-Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 42 ('breastfeed', 'infection', 'mosquito' -- and so, essentially, about the Zika virus), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.
+Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51} \textbf{[This topic has changed a lot.]}), \underline{drinking water (53) \textbf{[topic missing]}}, and \underline{garbage removal (Topic 49) \textbf{[topic missing]}} are included among those topics that are more prevalent in cities with Democratic mayors.
+Similarly, protecting citizens from natural disasters is a focus in \underline{topics 1 ('storm', 'runoff', 'drainage') \textbf{[topic missing]}} and \textbf{2} ('influenza', 'infection', 'vaccine' \textbf{[This is not about Zika anymore, but infectious diseases in general.]}), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.
 
@@
 
-\input{tables/stmTopWords60.tex} %\ref{tabSTMtopwords2}
-\input{tables/stmTopWords60New.tex}
+\input{tables/stmTopWords60.tex}
+\input{tables/stmTopWords60_OLD.tex} %\ref{tabSTMtopwords2}
 

### 2019-05-20 paper/tables/stmTopWords120_2.tex
added new results for model with 120 topics

--- 2018-08-05 paper/tables/stmTopWords120_2.tex
@@
-% latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Sun Aug  5 19:55:00 2018
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Mon May 20 11:38:16 2019
 \begin{table}[ht]
@@
   \hline
- 34 & \cellcolor{white}plan & \cellcolor{white}planning & \cellcolor{white}comprehensive & \cellcolor{white}master & \cellcolor{white}review & \cellcolor{white}amendment & \mybar{42} \\ 
-   82 & \cellcolor{white}com & \cellcolor{white}mar & \cellcolor{white}spec & \cellcolor{white}jun & \cellcolor{white}est & \cellcolor{white}comm & \mybar{1388} \\ 
-   22 & \cellcolor{white}server & \cellcolor{white}software & \cellcolor{white}wireless & \cellcolor{white}technology & \cellcolor{white}desktop & \cellcolor{white}broadband & \mybar{430} \\ 
-   80 & \cellcolor{white}artist & \cellcolor{white}art & \cellcolor{white}artwork & \cellcolor{white}exhibition & \cellcolor{white}artistic & \cellcolor{white}sculpture & \mybar{1099} \\ 
-  113 & \cellcolor{white}trench & \cellcolor{white}thickness & \cellcolor{white}compaction & \cellcolor{white}concrete & \cellcolor{white}slab & \cellcolor{white}excavation & \mybar{766} \\ 
-   87 & \cellcolor{white}respondent & \cellcolor{white}survey & \cellcolor{white}census & \cellcolor{white}racial & \cellcolor{white}demographic & \cellcolor{white}score & \mybar{427} \\ 
-   83 & \cellcolor{white}homeless & \cellcolor{white}homelessness & \cellcolor{white}supportive & \cellcolor{white}client & \cellcolor{white}transitional & \cellcolor{white}encampment & \mybar{229} \\
-   20 & \cellcolor{white}noise & \cellcolor{white}fugitive & \cellcolor{white}receptor & \cellcolor{white}exhaust & \cellcolor{white}vibration & \cellcolor{white}emission & \mybar{376} \\ 
-   35 & \cellcolor{white}landlord & \cellcolor{white}tenant & \cellcolor{white}owner & \cellcolor{white}property & \cellcolor{white}rent & \cellcolor{white}lien & \mybar{205} \\ 
-  105 & \cellcolor{white}beach & \cellcolor{white}orange & \cellcolor{white}arena & \cellcolor{white}rainier & \cellcolor{white}ocean & \cellcolor{white}resort & \mybar{457} \\ 
-    2 & \cellcolor{blue!10}yon & \cellcolor{blue!10}bay & \cellcolor{blue!10}gen & \cellcolor{blue!10}sou & \cellcolor{blue!10}coliseum & \cellcolor{blue!10}estuary & \mybar{385} \\ 
-    6 & \cellcolor{white}redevelopment & \cellcolor{white}land & \cellcolor{white}developer & \cellcolor{white}parcel & \cellcolor{white}development & \cellcolor{white}area & \mybar{70} \\ 
-  104 & \cellcolor{white}riparian & \cellcolor{white}wetland & \cellcolor{white}habitat & \cellcolor{white}marsh & \cellcolor{white}floodplain & \cellcolor{white}grassland & \mybar{968} \\ 
-   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}taxable & \cellcolor{white}deduction & \cellcolor{white}levy & \cellcolor{white}taxpayer & \mybar{172} \\ 
-   68 & \cellcolor{white}economy & \cellcolor{white}workforce & \cellcolor{white}economic & \cellcolor{white}sector & \cellcolor{white}industry & \cellcolor{white}innovation & \mybar{332} \\ 
-   28 & \cellcolor{white}figure & \cellcolor{white}table & \cellcolor{white}scenario & \cellcolor{white}margin & \cellcolor{white}analysis & \cellcolor{white}appendix & \mybar{207} \\ 
-  110 & \cellcolor{white}bond & \cellcolor{white}maturity & \cellcolor{white}debt & \cellcolor{white}issuer & \cellcolor{white}redemption & \cellcolor{white}obligation & \mybar{232} \\ 
-  102 & \cellcolor{white}sidewalk & \cellcolor{white}curb & \cellcolor{white}pole & \cellcolor{white}crosswalk & \cellcolor{white}ramp & \cellcolor{white}sign & \mybar{237} \\ 
-  118 & \cellcolor{blue!10}project & \cellcolor{blue!10}phase & \cellcolor{blue!10}construction & \cellcolor{blue!10}completion & \cellcolor{blue!10}improvement & \cellcolor{blue!10}complete & \mybar{45} \\
-   78 & \cellcolor{blue!10}parking & \cellcolor{blue!10}tow & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}garage & \cellcolor{blue!10}car & \cellcolor{blue!10}motor & \mybar{210} \\ 
-   71 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}retiree & \cellcolor{blue!10}retirement & \cellcolor{blue!10}pension & \cellcolor{blue!10}deductible & \cellcolor{blue!10}unfunded & \mybar{239} \\
-   91 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}forestry & \cellcolor{blue!10}deer & \cellcolor{blue!10}shrub & \cellcolor{blue!10}planting & \mybar{1240} \\ 
-  114 & \cellcolor{blue!10}incumbent & \cellcolor{blue!10}exam & \cellcolor{blue!10}supervision & \cellcolor{blue!10}supervise & \cellcolor{blue!10}examination & \cellcolor{blue!10}ability & \mybar{432} \\
-   16 & \cellcolor{blue!10}park & \cellcolor{blue!10}recreation & \cellcolor{blue!10}playground & \cellcolor{blue!10}zoo & \cellcolor{blue!10}trail & \cellcolor{blue!10}picnic & \mybar{290} \\ 
-   53 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}boat & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}maritime & \cellcolor{blue!10}dock & \cellcolor{blue!10}barge & \mybar{800} \\ 
-   76 & \cellcolor{blue!10}felony & \cellcolor{blue!10}violent & \cellcolor{blue!10}offender & \cellcolor{blue!10}gang & \cellcolor{blue!10}theft & \cellcolor{blue!10}inmate & \mybar{783} \\ 
-    4 & \cellcolor{blue!10}courtyard & \cellcolor{blue!10}realm & \cellcolor{blue!10}design & \cellcolor{blue!10}facade & \cellcolor{blue!10}proponent & \cellcolor{blue!10}articulation & \mybar{608} \\
-  100 & \cellcolor{blue!10}division & \cellcolor{blue!10}manage & \cellcolor{blue!10}staffing & \cellcolor{blue!10}oversee & \cellcolor{blue!10}management & \cellcolor{blue!10}analyst & \mybar{100} \\
-   97 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}alternative & \cellcolor{blue!10}propose & \mybar{132} \\
-   11 & \cellcolor{blue!10}historic & \cellcolor{blue!10}landmark & \cellcolor{blue!10}revival & \cellcolor{blue!10}archaeological & \cellcolor{blue!10}preservation & \cellcolor{blue!10}historical & \mybar{876} \\
-   77 & \cellcolor{blue!10}million & \cellcolor{blue!10}fiscal & \cellcolor{blue!10}forecast & \cellcolor{blue!10}revenue & \cellcolor{blue!10}quarter & \cellcolor{blue!10}billion & \mybar{138} \\ 
-   74 & \cellcolor{blue!10}board & \cellcolor{blue!10}chairperson & \cellcolor{blue!10}secretary & \cellcolor{blue!10}member & \cellcolor{blue!10}appoint & \cellcolor{blue!10}executive & \mybar{118} \\
-   47 & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complainant & \cellcolor{blue!10}misconduct & \cellcolor{blue!10}bias & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \mybar{580} \\
-   92 & \cellcolor{blue!10}sick & \cellcolor{blue!10}employee & \cellcolor{blue!10}wage & \cellcolor{blue!10}overtime & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{260} \\ 
-   10 & \cellcolor{blue!10}ave & \cellcolor{blue!10}avenue & \cellcolor{blue!10}south & \cellcolor{blue!10}east & \cellcolor{blue!10}west & \cellcolor{blue!10}blvd & \mybar{189} \\ 
-  112 & \cellcolor{blue!10}grant & \cellcolor{blue!10}loan & \cellcolor{blue!10}funding & \cellcolor{blue!10}program & \cellcolor{blue!10}recipient & \cellcolor{blue!10}federal & \mybar{85} \\ 
-   56 & \cellcolor{blue!10}downtown & \cellcolor{blue!10}mall & \cellcolor{blue!10}midtown & \cellcolor{blue!10}uptown & \cellcolor{blue!10}hotel & \cellcolor{blue!10}shopping & \mybar{414} \\ 
-   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}successor & \cellcolor{blue!10}oversight & \cellcolor{blue!10}attachment & \cellcolor{blue!10}describe & \mybar{125} \\ 
-   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}transit & \cellcolor{blue!10}bicyclist & \cellcolor{blue!10}lane & \cellcolor{blue!10}bus & \mybar{315} \\ 
-   62 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}income & \cellcolor{blue!10}household & \cellcolor{blue!10}moderate & \mybar{188} \\
-   99 & \cellcolor{blue!10}memorandum & \cellcolor{blue!10}resolution & \cellcolor{blue!10}council & \cellcolor{blue!10}legislation & \cellcolor{blue!10}entitle & \cellcolor{blue!10}commission & \mybar{173} \\
-   19 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}accounting & \cellcolor{blue!10}asset & \cellcolor{blue!10}statement & \cellcolor{blue!10}financial & \cellcolor{blue!10}net & \mybar{156} \\
-  103 & \cellcolor{blue!10}permission & \cellcolor{blue!10}ayes & \cellcolor{blue!10}correspondence & \cellcolor{blue!10}bid & \cellcolor{blue!10}smith & \cellcolor{blue!10}demolition & \mybar{203} \\
-  107 & \cellcolor{blue!10}appropriated & \cellcolor{blue!10}dollars & \cellcolor{blue!10}thousand & \cellcolor{blue!10}ongoing & \cellcolor{blue!10}matrix & \cellcolor{blue!10}justification & \mybar{117} \\
-   12 & \cellcolor{blue!10}approach & \cellcolor{blue!10}difficult & \cellcolor{blue!10}achieve & \cellcolor{blue!10}challenge & \cellcolor{blue!10}critical & \cellcolor{blue!10}often & \mybar{257} \\
-   46 & \cellcolor{blue!10}variance & \cellcolor{blue!10}fence & \cellcolor{blue!10}setback & \cellcolor{blue!10}exception & \cellcolor{blue!10}yard & \cellcolor{blue!10}applicant & \mybar{136} \\ 
-   90 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}procedure & \cellcolor{blue!10}internal & \cellcolor{blue!10}auditing & \cellcolor{blue!10}documentation & \mybar{226} \\
-   64 & \cellcolor{blue!10}density & \cellcolor{blue!10}urban & \cellcolor{blue!10}corridor & \cellcolor{blue!10}village & \cellcolor{blue!10}orient & \cellcolor{blue!10}transit & \mybar{165} \\ 
-   21 & \cellcolor{blue!10}goal & \cellcolor{blue!10}strategy & \cellcolor{blue!10}outreach & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}implementation & \mybar{105} \\
-   73 & \cellcolor{blue!10}parish & \cellcolor{blue!10}rouge & \cellcolor{blue!10}baton & \cellcolor{blue!10}hogan & \cellcolor{blue!10}councilman & \cellcolor{blue!10}thereto & \mybar{482} \\ 
-   29 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}discussion & \cellcolor{blue!10}feedback & \cellcolor{blue!10}discuss & \cellcolor{blue!10}presentation & \mybar{168} \\
-   32 & \cellcolor{blue!10}budget & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}appropriation & \cellcolor{blue!10}fund & \cellcolor{blue!10}endorse & \cellcolor{blue!10}balance & \mybar{129} \\
-   54 & \cellcolor{blue!10}aye & \cellcolor{blue!10}absent & \cellcolor{blue!10}khan & \cellcolor{blue!10}nay & \cellcolor{blue!10}berry & \cellcolor{blue!10}voting & \mybar{344} \\ 
-   39 & \cellcolor{blue!10}mode & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}tab & \cellcolor{blue!10}focus & \cellcolor{blue!10}else & \cellcolor{blue!10}alt & \mybar{117} \\ 
-  109 & \cellcolor{blue!10}auburn & \cellcolor{blue!10}buffalo & \cellcolor{blue!10}ward & \cellcolor{blue!10}brown & \cellcolor{blue!10}announce & \cellcolor{blue!10}casino & \mybar{177} \\ 
-   50 & \cellcolor{blue!10}news & \cellcolor{blue!10}warren & \cellcolor{blue!10}lovely & \cellcolor{blue!10}release & \cellcolor{blue!10}leader & \cellcolor{blue!10}proud & \mybar{498} \\ 
-   79 & \cellcolor{blue!20}digest & \cellcolor{blue!20}proposal & \cellcolor{blue!20}sander & \cellcolor{blue!20}reappoints & \cellcolor{blue!20}metropolitan & \cellcolor{blue!20}gray & \mybar{236} \\
-   27 & \cellcolor{blue!20}bankruptcy & \cellcolor{blue!20}plaintiff & \cellcolor{blue!20}creditor & \cellcolor{blue!20}trial & \cellcolor{blue!20}court & \cellcolor{blue!20}supreme & \mybar{810} \\ 
-   31 & \cellcolor{blue!20}agenda & \cellcolor{blue!20}speaker & \cellcolor{blue!20}item & \cellcolor{blue!20}committee & \cellcolor{blue!20}chair & \cellcolor{blue!20}divided & \mybar{146} \\ 
-   48 & \cellcolor{blue!20}consolidated & \cellcolor{blue!20}contingency & \cellcolor{blue!20}reinvestment & \cellcolor{blue!20}inc & \cellcolor{blue!20}contract & \cellcolor{blue!20}authorize & \mybar{134} \\
-   55 & \cellcolor{blue!80}suspect & \cellcolor{blue!80}shoot & \cellcolor{blue!80}fatal & \cellcolor{blue!80}homicide & \cellcolor{blue!80}stopper & \cellcolor{blue!80}pronounce & \mybar{512} \\ 
+ 29 & \cellcolor{blue!10}labor & \cellcolor{blue!10}worker & \cellcolor{blue!10}force & \cellcolor{blue!10}unemployed & \cellcolor{blue!10}earnings & \cellcolor{blue!10}civilian & \mybar{80} \\ 
+  111 & \cellcolor{blue!10}discharge & \cellcolor{blue!10}pollutant & \cellcolor{blue!10}inspection & \cellcolor{blue!10}inspect & \cellcolor{blue!10}pollution & \cellcolor{blue!10}inspector & \mybar{109} \\
+   68 & \cellcolor{blue!10}contractual & \cellcolor{blue!10}parts & \cellcolor{blue!10}duke & \cellcolor{blue!10}outside & \cellcolor{blue!10}postage & \cellcolor{blue!10}receipts & \mybar{274} \\ 
+   77 & \cellcolor{blue!10}curb & \cellcolor{blue!10}pavement & \cellcolor{blue!10}sidewalk & \cellcolor{blue!10}ramp & \cellcolor{blue!10}gutter & \cellcolor{blue!10}asphalt & \mybar{390} \\ 
+   65 & \cellcolor{blue!10}draft & \cellcolor{blue!10}update & \cellcolor{blue!10}process & \cellcolor{blue!10}review & \cellcolor{blue!10}staff & \cellcolor{blue!10}progress & \mybar{67} \\ 
+   24 & \cellcolor{blue!10}landlord & \cellcolor{blue!10}tenant & \cellcolor{blue!10}renewal & \cellcolor{blue!10}rent & \cellcolor{blue!10}lease & \cellcolor{blue!10}expired & \mybar{255} \\ 
+  106 & \cellcolor{blue!10}consultant & \cellcolor{blue!10}proposer & \cellcolor{blue!10}procurement & \cellcolor{blue!10}contract & \cellcolor{blue!10}firm & \cellcolor{blue!10}subcontractor & \mybar{179} \\
+   43 & \cellcolor{blue!10}blanket & \cellcolor{blue!10}medicare & \cellcolor{blue!10}payroll & \cellcolor{blue!10}premium & \cellcolor{blue!10}undistributed & \cellcolor{blue!10}refund & \mybar{107} \\
+  103 & \cellcolor{white}urban & \cellcolor{white}mixed & \cellcolor{white}density & \cellcolor{white}redevelopment & \cellcolor{white}development & \cellcolor{white}industrial & \mybar{115} \\ 
+   89 & \cellcolor{blue!10}taxable & \cellcolor{blue!10}res & \cellcolor{blue!10}deed & \cellcolor{blue!10}value & \cellcolor{blue!10}homestead & \cellcolor{blue!10}star & \mybar{41} \\ 
+   83 & \cellcolor{blue!10}building & \cellcolor{blue!10}demolition & \cellcolor{blue!10}story & \cellcolor{blue!10}demolish & \cellcolor{blue!10}floor & \cellcolor{blue!10}build & \mybar{82} \\ 
+  119 & \cellcolor{blue!10}cost & \cellcolor{blue!10}estimate & \cellcolor{blue!10}estimated & \cellcolor{blue!10}initial & \cellcolor{blue!10}costs & \cellcolor{blue!10}change & \mybar{52} \\ 
+  109 & \cellcolor{blue!10}respondent & \cellcolor{blue!10}satisfied & \cellcolor{blue!10}dissatisfied & \cellcolor{blue!10}survey & \cellcolor{blue!10}satisfaction & \cellcolor{blue!10}disagree & \mybar{403} \\
+   64 & \cellcolor{blue!10}must & \cellcolor{blue!10}signature & \cellcolor{blue!10}copy & \cellcolor{blue!10}application & \cellcolor{blue!10}applicant & \cellcolor{blue!10}submission & \mybar{139} \\
+   26 & \cellcolor{blue!10}tax & \cellcolor{blue!10}deduction & \cellcolor{blue!10}amt & \cellcolor{blue!10}assessed & \cellcolor{blue!10}bill & \cellcolor{blue!10}abatement & \mybar{171} \\ 
+   78 & \cellcolor{blue!10}yes & \cellcolor{blue!10}worksheet & \cellcolor{blue!10}text & \cellcolor{blue!10}pic & \cellcolor{blue!10}font & \cellcolor{blue!10}button & \mybar{476} \\ 
+    7 & \cellcolor{blue!10}greenhouse & \cellcolor{blue!10}emission & \cellcolor{blue!10}coal & \cellcolor{blue!10}climate & \cellcolor{blue!10}ozone & \cellcolor{blue!10}dioxide & \mybar{334} \\ 
+   54 & \cellcolor{blue!10}parking & \cellcolor{blue!10}tow & \cellcolor{blue!10}taxi & \cellcolor{blue!10}vehicle & \cellcolor{blue!10}shuttle & \cellcolor{blue!10}passenger & \mybar{236} \\ 
+   41 & \cellcolor{blue!10}assistant & \cellcolor{blue!10}analyst & \cellcolor{blue!10}technician & \cellcolor{blue!10}aide & \cellcolor{blue!10}specialist & \cellcolor{blue!10}asst & \mybar{119} \\ 
+   22 & \cellcolor{blue!10}allocation & \cellcolor{blue!10}val & \cellcolor{blue!10}cove & \cellcolor{blue!10}acct & \cellcolor{blue!10}glen & \cellcolor{blue!10}subtotal & \mybar{79} \\ 
+   63 & \cellcolor{blue!10}fee & \cellcolor{blue!10}charge & \cellcolor{blue!10}license & \cellcolor{blue!10}reservation & \cellcolor{blue!10}surcharge & \cellcolor{blue!10}refundable & \mybar{143} \\
+  117 & \cellcolor{blue!10}delay & \cellcolor{blue!10}perm & \cellcolor{blue!10}queue & \cellcolor{blue!10}peak & \cellcolor{blue!10}flt & \cellcolor{blue!10}detector & \mybar{113} \\ 
+    4 & \cellcolor{blue!10}datum & \cellcolor{blue!10}database & \cellcolor{blue!10}copyright & \cellcolor{blue!10}accuracy & \cellcolor{blue!10}data & \cellcolor{blue!10}compile & \mybar{193} \\ 
+   45 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}auditing & \cellcolor{blue!10}internal & \cellcolor{blue!10}implemented & \cellcolor{blue!10}procedure & \mybar{222} \\
+  100 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}significant & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significance & \cellcolor{blue!10}unavoidable & \mybar{136} \\
+   88 & \cellcolor{blue!10}gender & \cellcolor{blue!10}discrimination & \cellcolor{blue!10}transgender & \cellcolor{blue!10}immigrant & \cellcolor{blue!10}immigration & \cellcolor{blue!10}religion & \mybar{859} \\
+    9 & \cellcolor{blue!10}district & \cellcolor{blue!10}zoning & \cellcolor{blue!10}maker & \cellcolor{blue!10}vacancy & \cellcolor{blue!10}speaker & \cellcolor{blue!10}planner & \mybar{45} \\ 
+   12 & \cellcolor{blue!10}artist & \cellcolor{blue!10}artwork & \cellcolor{blue!10}art & \cellcolor{blue!10}arts & \cellcolor{blue!10}mural & \cellcolor{blue!10}sculpture & \mybar{1055} \\ 
+   94 & \cellcolor{blue!10}contracted & \cellcolor{blue!10}encumbrance & \cellcolor{blue!10}unencumbered & \cellcolor{blue!10}exp & \cellcolor{blue!10}expend & \cellcolor{blue!10}bud & \mybar{71} \\ 
+  110 & \cellcolor{blue!10}rouge & \cellcolor{blue!10}parish & \cellcolor{blue!10}baton & \cellcolor{blue!10}thereto & \cellcolor{blue!10}sewerage & \cellcolor{blue!10}adjudicate & \mybar{464} \\ 
+   46 & \cellcolor{blue!10}commissioner & \cellcolor{blue!10}chair & \cellcolor{blue!10}commission & \cellcolor{blue!10}committee & \cellcolor{blue!10}briefing & \cellcolor{blue!10}advisory & \mybar{187} \\
+   85 & \cellcolor{blue!10}sch & \cellcolor{blue!10}min & \cellcolor{blue!10}tin & \cellcolor{blue!10}hump & \cellcolor{blue!10}carpool & \cellcolor{blue!10}qua & \mybar{390} \\ 
+   15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}allege & \cellcolor{blue!10}complaint & \cellcolor{blue!10}doc & \cellcolor{blue!10}misconduct & \mybar{963} \\
+   30 & \cellcolor{blue!10}incumbent & \cellcolor{blue!10}examination & \cellcolor{blue!10}supervision & \cellcolor{blue!10}knowledge & \cellcolor{blue!10}exam & \cellcolor{blue!10}ability & \mybar{410} \\
+  107 & \cellcolor{blue!10}savings & \cellcolor{blue!10}ltd & \cellcolor{blue!10}village & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}excise & \cellcolor{blue!10}costs & \mybar{81} \\ 
+   72 & \cellcolor{blue!10}imp & \cellcolor{blue!10}burglary & \cellcolor{blue!10}theft & \cellcolor{blue!10}testify & \cellcolor{blue!10}petitioner & \cellcolor{blue!10}mischief & \mybar{116} \\ 
+   60 & \cellcolor{blue!10}bike & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bicyclist & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}route & \cellcolor{blue!10}mobility & \mybar{336} \\ 
+   82 & \cellcolor{blue!10}accomplishment & \cellcolor{blue!10}narrative & \cellcolor{blue!10}grantee & \cellcolor{blue!10}outcome & \cellcolor{blue!10}objective & \cellcolor{blue!10}mod & \mybar{101} \\
+   36 & \cellcolor{blue!10}decline & \cellcolor{blue!10}trend & \cellcolor{blue!10}recession & \cellcolor{blue!10}average & \cellcolor{blue!10}rate & \cellcolor{blue!10}percentage & \mybar{265} \\ 
+   52 & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}supportive & \cellcolor{blue!10}consolidated & \cellcolor{blue!10}transitional & \cellcolor{blue!10}counseling & \mybar{193} \\
+    1 & \cellcolor{blue!10}alderman & \cellcolor{blue!10}resolved & \cellcolor{blue!10}whereas & \cellcolor{blue!10}resolution & \cellcolor{blue!10}authorizing & \cellcolor{blue!10}authorize & \mybar{245} \\
+   92 & \cellcolor{blue!10}concept & \cellcolor{blue!10}design & \cellcolor{blue!10}realm & \cellcolor{blue!10}visual & \cellcolor{blue!10}character & \cellcolor{blue!10}conceptual & \mybar{433} \\ 
+   71 & \cellcolor{blue!10}bond & \cellcolor{blue!10}obligation & \cellcolor{blue!10}proceeds & \cellcolor{blue!10}redemption & \cellcolor{blue!10}debt & \cellcolor{blue!10}series & \mybar{174} \\ 
+   67 & \cellcolor{blue!10}dist & \cellcolor{blue!10}applied & \cellcolor{blue!10}col & \cellcolor{blue!10}occupancy & \cellcolor{blue!10}valuation & \cellcolor{blue!10}monoxide & \mybar{62} \\ 
+   25 & \cellcolor{blue!10}scenario & \cellcolor{blue!10}figure & \cellcolor{blue!10}appendix & \cellcolor{blue!10}assume & \cellcolor{blue!10}assumption & \cellcolor{blue!10}model & \mybar{162} \\ 
+   38 & \cellcolor{blue!10}horas & \cellcolor{blue!10}persona & \cellcolor{blue!10}para & \cellcolor{blue!10}yon & \cellcolor{blue!10}sou & \cellcolor{blue!10}ante & \mybar{1350} \\ 
+   14 & \cellcolor{blue!10}federal & \cellcolor{blue!10}agency & \cellcolor{blue!10}entity & \cellcolor{blue!10}recipient & \cellcolor{blue!10}grant & \cellcolor{blue!10}eligible & \mybar{90} \\ 
+   56 & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}marina & \cellcolor{blue!10}beach & \cellcolor{blue!10}port & \cellcolor{blue!10}boat & \mybar{844} \\ 
+   61 & \cellcolor{blue!10}revenue & \cellcolor{blue!10}balance & \cellcolor{blue!10}expenditure & \cellcolor{blue!10}reserve & \cellcolor{blue!10}forecast & \cellcolor{blue!10}budget & \mybar{101} \\
+   75 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}asset & \cellcolor{blue!10}liability & \cellcolor{blue!10}assets & \cellcolor{blue!10}statement & \cellcolor{blue!10}pension & \mybar{142} \\
+   37 & \cellcolor{blue!10}endorse & \cellcolor{blue!10}endorsed & \cellcolor{blue!10}budget & \cellcolor{blue!10}proposed & \cellcolor{blue!10}adopted & \cellcolor{blue!10}adopt & \mybar{111} \\ 
+   69 & \cellcolor{blue!10}tree & \cellcolor{blue!10}planned & \cellcolor{blue!10}circumference & \cellcolor{blue!10}gross & \cellcolor{blue!10}density & \cellcolor{blue!10}infill & \mybar{211} \\ 
+   90 & \cellcolor{blue!10}councilman & \cellcolor{blue!10}introduced & \cellcolor{blue!10}ordain & \cellcolor{blue!10}ordinance & \cellcolor{blue!10}digest & \cellcolor{blue!10}yea & \mybar{244} \\ 
+   97 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}grievance & \cellcolor{blue!10}employee & \cellcolor{blue!10}retirement & \cellcolor{blue!10}bargaining & \cellcolor{blue!10}actuary & \mybar{250} \\
+   39 & \cellcolor{blue!10}affordable & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordability & \cellcolor{blue!10}homeowner & \cellcolor{blue!10}income & \cellcolor{blue!10}bedroom & \mybar{150} \\
+   55 & \cellcolor{blue!10}ave & \cellcolor{blue!10}combo & \cellcolor{blue!10}blossom & \cellcolor{blue!10}pearl & \cellcolor{blue!10}cir & \cellcolor{blue!10}olive & \mybar{1091} \\ 
+   13 & \cellcolor{blue!20}strategy & \cellcolor{blue!20}goal & \cellcolor{blue!20}strategic & \cellcolor{blue!20}stakeholder & \cellcolor{blue!20}focus & \cellcolor{blue!20}initiative & \mybar{162} \\
+   57 & \cellcolor{blue!20}absent & \cellcolor{blue!20}int & \cellcolor{blue!20}preside & \cellcolor{blue!20}ordained & \cellcolor{blue!20}tag & \cellcolor{blue!20}numbers & \mybar{194} \\ 
+  101 & \cellcolor{blue!20}violent & \cellcolor{blue!20}gang & \cellcolor{blue!20}firearm & \cellcolor{blue!20}offender & \cellcolor{blue!20}crime & \cellcolor{blue!20}patrol & \mybar{511} \\ 
+   93 & \cellcolor{blue!80}shooting & \cellcolor{blue!80}suspect & \cellcolor{blue!80}pronounce & \cellcolor{blue!80}gunshot & \cellcolor{blue!80}flee & \cellcolor{blue!80}shoot & \mybar{730} \\ 
    \hline
@@
 White cells are non-significant topics.}
+\label{tabSTMtopwords120_2}
 \end{table}

### 2019-05-20 paper/tables/stmTopWords120_1.tex
fixed a small problem with the tex table labels and renamed some stuff for more sensible file names and table labels
new results

--- 2018-06-26 paper/tables/stmTopWords120.tex
@@
-% latex table generated in R 3.4.4 by xtable 1.8-2 package
-% Tue Jun 26 15:42:11 2018
+% latex table generated in R 3.6.0 by xtable 1.8-4 package
+% Mon May 20 11:38:16 2019
 \begin{table}[ht]
@@
   \hline
- 93 & \cellcolor{red!30}kindness & \cellcolor{red!30}winner & \cellcolor{red!30}hero & \cellcolor{red!30}famous & \cellcolor{red!30}tribute & \cellcolor{red!30}wager & \mybar{3042} \\ 
-   36 & \cellcolor{red!20}copy & \cellcolor{red!20}record & \cellcolor{red!20}request & \cellcolor{red!20}mail & \cellcolor{red!20}submit & \cellcolor{red!20}fax & \mybar{111} \\ 
-   98 & \cellcolor{red!20}community & \cellcolor{red!20}resident & \cellcolor{red!20}mission & \cellcolor{red!20}quality & \cellcolor{red!20}excellent & \cellcolor{red!20}life & \mybar{78} \\ 
-   52 & \cellcolor{red!20}county & \cellcolor{red!20}leg & \cellcolor{red!20}legislator & \cellcolor{red!20}legislature & \cellcolor{red!20}town & \cellcolor{red!20}municipality & \mybar{132} \\ 
-   18 & \cellcolor{red!20}often & \cellcolor{red!20}always & \cellcolor{red!20}sometimes & \cellcolor{red!20}never & \cellcolor{red!20}easy & \cellcolor{red!20}even & \mybar{505} \\ 
-   20 & \cellcolor{red!20}click & \cellcolor{red!20}blog & \cellcolor{red!20}email & \cellcolor{red!20}copyright & \cellcolor{red!20}dream & \cellcolor{red!20}sorry & \mybar{336} \\ 
-   38 & \cellcolor{red!10}camp & \cellcolor{red!10}yoga & \cellcolor{red!10}library & \cellcolor{red!10}camper & \cellcolor{red!10}fun & \cellcolor{red!10}librarian & \mybar{1009} \\ 
-   43 & \cellcolor{red!10}antibody & \cellcolor{red!10}infection & \cellcolor{red!10}hepatitis & \cellcolor{red!10}tuberculosis & \cellcolor{red!10}infect & \cellcolor{red!10}viral & \mybar{1551} \\ 
-   66 & \cellcolor{red!10}drinking & \cellcolor{red!10}water & \cellcolor{red!10}reservoir & \cellcolor{red!10}contaminant & \cellcolor{red!10}irrigation & \cellcolor{red!10}tap & \mybar{228} \\ 
-   68 & \cellcolor{red!10}spray & \cellcolor{red!10}mosquito & \cellcolor{red!10}pesticide & \cellcolor{red!10}pest & \cellcolor{red!10}repellent & \cellcolor{red!10}soap & \mybar{898} \\ 
-   33 & \cellcolor{red!10}fire & \cellcolor{red!10}alarm & \cellcolor{red!10}firefighter & \cellcolor{red!10}rescue & \cellcolor{red!10}apparatus & \cellcolor{red!10}emergency & \mybar{271} \\ 
-   56 & \cellcolor{red!10}holiday & \cellcolor{red!10}weekend & \cellcolor{red!10}parade & \cellcolor{red!10}event & \cellcolor{red!10}auburn & \cellcolor{red!10}host & \mybar{283} \\ 
-   44 & \cellcolor{red!10}microchip & \cellcolor{red!10}cat & \cellcolor{red!10}euthanasia & \cellcolor{red!10}spay & \cellcolor{red!10}rabies & \cellcolor{red!10}neuter & \mybar{1229} \\ 
-   70 & \cellcolor{red!10}election & \cellcolor{red!10}ethic & \cellcolor{red!10}ballot & \cellcolor{red!10}political & \cellcolor{red!10}candidate & \cellcolor{red!10}lobbyist & \mybar{382} \\ 
-   60 & \cellcolor{red!10}shall & \cellcolor{red!10}unless & \cellcolor{red!10}except & \cellcolor{red!10}mean & \cellcolor{red!10}deem & \cellcolor{red!10}forth & \mybar{103} \\ 
-   59 & \cellcolor{red!10}motion & \cellcolor{red!10}unanimously & \cellcolor{red!10}adjourn & \cellcolor{red!10}prince & \cellcolor{red!10}carry & \cellcolor{red!10}ken & \mybar{220} \\ 
-   81 & \cellcolor{red!10}effluent & \cellcolor{red!10}sludge & \cellcolor{red!10}wastewater & \cellcolor{red!10}mercury & \cellcolor{red!10}lbs & \cellcolor{red!10}gal & \mybar{537} \\ 
-   89 & \cellcolor{red!10}ask & \cellcolor{red!10}explain & \cellcolor{red!10}say & \cellcolor{red!10}reply & \cellcolor{red!10}suggest & \cellcolor{red!10}ruff & \mybar{427} \\ 
-    5 & \cellcolor{red!10}home & \cellcolor{red!10}family & \cellcolor{red!10}homeowner & \cellcolor{red!10}single & \cellcolor{red!10}residence & \cellcolor{red!10}cottage & \mybar{94} \\ 
-  105 & \cellcolor{red!10}proposer & \cellcolor{red!10}breach & \cellcolor{red!10}franchisee & \cellcolor{red!10}indemnify & \cellcolor{red!10}agree & \cellcolor{red!10}hereunder & \mybar{273} \\ 
-  119 & \cellcolor{red!10}alderman & \cellcolor{red!10}councilor & \cellcolor{red!10}councilwoman & \cellcolor{red!10}alderwoman & \cellcolor{red!10}common & \cellcolor{red!10}roll & \mybar{260} \\ 
-   14 & \cellcolor{red!10}borough & \cellcolor{red!10}exam & \cellcolor{red!10}trademark & \cellcolor{red!10}veteran & \cellcolor{red!10}immigrant & \cellcolor{red!10}new & \mybar{359} \\ 
-  116 & \cellcolor{red!10}asthma & \cellcolor{red!10}overdose & \cellcolor{red!10}diabetes & \cellcolor{red!10}obesity & \cellcolor{red!10}hospitalization & \cellcolor{red!10}prevalence & \mybar{609} \\
-   37 & \cellcolor{red!10}dental & \cellcolor{red!10}medicare & \cellcolor{red!10}deductible & \cellcolor{red!10}coinsurance & \cellcolor{red!10}prescription & \cellcolor{red!10}copay & \mybar{444} \\
-   67 & \cellcolor{red!10}plat & \cellcolor{red!10}thence & \cellcolor{red!10}easement & \cellcolor{red!10}pud & \cellcolor{red!10}petitioner & \cellcolor{red!10}annexation & \mybar{271} \\ 
-   35 & \cellcolor{red!10}parent & \cellcolor{red!10}youth & \cellcolor{red!10}child & \cellcolor{red!10}mentor & \cellcolor{red!10}literacy & \cellcolor{red!10}foster & \mybar{326} \\ 
-   75 & \cellcolor{red!10}website & \cellcolor{red!10}plain & \cellcolor{red!10}please & \cellcolor{red!10}online & \cellcolor{red!10}customize & \cellcolor{red!10}contact & \mybar{98} \\ 
-   21 & \cellcolor{red!10}bid & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontractor & \cellcolor{red!10}contract & \cellcolor{red!10}procurement & \mybar{238} \\ 
-   95 & \cellcolor{red!10}duct & \cellcolor{red!10}valve & \cellcolor{red!10}splice & \cellcolor{red!10}piping & \cellcolor{red!10}conduit & \cellcolor{red!10}conductor & \mybar{850} \\ 
-   83 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}drainage & \cellcolor{red!10}sewer & \cellcolor{red!10}sanitary & \cellcolor{red!10}infiltration & \mybar{224} \\ 
-   64 & \cellcolor{red!10}discrimination & \cellcolor{red!10}gender & \cellcolor{red!10}disability & \cellcolor{red!10}race & \cellcolor{red!10}religion & \cellcolor{red!10}racial & \mybar{437} \\ 
-   32 & \cellcolor{red!10}think & \cellcolor{red!10}really & \cellcolor{red!10}thing & \cellcolor{red!10}something & \cellcolor{red!10}maybe & \cellcolor{red!10}just & \mybar{899} \\ 
-   49 & \cellcolor{red!10}recycling & \cellcolor{red!10}recycle & \cellcolor{red!10}garbage & \cellcolor{red!10}trash & \cellcolor{red!10}waste & \cellcolor{red!10}bin & \mybar{405} \\ 
-    3 & \cellcolor{red!10}maturity & \cellcolor{red!10}portfolio & \cellcolor{red!10}rating & \cellcolor{red!10}jun & \cellcolor{red!10}yield & \cellcolor{red!10}investment & \mybar{276} \\ 
-    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}payment & \cellcolor{red!10}card & \cellcolor{red!10}cash & \cellcolor{red!10}account & \cellcolor{red!10}amt & \mybar{222} \\ 
-   12 & \cellcolor{red!10}password & \cellcolor{red!10}header & \cellcolor{red!10}archive & \cellcolor{red!10}browser & \cellcolor{red!10}folder & \cellcolor{red!10}text & \mybar{552} \\ 
-   90 & \cellcolor{red!10}student & \cellcolor{red!10}school & \cellcolor{red!10}elementary & \cellcolor{red!10}college & \cellcolor{red!10}academic & \cellcolor{red!10}graduate & \mybar{303} \\ 
-   48 & \cellcolor{red!10}application & \cellcolor{red!10}applicant & \cellcolor{red!10}must & \cellcolor{red!10}certificate & \cellcolor{red!10}license & \cellcolor{red!10}proof & \mybar{150} \\ 
-   92 & \cellcolor{red!10}food & \cellcolor{red!10}calorie & \cellcolor{red!10}meat & \cellcolor{red!10}vend & \cellcolor{red!10}utensil & \cellcolor{red!10}salad & \mybar{1291} \\ 
-   86 & \cellcolor{red!10}whereas & \cellcolor{red!10}hereby & \cellcolor{red!10}resolve & \cellcolor{red!10}bond & \cellcolor{red!10}anticipation & \cellcolor{red!10}redemption & \mybar{194} \\ 
-   26 & \cellcolor{red!10}petroleum & \cellcolor{red!10}spill & \cellcolor{red!10}contamination & \cellcolor{red!10}asbestos & \cellcolor{red!10}contaminate & \cellcolor{red!10}radioactive & \mybar{444} \\
-    4 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}sin & \mybar{644} \\ 
-    7 & \cellcolor{red!10}energy & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \cellcolor{red!10}efficiency & \mybar{416} \\ 
-   22 & \cellcolor{red!10}wireless & \cellcolor{red!10}server & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}cable & \cellcolor{red!10}technology & \mybar{376} \\
-   76 & \cellcolor{red!10}year & \cellcolor{red!10}fiscal & \cellcolor{red!10}five & \cellcolor{red!10}annual & \cellcolor{red!10}last & \cellcolor{red!10}three & \mybar{50} \\ 
-   34 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}per & \cellcolor{red!10}cost & \cellcolor{red!10}plus & \cellcolor{red!10}hourly & \mybar{109} \\ 
-  109 & \cellcolor{red!10}city & \cellcolor{red!10}fort & \cellcolor{red!10}manager & \cellcolor{red!10}worth & \cellcolor{red!10}hall & \cellcolor{red!10}municipal & \mybar{10} \\ 
-  103 & \cellcolor{red!10}com & \cellcolor{red!10}perm & \cellcolor{red!10}tor & \cellcolor{red!10}cigarette & \cellcolor{red!10}loo & \cellcolor{red!10}comm & \mybar{1386} \\ 
-   79 & \cellcolor{red!10}tow & \cellcolor{red!10}plow & \cellcolor{red!10}vehicle & \cellcolor{red!10}trailer & \cellcolor{red!10}motor & \cellcolor{red!10}truck & \mybar{594} \\ 
-   54 & \cellcolor{red!10}dwell & \cellcolor{red!10}building & \cellcolor{red!10}remodel & \cellcolor{red!10}unit & \cellcolor{red!10}occupancy & \cellcolor{red!10}alteration & \mybar{132} \\ 
-   23 & \cellcolor{red!10}name & \cellcolor{red!10}address & \cellcolor{red!10}description & \cellcolor{red!10}number & \cellcolor{red!10}list & \cellcolor{red!10}zip & \mybar{92} \\ 
-   69 & \cellcolor{red!10}vista & \cellcolor{red!10}ranch & \cellcolor{red!10}suite & \cellcolor{red!10}trinity & \cellcolor{red!10}coliseum & \cellcolor{red!10}mesa & \mybar{657} \\ 
-   61 & \cellcolor{red!10}cannabis & \cellcolor{red!10}marijuana & \cellcolor{red!10}cultivation & \cellcolor{red!10}dispensary & \cellcolor{red!10}collective & \cellcolor{red!10}liquor & \mybar{470} \\
-  114 & \cellcolor{red!10}beach & \cellcolor{red!10}orange & \cellcolor{red!10}platinum & \cellcolor{red!10}resort & \cellcolor{red!10}ocean & \cellcolor{red!10}angel & \mybar{517} \\ 
-    1 & \cellcolor{red!10}landlord & \cellcolor{red!10}tenant & \cellcolor{red!10}lease & \cellcolor{red!10}lessee & \cellcolor{red!10}golf & \cellcolor{red!10}rent & \mybar{288} \\ 
-  118 & \cellcolor{white}flood & \cellcolor{white}earthquake & \cellcolor{white}floodplain & \cellcolor{white}hurricane & \cellcolor{white}tornado & \cellcolor{white}disaster & \mybar{513} \\ 
-   99 & \cellcolor{white}roof & \cellcolor{white}porch & \cellcolor{white}awning & \cellcolor{white}masonry & \cellcolor{white}brick & \cellcolor{white}vinyl & \mybar{729} \\ 
-  111 & \cellcolor{white}buffalo & \cellcolor{white}player & \cellcolor{white}league & \cellcolor{white}ballpark & \cellcolor{white}baseball & \cellcolor{white}football & \mybar{542} \\ 
-  112 & \cellcolor{white}excavation & \cellcolor{white}trench & \cellcolor{white}excavate & \cellcolor{white}gravel & \cellcolor{white}silt & \cellcolor{white}concrete & \mybar{696} \\ 
-   53 & \cellcolor{white}downtown & \cellcolor{white}mall & \cellcolor{white}hotel & \cellcolor{white}midtown & \cellcolor{white}uptown & \cellcolor{white}shopping & \mybar{531} \\ 
+ 96 & \cellcolor{red!40}subcommittee & \cellcolor{red!40}agenda & \cellcolor{red!40}forum & \cellcolor{red!40}speaker & \cellcolor{red!40}item & \cellcolor{red!40}adjournment & \mybar{217} \\ 
+   49 & \cellcolor{red!40}prize & \cellcolor{red!40}celebration & \cellcolor{red!40}ceremony & \cellcolor{red!40}parade & \cellcolor{red!40}follower & \cellcolor{red!40}favorite & \mybar{2043} \\ 
+  102 & \cellcolor{red!30}motion & \cellcolor{red!30}second & \cellcolor{red!30}adjourn & \cellcolor{red!30}unanimous & \cellcolor{red!30}carry & \cellcolor{red!30}whiting & \mybar{207} \\ 
+   73 & \cellcolor{red!20}legislator & \cellcolor{red!20}player & \cellcolor{red!20}football & \cellcolor{red!20}leg & \cellcolor{red!20}town & \cellcolor{red!20}stadium & \mybar{695} \\ 
+   95 & \cellcolor{red!20}online & \cellcolor{red!20}email & \cellcolor{red!20}website & \cellcolor{red!20}browser & \cellcolor{red!20}contact & \cellcolor{red!20}server & \mybar{351} \\ 
+   70 & \cellcolor{red!20}election & \cellcolor{red!20}ballot & \cellcolor{red!20}lobbyist & \cellcolor{red!20}voter & \cellcolor{red!20}candidate & \cellcolor{red!20}campaign & \mybar{407} \\ 
+   74 & \cellcolor{red!20}tentative & \cellcolor{red!20}conditional & \cellcolor{red!20}approval & \cellcolor{red!20}grading & \cellcolor{red!20}attachment & \cellcolor{red!20}deviation & \mybar{177} \\
+   79 & \cellcolor{red!20}snow & \cellcolor{red!20}remember & \cellcolor{red!20}plow & \cellcolor{red!20}lock & \cellcolor{red!20}scam & \cellcolor{red!20}sure & \mybar{888} \\ 
+   28 & \cellcolor{red!20}craftsman & \cellcolor{red!20}revival & \cellcolor{red!20}historic & \cellcolor{red!20}gabled & \cellcolor{red!20}bungalow & \cellcolor{red!20}historical & \mybar{882} \\ 
+  114 & \cellcolor{red!20}park & \cellcolor{red!20}playground & \cellcolor{red!20}recreation & \cellcolor{red!20}picnic & \cellcolor{red!20}mesa & \cellcolor{red!20}trail & \mybar{235} \\ 
+   11 & \cellcolor{red!10}tuberculosis & \cellcolor{red!10}infection & \cellcolor{red!10}hepatitis & \cellcolor{red!10}overdose & \cellcolor{red!10}influenza & \cellcolor{red!10}vaccine & \mybar{1515} \\
+   21 & \cellcolor{red!10}think & \cellcolor{red!10}something & \cellcolor{red!10}want & \cellcolor{red!10}thing & \cellcolor{red!10}talk & \cellcolor{red!10}everybody & \mybar{1155} \\ 
+   86 & \cellcolor{red!10}sewer & \cellcolor{red!10}sanitary & \cellcolor{red!10}water & \cellcolor{red!10}pipeline & \cellcolor{red!10}drinking & \cellcolor{red!10}wastewater & \mybar{176} \\ 
+   59 & \cellcolor{red!10}fort & \cellcolor{red!10}worth & \cellcolor{red!10}plot & \cellcolor{red!10}tad & \cellcolor{red!10}falls & \cellcolor{red!10}demo & \mybar{192} \\ 
+   20 & \cellcolor{red!10}subsection & \cellcolor{red!10}licensee & \cellcolor{red!10}article & \cellcolor{red!10}chapter & \cellcolor{red!10}sec & \cellcolor{red!10}shall & \mybar{214} \\ 
+   47 & \cellcolor{red!10}inf & \cellcolor{red!10}micron & \cellcolor{red!10}effluent & \cellcolor{red!10}eff & \cellcolor{red!10}sludge & \cellcolor{red!10}isomer & \mybar{591} \\ 
+   62 & \cellcolor{red!10}bid & \cellcolor{red!10}buyer & \cellcolor{red!10}seller & \cellcolor{red!10}bidder & \cellcolor{red!10}price & \cellcolor{red!10}quote & \mybar{357} \\ 
+   48 & \cellcolor{red!10}contributor & \cellcolor{red!10}instruction & \cellcolor{red!10}filer & \cellcolor{red!10}political & \cellcolor{red!10}officeholder & \cellcolor{red!10}payee & \mybar{79} \\
+  104 & \cellcolor{red!10}provisions & \cellcolor{red!10}subcontractor & \cellcolor{red!10}surety & \cellcolor{red!10}rev & \cellcolor{red!10}bidder & \cellcolor{red!10}supplementary & \mybar{232} \\ 
+   27 & \cellcolor{red!10}breach & \cellcolor{red!10}franchisee & \cellcolor{red!10}hereunder & \cellcolor{red!10}agreement & \cellcolor{red!10}remedy & \cellcolor{red!10}agree & \mybar{213} \\ 
+  112 & \cellcolor{red!10}youth & \cellcolor{red!10}camp & \cellcolor{red!10}teach & \cellcolor{red!10}teen & \cellcolor{red!10}lesson & \cellcolor{red!10}yoga & \mybar{722} \\ 
+   23 & \cellcolor{red!10}dog & \cellcolor{red!10}rabies & \cellcolor{red!10}euthanasia & \cellcolor{red!10}euthanized & \cellcolor{red!10}pet & \cellcolor{red!10}spay & \mybar{1710} \\ 
+   35 & \cellcolor{red!10}trust & \cellcolor{red!10}revocable & \cellcolor{red!10}mfr & \cellcolor{red!10}apportionment & \cellcolor{red!10}living & \cellcolor{red!10}assn & \mybar{285} \\ 
+  116 & \cellcolor{red!10}emergency & \cellcolor{red!10}preparedness & \cellcolor{red!10}null & \cellcolor{red!10}dispatch & \cellcolor{red!10}rescue & \cellcolor{red!10}fire & \mybar{340} \\ 
+   80 & \cellcolor{red!10}energy & \cellcolor{red!10}efficiency & \cellcolor{red!10}customer & \cellcolor{red!10}saving & \cellcolor{red!10}rebate & \cellcolor{red!10}renewable & \mybar{382} \\ 
+  113 & \cellcolor{red!10}proud & \cellcolor{red!10}leadership & \cellcolor{red!10}honor & \cellcolor{red!10}pleased & \cellcolor{red!10}grateful & \cellcolor{red!10}passion & \mybar{1168} \\ 
+   18 & \cellcolor{red!10}garland & \cellcolor{red!10}invoice & \cellcolor{red!10}assoc & \cellcolor{red!10}check & \cellcolor{red!10}firefighter & \cellcolor{red!10}association & \mybar{152} \\ 
+   81 & \cellcolor{red!10}page & \cellcolor{red!10}last & \cellcolor{red!10}sub & \cellcolor{red!10}update & \cellcolor{red!10}prime & \cellcolor{red!10}award & \mybar{17} \\ 
+    2 & \cellcolor{red!10}mosquito & \cellcolor{red!10}insecticide & \cellcolor{red!10}spray & \cellcolor{red!10}bait & \cellcolor{red!10}repellent & \cellcolor{red!10}pesticide & \mybar{997} \\ 
+  120 & \cellcolor{red!10}project & \cellcolor{red!10}improvement & \cellcolor{red!10}funding & \cellcolor{red!10}justification & \cellcolor{red!10}completion & \cellcolor{red!10}acquisition & \mybar{47} \\
+  105 & \cellcolor{red!10}thence & \cellcolor{red!10}plat & \cellcolor{red!10}easement & \cellcolor{red!10}annexation & \cellcolor{red!10}pud & \cellcolor{red!10}westerly & \mybar{255} \\ 
+  118 & \cellcolor{red!10}comment & \cellcolor{red!10}concern & \cellcolor{red!10}suggest & \cellcolor{red!10}clarify & \cellcolor{red!10}suggestion & \cellcolor{red!10}dear & \mybar{307} \\ 
+   34 & \cellcolor{red!10}library & \cellcolor{red!10}campus & \cellcolor{red!10}doe & \cellcolor{red!10}branch & \cellcolor{red!10}center & \cellcolor{red!10}arena & \mybar{208} \\ 
+   40 & \cellcolor{red!10}portfolio & \cellcolor{red!10}treasury & \cellcolor{red!10}investment & \cellcolor{red!10}maturity & \cellcolor{red!10}yield & \cellcolor{red!10}liquidity & \mybar{250} \\ 
+  115 & \cellcolor{red!10}masonry & \cellcolor{red!10}plaster & \cellcolor{red!10}joist & \cellcolor{red!10}stud & \cellcolor{red!10}sheathing & \cellcolor{red!10}ceiling & \mybar{875} \\ 
+   53 & \cellcolor{red!10}department & \cellcolor{red!10}authority & \cellcolor{red!10}dpt & \cellcolor{red!10}correction & \cellcolor{red!10}citywide & \cellcolor{red!10}transit & \mybar{109} \\ 
+    3 & \cellcolor{red!10}vend & \cellcolor{red!10}utensil & \cellcolor{red!10}meat & \cellcolor{red!10}fat & \cellcolor{red!10}cheese & \cellcolor{red!10}salad & \mybar{1325} \\ 
+    8 & \cellcolor{red!10}assessor & \cellcolor{red!10}taxpayer & \cellcolor{red!10}determination & \cellcolor{red!10}informal & \cellcolor{red!10}petition & \cellcolor{red!10}notification & \mybar{39} \\
+   58 & \cellcolor{white}recycling & \cellcolor{white}bag & \cellcolor{white}garbage & \cellcolor{white}recycle & \cellcolor{white}recyclable & \cellcolor{white}recyclables & \mybar{318} \\ 
+   87 & \cellcolor{red!10}sign & \cellcolor{red!10}billboard & \cellcolor{red!10}pole & \cellcolor{red!10}speeding & \cellcolor{red!10}illuminate & \cellcolor{red!10}banner & \mybar{472} \\ 
+   31 & \cellcolor{red!10}student & \cellcolor{red!10}elementary & \cellcolor{red!10}school & \cellcolor{red!10}college & \cellcolor{red!10}graduate & \cellcolor{red!10}academic & \mybar{233} \\ 
+   32 & \cellcolor{red!10}dwelling & \cellcolor{red!10}alteration & \cellcolor{red!10}plumbing & \cellcolor{red!10}plumb & \cellcolor{red!10}canceled & \cellcolor{red!10}mechanical & \mybar{143} \\ 
+   51 & \cellcolor{red!10}combustible & \cellcolor{red!10}vent & \cellcolor{red!10}piping & \cellcolor{red!10}conductor & \cellcolor{red!10}duct & \cellcolor{red!10}flammable & \mybar{517} \\ 
+   91 & \cellcolor{red!10}app & \cellcolor{red!10}credit & \cellcolor{red!10}download & \cellcolor{red!10}post & \cellcolor{red!10}issued & \cellcolor{red!10}agent & \mybar{57} \\ 
+   66 & \cellcolor{white}wetland & \cellcolor{white}vernal & \cellcolor{white}riparian & \cellcolor{white}habitat & \cellcolor{white}specie & \cellcolor{white}species & \mybar{1040} \\ 
+   44 & \cellcolor{white}findings & \cellcolor{white}string & \cellcolor{white}tank & \cellcolor{white}carcinogen & \cellcolor{white}qty & \cellcolor{white}lust & \mybar{128} \\ 
+   42 & \cellcolor{white}contamination & \cellcolor{white}spill & \cellcolor{white}remediation & \cellcolor{white}groundwater & \cellcolor{white}asbestos & \cellcolor{white}hazardous & \mybar{343} \\ 
+   99 & \cellcolor{white}prep & \cellcolor{white}batch & \cellcolor{white}qualifier & \cellcolor{white}analytical & \cellcolor{white}surrogate & \cellcolor{white}sample & \mybar{313} \\ 
+   84 & \cellcolor{white}airport & \cellcolor{white}facility & \cellcolor{white}aviation & \cellcolor{white}maintenance & \cellcolor{white}operation & \cellcolor{white}aircraft & \mybar{150} \\ 
+   19 & \cellcolor{white}accessory & \cellcolor{white}height & \cellcolor{white}dwell & \cellcolor{white}frontage & \cellcolor{white}setback & \cellcolor{white}subsection & \mybar{218} \\ 
+    6 & \cellcolor{white}householder & \cellcolor{white}poverty & \cellcolor{white}disability & \cellcolor{white}married & \cellcolor{white}husband & \cellcolor{white}universe & \mybar{93} \\ 
+   98 & \cellcolor{white}obesity & \cellcolor{white}sugary & \cellcolor{white}epidemic & \cellcolor{white}soda & \cellcolor{white}sensible & \cellcolor{white}drink & \mybar{65} \\ 
+   33 & \cellcolor{white}avenue & \cellcolor{white}street & \cellcolor{white}west & \cellcolor{white}east & \cellcolor{white}boulevard & \cellcolor{white}south & \mybar{98} \\ 
+   10 & \cellcolor{white}deductible & \cellcolor{white}copay & \cellcolor{white}prescription & \cellcolor{white}coinsurance & \cellcolor{white}outpatient & \cellcolor{white}inpatient & \mybar{488} \\ 
+   50 & \cellcolor{white}ductile & \cellcolor{white}trench & \cellcolor{white}pipe & \cellcolor{white}manhole & \cellcolor{white}coupling & \cellcolor{white}compaction & \mybar{705} \\ 
+   17 & \cellcolor{white}margin & \cellcolor{white}error & \cellcolor{white}occupied & \cellcolor{white}race & \cellcolor{white}occupy & \cellcolor{white}islander & \mybar{79} \\ 
+    5 & \cellcolor{white}earthquake & \cellcolor{white}flood & \cellcolor{white}floodplain & \cellcolor{white}flooding & \cellcolor{white}landslide & \cellcolor{white}fault & \mybar{723} \\ 
+   76 & \cellcolor{white}variance & \cellcolor{white}setback & \cellcolor{white}yard & \cellcolor{white}exception & \cellcolor{white}fence & \cellcolor{white}front & \mybar{94} \\ 
+   16 & \cellcolor{white}business & \cellcolor{white}marijuana & \cellcolor{white}cannabis & \cellcolor{white}manufacturing & \cellcolor{white}industry & \cellcolor{white}collective & \mybar{319} \\ 
+  108 & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}bio & \cellcolor{blue!10}exhaust & \cellcolor{blue!10}unmitigated & \cellcolor{blue!10}noise & \cellcolor{blue!10}receptor & \mybar{262} \\ 
    \hline
@@
 White cells are non-significant topics.}
+\label{tabSTMtopwords120_1}
 \end{table}

### 2019-05-22 paper/manuscript_paNote.tex
adding example and table

@@
 City websites can be used to communicate the stance of a mayor on social or economic programs.
-
-%\begin{figure}
-%\centering
-%\includegraphics[scale=0.35]{figures/eriemayor}
-%\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
-%\label{fig:eriemayor}
-%\end{figure}
+Consider the example of the Gary, Indiana homepage, depicted in Figure \ref{fig:garymayor}.
+This screenshot provides a clear example of the utility of a city website for communicating the mayor's policy priorities and accomplishments.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.45]{figures/gary_hp}
+\caption{Screenshot from the homepage at \url{https://garyin.us/}, accessed on 05/22/2019. Image depicts Democratic mayor of Gary, IN, Karen Freeman-Wilson.}
+\label{fig:garymayor}
+\end{figure}
 
@@
 Parsing any one website is fairly straightforward, but parsing the 283 different websites in our sample in a consistent and comparable manner makes a rule-based approach impossible.
+The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
+The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{garymayor}.
+Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
+The Mayor's message represents a relatively small fraction of the total text on the page.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.35]{figures/gary_sidebyside}
+\caption{Side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.}
+\label{fig:garysbs}
+\end{figure}
 
@@
 These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful.
-We rely on the method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited and can easily be implemented through the R package \texttt{boilerpipeR}.
+We rely on the `boilerpipe' method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited, and can easily be implemented through the R package \texttt{boilerpipeR}.
+The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{ig:garybp}.
+We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.375]{figures/gary_bp}
+\caption{Result of running \url{https://garyin.us/}, accessed on 05/22/2019, through the default boilerpipe algorithm at \url{https://boilerpipe-web.appspot.com/}.}
+\label{fig:gary_bp}
+\end{figure}
 
@@
 After all the preprocessing is set and done, our corpus consists of 259,099 documents.
+In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
+The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package.
+
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{lrr}
+        \hline
+        Process & Software & gov2text \\
+        \hline
+        1. Assemble url list. & N/A & no \\
+        2. Collect website files. & wget \& Selenium & no \\
+        3.  & & \\
+        \hline
+    \end{tabular}
+    \caption{\label{tab:list} Data collection and processing pipeline.} 
+\end{table}
 
@@
 \input{tables/stmTopWords120_2.tex}
+\input{tables/stmTopWords120_1_OLD.tex}
+\input{tables/stmTopWords120_2_OLD.tex}
 

### 2019-05-23 paper/manuscript_paNote.tex
added table for pipeline

@@
 Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
+We provide an R package that can be used to apply our proposed pipeline.
 We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
@@
 
-To this end, we turn to to an approach that is much more common in natural langauge processing than political methodology -- part-of-speech (POS) tagging and named entity recognition (NER).
+To this end, we turn to a common method in natural langauge processing---part-of-speech (POS) tagging and named entity recognition (NER).
 While not their original purpose, these procedures perform very well in separating the wheat from the chaff.
-As names convey no substantive information, we NER is used to detect to remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient with respect to immigration and identity) as well as works of art (which frequently feature statutes, plans, etc.)} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, adjectives.
-Furthermore, we keep proper nouns that also occur as nouns -- this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
+As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient with respect to immigration and identity) as well as works of art (which frequently feature statutes, plans, etc.)} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, and adjectives.
+Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
 Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
@@
 In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
-The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package.
+The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.
 
@@
         \hline
-        Process & Software & gov2text \\
+        Process & Software dependency & \texttt{gov2text} inclusion \\
         \hline
@@
         2. Collect website files. & wget \& Selenium & no \\
-        3.  & & \\
+        3. Remove names. & \texttt{spacyR} & yes \\
+        4. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
+        5. Lemmatize text. & \texttt{spacyR} & yes \\
+        6. Retain tokens that are English words. & \texttt{Hunspell} & yes \\
+        7. Convert corpus to document-term matrix. & [MARKUS?] & no \\
         \hline
     \end{tabular}
-    \caption{\label{tab:list} Data collection and processing pipeline.} 
+    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
 \end{table}
@@
 We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
+We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline.
 This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.

### 2019-05-23 paper/manuscript_paNote.tex
revised table
noted wget limitation in conclusion

@@
         \hline
-        1. Assemble url list. & N/A & no \\
-        2. Collect website files. & wget \& Selenium & no \\
-        3. Remove names. & \texttt{spacyR} & yes \\
-        4. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
-        5. Lemmatize text. & \texttt{spacyR} & yes \\
+        1. Assemble url list. & Selenium & no \\
+        2. Collect website files. & wget & no \\
+        3. Lemmatize text. & \texttt{spacyR} & yes \\
+        4. Remove names. & \texttt{spacyR} & yes \\
+        5. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
         6. Retain tokens that are English words. & \texttt{Hunspell} & yes \\
-        7. Convert corpus to document-term matrix. & [MARKUS?] & no \\
+        7. Removal of duplicate documents. & \texttt{gov2text} & \texttt{gov2text} \\
         \hline
@@
 We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
+
+The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
+By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
+For any one website, it would be possible to customize a routine with Selenium to access dynamic elements, but the process would need to be customized for each website.
+This would add a costly website-by-website step, whereas \texttt{wget} can be applied across websites without website-specific supervision.
 

### 2019-05-23 paper/manuscript_paNote.tex
updating table

@@
 \usepackage{indentfirst}
-\usepackage[longnamesfirst]{natbib} % For references
+\usepackage{natbib} % For references
 \bibpunct{(}{)}{;}{a}{}{,} % Reference punctuation
@@
 For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
-Thus, lemmatization makes the results more easily comprehensible.} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyR}.
+Thus, lemmatization makes the results more easily comprehensible.} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
 This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources, as the grammatical rules of the English language remain their common denominator.
-To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyR} with an English parser, non-English words tend to be erroneously categorized as (proper) nouns.}.
-
+To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyr} with an English parser, non-English words tend to be erroneously categorized as (proper) nouns.}.
+
+The steps described above are customized to the case of studying text gathered from website files, but we also follow a couple of other steps that are common and advisable in most text analysis projects.
+First, we remove common uninformative words---stopwords (e.g., and, the, this), words that contain numbers, and words that have fewer than three characters.
 A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
 In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
-The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
+%The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
 For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus.
@@
 
-After all the preprocessing is set and done, our corpus consists of 259,099 documents.
+After all the preprocessing is set and done, our corpus consists of 356,911 documents.
 In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
@@
         \hline
-        Process & Software dependency & \texttt{gov2text} inclusion \\
+        Process & Software dependency & in \texttt{gov2text} \\
         \hline
-        1. Assemble url list. & Selenium & no \\
-        2. Collect website files. & wget & no \\
-        3. Lemmatize text. & \texttt{spacyR} & yes \\
-        4. Remove names. & \texttt{spacyR} & yes \\
-        5. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
-        6. Retain tokens that are English words. & \texttt{Hunspell} & yes \\
-        7. Removal of duplicate documents. & \texttt{gov2text} & \texttt{gov2text} \\
+        1. Assemble url list. & \texttt{Selenium} & no \\
+        2. Collect website files. & \texttt{wget} & no \\
+        3. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
+        4. Remove names. & \texttt{spacyr} & yes \\
+        5. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
+        6. Stopword/number/0-2 character word removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
+        7. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
+        8. Removal of duplicate documents. & \texttt{gov2text} & yes \\
         \hline
@@
 
-\bibliographystyle{apsr} % apsr stopped working for me
+\bibliographystyle{chicago} % apsr stopped working for me
 %\bibliographystyle{plainnat}

### 2019-05-23 paper/manuscript_paNote.tex
revising table
discussing dataset contribution

@@
 The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
+This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governements \citep[e.g., ][]{marschall2013local,sumner2019}.
 Details on the sources and methods of raw data collection can be found in the Appendix.
@@
 These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful.
-We rely on the `boilerpipe' method described in \cite{Kohlschutter2010}, which has been published in a reputable conference, is widely cited, and can easily be implemented through the R package \texttt{boilerpipeR}.
+We rely on the \texttt{boilerpipe} method described in \cite{Kohlschutter2010}, which is designed to extract blocks of substantive text from websites, and is implemented through the R package \texttt{boilerpipeR}.
+The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.
 The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{ig:garybp}.
@@
         2. Collect website files. & \texttt{wget} & no \\
-        3. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
-        4. Remove names. & \texttt{spacyr} & yes \\
-        5. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
-        6. Stopword/number/0-2 character word removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
-        7. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
-        8. Removal of duplicate documents. & \texttt{gov2text} & yes \\
+        3. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
+        4. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
+        5. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
+        6. Remove names. & \texttt{spacyr} & yes \\
+        7. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
+        8. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
+        9. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
+        10. Removal of duplicate documents. & \texttt{gov2text} & yes \\
         \hline

### 2019-05-23 paper/manuscript_paNote.tex
addressed nearly every point

@@
 The results are shown in Table \ref{tabSTMtopwords60}.
+First, it is notable that the 95\% credible includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor.
 Many of the topics associated with Democrats fit with what we understand to be national party priorities.
 Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
-Similarly, employee rights are represented in topics \textbf{10} and \textbf{29} \textbf{[DEBATABLE]}.
+Topic {\bf 6} ('race', 'islander','census,'female') covers racial and gender identity issues.
+Similarly, employee rights and benefits are represented in topics \textbf{10} and \textbf{29}.
 Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), \textbf{topic 45 ('asset', 'actuarial', 'liability', 'financial')}, \textbf{topic 35 ('bond', 'obligation', 'proceeds')} as well as \textbf{topic 55 ('taxable', 'deed', 'value')}.
-We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
+We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}).
 This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') depicts Democrats' complicated relationship with law enforcement \textbf{[This used to be about police as well, but now it's more of a crime topic]}.
+A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime.
 On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
-On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}.
-Finally, Democrats also focus more on the deliberative process of policymaking, as \underline{topics 31 ('agenda', 'committee') \textbf{[This is now the second-most REPUBLICAN topic 46]}}, \underline{34 (`comment', `draft', `feedback') \textbf{[This is now REPUBLICAN topic 5]}}, \textbf{1} (`absent', `preside', `authorized'), and \textbf{4} ('audit', 'procedure', 'oversight') attest to.
-\textbf{[Republicans also have topic 16]}  This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
+On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on law enforcement, even after controlling for crime \citep{Einstein2015}.
 
 City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government.
-Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51} \textbf{[This topic has changed a lot.]}), \underline{drinking water (53) \textbf{[topic missing]}}, and \underline{garbage removal (Topic 49) \textbf{[topic missing]}} are included among those topics that are more prevalent in cities with Democratic mayors.
-Similarly, protecting citizens from natural disasters is a focus in \underline{topics 1 ('storm', 'runoff', 'drainage') \textbf{[topic missing]}} and \textbf{2} ('influenza', 'infection', 'vaccine' \textbf{[This is not about Zika anymore, but infectious diseases in general.]}), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.
+Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51}), vaccination (Topic \textbf{2}),  and sanitation (Topic \textbf{47}), are prevalent among cities with Republican mayors.
+These basic service topics cannot be found among topics prevalent in cities with Democratic mayors.
+Similarly, zoning issues figure prominently in the set of republican topic (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules.
+The Democratic topics also include one that is somewhat focused on zoning Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.
 

### 2019-05-23 paper/manuscript_paNote.tex
revised and under 3k words

@@
 
-\section{Mayoral Politics and City Government Website Content}
+\section{Politics and Government Website Content}
 
@@
 
-One of the more subtle aspects of local government is the presence of different types of government structures.
+%One of the more subtle aspects of local government is the presence of different types of government structures.
 Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
@@
 For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text, arising from incorrectly converted documents, which leads to a general decrease in the amount of usable data.
-Two issues, in particular, need to be addressed: One, HTML files on city websites frequently do not have an ending but are still perfectly readable if correctly identified as such.
-Second, some documents contain the incorrect file ending.
+However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text.
 For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-To accurately assess their type, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature - or ``magic number''.
-This short sequence of bytes at the start (and sometimes end) of files is unique for each file type and therefore allows its correct identification through computer forensics tools such as \texttt{libmagic}.
-Files with incorrect endings are subsequently renamed.
+To accurately assess file types, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature.
+This short sequence of bytes at the start (and sometimes end) of files is unique for each file type and therefore allows its correct identification.
 
@@
 The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate.
-In theory, HTML tags intended to mark text content  exist to prevent this problem.
-In practice, not every web developer adheres to this standard, and even when they do, there is a large degree of variation in the way it is implemented.
-Parsing any one website is fairly straightforward, but parsing the 283 different websites in our sample in a consistent and comparable manner makes a rule-based approach impossible.
 The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
@@
 The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.
-The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{ig:garybp}.
+The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{fig:garybp}.
 We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.
@@
 \subsubsection{Extracting Text from PDF, XML, DOC, DOCX and TXT}
-Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending -- so the conversion described above is strictly necessary for the package to work correctly.}$^{,}$\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but this tool simply extracts all text and is therefore inferior to boilerpipe.} The breakdown of all files by type is given in Table \ref{tab:filetypes}.
+Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in Table \ref{tab:filetypes}.
 The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
@@
 To this end, we turn to a common method in natural langauge processing---part-of-speech (POS) tagging and named entity recognition (NER).
-While not their original purpose, these procedures perform very well in separating the wheat from the chaff.
-As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient with respect to immigration and identity) as well as works of art (which frequently feature statutes, plans, etc.)} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, and adjectives.
+As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient) as well as works of art (which frequently feature statutes, plans, etc.).} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, and adjectives.
 Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
@@
 For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
-Thus, lemmatization makes the results more easily comprehensible.} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
-This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources, as the grammatical rules of the English language remain their common denominator.
-To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyr} with an English parser, non-English words tend to be erroneously categorized as (proper) nouns.}.
-
-The steps described above are customized to the case of studying text gathered from website files, but we also follow a couple of other steps that are common and advisable in most text analysis projects.
-First, we remove common uninformative words---stopwords (e.g., and, the, this), words that contain numbers, and words that have fewer than three characters.
+} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
+This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources.
+To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).
 A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
@@
 
-After all the preprocessing is set and done, our corpus consists of 356,911 documents.
+After preprocessing, our corpus consists of 356,911 documents.
 In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
@@
         2. Collect website files. & \texttt{wget} & no \\
-        3. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
-        4. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
-        5. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
-        6. Remove names. & \texttt{spacyr} & yes \\
-        7. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
-        8. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
-        9. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
-        10. Removal of duplicate documents. & \texttt{gov2text} & yes \\
+        3. Correct file extensions. & \texttt{wand} \citep{wand} & yes \\
+        4. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
+        5. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
+        6. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
+        7. Remove names. & \texttt{spacyr} & yes \\
+        8. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
+        9. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
+        10. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
+        11. Removal of duplicate documents. & \texttt{gov2text} & yes \\
         \hline
@@
 Similarly, employee rights and benefits are represented in topics \textbf{10} and \textbf{29}.
-Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), \textbf{topic 45 ('asset', 'actuarial', 'liability', 'financial')}, \textbf{topic 35 ('bond', 'obligation', 'proceeds')} as well as \textbf{topic 55 ('taxable', 'deed', 'value')}.
+Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), Topic {\bf 45} ('asset', 'actuarial', 'liability', 'financial'), Topic \textbf{35} ('bond', 'obligation', 'proceeds') as well as Topic \textbf{55} ('taxable', 'deed', 'value').
 We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}).
@@
 \input{tables/stmTopWords60.tex}
-\input{tables/stmTopWords60_OLD.tex} %\ref{tabSTMtopwords2}
+%\input{tables/stmTopWords60_OLD.tex} %\ref{tabSTMtopwords2}
 
@@
 By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
-For any one website, it would be possible to customize a routine with Selenium to access dynamic elements, but the process would need to be customized for each website.
-This would add a costly website-by-website step, whereas \texttt{wget} can be applied across websites without website-specific supervision.
+For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.
 
@@
 %\input{tables/stateUrlSummary.tex}
-
-\newpage
 
@@
 Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
+
+One of the more subtle aspects of local government is the presence of different types of government structures.
+Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
+We do not have access to information about the type of governments across the breadth of our dataset.
+Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
+\cite{gerber2011mayors}, whose theory is somewhat comparable to ours, find that the inclusion of this potential confounder does not affect the results.
 

### 2019-05-23 paper/tables/stmTopWords60_income.tex
added stm results on income and education as tables

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu May 23 15:35:04 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{rllllllll}
  \hline
 \# & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & \multicolumn{2}{c}{Tokens assigned} \\ 
  \hline
 46 & \cellcolor{orange!60}chair & \cellcolor{orange!60}subcommittee & \cellcolor{orange!60}speaker & \cellcolor{orange!60}agenda & \cellcolor{orange!60}committee & \cellcolor{orange!60}commission & \mybar{446} \\ 
   19 & \cellcolor{orange!40}setback & \cellcolor{orange!40}variance & \cellcolor{orange!40}zoning & \cellcolor{orange!40}height & \cellcolor{orange!40}yard & \cellcolor{orange!40}accessory & \mybar{453} \\ 
    5 & \cellcolor{orange!30}draft & \cellcolor{orange!30}comment & \cellcolor{orange!30}review & \cellcolor{orange!30}revision & \cellcolor{orange!30}clarify & \cellcolor{orange!30}process & \mybar{356} \\ 
   58 & \cellcolor{orange!30}budget & \cellcolor{orange!30}revenue & \cellcolor{orange!30}adopted & \cellcolor{orange!30}balance & \cellcolor{orange!30}transfer & \cellcolor{orange!30}expenditure & \mybar{176} \\ 
   39 & \cellcolor{orange!30}downtown & \cellcolor{orange!30}mixed & \cellcolor{orange!30}retail & \cellcolor{orange!30}waterfront & \cellcolor{orange!30}orient & \cellcolor{orange!30}density & \mybar{419} \\ 
   50 & \cellcolor{orange!20}trench & \cellcolor{orange!20}manhole & \cellcolor{orange!20}ductile & \cellcolor{orange!20}excavation & \cellcolor{orange!20}pipe & \cellcolor{orange!20}grout & \mybar{1436} \\ 
    9 & \cellcolor{orange!20}trust & \cellcolor{orange!20}revocable & \cellcolor{orange!20}planned & \cellcolor{orange!20}mfr & \cellcolor{orange!20}apportionment & \cellcolor{orange!20}exhibit & \mybar{361} \\ 
    1 & \cellcolor{orange!20}absent & \cellcolor{orange!20}preside & \cellcolor{orange!20}authorize & \cellcolor{orange!20}ordained & \cellcolor{orange!20}int & \cellcolor{orange!20}tag & \mybar{377} \\ 
    4 & \cellcolor{orange!20}audit & \cellcolor{orange!20}auditor & \cellcolor{orange!20}procedure & \cellcolor{orange!20}timely & \cellcolor{orange!20}implemented & \cellcolor{orange!20}oversight & \mybar{472} \\ 
   25 & \cellcolor{orange!20}mitigation & \cellcolor{orange!20}impact & \cellcolor{orange!20}significant & \cellcolor{orange!20}adverse & \cellcolor{orange!20}environmental & \cellcolor{orange!20}measure & \mybar{217} \\ 
   45 & \cellcolor{orange!10}governmental & \cellcolor{orange!10}asset & \cellcolor{orange!10}actuarial & \cellcolor{orange!10}liability & \cellcolor{orange!10}financial & \cellcolor{orange!10}statement & \mybar{235} \\ 
   47 & \cellcolor{orange!10}effluent & \cellcolor{orange!10}inf & \cellcolor{orange!10}eff & \cellcolor{orange!10}infiltration & \cellcolor{orange!10}discharge & \cellcolor{orange!10}sludge & \mybar{751} \\ 
   12 & \cellcolor{orange!10}craftsman & \cellcolor{orange!10}architecture & \cellcolor{orange!10}brick & \cellcolor{orange!10}distinctive & \cellcolor{orange!10}revival & \cellcolor{orange!10}storefront & \mybar{1731} \\ 
   10 & \cellcolor{orange!10}grievance & \cellcolor{orange!10}deductible & \cellcolor{orange!10}coinsurance & \cellcolor{orange!10}dependent & \cellcolor{orange!10}employee & \cellcolor{orange!10}copay & \mybar{583} \\ 
   36 & \cellcolor{orange!10}respondent & \cellcolor{orange!10}compare & \cellcolor{orange!10}figure & \cellcolor{orange!10}trend & \cellcolor{orange!10}appendix & \cellcolor{orange!10}satisfied & \mybar{696} \\ 
   20 & \cellcolor{orange!10}customer & \cellcolor{orange!10}renewable & \cellcolor{orange!10}efficiency & \cellcolor{orange!10}energy & \cellcolor{orange!10}saving & \cellcolor{orange!10}conservation & \mybar{652} \\ 
   48 & \cellcolor{orange!10}contributor & \cellcolor{orange!10}filer & \cellcolor{orange!10}officeholder & \cellcolor{orange!10}political & \cellcolor{orange!10}rouge & \cellcolor{orange!10}payee & \mybar{293} \\ 
   56 & \cellcolor{orange!10}savings & \cellcolor{orange!10}neighborhood & \cellcolor{orange!10}village & \cellcolor{orange!10}excise & \cellcolor{orange!10}ltd & \cellcolor{orange!10}matrix & \mybar{131} \\ 
   60 & \cellcolor{orange!10}bicycle & \cellcolor{orange!10}bike & \cellcolor{orange!10}pedestrian & \cellcolor{orange!10}route & \cellcolor{orange!10}sidewalk & \cellcolor{orange!10}bicyclist & \mybar{561} \\ 
    3 & \cellcolor{orange!10}wetland & \cellcolor{orange!10}specie & \cellcolor{orange!10}species & \cellcolor{orange!10}vernal & \cellcolor{orange!10}ecological & \cellcolor{orange!10}riparian & \mybar{2293} \\ 
   28 & \cellcolor{orange!10}garland & \cellcolor{orange!10}assoc & \cellcolor{orange!10}association & \cellcolor{orange!10}firefighter & \cellcolor{orange!10}duke & \cellcolor{orange!10}xerox & \mybar{480} \\ 
   51 & \cellcolor{orange!10}vent & \cellcolor{orange!10}combustible & \cellcolor{orange!10}flammable & \cellcolor{orange!10}egress & \cellcolor{orange!10}ceiling & \cellcolor{orange!10}extinguisher & \mybar{1160} \\ 
   43 & \cellcolor{orange!10}medicare & \cellcolor{orange!10}payroll & \cellcolor{orange!10}blanket & \cellcolor{orange!10}contractual & \cellcolor{orange!10}undistributed & \cellcolor{orange!10}dept & \mybar{322} \\ 
   52 & \cellcolor{white}homeless & \cellcolor{white}homelessness & \cellcolor{white}affordable & \cellcolor{white}supportive & \cellcolor{white}housing & \cellcolor{white}affordability & \mybar{394} \\ 
   31 & \cellcolor{white}student & \cellcolor{white}teacher & \cellcolor{white}preschool & \cellcolor{white}academic & \cellcolor{white}kindergarten & \cellcolor{white}youth & \mybar{855} \\ 
   22 & \cellcolor{white}allocation & \cellcolor{white}subtotal & \cellcolor{white}admin & \cellcolor{white}cost & \cellcolor{white}yon & \cellcolor{white}allocate & \mybar{190} \\ 
   32 & \cellcolor{white}canceled & \cellcolor{white}dwelling & \cellcolor{white}suite & \cellcolor{white}ave & \cellcolor{white}tad & \cellcolor{white}alteration & \mybar{491} \\ 
   29 & \cellcolor{white}margin & \cellcolor{white}error & \cellcolor{white}disability & \cellcolor{white}speak & \cellcolor{white}employed & \cellcolor{white}language & \mybar{180} \\ 
    7 & \cellcolor{white}fugitive & \cellcolor{white}bio & \cellcolor{white}emission & \cellcolor{white}coal & \cellcolor{white}unmitigated & \cellcolor{white}exhaust & \mybar{773} \\ 
   11 & \cellcolor{white}obesity & \cellcolor{white}sugary & \cellcolor{white}epidemic & \cellcolor{white}drink & \cellcolor{white}calorie & \cellcolor{white}sensible & \mybar{96} \\ 
   34 & \cellcolor{white}playground & \cellcolor{white}recreation & \cellcolor{white}picnic & \cellcolor{white}park & \cellcolor{white}restroom & \cellcolor{white}zoo & \mybar{546} \\ 
   40 & \cellcolor{white}amt & \cellcolor{white}invoice & \cellcolor{white}acct & \cellcolor{white}exp & \cellcolor{white}unencumbered & \cellcolor{white}encumbrance & \mybar{116} \\ 
   53 & \cellcolor{white}applied & \cellcolor{white}col & \cellcolor{white}dist & \cellcolor{white}occupancy & \cellcolor{white}monoxide & \cellcolor{white}valuation & \mybar{128} \\ 
   18 & \cellcolor{teal!10}perm & \cellcolor{teal!10}queue & \cellcolor{teal!10}delay & \cellcolor{teal!10}peak & \cellcolor{teal!10}adj & \cellcolor{teal!10}flt & \mybar{187} \\ 
   55 & \cellcolor{teal!10}taxable & \cellcolor{teal!10}deed & \cellcolor{teal!10}res & \cellcolor{teal!10}homestead & \cellcolor{teal!10}value & \cellcolor{teal!10}book & \mybar{87} \\ 
    6 & \cellcolor{teal!10}race & \cellcolor{teal!10}householder & \cellcolor{teal!10}islander & \cellcolor{teal!10}census & \cellcolor{teal!10}occupied & \cellcolor{teal!10}female & \mybar{160} \\ 
   24 & \cellcolor{white}mail & \cellcolor{white}fax & \cellcolor{white}application & \cellcolor{white}click & \cellcolor{white}applicant & \cellcolor{white}copy & \mybar{367} \\ 
    8 & \cellcolor{teal!10}imp & \cellcolor{teal!10}assessor & \cellcolor{teal!10}taxpayer & \cellcolor{teal!10}petition & \cellcolor{teal!10}preliminary & \cellcolor{teal!10}determination & \mybar{91} \\ 
   17 & \cellcolor{teal!10}portfolio & \cellcolor{teal!10}micron & \cellcolor{teal!10}maturity & \cellcolor{teal!10}treasury & \cellcolor{teal!10}yield & \cellcolor{teal!10}investment & \mybar{538} \\ 
   35 & \cellcolor{teal!10}redemption & \cellcolor{teal!10}bond & \cellcolor{teal!10}increment & \cellcolor{teal!10}obligation & \cellcolor{teal!10}proceeds & \cellcolor{teal!10}lease & \mybar{339} \\ 
   38 & \cellcolor{teal!10}para & \cellcolor{teal!10}persona & \cellcolor{teal!10}horas & \cellcolor{teal!10}bud & \cellcolor{teal!10}contracted & \cellcolor{teal!10}ante & \mybar{1334} \\ 
   44 & \cellcolor{teal!10}findings & \cellcolor{teal!10}tank & \cellcolor{teal!10}string & \cellcolor{teal!10}carcinogen & \cellcolor{teal!10}lust & \cellcolor{teal!10}sic & \mybar{255} \\ 
   30 & \cellcolor{teal!10}subcontractor & \cellcolor{teal!10}bid & \cellcolor{teal!10}bidder & \cellcolor{teal!10}proposer & \cellcolor{teal!10}subcontract & \cellcolor{teal!10}bidding & \mybar{512} \\ 
   27 & \cellcolor{teal!10}article & \cellcolor{teal!10}subsection & \cellcolor{teal!10}shall & \cellcolor{teal!10}franchisee & \cellcolor{teal!10}paragraph & \cellcolor{teal!10}meaning & \mybar{658} \\ 
   15 & \cellcolor{teal!10}credit & \cellcolor{teal!10}docket & \cellcolor{teal!10}app & \cellcolor{teal!10}post & \cellcolor{teal!10}download & \cellcolor{teal!10}month & \mybar{61} \\ 
   37 & \cellcolor{teal!10}endorsed & \cellcolor{teal!10}endorse & \cellcolor{teal!10}rescue & \cellcolor{teal!10}assistant & \cellcolor{teal!10}analyst & \cellcolor{teal!10}technician & \mybar{355} \\ 
   14 & \cellcolor{teal!10}accomplishment & \cellcolor{teal!10}grantee & \cellcolor{teal!10}narrative & \cellcolor{teal!10}outcome & \cellcolor{teal!10}grant & \cellcolor{teal!10}recipient & \mybar{255} \\ 
   54 & \cellcolor{teal!10}license & \cellcolor{teal!10}licensee & \cellcolor{teal!10}citation & \cellcolor{teal!10}tow & \cellcolor{teal!10}fee & \cellcolor{teal!10}taxicab & \mybar{710} \\ 
   13 & \cellcolor{teal!10}initiative & \cellcolor{teal!10}outreach & \cellcolor{teal!10}strategy & \cellcolor{teal!10}leadership & \cellcolor{teal!10}engagement & \cellcolor{teal!10}focus & \mybar{502} \\ 
   33 & \cellcolor{teal!10}thence & \cellcolor{teal!10}east & \cellcolor{teal!10}south & \cellcolor{teal!10}corner & \cellcolor{teal!10}west & \cellcolor{teal!10}avenue & \mybar{340} \\ 
   42 & \cellcolor{teal!10}incumbent & \cellcolor{teal!10}prep & \cellcolor{teal!10}batch & \cellcolor{teal!10}qualifier & \cellcolor{teal!10}analytical & \cellcolor{teal!10}examination & \mybar{1091} \\ 
   57 & \cellcolor{teal!10}councilman & \cellcolor{teal!10}introduced & \cellcolor{teal!10}alderman & \cellcolor{teal!10}whereas & \cellcolor{teal!10}resolved & \cellcolor{teal!10}councilwoman & \mybar{615} \\ 
   23 & \cellcolor{teal!20}bag & \cellcolor{teal!20}recyclable & \cellcolor{teal!20}recyclables & \cellcolor{teal!20}reusable & \cellcolor{teal!20}vegetable & \cellcolor{teal!20}bait & \mybar{2254} \\ 
    2 & \cellcolor{teal!20}influenza & \cellcolor{teal!20}infection & \cellcolor{teal!20}vaccine & \cellcolor{teal!20}patient & \cellcolor{teal!20}tuberculosis & \cellcolor{teal!20}hepatitis & \mybar{2980} \\ 
   21 & \cellcolor{teal!20}everybody & \cellcolor{teal!20}think & \cellcolor{teal!20}something & \cellcolor{teal!20}thing & \cellcolor{teal!20}try & \cellcolor{teal!20}want & \mybar{2609} \\ 
   26 & \cellcolor{teal!20}mesa & \cellcolor{teal!20}canyon & \cellcolor{teal!20}via & \cellcolor{teal!20}odd & \cellcolor{teal!20}unidentified & \cellcolor{teal!20}paradise & \mybar{1886} \\ 
   49 & \cellcolor{teal!20}artist & \cellcolor{teal!20}fun & \cellcolor{teal!20}music & \cellcolor{teal!20}beginner & \cellcolor{teal!20}player & \cellcolor{teal!20}prize & \mybar{4565} \\ 
   16 & \cellcolor{teal!30}motion & \cellcolor{teal!30}second & \cellcolor{teal!30}adjourn & \cellcolor{teal!30}carry & \cellcolor{teal!30}unanimous & \cellcolor{teal!30}chairman & \mybar{419} \\ 
   41 & \cellcolor{teal!40}complainant & \cellcolor{teal!40}allegation & \cellcolor{teal!40}defendant & \cellcolor{teal!40}offender & \cellcolor{teal!40}commander & \cellcolor{teal!40}complaint & \mybar{1695} \\ 
   59 & \cellcolor{teal!80}burglary & \cellcolor{teal!80}robbery & \cellcolor{teal!80}theft & \cellcolor{teal!80}homicide & \cellcolor{teal!80}murder & \cellcolor{teal!80}gunshot & \mybar{945} \\ 
   \hline
\end{tabular}
\endgroup
\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict city median income based on coefficient size (wealthier cities are orange, poorer cities are teal). White cells are non-significant topics.} 
\label{tabSTMtopwords60_income}
\end{table}

### 2019-05-23 paper/tables/stmTopWords60_population.tex
added stm results on income and education as tables

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Thu May 23 15:37:29 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{rllllllll}
  \hline
 \# & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & \multicolumn{2}{c}{Tokens assigned} \\ 
  \hline
  2 & \cellcolor{cyan!80}influenza & \cellcolor{cyan!80}infection & \cellcolor{cyan!80}vaccine & \cellcolor{cyan!80}patient & \cellcolor{cyan!80}tuberculosis & \cellcolor{cyan!80}hepatitis & \mybar{2980} \\ 
   38 & \cellcolor{cyan!40}para & \cellcolor{cyan!40}persona & \cellcolor{cyan!40}horas & \cellcolor{cyan!40}bud & \cellcolor{cyan!40}contracted & \cellcolor{cyan!40}ante & \mybar{1334} \\ 
   59 & \cellcolor{cyan!30}burglary & \cellcolor{cyan!30}robbery & \cellcolor{cyan!30}theft & \cellcolor{cyan!30}homicide & \cellcolor{cyan!30}murder & \cellcolor{cyan!30}gunshot & \mybar{945} \\ 
   52 & \cellcolor{cyan!30}homeless & \cellcolor{cyan!30}homelessness & \cellcolor{cyan!30}affordable & \cellcolor{cyan!30}supportive & \cellcolor{cyan!30}housing & \cellcolor{cyan!30}affordability & \mybar{394} \\ 
   24 & \cellcolor{cyan!30}mail & \cellcolor{cyan!30}fax & \cellcolor{cyan!30}application & \cellcolor{cyan!30}click & \cellcolor{cyan!30}applicant & \cellcolor{cyan!30}copy & \mybar{367} \\ 
   29 & \cellcolor{cyan!20}margin & \cellcolor{cyan!20}error & \cellcolor{cyan!20}disability & \cellcolor{cyan!20}speak & \cellcolor{cyan!20}employed & \cellcolor{cyan!20}language & \mybar{180} \\ 
   36 & \cellcolor{cyan!20}respondent & \cellcolor{cyan!20}compare & \cellcolor{cyan!20}figure & \cellcolor{cyan!20}trend & \cellcolor{cyan!20}appendix & \cellcolor{cyan!20}satisfied & \mybar{696} \\ 
   41 & \cellcolor{cyan!20}complainant & \cellcolor{cyan!20}allegation & \cellcolor{cyan!20}defendant & \cellcolor{cyan!20}offender & \cellcolor{cyan!20}commander & \cellcolor{cyan!20}complaint & \mybar{1695} \\ 
   13 & \cellcolor{cyan!20}initiative & \cellcolor{cyan!20}outreach & \cellcolor{cyan!20}strategy & \cellcolor{cyan!20}leadership & \cellcolor{cyan!20}engagement & \cellcolor{cyan!20}focus & \mybar{502} \\ 
    6 & \cellcolor{cyan!10}race & \cellcolor{cyan!10}householder & \cellcolor{cyan!10}islander & \cellcolor{cyan!10}census & \cellcolor{cyan!10}occupied & \cellcolor{cyan!10}female & \mybar{160} \\ 
   10 & \cellcolor{cyan!10}grievance & \cellcolor{cyan!10}deductible & \cellcolor{cyan!10}coinsurance & \cellcolor{cyan!10}dependent & \cellcolor{cyan!10}employee & \cellcolor{cyan!10}copay & \mybar{583} \\ 
   31 & \cellcolor{cyan!10}student & \cellcolor{cyan!10}teacher & \cellcolor{cyan!10}preschool & \cellcolor{cyan!10}academic & \cellcolor{cyan!10}kindergarten & \cellcolor{cyan!10}youth & \mybar{855} \\ 
   22 & \cellcolor{cyan!10}allocation & \cellcolor{cyan!10}subtotal & \cellcolor{cyan!10}admin & \cellcolor{cyan!10}cost & \cellcolor{cyan!10}yon & \cellcolor{cyan!10}allocate & \mybar{190} \\ 
   11 & \cellcolor{cyan!10}obesity & \cellcolor{cyan!10}sugary & \cellcolor{cyan!10}epidemic & \cellcolor{cyan!10}drink & \cellcolor{cyan!10}calorie & \cellcolor{cyan!10}sensible & \mybar{96} \\ 
   44 & \cellcolor{cyan!10}findings & \cellcolor{cyan!10}tank & \cellcolor{cyan!10}string & \cellcolor{cyan!10}carcinogen & \cellcolor{cyan!10}lust & \cellcolor{cyan!10}sic & \mybar{255} \\ 
   23 & \cellcolor{cyan!10}bag & \cellcolor{cyan!10}recyclable & \cellcolor{cyan!10}recyclables & \cellcolor{cyan!10}reusable & \cellcolor{cyan!10}vegetable & \cellcolor{cyan!10}bait & \mybar{2254} \\ 
   17 & \cellcolor{cyan!10}portfolio & \cellcolor{cyan!10}micron & \cellcolor{cyan!10}maturity & \cellcolor{cyan!10}treasury & \cellcolor{cyan!10}yield & \cellcolor{cyan!10}investment & \mybar{538} \\ 
    4 & \cellcolor{cyan!10}audit & \cellcolor{cyan!10}auditor & \cellcolor{cyan!10}procedure & \cellcolor{cyan!10}timely & \cellcolor{cyan!10}implemented & \cellcolor{cyan!10}oversight & \mybar{472} \\ 
   42 & \cellcolor{cyan!10}incumbent & \cellcolor{cyan!10}prep & \cellcolor{cyan!10}batch & \cellcolor{cyan!10}qualifier & \cellcolor{cyan!10}analytical & \cellcolor{cyan!10}examination & \mybar{1091} \\ 
   27 & \cellcolor{cyan!10}article & \cellcolor{cyan!10}subsection & \cellcolor{cyan!10}shall & \cellcolor{cyan!10}franchisee & \cellcolor{cyan!10}paragraph & \cellcolor{cyan!10}meaning & \mybar{658} \\ 
   15 & \cellcolor{cyan!10}credit & \cellcolor{cyan!10}docket & \cellcolor{cyan!10}app & \cellcolor{cyan!10}post & \cellcolor{cyan!10}download & \cellcolor{cyan!10}month & \mybar{61} \\ 
   26 & \cellcolor{cyan!10}mesa & \cellcolor{cyan!10}canyon & \cellcolor{cyan!10}via & \cellcolor{cyan!10}odd & \cellcolor{cyan!10}unidentified & \cellcolor{cyan!10}paradise & \mybar{1886} \\ 
   51 & \cellcolor{cyan!10}vent & \cellcolor{cyan!10}combustible & \cellcolor{cyan!10}flammable & \cellcolor{cyan!10}egress & \cellcolor{cyan!10}ceiling & \cellcolor{cyan!10}extinguisher & \mybar{1160} \\ 
    7 & \cellcolor{cyan!10}fugitive & \cellcolor{cyan!10}bio & \cellcolor{cyan!10}emission & \cellcolor{cyan!10}coal & \cellcolor{cyan!10}unmitigated & \cellcolor{cyan!10}exhaust & \mybar{773} \\ 
   18 & \cellcolor{cyan!10}perm & \cellcolor{cyan!10}queue & \cellcolor{cyan!10}delay & \cellcolor{cyan!10}peak & \cellcolor{cyan!10}adj & \cellcolor{cyan!10}flt & \mybar{187} \\ 
   54 & \cellcolor{cyan!10}license & \cellcolor{cyan!10}licensee & \cellcolor{cyan!10}citation & \cellcolor{cyan!10}tow & \cellcolor{cyan!10}fee & \cellcolor{cyan!10}taxicab & \mybar{710} \\ 
   53 & \cellcolor{white}applied & \cellcolor{white}col & \cellcolor{white}dist & \cellcolor{white}occupancy & \cellcolor{white}monoxide & \cellcolor{white}valuation & \mybar{128} \\ 
   48 & \cellcolor{white}contributor & \cellcolor{white}filer & \cellcolor{white}officeholder & \cellcolor{white}political & \cellcolor{white}rouge & \cellcolor{white}payee & \mybar{293} \\ 
   25 & \cellcolor{magenta!10}mitigation & \cellcolor{magenta!10}impact & \cellcolor{magenta!10}significant & \cellcolor{magenta!10}adverse & \cellcolor{magenta!10}environmental & \cellcolor{magenta!10}measure & \mybar{217} \\ 
    9 & \cellcolor{magenta!10}trust & \cellcolor{magenta!10}revocable & \cellcolor{magenta!10}planned & \cellcolor{magenta!10}mfr & \cellcolor{magenta!10}apportionment & \cellcolor{magenta!10}exhibit & \mybar{361} \\ 
    8 & \cellcolor{magenta!10}imp & \cellcolor{magenta!10}assessor & \cellcolor{magenta!10}taxpayer & \cellcolor{magenta!10}petition & \cellcolor{magenta!10}preliminary & \cellcolor{magenta!10}determination & \mybar{91} \\ 
   20 & \cellcolor{magenta!10}customer & \cellcolor{magenta!10}renewable & \cellcolor{magenta!10}efficiency & \cellcolor{magenta!10}energy & \cellcolor{magenta!10}saving & \cellcolor{magenta!10}conservation & \mybar{652} \\ 
   33 & \cellcolor{magenta!10}thence & \cellcolor{magenta!10}east & \cellcolor{magenta!10}south & \cellcolor{magenta!10}corner & \cellcolor{magenta!10}west & \cellcolor{magenta!10}avenue & \mybar{340} \\ 
   56 & \cellcolor{magenta!10}savings & \cellcolor{magenta!10}neighborhood & \cellcolor{magenta!10}village & \cellcolor{magenta!10}excise & \cellcolor{magenta!10}ltd & \cellcolor{magenta!10}matrix & \mybar{131} \\ 
   28 & \cellcolor{magenta!10}garland & \cellcolor{magenta!10}assoc & \cellcolor{magenta!10}association & \cellcolor{magenta!10}firefighter & \cellcolor{magenta!10}duke & \cellcolor{magenta!10}xerox & \mybar{480} \\ 
   12 & \cellcolor{magenta!10}craftsman & \cellcolor{magenta!10}architecture & \cellcolor{magenta!10}brick & \cellcolor{magenta!10}distinctive & \cellcolor{magenta!10}revival & \cellcolor{magenta!10}storefront & \mybar{1731} \\ 
   21 & \cellcolor{magenta!10}everybody & \cellcolor{magenta!10}think & \cellcolor{magenta!10}something & \cellcolor{magenta!10}thing & \cellcolor{magenta!10}try & \cellcolor{magenta!10}want & \mybar{2609} \\ 
   35 & \cellcolor{magenta!10}redemption & \cellcolor{magenta!10}bond & \cellcolor{magenta!10}increment & \cellcolor{magenta!10}obligation & \cellcolor{magenta!10}proceeds & \cellcolor{magenta!10}lease & \mybar{339} \\ 
   45 & \cellcolor{magenta!10}governmental & \cellcolor{magenta!10}asset & \cellcolor{magenta!10}actuarial & \cellcolor{magenta!10}liability & \cellcolor{magenta!10}financial & \cellcolor{magenta!10}statement & \mybar{235} \\ 
   30 & \cellcolor{magenta!10}subcontractor & \cellcolor{magenta!10}bid & \cellcolor{magenta!10}bidder & \cellcolor{magenta!10}proposer & \cellcolor{magenta!10}subcontract & \cellcolor{magenta!10}bidding & \mybar{512} \\ 
   40 & \cellcolor{magenta!10}amt & \cellcolor{magenta!10}invoice & \cellcolor{magenta!10}acct & \cellcolor{magenta!10}exp & \cellcolor{magenta!10}unencumbered & \cellcolor{magenta!10}encumbrance & \mybar{116} \\ 
   55 & \cellcolor{magenta!10}taxable & \cellcolor{magenta!10}deed & \cellcolor{magenta!10}res & \cellcolor{magenta!10}homestead & \cellcolor{magenta!10}value & \cellcolor{magenta!10}book & \mybar{87} \\ 
    3 & \cellcolor{magenta!10}wetland & \cellcolor{magenta!10}specie & \cellcolor{magenta!10}species & \cellcolor{magenta!10}vernal & \cellcolor{magenta!10}ecological & \cellcolor{magenta!10}riparian & \mybar{2293} \\ 
   37 & \cellcolor{magenta!10}endorsed & \cellcolor{magenta!10}endorse & \cellcolor{magenta!10}rescue & \cellcolor{magenta!10}assistant & \cellcolor{magenta!10}analyst & \cellcolor{magenta!10}technician & \mybar{355} \\ 
   32 & \cellcolor{magenta!10}canceled & \cellcolor{magenta!10}dwelling & \cellcolor{magenta!10}suite & \cellcolor{magenta!10}ave & \cellcolor{magenta!10}tad & \cellcolor{magenta!10}alteration & \mybar{491} \\ 
   47 & \cellcolor{magenta!10}effluent & \cellcolor{magenta!10}inf & \cellcolor{magenta!10}eff & \cellcolor{magenta!10}infiltration & \cellcolor{magenta!10}discharge & \cellcolor{magenta!10}sludge & \mybar{751} \\ 
    5 & \cellcolor{magenta!10}draft & \cellcolor{magenta!10}comment & \cellcolor{magenta!10}review & \cellcolor{magenta!10}revision & \cellcolor{magenta!10}clarify & \cellcolor{magenta!10}process & \mybar{356} \\ 
   14 & \cellcolor{magenta!10}accomplishment & \cellcolor{magenta!10}grantee & \cellcolor{magenta!10}narrative & \cellcolor{magenta!10}outcome & \cellcolor{magenta!10}grant & \cellcolor{magenta!10}recipient & \mybar{255} \\ 
   39 & \cellcolor{magenta!10}downtown & \cellcolor{magenta!10}mixed & \cellcolor{magenta!10}retail & \cellcolor{magenta!10}waterfront & \cellcolor{magenta!10}orient & \cellcolor{magenta!10}density & \mybar{419} \\ 
   43 & \cellcolor{magenta!10}medicare & \cellcolor{magenta!10}payroll & \cellcolor{magenta!10}blanket & \cellcolor{magenta!10}contractual & \cellcolor{magenta!10}undistributed & \cellcolor{magenta!10}dept & \mybar{322} \\ 
   60 & \cellcolor{magenta!10}bicycle & \cellcolor{magenta!10}bike & \cellcolor{magenta!10}pedestrian & \cellcolor{magenta!10}route & \cellcolor{magenta!10}sidewalk & \cellcolor{magenta!10}bicyclist & \mybar{561} \\ 
   58 & \cellcolor{magenta!10}budget & \cellcolor{magenta!10}revenue & \cellcolor{magenta!10}adopted & \cellcolor{magenta!10}balance & \cellcolor{magenta!10}transfer & \cellcolor{magenta!10}expenditure & \mybar{176} \\ 
   50 & \cellcolor{magenta!10}trench & \cellcolor{magenta!10}manhole & \cellcolor{magenta!10}ductile & \cellcolor{magenta!10}excavation & \cellcolor{magenta!10}pipe & \cellcolor{magenta!10}grout & \mybar{1436} \\ 
   19 & \cellcolor{magenta!20}setback & \cellcolor{magenta!20}variance & \cellcolor{magenta!20}zoning & \cellcolor{magenta!20}height & \cellcolor{magenta!20}yard & \cellcolor{magenta!20}accessory & \mybar{453} \\ 
   34 & \cellcolor{magenta!20}playground & \cellcolor{magenta!20}recreation & \cellcolor{magenta!20}picnic & \cellcolor{magenta!20}park & \cellcolor{magenta!20}restroom & \cellcolor{magenta!20}zoo & \mybar{546} \\ 
    1 & \cellcolor{magenta!20}absent & \cellcolor{magenta!20}preside & \cellcolor{magenta!20}authorize & \cellcolor{magenta!20}ordained & \cellcolor{magenta!20}int & \cellcolor{magenta!20}tag & \mybar{377} \\ 
   46 & \cellcolor{magenta!20}chair & \cellcolor{magenta!20}subcommittee & \cellcolor{magenta!20}speaker & \cellcolor{magenta!20}agenda & \cellcolor{magenta!20}committee & \cellcolor{magenta!20}commission & \mybar{446} \\ 
   57 & \cellcolor{magenta!30}councilman & \cellcolor{magenta!30}introduced & \cellcolor{magenta!30}alderman & \cellcolor{magenta!30}whereas & \cellcolor{magenta!30}resolved & \cellcolor{magenta!30}councilwoman & \mybar{615} \\ 
   16 & \cellcolor{magenta!50}motion & \cellcolor{magenta!50}second & \cellcolor{magenta!50}adjourn & \cellcolor{magenta!50}carry & \cellcolor{magenta!50}unanimous & \cellcolor{magenta!50}chairman & \mybar{419} \\ 
   49 & \cellcolor{magenta!80}artist & \cellcolor{magenta!80}fun & \cellcolor{magenta!80}music & \cellcolor{magenta!80}beginner & \cellcolor{magenta!80}player & \cellcolor{magenta!80}prize & \mybar{4565} \\ 
   \hline
\end{tabular}
\endgroup
\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict city population based on coefficient size (larger cities are cyan, smaller cities are magenta). White cells are non-significant topics.} 
\label{tabSTMtopwords60_population}
\end{table}

### 2019-05-23 07_topicModel/02_02_stm_results_income.R

@@ -1,0 +1,92 @@
+library(stm)
+
+set.seed(1)
+
+load("out/stmSession_sim_60.rdata")
+
+#make a dataframe to store the results in
+df <- data.frame(coef = rep(0, numtopics), sig = rep(FALSE, numtopics),
+                 lower = rep(0, numtopics), upper = rep(0, numtopics),
+                 topic = 1:numtopics)
+
+conf_level <- 1 #in percent
+conf_level <- conf_level/100 #as a fraction
+conf_level <- conf_level/2 #two-sided
+
+conf_lower <- 0 + conf_level
+conf_upper <- 1 - conf_level
+
+for(j in 1:numtopics){
+  
+  coefs <- list()
+  
+  for(i in 1:sims){
+    coefs[[i]] <- prep$parameters[[j]][[i]]$est[9]
+  }
+  
+  coefs <- do.call(c, coefs)
+  coefs <- quantile(coefs, c(conf_lower, conf_upper))
+  
+  df$lower[j] <- coefs[1]
+  df$upper[j] <- coefs[2]
+  df$sig[j] <- all(coefs>0) | all(coefs<0)
+  df$coef[j] <- mean(coefs)
+  
+}
+
+#number of significant topics
+sum(df$sig)
+
+topwords <- stm::labelTopics(stmFit, topics = NULL, n = 7, frexweight = 0.5)
+topwords <- topwords$frex
+
+library(stringr)
+library(xtable)
+
+coeffBatches <- seq(-max(abs(df$coef)), max(abs(df$coef)), length.out = 17)
+blues <- rev(c("teal!10", "teal!20", "teal!30", "teal!40", "teal!50", "teal!60", "teal!70", "teal!80"))
+reds <- c("orange!10", "orange!20", "orange!30", "orange!40", "orange!50", "orange!60", "orange!70", "orange!80")
+
+f <- function(x) cut(x, coeffBatches, 
+                     labels= c(blues, reds),
+                     include.lowest = T, right = TRUE)
+
+f(-max(abs(df$coef)))
+
+topwords2 <- as.data.frame(topwords[,1:7])
+
+#tab = data.frame(category = c("A","B","C"), groupA = c(.2,.3,.5), groupB= c(.6,.7,.9))
+cellcolors <- lapply(df$coef, function(x) paste0("\\cellcolor{", f(x), "}"))
+cellcolors[which(df$sig==F)] <- "\\cellcolor{white}"
[…]

### 2019-05-24 paper/manuscript_paNote.tex
added stm results on income and education as tables
splitting and revising OA

@@
 \section{Introduction}
-Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
+Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation.
+The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
 The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
@@
 
+ Though government websites serve largely instrumental service-delivery purposes, they also offer officials a prime venue via which to communicate policy goals and accomplishments, which inevitably reflect officials' politics.
+In the current paper, we focus on the running example of the reflection of mayoral partisanship on municipal government websites.
 A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep{gerber2011mayors,de2016mayoral,einstein2016mayors,marion2013mayor}.
@@
 Furthermore, the sample is politically balanced---we have three blue states, and three red states.
-The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
+The partisan breakdown of city websites by state is provided in the appendix.
 This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governements \citep[e.g., ][]{marschall2013local,sumner2019}.
-Details on the sources and methods of raw data collection can be found in the Appendix.
-
-\input{tables/tabCitiesStatesParties.tex}
+Details on the sources and methods of raw data collection can be found in the online appendix.
 
@@
 \centering
-\includegraphics[scale=0.35]{figures/gary_sidebyside}
-\caption{Side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.}
+{\bf (a)} Naive Parsing  \\ \vspace{.2cm} 
+\includegraphics[scale=0.35]{figures/gary_sidebyside} \\ \vspace{.4cm}
+{\bf (b)} Boilerpipe 
+\includegraphics[scale=0.375]{figures/gary_bp}
+
+\caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.
+Bottom image provides the result of running \url{https://garyin.us/} through the \texttt{boilerpipe} algorithm at \url{https://boilerpipe-web.appspot.com/}.}
 \label{fig:garysbs}
@@
 
-\begin{figure}
-\centering
-\includegraphics[scale=0.375]{figures/gary_bp}
-\caption{Result of running \url{https://garyin.us/}, accessed on 05/22/2019, through the default boilerpipe algorithm at \url{https://boilerpipe-web.appspot.com/}.}
-\label{fig:gary_bp}
-\end{figure}
-
 \subsubsection{Extracting Text from PDF, XML, DOC, DOCX and TXT}
-Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in Table \ref{tab:filetypes}.
+Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
 The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
 Files of type XML, DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
-
-\input{tables/tabFiletypeFrequencies.tex}
 
@@
         9. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
-        10. Retain tokens that are English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
+        10. Retain only English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
         11. Removal of duplicate documents. & \texttt{gov2text} & yes \\
@@
 For our primary empirical investigation, the STM provides with a tool with which to estimate the relationship between the party of the city's mayor and the prevalence of each topic we estimate.
-Further details on our STM specification can be found in the appendix.
+We also include the municipality's population and median income as covariates.
+Further details on and results from our STM specification can be found in the online appendix.
 
@@
 
-\newpage
-\section*{Appendix}
-
-\subsection*{Raw data collection methods and sources}
-
-We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
-Two, the General Services Administration (GSA) maintains all `.gov' addresses, and provides a complete list of all such domains to the public.\footnote{The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
-This list is updated once per month---we rely on the version released on January 16, 2017.} The data from the GSA contains the following variables: (1) domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'); (2) the type of government entity to which the domain is registered, such as city, county, federal agency, etc; (3) for federal agencies, the name is specified; (4) the city in which the domain is registered.
-Naturally, the GSA's list does not contain cities which do not use a `.gov' website (or, in many cases, a city owns a registered `.gov' address, but uses a different one).
-Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
-Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the latter and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
-
-Not all of the URLs contained in these archives are functional.
-To test the URLs' functionality, we use a web driver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
-We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the web driver  \texttt{Geckodriver}.
-This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers.
-Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
-The use of a web driver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
-A web driver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
-This allows us to subsequently record and use the new URL for the actual website scraping.
-Consequently, an automated browser allows us to robustly answer the following questions: Is the website actually there?
-Does it work?
-If not, is it somewhere else or is it broken?
-We record this information and construct a list of verified URLs.
-
-To download the websites, we rely on the Unix command line tool \texttt{wget}.
-This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
-This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
-Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
-it does not follow external links).
-This way, all the files that make up a website are downloaded.
-For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
-For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites.
-However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
-
-The partisanship of the mayor of each city is coded in different ways, depending on the state.
-For Indiana, where elections are nominally partisan, this information is accessible through the state government's website\footnote{\url{http://www.in.gov/apps/sos/election/general/general2015?page=office&countyID=1&officeID=32&districtID=-1&candidate=}}.
-For Louisiana, we received data on the outcomes of mayoral elections from the Local Elections in America Project (LEAP) \citep{marschall2013local}.
-For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and coded the parties of the candidates based on the party committees from which they received donations.
-For California and Texas, where our data consists of highly populated cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
-Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
-When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
-Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.\footnote{In Indiana, the data includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.}
-
-Information on other covariates (population and median household income - from the American Community Survey 5-Year Data (2015)) was acquired through the API of the U.S.
-Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
-
-One of the more subtle aspects of local government is the presence of different types of government structures.
-Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
-We do not have access to information about the type of governments across the breadth of our dataset.
-Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\cite{gerber2011mayors}, whose theory is somewhat comparable to ours, find that the inclusion of this potential confounder does not affect the results.
-
-\section*{Details on STM specification}
-
-The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.\footnote{Since our corpus is at the larger end of that spectrum, we also estimated a model with 120 topics, but found no notable differences.} We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
-Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
-Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city.
-Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
-
-\input{tables/stmTopWords120_1.tex}
-\input{tables/stmTopWords120_2.tex}
-\input{tables/stmTopWords120_1_OLD.tex}
-\input{tables/stmTopWords120_2_OLD.tex}
-
-%\begin{figure}[htp]
-  %  \centering
-   % \caption{Five largest topic effects for the population covariate.
-The fact that the population and epidemiology topics are positively correlated with city size is indicative of the model's validity.}
-    %  \label{stmEffectPop}
-    % \includegraphics[width=\linewidth]{figures/stm_effect_pop.pdf}
-% \end{figure}
-
-% \begin{figure}[htp]
-  %  \centering
-   % \caption{Five largest topic effects for the median income covariate.
-The fact that the crime topic is most prevalent in poorer cities, good governance is the most positively correlated with income is indicative of the model's validity.}
-   % \label{stmEffectIncome}
-    %\includegraphics[width=\linewidth]{figures/stm_effect_income.pdf}
-%\end{figure}
-
 \end{document}
-
-%\begin{enumerate}
-%    \item Design
-%    \begin{enumerate}
-%        \item Choosing the sample
-%        \item Finding URLs
-%        \item list of .gov websites
-%        \item Finding supporting data
-%    \end{enumerate}
-%    \item Scraping
-%        \begin{enumerate}
-%            \item wget
-%            \item headless browser/Selenium
-%            \item Beautifulsoup/rvest
-%            \item APIs (httr)
-%            \item Wayback Machine
-%        \end{enumerate}
-%    \item Pre-processing
-%        \begin{enumerate}
-%            \item Determining document filetype
-%            \item File conversion
-%            \item Conventional preprocessing (lowercase, numbers, punctuation)
-%            \item Stemming and lemmatization
-%            \item spellchecking
-%            \item Dealing with duplicate text \& html documents in particular
-%        \end{enumerate}
-%    \item Analysis
-%        \begin{enumerate}
-%            \item LDA
-%            \item Other topic models (structural, author, dynamic -- maybe?)
-%            \item SVM (+ other machine learning classifiers?)
-%            \item Fightin Words
-%        \end{enumerate}
-%\end{enumerate}
-%
-%
-%
-%
-%
-%
-%% latex table generated in R 3.3.3 by xtable 1.8-2 package
-%% Wed Mar 22 11:32:43 2017
-%%\begin{table}[ht]
-%%    \centering
-%%    \begin{tabular}{lrrlrrl}
-%%        \hline
-%%        City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
-%%        \hline
-%%        Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
-%%        Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
-%%        Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
-%%        Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
-%%        Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
-%%        Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
-%%        Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
-%%        Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
-%%        Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
-%%        Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
-%%        North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
-%%        Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
-%%        Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
-%%        South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
-%%        Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
-%%        Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
-%%        \hline
-%%    \end{tabular}
-%%    \caption{} 
-%%\end{table}
-%
-%\subsection{Research Design}
-%
-%\begin{table}[ht]
-%    \centering
-%    \begin{tabular}{llr}
-%        \hline
-%        Variable & Unit & Source \\
-%        \hline
-%        Population size & 1000 people & Census \\
-%        Population growth last 5 years & Percent & Census \\
-%        Type of economy (agriculture/industry/services) & ? & Census \\
-%        Economic performance (GDP?) & \$ & Census \\
-%        Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-%        Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-%        Change of party control & 0/1 & in.gov/sos/elections/ \\
-%        Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
-%        Unemployment rate & Percent & Census \\
-%        Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
-%        \hline
-%    \end{tabular}
-%    \caption{List of covariates} 
-%\end{table}
-%
-%
-%
-%\begin{enumerate}
-%\item Corpus:
-%\begin{enumerate}
-%\item Last snapshots before the election (November 3, 2015 in Indiana; tbd. in Louisiana (probably February))
-%\item First snapshot that is at least 2 months after the new government's inauguration (which is in January for Indiana, May for Louisiana)
-%\end{enumerate}
-%\item Preprocessing:
-%\begin{enumerate}
-%\item restrict corpus to:
-%\begin{enumerate}
-%\item documents belonging to cities in which a change of power occurred
-%\item documents that were added, deleted or changed between the two snapshots
-%\end{enumerate}
-%\item words to lowercase
-%\item remove punctuation
-%\item stemming (Porter stemming algorithm?)
-%\item Remove stop words (regular list of stop words is enough, since we use an asymmetric prior)
-%\end{enumerate}
-%\item Apply Grimmer's expressed agenda model to the corpus
-%\begin{enumerate}
-%\item Asymmetric prior
-%\item Each document can have only one topic (in contrast to the author-topic model)
-%\item Cities $i = 1,..., n = 15$
-%\item Topic $k(k = 1,..., K )$
-%\item Documents $j(j = 1,...,D_i)$ from city i
-%\item Party covariate in the prior, where the deleted and unmodified documents are coded as from the first, and the added and modified documents from the second party
-%\end{enumerate}
-%\item Results
-%\begin{enumerate}
-%\item Label topics using Grimmer's automatic cluster labeling method, based on most commonly used words in documents belonging to topic
-%\item Evaluate topics
-%\end{enumerate}
-%\end{enumerate}
-%
-%Validation:
-%
-%\begin{itemize}
-%\item Do the above for cities in which no change of power occurred.
-%\item Check whether there is higher than average turnover around the new year by comparing changes to non-election years (and also Louisiana, where elections are later).
-%\item Check how long documents stay on websites on average. Use websites with a lot of snapshots for this (these exist for both small and large cities).
-%\end{itemize}
-%
-%Problem with using this model: Grimmer's expressed agenda model uses Senators as the actors.
-Senators is also who he is substantively interested in.
-For us, the equivalent to Senators is cities.
-However, we care about parties, not cities.
-%
-%\subsection{Survival model}
-%The existence of individual documents on municipal government websites can be though of as a survival process.
-No document stays on a website forever, and it appears to be a reasonable assumption that as documents get older and thus less relevant, they get replaced.
-The factors determining the steepness of the survival curve are the topic - fire safety regulations likely stay up longer than a bulletin on the annual spring banquet - and the change of party control after an election.
-%
-%\begin{quote}
-%\textit{H1}: The older a document, the more likely it is to be removed.
-%\end{quote}
-%
-%$S(t)$ has a downward slope. Admittedly, this is almost impossible not to be true. Also, test proportional, rising and falling hazard models.
-%
-%\begin{quote}
-%\textit{H2}: Documents pertaining to administrative matters are less likely to be removed.
-%\end{quote}
-%
-%Introduce a categorical variable for the top 10(?) topics. A negative coefficient for administrative topics would support this hypothesis.
-%
-%\begin{quote}
-%\textit{H3}: Documents introduced by the opposing party are more likely to be removed.
-%\end{quote}
-%
-%Introduce two variables into the survival model: One variable indicating which party has introduced a document, and a time-varying variable describing which party is currently in government.
-The hypothesis is tested through an interaction term between the two.
-%
-%\begin{quote}
-%\textit{H4a}: Democrats are more likely to remove documents with topics pertaining to private enterprise, private schools.
-%\end{quote}
-%
-%Interaction term between party in power and categorical topic variable.
-%
-%\begin{quote}
-%\textit{H4b}: Republicans are more likely to remove documents with topics pertaining to social justice, equality, taxes, public schools, etc.
-%\end{quote}
-%
-%Interaction term between party in power and categorical topic variable.
-%
-%\begin{quote}
-%\textit{H5}: In line with their commitment to small government, Republicans are more likely than Democrats to remove documents.
-%\end{quote}
-%
-%Party in power variable.\\
-%
-%
-%This model will take up a lot of degrees of freedom. The rarity of snapshots for some cities might be a problem. Documents being changed and being removed can be modeled as competing risks.
-%
-%
-%\begin{equation} 
-%\label{eq1}
-%\begin{split}
-%Y & = \text{Party that introduced the document} \\
-% & + \text{Party that is currently in power} \\
-% & + \text{Topic 1, topic 2, ..., topic k} \\
-% & + \text{Party that is currently in power} \times \text{Topic 1, topic 2, ..., topic k} \\
-% & + \text{Days since start of mayoral term (control)}
-%\end{split}
-%\end{equation}
-%
-%
-%
-%
-%
-%After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
-%
-%These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
-%
-%\begin{figure}[htp]
-%    \centering
-%    \caption{Percentage of state population covered.}
-%    \includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
-%\end{figure}
-%
-%We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
-To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
-We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
-%
-%<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
-Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
-%
-%It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
-%
-%\begin{enumerate}
-%
-%\item For what percentage and number of IN cities can we find data from the WBM?
-%\item For how many election cycles can we find political leadership data for these matched cities?
-%\item In what number and percentage of cities is the local leadership majority Republican? 
-%\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D). 
-%
-%\end{enumerate}
-%
-%\begin{enumerate}
-%    
-%    \item 30 cities, with a combined population of 1,180,435.
-However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
-%    \item 2015, 2011, 2007, 2003.
-%    \item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
-%    \item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic. 
-%    
-%\end{enumerate}
-%
-%
-%
-%
-%\section{Running Application: Party Differences in Municipal Websites}
-%
-%
-%\begin{landscape}
-%\begin{table}[htbp]
-%    %\caption{}
-%    \begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-%        \hline
-%        Names & Year & Journal & Findings & Important? \\ \hline
-%        Benedictis-Kessner, Justin De
-%        Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
-Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
-%        Caughey, Devin
-%        Warshaw, Christopher
-%        Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
-Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
-& Somewhat \\ \hline
-%        Einstein, Katherine Levine
-%        Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
-aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
-%        Einstein, Katherine Levine
-%        Glick, David M.
-& 2015 & Working Paper & Survey of 72 mayors.
-Unlike Republican mayors, roughly half of Democrats seem to agree that cities should aim to reduce inequality.
-Democratic mayors also seem to favor redistribution to accomplish that goal.
-& Somewhat \\ \hline
-%        Kiewiet, D Roderick
-%        Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
-Spending has thus decreased in general.
-Lack of funds means that there is not much discretion for partisanship.
-& Somewhat \\ \hline
-%        Tausanovitch, Chris
-%        Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
-Partisan elections do not make cities more or less responsive.
-& Yes \\ \hline
-%        Guillamón, Ma Dolores
-%        Bastida, Francisco
-%        Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
-Conservative parties spend more on police.
-Spending is higher before elections.
-Also contains a useful overview of the literature.
-& Yes \\ \hline
-%    \end{tabular}
-%    \label{}
-%\end{table}
-%\end{landscape}
-%
-%\begin{landscape}
-%    \begin{table}[htbp]
-%        %\caption{}
-%        \begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-%            \hline
-%            Names & Year & Journal & Findings & Important? \\ \hline
-%            Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
-%            Solé-Ollé, Albert
-%            Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
-The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
-Partisanship might also affect housing construction and price growth.
-& Yes \\ \hline
-%            Gerber, Elisabeth R.
-%            Hopkins, Daniel J.
-& 2011 & AJPS & Regression discontinuity design.
-Democratic mayors spend less on public safety.
-All other policy areas (including taxation) are unaffected.
-& Yes \\ \hline
-%            Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
-Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
-Non-partisan elections favor Republicans/upper class.
-Mixed evidence for whether partisanship of mayor is important for policy.
-& Somewhat \\ \hline
-%            Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
-spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
-& Somewhat \\ \hline
-%            Ferreira, Fernando
-%            Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design.
-Null results for spending and city gov.
-size with regard to mayor partisanship.
-& Yes \\ \hline
-%            Ansolabehere, Stephen
-%            Snyder, James M.
-& 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
-The important finding (for us) is the fact that counties whose government is controlled by the same party as the state government, receive more funding (county's share of state transfers, normalized by county pop.) from the state.
-& Somewhat \\ \hline
-%            Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
-%        \end{tabular}
-%        \label{}
-%    \end{table}
-%\end{landscape}
-%
-%\begin{landscape}
-%    \begin{table}[htbp]
-%        %\caption{}
-%        \begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-%            \hline
-%            Names & Year & Journal & Findings & Important? \\ \hline
-%            Armstrong, Cory L.
-& 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
-Manual content analysis (undergrads told to look around for 15 minutes).
-School board websites, more professional websites, and websites in Republican-dominated counties are found to be more transparent.
-& Yes \\ \hline
-%            Cegarra-Navarro, Juan
-%            Pachón, José
-%            Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
-Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
-More sophisticated websites are correlated with greater civic engagement and greater use of e-government functions.
-& Yes \\ \hline
-%            Dolson, Jordan
-%            Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
-Three categories: e-content (city information on website), e-participation, social media use.
-Tables on page 15 show frequencies of these categories across sites, and might be useful to inform our topics.
-Larger cities have better websites.
-Population growth and immigration are also tested, but the findings are somewhat inconclusive.
-& Yes \\ \hline
-%            Feeney, Mary K.
-%            Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
-city websites at two points in time (2010-2014).
-Count model of website features regarding information, e-services, utilities, transparency and civic engagement.
-Having a larger population leads to more features.
-Relying on a website contractor leads to more information and transparency.
-The authors say that mayor-councils are negatively correlated with website sophistication, but their regression tables state the opposite.
-& Yes \\ \hline
-%            Kaylor, Charles
-%            Deshazo, Randy
-%            Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
-Table 1 lists a number of possible ways this manifests, could be useful for our theory.
-& Somewhat \\ \hline
-%            Ansolabehere, Stephen
-%            Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
-Is website content correlated with city characteristics?
-Not particularly systematic, and the findings are inconclusive.
-& Somewhat \\ \hline
-%            Jeffres, Leo W.
-%            Lin, Carolyn A.
-& 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
-Features include information about city, opportunities for citizen feedback, galleries of photos, links, etc.
-Purely descriptive analysis, doesn't contain anything that isn't covered in any of the other aricles.
-& No \\ \hline
-%        \end{tabular}
-%        \label{}
-%    \end{table}
-%\end{landscape}
-%
-%\subsection{Informative Dirichlet model}
-%%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-%
-%For the analysis of the data, we present two approaches, the first being the informative dirichlet model developed by \citep{Monroe2008}.
-This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them with text with greater semantic, and in our case, partisan meaning.
-%
-%In Indiana, Democrats exhibit a preference for words related to public finance, such as 'fund', 'budget', or 'tax', indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
-This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-Beyond the focus on public finance, the words preferably used by Democrats do not fall into any particularly congruent categories, and largely sort into various areas related to city administration - i.e.
-`council', `services', `budget', `committee', `contract', etc.
-If there is theme around the words preferred by Republicans, it seems to center around city planning - street, fire, water, building, construction, park.
-These words suggest that the hands-off approach favored by Republicans results in a focus on supporting infrastructure and logistics.
-%
-%%Partisan top words - fightin words Indiana
-%\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
-%
-%For Lousiana, the results (see table \ref{tabFightinLA}) are less coherent.
-Only one of the finance-related terms appears again for Democrats - specifically `fund', although `rate' might also be used in a financial context.
-Beyond that, some focus on a `historic' `'district of a city seems evident, as is the use of some words - `infrastructure', `water', `building' that were used for Republicans in Indiana.
-Conversely, Republicans are now missing these words, and their preferred terms generally do not seem to follow any particular theme.
-%
-%%Partisan top words - fightin words Louisiana
-%\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
-%
-%The weakness of the fightin' words method is evident here, as a list of words does not necessarily provide sufficient information to glean preferred topics from.
-This is especially the case when the texts are spread across a broad number of issue-areas, with little semantic similarity.
-In \citep{Monroe2008}, the authors focus on the fairly constrained corpus of U.S.
-Senate speeches with respect to abortion - our context, by comparison, is far more eclectic.

### 2019-05-24 paper/manuscript_paNote_OA.tex
splitting and revising OA

--- 2018-10-06 paper/manuscript.tex
@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} {\bf Online Appendix} \\ Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
 
@@
 We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content.
-Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information through a new method of boilerplate removal.
+Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
+We provide an R package that can be used to apply our proposed pipeline.
 We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
@@
 \doublespacing
-\section{Introduction}
 
-Local governments convey voluminous information about all aspects of their policymaking, policy implementation, and public deliberation, via their official websites.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra}.
-Despite the potential for automated scraping of website contents, the conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
-Though highly accurate, the manual approach to data collection is costly, and cannot be scaled to capture even a fraction of the volume of content available on government websites.
-In this paper, we present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis.
-We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states (IN, LA, NY, WA, CA and TX) correlate with the partisanship of the city mayor.
+\section{Overview}
 
-Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for content (e.g., text, image) analysis.
-We describe and provide solutions to two central challenges in automatically gathering and analyzing website textual contents.
-First, plain text must be extracted from the files.
-This involves purging the files of syntax in HTML or other markup and programming languages and discarding any character encoding errors that result from reading in files with incorrectly specified character encodings.
-This challenge would arise in any context in which researchers sought to study the textual contents of websites, and is not unique to comparative analysis of government websites.
-The second challenge we address in our methodological pipeline is, however, specific to the research objective of comparing websites on the basis of a common lexicon.
-For any two governments, the textual signatures that most dramatically differentiate the textual contents of their websites consist of what we can call ``boilerplate'' text---header, footer, or other titling text that is designed to identify the website as being associated with a specific government entity (e.g., ``Welcome to the city of Santa Cruz'', ``The City of Los Angeles welcomes you'').
-This boilerplate text is replicated across many files that are associated with a government's website, but it provides little information regarding the form and/or function of the government.
-The second methodological innovation we offer in our pipeline is designed to minimize the impact of this boilerplate text on the comparative analysis of government website content.
+In this online appendix we include supporting information about our data, the data collection process, and some additional analyses.
+In the first section, we present additional details on data collection, along with some additional descriptive statistics.
+In the second section, we provide additional details on, and results from, our topic modeling analysis.
 
-Government websites provide information about how public policies shape the lives of local residents, and how local residents can engage with government to shape public policy.
-As such, government websites reflect both the results of and inputs to, the political leadership in the city.
-In our illustrative application, we explore the ways in which the contents of city government websites differ on the basis of the partisanship of the city's elected executive.
-A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions, including city budget priorities \citep{gerber2011mayors,de2016mayoral}, policies affecting inequality in cities \citep{einstein2016mayors}, and framing of criminal justice policy \citep{marion2013mayor}.
-Furthermore, recent media coverage of changes to government websites that follow transitions in party control suggest that changes in web content are salient government actions, as perceived by the general public \citep{sharfstein2017science,kirby2017trump,duarte2017deniable}.
-We study whether significant differences between city governments based on mayoral partisanship are reflected in the contents of city websites.
+\section{Data collection methods and sources}
 
-\section{The Significance of Government Website Content}
-
- According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected.
-Official city websites allow mayors to perform all three of these functions.
-Their offices frequently take a prominent position on the front page, and many websites also feature a picture of the mayor.
-We present an example of this in Figure \ref{fig:eriemayor}.
-The Erie, Pennsylvania website homepage presents an image of the Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city.
-In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies \citep{stanyer2008elected}.
-Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events.
-City websites present an opportunity for local officials to brandish these accomplishments.
-Finally, they also give mayors a platform from which they can advertise their political beliefs.
-On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available.
-As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors.
-City websites can then be used to communicate the stance of a mayor on social or economic programs.
-Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.35]{figures/eriemayor}
-\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
-\label{fig:eriemayor}
-\end{figure}
-
-Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
-In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
-Furthermore, the use of a local government website is associated with an individual's perspective on government.
-\citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
-Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
-
-The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents produced by governments, public officials, and candidates for office.
-The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view.
-For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use, and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}.
-As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency.
-To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated.
-The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue.
-Like most e-government studies, however, this publication does not make any use of automated text analysis.
-Branching out of the topic of e-government service provision, \citet{mcnutt2010virtual} uses Canadian government websites to study how well-connected government websites are to non-profits and intergovernmental organizations in different public policy domains.
-%Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}.
-\cite{Lin2011} provide a good example of a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles.
-The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased.
-Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
-%Another well-known example fitting into this area of study is the set of studies conducted by King et al.
-\citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere.
-However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.
-
-The websites of politicians and their parties have also been the object of research.
-Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-\cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them.
-\cite{Cryer2017} mentions that she relied on Archive-it, a web service of the Internet Archive.
-Though the Internet Archive may provide extensive coverage of high profile officials or national governments, we found that its coverage of municipal government websites was sparse and irregular.
-\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress.
-\cite{Therriault2010} use automated text analysis, and also has the most extensive overview of the associated methodology.
-However, the division of the website into sections (home page, topics, issues, details) is done by hand.
-The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).
-
-Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
-\cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
-%In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
-We then define a pipeline for data collection and analysis that includes methods to access government website URLs, scrape their raw contents from the World Wide Web, gather plain text from the website files, and identify boilerplate text within the plain text contents.
-Lastly, we illustrate the analysis of municipal government website text by exploring the relationship between the city mayors' party affiliations and the topical contents of the websites.
-
-\section{Data: US Municipal Government Website Text}
-
-For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
-The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
-Municipal elections in Indiana and Louisiana are partisan across the board,\footnote{In Indiana, this includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.} so our sample is primarily focused on these two states.
-Here, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
-New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see below for more detail on how we use this data).
-Finally, California and Texas contain a number of large cities, whose mayors are sufficiently well-known for their partisanship to be available.
-These six states also provide us with a sample that is well-balanced on a number of theoretically important indicators.
-One, each of the four geographic regions are represented with at least one state.
-Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage, as both major cities and less densely populated areas are covered.
-Furthermore, the sample is politically balanced---we have three blue states (CA, WA, NY) and three red states (TX, IN, LA).
-Finally, our dataset contains some of the wealthiest states (NY, CA, WA and TX are \#2, \#8, \#9 and \#16 respectively, by GDP per capita \citep{BureauofEconomicAnalysis2017}), but also some of the poorer ones (IN and LA).
-
-We acquired the website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
+We acquired the municipal website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
 Two, the General Services Administration (GSA) maintains all `.gov' addresses, and provides a complete list of all such domains to the public.\footnote{The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
@@
 When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
-Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.
-The partisan breakdown of city websites is depicted in Table \ref{tab:cityparties}.
-The dataset has a relative party balance, with variation in each state.
+Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.\footnote{In Indiana, the data includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.}
+
+Information on other covariates (population and median household income - from the American Community Survey 5-Year Data (2015)) was acquired through the API of the U.S.
+Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
+
+%One of the more subtle aspects of local government is the presence of different types of government structures.
+Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
+We do not have access to information about the type of governments across the breadth of our dataset.
+Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
+\cite{gerber2011mayors}, whose theory is somewhat comparable to ours, find that the inclusion of this potential confounder does not affect the results.
+
+Tables \ref{tab:cityparties} and \ref{tab:filetypes} provide additional information about the data collected for this project.
+In Table \ref{tab:cityparties}, we present the state-by-state breakdown of the mayoral partisanship of the cities collected in the respective state.
+In Table \ref{tab:filetypes}, we present the distribution of file extensions before and after processing.
 
@@
 
-One of the more subtle aspects of local government is the presence of different types of government structures.
-Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is a certain degree of variance in where a city's executive authority lies.
-Unfortunately, we do not have access to information about the type of governments across the breadth of our dataset and therefore cannot explore heterogeneity in the relationship between mayoral partisanship and municipal website contents based on the executive system variant.
-Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\cite{gerber2011mayors}, whose model is somewhat comparable to ours in the sense that they also test the effect of mayoral partisanship on city policy priorities (on a sample of large cities, for which this information is more easily available), find that the inclusion of this potential confounder does not affect the results.
-Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S.
-Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
-
-\section{The Web to Text Pipeline}
-
-Once we have gathered the website files, we have the raw data necessary for text analysis, but it is not yet formatted effectively.
-As is common in text analysis applications, we need to pre-process our data \citep{denny2018text}.
-In this section, we describe our pre-processing pipeline, with which we take an archive of website files, and output a corpus of formatted plain text files that are suitable for comparative analysis with text as data methods.
-In this pipeline, we address two methodological challenges.
-First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
-Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
-The first step in the methodological pipeline is aimed simply at extracting clean plain text from this heterogeneous file base.
-The second step in our methodological pipeline is to process the text to remove boilerplate language---language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
-Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
-We will clarify this distinction as we describe steps in our pipeline.
-
-\subsection{Site to Text Conversion}
-The format of a file has a major impact on whether and how textual data can be extracted from a document.
-For all text analysis projects, researchers need to consider file formats.
-For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text, arising from incorrectly converted documents, which leads to a general decrease in the amount of usable data.
-Two issues, in particular, need to be addressed: One, HTML files on city websites frequently do not have an ending but are still perfectly readable if correctly identified as such.
-Second, some documents contain the incorrect file ending.
-For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-To accurately assess their type, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature - or ``magic number''.
-This short sequence of bytes at the start (and sometimes end) of files is unique for each file type and therefore allows its correct identification through computer forensics tools such as \texttt{libmagic}.
-
-Consequently, we rename all documents so that their file ending reflects their actual file type.
-This is strictly necessary because we rely on the \texttt{readtext} R package \citep{readtext}, which determines a document's type solely through its ending---to convert the files to plain text.\footnote{We have also experimented with several Unix-based alternatives, but found that they largely led to the same results as \texttt{readtext}.} The breakdown of the files by type is given in Table \ref{tab:filetypes}.
-The most frequent file types are HTML and PDF, from which we are able to extract a substantial amount of usable text.
-Files of type XML, DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
-
 \input{tables/tabFiletypeFrequencies.tex}
 
-We then take several steps to pre-process the data as required for the subsequent analysis.
-Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}.
-The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
-%With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
-
-The text documents are converted to UTF-8 character encoding and then stripped of dates, punctuation, numbers, and words connected by underscores.
-At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
-"You are here", "Home", "Directory" etc.) in HTML documents, or commonly used forms or phrases in pdf, doc and docx files.
-This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate (through their unique boilerplate structure, e.g.
-a menu with certain terms repeated on every site of the domain), and not the substantive features of their contents.
-Boilerplate removal is a useful step in many forms of text analysis, as the analysis is focused in on text that varies above and beyond a standard template for textual content.
-Our solution to this problem is described in more detail in Section \ref{boilerplate}.
-
-The last round of preprocessing is intended to remove everything from the file that is not an English word.
-This step is tailored to our intention to use the text for topic modeling.
-The final preprocessing round includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
-Furthermore, some documents contain gibberish, often as a result of faulty or impartial optical character recognition applied to text that was produced through a non-machine-readable medium.
-To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example, Los Angeles, do contain a sizable proportion of Spanish content.
-The analysis of this content is beyond the scope of this paper but could be explored in future work, for example using methods of text processing that are applicable to multilingual corpora \citep{lucas2015computer}.
-} However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
-Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
-Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to the total number of tokens is less than 0.15.
-Furthermore, \texttt{hunspell} does not spellcheck individual characters or two-character words, so we remove these token types entirely.
-Since these pre-processing steps reduce documents which are largely unsuitable to only a few tokens (i.e., word occurrences), we also remove all remaining documents containing less than 50 tokens.
-Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive\footnote{Topic models essentially do not pick up on extremely rare words, so their inclusion is a waste of computational resources.
-Removing them in this manner is also the default preprocessing choice in the \texttt{stm} package.} to our models while increasing their computational cost, we also discard any token types that occur in only one document.
-We also conduct lemmatization to reduce words to their basic form.
-Lemmatization is similar to stemming but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
-For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
-Thus, lemmatization makes the results more easily comprehensible.
-To this end, we rely on the R package \texttt{spacyr}, which provides an R implementation of the Python library \texttt{spaCy}.
-
-\subsection{Boilerplate Removal}\label{boilerplate}
-As noted above, city websites contain a large amount of text that is uninformative for its actual content, and therefore a hindrance to understanding through algorithmic text analysis.
-This is a common issue with textual data in which informative content is embedded in technically structured documents.
-See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
-In the case of websites, lines in documents are generally quite informative, so all of our boilerplate removal efforts are done at the line level.
-
-%this is outdated; not deleting it yet in case we need it for further reference
-%Consequently we remove this content as follows: Each line of every document is compared to every line in every other document belonging to the same city.
-We count how many times each line is duplicated for that city.
-We remove any line occurring more than our chosen threshold of 10.\footnote{Empirically, lines tend to be duplicated either hundreds of times or only once or twice, if at all.} This means that each document only retains the information that is particular about it.
-We implement this algorithm through hash tables, which reduces the computational complexity from O($N^2$) to O($N$).
-Before this step is taken, we remove numbers and dates from the documents because they frequently make lines unique, despite the fact that they are virtually the same (for example different days on a city calendar).
-
-\subsection*{Boilerplate Classification}
-In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
-We sampled 500 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
-To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.
-As an example, the most common line throughout all pages of the city of Seattle consists only of the word ``total'' and occurs 103,068 times.
-Similarly, the line ``page'' occurs 58,833 times.
-Even something completely nonsensical such as ``a a'' still appears on 376 occasions.
-To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
-
-These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines).
-We then trained a number of different classifiers with this informativeness measure as the dependent variable.
-The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself.
-The purpose of these covariates is as follows:
-
-\begin{itemize}
-\item {\bf Line length:} The length of the line and the number of tokens are ways to find lines consisting of only a word or two.
-This is highly predictive of lines which are used as website headers and navigational elements, which are of zero substantive interest to us but are very effective at differentiating cities.
-These terms also happen to be fairly common, which causes them to be overweighted by the topic model.
-
-\item {\bf Number of line duplications:} To directly address the latter problem, we include a measure of the number of times a line is duplicated within a city.
-Many lines occur hundreds or even thousands of times on a single website and therefore are terms that are highly predictive of the website, which causes the topic model to find topics that are highly predictive of cities, but not substantively informative.
-
-\item {\bf Line position in the document} Since boilerplate terms such as navigational elements, headers, footers, and so on, should occur more frequently at the beginning and the end of websites, we attempt to identify such content as following: We measure the distance between the midpoint of a document and the position of a line, expressed as quantiles (to account for differing document lengths).
-Since lines can occur in multiple documents or multiple times in the same document, we take the median of these measures.
-Thus, for example, a line which often occurs at the beginning of documents might have a score of 0.45, whereas a line that tends to be found more in the center, and thus is indicative of more relevant content, might be scored with a 0.11 instead.
-\end{itemize}
-
-%Finally, the keyness measure: This indicator shows whether a term occurs disproportionally frequently in one document collection, compared to another.
-In our case, this would be one city's documents, compared to all others.
-Mathematically, this is a simple chi-square test, asserting whether the frequency of a word in a city is greater than its expected count, as determined by its count in all other documents, and the number of tokens in the city.
-The variable used in the model is the chi-square value of this test for each word (which varies and is therefore calculated individually for each city).\footnote{Or alternatively, the log of the absolute chi-square value, after which the previously negative values are made negative again.}
-
-%A regression table for this model can be found in table 3.
-The associated accuracy in 5-fold cross-validation is 0.8325.
-The cross-validation accuracy of a simplified model with only the number of characters as a covariate is 0.825 (table 4).
-A model with the four covariates described above as well as interaction terms between each of them yields an accuracy of 0.885 (table 5).
-
-%\input{tables/boilerplateClassifier1.tex}
-\input{tables/boilerplateClassifierRFMetrics.tex}
-%\input{tables/boilerplateClassifierRFImportance.tex}
-
-We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess the performance of this classifier through five-fold cross-validation.
-This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score.
-This procedure is carried out five times so that each sample is part of the test set once.
-The aggregated (mean) results of this process can be found in Table \ref{randomForest}.
-For the implementation of this method, we rely on the R package \texttt{caret}, whose random forest classifier is based on the package \texttt{ranger}.
-We use this classifier to flag and remove all lines that are not classified (based on a threshold of $p = 0.5$) as substantively meaningful.
-The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e.
-a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}.
-Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common.
-After the removal, the distribution has changed---lines of medium length now occur more frequently than extremely short ones, which are unlikely to be substantively meaningful (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}).
-Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}).
-Finally, the position of the line in the documents is not as important to the random forest, and this also shows in the results.
-However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).
-Table \ref{tabBoilerplateIllustration} provides further illustration by listing the top 10 most likely boilerplate lines (in Anchorage, AK) -- all of which were flagged as such with a probability of 1.
-After all the preprocessing is set and done, our corpus consists of 259,099 documents.
-
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
-    \label{boilerplate_before_after1}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
-\end{figure}
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, extremely short lines are less common.}
-    \label{boilerplate_before_after2}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
-\end{figure}
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.
-After the boilerplate content is removed, lines that are duplicated hundreds or thousands of times are less common.}
-    \label{boilerplate_before_after3}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
-\end{figure}
-\begin{figure}[htp]
-    \centering
-    \caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK. After the boilerplate content is removed, lines at the beginning and end of documents are less common.}
-    \label{boilerplate_before_after4}
-    \includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
-\end{figure}
-
-\section{Partisan Language on Municipal Websites}
-
-We illustrate the analysis of municipal website content by studying differences in website content based on the party of the mayor.
-As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance.
-However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance.
-They find that cities with Democratic mayors spend a smaller share of their budgets on public safety, but that mayoral partisanship does not appear to be significantly related to spending in most other areas, where cities have less discretion.
-As opposed to budget allocation or even the presence/absence of policies, cities have a great deal of discretion regarding what is emphasized on their websites, and how policies are framed.
-Since (1) city governments have great discretion in composing their websites, (2) modifying website content is low cost relative to other policy changes, and (3), as reviewed above, city websites provide an effective and often-used means of communication with city residents.
-
-%BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
-As noted by \cite{GrimmerStewart2013}, for most applications, bag-of-words approaches have been found to be more than sufficient.
-Furthermore, there is reason to believe that city government websites are a particularly `safe' case for bag-of-words methods due to their informative, manner-of-fact based language.
-It is extremely unlikely for these pages to feature ambiguous language such as an abundance of negation or even sarcasm.
-
-\input{tables/tabBoilerplateIllustration.tex}
-
-\subsubsection{Analytical approach: Structural topic modeling}
-In order to analyze content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class of text-as-data methods, the structural topic model, developed by \citet{Roberts2014}.
-Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the structural topic model a topic is a multinomial distribution defined on the word types in the dictionary.
-Each word occurrence in a document is attributed with a single topic label.
-The word topic assignments are also drawn from a multinomial distribution.
-The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics.
-For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic.
-For our primary empirical investigation, the structural topic model provides with a tool with which to estimate the relationship between the party of the city's mayor and the prevalence of each topic we estimate.
-A topic interpreted through post-hoc analysis of the collective meaning of the most likely words to be drawn from the multinomial distribution defined by the respective topic.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
+\section{Supplemental Informational on Topic Modeling Application}
 
 The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.
-Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here.
-We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
+We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.\footnote{Since our corpus is at the larger end of that spectrum, we also estimated a model with 120 topics, but found no notable differences.} We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
 Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
 Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city.
-Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.
+Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
 
-\subsubsection{Structural topic model results}
+\subsection{Supplemental results}
 
-The results are shown in Table \ref{tabSTMtopwords60}.
-The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom.
-The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic.
-The topics that are entirely white have 90\% credible intervals on the effect of the mayoral party that include zero.
+In Tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2} we present results of the STM with 120 topics organized according to the effect of mayoral partisanship on topic prevalence.
+The partisan themes in the 120-topic STM mirror those in the 60-topic model, with cities led by Democratic mayors focused disproportionately on finances (e.g., Topics 75, 71, 61) and social problems (e.g., Topics 93, 101, 39, 52), and cities led by Republican mayors focused disproportionately on basic services and utilities (e.g., Topics 114, 11,  86, 116).
 
-Many of the topics associated with Democrats fit with what we understand to be national party priorities.
-Topic 21, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
-Similarly, employee rights are represented in Topic 47.
-Democrats also exhibit a strong preference for words related to public finances, such as Topic 32 ('budget', 'revenue', 'expenditure') as well as Topic 19 ('debt', 'bond', 'financial').
-We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
-This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, 55 ('robbery', 'homicide', 'sergeant') (a comparable topic is also the most Democratic topic in the model with 120 topics in tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2} of the Appendix) depicts Democrats' complicated relationship with law enforcement.
-On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
-On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on the police, even after controlling for crime \citep{Einstein2015}.
-Finally, Democrats also focus more on the deliberative process of policymaking, as topics 31 ('agenda', 'committee'), 34 ( `comment', `draft', `feedback'), 48 (`absent', `aye', `nay'), and 37 ('audit', 'procedure', 'oversight') attest to.
-This openness regarding the policy process on behalf of cities with Democratic mayors fits with the findings of \citet{grimmelikhuijsen2012developing}, which are that left-wing local governments exhibit greater transparency via website content.
+\input{tables/stmTopWords120_1.tex}
+\input{tables/stmTopWords120_2.tex}
 
-City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government.
-Basic utilities such as energy (Topic 7), fire protection (Topic 17), drinking water (53), and garbage removal (Topic 49) are included among those topics that are more prevalent in cities with Democratic mayors.
-Similarly, protecting citizens from natural disasters is a focus in topics 1 ('storm', 'runoff', 'drainage') and 42 ('breastfeed', 'infection', 'mosquito' -- and so, essentially, about the Zika virus), which may reflect the greater prevalence of Republican mayors in the southeast, a region which is more often affected by hurricanes and tropical diseases.
+In Tables \ref{tabSTMtopwords60_income} and \ref{tabSTMtopwords60_population} we present the topics ordered according to the effects of median income and population, respectively.
+Considering income-based variation in topics, there are several topics prevalent in more wealthy cities that focus on initiatives that go well-beyond standard city services---downtown and building revitalization (Topics 39 and 12), renewable energy (Topic 20), bike/pedestrian-oriented development (Topic 60), wildlife conservation (Topic 3).
+Such topics cannot be found among those that are more prevalent in less wealthy cities.
+When it comes to population, more populous cities deal disproportionately with issues related to public health (Topics  2 and 11), crime (Topic 59), homelessness (Topic 52), and diversity (Topic 6).
 
-%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{gerber2011mayors}.
-However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
-Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Republican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted HTML, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
+\input{tables/stmTopWords60_income.tex}
+\input{tables/stmTopWords60_population.tex}
 
-%When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
-Furthermore, as with the fightin' words approach, some smaller degree of focus on money (see topic 1) is still evident.
-For Republicans, topics 2 to 4 seem to be, once again about infrastructure and utilities, pointing to a certain degree of robustness in these results, as well as the emergence of a trend.
-The results produced by the structural topic model are not flawless, but the two parties do seem to have somewhat consistent themes on which they focus on in both states.
-Furthermore, in comparison to the fightin' words approach, the ability of the structural topic model to form coherent topics is quite evident and helpful in the interpretation of the results.
-
-%An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
-This is facilitated by the structural topic model, which uses document metadata t to account for variation in topics \citep{Roberts2014}.
-However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
-Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
-Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
-The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
-Interestingly the same is true for a number of the cities as well.
-The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
-
-%Partisan top words - stm Louisiana -- Rep
-%\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
-
-%Partisan top words - stm Louisiana -- Dem
-%\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
-
-%Partisan top words - stm Louisiana -- Rep
-%\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
-
-%Partisan top words - stm Louisiana -- Dem
-%\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
-
-%\subsubsection{Prediction with SVM}
-%An alternative approach to the problem is to ignore topics entirely and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
-Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
-Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
-However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
-Instead, we ranked the features according to tf-idf and selected the top 5000.
-These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross-validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
-Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
-Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
-
-%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backward: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-%Heatmaps
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
-%    \label{heatmaps_weights}
-%    \includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
-%\end{figure}
-
-%US map
-\begin{figure}[htp]
-    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-    \includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
-        \caption{Map of the cities in the corpus in the contiguous U.S.
-The corpus also includes Alaska.
-In the analysis, only cities in California, Indiana, Louisiana, New York, Texas and Washington are used.
-The colors represent the partisanship of the mayor (blue corresponding to Democrats and red to Republicans).}
-    \label{us_map}
-\end{figure}
-
-%stm results
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
-This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
-%    \label{stm_results}
-%%    \includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-%\end{figure}
-
-%Partisan top words - topic model Indiana
-%\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
-
-%Partisan top words - topic model Louisiana
-%\input{tables/partisanTopWordsLA.tex} %tabLDALA
-
-%Partisan top words - stm Indiana
-%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
-
-%Partisan top words - stm Louisiana
-%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
-
-%Some basic descriptive statistics of documents by party
-%\input{tables/descriptiveStatisticsPartisanIN.tex}
-
-%Some basic descriptive statistics of documents by party
-%\input{tables/descriptiveStatisticsPartisanLA.tex}
-
-%fightin words results
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-%        \caption{Total number of lines retained at a given threshold for removing duplicated lines.
-For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
-%    \label{linesCutoff}
-%\end{figure}
-
-%\section{Ground truth test}
-%In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
-Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
-However, the aspirations some mayors have shown towards higher offices - in some cases, even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
-One of the most vicious and blatantly partisan cleavages in current U.S.
-politics - the debate surrounding sanctuary cities - has seen mayors in a central role.
-Research into local politics has shown that partisan elections consistently have greater turnout \citep{Schaffner2001}.
-When voters are denied this cue, they make use of other, and considerably more irrational heuristics, such as name, gender, or occupation of the contenders.
-Consequently, it only makes sense for any office-seeking politician to emphasize their partisanship.
-Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
-%
-%In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
-As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
-Consequently, they are very likely to emphasize conservative/liberal values on this platform.
-If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
-%
-%Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
-We do the same for the city documents, and then compare the four document collections using cosine similarity.
-This measure is the cosine between the angle of two vectors, in this case, the frequencies of all words in the two vocabularies.
-Compared to a simple Euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
-The cosine measure between two documents ranges between 0 and 1, 0 signifying absolutely no correlation, and 1 perfect overlap.
-Figure \ref{groundtruth} shows the result of this test.
-The expectation is for a greater similarity between Republican cities and the Republican ground truth than Republican cities and Democratic ground truth - and vice versa.
-At present, however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
-
-%ground truth test
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
-%    \caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
-%    \label{groundtruth}
-%\end{figure}
-%
-%%ground truth test
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
-%    \caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
-%    \label{groundtruth}
-%\end{figure}
-
-%Ground truth test between top100 mayors and IN + LA; with bootstrapped confidence bounds
-% label: groundtruth_bootstrapped
-%\input{tables/groundtruth_bootstrapped.tex}
-
-%\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
-
-\input{tables/stmTopWords60.tex} %\ref{tabSTMtopwords2}
-
-\section{Conclusion}
-
-We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
-This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
-The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language.
-Government website contents can, and have been, used to study questions related representation, government transparency, and public policy priorities.
-The methods we develop can be used to scale up projects involving website data collection by automating the process.
-
-In terms of pure scope, our method is superior to the existing approaches.
-Manual content analysis (see, for example, \cite{Druckman2009}) relies on research assistants reading and evaluating websites, and therefore might struggle to provide a complete understanding of even individual websites, which often contain thousands of pages.
-Scrapers conventionally used in the social sciences (see, for example, \citealt{Cryer2017}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
-By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
-Consequently, our approach facilitates the kind of bulk data collection and analysis necessitated by an ever-growing web.
-
-Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
-We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
-
-We offer several contributions that will be valuable in future research endeavors.
-First, the data collected in the current study can be used for comparative analysis of US city website contents.
-Second, the pipeline we present can be used as a set of procedures to follow in gathering large-scale datasets of textual contents from other samples of governments.
-For example, the pipeline we have developed could be used to build comparative datasets of state or federal bureaucratic agencies.
-Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.
+\section*{Funding}
+This work was supported by the National Science Foundation [1320219, 1637089, 1641047].
 
@@
 
-\newpage
-
-\bibliographystyle{apsr} % apsr stopped working for me
+\bibliographystyle{chicago} % apsr stopped working for me
 %\bibliographystyle{plainnat}
 \bibliography{ref}
-
-\newpage
-\section*{Appendix}
-
-\input{tables/stmTopWords120_1.tex}
-\input{tables/stmTopWords120_2.tex}
 

### 2019-05-26 paper/tables/stmTopWords60_KeepEverything.tex
stm results from the keepEverythingExtractor in boilerpipe

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Sun May 26 16:14:58 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{rllllllll}
  \hline
 \# & Top Word 1 & Top Word 2 & Top Word 3 & Top Word 4 & Top Word 5 & Top Word 6 & \multicolumn{2}{c}{Tokens assigned} \\ 
  \hline
 30 & \cellcolor{red!80}riverfront & \cellcolor{red!80}department & \cellcolor{red!80}authority & \cellcolor{red!80}transit & \cellcolor{red!80}police & \cellcolor{red!80}enjoy & \mybar{212} \\ 
   55 & \cellcolor{red!60}posted & \cellcolor{red!60}dream & \cellcolor{red!60}celebration & \cellcolor{red!60}broadcast & \cellcolor{red!60}ballpark & \cellcolor{red!60}football & \mybar{544} \\ 
    5 & \cellcolor{red!50}trust & \cellcolor{red!50}revocable & \cellcolor{red!50}leisure & \cellcolor{red!50}learn & \cellcolor{red!50}mfr & \cellcolor{red!50}living & \mybar{327} \\ 
   56 & \cellcolor{red!30}click & \cellcolor{red!30}reserved & \cellcolor{red!30}trademark & \cellcolor{red!30}password & \cellcolor{red!30}search & \cellcolor{red!30}connected & \mybar{387} \\ 
   49 & \cellcolor{red!20}chair & \cellcolor{red!20}agenda & \cellcolor{red!20}subcommittee & \cellcolor{red!20}briefing & \cellcolor{red!20}presentation & \cellcolor{red!20}committee & \mybar{416} \\ 
   47 & \cellcolor{red!10}motion & \cellcolor{red!10}second & \cellcolor{red!10}adjourn & \cellcolor{red!10}carry & \cellcolor{red!10}whiting & \cellcolor{red!10}unanimous & \mybar{451} \\ 
   51 & \cellcolor{red!10}storm & \cellcolor{red!10}drain & \cellcolor{red!10}sanitary & \cellcolor{red!10}water & \cellcolor{red!10}sewer & \cellcolor{red!10}infiltration & \mybar{391} \\ 
   43 & \cellcolor{red!10}article & \cellcolor{red!10}subsection & \cellcolor{red!10}shall & \cellcolor{red!10}provision & \cellcolor{red!10}chapter & \cellcolor{red!10}unlawful & \mybar{467} \\ 
    2 & \cellcolor{red!10}virus & \cellcolor{red!10}tuberculosis & \cellcolor{red!10}infection & \cellcolor{red!10}influenza & \cellcolor{red!10}hepatitis & \cellcolor{red!10}cannabis & \mybar{2555} \\ 
    1 & \cellcolor{red!10}councilman & \cellcolor{red!10}whereas & \cellcolor{red!10}alderman & \cellcolor{red!10}resolved & \cellcolor{red!10}yea & \cellcolor{red!10}resolution & \mybar{576} \\ 
   59 & \cellcolor{red!10}subcontractor & \cellcolor{red!10}proposer & \cellcolor{red!10}bidder & \cellcolor{red!10}bid & \cellcolor{red!10}consultant & \cellcolor{red!10}subcontract & \mybar{508} \\ 
   33 & \cellcolor{red!10}eff & \cellcolor{red!10}inf & \cellcolor{red!10}effluent & \cellcolor{red!10}ether & \cellcolor{red!10}batch & \cellcolor{red!10}isomer & \mybar{1240} \\ 
   54 & \cellcolor{red!10}dwelling & \cellcolor{red!10}alteration & \cellcolor{red!10}plumbing & \cellcolor{red!10}canceled & \cellcolor{red!10}plumb & \cellcolor{red!10}mechanical & \mybar{311} \\ 
   12 & \cellcolor{red!10}think & \cellcolor{red!10}something & \cellcolor{red!10}somebody & \cellcolor{red!10}appreciate & \cellcolor{red!10}seem & \cellcolor{red!10}everything & \mybar{2911} \\ 
   21 & \cellcolor{red!10}artist & \cellcolor{red!10}ceremony & \cellcolor{red!10}jazz & \cellcolor{red!10}celebrate & \cellcolor{red!10}prize & \cellcolor{red!10}yoga & \mybar{3326} \\ 
   11 & \cellcolor{red!10}disaster & \cellcolor{red!10}evacuation & \cellcolor{red!10}marshal & \cellcolor{red!10}apparatus & \cellcolor{red!10}tornado & \cellcolor{red!10}aircraft & \mybar{1174} \\ 
    4 & \cellcolor{red!10}craftsman & \cellcolor{red!10}architecture & \cellcolor{red!10}facade & \cellcolor{red!10}distinctive & \cellcolor{red!10}architectural & \cellcolor{red!10}historic & \mybar{1634} \\ 
   34 & \cellcolor{red!10}contributor & \cellcolor{red!10}filer & \cellcolor{red!10}officeholder & \cellcolor{red!10}political & \cellcolor{red!10}payee & \cellcolor{red!10}candidate & \mybar{272} \\ 
   17 & \cellcolor{red!10}assessor & \cellcolor{red!10}informal & \cellcolor{red!10}taxpayer & \cellcolor{red!10}doc & \cellcolor{red!10}viewing & \cellcolor{red!10}determination & \mybar{442} \\ 
   18 & \cellcolor{red!10}setback & \cellcolor{red!10}variance & \cellcolor{red!10}plat & \cellcolor{red!10}height & \cellcolor{red!10}thence & \cellcolor{red!10}frontage & \mybar{472} \\ 
   19 & \cellcolor{red!10}findings & \cellcolor{red!10}tank & \cellcolor{red!10}carcinogen & \cellcolor{red!10}string & \cellcolor{red!10}qty & \cellcolor{red!10}yon & \mybar{247} \\ 
    3 & \cellcolor{white}vend & \cellcolor{white}meat & \cellcolor{white}utensil & \cellcolor{white}towel & \cellcolor{white}fat & \cellcolor{white}cheese & \mybar{2791} \\ 
   38 & \cellcolor{white}application & \cellcolor{white}applicant & \cellcolor{white}must & \cellcolor{white}copy & \cellcolor{white}tenant & \cellcolor{white}mail & \mybar{390} \\ 
   60 & \cellcolor{white}wetland & \cellcolor{white}shoreline & \cellcolor{white}vernal & \cellcolor{white}riparian & \cellcolor{white}habitat & \cellcolor{white}marsh & \mybar{1986} \\ 
   26 & \cellcolor{white}student & \cellcolor{white}teacher & \cellcolor{white}classroom & \cellcolor{white}beech & \cellcolor{white}academic & \cellcolor{white}doe & \mybar{832} \\ 
    7 & \cellcolor{blue!10}obesity & \cellcolor{blue!10}sugary & \cellcolor{blue!10}epidemic & \cellcolor{blue!10}drink & \cellcolor{blue!10}sensible & \cellcolor{blue!10}ounce & \mybar{98} \\ 
   20 & \cellcolor{white}garland & \cellcolor{white}invoice & \cellcolor{white}assoc & \cellcolor{white}rouge & \cellcolor{white}baton & \cellcolor{white}vendor & \mybar{524} \\ 
   31 & \cellcolor{blue!10}credit & \cellcolor{blue!10}docket & \cellcolor{blue!10}bbl & \cellcolor{blue!10}agent & \cellcolor{blue!10}month & \cellcolor{blue!10}app & \mybar{61} \\ 
   40 & \cellcolor{white}slideshow & \cellcolor{white}arrow & \cellcolor{white}printer & \cellcolor{white}stumble & \cellcolor{white}blogger & \cellcolor{white}google & \mybar{189} \\ 
    8 & \cellcolor{blue!10}deductible & \cellcolor{blue!10}outpatient & \cellcolor{blue!10}prescription & \cellcolor{blue!10}coinsurance & \cellcolor{blue!10}copay & \cellcolor{blue!10}inpatient & \mybar{809} \\ 
   41 & \cellcolor{blue!10}playground & \cellcolor{blue!10}park & \cellcolor{blue!10}tennis & \cellcolor{blue!10}picnic & \cellcolor{blue!10}viewpoint & \cellcolor{blue!10}ravine & \mybar{405} \\ 
   45 & \cellcolor{blue!10}taxable & \cellcolor{blue!10}res & \cellcolor{blue!10}deed & \cellcolor{blue!10}value & \cellcolor{blue!10}homestead & \cellcolor{blue!10}star & \mybar{106} \\ 
   36 & \cellcolor{blue!10}thickness & \cellcolor{blue!10}fitting & \cellcolor{blue!10}conduit & \cellcolor{blue!10}conductor & \cellcolor{blue!10}ductile & \cellcolor{blue!10}trench & \mybar{1756} \\ 
   22 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}significant & \cellcolor{blue!10}adverse & \cellcolor{blue!10}sensitive & \mybar{346} \\ 
   35 & \cellcolor{blue!10}householder & \cellcolor{blue!10}universe & \cellcolor{blue!10}margin & \cellcolor{blue!10}poverty & \cellcolor{blue!10}race & \cellcolor{blue!10}census & \mybar{251} \\ 
   15 & \cellcolor{blue!10}imp & \cellcolor{blue!10}amt & \cellcolor{blue!10}micron & \cellcolor{blue!10}rend & \cellcolor{blue!10}land & \cellcolor{blue!10}sustain & \mybar{117} \\ 
   16 & \cellcolor{blue!10}dist & \cellcolor{blue!10}applied & \cellcolor{blue!10}col & \cellcolor{blue!10}occupancy & \cellcolor{blue!10}monoxide & \cellcolor{blue!10}valuation & \mybar{123} \\ 
   58 & \cellcolor{blue!10}pickup & \cellcolor{blue!10}bag & \cellcolor{blue!10}recyclable & \cellcolor{blue!10}bin & \cellcolor{blue!10}landfill & \cellcolor{blue!10}curbside & \mybar{651} \\ 
   46 & \cellcolor{blue!10}contracted & \cellcolor{blue!10}medicare & \cellcolor{blue!10}allocation & \cellcolor{blue!10}subtotal & \cellcolor{blue!10}unencumbered & \cellcolor{blue!10}payroll & \mybar{236} \\ 
   14 & \cellcolor{blue!10}perm & \cellcolor{blue!10}queue & \cellcolor{blue!10}delay & \cellcolor{blue!10}peak & \cellcolor{blue!10}adj & \cellcolor{blue!10}volume & \mybar{232} \\ 
   39 & \cellcolor{blue!10}successor & \cellcolor{blue!10}franchisee & \cellcolor{blue!10}covenant & \cellcolor{blue!10}redemption & \cellcolor{blue!10}bankruptcy & \cellcolor{blue!10}obligation & \mybar{678} \\ 
   44 & \cellcolor{blue!10}prune & \cellcolor{blue!10}circumference & \cellcolor{blue!10}tree & \cellcolor{blue!10}planting & \cellcolor{blue!10}shrub & \cellcolor{blue!10}root & \mybar{1798} \\ 
   23 & \cellcolor{blue!10}tax & \cellcolor{blue!10}increment & \cellcolor{blue!10}deduction & \cellcolor{blue!10}abatement & \cellcolor{blue!10}assessed & \cellcolor{blue!10}levy & \mybar{397} \\ 
    6 & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}exhaust & \cellcolor{blue!10}renewable & \cellcolor{blue!10}bio & \cellcolor{blue!10}emission & \cellcolor{blue!10}coal & \mybar{859} \\ 
   57 & \cellcolor{blue!10}savings & \cellcolor{blue!10}costs & \cellcolor{blue!10}capital & \cellcolor{blue!10}ltd & \cellcolor{blue!10}improvement & \cellcolor{blue!10}excise & \mybar{172} \\ 
   27 & \cellcolor{blue!10}density & \cellcolor{blue!10}mixed & \cellcolor{blue!10}planned & \cellcolor{blue!10}infill & \cellcolor{blue!10}orient & \cellcolor{blue!10}retail & \mybar{365} \\ 
   52 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}bike & \cellcolor{blue!10}route & \cellcolor{blue!10}bus & \cellcolor{blue!10}curb & \mybar{572} \\ 
   48 & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}asset & \cellcolor{blue!10}governmental & \cellcolor{blue!10}assets & \cellcolor{blue!10}investment & \cellcolor{blue!10}debt & \mybar{342} \\ 
   37 & \cellcolor{blue!10}supervisor & \cellcolor{blue!10}technician & \cellcolor{blue!10}aide & \cellcolor{blue!10}incumbent & \cellcolor{blue!10}employee & \cellcolor{blue!10}trainee & \mybar{758} \\ 
   32 & \cellcolor{blue!10}introduced & \cellcolor{blue!10}absent & \cellcolor{blue!10}councilor & \cellcolor{blue!10}preside & \cellcolor{blue!10}digest & \cellcolor{blue!10}legislator & \mybar{615} \\ 
   28 & \cellcolor{blue!10}persona & \cellcolor{blue!10}para & \cellcolor{blue!10}sin & \cellcolor{blue!10}ante & \cellcolor{blue!10}junta & \cellcolor{blue!10}combo & \mybar{2376} \\ 
   24 & \cellcolor{blue!10}audit & \cellcolor{blue!10}procedure & \cellcolor{blue!10}effectiveness & \cellcolor{blue!10}ensure & \cellcolor{blue!10}software & \cellcolor{blue!10}timely & \mybar{497} \\ 
   42 & \cellcolor{blue!10}budget & \cellcolor{blue!10}endorse & \cellcolor{blue!10}revenue & \cellcolor{blue!10}endorsed & \cellcolor{blue!10}balance & \cellcolor{blue!10}expenditure & \mybar{232} \\ 
   13 & \cellcolor{blue!10}homeless & \cellcolor{blue!10}affordable & \cellcolor{blue!10}affordability & \cellcolor{blue!10}housing & \cellcolor{blue!10}supportive & \cellcolor{blue!10}homelessness & \mybar{380} \\ 
   10 & \cellcolor{blue!20}impound & \cellcolor{blue!20}taxicab & \cellcolor{blue!20}license & \cellcolor{blue!20}cat & \cellcolor{blue!20}dog & \cellcolor{blue!20}neuter & \mybar{700} \\ 
    9 & \cellcolor{blue!20}strategy & \cellcolor{blue!20}stakeholder & \cellcolor{blue!20}focus & \cellcolor{blue!20}goal & \cellcolor{blue!20}engagement & \cellcolor{blue!20}outreach & \mybar{732} \\ 
   25 & \cellcolor{blue!20}profile & \cellcolor{blue!20}executive & \cellcolor{blue!20}bend & \cellcolor{blue!20}sustainability & \cellcolor{blue!20}cleanup & \cellcolor{blue!20}rates & \mybar{110} \\ 
   53 & \cellcolor{blue!30}theft & \cellcolor{blue!30}burglary & \cellcolor{blue!30}fwy & \cellcolor{blue!30}aggravated & \cellcolor{blue!30}aggravate & \cellcolor{blue!30}robbery & \mybar{253} \\ 
   29 & \cellcolor{blue!40}sitemap & \cellcolor{blue!40}clerk & \cellcolor{blue!40}calendar & \cellcolor{blue!40}online & \cellcolor{blue!40}bureau & \cellcolor{blue!40}alert & \mybar{124} \\ 
   50 & \cellcolor{blue!60}arrest & \cellcolor{blue!60}complainant & \cellcolor{blue!60}allegation & \cellcolor{blue!60}shooting & \cellcolor{blue!60}homicide & \cellcolor{blue!60}victim & \mybar{1665} \\ 
   \hline
\end{tabular}
\endgroup
\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
\label{tabSTMtopwords60}
\end{table}

### 2019-05-26 07_topicModel/01_stm_estimation_KeepEverything.R

@@ -1,0 +1,54 @@
+library('quanteda')
+library('stm')
+library('tidyr')
+library('ggplot2')
+library('scales')
+library('stringr')
+set.seed(1)
+
+# load(file = "../06_preprocessing/out/preprocessing_finished.rdata")
+# #merge in census covariates
+# load("../04_extractText/out/citydocs.rdata")
+# # load("../00_scrapeCovariates/out/websiteMetadata_Census.rdata")
+# # websiteMeta <- subset(websiteMeta, select = c(State_City, B01001_001E, B19013_001E))
+# # d <- merge(d, websiteMeta, by = "State_City")
+# d_reordered <- d[match(names(tks_all), d$id),]
+# docvars(tks_all) <- d_reordered
+# rm(websiteMeta, d, d_reordered)
+# #use only the states for which we have data on multiple cities
+# tks_all <- tokens_subset(tks_all, State %in% c("Indiana", "Louisiana", "New York", "California", "Washington", "Texas"))
+# #convert to dfm and then stm
+# d_dfm <- dfm(tks_all)
+# d_stm <- convert(d_dfm, to = "stm")
+# save(d_stm, file = "out/ready_for_stm.rdata")
+load("../06_preprocessing/out/stm_corpus_KeepEverything.rdata")
+
+#Number of topics
+numtopics <- 60
+
+#Train the model
+stmFit <- stm(documents = d_stm$documents,
+              vocab = d_stm$vocab,
+              data = d_stm$meta,
+              K = numtopics, 
+              prevalence =~ party + State + B01001_001E + B19013_001E,
+              max.em.its = 9999,
+              init.type = "Spectral")
+
+#save.image("rfiles/stmSession2, _Party.rdata")
+save.image(paste("out/stmSession_model_", numtopics, "_KeepEverything.rdata", sep = ""))
+
+#set seed again in case the script was restarted from here
+set.seed(1)
+
+#Estimate effects from the model outputs
+sims <- 1000
+
+#re-estimate the effects, this time do 1000 draws from the posterior
+prep <- estimateEffect(formula = 1:numtopics ~ party + State + B01001_001E + B19013_001E, 
+                       stmobj = stmFit,
+                       metadata = d_stm$meta, 
+                       uncertainty = "Global",
+                       nsims = sims)
+
+save.image(paste("out/stmSession_sim_", numtopics, "_KeepEverything.rdata", sep = ""))

### 2019-05-28 paper/manuscript_paNote.tex
writing up the keep everything analysis

@@
 The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{garymayor}.
-Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
+The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
 The Mayor's message represents a relatively small fraction of the total text on the page.
@@
 The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.
-The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in Figure \ref{fig:garybp}.
-We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.
+The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}.
+We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data.
+In this replication analysis we show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
+}
 

### 2019-05-28 paper/manuscript_paNote_OA.tex
writing up the keep everything analysis

@@
 \subsection{Supplemental results}
+
+In Table \ref{tabSTMtopwords60keep}, we present topic results from an STM, and mayoral party effect, estimated on data processed using a minimal HTML parser, implemented as the 'KeepEvertything' algorithm in the boilerpipeR package.
+An illustration of the content removed by the full boilerpipe procedure is given by Topic 5.
+This is the fourth-most Republican topic, and is a website boilerplate topic, with top words 'click', 'reserved', 'trademark', 'password', 'search', and 'connected'.
+As further illustration, the second-most Democratic topic is another website boilerplate topic, with top words 'sitemap', 'clerk', 'calendar', 'online', 'bureau', and 'alert'.
+We do not see any clear boilerplate topics when using data processed using boilerpipe.
+
+\input{tables/stmTopWords60_KeepEverything.tex}
 

### 2019-05-31 paper/manuscript_paNote.tex
revising with javascript comments

@@
 By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
-For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.
+For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ In an attempt to assess the consequences of this limitation, we investigated whether the presence of JavaScript was related to the amount of text we gathered from the website---with the concern being that the presence of JavaScript would block us from gathering most of a city's website content.
+We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
+This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.
+We would surely gather more content if we could scrape the dynamic content, but JavaScript does not completely block access to content on most city sites on which it is used.}
 

### 2019-05-31 paper/manuscript_paNote.tex
cutting some words

--- 2019-05-28 paper/manuscript_paNote.tex
@@
 \section{The Web to Text Pipeline}
-In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents that are suitable for comparative analysis with text as data methods.
-Here, we address three methodological challenges.
+In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents.
+We address three methodological challenges.
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
@@
 
-We leverage methods developed in the information retrieval literature to deal with this problem.
-These boilerplate detection tools are classifiers which rely on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is useful.
 We rely on the \texttt{boilerpipe} method described in \cite{Kohlschutter2010}, which is designed to extract blocks of substantive text from websites, and is implemented through the R package \texttt{boilerpipeR}.
+\texttt{boilerpipe} is a classifier that relies on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is substantive.
 The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.
@@
 We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data.
-In this replication analysis we show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
+We show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
 }
@@
 To this end, we turn to a common method in natural langauge processing---part-of-speech (POS) tagging and named entity recognition (NER).
-As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient) as well as works of art (which frequently feature statutes, plans, etc.).} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, and adjectives.
+As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.
 Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
-Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word.
-For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''.
+Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word.
 } POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
-This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources.
 To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).
@@
 
-In order to analyze content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
+To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
 Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary.
@@
 For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.
+\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
+We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
+This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.}
 

### 2019-07-31 paper/manuscript_psrmNote.tex
comment on the longevity of the software we use (to address Gill's comment)

--- 2019-05-31 paper/manuscript_paNote.tex
@@
 
-\noindent PA Letter Requirements:\\
-2-4 pages\\
-no longer than 1500-3000 words\\
-1-3 small display items (figures, tables, or equations)\\
-200-300 word abstract\\
-
 \section{Introduction}
@@
 The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
-Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.%Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
+Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.
+We make a software recommendation for each of these steps and gather most of them our R package, \texttt{gov2text}.
+All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem.
+As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.%Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
 We will clarify this distinction as we describe steps in our pipeline.
@@
 The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
-The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{garymayor}.
+The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{fig:garymayor}.
 The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
@@
 
-\subsubsection{Extracting Text from PDF, XML, DOC, DOCX and TXT}
+\subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
 Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
 The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
-Files of type XML, DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
+Files of type DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
 
@@
 For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic.
-For our primary empirical investigation, the STM provides with a tool with which to estimate the relationship between the party of the city's mayor and the prevalence of each topic we estimate.
+For our primary empirical investigation, the STM provides a tool to estimate the relationship between the party of the city's mayor and the prevalence of each topic.
 We also include the municipality's population and median income as covariates.
@@
 The results are shown in Table \ref{tabSTMtopwords60}.
-First, it is notable that the 95\% credible includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor.
+First, it is notable that the 95\% credible interval includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor.
 Many of the topics associated with Democrats fit with what we understand to be national party priorities.
 Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
-Topic {\bf 6} ('race', 'islander','census,'female') covers racial and gender identity issues.
+Topic {\bf 6} ('race', 'islander', 'census, 'female') covers racial and gender identity issues.
 Similarly, employee rights and benefits are represented in topics \textbf{10} and \textbf{29}.
@@
 We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}).
-This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
+This finding is consistent with \cite{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
 A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime.
@@
 Similarly, zoning issues figure prominently in the set of republican topic (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules.
-The Democratic topics also include one that is somewhat focused on zoning Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.
+The Democratic topics also include one that is somewhat focused on zoning, Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.
 
@@
 By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
-For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.
-\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
+For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
 We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.

### 2019-07-31 paper/manuscript_psrmNote.tex
uncommented a note about how not everything we do is universally applicable (this was in the original submission); since the reviewers clearly chafed against this

@@
 All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem.
-As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.%Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
+As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.
+Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
 We will clarify this distinction as we describe steps in our pipeline.

### 2019-07-31 paper/manuscript_psrmNote.tex
reworded the section on filetype detection to put the high-level methid first, and only then the implementation. Also mention that the underlying library will already be installed on many systems, to assuage Gill's concern

@@
 For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-To accurately assess file types, we rely on the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which determines the type of a file on the basis of its file signature.
-This short sequence of bytes at the start (and sometimes end) of files is unique for each file type and therefore allows its correct identification.
+A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification.
+We implement this method using the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions, Mac OS X, and has also been ported to Windows.
 

### 2019-07-31 paper/manuscript_psrmNote.tex
changed magic-related details to footnote

@@
 A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification.
-We implement this method using the R package \texttt{wand} \citep{wand}, which is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions, Mac OS X, and has also been ported to Windows.
+We implement this method using the R package \texttt{wand} \citep{wand}.\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}
 

### 2019-07-31 paper/manuscript_psrmNote.tex
re-worded the boilerpipe section to focus a bit more on the wider boilerplate extraction literature rather than just this algorithm

@@
 
-We rely on the \texttt{boilerpipe} method described in \cite{Kohlschutter2010}, which is designed to extract blocks of substantive text from websites, and is implemented through the R package \texttt{boilerpipeR}.
-\texttt{boilerpipe} is a classifier that relies on both structural features, such as HTML tags, as well as text statistics such as word and sentence length to estimate whether a given portion of an HTML file is substantive.
+A subfield of the information retrieval literature, dealing with boilerplate extraction, can offer a solution to this problem.
+The goal of this branch of research is to develop algorithms with the ability to estimate whether a given portion of an HTML file is substantive.
+To this end, structural features, such as HTML tags (which are not sufficiently informative on their own), text statistics such as word and sentence length, as well as other heuristics are used.
+We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
 The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.

### 2019-07-31 paper/manuscript_psrmNote.tex
added a footnote citing a paper which explains why extracting text from pdfs is surprisingly difficult

@@
 \subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
-Other files are read in through the \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
+The extraction of information from other text-based file formats is more straightforward.\footnote{See \cite{Berg2012} for a discussion of why extracting text from PDFs is nevertheless nontrivial.} To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
 The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.

### 2019-07-31 paper/manuscript_psrmNote.tex
plastered the preprocessing section with 'proceed with caution' and 'use your own brain' warnings

@@
 Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}.
+As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model.
+The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing.
 The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites.
@@
 
-To this end, we turn to a common method in natural langauge processing---part-of-speech (POS) tagging and named entity recognition (NER).
-As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.
-Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
+To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER).
+In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended.
+Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
 Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word.

### 2019-08-01 paper/manuscript_psrmNote_OA.tex
added a (very long) footnote in the appendix on why we don't use the Internet Archive

--- 2019-05-28 paper/manuscript_paNote_OA.tex
@@
 
-To download the websites, we rely on the Unix command line tool \texttt{wget}.
-This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
+To download the websites, we rely on the Unix command line tool \texttt{wget}.\footnote{An alternative source of web data which has attained some popularity within the digital humanities is the Internet Archive's Wayback machine (\url{https://archive.org/}), which preserves snapshots of websites over time.
+In theory, this would be very useful to projects such as ours, since it would allow us to measure the evolution of websites over time, in response to changes in city executives.
+However, the Wayback Machine suffers from some limitations that, in our eyes, inhibit its usefulness for scientific research in general, and our project in particular.
+First of all, the Internet Archive does not conduct all of its web crawling itself.
+Rather, third parties donate their crawling data to the Internet Archive.
+This means that the source of the data varies and the crawling process often remains opaque, which is a problem with respect to scientific transparency.
+Second, this also means that the crawling isn’t done in regular intervals unless the website in question is extremely prominent.
+Our research is focused on municipal websites, many of which are fairly obscure, preventing the Wayback Machine from being useful to us.
+For example, as of the time of writing, the website of Attica, IN, has only been crawled 25 times since the Wayback Machine's inception in 1996 (and in this case, all of these crawls are from 2014 on).
+By contrast, the website of New York City has been crawled over 7,000 times.
+Third, webcrawls are not instant and are not always done on an entire website at the same time.
+This means that for example, a website's frontpage might have been scraped one day, and its page on the city's mayor only a month later -- within the same crawl.
+Once again, this problem is exacerbated for small, less prominent websites.
+While we appreciate the Internet Archive's efforts to preserve snapshots of the web and recommend its API to practitioners who can work around the limitations outlined here, these problems preclude its usefulness for our purposes.} This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
 This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
@@
 In Table \ref{tabSTMtopwords60keep}, we present topic results from an STM, and mayoral party effect, estimated on data processed using a minimal HTML parser, implemented as the 'KeepEvertything' algorithm in the boilerpipeR package.
-An illustration of the content removed by the full boilerpipe procedure is given by Topic 5.
+An illustration of the content removed by the full boilerpipe procedure is given by Topic 56.
 This is the fourth-most Republican topic, and is a website boilerplate topic, with top words 'click', 'reserved', 'trademark', 'password', 'search', and 'connected'.

### 2019-08-02 paper/manuscript_paNote_OA.tex
fixed reference to topic 5 --> should be 56
shortened PSRM abstract

@@
 
-\begin{abstract}
+%\begin{abstract}
 
-A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars.
+%A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars.
 Existing research in public administration, public policy, and political science has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
@@
 
-\end{abstract}
+%\end{abstract}
 \thispagestyle{empty}

### 2019-08-02 paper/manuscript_psrmNote.tex
shortened PSRM abstract

@@
 
-A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars.
-Existing research in public administration, public policy, and political science has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
-We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content.
-Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
-We provide an R package that can be used to apply our proposed pipeline.
-We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
-We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
-Using a structural topic model, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity and fire safety.
+A local government's website is an important source of information about policies and procedures for residents and community stakeholders.
+Existing research in political science and related fields has relied on manual methods of website content collection, limiting the scale and scope of website content analysis.
+Our objectives and corresponding contributions are two-fold.
+First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
+Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
+We build upon recent research that analyzes how variation in the partisan control of government relates to content posted on the government's website.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.

### 2019-08-02 paper/manuscript_psrmNote.tex
made remaining revisions

@@
 We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
+
+Our research objectives and corresponding contributions are two-fold.
+First, we present a set of tools that can be effectively used in combination to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT).
+Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.\footnote{It is useful to note a couple of features that we do not intend to provide with this pipeline.
+First, this is not intended to be a pipeline for scraping and analyzing any and all websites.
+Our focus is on government websites, as we assume that the contents are in the public domain, and not subject to limitations on the application of scraping technology.
+Second, though such extensions would be valuable, we do not address the collection and analysis of image, video, sound, and  tabular data from government websites.} Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
+By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset.
+In summary, our contributions offer scholars of government a roadmap for collecting, and an example of, large scale textual data extracted from government websites.
 
@@
 
-We illustrate the analysis of municipal website content by studying differences in website content based on the party of the mayor.
+City mayors use government websites to present their policy priorities to the public.
+Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis.
+Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with the Front Porch Alliance---a faith-based initiative to create partnerships with religious organizations for the use and administration of city resources.
+Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}.
+When Democrat Bart Peterson took office in 2000, the material related to the Front Porch Alliance was removed from the website.
+We consider whether the partisan manipulation of city website contents documented in this example holds in a large-scale and more recent sample of city websites.
+We illustrate the analysis of municipal website content by studying the ways in which differences in website content correlate with the partisanship of the city's mayor mayor.
 As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance.

### 2019-08-03 paper/manuscript_psrmNote_OA.tex
coherence and exclusivity; added to online appendix
explanation for appendix figure 1 (coherence & exclusivity)

@@
 
-In Tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2} we present results of the STM with 120 topics organized according to the effect of mayoral partisanship on topic prevalence.
+In Tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2}, we present results of the STM with 120 topics organized according to the effect of mayoral partisanship on topic prevalence.
 The partisan themes in the 120-topic STM mirror those in the 60-topic model, with cities led by Democratic mayors focused disproportionately on finances (e.g., Topics 75, 71, 61) and social problems (e.g., Topics 93, 101, 39, 52), and cities led by Republican mayors focused disproportionately on basic services and utilities (e.g., Topics 114, 11,  86, 116).
@@
 
-In Tables \ref{tabSTMtopwords60_income} and \ref{tabSTMtopwords60_population} we present the topics ordered according to the effects of median income and population, respectively.
+In Tables \ref{tabSTMtopwords60_income} and \ref{tabSTMtopwords60_population}, we present the topics ordered according to the effects of median income and population, respectively.
 Considering income-based variation in topics, there are several topics prevalent in more wealthy cities that focus on initiatives that go well-beyond standard city services---downtown and building revitalization (Topics 39 and 12), renewable energy (Topic 20), bike/pedestrian-oriented development (Topic 60), wildlife conservation (Topic 3).
@@
 
+In Figure \ref{fig:coherence_exclusivity}, we present a quantitative assessment of relative topic quality for our main model, using two metrics, semantic coherence and exclusivity.
+Semantic coherence \citep{Mimno2011} describes the extent to which the 10 top words in a topic model belong to the same underlying concept.
+Exclusivity \citep{Bischof2012,Roberts2014} measures whether the top 10 words in one topic feature primarily in this topic, rather than being dispersed across a range of topics.
+As coherence tends to be outright better in models with fewer topics, the comparison with exclusivity creates a trade-off.
+Figure \ref{fig:coherence_exclusivity} shows that the model performs well in this regard, as most topics have both high coherence and exclusivity.
+Even topic 11, which does worst in terms of coherence, looks like a good topic upon manual inspection, as its top words all pertain to obesity.
+
 \input{tables/stmTopWords60_income.tex}
 \input{tables/stmTopWords60_population.tex}
+
+\begin{figure}
+	\centering
+	\includegraphics{figures/stm_60_coherence_exclusivity.pdf}
+	\caption{Semantic coherence and exclusivity for each of the 60 topics in our main structural topic model.
+Coherence describes the extent to which the 10 top words in a topic model belong to the same underlying concept.
+Exclusivity measures whether the top words in one topic feature primarily in this topic, rather than being dispersed across a range of topics.
+The model performs well in this trade-off, as both coherence and exclusivity are high for most topics.}
+	\label{fig:coherence_exclusivity}
+\end{figure}
 

### 2019-08-05 paper/manuscript_psrmNote_OA.tex
no real changes, just making sure everything is lined up correctly

@@
 
-To download the websites, we rely on the Unix command line tool \texttt{wget}.\footnote{An alternative source of web data which has attained some popularity within the digital humanities is the Internet Archive's Wayback machine (\url{https://archive.org/}), which preserves snapshots of websites over time.
+To download the websites, we rely on the Unix command line tool \texttt{wget}.\footnote{An alternative source of web data which has attained some popularity within the digital humanities is the Internet Archive's Wayback Machine (\url{https://archive.org/}), which preserves snapshots of websites over time.
 In theory, this would be very useful to projects such as ours, since it would allow us to measure the evolution of websites over time, in response to changes in city executives.

### 2019-10-10 paper/manuscript_ssqNote_title.tex
submitted to SSQ

--- 2019-08-02 paper/manuscript_psrmNote.tex
@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States\footnote{This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}}
 
@@
 Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
-Email: bdesmarais@psu.edu}} \date{\today}
+Email: bdesmarais@psu.edu.
+}} \date{\today}
 
@@
 
-A local government's website is an important source of information about policies and procedures for residents and community stakeholders.
-Existing research in political science and related fields has relied on manual methods of website content collection, limiting the scale and scope of website content analysis.
-Our objectives and corresponding contributions are two-fold.
+\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
+Our objectives and corresponding contributions in this research note are two-fold.
 First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
 Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-We build upon recent research that analyzes how variation in the partisan control of government relates to content posted on the government's website.
+\\~\\
+\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \\~\\
+\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
+We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
+\\~\\
+\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.
+
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 % Description of the possible challenges
-\doublespacing
-
-\section{Introduction}
-Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
-The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
-Though accurate, the manual approach to data collection is costly for large-scale analysis.
-We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
-We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
-
-%Though there exists a variety of software tools that are designed to automatically scrape all of the files available at a website \citep{glez2013web}, raw website downloads have to be processed significantly before the files are adequately prepared for content (e.g., text, image) analysis.
-We describe and provide solutions to two central challenges in automatically gathering and analyzing website textual contents.
-First, plain text must be extracted from the files.
-This challenge would arise in any context in which researchers sought to study the textual contents of websites.
-The second challenge we address in our methodological pipeline is, however, specific to the research objective of comparing websites on the basis of a common lexicon.
-For any two governments, the textual signatures that most dramatically differentiate the textual contents of their websites consist of what we can call ``boilerplate'' text---header, footer, or other titling text that is designed to identify the website as being associated with a specific government entity (e.g., ``Welcome to the city of Santa Cruz'', ``The City of Los Angeles welcomes you'').
-The second methodological innovation we offer in our pipeline is designed to minimize the impact of this boilerplate text on the comparative analysis of government website content.
-
-\section{Politics and Government Website Content}
-
- Though government websites serve largely instrumental service-delivery purposes, they also offer officials a prime venue via which to communicate policy goals and accomplishments, which inevitably reflect officials' politics.
-In the current paper, we focus on the running example of the reflection of mayoral partisanship on municipal government websites.
-A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep{gerber2011mayors,de2016mayoral,einstein2016mayors,marion2013mayor}.
-Official city websites allow mayors to present their views and policy priorities to the public.
-In local politics, where campaign funds are low, this lends incumbents a crucial advantage in becoming more well-known among their constituencies \citep{stanyer2008elected}.
-Local government websites are frequently visited by the public \citep{thomas2003new}.
-City websites can be used to communicate the stance of a mayor on social or economic programs.
-Consider the example of the Gary, Indiana homepage, depicted in Figure \ref{fig:garymayor}.
-This screenshot provides a clear example of the utility of a city website for communicating the mayor's policy priorities and accomplishments.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.45]{figures/gary_hp}
-\caption{Screenshot from the homepage at \url{https://garyin.us/}, accessed on 05/22/2019. Image depicts Democratic mayor of Gary, IN, Karen Freeman-Wilson.}
-\label{fig:garymayor}
-\end{figure}
-
-%Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
-In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
-%Furthermore, the use of a local government website is associated with an individual's perspective on government.
-\citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
-Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
-
-The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
-As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
-The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
-Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.
-
-%Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
-\cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
-%In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
-We then define a pipeline for data collection and analysis that includes methods to access government website URLs, scrape their raw contents from the World Wide Web, gather plain text from the website files, and identify boilerplate text within the plain text contents.
-Lastly, we illustrate the analysis of municipal government website text by exploring the relationship between the city mayors' party affiliations and the topical contents of the websites.
-
-\section{Data: US Municipal Government Website Text}
-
-For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
-The websites were scraped in March 2018.
-The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
-Municipal elections in Indiana and Louisiana are partisan across the board, so our sample is primarily focused on these two states.
-For Indiana and Louisiana, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
-New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see appendix for more detail).
-California and Texas contain a number of large cities whose mayors are sufficiently well-known for their partisanship to be available.
-Our sample is well-balanced on a number of theoretically important dimensions.
-One, each of the four Census regions are represented with at least one state.
-Two, we have a fairly well-balanced sample with respect to the urban/rural cleavage.
-Furthermore, the sample is politically balanced---we have three blue states, and three red states.
-The partisan breakdown of city websites by state is provided in the appendix.
-This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governements \citep[e.g., ][]{marschall2013local,sumner2019}.
-Details on the sources and methods of raw data collection can be found in the online appendix.
-
-%One of the more subtle aspects of local government is the presence of different types of government structures.
-Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
-We do not have access to information about the type of governments across the breadth of our dataset.
-Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\cite{gerber2011mayors}, whose theory is somewhat comparable to ours, find that the inclusion of this potential confounder does not affect the results.
-
-\section{The Web to Text Pipeline}
-In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents.
-We address three methodological challenges.
-First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
-Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
-The first step is aimed at extracting clean plain text from this heterogeneous file base.
-The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
-Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.
-We make a software recommendation for each of these steps and gather most of them our R package, \texttt{gov2text}.
-All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem.
-As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.
-Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
-We will clarify this distinction as we describe steps in our pipeline.
-
-\subsection{Site to Text Conversion}
-\subsubsection{File Type Detection}
-The format of a file has a major impact on whether and how textual data can be extracted from a document.
-For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text.
-For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification.
-We implement this method using the R package \texttt{wand} \citep{wand}.\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}
-
-\subsubsection{Extracting Text from HTML}
-The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate.
-The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
-The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{fig:garymayor}.
-The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
-The Mayor's message represents a relatively small fraction of the total text on the page.
-
-\begin{figure}
-\centering
-{\bf (a)} Naive Parsing  \\ \vspace{.2cm} 
-\includegraphics[scale=0.35]{figures/gary_sidebyside} \\ \vspace{.4cm}
-{\bf (b)} Boilerpipe 
-\includegraphics[scale=0.375]{figures/gary_bp}
-
-\caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.
-Bottom image provides the result of running \url{https://garyin.us/} through the \texttt{boilerpipe} algorithm at \url{https://boilerpipe-web.appspot.com/}.}
-\label{fig:garysbs}
-\end{figure}
-
-A subfield of the information retrieval literature, dealing with boilerplate extraction, can offer a solution to this problem.
-The goal of this branch of research is to develop algorithms with the ability to estimate whether a given portion of an HTML file is substantive.
-To this end, structural features, such as HTML tags (which are not sufficiently informative on their own), text statistics such as word and sentence length, as well as other heuristics are used.
-We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
-The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.
-The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}.
-We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data.
-We show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
-}
-
-\subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
-The extraction of information from other text-based file formats is more straightforward.\footnote{See \cite{Berg2012} for a discussion of why extracting text from PDFs is nevertheless nontrivial.} To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
-The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
-Files of type DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
-
-\subsection{Preprocessing}
-Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}.
-As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model.
-The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing.
-The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites.
-Some of it is substantively informative and some of it is completely irrelevant.
-As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents.
-The same is true for streets, locations and not least of all, the city itself.
-Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city.
-Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.
-
-%The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
-%With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
-
-To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER).
-In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended.
-Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
-Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word.
-} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
-To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).
-A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
-In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
-%The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
-For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus.
-These short and repetitive -- but numerous -- texts would pose severe problems to a topic model.
-Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.
-
-After preprocessing, our corpus consists of 356,911 documents.
-In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
-The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.
-
-\begin{table}[ht]
-    \centering
-    \begin{tabular}{lrr}
-        \hline
-        Process & Software dependency & in \texttt{gov2text} \\
-        \hline
-        1. Assemble url list. & \texttt{Selenium} & no \\
-        2. Collect website files. & \texttt{wget} & no \\
-        3. Correct file extensions. & \texttt{wand} \citep{wand} & yes \\
-        4. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
-        5. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
-        6. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
-        7. Remove names. & \texttt{spacyr} & yes \\
-        8. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
-        9. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
-        10. Retain only English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
-        11. Removal of duplicate documents. & \texttt{gov2text} & yes \\
-        \hline
-    \end{tabular}
-    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
-\end{table}
-
-%The text documents are converted to UTF-8 character encoding and then stripped of dates, punctuation, numbers, and words connected by underscores.
-At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
-"You are here", "Home", "Directory" etc.) in HTML documents, or commonly used forms or phrases in pdf, doc and docx files.
-This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate (through their unique boilerplate structure, e.g.
-a menu with certain terms repeated on every site of the domain), and not the substantive features of their contents.
-Boilerplate removal is a useful step in many forms of text analysis, as the analysis is focused in on text that varies above and beyond a standard template for textual content.
-Our solution to this problem is described in more detail in Section \ref{boilerplate}.
-
-%The last round of preprocessing is intended to remove everything from the file that is not an English word.
-This step is tailored to our intention to use the text for topic modeling.
-The final preprocessing round includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
-Furthermore, some documents contain gibberish, often as a result of faulty or impartial optical character recognition applied to text that was produced through a non-machine-readable medium.
-To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example, Los Angeles, do contain a sizable proportion of Spanish content.
-The analysis of this content is beyond the scope of this paper but could be explored in future work, for example using methods of text processing that are applicable to multilingual corpora \citep{lucas2015computer}.
-} However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
-Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
-Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to the total number of tokens is less than 0.15.
-Furthermore, \texttt{hunspell} does not spellcheck individual characters or two-character words, so we remove these token types entirely.
-Since these pre-processing steps reduce documents which are largely unsuitable to only a few tokens (i.e., word occurrences), we also remove all remaining documents containing less than 50 tokens.
-Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive\footnote{Topic models essentially do not pick up on extremely rare words, so their inclusion is a waste of computational resources.
-Removing them in this manner is also the default preprocessing choice in the \texttt{stm} package.} to our models while increasing their computational cost, we also discard any token types that occur in only one document.
-
-%\subsection{Boilerplate Removal}\label{boilerplate}
-%As noted above, city websites contain a large amount of text that is uninformative for its actual content, and therefore a hindrance to understanding through algorithmic text analysis.
-This is a common issue with textual data in which informative content is embedded in technically structured documents.
-See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
-
-%\subsection*{Boilerplate Classification}
-%In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
-We sampled 500 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
-To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.
-As an example, the most common line throughout all pages of the city of Seattle consists only of the word ``total'' and occurs 103,068 times.
-Similarly, the line ``page'' occurs 58,833 times.
-Even something completely nonsensical such as ``a a'' still appears on 376 occasions.
-To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
-
-%These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines).
-We then trained a number of different classifiers with this informativeness measure as the dependent variable.
-The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself.
-The purpose of these covariates is as follows:
-
-\section{Partisan Language on Municipal Websites}
-
-We illustrate the analysis of municipal website content by studying differences in website content based on the party of the mayor.
-As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance.
-However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance.
-These constraints do not apply to website contents.
-City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.
-
-%BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.
-As noted by \cite{GrimmerStewart2013}, for most applications, bag-of-words approaches have been found to be more than sufficient.
-Furthermore, there is reason to believe that city government websites are a particularly `safe' case for bag-of-words methods due to their informative, manner-of-fact based language.
-It is extremely unlikely for these pages to feature ambiguous language such as an abundance of negation or even sarcasm.
-
-%\input{tables/tabBoilerplateIllustration.tex}
-
-To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
-Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary.
-The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics.
-For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic.
-For our primary empirical investigation, the STM provides a tool to estimate the relationship between the party of the city's mayor and the prevalence of each topic.
-We also include the municipality's population and median income as covariates.
-Further details on and results from our STM specification can be found in the online appendix.
-
-\subsubsection{Structural topic model results}
-
-The results are shown in Table \ref{tabSTMtopwords60}.
-First, it is notable that the 95\% credible interval includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor.
-Many of the topics associated with Democrats fit with what we understand to be national party priorities.
-Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters.
-Topic {\bf 6} ('race', 'islander', 'census, 'female') covers racial and gender identity issues.
-Similarly, employee rights and benefits are represented in topics \textbf{10} and \textbf{29}.
-Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), Topic {\bf 45} ('asset', 'actuarial', 'liability', 'financial'), Topic \textbf{35} ('bond', 'obligation', 'proceeds') as well as Topic \textbf{55} ('taxable', 'deed', 'value').
-We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}).
-This finding is consistent with \cite{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime.
-On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
-On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on law enforcement, even after controlling for crime \citep{Einstein2015}.
-
-City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government.
-Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51}), vaccination (Topic \textbf{2}),  and sanitation (Topic \textbf{47}), are prevalent among cities with Republican mayors.
-These basic service topics cannot be found among topics prevalent in cities with Democratic mayors.
-Similarly, zoning issues figure prominently in the set of republican topic (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules.
-The Democratic topics also include one that is somewhat focused on zoning, Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.
-
-%Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{gerber2011mayors}.
-However, this kind of finding is not entirely without precedent in the literature (see \citep{Einstein2015}).
-Similar to the informed dirichlet model, the structural topic model also finds the emphasis on construction and infrastructure by Republicans - in table \ref{tabSTMINRep}, topics 2, 7 and 8 clearly focus on these issues.\footnote{The first Republican topic in Indiana (library, stream, obj, etc.) is likely an artifact from incorrectly converted HTML, and since it presumably only happens only in one Republican city, the topic is classified as very Republican.}
-
-%When comparing Indiana to Louisiana, it appears that the Democratic emphasis on law enforcement is robust.
-Furthermore, as with the fightin' words approach, some smaller degree of focus on money (see topic 1) is still evident.
-For Republicans, topics 2 to 4 seem to be, once again about infrastructure and utilities, pointing to a certain degree of robustness in these results, as well as the emergence of a trend.
-The results produced by the structural topic model are not flawless, but the two parties do seem to have somewhat consistent themes on which they focus on in both states.
-Furthermore, in comparison to the fightin' words approach, the ability of the structural topic model to form coherent topics is quite evident and helpful in the interpretation of the results.
-
-%An ostensibly intuitive solution to topics clustering into cities in LDA is to include dummies for the cities in a statistical model of topics.
-This is facilitated by the structural topic model, which uses document metadata t to account for variation in topics \citep{Roberts2014}.
-However, figure \ref{stm_results} shows that if anything, the STM exacerbates the problem.
-Here, we plot the \textit{p-values} of the coefficients for each city as well as the party variable across each topic.
-Under normal circumstances, plotting the p-values, as opposed to the fitted values, does not make much sense, but here it serves a diagnostic purpose.
-The plot shows that the party variable is never statistically significant at any conceivable level of confidence, nor is it even close to.
-Interestingly the same is true for a number of the cities as well.
-The topics cluster heavily into only about half of the cities, which does not present an improvement over LDA at all.
-
-%Partisan top words - stm Louisiana -- Rep
-%\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}
-
-%Partisan top words - stm Louisiana -- Dem
-%\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}
-
-%Partisan top words - stm Louisiana -- Rep
-%\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}
-
-%Partisan top words - stm Louisiana -- Dem
-%\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
-
-%\subsubsection{Prediction with SVM}
-%An alternative approach to the problem is to ignore topics entirely and go straight to predicting documents that are much more likely to be included on websites belonging to one or the other party.
-Classic machine learning techniques such as Naive Bayes, Linear Discriminant Analysis, or SVM should be expected to fare well in this context.
-Here, we rely on SVM, implemented with the SciKitLearn package in Python.\footnote{We also implemented SVM in R through the packages kernlab and e1071 in R.
-However, neither of these provide a regularized version of SVM (NOTE: at least that is what I am gathering from the stack overflow error), which prevents us from using all of the features contained in our data.
-Instead, we ranked the features according to tf-idf and selected the top 5000.
-These methods are also quite slow, and provide a maximum accuracy of 82\% in five-fold cross-validation.} A grid search reveals the tf-idf representation of the document-term matrix to be better than pure word counts, unigrams to be superior to bi-grams, the application of an L2 penalty to be preferable to either L1 or elasticnet, and an alpha (a constant to multiply with the regularization parameter C) of 0.0005 to lead to the best results.
-Applying five-fold cross-validation to the (tf-idf) document-term matrix with the dimensions 16011x35000 leads to an average accuracy of 89\%.\footnote{Other methods used: Elastic-net in the glmnet package in R.
-Accuracy is 0.6924795 for in-sample prediction, so not worth bothering with.}
-
-%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backward: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-
-%Heatmaps
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
-%    \label{heatmaps_weights}
-%    \includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
-%\end{figure}
-
-%US map
-%\begin{figure}[htp]
-  %  \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-    %\includegraphics[width=\linewidth]{figures/us_map.pdf} \vspace{-2cm}
-       % \caption{Map of the cities in the corpus in the contiguous U.S.
-The corpus also includes Alaska.
-In the analysis, only cities in California, Indiana, Louisiana, New York, Texas and Washington are used.
-The colors represent the partisanship of the mayor (blue corresponding to Democrats and red to Republicans).}
-    %\label{us_map}
-%\end{figure}
-
-%stm results
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \caption{Results from a structural topic model, displayed as the p-values for each variable for each topic.
-This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
-%    \label{stm_results}
-%%    \includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
-%\end{figure}
-
-%Partisan top words - topic model Indiana
-%\input{tables/partisanTopWords.tex} %\ref{tabFightinIN}
-
-%Partisan top words - topic model Louisiana
-%\input{tables/partisanTopWordsLA.tex} %tabLDALA
-
-%Partisan top words - stm Indiana
-%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}
-
-%Partisan top words - stm Louisiana
-%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}
-
-%Some basic descriptive statistics of documents by party
-%\input{tables/descriptiveStatisticsPartisanIN.tex}
-
-%Some basic descriptive statistics of documents by party
-%\input{tables/descriptiveStatisticsPartisanLA.tex}
-
-%fightin words results
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
-%        \caption{Total number of lines retained at a given threshold for removing duplicated lines.
-For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
-%    \label{linesCutoff}
-%\end{figure}
-
-%\section{Ground truth test}
-%In the realm of public administration, the notion that the partisan leaning of mayors might have an effect on how they run their cities is still frowned upon to some extent.
-Perceived more as managers than politicians, they have been portrayed as the last bastion of non-partisanship in America, and in many cases, also style themselves that way \citep{Dovere2018}.
-However, the aspirations some mayors have shown towards higher offices - in some cases, even the presidency - reveal that they are not quite as above the fray as some may believe them to be.
-One of the most vicious and blatantly partisan cleavages in current U.S.
-politics - the debate surrounding sanctuary cities - has seen mayors in a central role.
-Research into local politics has shown that partisan elections consistently have greater turnout \citep{Schaffner2001}.
-When voters are denied this cue, they make use of other, and considerably more irrational heuristics, such as name, gender, or occupation of the contenders.
-Consequently, it only makes sense for any office-seeking politician to emphasize their partisanship.
-Finally, decades of research in political psychology have consistently shown that no matter how hard we try, humans are simply incapable of escaping our partisan biases, a finding that is especially pronounced among elites \citep{Hatemi2011}.
-%
-%In an effort to underline this fact and remove any doubt about the fact that the partisanship of mayors colors their decision-making, we conduct a ground truth test between our main corpus - the websites of cities - and a second, decidedly more partisan set of texts: the campaign websites of these mayors.
-As noted above, partisanship has been shown to be a powerful driving force even in local politics, and mayors are incentivized to exploit it.
-Consequently, they are very likely to emphasize conservative/liberal values on this platform.
-If there is a greater correlation in word use between the cities managed by a party and the campaign websites of its mayors than with those of the other party, evidence for the partisanship of city websites can be established.
-%
-%Using the same methods as described for our main corpus, we have gathered these sites and then concatenated all of the documents belonging to mayors of the two parties into one ground truth document each.
-We do the same for the city documents, and then compare the four document collections using cosine similarity.
-This measure is the cosine between the angle of two vectors, in this case, the frequencies of all words in the two vocabularies.
-Compared to a simple Euclidean distance, this has the advantage of accounting for the fact that the two corpora being compared are not necessarily of the same length.
-The cosine measure between two documents ranges between 0 and 1, 0 signifying absolutely no correlation, and 1 perfect overlap.
-Figure \ref{groundtruth} shows the result of this test.
-The expectation is for a greater similarity between Republican cities and the Republican ground truth than Republican cities and Democratic ground truth - and vice versa.
-At present, however, this does not appear to be the case, presumably because the Republican ground truth consists of 8 documents, and the Democratic one of 290.
-
-%ground truth test
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \includegraphics[width=\linewidth]{figures/groundtruth_corrplot.png}
-%    \caption{Ground truth test. The values are cosine similarities between a pair of document collections.}
-%    \label{groundtruth}
-%\end{figure}
-%
-%%ground truth test
-%\begin{figure}[htp]
-%    \centering % Using \begin{figure*} makes the figure take up the entire width of the page
-%    \includegraphics[width=\linewidth]{figures/groundtruth_bs_bigcities_corrplot.png}
-%    \caption{Ground truth test. The values are cosine similarities between a pair of document collections (top 100 mayors vs. IN and LA).}
-%    \label{groundtruth}
-%\end{figure}
-
-%Ground truth test between top100 mayors and IN + LA; with bootstrapped confidence bounds
-% label: groundtruth_bootstrapped
-%\input{tables/groundtruth_bootstrapped.tex}
-
-%\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
-
-\input{tables/stmTopWords60.tex}
-%\input{tables/stmTopWords60_OLD.tex} %\ref{tabSTMtopwords2}
-
-\section{Conclusion}
-
-We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
-We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline.
-This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
-Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
-We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
-
-The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
-By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
-For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
-We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
-This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.}
-
-%We offer several contributions that will be valuable in future research endeavors.
-First, the data collected in the current study can be used for comparative analysis of US city website contents.
-Second, the pipeline we present can be used as a set of procedures to follow in gathering large-scale datasets of textual contents from other samples of governments.
-For example, the pipeline we have developed could be used to build comparative datasets of state or federal bureaucratic agencies.
-Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.
-
-\section*{Funding}
-This work was supported by the National Science Foundation [1320219, 1637089, 1641047].
-
-%\input{tables/tabCitiesStatesParties.tex}
-%\input{tables/stateUrlSummary.tex}
-
-\bibliographystyle{chicago} % apsr stopped working for me
-%\bibliographystyle{plainnat}
-\bibliography{ref}
 

### 2020-01-17 paper/archived/manuscript_ssqNote.tex
revising for APR

--- 2019-08-02 paper/manuscript_psrmNote.tex
@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
 
-\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+%\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
 Email: mvn5218@psu.edu.
@@
 Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
-Email: bdesmarais@psu.edu}} \date{\today}
+Email: bdesmarais@psu.edu.
+This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}} \date{\today}
 
@@
 
-A local government's website is an important source of information about policies and procedures for residents and community stakeholders.
-Existing research in political science and related fields has relied on manual methods of website content collection, limiting the scale and scope of website content analysis.
-Our objectives and corresponding contributions are two-fold.
+\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
+Our objectives and corresponding contributions in this research note are two-fold.
 First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
 Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-We build upon recent research that analyzes how variation in the partisan control of government relates to content posted on the government's website.
+\vspace{.1cm} \\
+\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \vspace{.1cm} \\
+\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
+We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
+\vspace{.1cm} \\
+\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.  \vspace{-.3cm}
+
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 
-\section{Introduction}
+\section{Introduction} \vspace{-.2cm}
 Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation.
@@
 
-\section{Politics and Government Website Content}
+\vspace{-.2cm}
+\section{Politics and Government Website Content} \vspace{-.2cm}
 
@@
 \includegraphics[scale=0.45]{figures/gary_hp}
-\caption{Screenshot from the homepage at \url{https://garyin.us/}, accessed on 05/22/2019. Image depicts Democratic mayor of Gary, IN, Karen Freeman-Wilson.}
+\caption{Screenshot from the homepage at \url{https://garyin.us/}, accessed on 05/22/2019. Image depicts Democratic mayor of Gary, IN, Karen Freeman-Wilson.} \vspace{-.3cm}
 \label{fig:garymayor}
@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcnutt2010virtual,Armstrong2011,Feeney2017}.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
@@
 
-\section{Data: US Municipal Government Website Text}
+\vspace{-.2cm}
+
+\section{Data: US Municipal Government Website Text} \vspace{-.2cm}
 
@@
 
-\section{The Web to Text Pipeline}
+\vspace{-.2cm}
+\section{The Web to Text Pipeline} \vspace{-.2cm}
 In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents.
@@
 We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
-The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in political science.
+The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in the social sciences.
 The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}.
@@
     \end{tabular}
-    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
+    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.}  \vspace{-.9cm}
 \end{table}
@@
 To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
-Building on the conception of ``topics'' in Latent Dirichlet Allocation, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary.
+Building on the conception of ``topics'' in conventional topic models \citep{valdez2018topic}, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary.
 The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics.
@@
 
-\section*{Funding}
-This work was supported by the National Science Foundation [1320219, 1637089, 1641047].
-
 %\input{tables/tabCitiesStatesParties.tex}

### 2020-01-17 paper/archived/manuscript_ssqNote_OA copy.tex
revising for APR

--- 2019-08-05 paper/manuscript_psrmNote_OA.tex
@@
 
-\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+%\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
 Email: mvn5218@psu.edu.
@@
 
-A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars.
-Existing research in public administration, public policy, and political science has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
-We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content.
-Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
-We provide an R package that can be used to apply our proposed pipeline.
-We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
-We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
-Using a structural topic model, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity and fire safety.
+\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
+Our objectives and corresponding contributions in this research note are two-fold.
+First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
+Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
+\\~\\
+\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \\~\\
+\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
+We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
+\\~\\
+\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.
+
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 \end{figure}
-
-\section*{Funding}
-This work was supported by the National Science Foundation [1320219, 1637089, 1641047].
 

### 2020-01-17 paper/manuscript_aprNote.tex
revising for APR

--- 2020-01-17 paper/archived/manuscript_ssqNote.tex
@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
 
-\usepackage{geometry}                        % See geometry.pdf to learn the layout options. There are lots.
+\usepackage[margin=1in]{geometry}                        % See geometry.pdf to learn the layout options. There are lots.
 % \geometry{a4paper}                           % ... or a4paper or a5paper or ...
@@
 %\usepackage[margin = 1.25in]{geometry}
-%\usepackage[nolists,figuresfirst]{endfloat} % Figures and tables at the end
+\usepackage[nolists,figuresfirst]{endfloat} % Figures and tables at the end
 \usepackage{subfig}
@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} Government Websites As Data: \\ Understanding how Mayoral Partisanship Shapes Municipal Website Content}
 
@@
 
-\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
-Our objectives and corresponding contributions in this research note are two-fold.
-First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
-Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-\vspace{.1cm} \\
-\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \vspace{.1cm} \\
-\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
-We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
-\vspace{.1cm} \\
-\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.  \vspace{-.3cm}
-
+A local government's website is an important source of information about policies and procedures for residents and community stakeholders .
+Existing research in political science and related fields has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
+In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
+Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
+In our application, we collect and analyze a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
+We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
+Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
+As an additional contribution, we provide an R package that can be used to process government website files into raw text.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 % Description of the possible challenges
+\newpage
+
+\begin{center}
+\Large
+Government Websites As Data: Understanding how Mayoral Partisanship Shapes Municipal Website Content
+\end{center}
 \doublespacing
-
+\vspace{-1cm}
 \section{Introduction} \vspace{-.2cm}
-Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
+Government websites convey voluminous information about all aspects of government policy priorities, policy implementation, and public deliberation.
+The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra}.
 The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
 Though accurate, the manual approach to data collection is costly for large-scale analysis.
-We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
-We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
+We propose the use of automatic web-scraping to gather and process government websites in order to build datasets that can be used for text analysis, as well as the solutions we adopt.
+We apply this approach to build a novel dataset of U.S.
+municipal government website contents, and analyze how the textual contents of city government websites in six American states correlate with the partisanship of the city mayor.
 
-Our research objectives and corresponding contributions are two-fold.
-First, we present a set of tools that can be effectively used in combination to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT).
-Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.\footnote{It is useful to note a couple of features that we do not intend to provide with this pipeline.
-First, this is not intended to be a pipeline for scraping and analyzing any and all websites.
-Our focus is on government websites, as we assume that the contents are in the public domain, and not subject to limitations on the application of scraping technology.
-Second, though such extensions would be valuable, we do not address the collection and analysis of image, video, sound, and  tabular data from government websites.} Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
-By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset.
-In summary, our contributions offer scholars of government a roadmap for collecting, and an example of, large scale textual data extracted from government websites.
+Our contributions are two-fold.
+First, we propose, and provide software to apply, the large-scale automated collection of textual data from government websites--covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT) into plain text for analysis.
+Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
+By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we both illustrate the utility of automated web content collection from government websites, and present new findings on the relationship between government website concepts and executive partisanship.
 
@@
 
-\vspace{-.2cm}
-\section{Politics and Government Website Content} \vspace{-.2cm}
+\vspace{-.8cm}
+\section{Politics and Government Website Content} \vspace{-.3cm}
 
@@
 In the current paper, we focus on the running example of the reflection of mayoral partisanship on municipal government websites.
-A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep{gerber2011mayors,de2016mayoral,einstein2016mayors,marion2013mayor}.
+A substantial body of research has found that the partisanship of the mayor affects city governance along multiple dimensions of spending and policy attention \citep[e.g.,][]{gerber2011mayors,de2016mayoral,einstein2016mayors}.
 Official city websites allow mayors to present their views and policy priorities to the public.
@@
 City websites can be used to communicate the stance of a mayor on social or economic programs.
-Consider the example of the Gary, Indiana homepage, depicted in Figure \ref{fig:garymayor}.
-This screenshot provides a clear example of the utility of a city website for communicating the mayor's policy priorities and accomplishments.
+Consider the screenshot of the Gary, Indiana homepage in Figure \ref{fig:garymayor}.
+This provides a clear example of the utility of a city website for communicating the mayor's policy priorities and accomplishments.
 
@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017}.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
-The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,Esterling2011,Esterling2011a,Norris2003}.
 For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
@@
 
-\vspace{-.2cm}
+\vspace{-.8cm}
 
-\section{Data: US Municipal Government Website Text} \vspace{-.2cm}
+\section{Data: US Municipal Government Website Text} \vspace{-.3cm}
 
-For data availability reasons, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
+For data availability reasons when it comes to mayoral partisanship, we focus our analysis of municipal websites on six states---Indiana, Louisiana, New York, Washington, California, and Texas.
 The websites were scraped in March 2018.
-The selection of states and cities is largely dictated by the presence of partisan mayors and availability of the relevant data.
+The selection of states and cities is largely dictated by the presence of partisan mayors.
 Municipal elections in Indiana and Louisiana are partisan across the board, so our sample is primarily focused on these two states.
 For Indiana and Louisiana, all cities with a website are included, resulting in a considerably larger sample than for the other four states.
-New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see appendix for more detail).
+New York and Washington do not have nominally partisan elections, but for a subset of cities, partisanship can be determined through contribution data (see supplementary material for more detail).
 California and Texas contain a number of large cities whose mayors are sufficiently well-known for their partisanship to be available.
@@
 Furthermore, the sample is politically balanced---we have three blue states, and three red states.
-The partisan breakdown of city websites by state is provided in the appendix.
+The partisan breakdown of city websites by state is provided in the supplementary material.
 This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governements \citep[e.g., ][]{marschall2013local,sumner2019}.
-Details on the sources and methods of raw data collection can be found in the online appendix.
+Details on the sources and methods of raw data collection can be found in the supplementary material.
 
@@
 
-\vspace{-.2cm}
-\section{The Web to Text Pipeline} \vspace{-.2cm}
-In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents.
-We address three methodological challenges.
-First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
-Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
-The first step is aimed at extracting clean plain text from this heterogeneous file base.
-The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
-Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.
-We make a software recommendation for each of these steps and gather most of them our R package, \texttt{gov2text}.
-All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem.
-As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.
-Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
-We will clarify this distinction as we describe steps in our pipeline.
+\vspace{-.8cm}
 
-\subsection{Site to Text Conversion}
-\subsubsection{File Type Detection}
-The format of a file has a major impact on whether and how textual data can be extracted from a document.
-For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text.
-For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification.
-We implement this method using the R package \texttt{wand} \citep{wand}.\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}
-
-\subsubsection{Extracting Text from HTML}
-The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate.
-The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
-The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{fig:garymayor}.
-The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
-The Mayor's message represents a relatively small fraction of the total text on the page.
-
-\begin{figure}
-\centering
-{\bf (a)} Naive Parsing  \\ \vspace{.2cm} 
-\includegraphics[scale=0.35]{figures/gary_sidebyside} \\ \vspace{.4cm}
-{\bf (b)} Boilerpipe 
-\includegraphics[scale=0.375]{figures/gary_bp}
-
-\caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.
-Bottom image provides the result of running \url{https://garyin.us/} through the \texttt{boilerpipe} algorithm at \url{https://boilerpipe-web.appspot.com/}.}
-\label{fig:garysbs}
-\end{figure}
-
-A subfield of the information retrieval literature, dealing with boilerplate extraction, can offer a solution to this problem.
-The goal of this branch of research is to develop algorithms with the ability to estimate whether a given portion of an HTML file is substantive.
-To this end, structural features, such as HTML tags (which are not sufficiently informative on their own), text statistics such as word and sentence length, as well as other heuristics are used.
-We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
-The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in the social sciences.
-The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}.
-We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data.
-We show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
-}
-
-\subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
-The extraction of information from other text-based file formats is more straightforward.\footnote{See \cite{Berg2012} for a discussion of why extracting text from PDFs is nevertheless nontrivial.} To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
-The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
-Files of type DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
-
-\subsection{Preprocessing}
-Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}.
-As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model.
-The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing.
-The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites.
-Some of it is substantively informative and some of it is completely irrelevant.
-As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents.
-The same is true for streets, locations and not least of all, the city itself.
-Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city.
-Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.
-
-%The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
-%With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
-
-To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER).
-In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended.
-Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
-Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word.
-} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
-To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).
-A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
-In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
-%The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
-For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus.
-These short and repetitive -- but numerous -- texts would pose severe problems to a topic model.
-Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.
-
-After preprocessing, our corpus consists of 356,911 documents.
-In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
-The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.
-
-\begin{table}[ht]
-    \centering
-    \begin{tabular}{lrr}
-        \hline
-        Process & Software dependency & in \texttt{gov2text} \\
-        \hline
-        1. Assemble url list. & \texttt{Selenium} & no \\
-        2. Collect website files. & \texttt{wget} & no \\
-        3. Correct file extensions. & \texttt{wand} \citep{wand} & yes \\
-        4. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
-        5. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
-        6. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
-        7. Remove names. & \texttt{spacyr} & yes \\
-        8. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
-        9. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
-        10. Retain only English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
-        11. Removal of duplicate documents. & \texttt{gov2text} & yes \\
-        \hline
-    \end{tabular}
-    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.}  \vspace{-.9cm}
-\end{table}
-
-%The text documents are converted to UTF-8 character encoding and then stripped of dates, punctuation, numbers, and words connected by underscores.
-At this point, the documents of one city still closely resemble one another in the form of boilerplate content, be it website elements (i.e.
-"You are here", "Home", "Directory" etc.) in HTML documents, or commonly used forms or phrases in pdf, doc and docx files.
-This is an issue, because this boilerplate content causes the results of analyzing this data with text analysis methods to characterize documents primarily by the cities from which they originate (through their unique boilerplate structure, e.g.
-a menu with certain terms repeated on every site of the domain), and not the substantive features of their contents.
-Boilerplate removal is a useful step in many forms of text analysis, as the analysis is focused in on text that varies above and beyond a standard template for textual content.
-Our solution to this problem is described in more detail in Section \ref{boilerplate}.
-
-%The last round of preprocessing is intended to remove everything from the file that is not an English word.
-This step is tailored to our intention to use the text for topic modeling.
-The final preprocessing round includes setting every character to lowercase, as well as the removal of bullet points which frequently occur in HTML documents, extraneous whitespace, XML documents mislabeled as HTML files, and empty documents.
-Furthermore, some documents contain gibberish, often as a result of faulty or impartial optical character recognition applied to text that was produced through a non-machine-readable medium.
-To combat this problem, we employ two solutions.
-One, we use spellchecking, implemented through the \texttt{hunspell} R package \citep{hunspell}, to remove all non-English words.\footnote{Some of the cities, for example, Los Angeles, do contain a sizable proportion of Spanish content.
-The analysis of this content is beyond the scope of this paper but could be explored in future work, for example using methods of text processing that are applicable to multilingual corpora \citep{lucas2015computer}.
-} However, \texttt{hunspell} does not cover everything, either because some tokens are not actual words (for example artifacts from defective encoding), or because random sequences of characters just so happen to form words that exist in a dictionary (for example "eh" or "duh").
-Since we rely on a bag-of-words model in which syntax does not matter, we can ameliorate these problems by removing all text except for whitespaces and the characters that appear in the English alphabet.
-Since a lot of the nonsensical text tends to be quite repetitive, we also delete all documents in which the proportion of unique to the total number of tokens is less than 0.15.
-Furthermore, \texttt{hunspell} does not spellcheck individual characters or two-character words, so we remove these token types entirely.
-Since these pre-processing steps reduce documents which are largely unsuitable to only a few tokens (i.e., word occurrences), we also remove all remaining documents containing less than 50 tokens.
-Finally, to remove words that are extremely rare (which also has the advantage of eliminating any remaining oddities) and thus add nothing substantive\footnote{Topic models essentially do not pick up on extremely rare words, so their inclusion is a waste of computational resources.
-Removing them in this manner is also the default preprocessing choice in the \texttt{stm} package.} to our models while increasing their computational cost, we also discard any token types that occur in only one document.
-
-%\subsection{Boilerplate Removal}\label{boilerplate}
-%As noted above, city websites contain a large amount of text that is uninformative for its actual content, and therefore a hindrance to understanding through algorithmic text analysis.
-This is a common issue with textual data in which informative content is embedded in technically structured documents.
-See, e.g., \citet{burgess2016legislative,wilkerson2015tracing} and \citet{linder2018text} for examples of boilerplate removal in the analysis of legislative text.
-
-%\subsection*{Boilerplate Classification}
-%In order to determine whether a line should be discarded, we train a classifier on a human-coded sample.
-We sampled 500 lines from documents in each of the following five cities: Los Angeles, CA, Indianapolis, IN, New York, NY, Shreveport, LA, and Seattle, WA.
-To ensure that lines which occur more frequently in these cities (sometimes hundreds of thousands of times) had a higher probability of being scrutinized by the classifier, we use sampling weights equivalent to the proportion of total lines in a city's corpus made up by each specific line type.
-As an example, the most common line throughout all pages of the city of Seattle consists only of the word ``total'' and occurs 103,068 times.
-Similarly, the line ``page'' occurs 58,833 times.
-Even something completely nonsensical such as ``a a'' still appears on 376 occasions.
-To account for the higher likelihood of some lines being part of the training set, we use inverse probability weights in training the classifier---the weight of each line in the sample is 1/[number of occurrences in the corpus].\footnote{Note that the performance of the classifier is robust to the use of these weights and only changes by about one percentage point if they are not used.}
-
-%These 500 lines were then hand-coded as either substantively informative (210 lines) or not (290 lines).
-We then trained a number of different classifiers with this informativeness measure as the dependent variable.
-The independent variables we use are: (1) number of times the line was duplicated within the city, (2) the length of the line, in characters, (3) the number of tokens in the line, and (4) the median distance from the document midpoint to the position of the line itself.
-The purpose of these covariates is as follows:
-
-\section{Partisan Language on Municipal Websites}
+\section{Partisan Language on Municipal Websites} \vspace{-.3cm}
 
@@
 We consider whether the partisan manipulation of city website contents documented in this example holds in a large-scale and more recent sample of city websites.
-We illustrate the analysis of municipal website content by studying the ways in which differences in website content correlate with the partisanship of the city's mayor mayor.
+We illustrate the analysis of municipal website content by studying how differences in website content correlate with the partisanship of the city's mayor.
 As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance.
@@
 These constraints do not apply to website contents.
-City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.
+City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and city websites provide an effective and often-used means of communication with city residents.
 
@@
 
-To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
+We use well established web-scraping and text-processing tools to go from a list of municipal website URLs to a corpus of clean text to analyze.
+The first step is to automatically download the entire file contents of municipal websites, which we do using the Unix tool \texttt{wget} \citep{glez2013web}.
+Step two is to convert each file (including, e.g., HTML, DOC, PDF) into a plain text file, which we do using the \texttt{readtext} R package \citep{readtext}.
+Step three is to discard website boilerplate text (e.g., navigation menus), which we do using the ``boilerpipe''  algorithm \citep{Kohlschutter2010}, which is implemented in the R package \texttt{boilerpipeR}.
+The fourth step is a final processing wave applied to the resulting text corpus, which includes, e.g., removing strings that are not English words.
+This web-scraping and processing pipeline is described in greater detail in the supplementary material, and we have implemented all but the first step in a new R package (\texttt{gov2test}).
+
+To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed model for text, the structural topic model (STM), developed by \citet{Roberts2014}.
 Building on the conception of ``topics'' in conventional topic models \citep{valdez2018topic}, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary.
@@
 We also include the municipality's population and median income as covariates.
-Further details on and results from our STM specification can be found in the online appendix.
+Further details on and results from our STM specification can be found in the supplementary material.
 
+\vspace{-.4cm}
 \subsubsection{Structural topic model results}
@@
 The results are shown in Table \ref{tabSTMtopwords60}.
-First, it is notable that the 95\% credible interval includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor.
+First, it is notable that the 95\% credible interval includes zero (indicated by rows with white backgrounds) in only seven of the sixty topics.
+This suggests that the topics discussed on city websites varies systematically with the partisanship of the mayor.
 Many of the topics associated with Democrats fit with what we understand to be national party priorities.
@@
 Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51}), vaccination (Topic \textbf{2}),  and sanitation (Topic \textbf{47}), are prevalent among cities with Republican mayors.
-These basic service topics cannot be found among topics prevalent in cities with Democratic mayors.
+These basic service issues cannot be found among topics prevalent in cities with Democratic mayors.
 Similarly, zoning issues figure prominently in the set of republican topic (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules.
@@
 %\input{tables/stmTopWords.tex} %\ref{tabSTMtopwords}
-
-\input{tables/stmTopWords60.tex}
+\vspace{-.2cm}
+\input{tables/stmTopWords60.tex} \vspace{-.2cm}
 %\input{tables/stmTopWords60_OLD.tex} %\ref{tabSTMtopwords2}
 
-\section{Conclusion}
+\vspace{-.8cm}
+\section{Conclusion} \vspace{-.3cm}
 
-We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
-We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline.
+We have proposed the automatic collection and processing of government websites for comparative content analysis.
+We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of the methods we use.
 This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
@@
 
-The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
-By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
-For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
-We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
-This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.}
-
+\vspace{-.6cm}
 %We offer several contributions that will be valuable in future research endeavors.
@@
 %\input{tables/stateUrlSummary.tex}
-
+\begin{spacing}{1.25}
  \bibliographystyle{chicago} % apsr stopped working for me
@@
 \bibliography{ref}
+\end{spacing}
 

### 2020-01-17 paper/manuscript_aprNote_OA.tex
revising for APR

--- 2020-01-17 paper/archived/manuscript_ssqNote_OA copy.tex
@@
 
+\linespread{0.9}
 %============Article Title, Authors==================
-\title{\vspace{-2cm} {\bf Online Appendix} \\ Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} {\bf Online Appendix} \\ Government Websites As Data: \\ Understanding how Mayoral Partisanship Shapes Municipal Website Content}
 
@@
 
-\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
-Our objectives and corresponding contributions in this research note are two-fold.
-First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
-Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-\\~\\
-\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \\~\\
-\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
-We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
-\\~\\
-\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.
-
+A local government's website is an important source of information about policies and procedures for residents and community stakeholders .
+Existing research in political science and related fields has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
+In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
+Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
+In our application, we collect and analyze a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
+We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
+Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
+As an additional contribution, we provide an R package that can be used to process government website files into raw text.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 
-In this online appendix we include supporting information about our data, the data collection process, and some additional analyses.
+In this online appendix we include supporting information about our data, the data collection process, the data collection and cleaning pipeline, and some additional analyses.
 In the first section, we present additional details on data collection, along with some additional descriptive statistics.
@@
 \input{tables/tabFiletypeFrequencies.tex}
+
+\section{The Web to Text Pipeline} \vspace{-.2cm}
+In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents.\footnote{It is useful to note a couple of features that we do not intend to provide with this pipeline.
+First, this is not intended to be a pipeline for scraping and analyzing any and all websites.
+Our focus is on government websites, as we assume that the contents are in the public domain, and not subject to limitations on the application of scraping technology.
+Second, though such extensions would be valuable, we do not address the collection and analysis of image, video, sound, and  tabular data from government websites.}  We address three methodological challenges.
+First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
+Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
+The first step is aimed at extracting clean plain text from this heterogeneous file base.
+The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
+Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.
+We make a software recommendation for each of these steps and gather most of them our R package, \texttt{gov2text}.
+All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem.
+As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.
+Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
+We will clarify this distinction as we describe steps in our pipeline.
+
+\subsection{Site to Text Conversion}
+\subsubsection{File Type Detection}
+The format of a file has a major impact on whether and how textual data can be extracted from a document.
+For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
+However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text.
+For example, we found thousands of documents that ended in .html, when they were actually PDFs.
+A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification.
+We implement this method using the R package \texttt{wand} \citep{wand}.\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}
+
+\subsubsection{Extracting Text from HTML}
+The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate.
+The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
+The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{fig:garymayor}.
+The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site.
+The Mayor's message represents a relatively small fraction of the total text on the page.
+
+\begin{figure}
+\centering
+{\bf (a)} Naive Parsing  \\ \vspace{.2cm} 
+\includegraphics[scale=0.35]{figures/gary_sidebyside} \\ \vspace{.4cm}
+{\bf (b)} Boilerpipe 
+\includegraphics[scale=0.375]{figures/gary_bp}
+
+\caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.
+Bottom image provides the result of running \url{https://garyin.us/} through the \texttt{boilerpipe} algorithm at \url{https://boilerpipe-web.appspot.com/}.}
+\label{fig:garysbs}
+\end{figure}
+
+A subfield of the information retrieval literature, dealing with boilerplate extraction, can offer a solution to this problem.
+The goal of this branch of research is to develop algorithms with the ability to estimate whether a given portion of an HTML file is substantive.
+To this end, structural features, such as HTML tags (which are not sufficiently informative on their own), text statistics such as word and sentence length, as well as other heuristics are used.
+We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
+The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in the social sciences.
+The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}.
+We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data.
+We show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
+}
+
+\subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
+The extraction of information from other text-based file formats is more straightforward.\footnote{See \cite{Berg2012} for a discussion of why extracting text from PDFs is nevertheless nontrivial.} To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
+The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
+Files of type DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.
+
+\subsection{Preprocessing}
+Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}.
+As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model.
+The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing.
+The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites.
+Some of it is substantively informative and some of it is completely irrelevant.
+As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents.
+The same is true for streets, locations and not least of all, the city itself.
+Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city.
+Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.
+
+%The type of text analysis we conduct---topic modeling---requires that the words in the document be meaningful and interpretable, and does not make use of the sequence of words within a document (i.e., is a bag-of-words method).
+%With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
+
+To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER).
+In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended.
+Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
+Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word.
+} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
+To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).
+A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
+In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
+%The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
+For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus.
+These short and repetitive -- but numerous -- texts would pose severe problems to a topic model.
+Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.
+
+After preprocessing, our corpus consists of 356,911 documents.
+In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data.
+The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.
+
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{lrr}
+        \hline
+        Process & Software dependency & in \texttt{gov2text} \\
+        \hline
+        1. Assemble url list. & \texttt{Selenium} & no \\
+        2. Collect website files. & \texttt{wget} & no \\
+        3. Correct file extensions. & \texttt{wand} \citep{wand} & yes \\
+        4. Discard website boilerplate. & \texttt{boilerpipeR} \citep{boilerpipeR} & yes \\
+        5. Convert non-HTML files to text. & \texttt{readtext} \citep{readtext} & yes \\
+        6. Lemmatize text. & \texttt{spacyr} \citep{spacyr}& yes \\
+        7. Remove names. & \texttt{spacyr} & yes \\
+        8. Retain nouns, verbs, adjectives. & \texttt{spacyr} & yes \\
+        9. Stopword/number removal. & \texttt{quanteda} \citep{quanteda} & yes \\ 
+        10. Retain only English words. & \texttt{Hunspell} \citep{hunspell} & yes \\
+        11. Removal of duplicate documents. & \texttt{gov2text} & yes \\
+        \hline
+    \end{tabular}
+    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.}  \vspace{-.9cm}
+\end{table}
+
+The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
+By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
+For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
+We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
+This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.}
 

### 2021-03-23 paper/archived/manuscript_aprNote.tex
pushing JITP

--- 2020-01-17 paper/manuscript_aprNote.tex
@@
 
-A local government's website is an important source of information about policies and procedures for residents and community stakeholders .
-Existing research in political science and related fields has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
+A local government's website is an important source of information about policy priorities,  procedures, and debates.
+Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
 In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
-Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information.
-In our application, we collect and analyze a new and innovative dataset---the websites of over two hundred municipal governments in the United States.
-We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website.
+We also provide software to ease the use of this data collection method.
+In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship.
 Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
-As an additional contribution, we provide an R package that can be used to process government website files into raw text.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime.
-On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
+On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{brown2017republicans}.
 On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on law enforcement, even after controlling for crime \citep{Einstein2015}.

### 2021-03-23 paper/archived/manuscript_aprNote_title.tex
pushing JITP

--- 2020-01-17 paper/archived/manuscript_ssqNote_OA copy.tex
@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} {\bf Online Appendix} \\ Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} Government Websites As Data: \\ Understanding how Mayoral Partisanship Shapes Municipal Website Content
+\footnote{This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}}
 
-%\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
 Email: mvn5218@psu.edu.
@@
 
-\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
-Our objectives and corresponding contributions in this research note are two-fold.
-First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
-Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-\\~\\
-\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \\~\\
-\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
-We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
-\\~\\
-\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.
-
+A local government's website is an important source of information about policy priorities,  procedures, and debates.
+Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
+In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
+We also provide software to ease the use of this data collection method.
+In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship.
+Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.
@@
 % Description of the possible challenges
-\doublespacing
-
-\section{Overview}
-
-In this online appendix we include supporting information about our data, the data collection process, and some additional analyses.
-In the first section, we present additional details on data collection, along with some additional descriptive statistics.
-In the second section, we provide additional details on, and results from, our topic modeling analysis.
-
-\section{Data collection methods and sources}
-
-We acquired the municipal website URLs from two sources: One, we scraped the URLs of city websites from their respective Wikipedia pages, which we found from lists of cities contained within each state.
-Two, the General Services Administration (GSA) maintains all `.gov' addresses, and provides a complete list of all such domains to the public.\footnote{The dataset is made available at \url{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}.
-This list is updated once per month---we rely on the version released on January 16, 2017.} The data from the GSA contains the following variables: (1) domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'); (2) the type of government entity to which the domain is registered, such as city, county, federal agency, etc; (3) for federal agencies, the name is specified; (4) the city in which the domain is registered.
-Naturally, the GSA's list does not contain cities which do not use a `.gov' website (or, in many cases, a city owns a registered `.gov' address, but uses a different one).
-Furthermore, some of the links are non-functional, and some of the county websites on the list are incorrectly marked as city websites (and vice versa).
-Since the GSA data is less complete and less reliable than the URLs found on Wikipedia, we mainly rely on the latter and only supplement them with the GSA data if a specific city doesn't have a URL recorded on Wikipedia, or our tests (see below) find it to be non-functional.
-
-Not all of the URLs contained in these archives are functional.
-To test the URLs' functionality, we use a web driver-controlled browser - a browser that is automatically controlled by a program rather than a human user.
-We use the Python bindings for the program \texttt{Selenium}, which we use to control \texttt{Firefox} through the web driver  \texttt{Geckodriver}.
-This is advantageous compared to conventional scraping tools such as \texttt{Beautiful Soup} or \texttt{Rvest} because most websites are designed to be explored by browsers.
-Modern browsers perform a lot of actions behind the scenes, such as URL resolution and redirection.
-The use of a web driver-controlled browser is necessary in our case because a) some city websites simply don't work, but they don't always output an error code correctly (this can fail, for example, if a webmaster simply stops maintaining a site without removing it entirely) which would throw off an automatic scraper, and more often, b) cities sometimes change their websites' URLs, in which case they redirect from the old to the new URL.
-A web driver-controlled browser, unlike the more rigid conventional scraping tools, will simply follow this redirection.
-This allows us to subsequently record and use the new URL for the actual website scraping.
-Consequently, an automated browser allows us to robustly answer the following questions: Is the website actually there?
-Does it work?
-If not, is it somewhere else or is it broken?
-We record this information and construct a list of verified URLs.
-
-To download the websites, we rely on the Unix command line tool \texttt{wget}.\footnote{An alternative source of web data which has attained some popularity within the digital humanities is the Internet Archive's Wayback Machine (\url{https://archive.org/}), which preserves snapshots of websites over time.
-In theory, this would be very useful to projects such as ours, since it would allow us to measure the evolution of websites over time, in response to changes in city executives.
-However, the Wayback Machine suffers from some limitations that, in our eyes, inhibit its usefulness for scientific research in general, and our project in particular.
-First of all, the Internet Archive does not conduct all of its web crawling itself.
-Rather, third parties donate their crawling data to the Internet Archive.
-This means that the source of the data varies and the crawling process often remains opaque, which is a problem with respect to scientific transparency.
-Second, this also means that the crawling isn’t done in regular intervals unless the website in question is extremely prominent.
-Our research is focused on municipal websites, many of which are fairly obscure, preventing the Wayback Machine from being useful to us.
-For example, as of the time of writing, the website of Attica, IN, has only been crawled 25 times since the Wayback Machine's inception in 1996 (and in this case, all of these crawls are from 2014 on).
-By contrast, the website of New York City has been crawled over 7,000 times.
-Third, webcrawls are not instant and are not always done on an entire website at the same time.
-This means that for example, a website's frontpage might have been scraped one day, and its page on the city's mayor only a month later -- within the same crawl.
-Once again, this problem is exacerbated for small, less prominent websites.
-While we appreciate the Internet Archive's efforts to preserve snapshots of the web and recommend its API to practitioners who can work around the limitations outlined here, these problems preclude its usefulness for our purposes.} This program is used to download files from the Internet, and with the use of a recursive option, acts like a web crawler and scraper.
-This means that \texttt{wget} downloads HTML files, parses them and then follows the links contained therein.
-Then it follows those links and repeats the process until it has constructed a complete tree of the website (note that the program is instructed to stay on the same domain, i.e.
-it does not follow external links).
-This way, all the files that make up a website are downloaded.
-For some cities, whose websites make heavy use of JavaScript to serve content dynamically, such content is not reachable with our methodology and would require additional steps to obtain.
-For this paper, we ignore such sites and restricted our corpus to cities with at least three successfully downloaded pages.\footnote{There is a possibility that this leads to a small bias in selecting against cities with the resources to build more elaborate websites.
-However, given that our sample is generally more on the wealthy side, this, if anything, should lead to a more balanced sample.}
-
-The partisanship of the mayor of each city is coded in different ways, depending on the state.
-For Indiana, where elections are nominally partisan, this information is accessible through the state government's website\footnote{\url{http://www.in.gov/apps/sos/election/general/general2015?page=office&countyID=1&officeID=32&districtID=-1&candidate=}}.
-For Louisiana, we received data on the outcomes of mayoral elections from the Local Elections in America Project (LEAP) \citep{marschall2013local}.
-For the other states, where mayoral elections are not nominally partisan (but the partisanship of the mayor is still well-known), we employed different means: For New York and Washington, we searched the state campaign finance websites, and coded the parties of the candidates based on the party committees from which they received donations.
-For California and Texas, where our data consists of highly populated cities, partisanship information was acquired from Ballotpedia\footnote{\url{https://ballotpedia.org/List_of_current_mayors_of_the_top_100_cities_in_the_United_States}}.
-Finally, we also scraped mayoral partisanship from the cities' Wikipedia pages.
-When compared to the other data sources above, (and manual searches in case of conflicts) Wikipedia proved to be very reliable and added additional cases to our dataset even for Indiana and Louisiana.
-Generally speaking, we found data scraped from Wikipedia, aided by manual corrections in case of missing or conflicting data, to be more reliable than data from governmental sources.\footnote{In Indiana, the data includes only cities - incorporated municipalities with at least 2,000 inhabitants - as opposed to towns.}
-
-Information on other covariates (population and median household income - from the American Community Survey 5-Year Data (2015)) was acquired through the API of the U.S.
-Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
-
-%One of the more subtle aspects of local government is the presence of different types of government structures.
-Between council-manager governments and mayor-council governments \citep{morgan1992policy}---either in the weak or strong mayor variant \citep{desantis2002city}---there is variance in where a city's executive authority lies.
-We do not have access to information about the type of governments across the breadth of our dataset.
-Given the prominent place that mayors tend to have on their cities' websites, we feel that any bias arising from this nuance should be minor.
-\cite{gerber2011mayors}, whose theory is somewhat comparable to ours, find that the inclusion of this potential confounder does not affect the results.
-
-Tables \ref{tab:cityparties} and \ref{tab:filetypes} provide additional information about the data collected for this project.
-In Table \ref{tab:cityparties}, we present the state-by-state breakdown of the mayoral partisanship of the cities collected in the respective state.
-In Table \ref{tab:filetypes}, we present the distribution of file extensions before and after processing.
-
-\input{tables/tabCitiesStatesParties.tex}
-
-\input{tables/tabFiletypeFrequencies.tex}
-
-\section{Supplemental Informational on Topic Modeling Application}
-
-The structural topic model is implemented in the R package \texttt{STM} \citep{stm}.
-We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora.\footnote{Since our corpus is at the larger end of that spectrum, we also estimated a model with 120 topics, but found no notable differences.} We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic.
-Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}).
-Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city.
-Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.\footnote{The ``Fightin' Words'' methodology developed by \citet{Monroe2008} could also be used to analyze word-frequency differences between cities based on mayors' partisanship, but we elected to use the structural topic model since, unlike ``Fightin' Words'' , the structural topic model enables us to adjust for several other features through multiple regression.}
-
-\subsection{Supplemental results}
-
-In Table \ref{tabSTMtopwords60keep}, we present topic results from an STM, and mayoral party effect, estimated on data processed using a minimal HTML parser, implemented as the 'KeepEvertything' algorithm in the boilerpipeR package.
-An illustration of the content removed by the full boilerpipe procedure is given by Topic 56.
-This is the fourth-most Republican topic, and is a website boilerplate topic, with top words 'click', 'reserved', 'trademark', 'password', 'search', and 'connected'.
-As further illustration, the second-most Democratic topic is another website boilerplate topic, with top words 'sitemap', 'clerk', 'calendar', 'online', 'bureau', and 'alert'.
-We do not see any clear boilerplate topics when using data processed using boilerpipe.
-
-\input{tables/stmTopWords60_KeepEverything.tex}
-
-In Tables \ref{tabSTMtopwords120_1} and \ref{tabSTMtopwords120_2}, we present results of the STM with 120 topics organized according to the effect of mayoral partisanship on topic prevalence.
-The partisan themes in the 120-topic STM mirror those in the 60-topic model, with cities led by Democratic mayors focused disproportionately on finances (e.g., Topics 75, 71, 61) and social problems (e.g., Topics 93, 101, 39, 52), and cities led by Republican mayors focused disproportionately on basic services and utilities (e.g., Topics 114, 11,  86, 116).
-
-\input{tables/stmTopWords120_1.tex}
-\input{tables/stmTopWords120_2.tex}
-
-In Tables \ref{tabSTMtopwords60_income} and \ref{tabSTMtopwords60_population}, we present the topics ordered according to the effects of median income and population, respectively.
-Considering income-based variation in topics, there are several topics prevalent in more wealthy cities that focus on initiatives that go well-beyond standard city services---downtown and building revitalization (Topics 39 and 12), renewable energy (Topic 20), bike/pedestrian-oriented development (Topic 60), wildlife conservation (Topic 3).
-Such topics cannot be found among those that are more prevalent in less wealthy cities.
-When it comes to population, more populous cities deal disproportionately with issues related to public health (Topics  2 and 11), crime (Topic 59), homelessness (Topic 52), and diversity (Topic 6).
-
-In Figure \ref{fig:coherence_exclusivity}, we present a quantitative assessment of relative topic quality for our main model, using two metrics, semantic coherence and exclusivity.
-Semantic coherence \citep{Mimno2011} describes the extent to which the 10 top words in a topic model belong to the same underlying concept.
-Exclusivity \citep{Bischof2012,Roberts2014} measures whether the top 10 words in one topic feature primarily in this topic, rather than being dispersed across a range of topics.
-As coherence tends to be outright better in models with fewer topics, the comparison with exclusivity creates a trade-off.
-Figure \ref{fig:coherence_exclusivity} shows that the model performs well in this regard, as most topics have both high coherence and exclusivity.
-Even topic 11, which does worst in terms of coherence, looks like a good topic upon manual inspection, as its top words all pertain to obesity.
-
-\input{tables/stmTopWords60_income.tex}
-\input{tables/stmTopWords60_population.tex}
-
-\begin{figure}
-	\centering
-	\includegraphics{figures/stm_60_coherence_exclusivity.pdf}
-	\caption{Semantic coherence and exclusivity for each of the 60 topics in our main structural topic model.
-Coherence describes the extent to which the 10 top words in a topic model belong to the same underlying concept.
-Exclusivity measures whether the top words in one topic feature primarily in this topic, rather than being dispersed across a range of topics.
-The model performs well in this trade-off, as both coherence and exclusivity are high for most topics.}
-	\label{fig:coherence_exclusivity}
-\end{figure}
-
-%\input{tables/tabCitiesStatesParties.tex}
-%\input{tables/stateUrlSummary.tex}
-
-\bibliographystyle{chicago} % apsr stopped working for me
-%\bibliographystyle{plainnat}
-\bibliography{ref}
-
-%\begin{figure}[htp]
-  %  \centering
-   % \caption{Five largest topic effects for the population covariate.
-The fact that the population and epidemiology topics are positively correlated with city size is indicative of the model's validity.}
-    %  \label{stmEffectPop}
-    % \includegraphics[width=\linewidth]{figures/stm_effect_pop.pdf}
-% \end{figure}
-
-% \begin{figure}[htp]
-  %  \centering
-   % \caption{Five largest topic effects for the median income covariate.
-The fact that the crime topic is most prevalent in poorer cities, good governance is the most positively correlated with income is indicative of the model's validity.}
-   % \label{stmEffectIncome}
-    %\includegraphics[width=\linewidth]{figures/stm_effect_income.pdf}
-%\end{figure}
 
 \end{document}
-
-%\begin{enumerate}
-%    \item Design
-%    \begin{enumerate}
-%        \item Choosing the sample
-%        \item Finding URLs
-%        \item list of .gov websites
-%        \item Finding supporting data
-%    \end{enumerate}
-%    \item Scraping
-%        \begin{enumerate}
-%            \item wget
-%            \item headless browser/Selenium
-%            \item Beautifulsoup/rvest
-%            \item APIs (httr)
-%            \item Wayback Machine
-%        \end{enumerate}
-%    \item Pre-processing
-%        \begin{enumerate}
-%            \item Determining document filetype
-%            \item File conversion
-%            \item Conventional preprocessing (lowercase, numbers, punctuation)
-%            \item Stemming and lemmatization
-%            \item spellchecking
-%            \item Dealing with duplicate text \& html documents in particular
-%        \end{enumerate}
-%    \item Analysis
-%        \begin{enumerate}
-%            \item LDA
-%            \item Other topic models (structural, author, dynamic -- maybe?)
-%            \item SVM (+ other machine learning classifiers?)
-%            \item Fightin Words
-%        \end{enumerate}
-%\end{enumerate}
-%
-%
-%
-%
-%
-%
-%% latex table generated in R 3.3.3 by xtable 1.8-2 package
-%% Wed Mar 22 11:32:43 2017
-%%\begin{table}[ht]
-%%    \centering
-%%    \begin{tabular}{lrrlrrl}
-%%        \hline
-%%        City & DemVotes & RepVotes & Winner & Change & Pop15 & url \\ 
-%%        \hline
-%%        Attica &  & 187 & Republican & 0 & 3117 & https://attica-in.gov/ \\ 
-%%        Connersville & 1005 & 995 & Democratic & 1 & 13010 & http://connersvillecommunity.com/ \\ 
-%%        Frankfort &  & 1748 & Republican & 0 & 16060 & http://frankfort-in.gov/ \\ 
-%%        Huntingburg & 447 & 793 & Republican & 0 & 6035 & http://www.huntingburg-in.gov/ \\ 
-%%        Indianapolis & 92830 & 56661 & Democratic & 1 & 862781 & http://www.indy.gov \\ 
-%%        Lake Station & 1483 & 227 & Democratic & 0 & 12054 & http://www.lakestation-in.gov/ \\ 
-%%        Linton & 785 & 692 & Democratic & 0 & 5284 & http://www.linton-in.gov/ \\ 
-%%        Madison & 1192 & 1915 & Republican & 0 & 12040 & http://www.madison-in.gov/ \\ 
-%%        Mitchell & 229 & 495 & Republican & 1 & 4252 & http://mitchell-in.com/ \\ 
-%%        Monticello & 0 &  & Democratic & 0 & 5322 & http://www.monticelloin.gov/ \\ 
-%%        North Vernon & 679 & 697 & Republican & 1 & 6619 & http://www.northvernon-in.gov/ \\ 
-%%        Richmond & 3421 & 2731 & Democratic & 0 & 35854 & http://www.richmondindiana.gov/ \\ 
-%%        Rockport & 286 & 272 & Democratic & 1 & 2223 & http://www.cityofrockport-in.gov/ \\ 
-%%        South Bend & 8515 & 2074 & Democratic & 0 & 101516 & https://www.southbendin.gov/ \\ 
-%%        Union City & 338 & 440 & Republican & 0 & 3447 & http://www.unioncity-in.gov/ \\ 
-%%        Winchester & 606 & 524 & Democratic & 1 & 4769 & http://www.winchester-in.gov/ \\ 
-%%        \hline
-%%    \end{tabular}
-%%    \caption{} 
-%%\end{table}
-%
-%\subsection{Research Design}
-%
-%\begin{table}[ht]
-%    \centering
-%    \begin{tabular}{llr}
-%        \hline
-%        Variable & Unit & Source \\
-%        \hline
-%        Population size & 1000 people & Census \\
-%        Population growth last 5 years & Percent & Census \\
-%        Type of economy (agriculture/industry/services) & ? & Census \\
-%        Economic performance (GDP?) & \$ & Census \\
-%        Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-%        Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
-%        Change of party control & 0/1 & in.gov/sos/elections/ \\
-%        Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
-%        Unemployment rate & Percent & Census \\
-%        Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
-%        \hline
-%    \end{tabular}
-%    \caption{List of covariates} 
-%\end{table}
-%
-%
-%
-%\begin{enumerate}
-%\item Corpus:
-%\begin{enumerate}
-%\item Last snapshots before the election (November 3, 2015 in Indiana; tbd. in Louisiana (probably February))
-%\item First snapshot that is at least 2 months after the new government's inauguration (which is in January for Indiana, May for Louisiana)
-%\end{enumerate}
-%\item Preprocessing:
-%\begin{enumerate}
-%\item restrict corpus to:
-%\begin{enumerate}
-%\item documents belonging to cities in which a change of power occurred
-%\item documents that were added, deleted or changed between the two snapshots
-%\end{enumerate}
-%\item words to lowercase
-%\item remove punctuation
-%\item stemming (Porter stemming algorithm?)
-%\item Remove stop words (regular list of stop words is enough, since we use an asymmetric prior)
-%\end{enumerate}
-%\item Apply Grimmer's expressed agenda model to the corpus
-%\begin{enumerate}
-%\item Asymmetric prior
-%\item Each document can have only one topic (in contrast to the author-topic model)
-%\item Cities $i = 1,..., n = 15$
-%\item Topic $k(k = 1,..., K )$
-%\item Documents $j(j = 1,...,D_i)$ from city i
-%\item Party covariate in the prior, where the deleted and unmodified documents are coded as from the first, and the added and modified documents from the second party
-%\end{enumerate}
-%\item Results
-%\begin{enumerate}
-%\item Label topics using Grimmer's automatic cluster labeling method, based on most commonly used words in documents belonging to topic
-%\item Evaluate topics
-%\end{enumerate}
-%\end{enumerate}
-%
-%Validation:
-%
-%\begin{itemize}
-%\item Do the above for cities in which no change of power occurred.
-%\item Check whether there is higher than average turnover around the new year by comparing changes to non-election years (and also Louisiana, where elections are later).
-%\item Check how long documents stay on websites on average. Use websites with a lot of snapshots for this (these exist for both small and large cities).
-%\end{itemize}
-%
-%Problem with using this model: Grimmer's expressed agenda model uses Senators as the actors.
-Senators is also who he is substantively interested in.
-For us, the equivalent to Senators is cities.
-However, we care about parties, not cities.
-%
-%\subsection{Survival model}
-%The existence of individual documents on municipal government websites can be though of as a survival process.
-No document stays on a website forever, and it appears to be a reasonable assumption that as documents get older and thus less relevant, they get replaced.
-The factors determining the steepness of the survival curve are the topic - fire safety regulations likely stay up longer than a bulletin on the annual spring banquet - and the change of party control after an election.
-%
-%\begin{quote}
-%\textit{H1}: The older a document, the more likely it is to be removed.
-%\end{quote}
-%
-%$S(t)$ has a downward slope. Admittedly, this is almost impossible not to be true. Also, test proportional, rising and falling hazard models.
-%
-%\begin{quote}
-%\textit{H2}: Documents pertaining to administrative matters are less likely to be removed.
-%\end{quote}
-%
-%Introduce a categorical variable for the top 10(?) topics. A negative coefficient for administrative topics would support this hypothesis.
-%
-%\begin{quote}
-%\textit{H3}: Documents introduced by the opposing party are more likely to be removed.
-%\end{quote}
-%
-%Introduce two variables into the survival model: One variable indicating which party has introduced a document, and a time-varying variable describing which party is currently in government.
-The hypothesis is tested through an interaction term between the two.
-%
-%\begin{quote}
-%\textit{H4a}: Democrats are more likely to remove documents with topics pertaining to private enterprise, private schools.
-%\end{quote}
-%
-%Interaction term between party in power and categorical topic variable.
-%
-%\begin{quote}
-%\textit{H4b}: Republicans are more likely to remove documents with topics pertaining to social justice, equality, taxes, public schools, etc.
-%\end{quote}
-%
-%Interaction term between party in power and categorical topic variable.
-%
-%\begin{quote}
-%\textit{H5}: In line with their commitment to small government, Republicans are more likely than Democrats to remove documents.
-%\end{quote}
-%
-%Party in power variable.\\
-%
-%
-%This model will take up a lot of degrees of freedom. The rarity of snapshots for some cities might be a problem. Documents being changed and being removed can be modeled as competing risks.
-%
-%
-%\begin{equation} 
-%\label{eq1}
-%\begin{split}
-%Y & = \text{Party that introduced the document} \\
-% & + \text{Party that is currently in power} \\
-% & + \text{Topic 1, topic 2, ..., topic k} \\
-% & + \text{Party that is currently in power} \times \text{Topic 1, topic 2, ..., topic k} \\
-% & + \text{Days since start of mayoral term (control)}
-%\end{split}
-%\end{equation}
-%
-%
-%
-%
-%
-%After the counties, townships and cities that cannot be matched to the Census data\footnote{There are five cities that are not contained in the Census data} and duplicate websites (some cities have more than one website) are removed, 1813 domains/cities remain.
-%
-%These cities contain 90,616,865 people, and thus about 28\% of the U.S. population (see figure 1).
-%
-%\begin{figure}[htp]
-%    \centering
-%    \caption{Percentage of state population covered.}
-%    \includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
-%\end{figure}
-%
-%We use the resulting list of websites to acccess their copies stored in the Internet Archive's Wayback Machine.
-To this end, we rely on the Ruby Gem 'Wayback Machine Downloader'\footnote{https://github.com/hartator/wayback-machine-downloader} (WbMD).
-We supply the URL that each .gov website redirects to to the WbMD, which then downloads every file present in the WbM from a snapshot in October 2016, or, if not available, as soon as possible after this point.
-%
-%<Note: We have not actually done this last step for all websites (however, the R script which runs the Ruby package is already set up to do so once we need to).
-Instead 10 websites were randomly sampled from an older version of the GSA list, which still contained counties and townships, which is why one of the 10 websites is from Dutchess County, NY.>
-%
-%It would be fine to focus on Indiana as a case. First, we need to answer some preliminary questions about the data.
-%
-%\begin{enumerate}
-%
-%\item For what percentage and number of IN cities can we find data from the WBM?
-%\item For how many election cycles can we find political leadership data for these matched cities?
-%\item In what number and percentage of cities is the local leadership majority Republican? 
-%\item Relatedly, in a typical election cycle, for how many cities do we see a transition in party leadership (i.e., a shift from majority D (R) to majority (R) D). 
-%
-%\end{enumerate}
-%
-%\begin{enumerate}
-%    
-%    \item 30 cities, with a combined population of 1,180,435.
-However, since only cities (as opposed to towns and villages) hold mayoral elections, only 16 of these, with a combined population of 1,094,383 can be matched to the election data.
-%    \item 2015, 2011, 2007, 2003.
-%    \item Of the 16 cities, 7 have Republican mayors after the 2015 elections.
-%    \item In 6 cases, a shift of party control occurs, with 4 of these being Republican --> Democratic. 
-%    
-%\end{enumerate}
-%
-%
-%
-%
-%\section{Running Application: Party Differences in Municipal Websites}
-%
-%
-%\begin{landscape}
-%\begin{table}[htbp]
-%    %\caption{}
-%    \begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-%        \hline
-%        Names & Year & Journal & Findings & Important? \\ \hline
-%        Benedictis-Kessner, Justin De
-%        Warshaw, Christopher & 2016 & JOP* & Regression discontinuity design.
-Democratic mayors spend more (but it is unclear on what, not the typical Democratic issue-areas), issue more debt, pay more interest & Yes \\ \hline
-%        Caughey, Devin
-%        Warshaw, Christopher
-%        Xu, Yiqing & 2015 & Working Paper & Regression discontinuity design.
-Partisan composition of state governments affects state policy liberalism (composite index for the areas of social welfare, taxation, labor, civil rights, women’s rights, moral legislation, family planning, environment).
-& Somewhat \\ \hline
-%        Einstein, Katherine Levine
-%        Kogan, Vladimir & 2015 & Urban Affairs Review & Cities with more Democratic citizens spend more; more progressive (rather than regressive) forms of taxation; pursue intergov.
-aid more; spend more on police, fire, parks \& recreation & Somewhat \\ \hline
-%        Einstein, Katherine Levine
-%        Glick, David M.
-& 2015 & Working Paper & Survey of 72 mayors.
-Unlike Republican mayors, roughly half of Democrats seem to agree that cities should aim to reduce inequality.
-Democratic mayors also seem to favor redistribution to accomplish that goal.
-& Somewhat \\ \hline
-%        Kiewiet, D Roderick
-%        Mccubbins, Mathew D & 2014 & Annual Review & City budgets have been severeley constrained since the Great Recession.
-Spending has thus decreased in general.
-Lack of funds means that there is not much discretion for partisanship.
-& Somewhat \\ \hline
-%        Tausanovitch, Chris
-%        Warshaw, Christopher & 2014 & APSR* & Cities are responsive (taxes, expenditures, regressiveness of taxation) to citizens' conservatism/liberalism.
-Partisan elections do not make cities more or less responsive.
-& Yes \\ \hline
-%        Guillamón, Ma Dolores
-%        Bastida, Francisco
-%        Benito, Bernardino & 2013 & European Journal of Law and Economics & Police spending in Spain.
-Conservative parties spend more on police.
-Spending is higher before elections.
-Also contains a useful overview of the literature.
-& Yes \\ \hline
-%    \end{tabular}
-%    \label{}
-%\end{table}
-%\end{landscape}
-%
-%\begin{landscape}
-%    \begin{table}[htbp]
-%        %\caption{}
-%        \begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-%            \hline
-%            Names & Year & Journal & Findings & Important? \\ \hline
-%            Gerber, Elisabeth R. & 2013 & Cityscape & Partisanship of both citizens and elected city officials separately affect climate policy. & Yes \\ \hline
-%            Solé-Ollé, Albert
-%            Viladecans-Marsal, Elisabet & 2013 & Journal of Urban Economics & Spanish cities.
-The authors "employ a regression discontinuity design to document that cities controlled by left-wing parties convert much less land from rural to urban uses than is the case in similar cities con- trolled by the right".
-Partisanship might also affect housing construction and price growth.
-& Yes \\ \hline
-%            Gerber, Elisabeth R.
-%            Hopkins, Daniel J.
-& 2011 & AJPS & Regression discontinuity design.
-Democratic mayors spend less on public safety.
-All other policy areas (including taxation) are unaffected.
-& Yes \\ \hline
-%            Trounstine, Jessica & 2010 & Annual Review & Race and ethnicity in local elections (not relevant to us).
-Partisan elections have higher turnout; non-partisan elections still tend to have some partisanship in them because voters learn about party of candidates from media.
-Non-partisan elections favor Republicans/upper class.
-Mixed evidence for whether partisanship of mayor is important for policy.
-& Somewhat \\ \hline
-%            Palus, Christine Kelleher & 2010 & State and Local Government Review & Ideology (liberal/conservative) of citizen is well represented by gov.
-spending in five areas: (1) community development, housing, and conservation, (2) health and human services, (3) culture, the arts, and recreation, (4) environmental programs, and (5) transportation.
-& Somewhat \\ \hline
-%            Ferreira, Fernando
-%            Gyourko, Joseph & 2009 & The Quarterly Journal of Economics & Regression discontinuity design.
-Null results for spending and city gov.
-size with regard to mayor partisanship.
-& Yes \\ \hline
-%            Ansolabehere, Stephen
-%            Snyder, James M.
-& 2006 & Scandinavian Journal of Economics & Despite the journal, this is about the U.S.
-The important finding (for us) is the fact that counties whose government is controlled by the same party as the state government, receive more funding (county's share of state transfers, normalized by county pop.) from the state.
-& Somewhat \\ \hline
-%            Murphy, Russell D. & 2002 & Annual Review & Not useful. Too philosophical; mostly cites papers written a hundred years ago. Also exclusively about larger cities. & No \\ \hline
-%        \end{tabular}
-%        \label{}
-%    \end{table}
-%\end{landscape}
-%
-%\begin{landscape}
-%    \begin{table}[htbp]
-%        %\caption{}
-%        \begin{tabular}{|p{2cm}|c|p{3cm}|p{12cm}|l|}
-%            \hline
-%            Names & Year & Journal & Findings & Important? \\ \hline
-%            Armstrong, Cory L.
-& 2011 & Government Information Quarterly & Comparison of county and school board websites in Florida (where the two align) with regard to transparency (presence or absence of public records).
-Manual content analysis (undergrads told to look around for 15 minutes).
-School board websites, more professional websites, and websites in Republican-dominated counties are found to be more transparent.
-& Yes \\ \hline
-%            Cegarra-Navarro, Juan
-%            Pachón, José
-%            Cegarra, José & 2012 & International Journal of Information Management & Survey of Spanish municipal government officials (specifically, the city website managers).
-Respondents are asked about the features of their websites, the level of civic engagement and the size of their municipality.
-More sophisticated websites are correlated with greater civic engagement and greater use of e-government functions.
-& Yes \\ \hline
-%            Dolson, Jordan
-%            Young, Robert & 2012 & Canadian Journal of Urban Research & Determinants of website content.
-Three categories: e-content (city information on website), e-participation, social media use.
-Tables on page 15 show frequencies of these categories across sites, and might be useful to inform our topics.
-Larger cities have better websites.
-Population growth and immigration are also tested, but the findings are somewhat inconclusive.
-& Yes \\ \hline
-%            Feeney, Mary K.
-%            Brown, Adrian & 2017 & Government Information Quarterly & 500 U.S.
-city websites at two points in time (2010-2014).
-Count model of website features regarding information, e-services, utilities, transparency and civic engagement.
-Having a larger population leads to more features.
-Relying on a website contractor leads to more information and transparency.
-The authors say that mayor-councils are negatively correlated with website sophistication, but their regression tables state the opposite.
-& Yes \\ \hline
-%            Kaylor, Charles
-%            Deshazo, Randy
-%            Van Eck, David & 2001 & Government Information Quarterly & Model of best practices of e-government.
-Table 1 lists a number of possible ways this manifests, could be useful for our theory.
-& Somewhat \\ \hline
-%            Ansolabehere, Stephen
-%            Urban, Florian & 2002 & Cities & Websites of 20 major cities across the world.
-Is website content correlated with city characteristics?
-Not particularly systematic, and the findings are inconclusive.
-& Somewhat \\ \hline
-%            Jeffres, Leo W.
-%            Lin, Carolyn A.
-& 2006 & Journal of Computer-Mediated Communication & 50 largest metropolitan areas in the U.S.
-Features include information about city, opportunities for citizen feedback, galleries of photos, links, etc.
-Purely descriptive analysis, doesn't contain anything that isn't covered in any of the other aricles.
-& No \\ \hline
-%        \end{tabular}
-%        \label{}
-%    \end{table}
-%\end{landscape}
-%
-%\subsection{Informative Dirichlet model}
-%%However, \cite{Monroe2008} advise against using these types of methods in this context because they get the data generation process backwards: Our theory assumes that party leads to variation in writing, and yet we rely on the documents to predict party, in spite of the fact that we actually have perfect knowledge of it.
-%
-%For the analysis of the data, we present two approaches, the first being the informative dirichlet model developed by \citep{Monroe2008}.
-This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text.
-Table \ref{tabFightinIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them with text with greater semantic, and in our case, partisan meaning.
-%
-%In Indiana, Democrats exhibit a preference for words related to public finance, such as 'fund', 'budget', or 'tax', indicative of a greater willingness to emphasize the city's efforts to raise and spend money.
-This finding is consistent with \citep{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
-Beyond the focus on public finance, the words preferably used by Democrats do not fall into any particularly congruent categories, and largely sort into various areas related to city administration - i.e.
-`council', `services', `budget', `committee', `contract', etc.
-If there is theme around the words preferred by Republicans, it seems to center around city planning - street, fire, water, building, construction, park.
-These words suggest that the hands-off approach favored by Republicans results in a focus on supporting infrastructure and logistics.
-%
-%%Partisan top words - fightin words Indiana
-%\input{tables/fightinwordsIN.tex} %\ref{tabFightinIN}
-%
-%For Lousiana, the results (see table \ref{tabFightinLA}) are less coherent.
-Only one of the finance-related terms appears again for Democrats - specifically `fund', although `rate' might also be used in a financial context.
-Beyond that, some focus on a `historic' `'district of a city seems evident, as is the use of some words - `infrastructure', `water', `building' that were used for Republicans in Indiana.
-Conversely, Republicans are now missing these words, and their preferred terms generally do not seem to follow any particular theme.
-%
-%%Partisan top words - fightin words Louisiana
-%\input{tables/fightinwordsLA.tex} %\ref{tabFightinLA}
-%
-%The weakness of the fightin' words method is evident here, as a list of words does not necessarily provide sufficient information to glean preferred topics from.
-This is especially the case when the texts are spread across a broad number of issue-areas, with little semantic similarity.
-In \citep{Monroe2008}, the authors focus on the fairly constrained corpus of U.S.
-Senate speeches with respect to abortion - our context, by comparison, is far more eclectic.

### 2021-03-23 paper/jitp_cover_letter/jitp_cover_letter.tex
pushing JITP

\documentclass[a4paper]{letter} 
%%%% choose one of the following 4 lines to set colour and/or  date style, 
\usepackage[colour]{leedsletter} % Day, num Month year, and colour (use lp2)
%\usepackage[]{leedsletter} % Black-and-white, with US style date Month num, year
%\usepackage[myukdate]{leedsletter} 
%\usepackage[colour]{leedsletter} 
%%%% end
\department{ \vspace{-1cm} {\bf Department of Political Science}\\[38pt]
\vspace{-1.5cm}
~\\
Pennsylvania State University\\
203 Pond Lab \\
University Park, PA 16802\\ \vspace{.3cm} \\
%%%% edit the following three lines to suit you.  If you add a line, then 38pt -> 26pt above
T~~ 814.865.4598\\
F~~ 814.863.8979\\
E~~ bdesmarais@psu.edu  \\
W~~brucedesmarais.com} \vspace{-3cm}
%%%% end

\alignit{10pt} %%  tweaking parameter - probably no need to change.

%%%  need to edit  user info 
\signature{Bruce A. Desmarais Ph.D.\\[5pt] 
\rlap{DeGrandis-McCourtney Early Career Professor} \\
\rlap{Director, Graduate Programs in Social Data Analytics} \\
\rlap{Associate Director, Center for Social Data Analytics} \\ Department of Political Science\\ Institute for CyberScience}
% end personal details

% end personal details 
%%%%%%%%%%%%%%%%%%%%%% a bove this line is sender specific %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% and probably only needs edited once %%%%%%%%%%%%
%%% what follows is letter specific

% the next line is specific to this letter, and may be used for "short" letters

\skipit{1.7}  % this amount (default = 1.7) increases 2 gaps: address-date-opening 
 \vspace{-2cm}
\begin{document} 
\begin{letter}

%% if this is a ``short'' or long address, then alter \skipit above

\opening{Dear JITP Editorial Team:}
\medskip

% overview of Ted
%% He took my course, has worked as my RA, is my advisee, has R&R at PSRM

We are very excited for the opportunity to have our manuscript entitled, ``Government Websites As Data:  A methodological pipeline with application to the websites of municipalities in the United States,'' considered for publication at {\em The Journal of Information Technology \& Politics}.  We introduce a novel methodological pipeline, along with statistical software that we have developed, for automatically scraping and processing substantive text from large sets of government websites. Our contribution lies in the fact that our methodology is capable of cutting through heterogeneous file types and site organizations to extract substantively meaningful and representative blocks of plain text. We illustrate this methodology with an application to a large sample of the websites of U.S. municipal governments, and find that the textual content of websites varies systematically with the partisanship of the mayor.

We have presented our work in the form of a Workbench Note. As JITP readers and contributors are likely to engage with research problems that involve the collection of website contents, we see JITP as an ideal outlet in which to publish our research. We appreciate your consideration of our work, and welcome feedback on our manuscript.

\closing{Sincerely,}

\end{letter} 
\end{document}

### 2021-05-21 paper/archived/initial_jitp_submission/manuscript_jitp copy.tex
added memo

--- 2020-01-17 paper/archived/manuscript_ssqNote.tex
@@
 
-\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
-Our objectives and corresponding contributions in this research note are two-fold.
-First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
-Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-\vspace{.1cm} \\
-\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \vspace{.1cm} \\
-\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
-We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
-\vspace{.1cm} \\
-\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.  \vspace{-.3cm}
+A local government's website is an important source of information about policy priorities,  procedures, and debates.
+Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
+In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
+We also provide software to ease the use of this data collection method.
+In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship.
+Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
 
@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, and function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017}.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and  verall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
-The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
 For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
@@
 The partisan breakdown of city websites by state is provided in the appendix.
-This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governements \citep[e.g., ][]{marschall2013local,sumner2019}.
+This dataset of city website contents represents a contribution in the growing area of cross-municipality datasets covering local governments \citep[e.g., ][]{marschall2013local,sumner2020crowdsourcing}.
 Details on the sources and methods of raw data collection can be found in the online appendix.

### 2021-05-21 paper/jitp_rr_memo/jitp_rr_memo.tex
added memo

\documentclass[12pt,titlepage]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{graphicx}
\usepackage[capposition=top]{floatrow}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{adjustbox}
\usepackage{url}
\usepackage[section]{placeins}
\usepackage{setspace}   %Allows double spacing with the \doublespacing command
\usepackage{lscape}
\usepackage{float}
\usepackage{multirow} % table
\usepackage{dcolumn} % table
\usepackage{booktabs} % table
\usepackage{titling}
\usepackage{blindtext}
\usepackage{nameref} % ref section title!! don't ref the section title [external document]

%%%% Cross-referencing ----------------
% In your preamble

%\usepackage{xr-hyper}
% must use xr-hyper
\usepackage[colorlinks=black,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}

%\myexternaldocument{appendix}
%%%% Cross-referencing ----------------

% We expect to receive your revision by 18-May-2021. If it is not possible for you to submit your revision by this date, please contact the Editorial Office to rearrange the due date. Otherwise we may have to consider your paper as a new submission.

% HL: Just a note to share here that PRSM replication team can be pretty stringent on wanting to see the exact same number being reproduced in the replication file. I am also not sure if we want the replication team to run our models on their HPC.

\title{Revision Memo for, ``Government Websites As Data: A methodological pipeline with application to the websites of municipalities in the United States''}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

Dear Profs. Copeland, Gainous, and Towner,\\

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review. We do believe that addressing reviewers' comments has significantly improved the paper. \\

%% R1 ----------------------------------
\section*{Reviewer 1}

\begin{enumerate}

\item \emph{My main recommendation is to add some figures/plots that show the substantive findings about the differences between Democratic and Republican mayors.  You do a good job describing the findings in the text, but I think figures would also help make the findings clear to readers.  }

	\textbf{Response}:

	\item \emph{ Also, in the conclusion can you give some more examples of other research areas and questions where this approach will be useful? I think that would increase the usage and citations. Along similar lines, I hope you plan to produce step-by-step replication code and instructions about how readers can use your workflow.  I think that too will increase the usage and citations of your approach.  }

	\textbf{Response}:

\item \emph{ One minor point -- there's a typo in the abstract -- "can can" }

\textbf{Response}:

\end{enumerate}

%% R2 -------------------
\section*{Reviewer 2}

\begin{enumerate}

\item \emph{  Research question & objective: From the title, it seems that the main objective of this study is to develop a new methodology that aid in collecting and analyzing data from government websites and examining the association between website content and mayoral partisanship is a way to validate. However, the author(s) did not develop the discussion about the challenges and issues that they found in the existing methodology after indicating the problem statement in the Introduction as “The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset (p. 1, line 42-44).” This leaves me confused about the objective and the research question of this study. While the objective is to develop a new methodology, the research question is to examine the mayoral partisanship in the website contents? The author(s) should address this gap by clearly explaining the differences in a set of research objectives throughout the manuscript.}

    \textbf{Response}:

\item \emph{ Locating within the existing literature: While the main objective of this study is to develop a new methodology, it lacked discussion of the existing methodologies. Instead, the author(s) discussed the current literature about the partisanship and government website contents in section 2 and then jumped right into the method part in sections 3-5. Without locating the objective of the study in the existing literature, the conclusion is a mere summary of this study and it did not develop into a deeper discussion of theoretical and practical implications of this study.}

    \textbf{Response}:

\item \emph{The abstract is not well framed to effectively introduce the goal and the question of this study. The last sentence is particularly confusing to grasp the main contribution of this study.}

     \textbf{Response}:

\item \emph{The last paragraph that explains the structure of this study is clear, which should be used as the reference to organize the overall narratives of the manuscript.}

     \textbf{Response}:

\item \emph{ While it is essential to provide the background of the association between government website content and mayoral partisanship, it did not well developed. As the findings are related to the types of contents of government websites depending on mayors’ partisanship, while it explained the ways government websites are used to reflect policy priorities, it lacked the discussion of the overall political objectives of each party. }\\

    \textbf{Response}:

    \item \emph{As this paper’s contribution is mainly methodological, there should be a separate, in-depth discussion of the problems and limitations in the existing methodologies. This discussion is more important than the reflection of partisanship on government website contents because it explains the need for a new methodology, supporting the contribution of this study.}\\

    \textbf{Response}:

        \item \emph{The conclusion should be improved by adding its theoretical and practical implications by aligning with the limitations of the existing studies that you should discuss earlier (see my comment \#6.)}\\

    \textbf{Response}:

            \item \emph{The author(s) should check typos after revising}\\

    \textbf{Response}:

     \item \emph{Abstract: “… from large samples of government websites can can compliment … (p. 1, line 22).”}\\

    \textbf{Response}:

    \item \emph{Section 2: “… mobile accessibility, and verall function… (p. 3, line 42)”}\\

    \textbf{Response}:

\end{enumerate}

\newpage
\singlespacing
%\bibliographystyle{apsr}
% \bibliography{spatialPredict.bib}

\end{document}

### 2021-05-21 paper/manuscript_jitp_OA_rr.tex
added memo

--- 2020-01-17 paper/archived/manuscript_ssqNote_OA copy.tex
@@
 
-\noindent {\bf Objective:} Existing social science research that uses government website content has relied on manual methods of content collection, limiting the scale and scope of projects.
-Our objectives and corresponding contributions in this research note are two-fold.
-First, we develop a methodological pipeline to gather, process, and analyze website content, along with an R package implementation of the pipeline.
-Second, we illustrate the pipeline through the collection and analysis of the websites of over two hundred municipal governments in the United States.
-\\~\\
-\noindent {\bf Methods:} We propose and utilize a pipeline consisting of tools for web-scraping, text parsing and cleaning, and text analysis.  \\~\\
-\noindent {\bf Results:} Our pipeline is effective in extracting large-scale meaningful substantive text from government websites.
-We identify a strong relationship between the topical content on municipal websites and the partisanship of the mayor.
-\\~\\
-\noindent {\bf Conclusion:}  The pipeline we develop, associated software, and dataset of municipal websites, represent valuable research tools for social scientists.
+A local government's website is an important source of information about policy priorities,  procedures, and debates.
+Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
+In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
+We also provide software to ease the use of this data collection method.
+In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship.
+Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
 

### 2021-05-21 paper/manuscript_jitp_rr.tex
added memo

--- 2021-05-21 paper/archived/initial_jitp_submission/manuscript_jitp copy.tex
@@
 First, we present a set of tools that can be effectively used in combination to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT).
-Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.\footnote{It is useful to note a couple of features that we do not intend to provide with this pipeline.
-First, this is not intended to be a pipeline for scraping and analyzing any and all websites.
-Our focus is on government websites, as we assume that the contents are in the public domain, and not subject to limitations on the application of scraping technology.
-Second, though such extensions would be valuable, we do not address the collection and analysis of image, video, sound, and  tabular data from government websites.} Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
+Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.
+Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
 By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset.
@@
 A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime.
-On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{Brown2017}.
+On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{brown2017different}.
 On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on law enforcement, even after controlling for crime \citep{Einstein2015}.

### 2021-05-21 paper/jitp_rr_memo/jitp_rr_memo.tex
added proportion difference figures and discussion

@@
 
-	\textbf{Response}:
+	\textbf{Response}: We thank the reviewer for this recommendation.
+We recognize that the STM results presented in Table 2 conveyed the content, direction of partisan bias, and statistical significance, but did not convey magnitude of differences/effects in any meaningful way.
+We have added Figure 3, in which we illustrate the magnitudes of the differences between the prevalence of topics based on the mayor's partisanship.
+We also added discussion of the differences illustrated in this figure.
+We see this as a major enhancement of our results interpretation.
 

### 2021-05-21 paper/manuscript_jitp_rr.tex
added proportion difference figures and discussion

@@
 
+We further interpret the STM results using the visualizations we present in Figure \ref{demreptop}.
+In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics.
+We illustrate the topics that are discussed above.
+Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities.
+This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM.
+Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities.
+This represents 40\% of the average proportion of content allocated to a given topic.
+To recap these results, the differences in content we find are meaningful both in terms of topics and the sizes of differences based on the partisanship of the city's mayor.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.725]{figures/Democratic_topics}\\
+\includegraphics[scale=0.725]{figures/Republican_topics} \vspace{-.65cm}
+\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites.
+Depicting topics highlighted in discussion.
+Top plot gives more Democratic topics, and bottom gives more Republican topics.} \vspace{-.3cm}
+\label{fig:demreptop}
+\end{figure}
+
 %Interestingly enough, Democrats also `own' the topic related to law enforcement, which might be somewhat unexpected given Republicans' usual focus on law and order \citep{gerber2011mayors}.

### 2021-05-24 paper/jitp_rr_memo/jitp_rr_memo.tex
adding note of the tutorial

@@
 
-	\item \emph{ Also, in the conclusion can you give some more examples of other research areas and questions where this approach will be useful?
-I think that would increase the usage and citations.
-Along similar lines, I hope you plan to produce step-by-step replication code and instructions about how readers can use your workflow.
+	\item \emph{ Also, in the conclusion can you give some more examples of other research areas and questions where this approach will be useful? I think that would increase the usage and citations.  }
+
+	\textbf{Response}:
+
+	\item \emph{ Along similar lines, I hope you plan to produce step-by-step replication code and instructions about how readers can use your workflow.
 I think that too will increase the usage and citations of your approach.
@@
 
-	\textbf{Response}:
+	\textbf{Response}: We will make three categories of online materials available to help readers/users effectively apply the methods workflow we develop.
+First, we will post a conventional replication archive to Dataverse.
+The replication archive will include all of our code and data.
+Second, the \texttt{gov2text} package is available on GitHub.
+Third, we have posted an interactive tutorial on Google Colab that demonstrates the key steps in the application of our pipeline using the \texttt{gov2text} package.
 
@@
 
-\textbf{Response}:
+\textbf{Response}: Fixed.
 

### 2021-05-24 paper/manuscript_jitp_rr.tex
adding note of the tutorial

@@
 Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
-In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.
+In this research note, we propose that the automated collection of website content from large samples of government websites can compliment more targeted manual methods, and offer contributions through comparative analyses.
 We also provide software to ease the use of this data collection method.
@@
 The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.
+The package is hosted on GitHub at ({\em blinded for anonymity}).
+We have also created an interactive tutorial, hosted on Google Colab \citep{bisong2019google}, in which we illustrate the use of \texttt{gov2text}.
 

### 2021-05-24 paper/jitp_rr_memo/jitp_rr_memo.tex
finished addressing points from R1

@@
 
-	\textbf{Response}:
+	\textbf{Response}: We have added a paragraph to the conclusion in which we recap the uses of website content analysis that we reviewed in the front end of the paper, and also note and cite potential applications outside of the analysis of government websites and candidates.
+We give examples of politics and policy research in which researchers have analyzed (1) company websites, and (2) the websites of interest groups.
 

### 2021-05-24 paper/manuscript_jitp_rr.tex
finished addressing points from R1

@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and  verall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
@@
 
+Above we reviewed several research projects that involved the analysis of government websites \citep{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}, and those of politicians or candidates in elections  \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+Our pipeline would be applicable to projects such as these.
+However, the application of the methods we propose is not limited to government and politician websites.
+Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites.
+For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.
+\citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.
+There is a broad body of research programs that could make use of the data collection and processing pipeline we present.
+
 The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.

### 2021-05-25 paper/jitp_rr_memo/jitp_rr_memo.tex
addressed most of R2's comments

@@
 
-    \textbf{Response}:
+    \textbf{Response}:  In the initial draft we did too little to walk the reader through the challenges posed by manual collection of website data, and also did not clearly describe the organization and relationships between our primary and secondary research objectives.
+We have substantially revised the front end of the paper to further justify and clarify our research objectives.
+To better situate our contribution in the existing literature and methodology, we discuss an example of the manual data collection process used in a recent study in which manual data collection was used to gather data on the contents of the websites of U.S.
+municipalities.
+This example anchors our discussion of the cost and scale limitations associated with manual data collection.
 
@@
 
-    \textbf{Response}:
+    \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods.
+We have also revised the conclusion to point specifically to the implications of our contributions.
+In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.
 
@@
 
-     \textbf{Response}:
+     \textbf{Response}:  We revised the abstract to more effectively present and justify our main objective of introducing a methodological pipeline for extracting content from government website.
+We also contextualized discussion of the application by noting that it serves to illustrate and validate the methodological contribution.
 
@@
 
-     \textbf{Response}:
+     \textbf{Response}: We unpacked and expanded upon this paragraph in the revised presentation of our research objectives and approach.
 
@@
 
-    \textbf{Response}:
+    \textbf{Response}:  We have revised the conclusion in accordance with this comment (as well as earlier comments from R2 and R1).
 
-            \item \emph{The author(s) should check typos after revising}\\
+            \item \emph{The author(s) should check typos after revising.
+Abstract: “… from large samples of government websites can can compliment … (p.
+1, line 22).” Section 2: “… mobile accessibility, and verall function… (p.
+3, line 42)”}\\
 
-    \textbf{Response}:
-
-     \item \emph{Abstract: “… from large samples of government websites can can compliment … (p. 1, line 22).”}\\
-
-    \textbf{Response}:
-
-    \item \emph{Section 2: “… mobile accessibility, and verall function… (p. 3, line 42)”}\\
-
-    \textbf{Response}:
+    \textbf{Response}: We
 

### 2021-05-25 paper/manuscript_jitp_rr.tex
addressed most of R2's comments

@@
 
-A local government's website is an important source of information about policy priorities,  procedures, and debates.
-Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis.
-In this research note, we propose that the automated collection of website content from large samples of government websites can compliment more targeted manual methods, and offer contributions through comparative analyses.
+The content of a government's website is an important source of information about policy priorities,  procedures, and services.
+Existing research on government websites has relied on manual methods of website content collection and processing, which imposes cost limitations on the scale of website data collection.
+In this research note, we propose that the automated collection of website content from large samples of government websites can offer relief from the costs of manual collection, and enable contributions through large-scale comparative analyses.
 We also provide software to ease the use of this data collection method.
-In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship.
-Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
+In an illustrative application, we collect textual content from the websites of over two hundred municipal governments in the United States, and study how website content is associated with mayoral partisanship.
+Using statistical topic modeling, we find that the partisanship of the mayor predicts differences in the contents of city websites that align with differences in the platforms of Democrats and Republicans.
+The application validates the utility of website content data extracted via our methodological pipeline.
 
@@
 We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
-We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
+We provide an illustrative application in which we explore how the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
 
-Our research objectives and corresponding contributions are two-fold.
-First, we present a set of tools that can be effectively used in combination to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT).
+The manual content analysis of government websites is feasible when researchers have access to substantial resources and/or focus their data collection efforts on a small sample of websites.
+Consider the example of \citet{Feeney2017}.
+They analyzed the websites of 500 U.S.
+municipalities, and recorded information about the sites' coverage of, e.g., the city's social media accounts, the city council agenda, department descriptions, and police reports.
+To do this, \citet{Feeney2017}, employed two researchers to hand-code each of the 500 websites.
+If each researcher could complete 5--10 websites per hour, between hours spent on training and data collection, the budget to complete such a project would need to be on the order of thousands of dollars.
+
+Our primary research objective is to introduce a methodological pipeline for government website content extraction that will enable researchers to analyze government website content without incurring the substantial costs associated with manual data collection.
+Since it is possible to use computer-automated methods to (1) access websites, (2) parse content, and (3) analyze and categorize content, we propose that automated methods can be combined to dramatically lower the cost and increase the scale of projects involving the analysis of government website content.
+The approach that we propose is a methodological pipeline that can ingest a set of urls that point to government website, and output a corpus of plain text that is extracted from the files available at each URL.
+The pipeline that we introduce can be used to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT).
 Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.
-Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
+
+Our secondary objective is to illustrate the application and use of our pipeline through a study of the relationship between the political party of a (U.S.) city's mayor, and the textual contents of the city's website.
+We gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States.
 By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset.
-In summary, our contributions offer scholars of government a roadmap for collecting, and an example of, large scale textual data extracted from government websites.
 
@@
 We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline.
-This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis.
+The key implication of our results is that the methodology we introduce holds the potential to vastly scale up, and lower the cost of, the data collection efforts underpinning the growing body of research that is focused on government website analysis.
 Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
@@
 
-Above we reviewed several research projects that involved the analysis of government websites \citep{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}, and those of politicians or candidates in elections  \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+Above we referenced several research projects that involved the analysis of government websites, and those of politicians or candidates in elections.
 Our pipeline would be applicable to projects such as these.

### 2021-05-26 paper/jitp_rr_memo/jitp_rr_memo.tex
finished revisions (round 1)

@@
 We do believe that addressing reviewers' comments has significantly improved the paper.
+We should note that we are approximately 450 words over the 5,000 limit for Workbench Notes.
+We thoroughly trimmed the text to make room for the revisions requested by the reviewers, but would be happy to cut or move additional content to the online appendix if we need to be under the 5,000 limit.
 \\
@@
 
-    \textbf{Response}:
+    \textbf{Response}: We now recognize that our initial submission jumped right into the estimation and interpretation of differences based on mayoral partisanship, without first discussing why we would expect the priorities of mayors to differ according to party.
+We added discussion of findings from two recent articles that address how Republican and Democratic mayors differ in terms of policy priorities.
 
@@
 
-    \textbf{Response}:
+    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection address this point.
+See also our responses to R2's comments 1--3.
 
@@
 
-    \textbf{Response}: We
+    \textbf{Response}: We have closely proof read the revised manuscript.
 

### 2021-05-26 paper/manuscript_jitp_rr.tex
finished revisions (round 1)

@@
 Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation.
-The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
+A substantial body of research has focused on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}.
 The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset.
-Though accurate, the manual approach to data collection is costly for large-scale analysis.
-We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt.
-We provide an illustrative application in which we explore how the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.
-
-The manual content analysis of government websites is feasible when researchers have access to substantial resources and/or focus their data collection efforts on a small sample of websites.
+The manual content analysis of government websites is only feasible when researchers have access to substantial resources or focus on a small sample of websites.
 Consider the example of \citet{Feeney2017}.
 They analyzed the websites of 500 U.S.
-municipalities, and recorded information about the sites' coverage of, e.g., the city's social media accounts, the city council agenda, department descriptions, and police reports.
-To do this, \citet{Feeney2017}, employed two researchers to hand-code each of the 500 websites.
+municipalities, and recorded information about the sites' coverage of, e.g., the city's social media accounts, council agenda, department descriptions, and police reports.
+They employed two researchers to code each of the 500 websites.
 If each researcher could complete 5--10 websites per hour, between hours spent on training and data collection, the budget to complete such a project would need to be on the order of thousands of dollars.
 
-Our primary research objective is to introduce a methodological pipeline for government website content extraction that will enable researchers to analyze government website content without incurring the substantial costs associated with manual data collection.
+Our primary research objective is to introduce a methodological pipeline that will enable researchers to gather and analyze government website content without incurring the substantial costs associated with manual data collection.
 Since it is possible to use computer-automated methods to (1) access websites, (2) parse content, and (3) analyze and categorize content, we propose that automated methods can be combined to dramatically lower the cost and increase the scale of projects involving the analysis of government website content.
-The approach that we propose is a methodological pipeline that can ingest a set of urls that point to government website, and output a corpus of plain text that is extracted from the files available at each URL.
-The pipeline that we introduce can be used to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT).
-Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.
+Our pipeline ingests a set of urls that point to government websites, and outputs a corpus of plain text that is extracted from the files, of all types (e.g., HTML, DOC, PDF, and TXT) available at each URL.
 
@@
 The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
-The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
+The websites of politicians and their parties have also been the object of research \citep{Druckman2009,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
 For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
@@
 The first step is aimed at extracting clean plain text from this heterogeneous file base.
-The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments.
+The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is substantively uninformative.
 Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways.
-We make a software recommendation for each of these steps and gather most of them our R package, \texttt{gov2text}.
-All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem.
-As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community.
+We make a software recommendation for each of these steps and gather most of them in our R package, \texttt{gov2text}.
 Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling.
@@
 \subsubsection{File Type Detection}
-The format of a file has a major impact on whether and how textual data can be extracted from a document.
-For the most part, the file type of a document can be correctly determined through the filename ending---its extension.
+The format of a file impacts how textual data can be extracted from a document.
+For the most part, the file type of a document can be correctly determined its extension.
 However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text.
 For example, we found thousands of documents that ended in .html, when they were actually PDFs.
-A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification.
-We implement this method using the R package \texttt{wand} \citep{wand}.\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}
+A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type.
+We implement this method using the R package \texttt{wand} \citep{wand}.%\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}
 
 \subsubsection{Extracting Text from HTML}
-The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate.
+The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other ``boilerplate''.
 The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites.
@@
 \caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site.
-Bottom image provides the result of running \url{https://garyin.us/} through the \texttt{boilerpipe} algorithm at \url{https://boilerpipe-web.appspot.com/}.}
+Bottom image provides the result of running \url{https://garyin.us/} through \texttt{boilerpipe}.}
 \label{fig:garysbs}
@@
 
-A subfield of the information retrieval literature, dealing with boilerplate extraction, can offer a solution to this problem.
-The goal of this branch of research is to develop algorithms with the ability to estimate whether a given portion of an HTML file is substantive.
-To this end, structural features, such as HTML tags (which are not sufficiently informative on their own), text statistics such as word and sentence length, as well as other heuristics are used.
-We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
-The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in the social sciences.
+To remove text that does not represent substantive content we rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}.
+The \texttt{boilerpipe} algorithm has been widely used in the natural language processing literature, but to our knowledge has not been previously used in the social sciences.
 The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}.
-We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data.
-We show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
+We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we show that without using \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text.
 }
@@
 \subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
-The extraction of information from other text-based file formats is more straightforward.\footnote{See \cite{Berg2012} for a discussion of why extracting text from PDFs is nevertheless nontrivial.} To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix.
+The extraction of information from other text-based file formats is more straightforward.
+To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.} The breakdown of all files by type is given in the online appendix.
 The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text.
@@
 \subsection{Preprocessing}
-Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}.
-As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model.
-The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing.
-The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites.
-Some of it is substantively informative and some of it is completely irrelevant.
-As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents.
-The same is true for streets, locations and not least of all, the city itself.
+Preprocessing is an important part of text-as-data research \citep{denny2018text}.
+Our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model.
+The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable, yet substantively irrelevant, differences between websites.
+For example, names of city officials, streets, and the city itself feature frequently in city documents.
 Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city.
-Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.
 
@@
 
-To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER).
-In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended.
-Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
+To process the text we extract, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER) to remove most names.\footnote{We retain laws, nationalities or religious or political groups, and works of art.} For applications where the names of political actors might be of interest, this step is not recommended.
+Furthermore, we select words on the basis of their POS-tags, retaining only nouns, verbs, and adjectives.
+We keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name.
 Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word.
 } POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}.
-To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).
-A final and crucial step is the removal of duplicate documents, which occur very frequently on websites.
-In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
+To deal with any leftover issues, we remove words with less than three characters, stopwords and non-English words (using the R package \texttt{Hunspell}).
+We also remove duplicate documents, which occur very frequently on websites.
+%In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion.
 %The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars.
@@
 The package is hosted on GitHub at ({\em blinded for anonymity}).
-We have also created an interactive tutorial, hosted on Google Colab \citep{bisong2019google}, in which we illustrate the use of \texttt{gov2text}.
+We have also created an interactive tutorial for texttt{gov2text} hosted on Google Colab \citep{bisong2019google}.
 
@@
 \end{table}
+
+The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
+By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
+We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
+We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
+This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.
 
@@
 
+The policy priorities of U.S.
+mayors are shaped in large part by their partisan affiliations.
+For example, \citet{einstein2018mayors} finds that Democratic mayors are much more likely than Republicans to support municipal-level redistributive policies, and \citet{einstein2021pictures} finds that Democratic mayors are more likely to support city-level policies aimed at addressing racial inequality.
 City mayors use government websites to present their policy priorities to the public.
 Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis.
-Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with the Front Porch Alliance---a faith-based initiative to create partnerships with religious organizations for the use and administration of city resources.
+Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with a faith-based initiative to create administrative partnerships with religious organizations.
 Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}.
-When Democrat Bart Peterson took office in 2000, the material related to the Front Porch Alliance was removed from the website.
-We consider whether the partisan manipulation of city website contents documented in this example holds in a large-scale and more recent sample of city websites.
-We illustrate the analysis of municipal website content by studying the ways in which differences in website content correlate with the partisanship of the city's mayor mayor.
+When Democrat Bart Peterson took office in 2000, the material related to the faith-based initiative was removed from the website.
+
+We illustrate the analysis of municipal website content by studying how differences in website content correlate with the partisanship of the city's mayor.
 As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance.
@@
 These constraints do not apply to website contents.
-City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.
+City governments have great discretion in composing their websites, modifying website content is low cost.
 
@@
 The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics.
-For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic.
 For our primary empirical investigation, the STM provides a tool to estimate the relationship between the party of the city's mayor and the prevalence of each topic.
@@
 Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), Topic {\bf 45} ('asset', 'actuarial', 'liability', 'financial'), Topic \textbf{35} ('bond', 'obligation', 'proceeds') as well as Topic \textbf{55} ('taxable', 'deed', 'value').
-We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}).
+We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater emphasis on the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}).
 This finding is consistent with \cite{Einstein2015}, who show that Democratic mayors tend to favor greater spending.
@@
 These basic service topics cannot be found among topics prevalent in cities with Democratic mayors.
-Similarly, zoning issues figure prominently in the set of republican topic (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules.
+Similarly, zoning issues figure prominently in the set of Republican topics (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules.
 The Democratic topics also include one that is somewhat focused on zoning, Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.
@@
 This represents 40\% of the average proportion of content allocated to a given topic.
-To recap these results, the differences in content we find are meaningful both in terms of topics and the sizes of differences based on the partisanship of the city's mayor.
 
@@
 \includegraphics[scale=0.725]{figures/Republican_topics} \vspace{-.65cm}
-\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites.
-Depicting topics highlighted in discussion.
-Top plot gives more Democratic topics, and bottom gives more Republican topics.} \vspace{-.3cm}
+\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites. Depicting topics highlighted in discussion. } \vspace{-.3cm}
 \label{fig:demreptop}
@@
 We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
-We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline.
-The key implication of our results is that the methodology we introduce holds the potential to vastly scale up, and lower the cost of, the data collection efforts underpinning the growing body of research that is focused on government website analysis.
-Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government.
-We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
+The key implication of our results is that researchers can use the methods we introduce scale up, and lower the cost of, data collection for projects focused on the comparative analysis of website content.
+Through an application to the analysis of municipal websites in six different state, we find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
 
-Above we referenced several research projects that involved the analysis of government websites, and those of politicians or candidates in elections.
-Our pipeline would be applicable to projects such as these.
+We have highlighted projects focused on government and politician websites.
 However, the application of the methods we propose is not limited to government and politician websites.
@@
 There is a broad body of research programs that could make use of the data collection and processing pipeline we present.
-
-The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
-By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
-For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website.
-We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site.
-This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.}
 

### 2021-05-27 paper/manuscript_jitp_rr.tex
fixed some typos

@@
 The package is hosted on GitHub at ({\em blinded for anonymity}).
-We have also created an interactive tutorial for texttt{gov2text} hosted on Google Colab \citep{bisong2019google}.
+We have also created an interactive tutorial for \texttt{gov2text} hosted on Google Colab \citep{bisong2019google}.
 
@@
 City mayors use government websites to present their policy priorities to the public.
-Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis.
+Consider an example; \citet[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis.
 Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with a faith-based initiative to create administrative partnerships with religious organizations.
@@
 These constraints do not apply to website contents.
-City governments have great discretion in composing their websites, modifying website content is low cost.
+City governments have great discretion in composing their websites, and modifying website content is low cost.
 
@@
 
-We further interpret the STM results using the visualizations we present in Figure \ref{demreptop}.
+We further interpret the STM results using the visualizations we present in Figure \ref{fig:demreptop}.
 In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics.
@@
 We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis.
-The key implication of our results is that researchers can use the methods we introduce scale up, and lower the cost of, data collection for projects focused on the comparative analysis of website content.
-Through an application to the analysis of municipal websites in six different state, we find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
+The key implication of our results is that researchers can use the methods we introduce to scale up, and lower the cost of, data collection for projects focused on the comparative analysis of website content.
+Through an application to the analysis of municipal websites in six different states, we find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
 

### 2021-05-27 paper/manuscript_jitp_rr.tex
decreased the negative vspace at the end of table 1 so it doesn't overlap with the text
added updated figure to the paper

@@
     \end{tabular}
-    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.}  \vspace{-.9cm}
+    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.}  \vspace{-.5cm}
 \end{table}
@@
 \centering
-\includegraphics[scale=0.725]{figures/Democratic_topics}\\
-\includegraphics[scale=0.725]{figures/Republican_topics} \vspace{-.65cm}
-\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites. Depicting topics highlighted in discussion. } \vspace{-.3cm}
+\includegraphics[scale=0.725]{figures/Democratic_Republican_topics}
+\caption{Topic differences in proportion to prevalence between Democrat and Republican mayor city websites.
+Depicting topics highlighted in discussion.
+Manually assigned labels are in black, top words for each topic as determined by the STM are in gray.} \vspace{-.3cm}
 \label{fig:demreptop}

### 2021-06-01 paper/jitp_rr_memo/jitp_rr_memo.tex
upadted memo
revised memo to address data scope

@@
 We do believe that addressing reviewers' comments has significantly improved the paper.
-We should note that we are approximately 450 words over the 5,000 limit for Workbench Notes.
-We thoroughly trimmed the text to make room for the revisions requested by the reviewers, but would be happy to cut or move additional content to the online appendix if we need to be under the 5,000 limit.
 \\
@@
 First, we will post a conventional replication archive to Dataverse.
-The replication archive will include all of our code and data.
+The replication archive will include all of the code necessary to replicate the text analysis results we present, as well as the raw text corpora that we extracted from the websites.
 Second, the \texttt{gov2text} package is available on GitHub.

### 2021-06-01 paper/manuscript_jitp_rr.tex
revised memo to address data scope

@@
 \vspace{-.2cm}
-\section{The Web to Text Pipeline} \vspace{-.2cm}
+\section{The Web-to-Text Pipeline} \vspace{-.2cm}
 In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents.

### 2021-06-03 paper/jitp_rr_memo/jitp_rr_memo.tex
added the discussion of the downsides of the manual approach reviewer 2 asked for

@@
     \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods.
-We have also revised the conclusion to point specifically to the implications of our contributions.
+We have also added a discussion of the manual content analysis and its downsides in the e-government literature (as well as a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues) to the end of the literature section.
+Finally, we revised the conclusion to point specifically to the implications of our contributions.
 In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.
@@
 
-    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection address this point.
+    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection at the end of the literature section address this point.
 See also our responses to R2's comments 1--3.

### 2021-06-03 paper/manuscript_jitp_rr.tex
added the discussion of the downsides of the manual approach reviewer 2 asked for

@@
 
-The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents.
+%This used to say 'The existing research that uses scraped websites', but most of these were actually based on hand-coding
+%I also changed the end of the sentence (which was 'an indication of the theoretical value of empirical analysis of web contents') to make it more focused on what R2 wanted
+
+Existing research that analyzes websites \textit{manually} provides an indication of the potential benefits of automated analysis of web contents.
 Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
 As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
-The websites of politicians and their parties have also been the object of research \citep{Druckman2009,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}.
-For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
+Papers in the e-government literature differ in terms of specific instruments, indices, and items, but they largely follow the same principle: researchers manually visit each website and record whether a feature is present or not \citep{kaylor2001gauging, Urban2002, jeffres2006metropolitan, Armstrong2011, dolson2012explaining, Feeney2017}\footnote{Another literature following a similar approach concerns the websites of politicians and their parties.
+By and large, researchers in this field also rely on hand-coding \citep{Norris2003,Druckman2009,Druckman2010,Esterling2011}, albeit with some exceptions, who do use targeted scrapers \citep{Therriault2010,cryer2019navigating}.}.
+This approach is also used by the Rutgers E-Governance Institute, whose survey instrument has influenced the e-government literature at large.
+\cite{holzer2016digital} have conducted seven studies, between 2003 and 2016, of the largest city's website in each of the world's 100 nations with the most internet users.
+In each case, evaluators visit each website and manually score it according to 104 items.
+However, this level of thoroughness comes at a price - \cite{holzer2016digital} name a total of 127 website evaluators in their list of acknowledgements.
+
+This approach is labor-intensive and therefore expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems.
+Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within the narrow confines of their pre-defined objectives.
+Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}.
+In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial resources might struggle to provide a complete understanding of individual websites.
+Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
+By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
+
+%For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
 Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.
+%removed this sentence for now, but could put it back in the footnote
 

### 2021-06-03 paper/jitp_rr_memo/jitp_rr_memo.tex
finished incorporating additional revisions

@@
 Each of the comments from reviewers is addressed in the order presented in the review.
+We should note that we are now approximately 300 words over the 5,000 word limit.
+We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers.
+Of course, we are happy to trim further if necessary.
 We do believe that addressing reviewers' comments has significantly improved the paper.
@@
 
-    \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods.
-We have also added a discussion of the manual content analysis and its downsides in the e-government literature (as well as a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues) to the end of the literature section.
+    \textbf{Response}: We agree with this critique of our literature discussion, and we have completely revised Section 2 to focus primarily on the methods that have been applied to collecting data from government websites, and to specifically focus on the challenges posed by manual data collection.
+We also incorporated a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues.
+The discussion of mayoral partisanship and government websites has now been shifted down to the point at which we introduce our application.
 Finally, we revised the conclusion to point specifically to the implications of our contributions.

### 2021-06-03 paper/manuscript_jitp_rr.tex
finished incorporating additional revisions

@@
 \vspace{-.2cm}
-\section{Politics and Government Website Content} \vspace{-.2cm}
+\section{The study of Government Website Content} \vspace{-.2cm}
+
+%Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
+In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
+%Furthermore, the use of a local government website is associated with an individual's perspective on government.
+\citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
+Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
+
+%This used to say 'The existing research that uses scraped websites', but most of these were actually based on hand-coding
+%I also changed the end of the sentence (which was 'an indication of the theoretical value of empirical analysis of web contents') to make it more focused on what R2 wanted
+
+Existing research that analyzes government websites \textit{manually} provides an indication of the potential benefits of automated analysis of web contents.
+Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
+As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
+In most research on website content, researchers manually visit each website and record whether a feature is present or not \citep{kaylor2001gauging, Urban2002, jeffres2006metropolitan, Armstrong2011, dolson2012explaining, Feeney2017}\footnote{A related literature concerns the websites of politicians and their parties.
+By and large, researchers in this field also rely on hand-coding \citep{Norris2003,Druckman2009,Druckman2010,Esterling2011}, albeit with some exceptions, who do use targeted scrapers \citep{Therriault2010,cryer2019navigating}.}.
+This approach is also used by the Rutgers E-Governance Institute, whose survey instrument has influenced the e-government literature at large.
+\cite{holzer2016digital} have conducted seven studies, between 2003 and 2016, of the largest city's website in each of the world's 100 nations with the most internet users.
+In each case, evaluators visit each website and manually score it according to 104 items.
+However, this level of thoroughness comes at a price---\cite{holzer2016digital} name a total of 127 website evaluators in their list of acknowledgements.
+
+The manual approach is expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems.
+Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within their pre-defined objectives.
+Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}.
+In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites.
+Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
+By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
+
+%For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
+Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.
+%removed this sentence for now, but could put it back in the footnote
+
+%Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
+\cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
+%In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
+We then define a pipeline for data collection and analysis that includes methods to access government website URLs, scrape their raw contents from the World Wide Web, gather plain text from the website files, and identify boilerplate text within the plain text contents.
+Lastly, we illustrate the analysis of municipal government website text by exploring the relationship between the city mayors' party affiliations and the topical contents of the websites.
+
+\vspace{-.2cm}
+
+\section{Application: Mayoral Partisanship and \\ U.S. Municipal Government Website Text} \vspace{-.2cm}
 
@@
 \end{figure}
-
-%Members of the public visit municipal government websites for a wide variety of purposes \citep{sandoval2012government}, and with significant regularity.
-In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}.
-%Furthermore, the use of a local government website is associated with an individual's perspective on government.
-\citet{tolbert2006effects} find that users of local government websites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments.
-Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.
-
-%This used to say 'The existing research that uses scraped websites', but most of these were actually based on hand-coding
-%I also changed the end of the sentence (which was 'an indication of the theoretical value of empirical analysis of web contents') to make it more focused on what R2 wanted
-
-Existing research that analyzes websites \textit{manually} provides an indication of the potential benefits of automated analysis of web contents.
-Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}.
-As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities.
-Papers in the e-government literature differ in terms of specific instruments, indices, and items, but they largely follow the same principle: researchers manually visit each website and record whether a feature is present or not \citep{kaylor2001gauging, Urban2002, jeffres2006metropolitan, Armstrong2011, dolson2012explaining, Feeney2017}\footnote{Another literature following a similar approach concerns the websites of politicians and their parties.
-By and large, researchers in this field also rely on hand-coding \citep{Norris2003,Druckman2009,Druckman2010,Esterling2011}, albeit with some exceptions, who do use targeted scrapers \citep{Therriault2010,cryer2019navigating}.}.
-This approach is also used by the Rutgers E-Governance Institute, whose survey instrument has influenced the e-government literature at large.
-\cite{holzer2016digital} have conducted seven studies, between 2003 and 2016, of the largest city's website in each of the world's 100 nations with the most internet users.
-In each case, evaluators visit each website and manually score it according to 104 items.
-However, this level of thoroughness comes at a price - \cite{holzer2016digital} name a total of 127 website evaluators in their list of acknowledgements.
-
-This approach is labor-intensive and therefore expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems.
-Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within the narrow confines of their pre-defined objectives.
-Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}.
-In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial resources might struggle to provide a complete understanding of individual websites.
-Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
-By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
-
-%For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S.
-Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.
-%removed this sentence for now, but could put it back in the footnote
-
-%Important to our methodological objectives, research analyzing and improving the scraping, pre-processing and text analysis pipeline that is applicable to government websites is still in its infancy.
-\cite{Eschenfelder2002} provide something of an overview of how federal websites should be assessed from an e-governance point of view, but they largely focus on the substantive criteria that should be fulfilled, rather than the technical aspects of website acquisition and analysis.
-%In what follows we first define the target dataset---the textual contents of websites of United States municipalities, along with associated metadata on the municipalities and their governments.
-We then define a pipeline for data collection and analysis that includes methods to access government website URLs, scrape their raw contents from the World Wide Web, gather plain text from the website files, and identify boilerplate text within the plain text contents.
-Lastly, we illustrate the analysis of municipal government website text by exploring the relationship between the city mayors' party affiliations and the topical contents of the websites.
-
-\vspace{-.2cm}
-
-\section{Data: US Municipal Government Website Text} \vspace{-.2cm}
 
@@
 First, though they contain significant amounts of text, websites are not comprised of clean plain text files.
-Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files.
 The first step is aimed at extracting clean plain text from this heterogeneous file base.
@@
 \subsubsection{File Type Detection}
-The format of a file impacts how textual data can be extracted from a document.
-For the most part, the file type of a document can be correctly determined its extension.
-However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text.
+The format of a file impacts how text can be extracted from a document.
+For the most part, the file type of a document can be correctly determined by its extension.
+However, there are exceptions to this.
 For example, we found thousands of documents that ended in .html, when they were actually PDFs.
@@
 
-The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files.
+The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather website files.
 By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript.
@@
 
-We further interpret the STM results using the visualizations we present in Figure \ref{fig:demreptop}.
-In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics.
+In Figure \ref{fig:demreptop} we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics.
 We illustrate the topics that are discussed above.

### 2021-06-04 paper/jitp_rr_memo/jitp_rr_memo.tex
made a change to the reviewer memo to reflect the literature section being split in two

@@
 
-    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection at the end of the literature section address this point.
+    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection in Section 2 (with the former contents of Section 2 being moved down to Section 3) address this point.
 See also our responses to R2's comments 1--3.

### 2021-06-04 paper/jitp_cover_letter/jitp_cover_letter_rr.tex
resubmitted files

--- 2021-03-23 paper/jitp_cover_letter/jitp_cover_letter.tex
@@
 
-\opening{Dear JITP Editorial Team:}
+\opening{Dear {\em JITP} Editorial Team:}
 \medskip
 
-% overview of Ted
-%% He took my course, has worked as my RA, is my advisee, has R&R at PSRM
-
-We are very excited for the opportunity to have our manuscript entitled, ``Government Websites As Data:  A methodological pipeline with application to the websites of municipalities in the United States,'' considered for publication at {\em The Journal of Information Technology \& Politics}.
-We introduce a novel methodological pipeline, along with statistical software that we have developed, for automatically scraping and processing substantive text from large sets of government websites.
-Our contribution lies in the fact that our methodology is capable of cutting through heterogeneous file types and site organizations to extract substantively meaningful and representative blocks of plain text.
-We illustrate this methodology with an application to a large sample of the websites of U.S.
-municipal governments, and find that the textual content of websites varies systematically with the partisanship of the mayor.
-
-We have presented our work in the form of a Workbench Note.
-As JITP readers and contributors are likely to engage with research problems that involve the collection of website contents, we see JITP as an ideal outlet in which to publish our research.
-We appreciate your consideration of our work, and welcome feedback on our manuscript.
+We greatly appreciate the opportunity to revise and resubmit our manuscript entitled, ``Government Websites As Data:  A methodological pipeline with application to the websites of municipalities in the United States,'' for publication at {\em The Journal of Information Technology \& Politics}.
+Revising in response to the reviewer comments has sharpened the communication of our contributions, and improved the paper overall.
+We are excited to continue developing our manuscript with the guidance of the {\em JITP} editorial team and reviewers.
 

### 2021-06-04 paper/manuscript_jitp_rr-attributed.tex
resubmitted files

--- 2021-06-03 paper/manuscript_jitp_rr.tex
@@
 
-%\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
-Email: mvn5218@psu.edu.
+\author{ Markus Neumann\footnote{Wesleyan Media Project, Postdoctoral Research Fellow,  Wesleyan University, Middletown, CT 06459, USA.
+Email: mneumann01@wesleyan.edu.
 Corresponding author.} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA.

### 2021-09-23 paper/archived/manuscript_jitp_rr-attributed.tex
started revisions for R&R 2 at JITP

--- 2021-06-04 paper/manuscript_jitp_rr-attributed.tex
@@
 Email: mneumann01@wesleyan.edu.
-Corresponding author.} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA.
-Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+Corresponding author.} \and Fridolin Linder\footnote{Intelligent Traffic Systems - Digital Lab, Siemens, Munich, Germany.
+Email: fridolin.linder@gmail.com} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
 Email: bdesmarais@psu.edu.

### 2021-09-23 paper/archived/manuscript_jitp_title_rr.tex
started revisions for R&R 2 at JITP

--- 2021-05-21 paper/archived/initial_jitp_submission/manuscript_jitp copy.tex
@@
 %============Article Title, Authors==================
-\title{\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States}
+\title{\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States\footnote{This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}}
 
-%\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
 Email: mvn5218@psu.edu.
@@
 Email: bdesmarais@psu.edu.
-This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}} \date{\today}
+}} \date{\today}
 
@@
 Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.
-
 %\noindent We explore the effect of transitions of power in municipal governments on the content of their websites.

### 2021-09-23 paper/jitp_rr_memo/jitp_rr2_memo.tex
started revisions for R&R 2 at JITP

--- 2021-06-03 paper/jitp_rr_memo/jitp_rr_memo.tex
@@
 
-Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments.
+Thank you for your comments and for giving us the opportunity to revise and resubmit our paper.
+Thanks also to Reviewer 1 for their constructive comments.
 As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible.
-Each of the comments from reviewers is addressed in the order presented in the review.
-We should note that we are now approximately 300 words over the 5,000 word limit.
+Each of the comments s addressed in the order presented in the review.
+We should note that we are now approximately NNN words over the 5,000 word limit.
 We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers.
@@
 
-\item \emph{My main recommendation is to add some figures/plots that show the substantive findings about the differences between Democratic and Republican mayors.
-You do a good job describing the findings in the text, but I think figures would also help make the findings clear to readers.
+\item \emph{ Abstract: in the last sentence, “The application validates the utility of website content data…”, I’d suggest changing the word, validate, to demonstrate/illustrate as validation of a new method requires a much more rigorous approach.
 }
 
-	\textbf{Response}: We thank the reviewer for this recommendation.
-We recognize that the STM results presented in Table 2 conveyed the content, direction of partisan bias, and statistical significance, but did not convey magnitude of differences/effects in any meaningful way.
-We have added Figure 3, in which we illustrate the magnitudes of the differences between the prevalence of topics based on the mayor's partisanship.
-We also added discussion of the differences illustrated in this figure.
-We see this as a major enhancement of our results interpretation.
+	\textbf{Response}: We agree with this comment, and revised it to be, ``illustrates.''
 
-	\item \emph{ Also, in the conclusion can you give some more examples of other research areas and questions where this approach will be useful? I think that would increase the usage and citations.  }
-
-	\textbf{Response}: We have added a paragraph to the conclusion in which we recap the uses of website content analysis that we reviewed in the front end of the paper, and also note and cite potential applications outside of the analysis of government websites and candidates.
-We give examples of politics and policy research in which researchers have analyzed (1) company websites, and (2) the websites of interest groups.
-
-	\item \emph{ Along similar lines, I hope you plan to produce step-by-step replication code and instructions about how readers can use your workflow.
-I think that too will increase the usage and citations of your approach.
+	\item \emph{ In section 2, the author(s) added the discussion of the existing studies that used manual methods.
+However, it is not clear how the author(s) connect the website evaluation studies to the use of website data.
+These seem to be two separate branches of study in the e-government website literature.
+If there is an important connection, the author(s) should explain and make a clearer argument on how the current study can help with the limitations found in the manual website evaluation study.
+Otherwise, the author(s) should use more relevant examples of the existing studies that are more tightly aligned with the subject of the current study.
 }
 
-	\textbf{Response}: We will make three categories of online materials available to help readers/users effectively apply the methods workflow we develop.
-First, we will post a conventional replication archive to Dataverse.
-The replication archive will include all of the code necessary to replicate the text analysis results we present, as well as the raw text corpora that we extracted from the websites.
-Second, the \texttt{gov2text} package is available on GitHub.
-Third, we have posted an interactive tutorial on Google Colab that demonstrates the key steps in the application of our pipeline using the \texttt{gov2text} package.
+	\textbf{Response}:
 
-\item \emph{ One minor point -- there's a typo in the abstract -- "can can" }
+	\item \emph{ Conclusion: In the last paragraph, the author(s) presented two studies by explaining the implications of the study.
+These sets of existing studies should have been discussed earlier.
+Also, the author(s) should explain more in detail why these studies show the usefulness of the new methodology that this study provides.
+Have these studies used the manual method?
+If not, any ideas on how the approaches these studies used can be applied in the context of e-government studies?
+}
 
-\textbf{Response}: Fixed.
+	\textbf{Response}:
 
@@
 
-%% R2 -------------------
-\section*{Reviewer 2}
-
-\begin{enumerate}
-
-\item \emph{  Research question & objective: From the title, it seems that the main objective of this study is to develop a new methodology that aid in collecting and analyzing data from government websites and examining the association between website content and mayoral partisanship is a way to validate.
-However, the author(s) did not develop the discussion about the challenges and issues that they found in the existing methodology after indicating the problem statement in the Introduction as “The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset (p.
-1, line 42-44).” This leaves me confused about the objective and the research question of this study.
-While the objective is to develop a new methodology, the research question is to examine the mayoral partisanship in the website contents?
-The author(s) should address this gap by clearly explaining the differences in a set of research objectives throughout the manuscript.}
-
-    \textbf{Response}:  In the initial draft we did too little to walk the reader through the challenges posed by manual collection of website data, and also did not clearly describe the organization and relationships between our primary and secondary research objectives.
-We have substantially revised the front end of the paper to further justify and clarify our research objectives.
-To better situate our contribution in the existing literature and methodology, we discuss an example of the manual data collection process used in a recent study in which manual data collection was used to gather data on the contents of the websites of U.S.
-municipalities.
-This example anchors our discussion of the cost and scale limitations associated with manual data collection.
-
-\item \emph{ Locating within the existing literature: While the main objective of this study is to develop a new methodology, it lacked discussion of the existing methodologies.
-Instead, the author(s) discussed the current literature about the partisanship and government website contents in section 2 and then jumped right into the method part in sections 3-5.
-Without locating the objective of the study in the existing literature, the conclusion is a mere summary of this study and it did not develop into a deeper discussion of theoretical and practical implications of this study.}
-
-    \textbf{Response}: We agree with this critique of our literature discussion, and we have completely revised Section 2 to focus primarily on the methods that have been applied to collecting data from government websites, and to specifically focus on the challenges posed by manual data collection.
-We also incorporated a footnote about the literature on campaign websites, which uses similar methods and thus faces the same issues.
-The discussion of mayoral partisanship and government websites has now been shifted down to the point at which we introduce our application.
-Finally, we revised the conclusion to point specifically to the implications of our contributions.
-In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.
-
-\item \emph{The abstract is not well framed to effectively introduce the goal and the question of this study. The last sentence is particularly confusing to grasp the main contribution of this study.}
-
-     \textbf{Response}:  We revised the abstract to more effectively present and justify our main objective of introducing a methodological pipeline for extracting content from government website.
-We also contextualized discussion of the application by noting that it serves to illustrate and validate the methodological contribution.
-
-\item \emph{The last paragraph that explains the structure of this study is clear, which should be used as the reference to organize the overall narratives of the manuscript.}
-
-     \textbf{Response}: We unpacked and expanded upon this paragraph in the revised presentation of our research objectives and approach.
-
-\item \emph{ While it is essential to provide the background of the association between government website content and mayoral partisanship, it did not well developed.
-As the findings are related to the types of contents of government websites depending on mayors’ partisanship, while it explained the ways government websites are used to reflect policy priorities, it lacked the discussion of the overall political objectives of each party.
-}\\
-
-    \textbf{Response}: We now recognize that our initial submission jumped right into the estimation and interpretation of differences based on mayoral partisanship, without first discussing why we would expect the priorities of mayors to differ according to party.
-We added discussion of findings from two recent articles that address how Republican and Democratic mayors differ in terms of policy priorities.
-
-    \item \emph{As this paper’s contribution is mainly methodological, there should be a separate, in-depth discussion of the problems and limitations in the existing methodologies.
-This discussion is more important than the reflection of partisanship on government website contents because it explains the need for a new methodology, supporting the contribution of this study.}\\
-
-    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection at the end of the literature section address this point.
-See also our responses to R2's comments 1--3.
-
-        \item \emph{The conclusion should be improved by adding its theoretical and practical implications by aligning with the limitations of the existing studies that you should discuss earlier (see my comment \#6.)}\\
-
-    \textbf{Response}:  We have revised the conclusion in accordance with this comment (as well as earlier comments from R2 and R1).
-
-            \item \emph{The author(s) should check typos after revising.
-Abstract: “… from large samples of government websites can can compliment … (p.
-1, line 22).” Section 2: “… mobile accessibility, and verall function… (p.
-3, line 42)”}\\
-
-    \textbf{Response}: We have closely proof read the revised manuscript.
-
-\end{enumerate}
-
-\newpage
-\singlespacing
 %\bibliographystyle{apsr}

### 2021-09-23 paper/manuscript_jitp_rr2.tex
started revisions for R&R 2 at JITP

--- 2021-06-04 paper/manuscript_jitp_rr-attributed.tex
@@
 \usepackage{graphicx}
-\usepackage{fancyvrb}
+\usepackage{color,soul}
 \usepackage{tikz}
@@
 
-\author{ Markus Neumann\footnote{Wesleyan Media Project, Postdoctoral Research Fellow,  Wesleyan University, Middletown, CT 06459, USA.
-Email: mneumann01@wesleyan.edu.
+\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA.
+Email: mvn5218@psu.edu.
 Corresponding author.} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA.
@@
 Using statistical topic modeling, we find that the partisanship of the mayor predicts differences in the contents of city websites that align with differences in the platforms of Democrats and Republicans.
-The application validates the utility of website content data extracted via our methodological pipeline.
+The application \hl{illustrates} the utility of website content data extracted via our methodological pipeline.
 

### 2021-09-24 paper/jitp_rr_memo/jitp_rr2_memo.tex
addressed reviewer points

@@
 Each of the comments s addressed in the order presented in the review.
-We should note that we are now approximately NNN words over the 5,000 word limit.
+We should note that we are now approximately 500 words over the 5,000 word limit.
 We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers.
@@
 
-	\textbf{Response}:
+	\textbf{Response}:  We revised this section to note the connection/relevance.
+We note that it is now standard practice for researchers to conduct ``supervised'' or ``human-in-the-loop'' machine coding exercises in which a relatively small number of human-coded items are used to train a machine classification algorithm such that a large set of items can be machine-coded.
+Given the ubiquity and effectiveness of human-coding attributes of government websites, there is substantial potential for supervised machine coding.
+However, in order to train a machine classifier, researchers must have access to website contents in a machine-readable format.
+Our pipeline can be used to collect such website content from a large set of websites.
 
@@
 
-	\textbf{Response}:
+	\textbf{Response}:  We removed the discussion of these studies from the conclusion.
+We added a brief paragraph to Section 2, in which we discuss the fact that researchers in other areas---beyond the analysis of government websites---have conducted computational content analyses of websites.
+We point to these studies as evidence that our pipeline will be applicable beyond the study of government websites.
 

### 2021-09-24 paper/manuscript_jitp_rr2.tex
addressed reviewer points

@@
 In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites.
-Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one.
-By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.
+\hl{It is now standard practice to combine human coding with machine-learning based content classification} \citep[e.g., ][]{sebHok2021multiclass,fowler2021political}.
+\hl{If researchers had access to machine-readable content associated with government websites, a smaller quantity of human coding could be used to develop machine classifiers for attributes of interest, which could in tern be used to classify much larger sets of websites than is possible to do with human-only coding methods.} Unfortunately, scrapers conventionally used in the social sciences \citep[e.g.,][]{cryer2019navigating} rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each site.
+By contrast, the only input our pipeline requires is the site URL.
+
+\hl{Though our main focus in the current article is on the application to government websites, it is important to note that the pipeline we develop will be useful in the context of many other research designs that involve the collection of website content.
+Though we are not familiar with existing applications of automated text analysis to government websites, previous work in other domains has involved computational content analysis of websites.} \hl{For example, }\citet{coyle2020no} \hl{analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.} \citet{kluver2015measuring} \hl{use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.}
 
@@
 Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites.
-For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.
-\citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.
 There is a broad body of research programs that could make use of the data collection and processing pipeline we present.

### 2021-09-27 paper/manuscript_jitp_rr2.tex
typo

@@
 \hl{It is now standard practice to combine human coding with machine-learning based content classification} \citep[e.g., ][]{sebHok2021multiclass,fowler2021political}.
-\hl{If researchers had access to machine-readable content associated with government websites, a smaller quantity of human coding could be used to develop machine classifiers for attributes of interest, which could in tern be used to classify much larger sets of websites than is possible to do with human-only coding methods.} Unfortunately, scrapers conventionally used in the social sciences \citep[e.g.,][]{cryer2019navigating} rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each site.
+\hl{If researchers had access to machine-readable content associated with government websites, a smaller quantity of human coding could be used to develop machine classifiers for attributes of interest, which could in turn be used to classify much larger sets of websites than is possible to do with human-only coding methods.} Unfortunately, scrapers conventionally used in the social sciences \citep[e.g.,][]{cryer2019navigating} rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each site.
 By contrast, the only input our pipeline requires is the site URL.

### 2021-09-28 paper/manuscript_jitp_rr2.tex
removed fragment

@@
 \hl{Though our main focus in the current article is on the application to government websites, it is important to note that the pipeline we develop will be useful in the context of many other research designs that involve the collection of website content.
-Though we are not familiar with existing applications of automated text analysis to government websites, previous work in other domains has involved computational content analysis of websites.} \hl{For example, }\citet{coyle2020no} \hl{analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.} \citet{kluver2015measuring} \hl{use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.}
+Previous work in other domains has involved computational content analysis of websites.} \hl{For example, }\citet{coyle2020no} \hl{analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.} \citet{kluver2015measuring} \hl{use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.}
 

### 2021-10-01 paper/jitp_rr_memo/jitp_rr2_memo.tex
typo
added sentence about scraping technique in our paper vs others to memo

@@
 As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible.
-Each of the comments s addressed in the order presented in the review.
+Each of the comments is addressed in the order presented in the review.
 We should note that we are now approximately 500 words over the 5,000 word limit.
@@
 We point to these studies as evidence that our pipeline will be applicable beyond the study of government websites.
+The previous paragraph already explains that our methodology would improve the approaches in these studies by making it possible to use the same scraping technique for all websites being studied, rather than having to specify HTML tags for each site individually.
 
